### 2024-02-29 Chapter1/chapter1.tex
:construction: Add abbreviations and notation

%!TEX root = ../thesis.tex
%*******************************************************************************
%*********************************** First Chapter *****************************
%*******************************************************************************

\chapter{Getting started}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter1/Figs/Raster/}{Chapter1/Figs/PDF/}{Chapter1/Figs/}}
\else
    \graphicspath{{Chapter1/Figs/Vector/}{Chapter1/Figs/}}
\fi

%********************************** %First Section  **************************************

\begin{section}{Introduction}
	\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
		With the great advance in communication performance, a bottleneck of wireless networks has come to energy supply. \gls{swipt} is a promising solution to connect and power mobile devices via \gls{rf} waves. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and Machine to Machine (M2M) networks. The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.

		% The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS). Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape. It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT. Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}. A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}. Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; (iii) a combination of PS and TS is generally the best strategy; (iv) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
	\end{subsection}

	\begin{equation}
		\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
		\label{eq:update_geodesic}
	\end{equation}

	% \begin{subsection}{Intelligent Reflecting Surface}
	% 	Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency. In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming). Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.

	% 	Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation. \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power. The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}. In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice. To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}. The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}. In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
	% \end{subsection}

	% \begin{subsection}{IRS-Aided SWIPT}
	% 	By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff. In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}. However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage. The proposed framework provides a flexible tradeoff between performance and complexity. To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network. In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

	% 	\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}. Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region. This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.

	% 	\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint. The problem is solved by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform and the splitting ratio are optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.

	% 	\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. To facilitate practical SWIPT implementation, the Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in time and power domains, respectively. The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes. The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.

	% 	\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that (i) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; (ii) IRS mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; (v) there exist two optimal IRS development locations, one close to the AP and one close to the UE; (vi) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; (vii) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; (viii) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; (ix) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.

	% 	\emph{Organization:} Section~\ref{se:system_model} introduces the system model. Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming design. Section~\ref{se:performance_evaluation} provides simulation results. Section~\ref{se:conclusion_and_future_works} concludes the paper.

	% 	\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices. $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\odot$ denotes the Hadamard product. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterated value and the stationary solution.
	% \end{subsection}
\end{section}

%********************************** %Second Section  *************************************
\section{Why do we use loren ipsum?} %Section - 1.2

It is a long established fact that a reader will be distracted by the readable content of a page when looking at its layout. The point of using Lorem Ipsum is that it has a more-or-less normal distribution of letters, as opposed to using `Content here, content here', making it look like readable English. Many desktop publishing packages and web page editors now use Lorem Ipsum as their default model text, and a search for `lorem ipsum' will uncover many web sites still in their infancy. Various versions have evolved over the years, sometimes by accident, sometimes on purpose (injected humour and the like).

%********************************** % Third Section  *************************************
\section{Where does it come from?}  %Section - 1.3
\label{section1.3}

Contrary to popular belief, Lorem Ipsum is not simply random text. It has roots in a piece of classical Latin literature from 45 BC, making it over 2000 years old. Richard McClintock, a Latin professor at Hampden-Sydney College in Virginia, looked up one of the more obscure Latin words, consectetur, from a Lorem Ipsum passage, and going through the cites of the word in classical literature, discovered the undoubtable source. Lorem Ipsum comes from sections 1.10.32 and 1.10.33 of "de Finibus Bonorum et Malorum" (The Extremes of Good and Evil) by Cicero, written in 45 BC. This book is a treatise on the theory of ethics, very popular during the Renaissance. The first line of Lorem Ipsum, "Lorem ipsum dolor sit amet..", comes from a line in section 1.10.32.

The standard chunk of Lorem Ipsum used since the 1500s is reproduced below for those interested. Sections 1.10.32 and 1.10.33 from ``de Finibus Bonorum et Malorum" by Cicero are also reproduced in their exact original form, accompanied by English versions from the 1914 translation by H. Rackham

``Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum."

Section 1.10.32 of ``de Finibus Bonorum et Malorum", written by Cicero in 45 BC: ``Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem. Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur? Quis autem vel eum iure reprehenderit qui in ea voluptate velit esse quam nihil molestiae consequatur, vel illum qui dolorem eum fugiat quo voluptas nulla pariatur?"

1914 translation by H. Rackham: ``But I must explain to you how all this mistaken idea of denouncing pleasure and praising pain was born and I will give you a complete account of the system, and expound the actual teachings of the great explorer of the truth, the master-builder of human happiness. No one rejects, dislikes, or avoids pleasure itself, because it is pleasure, but because those who do not know how to pursue pleasure rationally encounter consequences that are extremely painful. Nor again is there anyone who loves or pursues or desires to obtain pain of itself, because it is pain, but because occasionally circumstances occur in which toil and pain can procure him some great pleasure. To take a trivial example, which of us ever undertakes laborious physical exercise, except to obtain some advantage from it? But who has any right to find fault with a man who chooses to enjoy a pleasure that has no annoying consequences, or one who avoids a pain that produces no resultant pleasure?"

Section 1.10.33 of ``de Finibus Bonorum et Malorum", written by Cicero in 45 BC: ``At vero eos et accusamus et iusto odio dignissimos ducimus qui blanditiis praesentium voluptatum deleniti atque corrupti quos dolores et quas molestias excepturi sint occaecati cupiditate non provident, similique sunt in culpa qui officia deserunt mollitia animi, id est laborum et dolorum fuga. Et harum quidem rerum facilis est et expedita distinctio. Nam libero tempore, cum soluta nobis est eligendi optio cumque nihil impedit quo minus id quod maxime placeat facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet ut et voluptates repudiandae sint et molestiae non recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat."

1914 translation by H. Rackham: ``On the other hand, we denounce with righteous indignation and dislike men who are so beguiled and demoralized by the charms of pleasure of the moment, so blinded by desire, that they cannot foresee the pain and trouble that are bound to ensue; and equal blame belongs to those who fail in their duty through weakness of will, which is the same as saying through shrinking from toil and pain. These cases are perfectly simple and easy to distinguish. In a free hour, when our power of choice is untrammelled and when nothing prevents our being able to do what we like best, every pleasure is to be welcomed and every pain avoided. But in certain circumstances and owing to the claims of duty or the obligations of business it will frequently occur that pleasures have to be repudiated and annoyances accepted. The wise man therefore always holds in these matters to this principle of selection: he rejects pleasures to secure other greater pleasures, or else he endures pains to avoid worse pains."

### 2024-02-29 Declaration/declaration.tex
:construction: Add abbreviations and notation

% ******************************* Thesis Declaration ***************************

\begin{declaration}

I hereby declare that the contents presented in this dissertation are original and have been carried out by myself under the guidance of my supervisor Prof. Bruno Clerckx.
Any work from other researchers, scholars, or sources have been properly cited and acknowledged.
The contents have not been submitted in whole or in part for consideration of any other degree or qualification in any academic institution.
I am aware of the ethical standards and academic integrity policies of Imperial College London, and I have adhered to these principles throughout the course of my study.
In signing this declaration, I affirm my commitment to academic honesty, intellectual integrity, and the pursuit of knowledge in the service of truth and understanding.

The copyright of this thesis rests with the author. Unless otherwise indicated, its contents are licensed under a \href{https://creativecommons.org/licenses/by-nc/4.0/deed.en}{Creative Commons Attribution-Non Commercial 4.0 International License} (CC BY-NC). Under this license, you may copy and redistribute the material in any medium or format. You may also create and distribute modified versions of the work. This is on the condition that: you credit the author and do not use it, or any derivative works, for a commercial purpose. When reusing or sharing this work, ensure you make the license terms clear to others by naming the license and linking to the license text. Where a work has been adapted, you should indicate that the work has been changed and describe those changes. Please seek permission from the copyright holder for uses of this work that are not included in this license or permitted under UK Copyright Law.

The source code of all simulation results in this dissertation are publicly available at \url{https://github.com/snowztail/}.

\end{declaration}

### 2024-02-29 glossaries.tex
:construction: Add abbreviations and notation

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{am}{AM}{Arithmetic Mean}
\newacronym{ao}{AO}{Alternating Optimization}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bd}{BD}{Beyond-Diagonal}
\newacronym{ber}{BER}{Bit Error Rate}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{clt}{CLT}{Central Limit Theorem}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csit}{CSIT}{\gls{csi} at the Transmitter}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{cw}{CW}{Continuous Waveform}
\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
\newacronym{dc}{DC}{Direct Current}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dof}{DoF}{Degree of Freedom}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{eirp}{EIRP}{Effective Isotropic Radiated Power}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{gm}{GM}{Geomtric Mean}
\newacronym{gp}{GP}{Geometric Programming}
\newacronym{ic}{IC}{Interference Channel}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{los}{LoS}{Line-of-Sight}
\newacronym{m2m}{M2M}{Machine-to-Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{mse}{MSE}{Mean-Square Error}
\newacronym{nlos}{NLoS}{Non-\gls{los}}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pc}{PC}{Point-to-point Channel}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pga}{PGA}{Projected Gradient Ascent}
\newacronym{pin}{PIN}{Positive Intrinsic Negative}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{ps}{PS}{Power Splitting}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{r-e}{R-E}{Rate-Energy}
\newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
\newacronym{rfid}{RFID}{\gls{rf} Identification}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sca}{SCA}{Successive Convex Approximation}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{sdp}{SDP}{Semi-Definite Programming}
\newacronym{sdr}{SDR}{Semi-Definite Relaxation}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{siso}{SISO}{Single-Input Single-Output}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{smf}{SMF}{Scaled Matched Filter}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{svd}{SVD}{Singular Value Decomposition}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ts}{TS}{Time Switching}
\newacronym{ue}{UE}{User Equipment}
\newacronym{wf}{WF}{Water-Filling}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{zf}{ZF}{Zero-Forcing}

% \nomenclature[g-pi]{$\pi$}{ $\simeq 3.14\ldots$}
% \nomenclature[c-pi]{$\pi$}{$\simeq 3.14\ldots$}
% \nomenclature[c-pi]{$\pi$}{Archimedes' constant $\simeq 3.1415\ldots$}

\nomenclature[e-1]{$a,A$}{Scalar}
\nomenclature[e-2]{$\mathbf{a}$}{Column vector}
\nomenclature[e-3]{$\mathbf{A}$}{Matrix}
\nomenclature[e-3]{$\mathcal{A}$}{Finite set}
\nomenclature[e-4]{$\mathbf{0}$}{Zero matrix}
\nomenclature[e-5]{$\mathbf{1}$}{One matrix}
\nomenclature[e-6]{$\mathbf{I}$}{Identity matrix}

\nomenclature[n-1]{$\mathbb{R}$}{Real numbers}
\nomenclature[n-2]{$\mathbb{R}_+$}{Real nonnegative numbers}
\nomenclature[n-3]{$\mathbb{C}$}{Complex numbers}
\nomenclature[n-4]{$\mathbb{I}$}{Probability domain $[0,1]$}
\nomenclature[n-5]{$\mathbb{H}_+^{n \times n}$}{Positive semi-definite matrices of dimension $n \times n$}
\nomenclature[n-6]{$\mathbb{U}^{n \times n}$}{Unitary matrices of dimension $n \times n$}

\nomenclature[c-j]{$\jmath$}{The imaginary unit $= \sqrt{-1}$}
\nomenclature[c-e]{$e$}{Euler's number $\simeq 2.71828\ldots$}
\nomenclature[c-pi]{$\pi$}{Archimedes' constant $\simeq 3.14159\ldots$}

\nomenclature[o-a]{$(\cdot)^*$}{Complex conjugate}
\nomenclature[o-b]{$(\cdot)^\mathsf{T}$}{Transpose}
\nomenclature[o-c]{$(\cdot)^\mathsf{H}$}{Hermitian (conjugate transpose)}
\nomenclature[o-d]{$(\cdot)^\dagger$}{Moore-Penrose inverse}
\nomenclature[o-e]{$(\cdot)^+$}{Ramp functio $\max(0, \cdot)$}
\nomenclature[o-f]{$\lvert \cdot \rvert$}{Absolute value of a complex number}
\nomenclature[o-g]{$\lVert \cdot \rVert$}{Euclidean norm of a vector}
\nomenclature[o-h]{$\lVert \cdot \rVert _ \mathrm{F}$}{Frobenius norm of a matrix}
\nomenclature[o-i]{$\mathrm{arg}(\cdot)$}{Argument of a complex number}
\nomenclature[o-j]{$\mathrm{card}(\cdot)$}{Cardinality of a finite set}
\nomenclature[o-k]{$\log(\cdot)$}{Natural logarithm of a real number}
\nomenclature[o-l]{$\exp(\cdot)$}{Exponential of a scalar or square matrix}
\nomenclature[o-m]{$\mathrm{tr}(\cdot)$}{Trace of a square matrix}
\nomenclature[o-n]{$\mathrm{det}(\cdot)$}{Determinant of a square matrix}
\nomenclature[o-o]{$\mathrm{sv}(\cdot)$}{Singular values sorted from largest to smallest}
\nomenclature[o-p]{$\mathrm{diag}(\cdot)$}{Constructs a square matrix with inputs on the main diagonal}
\nomenclature[o-q]{$\mathrm{diag}^{-1}(\cdot)$}{Retrieves the main diagonal of a square matrix}
\nomenclature[o-r]{$\Re(\cdot)$}{Retrieves the real part of a complex number}
\nomenclature[o-s]{$\Im(\cdot)$}{Retrieves the imaginary part of a complex number}
\nomenclature[o-t]{$\mathbb{E}(\cdot)$}{Expectation operator}
\nomenclature[o-u]{$\mathbb{A}(\cdot)$}{Extracts the \glsdesc{dc} component of a signal}
\nomenclature[o-v]{$\odot$}{Hadamard product}
\nomenclature[o-w]{$\otimes$}{Kronecker product}
\nomenclature[o-x]{$(\cdot)_{[x:y]}$}{Shortcut for $(\cdot)_x,(\cdot)_{x+1},\ldots,(\cdot)_y$}

\nomenclature[r-a]{$\sim$}{Follows a distribution}
\nomenclature[r-b]{$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$}{Multivariate \glsdesc{cscg} with covariance $\mathbf{\Sigma}$}

\nomenclature[s-d]{$(\cdot)_\text{D}$}{Direct}
\nomenclature[s-f]{$(\cdot)_\text{F}$}{Forward}
\nomenclature[s-b]{$(\cdot)_\text{B}$}{Backward}
\nomenclature[s-i]{$(\cdot)_\text{I}$}{Information}
\nomenclature[s-p]{$(\cdot)_\text{P}$}{Power}

\nomenclature[u-a]{$(\cdot)^{(r)}$}{$r$-th iterated value}
\nomenclature[u-b]{$(\cdot)^\star$}{Stationary point}

### 2024-03-02 content/chapter1.tex
:construction: Update repo architecture
:construction: Add first chapter

--- 2024-02-29 Chapter1/chapter1.tex
@@
 
-\ifpdf
-    \graphicspath{{Chapter1/Figs/Raster/}{Chapter1/Figs/PDF/}{Chapter1/Figs/}}
-\else
-    \graphicspath{{Chapter1/Figs/Vector/}{Chapter1/Figs/}}
-\fi
+\graphicspath{{assets/chapter_1/}}
 
@@
 
-		% The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
+		The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
 \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
@@
 
-	\begin{equation}
-		\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
-		\label{eq:update_geodesic}
-	\end{equation}
-
-	% \begin{subsection}{Intelligent Reflecting Surface}
-	% 	Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
+	\begin{subsection}{Intelligent Reflecting Surface}
+		Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
 In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
@@
 
-	% 	Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
+		Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
 \cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
@@
 In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
-	% \end{subsection}
+	\end{subsection}
 
-	% \begin{subsection}{IRS-Aided SWIPT}
-	% 	By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.
+	\begin{subsection}{IRS-Aided SWIPT}
+		By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.
 In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
@@
 
-	% 	\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
+		\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
 Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
@@
 
-	% 	\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint.
+		\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint.
 The problem is solved by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
@@
 
-	% 	\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
+		\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
 To facilitate practical SWIPT implementation, the Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in time and power domains, respectively.
@@
 
-	% 	\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
+		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
 It is concluded that (i) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; (ii) IRS mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; (v) there exist two optimal IRS development locations, one close to the AP and one close to the UE; (vi) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; (vii) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; (viii) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; (ix) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+	\end{subsection}
 
-	% 	\emph{Organization:} Section~\ref{se:system_model} introduces the system model.
-Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming design.
-Section~\ref{se:performance_evaluation} provides simulation results.
-Section~\ref{se:conclusion_and_future_works} concludes the paper.
-
-	% 	\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
-$j$ denotes the imaginary unit.
-$\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
-$\boldsymbol{I}$ denotes the identity matrix.
-$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
-$\Re\{\cdot\}$ retrieves the real part of a complex entity.
-$[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
-$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
-$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
-$\odot$ denotes the Hadamard product.
-$\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
-$\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
-$\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t.
-random variable $X$ ($X$ is omitted for simplicity).
-The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
-$\sim$ means ``distributed as''.
-$(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterated value and the stationary solution.
-	% \end{subsection}
+	\begin{equation}
+		\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
+		\label{eq:update_geodesic}
+	\end{equation}
 \end{section}
 
-%********************************** %Second Section  *************************************
-\section{Why do we use loren ipsum?} %Section - 1.2
+\begin{section}{System Model}\label{se:system_model}
+	\begin{figure}[!t]
+		\centering
+		\def\svgwidth{0.9\columnwidth}
+		\input{assets/chapter_1/system.eps_tex}
+		\caption{An IRS-aided multi-carrier MISO SWIPT system.}
+		\label{fi:system}
+	\end{figure}
 
-It is a long established fact that a reader will be distracted by the readable content of a page when looking at its layout.
-The point of using Lorem Ipsum is that it has a more-or-less normal distribution of letters, as opposed to using `Content here, content here', making it look like readable English.
-Many desktop publishing packages and web page editors now use Lorem Ipsum as their default model text, and a search for `lorem ipsum' will uncover many web sites still in their infancy.
-Various versions have evolved over the years, sometimes by accident, sometimes on purpose (injected humour and the like).
+	As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
+We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels is known.
+The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
 
-%********************************** % Third Section  *************************************
-\section{Where does it come from?}  %Section - 1.3
-\label{section1.3}
+	\begin{subsection}{Transmitted Signal}
+		Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
+The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
+		\begin{equation}
+			\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
+		\end{equation}
+		where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$.
+On the other hand, the power signal transmitted over subband $n$ at time $t$ is
+		\begin{equation}
+			\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
+		\end{equation}
+		where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
+		\begin{equation}
+			\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
+		\end{equation}
+		We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+	\end{subsection}
 
-Contrary to popular belief, Lorem Ipsum is not simply random text.
-It has roots in a piece of classical Latin literature from 45 BC, making it over 2000 years old.
-Richard McClintock, a Latin professor at Hampden-Sydney College in Virginia, looked up one of the more obscure Latin words, consectetur, from a Lorem Ipsum passage, and going through the cites of the word in classical literature, discovered the undoubtable source.
-Lorem Ipsum comes from sections 1.10.32 and 1.10.33 of "de Finibus Bonorum et Malorum" (The Extremes of Good and Evil) by Cicero, written in 45 BC.
-This book is a treatise on the theory of ethics, very popular during the Renaissance.
-The first line of Lorem Ipsum, "Lorem ipsum dolor sit amet..", comes from a line in section 1.10.32.
+	\begin{subsection}{Reflection Pattern and Composite Channel}
+		According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
+The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
+IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
+		\begin{equation}
+			\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
+		\end{equation}
+		where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
+This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.} and $\theta_l \in [0,2\pi)$ is the phase shift.
+We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.
 
-The standard chunk of Lorem Ipsum used since the 1500s is reproduced below for those interested.
-Sections 1.10.32 and 1.10.33 from ``de Finibus Bonorum et Malorum" by Cicero are also reproduced in their exact original form, accompanied by English versions from the 1914 translation by H.
-Rackham
+		\begin{remark}\label{re:reflection_coefficient}
+			The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely.
+Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
+In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
+		\end{remark}
 
-``Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum."
+		At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
+The auxiliary AP-IRS-UE link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflected channel.
+Hence, the composite equivalent channel reduces to
+		\begin{equation}\label{eq:h_n}
+			\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n},
+		\end{equation}
+		where we define the cascaded incident-reflected channel at subband $n$ as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
+We also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
 
-Section 1.10.32 of ``de Finibus Bonorum et Malorum", written by Cicero in 45 BC: ``Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo.
-Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt.
-Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem.
-Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur?
-Quis autem vel eum iure reprehenderit qui in ea voluptate velit esse quam nihil molestiae consequatur, vel illum qui dolorem eum fugiat quo voluptas nulla pariatur?"
+		\begin{remark}\label{re:subband_tradeoff}
+			The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
+Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
+That is to say, IRS essentially enables a flexible subchannel design.
+In the MISO case, a similar effect also exists in the spatial domain.
+Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
+		\end{remark}
+	\end{subsection}
 
-1914 translation by H.
-Rackham: ``But I must explain to you how all this mistaken idea of denouncing pleasure and praising pain was born and I will give you a complete account of the system, and expound the actual teachings of the great explorer of the truth, the master-builder of human happiness.
-No one rejects, dislikes, or avoids pleasure itself, because it is pleasure, but because those who do not know how to pursue pleasure rationally encounter consequences that are extremely painful.
-Nor again is there anyone who loves or pursues or desires to obtain pain of itself, because it is pain, but because occasionally circumstances occur in which toil and pain can procure him some great pleasure.
-To take a trivial example, which of us ever undertakes laborious physical exercise, except to obtain some advantage from it?
-But who has any right to find fault with a man who chooses to enjoy a pleasure that has no annoying consequences, or one who avoids a pain that produces no resultant pleasure?"
+	\begin{subsection}{Received Signal}
+		The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
+		\begin{equation}
+			y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
+		\end{equation}
+		where $\tilde{n}_n(t)$ is the noise at RF band $n$.
+Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
+	\end{subsection}
 
-Section 1.10.33 of ``de Finibus Bonorum et Malorum", written by Cicero in 45 BC: ``At vero eos et accusamus et iusto odio dignissimos ducimus qui blanditiis praesentium voluptatum deleniti atque corrupti quos dolores et quas molestias excepturi sint occaecati cupiditate non provident, similique sunt in culpa qui officia deserunt mollitia animi, id est laborum et dolorum fuga.
-Et harum quidem rerum facilis est et expedita distinctio.
-Nam libero tempore, cum soluta nobis est eligendi optio cumque nihil impedit quo minus id quod maxime placeat facere possimus, omnis voluptas assumenda est, omnis dolor repellendus.
-Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet ut et voluptates repudiandae sint et molestiae non recusandae.
-Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat."
+	\begin{subsection}{Receiving Modes}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[TS receiver\label{fi:ts_receiver}]{
+				\resizebox{0.9\columnwidth}{!}{
+					\input{assets/chapter_1/ts_receiver.tex}
+				}
+			}
+			\\
+			\subfloat[PS receiver\label{fi:ps_receiver}]{
+				\resizebox{0.9\columnwidth}{!}{
+					\input{assets/chapter_1/ps_receiver.tex}
+				}
+			}
+			\caption{Diagrams of practical co-located receivers.}
+			\label{fi:receiver}
+		\end{figure}
 
-1914 translation by H.
-Rackham: ``On the other hand, we denounce with righteous indignation and dislike men who are so beguiled and demoralized by the charms of pleasure of the moment, so blinded by desire, that they cannot foresee the pain and trouble that are bound to ensue; and equal blame belongs to those who fail in their duty through weakness of will, which is the same as saying through shrinking from toil and pain.
-These cases are perfectly simple and easy to distinguish.
-In a free hour, when our power of choice is untrammelled and when nothing prevents our being able to do what we like best, every pleasure is to be welcomed and every pain avoided.
-But in certain circumstances and owing to the claims of duty or the obligations of business it will frequently occur that pleasures have to be repudiated and annoyances accepted.
-The wise man therefore always holds in these matters to this principle of selection: he rejects pleasures to secure other greater pleasures, or else he endures pains to avoid worse pains."
+		As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013}.
+The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
+During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly.
+The duration ratio $\eta$ controls the R-E tradeoff and is independent from the waveform and beamforming design.
+On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
+The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
+During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoffs.
+In the following context, we consider the optimization with the PS receiver, as the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+	\end{subsection}
+
+	\begin{subsection}{Information Decoder}
+		A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
+Therefore, the achievable rate is\footnote{It requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
+		\begin{equation}\label{eq:R}
+			R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
+		\end{equation}
+		where $\sigma_n^2$ is the noise variance at the RF-band and during the RF-to-baseband conversion on tone $n$.
+	\end{subsection}
+
+	\begin{subsection}{Energy Harvester}\label{se:energy_harvester}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
+				\resizebox{0.45\columnwidth}{!}{
+					% \includegraphics{assets/antenna_equivalent_circuit.eps}
+					\input{assets/chapter_1/antenna_equivalent_circuit.tex}
+				}
+			}
+			\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
+				\resizebox{0.45\columnwidth}{!}{
+					% \includegraphics{assets/a_single_diode_rectifier.eps}
+					\input{assets/chapter_1/a_single_diode_rectifier.tex}
+				}
+			}
+			\caption{Equivalent circuits of receive antenna and energy harvester.}
+		\end{figure}
+
+		Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output DC on both the power and shape of the received signal.
+Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has a resistance $R_{\mathrm{A}}$ and the incoming signal creates a voltage source $v_{\mathrm{S}}(t)$.
+Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
+When perfectly matched (i.e., $R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
+Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
+As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output DC is equivalent to maximizing a monotonic function\footnote{This small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+		\begin{equation}\label{eq:z}
+			z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}},
+		\end{equation}
+		where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
+With a slight abuse of notation, we refer to $z$ as the average output DC in this paper.
+It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
+However, due to the coupling effect among different frequencies, some high-order AC components compensate each other in frequency and further contribute to the output DC power.
+In other words, even-order terms with $i \ge 4$ account for the nonlinear diode behavior.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
+Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order DC terms.
+Let $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
+Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
+
+		\begin{figure*}[!t]
+			\begin{equation*}
+				\boldsymbol{W}_{\mathrm{I/P}}=
+				\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
+					\matrix [matrix of math nodes,left delimiter=(,right delimiter=)] (m)
+					{
+						\boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},2}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+						\boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},2}^H & \ddots & \vdots \\
+						\vdots & \ddots & \ddots & \boldsymbol{w}_{\mathrm{I/P},N-1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+						\boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},1}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N-1}^H & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+					};
+					\draw[dotted,thick] (m-4-1.north west) rectangle (m-4-1.south east);
+					\draw[dotted,thick,fill=gray,opacity=0.125] (m-2-1.north west) rectangle (m-2-1.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-3-2.north west) rectangle (m-3-2.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-4-3.north west) rectangle (m-4-3.south east);
+					\draw[dashed,thick,fill=gray,opacity=0.5] (m-1-1.north west) rectangle (m-1-1.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-2-2.north west) rectangle (m-2-2.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-3-3.north west) rectangle (m-3-3.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-4-4.north west) rectangle (m-4-4.south east);
+					\draw[solid,thick,fill=gray,opacity=0.25] (m-1-2.north west) rectangle (m-1-2.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-2-3.north west) rectangle (m-2-3.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-3-4.north west) rectangle (m-3-4.south east);
+					\draw[solid,thick] (m-1-4.north west) rectangle (m-1-4.south east);
+					\draw[<-] (m-4-3.south|-m.south) -- ++(0.5,-0.15) node[below]{$k=-1$};
+					\draw[<-] (rd.east|-m.south) -- ++(0.5,-0.15) node[right]{$k=0$};
+					\draw[<-] (rd.east|-m-3-4.east) -- ++(0.5,-0.15) node[right]{$k=1$};
+				\end{tikzpicture}
+			\end{equation*}
+			\caption{$\boldsymbol{W}_{\mathrm{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
+$\boldsymbol{W}_{\mathrm{I/P},k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\mathrm{I/P}}$ and nulls all remaining blocks.
+Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively.
+For $\boldsymbol{w}_{\mathrm{I/P},n_1}\boldsymbol{w}_{\mathrm{I/P},n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
+			\label{fi:block_diagonal}
+		\end{figure*}
+
+		\begin{figure*}[!b]
+			\hrule
+			\begin{align}
+				&z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
+				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
+				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
+				&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
+				&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
+			\end{align}
+		\end{figure*}
+	\end{subsection}
+
+	\begin{subsection}{Rate-Energy Region}
+		The achievable R-E region is defined as
+		\begin{align}
+			\mathcal{C}_{\mathrm{R-E}}
+			&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
+			&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
+		\end{align}
+		where $P$ is the average transmit power budget and 1/2 converts the peak value of the sine waves to the average value.
+	\end{subsection}
+\end{section}
+
+\begin{section}{Problem Formulation}\label{se:problem_formulation}
+	We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
+	\begin{maxi!}
+		{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+		\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
+		\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
+		\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
+		\addConstraint{0 \le \rho \le 1.}
+	\end{maxi!}
+	Problem~\eqref{op:original} is intricate because of the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
+To obtain a feasible solution, we propose a BCD algorithm that iteratively updates (i) the IRS phase shift; (ii) the active precoder; (iii) the waveform amplitude and splitting ratio, until convergence.
+
+	\begin{subsection}{Passive Beamforming}
+		In this section, we optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
+		\begin{align}
+			\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
+			& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+			& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+			& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi}),
+		\end{align}
+		where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t']^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+On the other hand, we define $t_{\mathrm{I/P},k}$ as
+		\begin{align}
+			t_{\mathrm{I/P},k}
+			& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
+			& = \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k},
+		\end{align}
+		where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
+		\begin{align}
+			R(\boldsymbol{\Phi})
+			& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
+			z(\boldsymbol{\Phi})
+			& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
+			& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+		\end{align}
+		To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
+Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
+		\begin{align}
+			(t_{\mathrm{I},0}^{(i)})^2
+			& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
+			t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
+			& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
+			t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
+			& \ge t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}.\label{eq:taylor_3}
+		\end{align}
+		Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real-valued because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
+Due to symmetry \cite{Golub2013}, we have
+		\begin{equation}\label{eq:coupled_terms}
+			\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
+		\end{equation}
+		Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
+		\begin{figure*}[!b]
+			\hrule
+			\begin{align}
+				\tilde{z}(\boldsymbol{\Phi}^{(i)})
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}\right).\label{eq:z_irs_approx}
+			\end{align}
+		\end{figure*}
+		\begin{maxi!}
+			{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
+			\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
+			\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_modulus}
+			\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
+			\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
+		\end{maxi!}
+		We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}.
+In this specific case, we found the solution provided by CVX toolbox \cite{Grant2016} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
+This conclusion is summarized below.
+
+		\begin{proposition}\label{pr:relaxation}
+			Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by SDR.
+		\end{proposition}
+
+		% \begin{proof}\label{pf:relaxation}
+		% 	Please refer to Appendix~\ref{ap:relaxation}.
+		% \end{proof}
+
+		In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
+The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010b}.
+
+		\begin{algorithm}[!t]
+			\caption{SCA: IRS Phase Shift.}
+			\label{al:sca}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+				\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
+				\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
+				\Repeat
+					\State $i \gets i + 1$
+					\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
+					\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
+					\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+				\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+				\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
+				\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
+				\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+
+		\begin{proposition}\label{pr:sca}
+			For any feasible initial point with given waveform and splitting ratio, the SCA Algorithm~\ref{al:sca} is guaranteed to converge to local optimal points of the original problem~\eqref{op:original}.
+		\end{proposition}
+
+		% \begin{proof}\label{pf:sca}
+		% 	Please refer to Appendix~\ref{ap:sca}.
+		% \end{proof}
+	\end{subsection}
+
+	\begin{subsection}{Active Beamforming}
+		The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
+Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduce the size of variables from $2MN$ to $2(M+N)$.
+The weight on subband $n$ is essentially
+		\begin{equation}\label{eq:w}
+			\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n},
+		\end{equation}
+		where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
+Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$.
+The MRT precoder at subband $n$ is given by
+		\begin{equation}\label{eq:b_n}
+			\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
+		\end{equation}
+
+		\begin{proposition}\label{pr:mrt}
+			For single-user SWIPT, the global optimal information and power precoders coincide at the MRT.
+		\end{proposition}
+
+		% \begin{proof}\label{pf:mrt}
+		% 	Please refer to Appendix~\ref{ap:mrt}.
+		% \end{proof}
+	\end{subsection}
+
+	\begin{subsection}{Waveform and Splitting Ratio}
+		Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
+On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
+Hence, the rate \eqref{eq:R} reduces to
+		\begin{equation}\label{eq:R_waveform}
+			R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right),
+		\end{equation}
+		and the DC \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
+		\begin{figure*}[!b]
+			\hrule
+			\begin{align}
+				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
+				& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
+			\end{align}
+		\end{figure*}
+		\begin{maxi!}
+			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
+			\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}.}
+		\end{maxi!}
+		Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
+		\begin{mini!}
+			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
+			\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
+			\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
+			\addConstraint{\rho + \bar{\rho} \le 1.}\label{co:waveform_splitting_ratio}
+		\end{mini!}
+		It can be concluded that $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power is wasted at the receiver.
+The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
+		\begin{align}
+			1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
+			z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}.
+		\end{align}
+		We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
+		\begin{mini!}
+			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
+			\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
+			\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
+			\addConstraint{\rho + \bar{\rho} \le 1,}
+		\end{mini!}
+		where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$ and $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
+		\begin{align}
+			\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
+			\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
+		\end{align}
+		With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2016}.
+We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
+The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
+
+		\begin{algorithm}[!t]
+			\caption{GP: Waveform Amplitude and Splitting Ratio.}
+			\label{al:gp}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
+				\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+				\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+				\Repeat
+					\State $i \gets i + 1$
+					\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
+					\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
+					\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+				\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
+				\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+
+		\begin{proposition}\label{pr:gp}
+			For any feasible initial point, the GP Algorithm~\ref{al:gp} is guaranteed to converge to local optimal points of the waveform amplitude and splitting ratio design problem \eqref{op:waveform}.
+		\end{proposition}
+
+		\begin{proof}\label{pf:gp}
+			Please refer to \cite{Clerckx2016a,Clerckx2018b}.
+		\end{proof}
+	\end{subsection}
+
+	\begin{subsection}{Low-Complexity Adaptive Design}
+		To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in time and power domains, respectively.
+For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
+		\begin{equation}\label{eq:wf}
+			s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
+		\end{equation}
+		where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
+The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
+On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
+		\begin{equation}\label{eq:smf}
+			s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
+		\end{equation}
+		where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity.
+When the receiver works in TS mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session).
+When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
+		\begin{align}
+			s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
+			s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
+		\end{align}
+		where the $\delta$ determines the power ratio of multisine waveform at the transmitter, and $\rho$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
+Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient SWIPT design.}
+
+		Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
+Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no SCA is involved.
+The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
+Similarly, no loss is introduced by SDR and local optimality is guaranteed.
+The proofs are omitted here.
+Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010b}.
+Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
+
+		\begin{algorithm}[!t]
+			\caption{M-SCA: IRS Phase Shift.}
+			\label{al:m_sca}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
+				\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+				\If{$\rho=0$}
+					\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+				\Else
+					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
+					\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
+					\Repeat
+						\State $i \gets i + 1$
+							\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+							\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
+							\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+					\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
+				\EndIf
+				\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
+				\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+	\end{subsection}
+
+	\begin{subsection}{Block Coordinate Descent}
+		Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+The steps are summarized in the BCD Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
+It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
+
+		\begin{algorithm}[!t]
+			\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
+			\label{al:bcd}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
+				\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+				\State Compute $z^{(0)}$ by \eqref{eq:z_waveform}
+				\Repeat
+					\State $i \gets i + 1$
+					\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$, $\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
+					\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+					\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by Algorithm~\ref{al:gp}
+					\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+					\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
+				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+				\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+
+		For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
+The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
+The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010b}.
+
+		\begin{algorithm}[!t]
+			\caption{LC-BCD: Waveform and Beamforming.}
+			\label{al:lc_bcd}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
+				\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+				\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+				\Repeat
+					\State $i \gets i + 1$
+					\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
+					\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+					\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
+					\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+					\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\If{$\rho=0$}
+						\State $\Delta \gets R^{(i)} - R^{(i-1)}$
+					\Else
+						\State $\Delta \gets z^{(i)} - z^{(i-1)}$
+					\EndIf
+				\Until $\lvert \Delta \rvert \le \epsilon$
+				\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+	\end{subsection}
+\end{section}
+
+\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
+	\begin{figure}[!t]
+		\centering
+		\def\svgwidth{0.9\columnwidth}
+		% \import{assets/}{layout.eps_tex}
+		\input{assets/chapter_1/layout.eps_tex}
+		\caption{System layout in simulation.}
+		\label{fi:layout}
+	\end{figure}
+
+	To evaluate the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
+Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
+$d_{\mathrm{D}}=\qty{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$ are chosen as reference.
+The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
+We consider a large open space Wi-Fi-like environment at center frequency \qty{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
+Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \qty{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
+All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
+CSCG variables.
+Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\qty{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
+We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\qty{40}{dBm}$, the receive antenna gain as \qty{3}{dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
+To further reduce the complexity, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound for the LC-BCD algorithm.
+Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+
+	\begin{figure}[!t]
+		\centering
+		\resizebox{0.8\columnwidth}{!}{
+			% \includegraphics{assets/channel_amplitude.eps}
+			\input{assets/chapter_1/channel_amplitude.tex}
+		}
+		\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+		\label{fi:channel_amplitude}
+	\end{figure}
+
+	Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the sorted equivalent subchannel amplitude for one channel realization.
+Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
+Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity.
+On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
+This is reminiscent of the WF scheme at high SNR, but is realized by channel alignment instead of resource allocation.
+Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding an IRS (the plots are not attached).
+In other words, IRS has a subtle impact on the waveform design.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[R-E region\label{fi:re_subband}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_subband.eps}
+				\input{assets/chapter_1/re_subband.tex}
+			}
+		}
+		\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/waveform_subband.eps}
+				\input{assets/chapter_1/waveform_subband.tex}
+			}
+		}
+		\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+	\end{figure}
+
+	Fig.~\subref*{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
+First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
+This is because less power is allocated to each subband but more balanced DC terms are introduced by frequency coupling to boost the harvested energy.
+On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT.
+It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+This observation origins from the rectifier nonlinearity.
+Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2}, while the multisine has $(2N^3+N)/3$ monomials as the components of different frequencies compensate and produce DC.
+Second, the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
+When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
+When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region.
+It aligns with the conclusion based on the conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
+As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model.
+Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[R-E region\label{fi:re_noise}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_noise.eps}
+				\input{assets/chapter_1/re_noise.tex}
+			}
+		}
+		\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/splitting_ratio_noise.eps}
+				\input{assets/chapter_1/splitting_ratio_noise.tex}
+			}
+		}
+		\caption{Average R-E region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+	\end{figure}
+
+	The average noise power influences the R-E region as shown in Fig.~\subref*{fi:re_noise}.
+First, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
+At low SNR, the power is allocated to the modulated waveform on a few strongest subbands to achieve a high rate.
+As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power because of frequency coupling and harvester nonlinearity.
+Second, there exists a turning point in the R-E region, especially for a low noise level ($\sigma_n^2 \le \qty{-40}{dBm}$).
+The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
+As $\bar{R}$ further decreases, thanks to the advantage of multisine, a superposed waveform with a small $\rho$ can outperform a modulated waveform with a large $\rho$.
+The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
+Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[R-E region\label{fi:re_distance}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_distance.eps}
+				\input{assets/chapter_1/re_distance.tex}
+			}
+		}
+		\subfloat[Path loss product\label{fi:path_loss}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/path_loss.eps}
+				\input{assets/chapter_1/path_loss.tex}
+			}
+		}
+		\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{V}}=\qty{2}{\meter}$.}
+	\end{figure}
+
+	In Fig.~\subref*{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
+Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
+Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \qty{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
+It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[R-E region\label{fi:re_tx}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_tx.eps}
+				\input{assets/chapter_1/re_tx.tex}
+			}
+		}
+		\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/scaling_tx.eps}
+				\input{assets/chapter_1/scaling_tx.tex}
+			}
+		}
+		\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{0.2}{\meter}$.}
+	\end{figure}
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[R-E region\label{fi:re_reflector}]{
+			\resizebox{0.425\columnwidth}{!}{
+				% \includegraphics{assets/re_reflector.eps}
+				\input{assets/chapter_1/re_reflector.tex}
+			}
+		}
+		\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
+			\resizebox{0.475\columnwidth}{!}{
+				% \includegraphics{assets/scaling_reflector.eps}
+				\input{assets/chapter_1/scaling_reflector.tex}
+			}
+		}
+		\caption{Average R-E region, WIT SNR and WPT DC versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{0.2}{\meter}$.}
+	\end{figure}
+
+	The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
+First, it is observed that adding either active or passive elements can improve the equivalent SNR, which produces a nearly concave R-E region and favors the PS receiver.
+Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
+To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; (ii) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dBA} gap compared to the nonlinear model-based SMF and GP designs.
+Third, doubling $M$ brings a \qty{3}{\dB} gain at the output SNR and a \qty{12}{dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
+Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \qty{6}{\dB} gain at the output SNR and a \qty{24}{dBA} increase at the harvested DC.
+From the perspective of WIT, it suggests that passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
+An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
+From the perspective of WPT, it suggests that passive beamforming comes with a power scaling order $L^4$ under the truncated nonlinear harvester model.
+We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel becomes negligible.
+Let $X$ be the cascaded small-scale fading coefficient.
+The DC in such case reduces to
+	\begin{equation}
+		z = \beta_2 \Lambda_{\mathrm{R}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{R}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
+	\end{equation}
+	which scales quartically with $L$.
+Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
+These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[$B=\qty{1}{\MHz}$\label{fi:re_irs_1mhz}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_irs_1mhz.eps}
+				\input{assets/chapter_1/re_irs_1mhz.tex}
+			}
+		}
+		\subfloat[$B=\qty{10}{\MHz}$\label{fi:re_irs_10mhz}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_irs_10mhz.eps}
+				\input{assets/chapter_1/re_irs_10mhz.tex}
+			}
+		}
+		\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+	\end{figure}
+
+	Figs.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
+The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.
+The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}.
+The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region.
+The random IRS models the phase shift of all elements as i.i.d.
+uniform random variables over $[0, 2\pi)$.
+First, random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
+Their R-E boundaries coincide as the antenna mode reflection of the random IRS is canceled out after averaging.
+Second, when the bandwidth is small, the performance of ideal, adaptive, and WIT/WPT-optimized IRS are similar; when the bandwidth is large, the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS.
+In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
+It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
+Hence, the achievable R-E region is obtained by optimizing the waveform amplitude and splitting ratio.
+On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoffs points for broadband SWIPT.
+As shown in Fig.~\ref{fi:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high SNR, or focused on a few strongest subbands to boost the output DC, thanks to adaptive passive beamforming.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_csi.eps}
+				\input{assets/chapter_1/re_csi.tex}
+			}
+		}
+		\subfloat[Quantized IRS\label{fi:re_quantization}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_quantization.eps}
+				\input{assets/chapter_1/re_quantization.tex}
+			}
+		}
+		\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.
+$\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect CSIT and no CSIT (and random IRS); $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
+	\end{figure}
+
+	We then explore the impacts of imperfect cascaded CSIT and quantized IRS on the R-E performance.
+Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
+We assume the cascaded channel at subband $n$ is
+	\begin{equation}
+		\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n},
+	\end{equation}
+	where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
+These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
+\end{section}
+
+\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
+	This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in an IRS-aided multi-carrier MISO SWIPT system.
+Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
+A three-stage BCD algorithm was proposed to solve the problem.
+In the first stage, the IRS phase shift was obtained by the SCA technique and eigen decomposition.
+In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the GP method.
+We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves a good balance between performance and complexity.
+Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
+Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
+Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of the waveform design.
+
+	One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
+Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.
+\end{section}

### 2024-03-02 content/chapter_1.tex
:construction: Update hooks for first chapter

--- 2024-03-02 content/chapter1.tex
@@
 \begin{section}{Introduction}
-	\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
+	\begin{subsection}{\glsfmtlong{swipt}}
 		With the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
 \gls{swipt} is a promising solution to connect and power mobile devices via \gls{rf} waves.
-It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and Machine to Machine (M2M) networks.
-The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
+It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and \gls{m2m} networks.
+The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on \gls{wpt} and \gls{swipt} \cite{Clerckx2019}.
 
-		The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
-\cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
-Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
-On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape.
+		The concept of \gls{swipt} was first cast in \cite{Varshney2008}, where the authors investigated the \gls{r-e} tradeoff for a flat Gaussian channel and typical discrete channels.
+\cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., \gls{ts} and \gls{ps}.
+Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the \gls{r-e} region for multi-antenna broadcast and interference channels.
+On the other hand, \cite{Trotter2009} pointed out that the \gls{rf}-to-\gls{dc} conversion efficiency of rectifiers depends on the input power and waveform shape.
 It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
-Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT.
+Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for \gls{wpt}.
 Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}.
-A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
-Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; (iii) a combination of PS and TS is generally the best strategy; (iv) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
-Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
-The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
-It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
-Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
+A low-complexity adaptive waveform design by \gls{smf} was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
+Beyond \gls{wpt}, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to \gls{swipt} design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the \gls{r-e} region; (iii) a combination of \gls{ps} and \gls{ts} is generally the best strategy; (iv) the optimal input distribution is not the conventional \gls{cscg}; (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient \gls{swipt} design.
+Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for \gls{swipt} under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier \gls{swipt}, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier \gls{swipt}.
+The answers shed new light to the fundamental limits of \gls{swipt} and practical signaling (e.g., modulation and waveform) strategies.
+It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of \gls{cscg} and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger \gls{r-e} region compared to conventional \gls{cscg}.
+Recently, \cite{Varasteh2020a} used machine learning techniques to design \gls{swipt} signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
 	\end{subsection}
 
-	\begin{subsection}{Intelligent Reflecting Surface}
-		Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
+	\begin{subsection}{\glsfmtlong{ris}}
+		\gls{ris} has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
+In practice, a \gls{ris} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
+Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the \gls{ris} assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
 
 		Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
-\cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
+\cite{Wu2018} proposed a \gls{ris}-assisted \gls{miso} system and jointly optimized the precoder at the \gls{ap} and the phase shifts at the \gls{ris} to minimize the transmit power.
 The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
 In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
-To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}.
-In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
+To estimate the cascaded \gls{ap}-\gls{ris}-\gls{ue} link without \gls{rf}-chains at the \gls{ris}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
+The hardware architecture, design challenges, and application opportunities of practical \gls{ris} were covered in \cite{Wu2020}.
+In \cite{Dai2020}, a prototype \gls{ris} with \num{256} \num{2}-bit elements based on \gls{pin} diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
 	\end{subsection}
 
-	\begin{subsection}{IRS-Aided SWIPT}
-		By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.
-In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
-It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
-However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
+	\begin{subsection}{\glsfmtshort{ris}-Aided \glsfmtshort{swipt}}
+		By integrating \gls{ris} with \gls{swipt}, the constructive reflection can boost the end-to-end power efficiency and improve the \gls{r-e} tradeoff.
+In multi-user cases, dedicated energy beams were proved unnecessary for the weighted sum-power maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
+It was also claimed that \gls{los} links could boost the power efficiency since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
+However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the \gls{rf} and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
+Based on practical \gls{ris} and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based \gls{ris}-assisted \gls{swipt} system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
 The proposed framework provides a flexible tradeoff between performance and complexity.
 To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.
-We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
+In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output \gls{dc} power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for \gls{swipt} with the passive beamforming capability of \gls{ris}, to investigate the \gls{r-e} tradeoff for one \gls{swipt} user with co-located information decoder and energy harvester.
+We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the \gls{r-e} region of \gls{ris}-aided \gls{swipt}?} The contributions of this paper are summarized as follows.
 
-		\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
-Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
-To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
-The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region.
-This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
+		\emph{First,} we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
+Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output \gls{dc} power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce \gls{dc}), waveform coupling (i.e., different waveforms jointly contribute to \gls{dc}), and high-order objective function.
+To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the \gls{ts} and \gls{ps} receiving modes.
+The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable \gls{r-e} region.
+This is the first paper to propose a joint waveform, active and passive beamforming architecture for \gls{ris}-aided \gls{swipt}.
 
-		\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint.
-The problem is solved by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
-For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof.
-Finally, the superposed waveform and the splitting ratio are optimized by the Geometric Programming (GP) technique.
-The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
-This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.
+		\emph{Second,} we characterize each \gls{r-e} boundary point by energy maximization under a rate constraint.
+The problem is solved by a \gls{bcd} algorithm based on the \gls{csit}.
+For active beamforming, we prove that the global optimal active information and power precoders coincide at \gls{mrt} even with rectifier nonlinearity.
+For passive beamforming, we propose a \gls{sca} algorithm and retrieve the \gls{ris} phase shift by eigen decomposition with optimality proof.
+Finally, the superposed waveform and the splitting ratio are optimized by the \gls{gp} technique.
+The \gls{ris} phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
+This is the first paper to jointly optimize waveform and active/passive beamforming in \gls{ris}-aided \gls{swipt}.
 
-		\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
-To facilitate practical SWIPT implementation, the Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in time and power domains, respectively.
+		\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the \gls{gp} algorithm.
+To facilitate practical \gls{swipt} implementation, the \gls{wf} strategy for modulated waveform and the \gls{smf} strategy for multisine waveform are combined in time and power domains, respectively.
 The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes.
-The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.
+The proposed low-complexity \gls{bcd} algorithm achieves a good balance between performance and complexity.
 
 		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that (i) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; (ii) IRS mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; (v) there exist two optimal IRS development locations, one close to the AP and one close to the UE; (vi) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; (vii) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; (viii) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; (ix) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
+It is concluded that (i) \gls{ris} enables constructive reflection and flexible subchannel design in the frequency domain that is essential for \gls{swipt} systems; (ii) \gls{ris} mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) \gls{ts} is preferred at low \gls{snr} while \gls{ps} is preferred at high \gls{snr}; (v) there exist two optimal \gls{ris} development locations, one close to the \gls{ap} and one close to the \gls{ue}; (vi) the output \gls{snr} scales linearly with the number of transmit antennas and quadratically with the number of \gls{ris} elements; (vii) due to the rectifier nonlinearity, the output \gls{dc} scales quadratically with the number of transmit antennas and quartically with the number of \gls{ris} elements; (viii) for narrowband \gls{swipt}, the optimal active and passive beamforming for any \gls{r-e} point are also optimal for the whole \gls{r-e} region; (ix) for broadband \gls{swipt}, the optimal active and passive beamforming depend on specific \gls{r-e} point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded \gls{csit} and finite \gls{ris} reflection states.
 	\end{subsection}
-
-	\begin{equation}
-		\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
-		\label{eq:update_geodesic}
-	\end{equation}
 \end{section}
@@
 		\input{assets/chapter_1/system.eps_tex}
-		\caption{An IRS-aided multi-carrier MISO SWIPT system.}
+		\caption{An \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
 		\label{fi:system}
@@
 
-	As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where an $M$-antenna AP delivers information and power simultaneously, through an $L$-element IRS, to a single-antenna UE over $N$ orthogonal evenly-spaced subbands.
-We consider a quasi-static block fading model and assume the CSIT of direct and cascaded channels is known.
+	As shown in Fig.~\ref{fi:system}, we propose a \gls{ris}-aided \gls{swipt} system where an $M$-antenna \gls{ap} delivers information and power simultaneously, through an $L$-element \gls{ris}, to a single-antenna \gls{ue} over $N$ orthogonal evenly-spaced subbands.
+We consider a quasi-static block fading model and assume the \gls{csit} of direct and cascaded channels is known.
 The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
@@
 The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
+\gls{ris} element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
 		\begin{equation}
@@
 		\end{equation}
-		where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the IRS, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
-This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.} and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the IRS vector and matrix, respectively.
+		where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the \gls{ris}, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
+This paper sticks to the most common \gls{ris} model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical \gls{ris}-aided \gls{swipt}.} and $\theta_l \in [0,2\pi)$ is the phase shift.
+We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the \gls{ris} vector and matrix, respectively.
 
@@
 Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
-In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each IRS element is the same at all subbands.
+In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each \gls{ris} element is the same at all subbands.
 		\end{remark}
 
-		At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the IRS-UE reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
-The auxiliary AP-IRS-UE link can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflected channel.
+		At subband $n$, we denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the \gls{ap}-\gls{ris} incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the \gls{ris}-\gls{ue} reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
+The auxiliary \gls{ap}-\gls{ris}-\gls{ue} link can be modeled as a concatenation of the incident channel, the \gls{ris} reflection, and the reflected channel.
 Hence, the composite equivalent channel reduces to
@@
 			The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
-Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier SWIPT.
+Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier \gls{swipt}.
 For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
-That is to say, IRS essentially enables a flexible subchannel design.
-In the MISO case, a similar effect also exists in the spatial domain.
+That is to say, \gls{ris} essentially enables a flexible subchannel design.
+In the \gls{miso} case, a similar effect also exists in the spatial domain.
 Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
@@
 	\begin{subsection}{Received Signal}
-		The received superposed signal at the single-antenna UE is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
+		The received superposed signal at the single-antenna \gls{ue} is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
 		\begin{equation}
@@
 		\end{equation}
-		where $\tilde{n}_n(t)$ is the noise at RF band $n$.
+		where $\tilde{n}_n(t)$ is the noise at \gls{rf} band $n$.
 Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
@@
 			\centering
-			\subfloat[TS receiver\label{fi:ts_receiver}]{
+			\subfloat[\gls{ts} receiver\label{fi:ts_receiver}]{
 				\resizebox{0.9\columnwidth}{!}{
@@
 			\\
-			\subfloat[PS receiver\label{fi:ps_receiver}]{
+			\subfloat[\gls{ps} receiver\label{fi:ps_receiver}]{
 				\resizebox{0.9\columnwidth}{!}{
@@
 		As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013}.
-The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
-During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly.
-The duration ratio $\eta$ controls the R-E tradeoff and is independent from the waveform and beamforming design.
-On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
+The \gls{ts} receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
+During each session, the transmitter optimizes the waveform for either \gls{wit} or \gls{wpt}, while the receiver activates the information decoder or the energy harvester correspondingly.
+The duration ratio $\eta$ controls the \gls{r-e} tradeoff and is independent from the waveform and beamforming design.
+On the other hand, the \gls{ps} receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
 The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
-During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoffs.
-In the following context, we consider the optimization with the PS receiver, as the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different \gls{r-e} tradeoffs.
+In the following context, we consider the optimization with the \gls{ps} receiver, as the \gls{ts} receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
 	\end{subsection}
@@
 		\end{equation}
-		where $\sigma_n^2$ is the noise variance at the RF-band and during the RF-to-baseband conversion on tone $n$.
+		where $\sigma_n^2$ is the noise variance at the \gls{rf}-band and during the \gls{rf}-to-baseband conversion on tone $n$.
 	\end{subsection}
@@
 
-		Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output DC on both the power and shape of the received signal.
+		Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output \gls{dc} on both the power and shape of the received signal.
 Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has a resistance $R_{\mathrm{A}}$ and the incoming signal creates a voltage source $v_{\mathrm{S}}(t)$.
@@
 Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output DC is equivalent to maximizing a monotonic function\footnote{This small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output \gls{dc} is equivalent to maximizing a monotonic function\footnote{This small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
 		\begin{equation}\label{eq:z}
@@
 		where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
-With a slight abuse of notation, we refer to $z$ as the average output DC in this paper.
-It can be observed that the conventional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
-However, due to the coupling effect among different frequencies, some high-order AC components compensate each other in frequency and further contribute to the output DC power.
+With a slight abuse of notation, we refer to $z$ as the average output \gls{dc} in this paper.
+It can be observed that the conventional linear harvester model, where the output \gls{dc} power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
+However, due to the coupling effect among different frequencies, some high-order frequency components compensate each other in frequency and further contribute to the output \gls{dc} power.
 In other words, even-order terms with $i \ge 4$ account for the nonlinear diode behavior.
 For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order DC terms.
+Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order \gls{dc} terms.
 Let $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
@@
 	\begin{subsection}{Rate-Energy Region}
-		The achievable R-E region is defined as
+		The achievable \gls{r-e} region is defined as
 		\begin{align}
-			\mathcal{C}_{\mathrm{R-E}}
+			\mathcal{C}_{\mathrm{\gls{r-e}}}
 			&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
@@
 \begin{section}{Problem Formulation}\label{se:problem_formulation}
-	We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
+	We characterize each \gls{r-e} boundary point through a current maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
 	\begin{maxi!}
@@
 	Problem~\eqref{op:original} is intricate because of the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
-To obtain a feasible solution, we propose a BCD algorithm that iteratively updates (i) the IRS phase shift; (ii) the active precoder; (iii) the waveform amplitude and splitting ratio, until convergence.
+To obtain a feasible solution, we propose a \gls{bcd} algorithm that iteratively updates (i) the \gls{ris} phase shift; (ii) the active precoder; (iii) the waveform amplitude and splitting ratio, until convergence.
 
 	\begin{subsection}{Passive Beamforming}
-		In this section, we optimize the IRS phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
+		In this section, we optimize the \gls{ris} phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
 		\begin{align}
@@
 		\end{equation}
-		Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
+		Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the \gls{dc} approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
 		\begin{figure*}[!b]
@@
 		\end{maxi!}
-		We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}.
-In this specific case, we found the solution provided by CVX toolbox \cite{Grant2016} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
+		We then apply \gls{sdr} to the unit-rank constraint \eqref{co:irs_rank} and formulate a \gls{sdp} with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}.
+In this specific case, we found the solution provided by \texttt{CVX toolbox} \cite{Grant2016} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
 This conclusion is summarized below.
@@
 		\begin{proposition}\label{pr:relaxation}
-			Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by SDR.
+			Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by \gls{sdr}.
 		\end{proposition}
@@
 
-		In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	IRS vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
-The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
-Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010b}.
+		In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	\gls{ris} vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
+The passive beamforming design is summarized in the \gls{sca} Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{\gls{sca}}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{\gls{sca}}}$ denotes the number of \gls{sca} iterations \cite{Luo2010b}.
 
 		\begin{algorithm}[!t]
-			\caption{SCA: IRS Phase Shift.}
+			\caption{\gls{sca}: \gls{ris} Phase Shift.}
 			\label{al:sca}
@@
 		\begin{proposition}\label{pr:sca}
-			For any feasible initial point with given waveform and splitting ratio, the SCA Algorithm~\ref{al:sca} is guaranteed to converge to local optimal points of the original problem~\eqref{op:original}.
+			For any feasible initial point with given waveform and splitting ratio, the \gls{sca} Algorithm~\ref{al:sca} is guaranteed to converge to local optimal points of the original problem~\eqref{op:original}.
 		\end{proposition}
@@
 Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$.
-The MRT precoder at subband $n$ is given by
+The \gls{mrt} precoder at subband $n$ is given by
 		\begin{equation}\label{eq:b_n}
@@
 		\begin{proposition}\label{pr:mrt}
-			For single-user SWIPT, the global optimal information and power precoders coincide at the MRT.
+			For single-user \gls{swipt}, the global optimal information and power precoders coincide at the \gls{mrt}.
 		\end{proposition}
@@
 	\begin{subsection}{Waveform and Splitting Ratio}
-		Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
+		Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given \gls{ris} phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
 On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
@@
 		\end{equation}
-		and the DC \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
+		and the \gls{dc} \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
 		\begin{figure*}[!b]
@@
 		\end{maxi!}
-		Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed GP
+		Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed \gls{gp}
 		\begin{mini!}
@@
 		\end{align}
-		We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
+		We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the \gls{gm}-\gls{am} inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
 		\begin{mini!}
@@
 		\end{align}
-		With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2016}.
+		With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as \texttt{CVX toolbox} \cite{Grant2016}.
 We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
-The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
+The joint waveform amplitude and splitting ratio design is summarized in the \gls{gp} Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
 
 		\begin{algorithm}[!t]
-			\caption{GP: Waveform Amplitude and Splitting Ratio.}
+			\caption{\gls{gp}: Waveform Amplitude and Splitting Ratio.}
 			\label{al:gp}
@@
 		\begin{proposition}\label{pr:gp}
-			For any feasible initial point, the GP Algorithm~\ref{al:gp} is guaranteed to converge to local optimal points of the waveform amplitude and splitting ratio design problem \eqref{op:waveform}.
+			For any feasible initial point, the \gls{gp} Algorithm~\ref{al:gp} is guaranteed to converge to local optimal points of the waveform amplitude and splitting ratio design problem \eqref{op:waveform}.
 		\end{proposition}
@@
 	\begin{subsection}{Low-Complexity Adaptive Design}
-		To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in time and power domains, respectively.
-For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
+		To facilitate practical \gls{swipt} implementation, we propose two closed-form adaptive waveform amplitude schemes by combining \gls{wf} and \gls{smf} in time and power domains, respectively.
+For \gls{wit}, the optimal \gls{wf} strategy assigns the amplitude of modulated tone $n$ by
 		\begin{equation}\label{eq:wf}
@@
 The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
-On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
+On the other hand, \gls{smf} was proposed in \cite{Clerckx2017} as a suboptimal \gls{wpt} resource allocation scheme that assigns the amplitude of sinewave $n$ by
 		\begin{equation}\label{eq:smf}
@@
 		where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity.
-When the receiver works in TS mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session).
-When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
+When the receiver works in \gls{ts} mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session).
+When the receiver works in \gls{ps} mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
 		\begin{align}
@@
 		\end{align}
-		where the $\delta$ determines the power ratio of multisine waveform at the transmitter, and $\rho$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the WIT point and $\delta^{\star}=\rho^{\star}=1$ at the WPT point when $N$ is relatively large.
-Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient SWIPT design.}
+		where the $\delta$ determines the power ratio of multisine waveform at the transmitter, and $\rho$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the \gls{wit} point and $\delta^{\star}=\rho^{\star}=1$ at the \gls{wpt} point when $N$ is relatively large.
+Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient \gls{swipt} design.}
 
@@
 Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no SCA is involved.
-The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode.
-Similarly, no loss is introduced by SDR and local optimality is guaranteed.
+To achieve the \gls{wit} point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no \gls{sca} is involved.
+The Modified-\gls{sca} (M-\gls{sca}) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in \gls{ps} mode.
+Similarly, no loss is introduced by \gls{sdr} and local optimality is guaranteed.
 The proofs are omitted here.
-Since each SDP involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010b}.
-Note that no SCA is involved at the WIT point where $I_{\mathrm{M-SCA}}=1$.
+Since each \gls{sdp} involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-\gls{sca}}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-\gls{sca}}}$ denotes the number of M-\gls{sca} iterations \cite{Luo2010b}.
+Note that no \gls{sca} is involved at the \gls{wit} point where $I_{\mathrm{M-\gls{sca}}}=1$.
 
 		\begin{algorithm}[!t]
-			\caption{M-SCA: IRS Phase Shift.}
+			\caption{M-\gls{sca}: \gls{ris} Phase Shift.}
 			\label{al:m_sca}
@@
 	\begin{subsection}{Block Coordinate Descent}
-		Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
-The steps are summarized in the BCD Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
+		Based on the direct and cascaded \gls{csit}, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+The steps are summarized in the \gls{bcd} Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
 It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
@@
 		\begin{algorithm}[!t]
-			\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
+			\caption{\gls{bcd}: Waveform, Beamforming and Splitting Ratio.}
 			\label{al:bcd}
@@
 
-		For the low-complexity design under PS mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-To achieve the WIT point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the BCD algorithm obtains the R-E region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable R-E region of the LC-BCD algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
-The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
-The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010b}.
+		For the low-complexity design under \gls{ps} mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+To achieve the \gls{wit} point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the \gls{bcd} algorithm obtains the \gls{r-e} region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable \gls{r-e} region of the \gls{lc}-\gls{bcd} algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
+The steps are summarized in Algorithm~\ref{al:lc_bcd}.
+The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{\gls{lc}-\gls{bcd}}}I_{\mathrm{M-\gls{sca}}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{\gls{lc}-\gls{bcd}}}$ denotes the number of \gls{lc}-\gls{bcd} iterations \cite{Luo2010b}.
 
 		\begin{algorithm}[!t]
-			\caption{LC-BCD: Waveform and Beamforming.}
+			\caption{\gls{lc}-\gls{bcd}: Waveform and Beamforming.}
 			\label{al:lc_bcd}
@@
 
-	To evaluate the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a line parallel to the AP-UE path.
-Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
+	To evaluate the proposed \gls{ris}-aided \gls{swipt} system, we consider the layout in Fig.~\ref{fi:layout} where the \gls{ris} moves along a line parallel to the \gls{ap}-\gls{ue} path.
+Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the \gls{ap} to the \gls{ris}, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
 $d_{\mathrm{D}}=\qty{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$ are chosen as reference.
@@
 Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \qty{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
-All fadings are modeled as Non-LoS (NLoS) with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
-CSCG variables.
+All fadings are modeled as \gls{nlos} with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
+\gls{cscg} variables.
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\qty{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average Effective Isotropic Radiated Power (EIRP) as $P=\qty{40}{dBm}$, the receive antenna gain as \qty{3}{dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
-To further reduce the complexity, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner R-E bound for the LC-BCD algorithm.
-Each R-E point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
+We also choose the average \gls{eirp} as $P=\qty{40}{dBm}$, the receive antenna gain as \qty{3}{dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
+To further reduce the complexity, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner \gls{r-e} bound for the \gls{lc}-\gls{bcd} algorithm.
+Each \gls{r-e} point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 
@@
 		}
-		\caption{Sorted equivalent subchannel amplitude with and without IRS versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+		\caption{Sorted equivalent subchannel amplitude with and without \gls{ris} versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
 		\label{fi:channel_amplitude}
@@
 
-	Fig.~\ref{fi:channel_amplitude} reveals how IRS influences the sorted equivalent subchannel amplitude for one channel realization.
-Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for WIT and WPT are dissimilar.
-Under the specified configuration, the WPT-optimized IRS aligns the strong subbands to exploit the rectifier nonlinearity.
-On the other hand, the WIT-optimized IRS provides a fair gain over all subchannels when $L$ is sufficiently large.
-This is reminiscent of the WF scheme at high SNR, but is realized by channel alignment instead of resource allocation.
-Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding an IRS (the plots are not attached).
-In other words, IRS has a subtle impact on the waveform design.
+	Fig.~\ref{fi:channel_amplitude} reveals how \gls{ris} influences the sorted equivalent subchannel amplitude for one channel realization.
+Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for \gls{wit} and \gls{wpt} are dissimilar.
+Under the specified configuration, the \gls{wpt}-optimized \gls{ris} aligns the strong subbands to exploit the rectifier nonlinearity.
+On the other hand, the \gls{wit}-optimized \gls{ris} provides a fair gain over all subchannels when $L$ is sufficiently large.
+This is reminiscent of the \gls{wf} scheme at high \gls{snr}, but is realized by channel alignment instead of resource allocation.
+Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding a \gls{ris} (the plots are not attached).
+In other words, \gls{ris} has a subtle impact on the waveform design.
 
@@
 		\centering
-		\subfloat[R-E region\label{fi:re_subband}]{
+		\subfloat[\gls{r-e} region\label{fi:re_subband}]{
 			\resizebox{0.45\columnwidth}{!}{
@@
 		}
-		\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
+		\subfloat[\gls{wpt} waveform amplitude\label{fi:waveform_subband}]{
 			\resizebox{0.45\columnwidth}{!}{
@@
 		}
-		\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+		\caption{Average \gls{r-e} region and \gls{wpt} waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
 	\end{figure}
 
-	Fig.~\subref*{fi:re_subband} illustrates the average R-E region versus the number of subband $N$.
+	Fig.~\subref*{fi:re_subband} illustrates the average \gls{r-e} region versus the number of subband $N$.
 First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
-This is because less power is allocated to each subband but more balanced DC terms are introduced by frequency coupling to boost the harvested energy.
-On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for WPT.
+This is because less power is allocated to each subband but more balanced \gls{dc} terms are introduced by frequency coupling to boost the harvested energy.
+On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for \gls{wpt}.
 It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
 This observation origins from the rectifier nonlinearity.
-Although both waveforms have equivalent second-order DC terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2}, while the multisine has $(2N^3+N)/3$ monomials as the components of different frequencies compensate and produce DC.
-Second, the R-E region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that PS outperforms TS for a small $N$ and is outperformed for a large $N$.
-When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the WPT point and the saddle PS SWIPT point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
-When $N$ is relatively small, only modulated waveform is used at both WIT and WPT points, and one can infer that no multisine waveform is needed for the entire R-E region.
-It aligns with the conclusion based on the conventional linear harvester model, namely the R-E region is convex, PS outperforms TS, and dedicated power waveform is unnecessary.
-As $N$ becomes sufficiently large, the multisine waveform further boosts WPT and creates some concavity in the high-power region, which accounts for the superiority of TS under the nonlinear harvester model.
-Therefore, we conclude that the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and receiving mode, both heavily depending on $N$.
+Although both waveforms have equivalent second-order \gls{dc} terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2}, while the multisine has $(2N^3+N)/3$ monomials as the components of different frequencies compensate and produce \gls{dc}.
+Second, the \gls{r-e} region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that \gls{ps} outperforms \gls{ts} for a small $N$ and is outperformed for a large $N$.
+When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the \gls{wpt} point and the saddle \gls{ps} \gls{swipt} point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
+When $N$ is relatively small, only modulated waveform is used at both \gls{wit} and \gls{wpt} points, and one can infer that no multisine waveform is needed for the entire \gls{r-e} region.
+It aligns with the conclusion based on the conventional linear harvester model, namely the \gls{r-e} region is convex, \gls{ps} outperforms \gls{ts}, and dedicated power waveform is unnecessary.
+As $N$ becomes sufficiently large, the multisine waveform further boosts \gls{wpt} and creates some concavity in the high-power region, which accounts for the superiority of \gls{ts} under the nonlinear harvester model.
+Therefore, we conclude that the rectifier nonlinearity enlarges the \gls{r-e} region by favoring a different waveform and receiving mode, both heavily depending on $N$.
 
@@
 		\centering
-		\subfloat[R-E region\label{fi:re_noise}]{
+		\subfloat[\gls{r-e} region\label{fi:re_noise}]{
 			\resizebox{0.45\columnwidth}{!}{
@@
 		}
-		\caption{Average R-E region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+		\caption{Average \gls{r-e} region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
 	\end{figure}
 
-	The average noise power influences the R-E region as shown in Fig.~\subref*{fi:re_noise}.
-First, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly.
-At low SNR, the power is allocated to the modulated waveform on a few strongest subbands to achieve a high rate.
-As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested DC power because of frequency coupling and harvester nonlinearity.
-Second, there exists a turning point in the R-E region, especially for a low noise level ($\sigma_n^2 \le \qty{-40}{dBm}$).
+	The average noise power influences the \gls{r-e} region as shown in Fig.~\subref*{fi:re_noise}.
+First, we note that the \gls{r-e} region is roughly concave/convex at low/high \gls{snr} such that \gls{ts}/\gls{ps} are preferred correspondingly.
+At low \gls{snr}, the power is allocated to the modulated waveform on a few strongest subbands to achieve a high rate.
+As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested \gls{dc} power because of frequency coupling and harvester nonlinearity.
+Second, there exists a turning point in the \gls{r-e} region, especially for a low noise level ($\sigma_n^2 \le \qty{-40}{dBm}$).
 The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
@@
 The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
-Besides, the LC-BCD algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
+Besides, the \gls{lc}-\gls{bcd} algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
 
@@
 		\centering
-		\subfloat[R-E region\label{fi:re_distance}]{
+		\subfloat[\gls{r-e} region\label{fi:re_distance}]{
 			\resizebox{0.45\columnwidth}{!}{
@@
 		}
-		\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{V}}=\qty{2}{\meter}$.}
+		\caption{Average \gls{r-e} region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{V}}=\qty{2}{\meter}$.}
 	\end{figure}
 
-	In Fig.~\subref*{fi:re_distance}, we compare the average R-E region achieved by different AP-IRS horizontal distance $d_{\mathrm{H}}$.
-Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the IRS should be placed close to either the AP or the UE based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
-Moreover, there exist two optimal IRS coordinates around $d_{\mathrm{H}}=0.6$ and \qty{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the R-E tradeoff.
-It suggests that equipping the AP with an IRS can potentially extend the operation range of SWIPT systems.
+	In Fig.~\subref*{fi:re_distance}, we compare the average \gls{r-e} region achieved by different \gls{ap}-\gls{ris} horizontal distance $d_{\mathrm{H}}$.
+Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the \gls{ris} should be placed close to either the \gls{ap} or the \gls{ue} based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
+Moreover, there exist two optimal \gls{ris} coordinates around $d_{\mathrm{H}}=0.6$ and \qty{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the \gls{r-e} tradeoff.
+It suggests that equipping the \gls{ap} with a \gls{ris} can potentially extend the operation range of \gls{swipt} systems.
 
@@
 		\centering
-		\subfloat[R-E region\label{fi:re_tx}]{
+		\subfloat[\gls{r-e} region\label{fi:re_tx}]{
 			\resizebox{0.45\columnwidth}{!}{
@@
 		}
-		\subfloat[WIT SNR and WPT DC\label{fi:scaling_tx}]{
+		\subfloat[\gls{wit} \gls{snr} and \gls{wpt} \gls{dc}\label{fi:scaling_tx}]{
 			\resizebox{0.45\columnwidth}{!}{
@@
 		}
-		\caption{Average R-E region, WIT SNR and WPT DC versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{0.2}{\meter}$.}
+		\caption{Average \gls{r-e} region, \gls{wit} \gls{snr} and \gls{wpt} \gls{dc} versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{0.2}{\meter}$.}
 	\end{figure}
@@
 		\centering
-		\subfloat[R-E region\label{fi:re_reflector}]{
+		\subfloat[\gls{r-e} region\label{fi:re_reflector}]{
 			\resizebox{0.425\columnwidth}{!}{
@@
 		}
-		\subfloat[WIT SNR and WPT DC\label{fi:scaling_reflector}]{
+		\subfloat[\gls{wit} \gls{snr} and \gls{wpt} \gls{dc}\label{fi:scaling_reflector}]{
 			\resizebox{0.475\columnwidth}{!}{
@@
 		}
-		\caption{Average R-E region, WIT SNR and WPT DC versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{0.2}{\meter}$.}
+		\caption{Average \gls{r-e} region, \gls{wit} \gls{snr} and \gls{wpt} \gls{dc} versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{0.2}{\meter}$.}
 	\end{figure}
 
-	The impacts of the number of transmit antennas $M$ and the IRS elements $L$ on the R-E behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
-First, it is observed that adding either active or passive elements can improve the equivalent SNR, which produces a nearly concave R-E region and favors the PS receiver.
+	The impacts of the number of transmit antennas $M$ and the \gls{ris} elements $L$ on the \gls{r-e} behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
+First, it is observed that adding either active or passive elements can improve the equivalent \gls{snr}, which produces a nearly concave \gls{r-e} region and favors the \gls{ps} receiver.
 Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the DC objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no SCA is required; (ii) in the waveform design problem, the WPT-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dBA} gap compared to the nonlinear model-based SMF and GP designs.
-Third, doubling $M$ brings a \qty{3}{\dB} gain at the output SNR and a \qty{12}{dBA} increase at the harvested DC, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
-Fourth, when the IRS is very close to the AP or UE, doubling $L$ can bring a \qty{6}{\dB} gain at the output SNR and a \qty{24}{dBA} increase at the harvested DC.
-From the perspective of WIT, it suggests that passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
-An interpretation is that the IRS coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
-From the perspective of WPT, it suggests that passive beamforming comes with a power scaling order $L^4$ under the truncated nonlinear harvester model.
+To investigate the performance loss, we truncate the \gls{dc} objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no \gls{sca} is required; (ii) in the waveform design problem, the \gls{wpt}-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dBA} gap compared to the nonlinear model-based \gls{smf} and \gls{gp} designs.
+Third, doubling $M$ brings a \qty{3}{\dB} gain at the output \gls{snr} and a \qty{12}{dBA} increase at the harvested \gls{dc}, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
+Fourth, when the \gls{ris} is very close to the \gls{ap} or \gls{ue}, doubling $L$ can bring a \qty{6}{\dB} gain at the output \gls{snr} and a \qty{24}{dBA} increase at the harvested \gls{dc}.
+From the perspective of \gls{wit}, it suggests that passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
+An interpretation is that the \gls{ris} coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
+From the perspective of \gls{wpt}, it suggests that passive beamforming comes with a power scaling order $L^4$ under the truncated nonlinear harvester model.
 We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel becomes negligible.
 Let $X$ be the cascaded small-scale fading coefficient.
-The DC in such case reduces to
+The \gls{dc} in such case reduces to
 	\begin{equation}
@@
 	which scales quartically with $L$.
-Compared with active antennas, IRS elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
-These observations demonstrate the R-E benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
+Compared with active antennas, \gls{ris} elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
+These observations demonstrate the \gls{r-e} benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
 
@@
 		}
-		\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+		\caption{Average \gls{r-e} region for ideal, adaptive, fixed and no \gls{ris} versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
 	\end{figure}
 
-	Figs.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the R-E region with different IRS strategies for narrowband and broadband SWIPT.
-The ideal Frequency-Selective (FS) IRS assumes the reflection coefficient of each element is independent and controllable at different frequencies.
-The adaptive IRS adjusts the passive beamforming for different R-E points by Algorithm~\ref{al:sca}.
-The WIT/WPT-optimized IRS is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole R-E region.
-The random IRS models the phase shift of all elements as i.i.d.
+	Figs.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the \gls{r-e} region with different \gls{ris} strategies for narrowband and broadband \gls{swipt}.
+The ideal Frequency-Selective (FS) \gls{ris} assumes the reflection coefficient of each element is independent and controllable at different frequencies.
+The adaptive \gls{ris} adjusts the passive beamforming for different \gls{r-e} points by Algorithm~\ref{al:sca}.
+The \gls{wit}/\gls{wpt}-optimized \gls{ris} is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole \gls{r-e} region.
+The random \gls{ris} models the phase shift of all elements as i.i.d.
 uniform random variables over $[0, 2\pi)$.
-First, random IRS and no IRS perform worse than other schemes since no passive beamforming is exploited.
-Their R-E boundaries coincide as the antenna mode reflection of the random IRS is canceled out after averaging.
-Second, when the bandwidth is small, the performance of ideal, adaptive, and WIT/WPT-optimized IRS are similar; when the bandwidth is large, the adaptive IRS outperforms the WIT/WPT-optimized IRS but is outperformed by the ideal FS IRS.
+First, random \gls{ris} and no \gls{ris} perform worse than other schemes since no passive beamforming is exploited.
+Their \gls{r-e} boundaries coincide as the antenna mode reflection of the random \gls{ris} is canceled out after averaging.
+Second, when the bandwidth is small, the performance of ideal, adaptive, and \gls{wit}/\gls{wpt}-optimized \gls{ris} are similar; when the bandwidth is large, the adaptive \gls{ris} outperforms the \gls{wit}/\gls{wpt}-optimized \gls{ris} but is outperformed by the ideal FS \gls{ris}.
 In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
-It suggests that for narrowband SWIPT, the optimal passive beamforming for any R-E point is optimal for the whole R-E region, and the corresponding composite channel and active precoder are also optimal for the whole R-E region.
-Hence, the achievable R-E region is obtained by optimizing the waveform amplitude and splitting ratio.
-On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal IRS reflection coefficient varies at different R-E tradeoffs points for broadband SWIPT.
-As shown in Fig.~\ref{fi:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high SNR, or focused on a few strongest subbands to boost the output DC, thanks to adaptive passive beamforming.
+It suggests that for narrowband \gls{swipt}, the optimal passive beamforming for any \gls{r-e} point is optimal for the whole \gls{r-e} region, and the corresponding composite channel and active precoder are also optimal for the whole \gls{r-e} region.
+Hence, the achievable \gls{r-e} region is obtained by optimizing the waveform amplitude and splitting ratio.
+On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal \gls{ris} reflection coefficient varies at different \gls{r-e} tradeoffs points for broadband \gls{swipt}.
+As shown in Fig.~\ref{fi:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high \gls{snr}, or focused on a few strongest subbands to boost the output \gls{dc}, thanks to adaptive passive beamforming.
 
@@
 		\centering
-		\subfloat[Imperfect cascaded CSIT\label{fi:re_csi}]{
+		\subfloat[Imperfect cascaded \gls{csit}\label{fi:re_csi}]{
 			\resizebox{0.45\columnwidth}{!}{
@@
 		}
-		\subfloat[Quantized IRS\label{fi:re_quantization}]{
+		\subfloat[Quantized \gls{ris}\label{fi:re_quantization}]{
 			\resizebox{0.45\columnwidth}{!}{
@@
 		}
-		\caption{Average R-E region with imperfect cascaded CSIT and quantized IRS for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.
-$\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect CSIT and no CSIT (and random IRS); $b=0$ and $b \to \infty$ correspond respectively to no IRS and continuous IRS.}
+		\caption{Average \gls{r-e} region with imperfect cascaded \gls{csit} and quantized \gls{ris} for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.
+$\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect \gls{csit} and no \gls{csit} (and random \gls{ris}); $b=0$ and $b \to \infty$ correspond respectively to no \gls{ris} and continuous \gls{ris}.}
 	\end{figure}
 
-	We then explore the impacts of imperfect cascaded CSIT and quantized IRS on the R-E performance.
-Due to the general lack of RF-chains at the IRS, it can be challenging to acquire accurate cascaded CSIT on a short-term basis.
+	We then explore the impacts of imperfect cascaded \gls{csit} and quantized \gls{ris} on the \gls{r-e} performance.
+Due to the general lack of \gls{rf}-chains at the \gls{ris}, it can be challenging to acquire accurate cascaded \gls{csit} on a short-term basis.
 We assume the cascaded channel at subband $n$ is
@@
 	\end{equation}
-	where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded CSIT and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
-CSCG distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded CSIT inaccuracy for broadband SWIPT with different $L$.
-On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete IRS codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution IRS) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable R-E gain over the benchmark scheme without IRS, and the performance gap between $b=4$ and unquantized IRS is negligible.
-These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical IRS-aided SWIPT systems.
+	where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded \gls{csit} and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+\gls{cscg} distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded \gls{csit} inaccuracy for broadband \gls{swipt} with different $L$.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete \gls{ris} codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution \gls{ris}) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable \gls{r-e} gain over the benchmark scheme without \gls{ris}, and the performance gap between $b=4$ and unquantized \gls{ris} is negligible.
+These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical \gls{ris}-aided \gls{swipt} systems.
 \end{section}
@@
 \begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-	This paper investigated the R-E tradeoff of a single user employing practical receiving strategies in an IRS-aided multi-carrier MISO SWIPT system.
-Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable R-E region.
-A three-stage BCD algorithm was proposed to solve the problem.
-In the first stage, the IRS phase shift was obtained by the SCA technique and eigen decomposition.
-In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the GP method.
-We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity BCD algorithm that achieves a good balance between performance and complexity.
-Numerical results revealed significant R-E gains by modeling harvester nonlinearity in the IRS-aided SWIPT design.
-Unlike active antennas, IRS elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
-Compared to the conventional no-IRS system, the IRS mainly affects the effective channel instead of the waveform design.
+	This paper investigated the \gls{r-e} tradeoff of a single user employing practical receiving strategies in a \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.
+Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable \gls{r-e} region.
+A three-stage \gls{bcd} algorithm was proposed to solve the problem.
+In the first stage, the \gls{ris} phase shift was obtained by the \gls{sca} technique and eigen decomposition.
+In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the \gls{gp} method.
+We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity \gls{bcd} algorithm that achieves a good balance between performance and complexity.
+Numerical results revealed significant \gls{r-e} gains by modeling harvester nonlinearity in the \gls{ris}-aided \gls{swipt} design.
+Unlike active antennas, \gls{ris} elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
+Compared to the conventional no-\gls{ris} system, the \gls{ris} mainly affects the effective channel instead of the waveform design.
 
-	One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier IRS-aided SWIPT system.
-Also, harvester saturation effect and practical IRS models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.
+	One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier \gls{ris}-aided \gls{swipt} system.
+Also, harvester saturation effect and practical \gls{ris} models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.
 \end{section}

### 2024-03-03 content/chapter_2.tex
:construction: Add chapters 2 and 3

%!TEX root = ../thesis.tex

\graphicspath{{assets/chapter_2/}}

\chapter{Getting started}

\begin{section}{Introduction}
	\label{sc:introduction}
	Future wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and superimposes its own information, and the co-located receiver cooperatively decodes both links.
	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
	Each \gls{ris} element is considered as a \emph{channel shaper} and the reflection pattern depends exclusively on the \gls{csi}.

	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	The achievable rate and optimal input distribution for binary-input \gls{ambc} were investigated in \cite{Qian2019b}, but its impact on the primary link was omitted.
	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to \emph{double fading};
		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
	Under those assumptions, the achievable rate region of cell-free \gls{sr} was characterized in \cite{Dai2023}.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
	However, this assumption severely limits the backscatter throughput.

	\begin{figure}[!t]
		\centering
		\subfloat[\gls{mbc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_2/mbc.tex}
			}
			\label{fg:mbc}
		}
		\subfloat[\gls{bbc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_2/bbc.tex}
			}
			\label{fg:bbc}
		}
		\\
		\subfloat[\gls{ambc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_2/ambc.tex}
			}
			\label{fg:ambc}
		}
		\subfloat[\gls{sr}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_2/sr.tex}
			}
			\label{fg:sr}
		}
		\\
		\subfloat[\gls{ris}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_2/ris.tex}
			}
			\label{fg:ris}
		}
		\subfloat[RIScatter]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_2/riscatter.tex}
			}
			\label{fg:riscatter}
		}
		\caption{
			Illustration of scattering applications.
			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
		}
		\label{fg:scatter_illustration}
	\end{figure}

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.4}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                       & \glsentryshort{mbc}/\glsentryshort{bbc} & \glsentryshort{ambc}        & \glsentryshort{sr} (large spreading factor)                         & \glsentryshort{ris} & RIScatter                                                          \\ \midrule
			\showrowcolors
			Information link(s)                    & Backscatter                             & Coexisting                  & Coexisting                                                          & Primary             & Coexisting                                                         \\
			Primary signal on backscatter decoding & Carrier                                 & Multiplicative interference & Spreading code                                                      & ---                 & Energy uncertainty                                                 \\
			Backscatter signal on primary decoding & ---                                     & Multiplicative interference & \glsentryshort{csi} uncertainty                                     & Passive beamforming & Dynamic passive beamforming                                        \\
			Cooperative devices                    & ---                                     & No                          & Primary transmitter and co-located receiver                         & ---                 & Primary transmitter, scatter nodes, and co-located receiver        \\
			Sequential decoding                    & ---                                     & No                          & Primary-to-backscatter, \glsentryshort{sic} and \glsentryshort{mrc} & ---                 & Backscatter-to-primary, no \glsentryshort{sic}/\glsentryshort{mrc} \\
			Reflection pattern depends on          & Information source                      & Information source          & Information source                                                  & \glsentryshort{csi} & Information source, \glsentryshort{csi}, and \glsentryshort{qos}   \\
			Reflection state distribution          & Equiprobable                            & Equiprobable                & Equiprobable or Gaussian                                            & Degenerate          & Flexible                                                           \\
			Load-switching speed                   & Fast                                    & Slow                        & Slow                                                                & Quasi-static        & Arbitrary                                                          \\ \bottomrule
		\end{tabularx}
	\end{table*}

	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019b} and \gls{qam} \cite{Dai2020a}.
	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
	In contrast, \cite{Vardakis2023} exploited commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user. \label{cm:2.5}
	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
	Most relevant literature considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
	Those problems are addressed in this paper and the contributions are summarized below.

	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
	A co-located receiver cooperatively decodes both coexisting links.
	Each reflection state is simultaneously a passive beamforming codeword and part of information codeword.
	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
	However, two major challenges for RIScatter are the receiver design and input distribution design.
	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.

	\emph{Second,} we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming afterwards.
	The proposed receiver may be built over legacy receivers with minor hardware upgrade, as it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
	This is the first paper to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.

	\emph{Third,} we address the second challenge in a single-user multi-node \gls{miso} scenario.
	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by the converging point of a sequence, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to other detection schemes.
	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.

	\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
	The observations include:
	1) adaptive reflection state distribution design can flexibly shift between backscatter modulation and passive beamforming;
	2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
	3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
	4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
	5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
	6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
	7) \gls{pga} active beamformer effectively increases the primary (resp. backscatter) rate by boosting the receive \gls{snr} (resp. widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
	8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
\end{section}

\begin{section}{RIScatter}
	\label{sc:riscatter}
	\begin{subsection}{Principles}
		\label{sc:principles}
		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
		\begin{equation}
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		\end{equation}
		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
		Specifically,
		\begin{itemize}
			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
			The reflection coefficient is used merely as part of information codeword \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
			\begin{equation}
				\Gamma_m = \alpha_m \exp(j \theta_m),
				\label{eq:passive_beamforming}
			\end{equation}
			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
		\end{itemize}

		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
		Each reflection coefficient simultaneously acts as a passive beamforming codeword and part of information codeword.
		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/chapter_2/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/chapter_2/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer corresponds to state \num{2}.
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		\begin{remark}
			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
			\label{re:dynamic_passive_beamforming}
		\end{remark}

		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user. The node receiver can be implemented using simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/chapter_2/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/chapter_2/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/chapter_2/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
		% The detail will be covered in Section~\ref{st:system_model}.
	\end{subsection}

	\begin{subsection}{System Model}
		\label{sc:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.7\columnwidth}
			\input{assets/chapter_2/riscatter_network.pdf_tex}
			\caption{A single-user multi-node RIScatter network.}
			\label{fg:riscatter_network}
		\end{figure}
		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
		Without loss of generality, we assume all nodes have $M$ available reflection states.
		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes. The impact of channel estimation error will be investigated in Section~\ref{sc:simulation_results}.}.

		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the (coded) backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
			\end{align}
		\end{subequations}
		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
		Without loss of generality, we assume the spreading factor $N$ is a positive integer.
		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
			\label{eq:receive_signal}
		\end{equation}
		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the maximum average transmit power, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.

		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
		The backscatter symbol $x_k$ (resp. symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp. value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp. $p(x_{m_{\mathcal{K}}})$).
		\begin{remark}
			Dispersed RIScatter nodes encode independently such that
			\begin{equation}
				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
				\label{eq:equivalent_distribution}
			\end{equation}
			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
			\label{re:independent_encoding}
		\end{remark}

		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the receive energy per backscatter block.
		When $x_{m_\mathcal{K}}$ is transmitted, the receive signal $y$ follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with variance
		\begin{equation}
			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
			\label{eq:receive_variance}
		\end{equation}
		and $z$ follows Gamma distribution with conditional \gls{pdf}
		\begin{equation}
			f(z|x_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
			\label{eq:energy_distribution}
		\end{equation}

		\begin{remark}
			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Qian2019b,Xu2020b,Zhang2021d,Hua2022,Hu2021a,Qian2019}.
			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
			\label{re:non_gaussian}
		\end{remark}

		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.\footnote{The reliability of the energy detector is improved by the adaptive input distribution and thresholding design. With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with low code-rate. In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.\label{fn:energy_detector}}
		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.

		\begin{remark}
			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
			It was proved deterministic detectors can be rate-optimal, but non-convex regions (consist of non-adjacent partitions) are generally required and the optimal number of thresholds is unknown \cite{Nguyen2018,Nguyen2021}.
			Next, we restrict the energy detector to convex deterministic decision regions and consider sequential threshold design.
		\end{remark}

		Let $L = M^K$ be the number of decision regions.
		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one mapped. Both notations are used interchangeably in the following context.}
		\begin{equation}
			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
		\end{equation}
		where $t_l$ is the decision threshold between hypotheses $x_{l}$ and $x_{l+1}$.
		An example is shown in Fig.~\ref{fg:energy_distribution}.

		\begin{figure}[!t]
			\centering
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/chapter_2/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of the receive energy per backscatter block conditioned on different reflection state.
			}
			\label{fg:energy_distribution}
		\end{figure}

		When the threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
		\begin{equation}
			q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|x_{m_{\mathcal{K}}}) \, d z.
			\label{eq:dmmac}
		\end{equation}
		The backscatter mutual information is
		\begin{equation}
			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_mutual_information}
		\end{equation}
		where $I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}})$ is the backscatter information function
		\begin{equation}
			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{p(\hat{x}_{m_{\mathcal{K}}'})}.
			\label{eq:backscatter_information_function}
		\end{equation}

		Once the backscatter information is successfully decoded, the user re-encodes to recover the reflection pattern, constructs the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
		The primary mutual information is
		\begin{equation}
			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_mutual_information}
		\end{equation}
		where $I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$ is the primary information function
		\begin{equation}
			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr).
			\label{eq:primary_information_function}
		\end{equation}
	\end{subsection}
\end{section}

\begin{section}{Rate-Region Characterization}
	With a slight abuse of notation, we define the weighed sum mutual information and information function as
	\begin{align}
		I(x_{\mathcal{K}})
		 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}           \\
		I(x_{m_\mathcal{K}})
		 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function}
	\end{align}
	where $\rho \in \mathbb{I}$ is the \gls{qos}.
	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented backscatter source.\label{fn:joint_encoding}}
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^\mathsf{T} \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0},}{\label{co:nonnegative_threshold}}
	\end{maxi!}
	where $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problems from the vertices of $M$-dimensional probability simplex to the simplex itself.
	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.

	\begin{subsection}{Input Distribution}
		\label{sc:input_distribution}
		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves the product term \eqref{eq:equivalent_distribution} and is generally non-convex (unless $K=1$).
		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical solution that guarantees those conditions on the converging point of a sequence.
		\begin{proposition}
			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & \text{if} \ p^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & \text{if} \ p^\star(x_{m_k}) = 0,\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			where $I_k(x_{m_k})$ is the weighted sum marginal information
			\begin{align}
				I_k(x_{m_k})
				 & \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) I(x_{m_\mathcal{K}}).
				\label{eq:weighted_sum_marginal_information}
			\end{align}
			\label{pr:input_kkt_condition}
		\end{proposition}

		\begin{proof}
			Please refer to Appendix \ref{ap:input_kkt_condition}.
			\label{pf:input_kkt_condition}
		\end{proof}

		For each RIScatter node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
		\begin{proposition}
			For any strictly positive initializer $\{\boldsymbol{p}_k^{(0)}\}_{k \in \mathcal{K}}$, the \gls{kkt} input probability of node $k$ at state $m_k$ is given by the converging point of the sequence
			\begin{equation}
				p^{(r+1)}(x_{m_k}) = \frac{p^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} p^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
				\label{eq:input_kkt_solution}
			\end{equation}
			where $r$ is the iteration index.
			\label{pr:input_kkt_solution}
		\end{proposition}
		\begin{proof}
			Please refer to Appendix \ref{ap:input_kkt_solution}.
			\label{pf:input_kkt_solution}
		\end{proof}

		At iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.

		% \setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			% \small
			\caption{Input Distribution Evaluation by a Sequence}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $p^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}

		\begin{remark}
			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
			\label{re:input_kkt_distribution}
		\end{remark}
	\end{subsection}

	\begin{subsection}{Active Beamforming}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{t}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:active_beamforming}}{\label{ob:active_beamforming}}
			\addConstraint{\eqref{co:transmit_power},}
		\end{maxi!}
		which is still non-convex due to the integration and entropy terms.
		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we have
		\begin{align}
			q(x_l|x_{m_{\mathcal{K}}})
			 & = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} \\
			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
			\label{eq:dmmac_gamma}
		\end{align}
		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
		\begin{align}
			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} \nonumber \\
			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
			\label{eq:regularized_incomplete_gamma}
		\end{align}
		whose gradient with respect to $\boldsymbol{w}^*$ is
		\begin{align}
			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
			 & = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \nonumber \\
			 & \quad \times \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
			\label{eq:regularized_incomplete_gamma_gradient}
		\end{align}
		where
		\begin{equation}
			g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
			\label{eq:regularized_incomplete_gamma_gradient_component}
		\end{equation}
		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we rewrite $I(x_{\mathcal{K}})$ and $\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})$ as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
		\begin{figure*}[!b]
			\hrule
			\begin{equation}
				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} p(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
				\label{eq:weighted_sum_mutual_information_explicit}
			\end{equation}
			\begin{align}
				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
				 & = \sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
				\label{eq:weighted_sum_mutual_information_gradient}
			\end{align}
		\end{figure*}
		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
		At iteration $r+1$, the unregulated active beamformer is updated by
		\begin{equation}
			\bar{\boldsymbol{w}}^{(r+1)} = \boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}}),
			\label{eq:beamforming_gradient_ascent}
		\end{equation}
		where $\gamma$ is the step size (refinable by backtracking line search \cite[Section 9.2]{Boyd2004}).
		Then, $\bar{\boldsymbol{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
		\begin{equation}
			\boldsymbol{w} = \frac{\sqrt{P} \bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
			\label{eq:beamforming_projection}
		\end{equation}

		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
		% \setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			% \small
			\caption{Active Beamforming Optimization by \gls{pga}}
			\label{al:active_beamforming}
			\begin{algorithmic}[1]
				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
				\Ensure $\boldsymbol{w}^\star$
				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $p(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)}$ by \eqref{eq:beamforming_gradient_ascent} \label{st:backtracking_line_search_begin}
					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
					\EndWhile
					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

	\begin{subsection}{Decision Threshold}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
		\end{maxi!}
		which is still non-convex since $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
		As shown in Fig.~\ref{fg:discrete_outputs}, the decision regions are formulated by grouping adjacent energy bins.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/chapter_2/discrete_outputs.tex}
			}
			\caption{The thresholds are chosen from fine-grained candidates instead of the continuous space. Each decision region consists of at least one bin.}
			\label{fg:discrete_outputs}
		\end{figure}

		\begin{remark}
			The design of the energy detector does not affect the primary achievable rate, since the composite channel \eqref{eq:equivalent_channel} can always be determined after backscatter decoding and re-encoding.
			This implies that any thresholding maximizing the total backscatter rate is optimal for problem \eqref{op:decision_threshold}.
			\label{re:backscatter_decision}
		\end{remark}

		\begin{remark}
			In terms of total backscatter rate, the nodes can be viewed as an augmented source, and problem \eqref{op:decision_threshold} becomes the rate-optimal quantizer design for \gls{dmtc}.
			\label{re:augmented_source}
		\end{remark}

		Thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
			\addConstraint{\eqref{co:sequential_threshold},}
		\end{maxi!}
		whose global optimal solution has been obtained in recent works.
		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$.
		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
		In Section \ref{sc:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
		\begin{equation}
			t_{l}^{\text{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
			\label{eq:detection_threshold_ml}
		\end{equation}
		which is suboptimal for problem \eqref{op:decision_threshold} unless all nodes are with equiprobable inputs.
	\end{subsection}
\end{section}

\begin{section}{Simulation Results}
	\label{sc:simulation_results}
	In this section, we provide numerical results to evaluate the proposed algorithms.
	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
	We set $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate regions are averaged over \num{e3} channel realizations.\footnote{The code is publicly available at \url{https://github.com/snowztail/riscatter/}.}

	\begin{subsection}{Evaluation of Proposed Algorithms}
		\begin{subsubsection}{Initialization}
			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
			For $\rho=0$ where the backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards the sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
			At the following points, both algorithms are initialized by the solutions at the previous point.
		\end{subsubsection}

		\begin{subsubsection}{Convergence}
			\label{sc:convergence}
			\begin{figure}[!t]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\input{assets/chapter_2/wsr_convergence.tex}
				}
				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
				\label{fg:wsr_convergence}
			\end{figure}
			The \gls{bcd} algorithm is convergent for problem \eqref{op:weighted_sum_rate} since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
			In company with \gls{bcd}, we also plotted the convergence results of \gls{kkt} and \gls{pga} algorithms in Fig.~\ref{fg:wsr_convergence} to show how much performance is gained by solving each subproblem.
			It is observed that Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} take around \num{100} and \num{10} iterations to converge, respectively.
			Overall, the \gls{bcd} algorithm requires at most \num{5} iterations to converge.
			As $\rho$ increases (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
		\end{subsubsection}
	\end{subsection}

	\begin{subsection}{Comparison of Scattering Applications}
		On top of the setup in Fig.~\ref{fg:riscatter_network}, we consider RIScatter and the following benchmark applications:
		\begin{itemize}
			\item \emph{Legacy:} Legacy transmission without scatter nodes.
			\item \emph{\gls{bbc}:} The primary signal is \gls{cw} and the receive signal is
			\begin{equation}
				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n].
			\end{equation}
			The total backscatter rate approaches $K \log M$ when $N$ is sufficiently large.
			\item \emph{\gls{ambc}:} The user decodes each link independently and semi-coherently while treating the other as interference.
			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
			\begin{equation}
				I_{\text{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\text{D}}^\mathsf{H}\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
			\end{equation}
			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
			\item \emph{\gls{sr}:} For a sufficiently large $N$, the average primary rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\text{D}}^\mathsf{H} \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
			\begin{equation}
				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n].
				\label{eq:intermediate_signal}
			\end{equation}
			The total backscatter rate approaches $K \log M$.
			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
			The primary achievable rate is a special case of \eqref{eq:primary_mutual_information}
			\begin{equation}
				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\end{equation}
			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{m_{\mathcal{K}}})$.
		\end{itemize}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/chapter_2/region_comparison.tex}
			}
			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
			\label{fg:region_comparison}
		\end{figure}

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
	\end{subsection}

	\begin{subsection}{Input Distribution under Different \glsfmtshort{qos}}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/chapter_2/distribution_weights.tex}
			}
			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
			\label{fg:distribution_weights}
		\end{figure}
		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
		This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at low \gls{snr} \cite{Shannon1948}.
		When the scattered signal is relatively weak, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy diversity and end up unused.
		At $\rho=1$ where the primary link is prioritized, the optimal input distribution is $[0, 0, 1, 0]^\mathsf{T}$ since state 3 provides higher primary \gls{snr} than other states.
		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a static discrete \gls{ris} element.
		Increasing $\rho$ from \num{0} to \num{1} creates a smooth transition from backscatter modulation to passive beamforming, suggesting RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
	\end{subsection}

	\begin{subsection}{Rate Region by Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
				\resizebox{0.6\columnwidth}{!}{
					\input{assets/chapter_2/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.
			}
		\end{figure}
		\begin{subsubsection}{Input Distribution}
			We compare these input distribution designs for problem \eqref{op:input_distribution}:
			\begin{itemize}
				\item \emph{Cooperation:} Joint encoding using a joint probability array $p(x_{m_{\mathcal{K}}})$ with $M^K$ entries by Algorithm \ref{al:input_distribution};
				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
				\item \emph{\gls{kkt}:} Solution by Algorithm \ref{al:input_distribution};
				\item \emph{Equiprobable:} Uniform input distribution.
			\end{itemize}
			We also consider these independent distribution recovery methods from the joint probability array:
			\begin{itemize}
				\item \emph{Marginalization:} Marginal probability distributions;
				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposed tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
			\end{itemize}

			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
		\end{subsubsection}

		\begin{subsubsection}{Active Beamforming}
			We consider three typical active beamforming schemes for problem \eqref{op:active_beamforming}:
			\begin{itemize}
				\item \emph{\gls{pga}:} Solution by Algorithm \ref{al:active_beamforming};
				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
			\end{itemize}

			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
			In the low-$\rho$ regime, the proposed \gls{pga} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
			This is because the semi-coherent backscatter decoding relies on the relative energy difference under different backscatter symbol tuples.
			Such an energy diversity is enhanced by \gls{pga} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizes the channel strength.
			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches E-\gls{mrt}.
			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the strongest composite channel.
			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
			Those observations confirm that the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to enlarge the achievable rate region.
		\end{subsubsection}

		\begin{subsubsection}{Decision Threshold}
			We evaluate the following decision threshold strategies for problem \eqref{op:decision_threshold_discrete}:
			\begin{itemize}
				\item \emph{\gls{dp}:} Benchmark \gls{dp} method for sequential quantizer \cite{He2021};
				\item \emph{\gls{smawk}:} \emph{\gls{dp}} accelerated by the \gls{smawk} algorithm \cite{He2021};
				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_ml} \cite{Qian2019}.
			\end{itemize}

			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
			The distribution-aware schemes \gls{dp}, \gls{smawk} and Bisection ensure higher total backscatter rate than \gls{ml}.
			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal thresholding depends heavily on the input distribution.
			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other hypotheses.
			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
		\end{subsubsection}

	\end{subsection}

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_tags.tex}
				}
			}
			\subfloat[Reflection States\label{fg:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fg:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_txs.tex}
				}
			}
			\subfloat[Spreading Factor\label{fg:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fg:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_noise.tex}
				}
			}
			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_csi.tex}
				}
			}
			\\
			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_snr_primary.tex}
				}
			}
			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_2/region_snr_backscatter.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
			}
			\label{fg:region_config}
		\end{figure}
		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
		\begin{subsubsection}{Number of Nodes}
			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
		\end{subsubsection}

		\begin{subsubsection}{Number of States}
			Fig.~\subref*{fg:region_states} shows the relationship between the available reflection states (i.e., \gls{qam} order) $M$ and the achievable rate region when $K=1$.
			We notice that increasing the reflection states has a marginal effect on the primary rate but significantly improves the backscatter rate.
			This is because the maximum amplitude normalized-\gls{qam} \eqref{eq:backscatter_modulation} involves more weak reflection points as $M$ increases.
			It enhances the receive energy diversity but cannot provide enough phase shift resolution with maximum reflection.
		\end{subsubsection}

		\begin{subsubsection}{Number of Transmit Antennas}
			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter tradeoff.
			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
		\end{subsubsection}

		\begin{subsubsection}{Spreading factor}
			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Here, the unit of total backscatter rate is bits per primary block to show backscatter throughput.}
			Using a very large $N$ (as in the case of \gls{sr}) can severely constrain the backscatter throughput, since the gain in energy certainty (by the law of large numbers) cannot withstand the loss in the gross rate.
			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
			On the other hand, when $N$ is too small, the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable and energy detection is error-prone.
			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., primary and backscatter \gls{snr}, data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
		\end{subsubsection}

		\begin{subsubsection}{Average Noise Power}
			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
			Note that the noise influences both primary and backscatter \gls{snr}.
			% It shows the proposed adaptive energy detector is suitable for a wide range of noise levels.
			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the \gls{snr} of energy detection.
		\end{subsubsection}

		% \begin{subsubsection}{Coverage Disk Radius}
		% 	Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
		% 	We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
		% 	This is because the double fading effect is less severe for near-far setups.
		% 	In a multi-user RIScatter network with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
		% \end{subsubsection}

		\begin{subsubsection}{Imperfect \gls{csi}}
			Due to the lack of \gls{rf} chains at RIScatter nodes, fast and accurate acquisition of the cascaded \gls{csi} can be challenging, especially when the backscatter \gls{snr} is weak or the number of nodes is large.
			We consider an imperfect \gls{csi} model, where the cascaded channel of node $k$ is estimated as
			\begin{equation}
				\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
			\end{equation}
			$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d. CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
			In Fig.~\subref*{fg:region_csi}, it is observed that the channel estimation error mainly affects the backscatter rate.
			When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus the estimation of the cascaded channel.
			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state and the primary rate is almost unchanged.
		\end{subsubsection}

		\begin{subsubsection}{Primary \gls{snr}}
			\label{sc:primary_snr}
			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
		\end{subsubsection}

		\begin{subsubsection}{Backscatter \gls{snr}}
			The primary \gls{snr} is fixed to \qty{20}{dB} with $Q=1$ in this study.
			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.
			This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
			In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
		\end{subsubsection}
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	\label{sc:conclusion}
	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris}, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
	We also proposed a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to benefit both subsystems.
	The achievable primary-total-backscatter rate region was then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
	Numerical results validated the proposed algorithms and emphasized the importance of adaptive input distribution and cooperative receiver design.

	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
\end{section}

### 2024-03-03 content/chapter_3.tex
:construction: Add chapters 2 and 3

%!TEX root = ../thesis.tex

\graphicspath{{assets/chapter_3/}}

\chapter{Getting started}

\begin{section}{Introduction}
	% The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
	This is empowered by the recent advances in \gls{ris}, a real-time programmable metasurface of numerous non-resonant sub-wavelength scattering elements.
	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than relays.
	Using \gls{ris} for {passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
	On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019b,Dai2020a}.
	Despite fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}

	The answer indeed depends on the hardware architecture and scattering model.
	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which groups adjacent elements using passive components.
	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
	Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.

	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
	Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself.
	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of channel manipulation.
	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020a,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
	In contrast, \gls{bd}-\gls{ris} can provide a higher channel power but existing results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}. \cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
	While these studies offer promising glimpses into the channel shaping potential, a comprehensive understanding of the capabilities and limitations is desired, and a universal design framework is missing.
	This paper aims to answer the channel shaping question through theoretical analysis and numerical optimization.
	The contributions are summarized below.

	First, we quantify the capability of a \gls{bd}-\gls{ris} to reshape the \gls{mimo} point-to-point channel in terms of singular values.
	The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
	% This generalizes most singular value metrics and provides a powerful design framework.
	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
	We then discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
	This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.

	Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
	It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
	This is the first paper to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.

	Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
	The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
	It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.

	% Third, we propose a closed-form iterative algorithm for power centric channel shaping problems.
	% The idea is to successively approximate the quadratic objective by a sequence of affines and solve the local problems by \gls{svd}.
	% Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.

	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.

\end{section}

\begin{section}{\glsfmtlong{bd}-\glsfmtlong{ris} Model}
	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
	The overall scattering matrix of the \gls{bd}-\gls{ris} is
	\begin{equation}
		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
	\end{equation}
	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
	That is, $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{H}$ and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.

	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (transmitter-receiver), backward (\gls{ris}-receiver), and forward (transmitter-\gls{ris}) channels, respectively.
	The equivalent channel is a function of the scattering matrix
	\begin{equation}
		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
		\label{eq:channel_equivalent}
	\end{equation}
	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
	% That is, $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns (resp. rows) of $\mathbf{H}_\mathrm{B}$ (resp. $\mathbf{H}_\mathrm{F}$).
	% , corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$.
	% $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$
	Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
	\begin{equation}
		\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{R}_g^\mathsf{H},
	\end{equation}
	where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary factor matrices.
	Let $\mathbf{H}_{\mathrm{B},g} = \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \mathbf{V}_{\mathrm{B},g}^\mathsf{H}$ and $\mathbf{H}_{\mathrm{F},g} = \mathbf{U}_{\mathrm{F},g} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}$ be the compact \gls{svd} of the backward and forward channels, respectively.
	The equivalent channel can thus be rewritten as
	\begin{equation}
		\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
		\label{eq:channel_equivalent_svd}
	\end{equation}

	\begin{remark}
		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} creates two critical opportunities:
		\begin{itemize}
			\item \textbf{Subspace alignment:} each group can align the singular matrices of the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) channels. In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ is
			\begin{equation}
				\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
			\end{equation}
			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr]$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr]$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
			Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R} \times N_\mathrm{T}$ passing through itself.
			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the direct-indirect and backward-forward alignments.
			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}. but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}, but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching. However,
			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching. However, in \gls{mimo} each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
			% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
			% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
			% is sufficient for perfect alignment
			% and is sufficient for perfect subspace alignment.
			% In \gls{mimo}, perfect subspace alignment is generally impossible due to the lack of direct control over the indirect channels.aa
			% backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) alignments of the singular matrices.
			\item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength. In \gls{siso}, diagonal \gls{ris} provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$. By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
			The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{R} \times N_\mathrm{T}$.
			% effect is more pronounced in \gls{mimo} since the number of subchannels associated with each group grows quadratically with the dimensions.
			% The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions. since the number of subchannels associated with each group grows quadratically with the dimensions.
			% It suggests that the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength. In \gls{siso}, the maximum indirect channel amplitude by diagonal \gls{ris} is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are independent permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$. By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
			% \begin{equation}
			% 	\item \
			% \end{equation}
			% and $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$. By rearrangement inequality,
			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength. In \gls{siso}, the optimal indirect channel amplitude is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ by diagonal \gls{ris} and $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},\pi_\mathrm{B}(n)} \rvert \lvert h_{\mathrm{F},\pi_\mathrm{F}(n)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi(\cdot)$ is a permutation of $\{1, \ldots, N_\mathrm{S}\}$.
			% this is unique to \gls{bd}-\gls{ris} --- each group can rearrange and combine the backward and forward subchannels by strength. In \gls{siso}, the optimal indirect channel amplitude is relaxed from $\sum_n \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ to $\sum_n \lvert h_{\mathrm{B},\pi(n)} \rvert \lvert h_{\mathrm{F},\pi(n)} \rvert$ where $\pi(\cdot)$ is a permutation of $\{1, \ldots, L\}$.
			% from strongest to weakest, which attains the maximum in rearrangement inequality.
		\end{itemize}
	\end{remark}

	% TODO: add illustrations for both

	% In \gls{siso}, the equivalent channel can be further simplified as
	% \begin{equation}
	% 	h = h_\mathrm{D} + \sum_g \mathbf{h}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{h}_{\mathrm{F},g},
	% \end{equation}
	% subspace alignment boils down to phase matching

	% For the \gls{siso} case in Fig. \subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
	% This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
	% Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
	% This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
	% That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
	% Now consider a diagonal \gls{ris} in \gls{mimo}.
	% Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
	% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
	% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
	% We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.

	% \begin{equation}
	% 	\mathbf{H} = \underbrace{\mathbf{H}_\mathrm{D} + \underbrace{\sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}_\text{group-wise}}_\text{direct-indirect},
	% \end{equation}
	% which involves three subspace alignment problems:
	% which involves three subspace alignment problems
	% \begin{equation}
	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{backward-forward}\\\text{additive alignment}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
	% \end{equation}
	% \begin{equation}
	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g}_{\substack{\text{backward}\\\text{align}}} \underbrace{\mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{forward}\\\text{align}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
	% \end{equation}
	% Then the equivalent channel can be rewritten as
	% Since the field of (block) unitary matrices formulate a field that is closed under multiplication
	% Since block unitary matrices satisfy the axioms of a field under matrix multiplication
	% \begin{remark}
	% 	% To understand the \gls{b} gain from in-group connections
	% \end{remark}

	% \begin{remark}
	% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
	% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
	% 	\begin{equation}
	% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
	% 		\label{eq:scattering_fc_tight}
	% 	\end{equation}
	% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
	% 	\begin{itemize}
	% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
	% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
	% 	\end{itemize}
	% \end{remark}

	% \begin{remark}
	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
	% \end{remark}
	% \begin{remark}
	% 	Individual forward and backward \gls{csi} are required for \gls{bd}-\gls{ris} designs.
	% 	This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
	% 	% Later we will show the potential benefits from the \gls{csi} overhead.
	% \end{remark}
\end{section}

\begin{section}{Channel Singular Values Redistribution}
	\begin{subsection}{A Toy Example}\label{sc:toy_example}
		We first illustrate the channel shaping capabilities of different \gls{ris} by a toy example.
		% We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{bd}-\gls{ris} has 4 independent angular parameters
		\begin{equation}
			\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
			\end{bmatrix}.
		\end{equation}
		In particular, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
		We also enforce symmetry by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
		\begin{figure}
			\centering
			\includegraphics[width=\columnwidth]{assets/chapter_3/singular_trend.eps}
			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetry unitary \gls{ris}.}
			\label{fg:singular_trend}
		\end{figure}
		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
		It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and design parameters.
		A larger performance gap is expected when asymmetric \gls{bd}-\gls{ris} is available.
		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
	\end{subsection}

	\begin{subsection}{Pareto Frontier Characterization}
		We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:pareto_unitary}}
		\end{maxi!}
		where $n \in \{1,\ldots,N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
		Varying $\{\rho_n\}$ unveils the entire achievable singular value region.
		Thus, the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
		The objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} for group $g$ corresponds to the Stiefel manifold.
		Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.

		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a block-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
		It leverages the fact that unitary matrices are closed under multiplication.
		At iteration $r$, the gradient is computed in the Euclidean space and translated to the Riemannian manifold \cite{Absil2009}
		\begin{gather}
			\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
			\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
		\end{gather}
		The Polak-Ribierre parameter \cite{Polak1969} is approximated as \cite{Abrudan2009}
		\begin{equation}
			\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
			\label{eq:parameter_cg}
		\end{equation}
		and the conjugate direction is
		\begin{equation}
			\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}. % $\mathcal{O}(N_\mathrm{S}^2)$
			\label{eq:direction_cg}
		\end{equation}
		In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
		\begin{equation}
			\mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}. % $\mathcal{O}(N_\mathrm{S}^3)$
			\label{eq:geodesic}
		\end{equation}
		An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.\footnote{To double the step size, one only need to square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.}
		Finally, the scattering matrix is updated along the geodesic as
		\begin{equation}
			\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
			\label{eq:update_geodesic}
		\end{equation}
		Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
		Convergence to stationary points is guaranteed.

		\begin{remark}
			Compared with universal manifold optimization \cite{Absil2009,Pan2022d}, Algorithm~\ref{ag:rcg} inherits a trifold benefit from \cite{Abrudan2008,Abrudan2009}:
			\begin{enumerate}
				\item No retraction thanks to rotational update \eqref{eq:geodesic}, \eqref{eq:update_geodesic};
				\item Lower computational complexity per iteration;
				\item Faster convergence thanks to proper parameter space.
			\end{enumerate}
		\end{remark}

		% \setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			% \small
			\caption{Block-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
			\label{ag:rcg}
			\begin{algorithmic}[1]
				\Require $f(\mathbf{\Theta})$, $G$
				\Ensure $\mathbf{\Theta}^\star$
				\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
				\Repeat
					\For {$g \gets 1$ to $G$}
						\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean} \label{ln:gradient_euclidean}
						\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riemannian}
						\State $\gamma_g^{(r)} \gets$ \eqref{eq:parameter_cg}
						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
							\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
						\EndIf
						\State $\mu \gets 1$
						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic}
						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
							\State $\mu \gets 2 \mu$
						\EndWhile
						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
							\State $\mu \gets \mu / 2$
						\EndWhile
						\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:update_geodesic}
					\EndFor
					\State $r \gets r+1$
				\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}

		\begin{lemma}\label{lm:pareto_gradient}
			The Euclidean gradient of \eqref{ob:pareto} w.r.t. \gls{bd}-\gls{ris} group $g$ is
			\begin{equation}
				\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathrm{diag}(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
				\label{eq:pareto_gradient}
			\end{equation}
			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}$, respectively.
		\end{lemma}
		\begin{proof}
			Please refer to Appendix~\ref{ap:pareto_gradient}.
		\end{proof}

		%  The Euclidean gradient of \gls{bd}-\gls{ris} group $g$ is computed as
		% where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto} where line \ref{ln:gradient_euclidean} uses \eqref{eq:pareto_gradient} explicitly.
		% \eqref{eq:pareto_gradient} is used in line \ref{ln:gradient_euclidean}.
	\end{subsection}

	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
		We then discuss some analytical bounds related to channel singular values.
		\begin{proposition}[degree of freedom]\label{pp:dof}
			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
		\end{proposition}
		\begin{proof}
			Please refer to Appendix~\ref{ap:dof}.
		\end{proof}

		\begin{proposition}[rank-deficient channel]\label{pp:rank_deficient}
			% If the forward/backward channel is rank-$k$, then a \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n > k$) channel singular value to the $n-k$-th singular value of $\mathbf{T}$, or suppress the $n$-th ($n < N - k + 1$) channel singular value to the $n$-th singular value of $\mathbf{T}$.
			% If the forward/backward channel is rank-$k$, then a sufficiently large \gls{bd}-\gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ equivalent channel singular values without bounds.
			If the forward or backward channel is rank-$k$, then regardless of the \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
			\begin{align}
				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_bound_enlarge}          \\
				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
			\end{align}
			where
			% \begin{align}
			% 	\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
			% 	\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k.
			% \end{align}
			\begin{equation}
				\mathbf{T} \mathbf{T}^\mathsf{H} =
				\begin{cases}
					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
				\end{cases}
				\label{eq:auxiliary_matrix}
			\end{equation}
			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
			% where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the forward channel is rank-$k$ and $\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the backward channel is rank-$k$.
		\end{proposition}
		\begin{proof}
			Please refer to Appendix~\ref{ap:rank_deficient}.
		\end{proof}

		% \begin{corollary}[degree of freedom]
		% 	In point-to-point \gls{mimo} with or without direct link, \gls{bd}-\gls{ris} cannot provide a higher \gls{dof} than diagonal \gls{ris}.
		% \end{corollary}

		\begin{corollary}[extreme singular values\label{co:extreme}]
			With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded above while the last $k$ channel singular values can be suppressed to zero.
			% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
			% If the forward or backward channel is rank-$k$ and the \gls{ris} is sufficiently large, then the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
			% If the forward/backward channel is rank-$k$, then the first (resp. last) $k$ singular values of the equivalent channel are unbounded above (resp. below).
			% a sufficiently large \gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ singular values of the equivalent channel without bounds.
		\end{corollary}

		\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} in \cite{Semmler2023}.}\label{co:los}]
			If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp. suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp. $n$-th) singular value of $\mathbf{T}$, that is,
			\begin{equation}
				\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
				\label{iq:sv_bound_los}
			\end{equation}
		\end{corollary}

		In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.

		\begin{proposition}[fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the channel singular values can be manipulated up to
			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
			% only bounds that apply here are those that apply to the singular values of
			\begin{equation}
				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
			\end{equation}
			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
			% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
		\end{proposition}

		\begin{proof}
			Please refer to Appendix~\ref{ap:fully_connected}.
		\end{proof}

		The problem now becomes how the singular values of matrix product are bounded by the singular values of its individual factors.
		Let $N' = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le N'$.
		We have the following corollaries.

		\begin{corollary}[generic singular value bounds \cite{Fulton2000}]
			\begin{equation}
				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
				\label{iq:sv_bound_fc}
			\end{equation}
			for all admissible triples $(I, J, K) \in T_r^{N'}$ with $r < N'$, where
			\begin{equation*}
				\begin{gathered}
					% T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
					% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
					T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \forall p < r, (F, G, H) \in T_p^r,\\
					\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
				\end{gathered}
			\end{equation*}
			\begin{equation*}
				U_r^{N'} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
			\end{equation*}
		\end{corollary}

		\begin{corollary}[upper bound on the largest singular value]
			\begin{equation}
				\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}).
			\end{equation}
		\end{corollary}

		% \begin{corollary}[lower bound on the smallest singular value]
		% 	\begin{equation}
		% 		\sigma_{N'}(\mathbf{H}) \ge \sigma_{N'}(\mathbf{H}_\mathrm{B}) \sigma_{N'}(\mathbf{H}_\mathrm{F}).
		% 	\end{equation}
		% \end{corollary}

		\begin{corollary}[upper bound on the product of first $k$ singular values]
			\begin{equation}
				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
			\end{equation}
		\end{corollary}

		% \begin{corollary}[lower bound on the product of last $k$ singular values]
		% 	\begin{equation}
		% 		\prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
		% 	\end{equation}
		% \end{corollary}

		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
			\begin{equation}
				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
				\label{iq:sv_bound_fc_power}
			\end{equation}
			When $k = N'$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels.
		\end{corollary}

		% \begin{remark}
		% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
		% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
		% 	\begin{equation}
		% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
		% 		\label{eq:scattering_fc_tight}
		% 	\end{equation}
		% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
		% 	\begin{itemize}
		% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
		% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
		% 	\end{itemize}
		% \end{remark}

		Tight bounds are inapplicable when a \gls{mimo} direct link is present, as the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
		Such a balance often involves optimization approaches and another example will be discussed in Section~\ref{sc:low_complexity}.
	\end{subsection}

\end{section}

\begin{section}{Achievable Rate Maximization}\label{sc:rate}
	The \gls{mimo} achievable rate maximization problem is formulated w.r.t. joint active and passive beamforming
	\begin{maxi!}
		{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
		\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
	\end{maxi!}
	where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the noise power, and $P$ is the transmit power budget.
	Two methods are proposed below to solve problem \eqref{op:rate}.

	\begin{subsection}{Alternating Optimization}
		Consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
		For a given $\mathbf{W}$, the passive beamforming subproblem is
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		\end{maxi!}
		where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
		\begin{lemma}\label{lm:rate_gradient}
			The Euclidean gradient of \eqref{ob:rate_passive} w.r.t. \gls{bd}-\gls{ris} block $g$ is
			\begin{equation}
				\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
				\label{eq:rate_gradient}
			\end{equation}
		\end{lemma}

		\begin{proof}
			Please refer to Appendix~\ref{ap:rate_gradient}.
		\end{proof}
		Algorithm \ref{ag:rcg} is then invoked to solve problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
		Since \eqref{ob:rate_passive} is a concave function of $\mathbf{\Theta}$, convergence to local-optimal points is guaranteed.
		On the other hand, the global optimal transmit precoder for a fixed $\mathbf{\Theta}$ is given by the eigenmode transmission \cite{Clerckx2013}
		\begin{equation}
			\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
			\label{eq:precoder_eigenmode}
		\end{equation}
		where $\mathbf{V}$ is the right channel singular matrix and $\mathbf{S}^\star$ is the optimal water-filling power allocation matrix.
		The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
	\end{subsection}

	\begin{subsection}{Low-Complexity Solution}\label{sc:low_complexity}
		We then propose a low-complexity solution to problem \eqref{op:rate} based on channel shaping.
		The passive beamforming subproblem \eqref{op:rate_passive} involves transmit covariance matrix $\mathbf{Q}$ and thus requires iterative \gls{rcg} update.
		Instead, we decouple the joint \gls{ris}-transceiver design by recasting \eqref{op:rate_passive} as channel power maximization
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
		\end{maxi!}
		% which only accounts for channel characteristics but has no trivial solution.
		\begin{remark}
			As mentioned in Section \ref{sc:bounds}, the key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
			Problem \eqref{op:power_passive} is very similar (in terms of maximizing the inner product of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$) to the weighted orthogonal Procrustes problem \cite{Gower2004}
			\begin{mini!}
				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
			\end{mini!}
			which has no trivial solution.
			One lossy transformation, by moving $\mathbf{\Theta}$ to one side \cite{Bell2003}, formulates standard orthogonal Procrustes problems
			\begin{mini!}
				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
			\end{mini!}
			which has global optimal solutions
			\begin{equation}
				\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}
				\label{eq:orthogonal_procrustes_solution}
			\end{equation}
			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
			This suboptimal solution only applies to fully-connected \gls{bd}-\gls{ris}.
		\end{remark}

		Inspired by \cite{Nie2017}, we propose a general solution to problem \eqref{op:power_passive} with arbitrary group size.
		The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form.

		\begin{proposition}\label{pp:power}
			Starting from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
			\begin{equation}
				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
				\label{eq:scattering_power}
			\end{equation}
			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
			\begin{equation}
				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
				\label{eq:auxiliary_matrix_power}
			\end{equation}
		\end{proposition}

		\begin{proof}
			Please refer to Appendix~\ref{ap:power}.
		\end{proof}
		Once the channel shaping problem \eqref{op:power_passive} is solved, the transmit precoder can be obtained by \eqref{eq:precoder_eigenmode}.
		This two-stage approach decouples both blocks and is computationally efficient.
	\end{subsection}

	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{fg:pc_rate_sx}]{
	% 		\resizebox{0.48\columnwidth}{!}{
	% 			\input{assets/chapter_3/pc_rate_sx.tex}
	% 		}
	% 	}
	% 	\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{fg:pc_rate_tx}]{
	% 		\resizebox{0.48\columnwidth}{!}{
	% 			\input{assets/chapter_3/pc_rate_tx.tex}
	% 		}
	% 	}
	% 	\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
	% 	\label{fg:pc_rate}
	% \end{figure}

	% Fig.~\ref{fg:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
	% To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
	% This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
	% If tetrads can be formed in \gls{bd}-\gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
	% Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
	% We thus conclude dyadic or tetradic \gls{bd}-\gls{ris} usually strike a good balance between performance and complexity.

	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{0.65\columnwidth}{!}{
	% 		\input{assets/chapter_3/power_sx.tex}
	% 	}
	% 	\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$. $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
	% 	\label{fg:power_sx}
	% \end{figure}

	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[Without Direct Link\label{fg:pc_power_bond_nd}]{
	% 		\resizebox{0.48\columnwidth}{!}{
	% 			\input{assets/chapter_3/pc_power_bond_nd.tex}
	% 		}
	% 	}
	% 	\subfloat[With Direct Link\label{fg:pc_power_bond_hd}]{
	% 		\resizebox{0.48\columnwidth}{!}{
	% 			\input{assets/chapter_3/pc_power_bond_hd.tex}
	% 		}
	% 	}
	% 	\caption{Average channel power versus \gls{ris} group size $L$. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
	% 	\label{fg:pc_power_bond}
	% \end{figure}
	% % Fig.~\ref{fg:power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
	% % Fig.~\ref{fg:power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
	% Fig.~\ref{fg:power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
	% % The behavior is more obvious for a large \gls{ris}.
	% This behavior is more pronounced for a large \gls{ris}.
	% For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
	% % \gls{bd}-\gls{ris} provides a higher channel power than conventional \gls{ris}.
	% % As $L$ increases from 1 to 2,
	% It implies that the channel shaping capability of \gls{bd}-\gls{ris} scales with group size $L$.

	% Fig.~\ref{fg:pc_power_bond_hd} and \ref{fg:pc_power_bond_nd} compare the average channel power without and with direct link.
	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
	% % ``Cascaded'' means the maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
	% % maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
	% % ? ``Cascaded'' means the \emph{power product} of the forward and backward channels.
	% % ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues of the forward and backward channels.
	% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
	% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect subspace.
	% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
	% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward subspace alignment for an optimal channel boost.
	% It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
	% This again emphasizes the advantage of in-group connection of \gls{bd}-\gls{ris}.
	% % This is because the direct and indirect channels superpose
	% % the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
	% % When the direct link is present, a small $L$ cannot align the direct-indirect subspace.

	% % neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
	% % We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
	% % For conventional \gls{ris},
	% % align the direct-indirect subspace.
	% % When the direct link is present, a small $L$ can neither align the direct-indirect subspace nor the forward-backward subspace.
	% % For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
	% % neither the direct-indirect nor the forward-backward subspace can be effectively aligned with a small $L$.

	% % When the direct link is present, a small $L$ can neither preserve the
	% % neither align the direct-indirect subspace nor the forward-backward subspace.

	% % When the direct link is absent, a large $L$ can align the forward-backward subspace but cannot preserve the forward-backward power balance.

\end{section}

\begin{section}{Simulation Results}\label{sc:simulation}
	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
	$\kappa \to \infty$ is assumed for all channels unless otherwise specified.

	\begin{table*}[!t]
		\caption{Average Performance of \gls{bd}-\gls{ris} Designs}
		\label{tb:complexity_test}
		\centering
		\begin{tabular}{ccccccc}
			\toprule
			\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                                 \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
			                                & Objective                              & Iterations                             & Time [s]         & Objective        & Iterations & Time [s]  \\ \midrule
			Geodesic                        & $\num{4.355e-3}$                       & 11.61                                  & $\num{2.038e-2}$ & $\num{1.164e-2}$ & 25.78      & 3.216     \\
			Non-geodesic                    & $\num{4.168e-3}$                       & 169.5                                  & $\num{1.420e-1}$ & $\num{8.873e-3}$ & 278.1      & 27.81     \\ \bottomrule
		\end{tabular}
	\end{table*}

	\begin{subsection}{Channel Singular Values Redistribution}
		\begin{subsubsection}{Pareto Frontier}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/singular_pareto_sx32_nd.tex}
					}
				}
				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/singular_pareto_sx128.tex}
					}
				}
				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
				\label{fg:singular_pareto}
			\end{figure}
			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
		\end{subsubsection}

		\begin{subsubsection}{Analytical Bounds and Numerical Results}
			\begin{figure}[!t]
				\centering
				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/singular_bound_rank1_sx32.tex}
					}
				}
				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/singular_bound_rank1_sx64.tex}
					}
				}
				\\
				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/singular_bound_rank2_sx128.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/singular_bound_rank4_sx256.tex}
					}
				}
				\caption{
					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
					`rank-$k$' refers to the forward channel.
				}
				\label{fg:singular_bound}
			\end{figure}
			Fig. \ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
			Here we assme a rank-$k$ forward channel without loss of generality.
			When the \gls{ris} is in the vicinity of the transmitter, Figs. \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
			% The observations align with Proposition \ref{pp:rank_deficient} that t
			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
			Those observations align with Proposition \ref{pp:rank_deficient} and Corollary \ref{co:extreme}.
			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.

			\begin{figure}[!t]
				\centering
				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/power_bond_txrx1_nd.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_3/power_bond_txrx4_nd.tex}
					}
				}
				\caption{
					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward subchannels.
				}
				\label{fg:power_bond}
			\end{figure}

			Fig. \ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form or via optimization approach \eqref{eq:scattering_power}.
			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
			% We observe that the bound is also tight for fully-connected \gls{bd}-\gls{ris}.
			% Increasing the group size of \gls{bd}-\gls{ris} significantly improves the channel power especially for a large \gls{mimo}.
			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a fully-connected one can achieve the bound.
			% The bound here indicates how much power can potentially be extracted from the forward and backward channels.
			% We observe that using a larger group size can approach the bound better, and full
			% We observe that the bound is tight for fully-connected \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
			For the \gls{siso} case in Fig. \subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
			Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
			This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
			Now consider a diagonal \gls{ris} in \gls{mimo}.
			Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
			Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
			It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
		\end{subsubsection}

		% The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
		% Clearly, a larger group size provides
		% and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
	\end{subsection}

	\begin{subsection}{Achievable Rate Maximization}
		\begin{figure}[!t]
			\centering
			\subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)\label{fg:power_sx_txrx16_nd}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_3/power_sx_txrx16_nd.tex}
				}
			}
			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_3/power_sx_txrx16.tex}
				}
			}
			\caption{
				Average maximum channel power versus \gls{ris} configuration.
				`OP-left' and `OP-right' refer to the suboptimal solutions to problem \eqref{op:power_passive} by lossy transformation \eqref{op:standard_orthogonal_procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
			}
			\label{fg:power_sx}
		\end{figure}

		We first focus on channel shaping subproblem \eqref{op:power_passive_approx}.
		Fig. \ref{fg:power_sx} shows the achievable channel power under different \gls{ris} configurations.
		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} is even larger with direct link.
		For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power as a 256-element diagonal \gls{ris} in Fig. \ref{fg:power_sx_txrx16}, but not in Fig. \ref{fg:power_sx_txrx16_nd}.
		% This again credits to the superior subspace alignment capability of \gls{bd}-\gls{ris}.
		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the subspace alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.

		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_3/rate_beamforming.tex}
				}
			}
			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_3/rate_txrx.tex}
				}
			}
			\\
			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_3/rate_sx.tex}
				}
			}
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_3/rate_kfactor.tex}
				}
			}
			\caption{
				Average achievable rate versus \gls{mimo} and \gls{ris} configurations.
				The noise power is $\eta = \qty{-75}{dB}$, corresponding to a direct \gls{snr} of \num{-10} to \qty{30}{dB}.
				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
				`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
			}
			\label{fg:rate}
		\end{figure}

		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
		At a transmit power of \qty{10}{dB}, Fig. \subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to 4T4R \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better tradeoff between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
	This translates to a wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.
	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior subspace alignment and subchannel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.

	One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
	Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
	Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward subspaces simultaneously.
	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
	% into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
	% even better channel shaping can be achieved by incorporating the \gls{ris} into the \gls{mimo} precoding and combining design.
\end{section}

### 2024-03-04 content/chapter_1.tex
:construction: Add chapters 2 and 3
:construction: Add section titles

--- 2024-02-29 Chapter1/chapter1.tex
@@
 %!TEX root = ../thesis.tex
-%*******************************************************************************
-%*********************************** First Chapter *****************************
-%*******************************************************************************
 
-\chapter{Getting started}  %Title of the First Chapter
+\graphicspath{{assets/chapter_1/}}
 
-\ifpdf
-    \graphicspath{{Chapter1/Figs/Raster/}{Chapter1/Figs/PDF/}{Chapter1/Figs/}}
-\else
-    \graphicspath{{Chapter1/Figs/Vector/}{Chapter1/Figs/}}
-\fi
+\chapter{Introduction}
+% \chapter{Summary of research problems and contribution}
 
-%********************************** %First Section  **************************************
+\begin{section}{Motivation}
 
-\begin{section}{Introduction}
-	\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
-		With the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
-\gls{swipt} is a promising solution to connect and power mobile devices via \gls{rf} waves.
-It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and Machine to Machine (M2M) networks.
-The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.
-
-		% The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels.
-\cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., Time Switching (TS) and Power Splitting (PS).
-Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels.
-On the other hand, \cite{Trotter2009} pointed out that the RF-to-DC conversion efficiency of rectifiers depends on the input power and waveform shape.
-It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
-Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for WPT.
-Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}.
-A low-complexity adaptive waveform design by Scaled Matched Filter (SMF) was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
-Beyond WPT, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to SWIPT design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the R-E region; (iii) a combination of PS and TS is generally the best strategy; (iv) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG); (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient SWIPT design.
-Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for SWIPT under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT.
-The answers shed new light to the fundamental limits of SWIPT and practical signaling (e.g., modulation and waveform) strategies.
-It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of CSCG and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG.
-Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
-	\end{subsection}
-
-	\begin{equation}
-		\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
-		\label{eq:update_geodesic}
-	\end{equation}
-
-	% \begin{subsection}{Intelligent Reflecting Surface}
-	% 	Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
-In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
-Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the IRS assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
-
-	% 	Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
-\cite{Wu2018} proposed an IRS-assisted Multiple-Input Single-Output (MISO) system and jointly optimized the precoder at the Access Point (AP) and the phase shifts at the IRS to minimize the transmit power.
-The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
-In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
-To estimate the cascaded AP-IRS-User Equipment (UE) link without RF-chains at the IRS, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
-The hardware architecture, design challenges, and application opportunities of practical IRS were covered in \cite{Wu2020}.
-In \cite{Dai2020}, a prototype IRS with \num{256} \num{2}-bit elements based on Positive Intrinsic-Negative (PIN) diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
-	% \end{subsection}
-
-	% \begin{subsection}{IRS-Aided SWIPT}
-	% 	By integrating IRS with SWIPT, the constructive reflection can boost the end-to-end power efficiency and improve the R-E tradeoff.
-In multi-user cases, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
-It was also claimed that Line-of-Sight (LoS) links could boost the WSP since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
-However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
-Based on practical IRS and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based IRS-assisted SWIPT system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
-The proposed framework provides a flexible tradeoff between performance and complexity.
-To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS, to investigate the R-E tradeoff for one SWIPT user with co-located information decoder and energy harvester.
-We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.
-
-	% 	\emph{First,} we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
-Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output DC power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce DC), waveform coupling (i.e., different waveforms jointly contribute to DC), and high-order objective function.
-To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the TS and PS receiving modes.
-The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable R-E region.
-This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT.
-
-	% 	\emph{Second,} we characterize each R-E boundary point by energy maximization under a rate constraint.
-The problem is solved by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT).
-For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity.
-For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof.
-Finally, the superposed waveform and the splitting ratio are optimized by the Geometric Programming (GP) technique.
-The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
-This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.
-
-	% 	\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm.
-To facilitate practical SWIPT implementation, the Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in time and power domains, respectively.
-The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes.
-The proposed low-complexity BCD algorithm achieves a good balance between performance and complexity.
-
-	% 	\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that (i) IRS enables constructive reflection and flexible subchannel design in the frequency domain that is essential for SWIPT systems; (ii) IRS mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) TS is preferred at low Signal-to-Noise Ratio (SNR) while PS is preferred at high SNR; (v) there exist two optimal IRS development locations, one close to the AP and one close to the UE; (vi) the output SNR scales linearly with the number of transmit antennas and quadratically with the number of IRS elements; (vii) due to the rectifier nonlinearity, the output DC scales quadratically with the number of transmit antennas and quartically with the number of IRS elements; (viii) for narrowband SWIPT, the optimal active and passive beamforming for any R-E point are also optimal for the whole R-E region; (ix) for broadband SWIPT, the optimal active and passive beamforming depend on specific R-E point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded CSIT and finite IRS reflection states.
-
-	% 	\emph{Organization:} Section~\ref{se:system_model} introduces the system model.
-Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming design.
-Section~\ref{se:performance_evaluation} provides simulation results.
-Section~\ref{se:conclusion_and_future_works} concludes the paper.
-
-	% 	\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters.
-$j$ denotes the imaginary unit.
-$\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
-$\boldsymbol{I}$ denotes the identity matrix.
-$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
-$\Re\{\cdot\}$ retrieves the real part of a complex entity.
-$[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
-$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
-$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
-$\odot$ denotes the Hadamard product.
-$\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
-$\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
-$\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t.
-random variable $X$ ($X$ is omitted for simplicity).
-The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
-$\sim$ means ``distributed as''.
-$(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterated value and the stationary solution.
-	% \end{subsection}
 \end{section}
 
-%********************************** %Second Section  *************************************
-\section{Why do we use loren ipsum?} %Section - 1.2
+\begin{section}{Objectives and Challenges}
 
-It is a long established fact that a reader will be distracted by the readable content of a page when looking at its layout.
-The point of using Lorem Ipsum is that it has a more-or-less normal distribution of letters, as opposed to using `Content here, content here', making it look like readable English.
-Many desktop publishing packages and web page editors now use Lorem Ipsum as their default model text, and a search for `lorem ipsum' will uncover many web sites still in their infancy.
-Various versions have evolved over the years, sometimes by accident, sometimes on purpose (injected humour and the like).
+\end{section}
 
-%********************************** % Third Section  *************************************
-\section{Where does it come from?}  %Section - 1.3
-\label{section1.3}
+\begin{section}{Outline and Contributions}
 
-Contrary to popular belief, Lorem Ipsum is not simply random text.
-It has roots in a piece of classical Latin literature from 45 BC, making it over 2000 years old.
-Richard McClintock, a Latin professor at Hampden-Sydney College in Virginia, looked up one of the more obscure Latin words, consectetur, from a Lorem Ipsum passage, and going through the cites of the word in classical literature, discovered the undoubtable source.
-Lorem Ipsum comes from sections 1.10.32 and 1.10.33 of "de Finibus Bonorum et Malorum" (The Extremes of Good and Evil) by Cicero, written in 45 BC.
-This book is a treatise on the theory of ethics, very popular during the Renaissance.
-The first line of Lorem Ipsum, "Lorem ipsum dolor sit amet..", comes from a line in section 1.10.32.
+\end{section}
 
-The standard chunk of Lorem Ipsum used since the 1500s is reproduced below for those interested.
-Sections 1.10.32 and 1.10.33 from ``de Finibus Bonorum et Malorum" by Cicero are also reproduced in their exact original form, accompanied by English versions from the 1914 translation by H.
-Rackham
+\begin{section}{Publications}
 
-``Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum."
-
-Section 1.10.32 of ``de Finibus Bonorum et Malorum", written by Cicero in 45 BC: ``Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo.
-Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt.
-Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem.
-Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur?
-Quis autem vel eum iure reprehenderit qui in ea voluptate velit esse quam nihil molestiae consequatur, vel illum qui dolorem eum fugiat quo voluptas nulla pariatur?"
-
-1914 translation by H.
-Rackham: ``But I must explain to you how all this mistaken idea of denouncing pleasure and praising pain was born and I will give you a complete account of the system, and expound the actual teachings of the great explorer of the truth, the master-builder of human happiness.
-No one rejects, dislikes, or avoids pleasure itself, because it is pleasure, but because those who do not know how to pursue pleasure rationally encounter consequences that are extremely painful.
-Nor again is there anyone who loves or pursues or desires to obtain pain of itself, because it is pain, but because occasionally circumstances occur in which toil and pain can procure him some great pleasure.
-To take a trivial example, which of us ever undertakes laborious physical exercise, except to obtain some advantage from it?
-But who has any right to find fault with a man who chooses to enjoy a pleasure that has no annoying consequences, or one who avoids a pain that produces no resultant pleasure?"
-
-Section 1.10.33 of ``de Finibus Bonorum et Malorum", written by Cicero in 45 BC: ``At vero eos et accusamus et iusto odio dignissimos ducimus qui blanditiis praesentium voluptatum deleniti atque corrupti quos dolores et quas molestias excepturi sint occaecati cupiditate non provident, similique sunt in culpa qui officia deserunt mollitia animi, id est laborum et dolorum fuga.
-Et harum quidem rerum facilis est et expedita distinctio.
-Nam libero tempore, cum soluta nobis est eligendi optio cumque nihil impedit quo minus id quod maxime placeat facere possimus, omnis voluptas assumenda est, omnis dolor repellendus.
-Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet ut et voluptates repudiandae sint et molestiae non recusandae.
-Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat."
-
-1914 translation by H.
-Rackham: ``On the other hand, we denounce with righteous indignation and dislike men who are so beguiled and demoralized by the charms of pleasure of the moment, so blinded by desire, that they cannot foresee the pain and trouble that are bound to ensue; and equal blame belongs to those who fail in their duty through weakness of will, which is the same as saying through shrinking from toil and pain.
-These cases are perfectly simple and easy to distinguish.
-In a free hour, when our power of choice is untrammelled and when nothing prevents our being able to do what we like best, every pleasure is to be welcomed and every pain avoided.
-But in certain circumstances and owing to the claims of duty or the obligations of business it will frequently occur that pleasures have to be repudiated and annoyances accepted.
-The wise man therefore always holds in these matters to this principle of selection: he rejects pleasures to secure other greater pleasures, or else he endures pains to avoid worse pains."
+\end{section}

### 2024-03-04 content/chapter_2.tex
:construction: Add section titles

@@
 
-\chapter{Getting started}
+\chapter{Background and Literature Review}
 
-\begin{section}{Introduction}
-	\label{sc:introduction}
-	Future wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
-	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
-	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
-	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
-	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
-	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
-	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
-	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and superimposes its own information, and the co-located receiver cooperatively decodes both links.
-	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
-	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
-	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
-	Each \gls{ris} element is considered as a \emph{channel shaper} and the reflection pattern depends exclusively on the \gls{csi}.
+\begin{section}{\glsfmtfull{ris}}
+	% \begin{subsection}{Programmable Metamaterials}
 
-	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
-	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
-	The achievable rate and optimal input distribution for binary-input \gls{ambc} were investigated in \cite{Qian2019b}, but its impact on the primary link was omitted.
-	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
-	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
-	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
-	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
-	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
-	Importantly, active-passive coexisting networks have three special and important properties:
-	\begin{enumerate}
-		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
-		\item Backscatter signal strength is much weaker than primary due to \emph{double fading};
-		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
-	\end{enumerate}
-	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
-	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
-	Under those assumptions, the achievable rate region of cell-free \gls{sr} was characterized in \cite{Dai2023}.
-	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
-	However, this assumption severely limits the backscatter throughput.
+	% \end{subsection}
 
-	\begin{figure}[!t]
-		\centering
-		\subfloat[\gls{mbc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/chapter_2/mbc.tex}
-			}
-			\label{fg:mbc}
-		}
-		\subfloat[\gls{bbc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/chapter_2/bbc.tex}
-			}
-			\label{fg:bbc}
-		}
-		\\
-		\subfloat[\gls{ambc}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/chapter_2/ambc.tex}
-			}
-			\label{fg:ambc}
-		}
-		\subfloat[\gls{sr}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/chapter_2/sr.tex}
-			}
-			\label{fg:sr}
-		}
-		\\
-		\subfloat[\gls{ris}]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/chapter_2/ris.tex}
-			}
-			\label{fg:ris}
-		}
-		\subfloat[RIScatter]{
-			\resizebox{0.48\linewidth}{!}{
-				\input{assets/chapter_2/riscatter.tex}
-			}
-			\label{fg:riscatter}
-		}
-		\caption{
-			Illustration of scattering applications.
-			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
-		}
-		\label{fg:scatter_illustration}
-	\end{figure}
+	\begin{subsection}{Hardware Implementation}
+		\begin{subsubsection}{Programmable Metamaterials}
 
-	\begin{table*}[!t]
-		\caption{Comparison of Scattering Applications}
-		\label{tb:scattering_applications}
-		\rowcolors{2}{gray!25}{white}
-		\renewcommand{\arraystretch}{1.4}
-		\begin{tabularx}{\textwidth}{CCCCCC}
-			\toprule
-			\hiderowcolors
-			                                       & \glsentryshort{mbc}/\glsentryshort{bbc} & \glsentryshort{ambc}        & \glsentryshort{sr} (large spreading factor)                         & \glsentryshort{ris} & RIScatter                                                          \\ \midrule
-			\showrowcolors
-			Information link(s)                    & Backscatter                             & Coexisting                  & Coexisting                                                          & Primary             & Coexisting                                                         \\
-			Primary signal on backscatter decoding & Carrier                                 & Multiplicative interference & Spreading code                                                      & ---                 & Energy uncertainty                                                 \\
-			Backscatter signal on primary decoding & ---                                     & Multiplicative interference & \glsentryshort{csi} uncertainty                                     & Passive beamforming & Dynamic passive beamforming                                        \\
-			Cooperative devices                    & ---                                     & No                          & Primary transmitter and co-located receiver                         & ---                 & Primary transmitter, scatter nodes, and co-located receiver        \\
-			Sequential decoding                    & ---                                     & No                          & Primary-to-backscatter, \glsentryshort{sic} and \glsentryshort{mrc} & ---                 & Backscatter-to-primary, no \glsentryshort{sic}/\glsentryshort{mrc} \\
-			Reflection pattern depends on          & Information source                      & Information source          & Information source                                                  & \glsentryshort{csi} & Information source, \glsentryshort{csi}, and \glsentryshort{qos}   \\
-			Reflection state distribution          & Equiprobable                            & Equiprobable                & Equiprobable or Gaussian                                            & Degenerate          & Flexible                                                           \\
-			Load-switching speed                   & Fast                                    & Slow                        & Slow                                                                & Quasi-static        & Arbitrary                                                          \\ \bottomrule
-		\end{tabularx}
-	\end{table*}
-
-	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
-	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
-	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
-	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
-	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019b} and \gls{qam} \cite{Dai2020a}.
-	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
-	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
-	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
-information elements) for passive beamforming (resp.
-backscatter modulation) \cite{Hu2021a}.
-	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
-	In contrast, \cite{Vardakis2023} exploited commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user.
-\label{cm:2.5}
-	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
-	Most relevant literature considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
-	Those problems are addressed in this paper and the contributions are summarized below.
-
-	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
-	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
-	A co-located receiver cooperatively decodes both coexisting links.
-	Each reflection state is simultaneously a passive beamforming codeword and part of information codeword.
-	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
-	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
-	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
-	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
-	However, two major challenges for RIScatter are the receiver design and input distribution design.
-	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
-
-	\emph{Second,} we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
-	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
-	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming afterwards.
-	The proposed receiver may be built over legacy receivers with minor hardware upgrade, as it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
-	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
-	This is the first paper to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.
-
-	\emph{Third,} we address the second challenge in a single-user multi-node \gls{miso} scenario.
-	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
-	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by the converging point of a sequence, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
-	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to other detection schemes.
-	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
-
-	\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
-	The observations include:
-	1) adaptive reflection state distribution design can flexibly shift between backscatter modulation and passive beamforming;
-	2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
-	3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
-	4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
-	5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
-	6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
-	7) \gls{pga} active beamformer effectively increases the primary (resp.
-backscatter) rate by boosting the receive \gls{snr} (resp.
-widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
-	8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
-\end{section}
-
-\begin{section}{RIScatter}
-	\label{sc:riscatter}
-	\begin{subsection}{Principles}
-		\label{sc:principles}
-		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
-		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
-		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
-		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
-		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
-		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
-		\begin{equation}
-			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
-			\label{eq:reflection_coefficient}
-		\end{equation}
-		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
-		Specifically,
-		\begin{itemize}
-			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
-			The reflection coefficient is used merely as part of information codeword \cite{Thomas2012a}
-			\begin{equation}
-				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-				\label{eq:backscatter_modulation}
-			\end{equation}
-			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
-			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
-			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
-			\begin{equation}
-				\Gamma_m = \alpha_m \exp(j \theta_m),
-				\label{eq:passive_beamforming}
-			\end{equation}
-			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
-		\end{itemize}
-
-		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
-		Each reflection coefficient simultaneously acts as a passive beamforming codeword and part of information codeword.
-		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
-		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Input Distribution]{
-				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/chapter_2/input_distribution.tex}
-				}
-				\label{fg:input_distribution}
-			}
-			\\
-			\subfloat[Reflection Pattern]{
-				\resizebox{0.8\columnwidth}{!}{
-					\input{assets/chapter_2/time_structure.tex}
-				}
-				\label{fg:time_structure}
-			}
-			\caption{
-				Input distribution and reflection pattern of scattering applications.
-				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
-				Shadowing means presence of primary link.
-				In this example, the optimal passive beamformer corresponds to state \num{2}.
-				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
-				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
-			}
-			\label{fg:scatter_comparison}
-		\end{figure}
-		\begin{remark}
-			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
-			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
-			\label{re:dynamic_passive_beamforming}
-		\end{remark}
-
-		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user.
-The node receiver can be implemented using simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
-		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Block Diagram]{
-				\resizebox{0.32\linewidth}{!}{
-					\input{assets/chapter_2/block_diagram.tex}
-				}
-				\label{fg:block_diagram}
-			}
-			\subfloat[Equivalent Circuit]{
-				\resizebox{0.37\linewidth}{!}{
-					\input{assets/chapter_2/equivalent_circuit.tex}
-				}
-				\label{fg:equivalent_circuit}
-			}
-			\subfloat[Scatter Model]{
-				\resizebox{0.28\linewidth}{!}{
-					\input{assets/chapter_2/scatter_model.tex}
-				}
-				\label{fg:scatter_model}
-			}
-			\caption{
-			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
-			The solid and dashed vectors represent signal and energy flows.
-			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
-			}
-			\label{fg:riscatter_node}
-		\end{figure*}
-		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
-		% The detail will be covered in Section~\ref{st:system_model}.
-	\end{subsection}
-
-	\begin{subsection}{System Model}
-		\label{sc:system_model}
-		\begin{figure}[!t]
-			\centering
-			\def\svgwidth{0.7\columnwidth}
-			\input{assets/chapter_2/riscatter_network.pdf_tex}
-			\caption{A single-user multi-node RIScatter network.}
-			\label{fg:riscatter_network}
-		\end{figure}
-		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
-		Without loss of generality, we assume all nodes have $M$ available reflection states.
-		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
-		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
-		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
-		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
-		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.
-The impact of channel estimation error will be investigated in Section~\ref{sc:simulation_results}.}.
-
-		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the (coded) backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
-		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
-		\begin{subequations}
-			\label{eq:equivalent_channel}
-			\begin{align}
-				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
-				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
-				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
-			\end{align}
-		\end{subequations}
-		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
-		Without loss of generality, we assume the spreading factor $N$ is a positive integer.
-		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
-		\begin{equation}
-			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
-			\label{eq:receive_signal}
-		\end{equation}
-		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the maximum average transmit power, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
-
-		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
-		The backscatter symbol $x_k$ (resp.
-symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp.
-value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp.
-$p(x_{m_{\mathcal{K}}})$).
-		\begin{remark}
-			Dispersed RIScatter nodes encode independently such that
-			\begin{equation}
-				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
-				\label{eq:equivalent_distribution}
-			\end{equation}
-			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
-			\label{re:independent_encoding}
-		\end{remark}
-
-		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the receive energy per backscatter block.
-		When $x_{m_\mathcal{K}}$ is transmitted, the receive signal $y$ follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with variance
-		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
-			\label{eq:receive_variance}
-		\end{equation}
-		and $z$ follows Gamma distribution with conditional \gls{pdf}
-		\begin{equation}
-			f(z|x_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
-			\label{eq:energy_distribution}
-		\end{equation}
-
-		\begin{remark}
-			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Qian2019b,Xu2020b,Zhang2021d,Hua2022,Hu2021a,Qian2019}.
-			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
-			\label{re:non_gaussian}
-		\end{remark}
-
-		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.\footnote{The reliability of the energy detector is improved by the adaptive input distribution and thresholding design.
-With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with low code-rate.
-In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.\label{fn:energy_detector}}
-		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.
-
-		\begin{remark}
-			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
-			It was proved deterministic detectors can be rate-optimal, but non-convex regions (consist of non-adjacent partitions) are generally required and the optimal number of thresholds is unknown \cite{Nguyen2018,Nguyen2021}.
-			Next, we restrict the energy detector to convex deterministic decision regions and consider sequential threshold design.
-		\end{remark}
-
-		Let $L = M^K$ be the number of decision regions.
-		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
-		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one mapped.
-Both notations are used interchangeably in the following context.}
-		\begin{equation}
-			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
-		\end{equation}
-		where $t_l$ is the decision threshold between hypotheses $x_{l}$ and $x_{l+1}$.
-		An example is shown in Fig.~\ref{fg:energy_distribution}.
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.8\columnwidth}{!}{
-				\input{assets/chapter_2/energy_distribution.tex}
-			}
-			\caption{
-				\gls{pdf} of the receive energy per backscatter block conditioned on different reflection state.
-			}
-			\label{fg:energy_distribution}
-		\end{figure}
-
-		When the threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
-		\begin{equation}
-			q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|x_{m_{\mathcal{K}}}) \, d z.
-			\label{eq:dmmac}
-		\end{equation}
-		The backscatter mutual information is
-		\begin{equation}
-			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
-			\label{eq:backscatter_mutual_information}
-		\end{equation}
-		where $I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}})$ is the backscatter information function
-		\begin{equation}
-			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{p(\hat{x}_{m_{\mathcal{K}}'})}.
-			\label{eq:backscatter_information_function}
-		\end{equation}
-
-		Once the backscatter information is successfully decoded, the user re-encodes to recover the reflection pattern, constructs the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
-		The primary mutual information is
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
-			\label{eq:primary_mutual_information}
-		\end{equation}
-		where $I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$ is the primary information function
-		\begin{equation}
-			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr).
-			\label{eq:primary_information_function}
-		\end{equation}
-	\end{subsection}
-\end{section}
-
-\begin{section}{Rate-Region Characterization}
-	With a slight abuse of notation, we define the weighed sum mutual information and information function as
-	\begin{align}
-		I(x_{\mathcal{K}})
-		 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}           \\
-		I(x_{m_\mathcal{K}})
-		 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function}
-	\end{align}
-	where $\rho \in \mathbb{I}$ is the \gls{qos}.
-	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented backscatter source.\label{fn:joint_encoding}}
-	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-		\addConstraint{\boldsymbol{1}^\mathsf{T} \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
-		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
-		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
-		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
-		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0},}{\label{co:nonnegative_threshold}}
-	\end{maxi!}
-	where $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
-	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
-	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problems from the vertices of $M$-dimensional probability simplex to the simplex itself.
-	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
-
-	\begin{subsection}{Input Distribution}
-		\label{sc:input_distribution}
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
-		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
-			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
-		\end{maxi!}
-		which involves the product term \eqref{eq:equivalent_distribution} and is generally non-convex (unless $K=1$).
-		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical solution that guarantees those conditions on the converging point of a sequence.
-		\begin{proposition}
-			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
-			\begin{subequations}
-				\label{eq:input_kkt_condition}
-				\begin{alignat}{2}
-					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & \text{if} \ p^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
-					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & \text{if} \ p^\star(x_{m_k}) = 0,\label{eq:dropped_states}
-				\end{alignat}
-			\end{subequations}
-			where $I_k(x_{m_k})$ is the weighted sum marginal information
-			\begin{align}
-				I_k(x_{m_k})
-				 & \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) I(x_{m_\mathcal{K}}).
-				\label{eq:weighted_sum_marginal_information}
-			\end{align}
-			\label{pr:input_kkt_condition}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix \ref{ap:input_kkt_condition}.
-			\label{pf:input_kkt_condition}
-		\end{proof}
-
-		For each RIScatter node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
-		\begin{proposition}
-			For any strictly positive initializer $\{\boldsymbol{p}_k^{(0)}\}_{k \in \mathcal{K}}$, the \gls{kkt} input probability of node $k$ at state $m_k$ is given by the converging point of the sequence
-			\begin{equation}
-				p^{(r+1)}(x_{m_k}) = \frac{p^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} p^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
-				\label{eq:input_kkt_solution}
-			\end{equation}
-			where $r$ is the iteration index.
-			\label{pr:input_kkt_solution}
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix \ref{ap:input_kkt_solution}.
-			\label{pf:input_kkt_solution}
-		\end{proof}
-
-		At iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
-		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.
-
-		% \setalgorithmcaptionfont{\small}
-		\begin{algorithm}[!t]
-			% \small
-			\caption{Input Distribution Evaluation by a Sequence}
-			\label{al:input_distribution}
-			\begin{algorithmic}[1]
-				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
-				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
-				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
-				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
-				\State \phantom{Set} $f(z|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
-				\State \phantom{Set} $q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
-				\State Initialize $r \gets 0$
-				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
-				\State Get $p^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
-				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
-				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:weighted_sum_marginal_information}
-				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
-				\Repeat
-					\State Update $r \gets r+1$
-					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
-					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
-				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
-			\end{algorithmic}
-		\end{algorithm}
-
-		\begin{remark}
-			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
-			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
-			\label{re:input_kkt_distribution}
-		\end{remark}
-	\end{subsection}
-
-	\begin{subsection}{Active Beamforming}
-		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{t}$, problem \eqref{op:weighted_sum_rate} reduces to
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:active_beamforming}}{\label{ob:active_beamforming}}
-			\addConstraint{\eqref{co:transmit_power},}
-		\end{maxi!}
-		which is still non-convex due to the integration and entropy terms.
-		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
-		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we have
-		\begin{align}
-			q(x_l|x_{m_{\mathcal{K}}})
-			 & = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} \\
-			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
-			\label{eq:dmmac_gamma}
-		\end{align}
-		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
-		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
-		\begin{align}
-			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
-			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} \nonumber \\
-			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
-			\label{eq:regularized_incomplete_gamma}
-		\end{align}
-		whose gradient with respect to $\boldsymbol{w}^*$ is
-		\begin{align}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
-			 & = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \nonumber \\
-			 & \quad \times \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
-			\label{eq:regularized_incomplete_gamma_gradient}
-		\end{align}
-		where
-		\begin{equation}
-			g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
-			\label{eq:regularized_incomplete_gamma_gradient_component}
-		\end{equation}
-		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we rewrite $I(x_{\mathcal{K}})$ and $\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})$ as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
-		\begin{figure*}[!b]
-			\hrule
-			\begin{equation}
-				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} p(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
-				\label{eq:weighted_sum_mutual_information_explicit}
-			\end{equation}
-			\begin{align}
-				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-				 & = \sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
-				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
-				\label{eq:weighted_sum_mutual_information_gradient}
-			\end{align}
-		\end{figure*}
-		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
-		At iteration $r+1$, the unregulated active beamformer is updated by
-		\begin{equation}
-			\bar{\boldsymbol{w}}^{(r+1)} = \boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}}),
-			\label{eq:beamforming_gradient_ascent}
-		\end{equation}
-		where $\gamma$ is the step size (refinable by backtracking line search \cite[Section 9.2]{Boyd2004}).
-		Then, $\bar{\boldsymbol{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
-		\begin{equation}
-			\boldsymbol{w} = \frac{\sqrt{P} \bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
-			\label{eq:beamforming_projection}
-		\end{equation}
-
-		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
-		% \setalgorithmcaptionfont{\small}
-		\begin{algorithm}[!t]
-			% \small
-			\caption{Active Beamforming Optimization by \gls{pga}}
-			\label{al:active_beamforming}
-			\begin{algorithmic}[1]
-				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
-				\Ensure $\boldsymbol{w}^\star$
-				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
-				\State \phantom{Set} $p(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
-				\State Initialize $r \gets 0$
-				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
-				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
-				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
-				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
-				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
-				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
-				\Repeat
-					\State Update $r \gets r+1$
-					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
-					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)}$ by \eqref{eq:beamforming_gradient_ascent} \label{st:backtracking_line_search_begin}
-					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
-					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
-					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
-						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
-						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
-					\EndWhile
-					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
-				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
-			\end{algorithmic}
-		\end{algorithm}
-	\end{subsection}
-
-	\begin{subsection}{Decision Threshold}
-		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
-			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
-		\end{maxi!}
-		which is still non-convex since $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
-		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
-		As shown in Fig.~\ref{fg:discrete_outputs}, the decision regions are formulated by grouping adjacent energy bins.
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.9\columnwidth}{!}{
-				\input{assets/chapter_2/discrete_outputs.tex}
-			}
-			\caption{The thresholds are chosen from fine-grained candidates instead of the continuous space. Each decision region consists of at least one bin.}
-			\label{fg:discrete_outputs}
-		\end{figure}
-
-		\begin{remark}
-			The design of the energy detector does not affect the primary achievable rate, since the composite channel \eqref{eq:equivalent_channel} can always be determined after backscatter decoding and re-encoding.
-			This implies that any thresholding maximizing the total backscatter rate is optimal for problem \eqref{op:decision_threshold}.
-			\label{re:backscatter_decision}
-		\end{remark}
-
-		\begin{remark}
-			In terms of total backscatter rate, the nodes can be viewed as an augmented source, and problem \eqref{op:decision_threshold} becomes the rate-optimal quantizer design for \gls{dmtc}.
-			\label{re:augmented_source}
-		\end{remark}
-
-		Thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
-		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
-			\addConstraint{\eqref{co:sequential_threshold},}
-		\end{maxi!}
-		whose global optimal solution has been obtained in recent works.
-		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$.
-		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
-		In Section \ref{sc:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
-		\begin{equation}
-			t_{l}^{\text{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
-			\label{eq:detection_threshold_ml}
-		\end{equation}
-		which is suboptimal for problem \eqref{op:decision_threshold} unless all nodes are with equiprobable inputs.
-	\end{subsection}
-\end{section}
-
-\begin{section}{Simulation Results}
-	\label{sc:simulation_results}
-	In this section, we provide numerical results to evaluate the proposed algorithms.
-	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
-	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
-	For all channels involved, we consider a distance-dependent path loss model
-	\begin{equation}
-		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
-	\end{equation}
-	together with a Rician fading model
-	\begin{equation}
-		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
-	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
-	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
-	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
-	We set $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate regions are averaged over \num{e3} channel realizations.\footnote{The code is publicly available at \url{https://github.com/snowztail/riscatter/}.}
-
-	\begin{subsection}{Evaluation of Proposed Algorithms}
-		\begin{subsubsection}{Initialization}
-			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
-			For $\rho=0$ where the backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards the sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
-			At the following points, both algorithms are initialized by the solutions at the previous point.
 		\end{subsubsection}
 
-		\begin{subsubsection}{Convergence}
-			\label{sc:convergence}
-			\begin{figure}[!t]
-				\centering
-				\resizebox{0.75\columnwidth}{!}{
-					\input{assets/chapter_2/wsr_convergence.tex}
-				}
-				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
-				\label{fg:wsr_convergence}
-			\end{figure}
-			The \gls{bcd} algorithm is convergent for problem \eqref{op:weighted_sum_rate} since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
-			In company with \gls{bcd}, we also plotted the convergence results of \gls{kkt} and \gls{pga} algorithms in Fig.~\ref{fg:wsr_convergence} to show how much performance is gained by solving each subproblem.
-			It is observed that Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} take around \num{100} and \num{10} iterations to converge, respectively.
-			Overall, the \gls{bcd} algorithm requires at most \num{5} iterations to converge.
-			As $\rho$ increases (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
+		\begin{subsubsection}{Physical Architecture}
+
 		\end{subsubsection}
@@
 
-	\begin{subsection}{Comparison of Scattering Applications}
-		On top of the setup in Fig.~\ref{fg:riscatter_network}, we consider RIScatter and the following benchmark applications:
-		\begin{itemize}
-			\item \emph{Legacy:} Legacy transmission without scatter nodes.
-			\item \emph{\gls{bbc}:} The primary signal is \gls{cw} and the receive signal is
-			\begin{equation}
-				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n].
-			\end{equation}
-			The total backscatter rate approaches $K \log M$ when $N$ is sufficiently large.
-			\item \emph{\gls{ambc}:} The user decodes each link independently and semi-coherently while treating the other as interference.
-			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
-			\begin{equation}
-				I_{\text{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\text{D}}^\mathsf{H}\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
-			\end{equation}
-			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
-			\item \emph{\gls{sr}:} For a sufficiently large $N$, the average primary rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
-			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\text{D}}^\mathsf{H} \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
-			\begin{equation}
-				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n].
-				\label{eq:intermediate_signal}
-			\end{equation}
-			The total backscatter rate approaches $K \log M$.
-			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
-			The primary achievable rate is a special case of \eqref{eq:primary_mutual_information}
-			\begin{equation}
-				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
-			\end{equation}
-			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{m_{\mathcal{K}}})$.
-		\end{itemize}
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/chapter_2/region_comparison.tex}
-			}
-			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
-			\label{fg:region_comparison}
-		\end{figure}
+	\begin{subsection}{Wave Scattering Model}
+		\begin{subsubsection}{Radiation Pattern}
 
-		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
-		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
-		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
-		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
-		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
-		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
-		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
-		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
-		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
-		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
-		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
-		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Circuit Topology}
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{Active and Passive Elements}
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{}
+
+		\end{subsubsection}
 	\end{subsection}
 
-	\begin{subsection}{Input Distribution under Different \glsfmtshort{qos}}
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/chapter_2/distribution_weights.tex}
-			}
-			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
-			\label{fg:distribution_weights}
-		\end{figure}
-		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
-		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
-		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
-		This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at low \gls{snr} \cite{Shannon1948}.
-		When the scattered signal is relatively weak, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
-		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy diversity and end up unused.
-		At $\rho=1$ where the primary link is prioritized, the optimal input distribution is $[0, 0, 1, 0]^\mathsf{T}$ since state 3 provides higher primary \gls{snr} than other states.
-		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a static discrete \gls{ris} element.
-		Increasing $\rho$ from \num{0} to \num{1} creates a smooth transition from backscatter modulation to passive beamforming, suggesting RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
-	\end{subsection}
+	\begin{subsection}{Comparison with Reflectarrays and Relays}
+		\begin{subsubsection}{Functionality}
 
-	\begin{subsection}{Rate Region by Different Schemes}
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
-				\resizebox{0.6\columnwidth}{!}{
-					\input{assets/chapter_2/region_distribution.tex}
-				}
-			}
-			\\
-			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_beamforming.tex}
-				}
-			}
-			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_threshold.tex}
-				}
-			}
-			\caption{
-				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.
-			}
-		\end{figure}
-		\begin{subsubsection}{Input Distribution}
-			We compare these input distribution designs for problem \eqref{op:input_distribution}:
-			\begin{itemize}
-				\item \emph{Cooperation:} Joint encoding using a joint probability array $p(x_{m_{\mathcal{K}}})$ with $M^K$ entries by Algorithm \ref{al:input_distribution};
-				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
-				\item \emph{\gls{kkt}:} Solution by Algorithm \ref{al:input_distribution};
-				\item \emph{Equiprobable:} Uniform input distribution.
-			\end{itemize}
-			We also consider these independent distribution recovery methods from the joint probability array:
-			\begin{itemize}
-				\item \emph{Marginalization:} Marginal probability distributions;
-				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposed tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
-				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
-			\end{itemize}
-
-			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
-			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
-			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
-			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
-			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
-			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
-			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
 		\end{subsubsection}
 
-		\begin{subsubsection}{Active Beamforming}
-			We consider three typical active beamforming schemes for problem \eqref{op:active_beamforming}:
-			\begin{itemize}
-				\item \emph{\gls{pga}:} Solution by Algorithm \ref{al:active_beamforming};
-				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
-				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
-			\end{itemize}
+		\begin{subsubsection}{Reconfigurability}
 
-			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
-			In the low-$\rho$ regime, the proposed \gls{pga} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
-			This is because the semi-coherent backscatter decoding relies on the relative energy difference under different backscatter symbol tuples.
-			Such an energy diversity is enhanced by \gls{pga} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizes the channel strength.
-			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches E-\gls{mrt}.
-			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the strongest composite channel.
-			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
-			Those observations confirm that the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to enlarge the achievable rate region.
 		\end{subsubsection}
 
-		\begin{subsubsection}{Decision Threshold}
-			We evaluate the following decision threshold strategies for problem \eqref{op:decision_threshold_discrete}:
-			\begin{itemize}
-				\item \emph{\gls{dp}:} Benchmark \gls{dp} method for sequential quantizer \cite{He2021};
-				\item \emph{\gls{smawk}:} \emph{\gls{dp}} accelerated by the \gls{smawk} algorithm \cite{He2021};
-				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
-				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_ml} \cite{Qian2019}.
-			\end{itemize}
+		\begin{subsubsection}{Complexity}
 
-			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
-			The distribution-aware schemes \gls{dp}, \gls{smawk} and Bisection ensure higher total backscatter rate than \gls{ml}.
-			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal thresholding depends heavily on the input distribution.
-			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other hypotheses.
-			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
 		\end{subsubsection}
 
-	\end{subsection}
+		\begin{subsubsection}{Power Consumption}
 
-	\begin{subsection}{Rate Region under Different Configurations}
-		\begin{figure}[!t]
-			\centering
-			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_tags.tex}
-				}
-			}
-			\subfloat[Reflection States\label{fg:region_states}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_states.tex}
-				}
-			}
-			\\
-			\subfloat[Transmit Antennas\label{fg:region_txs}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_txs.tex}
-				}
-			}
-			\subfloat[Spreading Factor\label{fg:region_duration}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_duration.tex}
-				}
-			}
-			\\
-			\subfloat[Average Noise Power\label{fg:region_noise}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_noise.tex}
-				}
-			}
-			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_csi.tex}
-				}
-			}
-			\\
-			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_snr_primary.tex}
-				}
-			}
-			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_2/region_snr_backscatter.tex}
-				}
-			}
-			\caption{
-				Average primary-total-backscatter rate regions for different system configurations.
-			}
-			\label{fg:region_config}
-		\end{figure}
-		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
-		\begin{subsubsection}{Number of Nodes}
-			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
-			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
-			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
-			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
-			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
-			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
 		\end{subsubsection}
 
-		\begin{subsubsection}{Number of States}
-			Fig.~\subref*{fg:region_states} shows the relationship between the available reflection states (i.e., \gls{qam} order) $M$ and the achievable rate region when $K=1$.
-			We notice that increasing the reflection states has a marginal effect on the primary rate but significantly improves the backscatter rate.
-			This is because the maximum amplitude normalized-\gls{qam} \eqref{eq:backscatter_modulation} involves more weak reflection points as $M$ increases.
-			It enhances the receive energy diversity but cannot provide enough phase shift resolution with maximum reflection.
+		\begin{subsubsection}{Dimension and Cost}
+
 		\end{subsubsection}
 
-		\begin{subsubsection}{Number of Transmit Antennas}
-			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter tradeoff.
-			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
-		\end{subsubsection}
+		\begin{subsubsection}{Applications}
 
-		\begin{subsubsection}{Spreading factor}
-			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Here, the unit of total backscatter rate is bits per primary block to show backscatter throughput.}
-			Using a very large $N$ (as in the case of \gls{sr}) can severely constrain the backscatter throughput, since the gain in energy certainty (by the law of large numbers) cannot withstand the loss in the gross rate.
-			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
-			On the other hand, when $N$ is too small, the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable and energy detection is error-prone.
-			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
-			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., primary and backscatter \gls{snr}, data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
-		\end{subsubsection}
-
-		\begin{subsubsection}{Average Noise Power}
-			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
-			Note that the noise influences both primary and backscatter \gls{snr}.
-			% It shows the proposed adaptive energy detector is suitable for a wide range of noise levels.
-			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the \gls{snr} of energy detection.
-		\end{subsubsection}
-
-		% \begin{subsubsection}{Coverage Disk Radius}
-		% 	Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
-		% 	We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
-		% 	This is because the double fading effect is less severe for near-far setups.
-		% 	In a multi-user RIScatter network with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
-		% \end{subsubsection}
-
-		\begin{subsubsection}{Imperfect \gls{csi}}
-			Due to the lack of \gls{rf} chains at RIScatter nodes, fast and accurate acquisition of the cascaded \gls{csi} can be challenging, especially when the backscatter \gls{snr} is weak or the number of nodes is large.
-			We consider an imperfect \gls{csi} model, where the cascaded channel of node $k$ is estimated as
-			\begin{equation}
-				\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
-			\end{equation}
-			$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d.
-CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
-			In Fig.~\subref*{fg:region_csi}, it is observed that the channel estimation error mainly affects the backscatter rate.
-			When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
-			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus the estimation of the cascaded channel.
-			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state and the primary rate is almost unchanged.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Primary \gls{snr}}
-			\label{sc:primary_snr}
-			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
-			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
-			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
-			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
-			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Backscatter \gls{snr}}
-			The primary \gls{snr} is fixed to \qty{20}{dB} with $Q=1$ in this study.
-			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.
-			This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
-			In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
 		\end{subsubsection}
@@
 
-\begin{section}{Conclusion}
-	\label{sc:conclusion}
-	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
-	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris}, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
-	We also proposed a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to benefit both subsystems.
-	The achievable primary-total-backscatter rate region was then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
-	Numerical results validated the proposed algorithms and emphasized the importance of adaptive input distribution and cooperative receiver design.
+\begin{section}{\glsfmtfull{wpt}}
+	\begin{subsection}{Building Blocks and Coupling Effect}
+		\begin{subsubsection}{Block Diagram}
 
-	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
-	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Coupling between Modules}
+
+		\end{subsubsection}
+	\end{subsection}
+
+	\begin{subsection}{Non-Linear Harvester Behavior}
+		\begin{subsubsection}{Rectifier Circuit Design}
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{Operation Regions and Signal Models}
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{Impact on Waveform Selection}
+
+		\end{subsubsection}
+	\end{subsection}
 \end{section}
+
+\begin{section}{\glsfmtfull{swipt}}
+	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
+
+	\end{subsection}
+
+	\begin{subsection}{Receiver Architectures}
+
+	\end{subsection}
+\end{section}
+
+\begin{section}{\glsfmtfull{bc}}
+	\begin{subsection}{\glsfmtfull{mbc}}
+
+	\end{subsection}
+
+	\begin{subsection}{\glsfmtfull{bbc}}
+
+	\end{subsection}
+
+	\begin{subsection}{\glsfmtfull{ambc}}
+
+	\end{subsection}
+
+	\begin{subsection}{\glsfmtfull{sr}}
+
+	\end{subsection}
+\end{section}
+
+% \begin{section}{\glsfmtfull{im}}
+
+% \end{section}
+
+\begin{section}{\glsfmtfull{mimo}}
+
+\end{section}

### 2024-03-04 content/chapter_3.tex
:construction: Add section titles

@@
 
-\chapter{Getting started}
+\chapter{\glsfmtshort{ris}-Aided \glsfmtshort{swipt}: Joint Waveform and Beamforming Design}\label{ch:ris_aided_swipt}
 
 \begin{section}{Introduction}
-	% The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
-	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
-	This is empowered by the recent advances in \gls{ris}, a real-time programmable metasurface of numerous non-resonant sub-wavelength scattering elements.
-	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than relays.
-	Using \gls{ris} for {passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
-	On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019b,Dai2020a}.
-	Despite fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
+	\begin{subsection}{\glsfmtlong{swipt}}
+		With the great advance in communication performance, a bottleneck of wireless networks has come to energy supply.
+\gls{swipt} is a promising solution to connect and power mobile devices via \gls{rf} waves.
+It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and \gls{m2m} networks.
+The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on \gls{wpt} and \gls{swipt} \cite{Clerckx2019}.
 
-	The answer indeed depends on the hardware architecture and scattering model.
-	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
-	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which groups adjacent elements using passive components.
-	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
-	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
-	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
-	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
-	Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
+		The concept of \gls{swipt} was first cast in \cite{Varshney2008}, where the authors investigated the \gls{r-e} tradeoff for a flat Gaussian channel and typical discrete channels.
+\cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., \gls{ts} and \gls{ps}.
+Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the \gls{r-e} region for multi-antenna broadcast and interference channels.
+On the other hand, \cite{Trotter2009} pointed out that the \gls{rf}-to-\gls{dc} conversion efficiency of rectifiers depends on the input power and waveform shape.
+It implies that the modeling of the energy harvester, particularly its nonlinearity, has a crucial impact on the waveform preference, resource allocation, and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}.
+Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, and performed joint waveform and beamforming design for \gls{wpt}.
+Simulation and experiments showed the benefit of modeling energy harvester nonlinearity in real system design \cite{Kim2019,Kim2020a} and demonstrated the joint waveform and beamforming strategy as a key technique to expand the operation range \cite{Kim2021}.
+A low-complexity adaptive waveform design by \gls{smf} was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
+Beyond \gls{wpt}, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to \gls{swipt} design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the \gls{r-e} region; (iii) a combination of \gls{ps} and \gls{ts} is generally the best strategy; (iv) the optimal input distribution is not the conventional \gls{cscg}; (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient \gls{swipt} design.
+Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for \gls{swipt} under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier \gls{swipt}, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier \gls{swipt}.
+The answers shed new light to the fundamental limits of \gls{swipt} and practical signaling (e.g., modulation and waveform) strategies.
+It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to harvester nonlinearity, a combination of \gls{cscg} and on-off keying in single-carrier setting and non-zero mean asymmetric inputs in multi-carrier setting lead to significantly larger \gls{r-e} region compared to conventional \gls{cscg}.
+Recently, \cite{Varasteh2020a} used machine learning techniques to design \gls{swipt} signaling under nonlinearity to complement the information-theoretic results of \cite{Varasteh2020}, and new modulation schemes were subsequently invented.
+	\end{subsection}
 
-	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
-	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
-	Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself.
-	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of channel manipulation.
-	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020a,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
-	In contrast, \gls{bd}-\gls{ris} can provide a higher channel power but existing results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
-\cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
-	While these studies offer promising glimpses into the channel shaping potential, a comprehensive understanding of the capabilities and limitations is desired, and a universal design framework is missing.
-	This paper aims to answer the channel shaping question through theoretical analysis and numerical optimization.
-	The contributions are summarized below.
+	\begin{subsection}{\glsfmtlong{ris}}
+		\gls{ris} has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency.
+In practice, a \gls{ris} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
+Different from the relay, backscatter and frequency-selective surface \cite{Anwar2018}, the \gls{ris} assists the primary transmission using passive components with negligible thermal noise but is limited to frequency-dependent reflection.
 
-	First, we quantify the capability of a \gls{bd}-\gls{ris} to reshape the \gls{mimo} point-to-point channel in terms of singular values.
-	The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
-	% This generalizes most singular value metrics and provides a powerful design framework.
-	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-	We then discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
-	This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
+		Inspired by the development of real-time reconfigurable metamaterials \cite{Cui2014}, the authors of \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the electromagnetic wave at a specific frequency to mitigate signal attenuation.
+\cite{Wu2018} proposed a \gls{ris}-assisted \gls{miso} system and jointly optimized the precoder at the \gls{ap} and the phase shifts at the \gls{ris} to minimize the transmit power.
+The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
+In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
+To estimate the cascaded \gls{ap}-\gls{ris}-\gls{ue} link without \gls{rf}-chains at the \gls{ris}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
+The hardware architecture, design challenges, and application opportunities of practical \gls{ris} were covered in \cite{Wu2020}.
+In \cite{Dai2020}, a prototype \gls{ris} with \num{256} \num{2}-bit elements based on \gls{pin} diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
+	\end{subsection}
 
-	Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
-	It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
-	This is the first paper to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
+	\begin{subsection}{\glsfmtshort{ris}-Aided \glsfmtshort{swipt}}
+		By integrating \gls{ris} with \gls{swipt}, the constructive reflection can boost the end-to-end power efficiency and improve the \gls{r-e} tradeoff.
+In multi-user cases, dedicated energy beams were proved unnecessary for the weighted sum-power maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
+It was also claimed that \gls{los} links could boost the power efficiency since rank-deficient channels require fewer energy beams \cite{Wu2020a}.
+However, \cite{Wu2020b,Tang2019,Wu2020a} were based on a linear energy harvester model that is known in both the \gls{rf} and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}.
+Based on practical \gls{ris} and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based \gls{ris}-assisted \gls{swipt} system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
+The proposed framework provides a flexible tradeoff between performance and complexity.
+To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
+In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output \gls{dc} power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for \gls{swipt} with the passive beamforming capability of \gls{ris}, to investigate the \gls{r-e} tradeoff for one \gls{swipt} user with co-located information decoder and energy harvester.
+We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the \gls{r-e} region of \gls{ris}-aided \gls{swipt}?} The contributions of this paper are summarized as follows.
 
-	Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
-	The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
-	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
-	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
-	It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.
+		\emph{First,} we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
+Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output \gls{dc} power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce \gls{dc}), waveform coupling (i.e., different waveforms jointly contribute to \gls{dc}), and high-order objective function.
+To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under the \gls{ts} and \gls{ps} receiving modes.
+The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable \gls{r-e} region.
+This is the first paper to propose a joint waveform, active and passive beamforming architecture for \gls{ris}-aided \gls{swipt}.
 
-	% Third, we propose a closed-form iterative algorithm for power centric channel shaping problems.
-	% The idea is to successively approximate the quadratic objective by a sequence of affines and solve the local problems by \gls{svd}.
-	% Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.
+		\emph{Second,} we characterize each \gls{r-e} boundary point by energy maximization under a rate constraint.
+The problem is solved by a \gls{bcd} algorithm based on the \gls{csit}.
+For active beamforming, we prove that the global optimal active information and power precoders coincide at \gls{mrt} even with rectifier nonlinearity.
+For passive beamforming, we propose a \gls{sca} algorithm and retrieve the \gls{ris} phase shift by eigen decomposition with optimality proof.
+Finally, the superposed waveform and the splitting ratio are optimized by the \gls{gp} technique.
+The \gls{ris} phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
+This is the first paper to jointly optimize waveform and active/passive beamforming in \gls{ris}-aided \gls{swipt}.
 
-	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
-	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
-	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
+		\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the \gls{gp} algorithm.
+To facilitate practical \gls{swipt} implementation, the \gls{wf} strategy for modulated waveform and the \gls{smf} strategy for multisine waveform are combined in time and power domains, respectively.
+The passive beamforming design is also adapted to accommodate the low-complexity waveform schemes.
+The proposed low-complexity \gls{bcd} algorithm achieves a good balance between performance and complexity.
 
+		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
+It is concluded that (i) \gls{ris} enables constructive reflection and flexible subchannel design in the frequency domain that is essential for \gls{swipt} systems; (ii) \gls{ris} mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) \gls{ts} is preferred at low \gls{snr} while \gls{ps} is preferred at high \gls{snr}; (v) there exist two optimal \gls{ris} development locations, one close to the \gls{ap} and one close to the \gls{ue}; (vi) the output \gls{snr} scales linearly with the number of transmit antennas and quadratically with the number of \gls{ris} elements; (vii) due to the rectifier nonlinearity, the output \gls{dc} scales quadratically with the number of transmit antennas and quartically with the number of \gls{ris} elements; (viii) for narrowband \gls{swipt}, the optimal active and passive beamforming for any \gls{r-e} point are also optimal for the whole \gls{r-e} region; (ix) for broadband \gls{swipt}, the optimal active and passive beamforming depend on specific \gls{r-e} point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded \gls{csit} and finite \gls{ris} reflection states.
+	\end{subsection}
 \end{section}
 
-\begin{section}{\glsfmtlong{bd}-\glsfmtlong{ris} Model}
-	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
-	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
-	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
-	The overall scattering matrix of the \gls{bd}-\gls{ris} is
+\begin{section}{System Model}\label{se:system_model}
+	\begin{figure}[!t]
+		\centering
+		\def\svgwidth{0.9\columnwidth}
+		\input{assets/chapter_3/system.eps_tex}
+		\caption{An \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
+		\label{fi:system}
+	\end{figure}
+
+	As shown in Fig.~\ref{fi:system}, we propose a \gls{ris}-aided \gls{swipt} system where an $M$-antenna \gls{ap} delivers information and power simultaneously, through an $L$-element \gls{ris}, to a single-antenna \gls{ue} over $N$ orthogonal evenly-spaced subbands.
+We consider a quasi-static block fading model and assume the \gls{csit} of direct and cascaded channels is known.
+The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
+
+	\begin{subsection}{Transmitted Signal}
+		Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
+The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
 		\begin{equation}
-		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
+			\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
 		\end{equation}
-	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
-	That is, $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{H}$ and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
-	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
-	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
-3]{Shen2020a}, \cite[Fig.
-5]{Li2023c}, and \cite[Fig.
-2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
+		where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$.
+On the other hand, the power signal transmitted over subband $n$ at time $t$ is
+		\begin{equation}
+			\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
+		\end{equation}
+		where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
+		\begin{equation}
+			\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
+		\end{equation}
+		We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+	\end{subsection}
 
-	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (transmitter-receiver), backward (\gls{ris}-receiver), and forward (transmitter-\gls{ris}) channels, respectively.
-	The equivalent channel is a function of the scattering matrix
+	\begin{subsection}{Reflection Pattern and Composite Channel}
+		According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
+The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
+\gls{ris} element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
 		\begin{equation}
-		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
-		\label{eq:channel_equivalent}
+			\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
 		\end{equation}
-	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
-	% That is, $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns (resp. rows) of $\mathbf{H}_\mathrm{B}$ (resp. $\mathbf{H}_\mathrm{F}$).
-	% , corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$.
-	% $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$
-	Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
-	\begin{equation}
-		\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{R}_g^\mathsf{H},
-	\end{equation}
-	where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary factor matrices.
-	Let $\mathbf{H}_{\mathrm{B},g} = \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \mathbf{V}_{\mathrm{B},g}^\mathsf{H}$ and $\mathbf{H}_{\mathrm{F},g} = \mathbf{U}_{\mathrm{F},g} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}$ be the compact \gls{svd} of the backward and forward channels, respectively.
-	The equivalent channel can thus be rewritten as
-	\begin{equation}
-		\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
-		\label{eq:channel_equivalent_svd}
-	\end{equation}
+		where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the \gls{ris}, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
+This paper sticks to the most common \gls{ris} model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical \gls{ris}-aided \gls{swipt}.} and $\theta_l \in [0,2\pi)$ is the phase shift.
+We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the \gls{ris} vector and matrix, respectively.
 
-	\begin{remark}
-		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} creates two critical opportunities:
-		\begin{itemize}
-			\item \textbf{Subspace alignment:} each group can align the singular matrices of the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) channels.
-In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ is
-			\begin{equation}
-				\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr]$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr]$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-			Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R} \times N_\mathrm{T}$ passing through itself.
-			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the direct-indirect and backward-forward alignments.
-			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}.
-but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
-			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}, but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
-			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching. However,
-			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching.
-However, in \gls{mimo} each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-			% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
-			% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
-			% is sufficient for perfect alignment
-			% and is sufficient for perfect subspace alignment.
-			% In \gls{mimo}, perfect subspace alignment is generally impossible due to the lack of direct control over the indirect channels.aa
-			% backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) alignments of the singular matrices.
-			\item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, diagonal \gls{ris} provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
-			The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{R} \times N_\mathrm{T}$.
-			% effect is more pronounced in \gls{mimo} since the number of subchannels associated with each group grows quadratically with the dimensions.
-			% The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
-since the number of subchannels associated with each group grows quadratically with the dimensions.
-			% It suggests that the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
-			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the maximum indirect channel amplitude by diagonal \gls{ris} is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are independent permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
-			% \begin{equation}
-			% 	\item \
-			% \end{equation}
-			% and $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality,
-			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the optimal indirect channel amplitude is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ by diagonal \gls{ris} and $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},\pi_\mathrm{B}(n)} \rvert \lvert h_{\mathrm{F},\pi_\mathrm{F}(n)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi(\cdot)$ is a permutation of $\{1, \ldots, N_\mathrm{S}\}$.
-			% this is unique to \gls{bd}-\gls{ris} --- each group can rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the optimal indirect channel amplitude is relaxed from $\sum_n \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ to $\sum_n \lvert h_{\mathrm{B},\pi(n)} \rvert \lvert h_{\mathrm{F},\pi(n)} \rvert$ where $\pi(\cdot)$ is a permutation of $\{1, \ldots, L\}$.
-			% from strongest to weakest, which attains the maximum in rearrangement inequality.
-		\end{itemize}
+		\begin{remark}\label{re:reflection_coefficient}
+			The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely.
+Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
+In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each \gls{ris} element is the same at all subbands.
 		\end{remark}
 
-	% TODO: add illustrations for both
+		At subband $n$, we denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the \gls{ap}-\gls{ris} incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the \gls{ris}-\gls{ue} reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
+The auxiliary \gls{ap}-\gls{ris}-\gls{ue} link can be modeled as a concatenation of the incident channel, the \gls{ris} reflection, and the reflected channel.
+Hence, the composite equivalent channel reduces to
+		\begin{equation}\label{eq:h_n}
+			\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n},
+		\end{equation}
+		where we define the cascaded incident-reflected channel at subband $n$ as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
+We also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
 
-	% In \gls{siso}, the equivalent channel can be further simplified as
-	% \begin{equation}
-	% 	h = h_\mathrm{D} + \sum_g \mathbf{h}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{h}_{\mathrm{F},g},
-	% \end{equation}
-	% subspace alignment boils down to phase matching
+		\begin{remark}\label{re:subband_tradeoff}
+			The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
+Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier \gls{swipt}.
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
+That is to say, \gls{ris} essentially enables a flexible subchannel design.
+In the \gls{miso} case, a similar effect also exists in the spatial domain.
+Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
+		\end{remark}
+	\end{subsection}
 
-	% For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-	% This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
-	% Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
-	% This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-	% That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
-	% Now consider a diagonal \gls{ris} in \gls{mimo}.
-	% Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-	% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
-	% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
-	% We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
+	\begin{subsection}{Received Signal}
+		The received superposed signal at the single-antenna \gls{ue} is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
+		\begin{equation}
+			y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
+		\end{equation}
+		where $\tilde{n}_n(t)$ is the noise at \gls{rf} band $n$.
+Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
+	\end{subsection}
 
-	% \begin{equation}
-	% 	\mathbf{H} = \underbrace{\mathbf{H}_\mathrm{D} + \underbrace{\sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}_\text{group-wise}}_\text{direct-indirect},
-	% \end{equation}
-	% which involves three subspace alignment problems:
-	% which involves three subspace alignment problems
-	% \begin{equation}
-	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{backward-forward}\\\text{additive alignment}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
-	% \end{equation}
-	% \begin{equation}
-	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g}_{\substack{\text{backward}\\\text{align}}} \underbrace{\mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{forward}\\\text{align}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
-	% \end{equation}
-	% Then the equivalent channel can be rewritten as
-	% Since the field of (block) unitary matrices formulate a field that is closed under multiplication
-	% Since block unitary matrices satisfy the axioms of a field under matrix multiplication
-	% \begin{remark}
-	% 	% To understand the \gls{b} gain from in-group connections
-	% \end{remark}
+	\begin{subsection}{Receiving Modes}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[\gls{ts} receiver\label{fi:ts_receiver}]{
+				\resizebox{0.9\columnwidth}{!}{
+					\input{assets/chapter_3/ts_receiver.tex}
+				}
+			}
+			\\
+			\subfloat[\gls{ps} receiver\label{fi:ps_receiver}]{
+				\resizebox{0.9\columnwidth}{!}{
+					\input{assets/chapter_3/ps_receiver.tex}
+				}
+			}
+			\caption{Diagrams of practical co-located receivers.}
+			\label{fi:receiver}
+		\end{figure}
 
-	% \begin{remark}
-	% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-	% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-	% 	\begin{equation}
-	% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
-	% 		\label{eq:scattering_fc_tight}
-	% 	\end{equation}
-	% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
-	% 	\begin{itemize}
-	% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-	% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
-	% 	\end{itemize}
-	% \end{remark}
+		As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013}.
+The \gls{ts} receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
+During each session, the transmitter optimizes the waveform for either \gls{wit} or \gls{wpt}, while the receiver activates the information decoder or the energy harvester correspondingly.
+The duration ratio $\eta$ controls the \gls{r-e} tradeoff and is independent from the waveform and beamforming design.
+On the other hand, the \gls{ps} receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
+The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
+During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different \gls{r-e} tradeoffs.
+In the following context, we consider the optimization with the \gls{ps} receiver, as the \gls{ts} receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+	\end{subsection}
 
-	% \begin{remark}
-	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
-	% \end{remark}
-	% \begin{remark}
-	% 	Individual forward and backward \gls{csi} are required for \gls{bd}-\gls{ris} designs.
-	% 	This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
-	% 	% Later we will show the potential benefits from the \gls{csi} overhead.
-	% \end{remark}
+	\begin{subsection}{Information Decoder}
+		A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
+Therefore, the achievable rate is\footnote{It requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
+		\begin{equation}\label{eq:R}
+			R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
+		\end{equation}
+		where $\sigma_n^2$ is the noise variance at the \gls{rf}-band and during the \gls{rf}-to-baseband conversion on tone $n$.
+	\end{subsection}
+
+	\begin{subsection}{Energy Harvester}\label{se:energy_harvester}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
+				\resizebox{0.45\columnwidth}{!}{
+					% \includegraphics{assets/antenna_equivalent_circuit.eps}
+					\input{assets/chapter_3/antenna_equivalent_circuit.tex}
+				}
+			}
+			\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
+				\resizebox{0.45\columnwidth}{!}{
+					% \includegraphics{assets/a_single_diode_rectifier.eps}
+					\input{assets/chapter_3/a_single_diode_rectifier.tex}
+				}
+			}
+			\caption{Equivalent circuits of receive antenna and energy harvester.}
+		\end{figure}
+
+		Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output \gls{dc} on both the power and shape of the received signal.
+Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has a resistance $R_{\mathrm{A}}$ and the incoming signal creates a voltage source $v_{\mathrm{S}}(t)$.
+Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
+When perfectly matched (i.e., $R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
+Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
+As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output \gls{dc} is equivalent to maximizing a monotonic function\footnote{This small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+		\begin{equation}\label{eq:z}
+			z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}},
+		\end{equation}
+		where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
+With a slight abuse of notation, we refer to $z$ as the average output \gls{dc} in this paper.
+It can be observed that the conventional linear harvester model, where the output \gls{dc} power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
+However, due to the coupling effect among different frequencies, some high-order frequency components compensate each other in frequency and further contribute to the output \gls{dc} power.
+In other words, even-order terms with $i \ge 4$ account for the nonlinear diode behavior.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
+Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order \gls{dc} terms.
+Let $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
+Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
+
+		\begin{figure*}[!t]
+			\begin{equation*}
+				\boldsymbol{W}_{\mathrm{I/P}}=
+				\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
+					\matrix [matrix of math nodes,left delimiter=(,right delimiter=)] (m)
+					{
+						\boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},2}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+						\boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},2}^H & \ddots & \vdots \\
+						\vdots & \ddots & \ddots & \boldsymbol{w}_{\mathrm{I/P},N-1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+						\boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},1}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N-1}^H & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+					};
+					\draw[dotted,thick] (m-4-1.north west) rectangle (m-4-1.south east);
+					\draw[dotted,thick,fill=gray,opacity=0.125] (m-2-1.north west) rectangle (m-2-1.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-3-2.north west) rectangle (m-3-2.south east); \draw[dotted,thick,fill=gray,opacity=0.125] (m-4-3.north west) rectangle (m-4-3.south east);
+					\draw[dashed,thick,fill=gray,opacity=0.5] (m-1-1.north west) rectangle (m-1-1.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-2-2.north west) rectangle (m-2-2.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-3-3.north west) rectangle (m-3-3.south east); \draw[dashed,thick,fill=gray,opacity=0.5] (m-4-4.north west) rectangle (m-4-4.south east);
+					\draw[solid,thick,fill=gray,opacity=0.25] (m-1-2.north west) rectangle (m-1-2.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-2-3.north west) rectangle (m-2-3.south east); \draw[solid,thick,fill=gray,opacity=0.25] (m-3-4.north west) rectangle (m-3-4.south east);
+					\draw[solid,thick] (m-1-4.north west) rectangle (m-1-4.south east);
+					\draw[<-] (m-4-3.south|-m.south) -- ++(0.5,-0.15) node[below]{$k=-1$};
+					\draw[<-] (rd.east|-m.south) -- ++(0.5,-0.15) node[right]{$k=0$};
+					\draw[<-] (rd.east|-m-3-4.east) -- ++(0.5,-0.15) node[right]{$k=1$};
+				\end{tikzpicture}
+			\end{equation*}
+			\caption{$\boldsymbol{W}_{\mathrm{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
+$\boldsymbol{W}_{\mathrm{I/P},k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\mathrm{I/P}}$ and nulls all remaining blocks.
+Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively.
+For $\boldsymbol{w}_{\mathrm{I/P},n_1}\boldsymbol{w}_{\mathrm{I/P},n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
+			\label{fi:block_diagonal}
+		\end{figure*}
+
+		\begin{figure*}[!b]
+			\hrule
+			\begin{align}
+				&z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
+				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
+				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
+				&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
+				&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
+			\end{align}
+		\end{figure*}
+	\end{subsection}
+
+	\begin{subsection}{Rate-Energy Region}
+		The achievable \gls{r-e} region is defined as
+		\begin{align}
+			\mathcal{C}_{\mathrm{\gls{r-e}}}
+			&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
+			&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
+		\end{align}
+		where $P$ is the average transmit power budget and 1/2 converts the peak value of the sine waves to the average value.
+	\end{subsection}
 \end{section}
 
-\begin{section}{Channel Singular Values Redistribution}
-	\begin{subsection}{A Toy Example}\label{sc:toy_example}
-		We first illustrate the channel shaping capabilities of different \gls{ris} by a toy example.
-		% We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
-		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
-		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{bd}-\gls{ris} has 4 independent angular parameters
-		\begin{equation}
-			\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
-				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
-				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
-			\end{bmatrix}.
+\begin{section}{Problem Formulation}\label{se:problem_formulation}
+	We characterize each \gls{r-e} boundary point through a current maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
+	\begin{maxi!}
+		{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+		\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
+		\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
+		\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
+		\addConstraint{0 \le \rho \le 1.}
+	\end{maxi!}
+	Problem~\eqref{op:original} is intricate because of the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}.
+To obtain a feasible solution, we propose a \gls{bcd} algorithm that iteratively updates (i) the \gls{ris} phase shift; (ii) the active precoder; (iii) the waveform amplitude and splitting ratio, until convergence.
+
+	\begin{subsection}{Passive Beamforming}
+		In this section, we optimize the \gls{ris} phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
+		\begin{align}
+			\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
+			& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+			& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+			& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi}),
+		\end{align}
+		where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t']^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+On the other hand, we define $t_{\mathrm{I/P},k}$ as
+		\begin{align}
+			t_{\mathrm{I/P},k}
+			& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
+			& = \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
+			& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k},
+		\end{align}
+		where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
+		\begin{align}
+			R(\boldsymbol{\Phi})
+			& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
+			z(\boldsymbol{\Phi})
+			& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
+			& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+		\end{align}
+		To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
+Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
+		\begin{align}
+			(t_{\mathrm{I},0}^{(i)})^2
+			& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
+			t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
+			& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
+			t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
+			& \ge t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}.\label{eq:taylor_3}
+		\end{align}
+		Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real-valued because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
+Due to symmetry \cite{Golub2013}, we have
+		\begin{equation}\label{eq:coupled_terms}
+			\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
 		\end{equation}
-		In particular, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		We also enforce symmetry by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
-		\begin{figure}
-			\centering
-			\includegraphics[width=\columnwidth]{assets/chapter_3/singular_trend.eps}
-			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetry unitary \gls{ris}.}
-			\label{fg:singular_trend}
-		\end{figure}
-		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
-		It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and design parameters.
-		A larger performance gap is expected when asymmetric \gls{bd}-\gls{ris} is available.
-		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
-	\end{subsection}
+		Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the \gls{dc} approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
+		\begin{figure*}[!b]
+			\hrule
+			\begin{align}
+				\tilde{z}(\boldsymbol{\Phi}^{(i)})
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}\right).\label{eq:z_irs_approx}
+			\end{align}
+		\end{figure*}
+		\begin{maxi!}
+			{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
+			\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
+			\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_modulus}
+			\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
+			\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
+		\end{maxi!}
+		We then apply \gls{sdr} to the unit-rank constraint \eqref{co:irs_rank} and formulate a \gls{sdp} with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}.
+In this specific case, we found the solution provided by \texttt{CVX toolbox} \cite{Grant2016} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
+This conclusion is summarized below.
 
-	\begin{subsection}{Pareto Frontier Characterization}
-		We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:pareto_unitary}}
-		\end{maxi!}
-		where $n \in \{1,\ldots,N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
-		Varying $\{\rho_n\}$ unveils the entire achievable singular value region.
-		Thus, the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
-		The objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} for group $g$ corresponds to the Stiefel manifold.
-		Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
+		\begin{proposition}\label{pr:relaxation}
+			Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by \gls{sdr}.
+		\end{proposition}
 
-		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a block-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
-		It leverages the fact that unitary matrices are closed under multiplication.
-		At iteration $r$, the gradient is computed in the Euclidean space and translated to the Riemannian manifold \cite{Absil2009}
-		\begin{gather}
-			\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
-			\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
-		\end{gather}
-		The Polak-Ribierre parameter \cite{Polak1969} is approximated as \cite{Abrudan2009}
-		\begin{equation}
-			\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-			\label{eq:parameter_cg}
-		\end{equation}
-		and the conjugate direction is
-		\begin{equation}
-			\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}. % $\mathcal{O}(N_\mathrm{S}^2)$
-			\label{eq:direction_cg}
-		\end{equation}
-		In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
-		\begin{equation}
-			\mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}. % $\mathcal{O}(N_\mathrm{S}^3)$
-			\label{eq:geodesic}
-		\end{equation}
-		An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.\footnote{To double the step size, one only need to square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.}
-		Finally, the scattering matrix is updated along the geodesic as
-		\begin{equation}
-			\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
-			\label{eq:update_geodesic}
-		\end{equation}
-		Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
-		Convergence to stationary points is guaranteed.
+		\begin{proof}\label{pf:relaxation}
+			Please refer to Appendix~\ref{ap:relaxation}.
+		\end{proof}
 
-		\begin{remark}
-			Compared with universal manifold optimization \cite{Absil2009,Pan2022d}, Algorithm~\ref{ag:rcg} inherits a trifold benefit from \cite{Abrudan2008,Abrudan2009}:
-			\begin{enumerate}
-				\item No retraction thanks to rotational update \eqref{eq:geodesic}, \eqref{eq:update_geodesic};
-				\item Lower computational complexity per iteration;
-				\item Faster convergence thanks to proper parameter space.
-			\end{enumerate}
-		\end{remark}
+		In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	\gls{ris} vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
+The passive beamforming design is summarized in the \gls{sca} Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
+Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{\gls{sca}}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{\gls{sca}}}$ denotes the number of \gls{sca} iterations \cite{Luo2010b}.
 
-		% \setalgorithmcaptionfont{\small}
 		\begin{algorithm}[!t]
-			% \small
-			\caption{Block-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
-			\label{ag:rcg}
+			\caption{\gls{sca}: \gls{ris} Phase Shift.}
+			\label{al:sca}
 			\begin{algorithmic}[1]
-				\Require $f(\mathbf{\Theta})$, $G$
-				\Ensure $\mathbf{\Theta}^\star$
-				\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+				\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
+				\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
 				\Repeat
-					\For {$g \gets 1$ to $G$}
-						\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean} \label{ln:gradient_euclidean}
-						\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riemannian}
-						\State $\gamma_g^{(r)} \gets$ \eqref{eq:parameter_cg}
-						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
-						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
-							\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
-						\EndIf
-						\State $\mu \gets 1$
-						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic}
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
-							\State $\mu \gets 2 \mu$
-						\EndWhile
-						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
-							\State $\mu \gets \mu / 2$
-						\EndWhile
-						\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:update_geodesic}
-					\EndFor
-					\State $r \gets r+1$
-				\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
+					\State $i \gets i + 1$
+					\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
+					\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
+					\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+				\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+				\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
+				\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
+				\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
 			\end{algorithmic}
@@
 
-		\begin{lemma}\label{lm:pareto_gradient}
-			The Euclidean gradient of \eqref{ob:pareto} w.r.t. \gls{bd}-\gls{ris} group $g$ is
-			\begin{equation}
-				\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathrm{diag}(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
-				\label{eq:pareto_gradient}
-			\end{equation}
-			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}$, respectively.
-		\end{lemma}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:pareto_gradient}.
+		\begin{proposition}\label{pr:sca}
+			For any feasible initial point with given waveform and splitting ratio, the \gls{sca} Algorithm~\ref{al:sca} is guaranteed to converge to local optimal points of the original problem~\eqref{op:original}.
+		\end{proposition}
+
+		\begin{proof}\label{pf:sca}
+			Please refer to Appendix~\ref{ap:sca}.
 		\end{proof}
-
-		%  The Euclidean gradient of \gls{bd}-\gls{ris} group $g$ is computed as
-		% where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
-		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto} where line \ref{ln:gradient_euclidean} uses \eqref{eq:pareto_gradient} explicitly.
-		% \eqref{eq:pareto_gradient} is used in line \ref{ln:gradient_euclidean}.
 	\end{subsection}
 
-	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
-		We then discuss some analytical bounds related to channel singular values.
-		\begin{proposition}[degree of freedom]\label{pp:dof}
-			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:dof}.
-		\end{proof}
+	\begin{subsection}{Active Beamforming}
+		The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
+Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduce the size of variables from $2MN$ to $2(M+N)$.
+The weight on subband $n$ is essentially
+		\begin{equation}\label{eq:w}
+			\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n},
+		\end{equation}
+		where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
+Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$.
+The \gls{mrt} precoder at subband $n$ is given by
+		\begin{equation}\label{eq:b_n}
+			\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
+		\end{equation}
 
-		\begin{proposition}[rank-deficient channel]\label{pp:rank_deficient}
-			% If the forward/backward channel is rank-$k$, then a \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n > k$) channel singular value to the $n-k$-th singular value of $\mathbf{T}$, or suppress the $n$-th ($n < N - k + 1$) channel singular value to the $n$-th singular value of $\mathbf{T}$.
-			% If the forward/backward channel is rank-$k$, then a sufficiently large \gls{bd}-\gls{ris} can at most enlarge (resp.
-suppress) the first (resp.
-last) $k$ equivalent channel singular values without bounds.
-			If the forward or backward channel is rank-$k$, then regardless of the \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
-			\begin{align}
-				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_bound_enlarge}          \\
-				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
-			\end{align}
-			where
-			% \begin{align}
-			% 	\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
-			% 	\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k.
-			% \end{align}
-			\begin{equation}
-				\mathbf{T} \mathbf{T}^\mathsf{H} =
-				\begin{cases}
-					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
-					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
-				\end{cases}
-				\label{eq:auxiliary_matrix}
-			\end{equation}
-			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
-			% where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the forward channel is rank-$k$ and $\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the backward channel is rank-$k$.
-		\end{proposition}
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:rank_deficient}.
-		\end{proof}
-
-		% \begin{corollary}[degree of freedom]
-		% 	In point-to-point \gls{mimo} with or without direct link, \gls{bd}-\gls{ris} cannot provide a higher \gls{dof} than diagonal \gls{ris}.
-		% \end{corollary}
-
-		\begin{corollary}[extreme singular values\label{co:extreme}]
-			With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded above while the last $k$ channel singular values can be suppressed to zero.
-			% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
-			% If the forward or backward channel is rank-$k$ and the \gls{ris} is sufficiently large, then the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
-			% If the forward/backward channel is rank-$k$, then the first (resp. last) $k$ singular values of the equivalent channel are unbounded above (resp. below).
-			% a sufficiently large \gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ singular values of the equivalent channel without bounds.
-		\end{corollary}
-
-		\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} in \cite{Semmler2023}.}\label{co:los}]
-			If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
-suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
-$n$-th) singular value of $\mathbf{T}$, that is,
-			\begin{equation}
-				\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
-				\label{iq:sv_bound_los}
-			\end{equation}
-		\end{corollary}
-
-		In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.
-
-		\begin{proposition}[fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
-			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the channel singular values can be manipulated up to
-			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
-			% only bounds that apply here are those that apply to the singular values of
-			\begin{equation}
-				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
-			\end{equation}
-			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-			% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
+		\begin{proposition}\label{pr:mrt}
+			For single-user \gls{swipt}, the global optimal information and power precoders coincide at the \gls{mrt}.
 		\end{proposition}
 
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:fully_connected}.
+		\begin{proof}\label{pf:mrt}
+			Please refer to Appendix~\ref{ap:mrt}.
 		\end{proof}
-
-		The problem now becomes how the singular values of matrix product are bounded by the singular values of its individual factors.
-		Let $N' = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le N'$.
-		We have the following corollaries.
-
-		\begin{corollary}[generic singular value bounds \cite{Fulton2000}]
-			\begin{equation}
-				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
-				\label{iq:sv_bound_fc}
-			\end{equation}
-			for all admissible triples $(I, J, K) \in T_r^{N'}$ with $r < N'$, where
-			\begin{equation*}
-				\begin{gathered}
-					% T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
-					% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-					T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \forall p < r, (F, G, H) \in T_p^r,\\
-					\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-				\end{gathered}
-			\end{equation*}
-			\begin{equation*}
-				U_r^{N'} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
-			\end{equation*}
-		\end{corollary}
-
-		\begin{corollary}[upper bound on the largest singular value]
-			\begin{equation}
-				\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}).
-			\end{equation}
-		\end{corollary}
-
-		% \begin{corollary}[lower bound on the smallest singular value]
-		% 	\begin{equation}
-		% 		\sigma_{N'}(\mathbf{H}) \ge \sigma_{N'}(\mathbf{H}_\mathrm{B}) \sigma_{N'}(\mathbf{H}_\mathrm{F}).
-		% 	\end{equation}
-		% \end{corollary}
-
-		\begin{corollary}[upper bound on the product of first $k$ singular values]
-			\begin{equation}
-				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
-			\end{equation}
-		\end{corollary}
-
-		% \begin{corollary}[lower bound on the product of last $k$ singular values]
-		% 	\begin{equation}
-		% 		\prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
-		% 	\end{equation}
-		% \end{corollary}
-
-		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
-			\begin{equation}
-				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
-				\label{iq:sv_bound_fc_power}
-			\end{equation}
-			When $k = N'$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels.
-		\end{corollary}
-
-		% \begin{remark}
-		% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-		% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-		% 	\begin{equation}
-		% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
-		% 		\label{eq:scattering_fc_tight}
-		% 	\end{equation}
-		% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
-		% 	\begin{itemize}
-		% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-		% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
-		% 	\end{itemize}
-		% \end{remark}
-
-		Tight bounds are inapplicable when a \gls{mimo} direct link is present, as the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
-		Such a balance often involves optimization approaches and another example will be discussed in Section~\ref{sc:low_complexity}.
 	\end{subsection}
 
+	\begin{subsection}{Waveform and Splitting Ratio}
+		Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given \gls{ris} phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
+On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
+Hence, the rate \eqref{eq:R} reduces to
+		\begin{equation}\label{eq:R_waveform}
+			R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right),
+		\end{equation}
+		and the \gls{dc} \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
+		\begin{figure*}[!b]
+			\hrule
+			\begin{align}
+				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
+				& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
+			\end{align}
+		\end{figure*}
+		\begin{maxi!}
+			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
+			\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}.}
+		\end{maxi!}
+		Following \cite{Clerckx2018b}, we introduce auxiliary variables $t'',\bar{\rho}$ and transform problem~\eqref{op:waveform} into a reversed \gls{gp}
+		\begin{mini!}
+			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
+			\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
+			\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
+			\addConstraint{\rho + \bar{\rho} \le 1.}\label{co:waveform_splitting_ratio}
+		\end{mini!}
+		It can be concluded that $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power is wasted at the receiver.
+The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
+		\begin{align}
+			1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
+			z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}.
+		\end{align}
+		We upper bound \eqref{eq:g_I} and \eqref{eq:g_P} by the \gls{gm}-\gls{am} inequality \cite{Chiang2005} and transform problem~\eqref{op:waveform_rgp} to
+		\begin{mini!}
+			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
+			\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
+			\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
+			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
+			\addConstraint{\rho + \bar{\rho} \le 1,}
+		\end{mini!}
+		where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$ and $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
+The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
+		\begin{align}
+			\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
+			\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
+		\end{align}
+		With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as \texttt{CVX toolbox} \cite{Grant2016}.
+We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
+The joint waveform amplitude and splitting ratio design is summarized in the \gls{gp} Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
+
+		\begin{algorithm}[!t]
+			\caption{\gls{gp}: Waveform Amplitude and Splitting Ratio.}
+			\label{al:gp}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
+				\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+				\State Set $g_{m_{\mathrm{I},n}}^{(0)}$, $g_{m_\mathrm{P}}^{(0)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+				\Repeat
+					\State $i \gets i + 1$
+					\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
+					\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
+					\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+				\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
+				\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+
+		\begin{proposition}\label{pr:gp}
+			For any feasible initial point, the \gls{gp} Algorithm~\ref{al:gp} is guaranteed to converge to local optimal points of the waveform amplitude and splitting ratio design problem \eqref{op:waveform}.
+		\end{proposition}
+
+		\begin{proof}\label{pf:gp}
+			Please refer to \cite{Clerckx2016a,Clerckx2018b}.
+		\end{proof}
+	\end{subsection}
+
+	\begin{subsection}{Low-Complexity Adaptive Design}
+		To facilitate practical \gls{swipt} implementation, we propose two closed-form adaptive waveform amplitude schemes by combining \gls{wf} and \gls{smf} in time and power domains, respectively.
+For \gls{wit}, the optimal \gls{wf} strategy assigns the amplitude of modulated tone $n$ by
+		\begin{equation}\label{eq:wf}
+			s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
+		\end{equation}
+		where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
+The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
+On the other hand, \gls{smf} was proposed in \cite{Clerckx2017} as a suboptimal \gls{wpt} resource allocation scheme that assigns the amplitude of sinewave $n$ by
+		\begin{equation}\label{eq:smf}
+			s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
+		\end{equation}
+		where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity.
+When the receiver works in \gls{ts} mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session).
+When the receiver works in \gls{ps} mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
+		\begin{align}
+			s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
+			s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
+		\end{align}
+		where the $\delta$ determines the power ratio of multisine waveform at the transmitter, and $\rho$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the \gls{wit} point and $\delta^{\star}=\rho^{\star}=1$ at the \gls{wpt} point when $N$ is relatively large.
+Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient \gls{swipt} design.}
+
+		Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
+Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
+To achieve the \gls{wit} point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no \gls{sca} is involved.
+The Modified-\gls{sca} (M-\gls{sca}) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in \gls{ps} mode.
+Similarly, no loss is introduced by \gls{sdr} and local optimality is guaranteed.
+The proofs are omitted here.
+Since each \gls{sdp} involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-\gls{sca}}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-\gls{sca}}}$ denotes the number of M-\gls{sca} iterations \cite{Luo2010b}.
+Note that no \gls{sca} is involved at the \gls{wit} point where $I_{\mathrm{M-\gls{sca}}}=1$.
+
+		\begin{algorithm}[!t]
+			\caption{M-\gls{sca}: \gls{ris} Phase Shift.}
+			\label{al:m_sca}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
+				\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+				\If{$\rho=0$}
+					\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+				\Else
+					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
+					\State Compute $z^{(0)}$ by \eqref{eq:z_irs}
+					\Repeat
+						\State $i \gets i + 1$
+							\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+							\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
+							\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
+					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
+					\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
+				\EndIf
+				\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
+				\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+	\end{subsection}
+
+	\begin{subsection}{Block Coordinate Descent}
+		Based on the direct and cascaded \gls{csit}, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+The steps are summarized in the \gls{bcd} Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
+It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
+
+		\begin{algorithm}[!t]
+			\caption{\gls{bcd}: Waveform, Beamforming and Splitting Ratio.}
+			\label{al:bcd}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
+				\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+				\State Compute $z^{(0)}$ by \eqref{eq:z_waveform}
+				\Repeat
+					\State $i \gets i + 1$
+					\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$, $\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
+					\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+					\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by Algorithm~\ref{al:gp}
+					\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+					\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
+				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
+				\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+
+		For the low-complexity design under \gls{ps} mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+To achieve the \gls{wit} point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the \gls{bcd} algorithm obtains the \gls{r-e} region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable \gls{r-e} region of the \gls{lc}-\gls{bcd} algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
+The steps are summarized in Algorithm~\ref{al:lc_bcd}.
+The computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{\gls{lc}-\gls{bcd}}}I_{\mathrm{M-\gls{sca}}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{\gls{lc}-\gls{bcd}}}$ denotes the number of \gls{lc}-\gls{bcd} iterations \cite{Luo2010b}.
+
+		\begin{algorithm}[!t]
+			\caption{\gls{lc}-\gls{bcd}: Waveform and Beamforming.}
+			\label{al:lc_bcd}
+			\begin{algorithmic}[1]
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
+				\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+				\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+				\Repeat
+					\State $i \gets i + 1$
+					\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
+					\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+					\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
+					\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+					\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\If{$\rho=0$}
+						\State $\Delta \gets R^{(i)} - R^{(i-1)}$
+					\Else
+						\State $\Delta \gets z^{(i)} - z^{(i-1)}$
+					\EndIf
+				\Until $\lvert \Delta \rvert \le \epsilon$
+				\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
+				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
+			\end{algorithmic}
+		\end{algorithm}
+	\end{subsection}
 \end{section}
 
-\begin{section}{Achievable Rate Maximization}\label{sc:rate}
-	The \gls{mimo} achievable rate maximization problem is formulated w.r.t. joint active and passive beamforming
-	\begin{maxi!}
-		{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
-		\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
-		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-	\end{maxi!}
-	where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the noise power, and $P$ is the transmit power budget.
-	Two methods are proposed below to solve problem \eqref{op:rate}.
-
-	\begin{subsection}{Alternating Optimization}
-		Consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
-		For a given $\mathbf{W}$, the passive beamforming subproblem is
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
-		\end{maxi!}
-		where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
-		\begin{lemma}\label{lm:rate_gradient}
-			The Euclidean gradient of \eqref{ob:rate_passive} w.r.t. \gls{bd}-\gls{ris} block $g$ is
-			\begin{equation}
-				\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
-				\label{eq:rate_gradient}
-			\end{equation}
-		\end{lemma}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:rate_gradient}.
-		\end{proof}
-		Algorithm \ref{ag:rcg} is then invoked to solve problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
-		Since \eqref{ob:rate_passive} is a concave function of $\mathbf{\Theta}$, convergence to local-optimal points is guaranteed.
-		On the other hand, the global optimal transmit precoder for a fixed $\mathbf{\Theta}$ is given by the eigenmode transmission \cite{Clerckx2013}
-		\begin{equation}
-			\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
-			\label{eq:precoder_eigenmode}
-		\end{equation}
-		where $\mathbf{V}$ is the right channel singular matrix and $\mathbf{S}^\star$ is the optimal water-filling power allocation matrix.
-		The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-	\end{subsection}
-
-	\begin{subsection}{Low-Complexity Solution}\label{sc:low_complexity}
-		We then propose a low-complexity solution to problem \eqref{op:rate} based on channel shaping.
-		The passive beamforming subproblem \eqref{op:rate_passive} involves transmit covariance matrix $\mathbf{Q}$ and thus requires iterative \gls{rcg} update.
-		Instead, we decouple the joint \gls{ris}-transceiver design by recasting \eqref{op:rate_passive} as channel power maximization
-		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
-		\end{maxi!}
-		% which only accounts for channel characteristics but has no trivial solution.
-		\begin{remark}
-			As mentioned in Section \ref{sc:bounds}, the key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
-			Problem \eqref{op:power_passive} is very similar (in terms of maximizing the inner product of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$) to the weighted orthogonal Procrustes problem \cite{Gower2004}
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
-			\end{mini!}
-			which has no trivial solution.
-			One lossy transformation, by moving $\mathbf{\Theta}$ to one side \cite{Bell2003}, formulates standard orthogonal Procrustes problems
-			\begin{mini!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
-				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
-			\end{mini!}
-			which has global optimal solutions
-			\begin{equation}
-				\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}
-				\label{eq:orthogonal_procrustes_solution}
-			\end{equation}
-			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-			This suboptimal solution only applies to fully-connected \gls{bd}-\gls{ris}.
-		\end{remark}
-
-		Inspired by \cite{Nie2017}, we propose a general solution to problem \eqref{op:power_passive} with arbitrary group size.
-		The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form.
-
-		\begin{proposition}\label{pp:power}
-			Starting from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
-			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
-				\label{eq:scattering_power}
-			\end{equation}
-			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
-			\begin{equation}
-				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-				\label{eq:auxiliary_matrix_power}
-			\end{equation}
-		\end{proposition}
-
-		\begin{proof}
-			Please refer to Appendix~\ref{ap:power}.
-		\end{proof}
-		Once the channel shaping problem \eqref{op:power_passive} is solved, the transmit precoder can be obtained by \eqref{eq:precoder_eigenmode}.
-		This two-stage approach decouples both blocks and is computationally efficient.
-	\end{subsection}
-
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{fg:pc_rate_sx}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/chapter_3/pc_rate_sx.tex}
-	% 		}
-	% 	}
-	% 	\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{fg:pc_rate_tx}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/chapter_3/pc_rate_tx.tex}
-	% 		}
-	% 	}
-	% 	\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:pc_rate}
-	% \end{figure}
-
-	% Fig.~\ref{fg:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
-	% To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
-	% This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
-	% If tetrads can be formed in \gls{bd}-\gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
-	% Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
-	% We thus conclude dyadic or tetradic \gls{bd}-\gls{ris} usually strike a good balance between performance and complexity.
-
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\resizebox{0.65\columnwidth}{!}{
-	% 		\input{assets/chapter_3/power_sx.tex}
-	% 	}
-	% 	\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
-$(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:power_sx}
-	% \end{figure}
-
-	% \begin{figure}[!t]
-	% 	\centering
-	% 	\subfloat[Without Direct Link\label{fg:pc_power_bond_nd}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/chapter_3/pc_power_bond_nd.tex}
-	% 		}
-	% 	}
-	% 	\subfloat[With Direct Link\label{fg:pc_power_bond_hd}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/chapter_3/pc_power_bond_hd.tex}
-	% 		}
-	% 	}
-	% 	\caption{Average channel power versus \gls{ris} group size $L$.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:pc_power_bond}
-	% \end{figure}
-	% % Fig.~\ref{fg:power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
-	% % Fig.~\ref{fg:power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
-	% Fig.~\ref{fg:power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
-	% % The behavior is more obvious for a large \gls{ris}.
-	% This behavior is more pronounced for a large \gls{ris}.
-	% For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
-	% % \gls{bd}-\gls{ris} provides a higher channel power than conventional \gls{ris}.
-	% % As $L$ increases from 1 to 2,
-	% It implies that the channel shaping capability of \gls{bd}-\gls{ris} scales with group size $L$.
-
-	% Fig.~\ref{fg:pc_power_bond_hd} and \ref{fg:pc_power_bond_nd} compare the average channel power without and with direct link.
-	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % ``Cascaded'' means the maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % ? ``Cascaded'' means the \emph{power product} of the forward and backward channels.
-	% % ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues of the forward and backward channels.
-	% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
-	% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect subspace.
-	% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
-	% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward subspace alignment for an optimal channel boost.
-	% It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
-	% This again emphasizes the advantage of in-group connection of \gls{bd}-\gls{ris}.
-	% % This is because the direct and indirect channels superpose
-	% % the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
-	% % When the direct link is present, a small $L$ cannot align the direct-indirect subspace.
-
-	% % neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
-	% % We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
-	% % For conventional \gls{ris},
-	% % align the direct-indirect subspace.
-	% % When the direct link is present, a small $L$ can neither align the direct-indirect subspace nor the forward-backward subspace.
-	% % For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
-	% % neither the direct-indirect nor the forward-backward subspace can be effectively aligned with a small $L$.
-
-	% % When the direct link is present, a small $L$ can neither preserve the
-	% % neither align the direct-indirect subspace nor the forward-backward subspace.
-
-	% % When the direct link is absent, a large $L$ can align the forward-backward subspace but cannot preserve the forward-backward power balance.
-
-\end{section}
-
-\begin{section}{Simulation Results}\label{sc:simulation}
-	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
-	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
-	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
-	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
-	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
-	$\kappa \to \infty$ is assumed for all channels unless otherwise specified.
-
-	\begin{table*}[!t]
-		\caption{Average Performance of \gls{bd}-\gls{ris} Designs}
-		\label{tb:complexity_test}
-		\centering
-		\begin{tabular}{ccccccc}
-			\toprule
-			\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                                 \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
-			                                & Objective                              & Iterations                             & Time [s]         & Objective        & Iterations & Time [s]  \\ \midrule
-			Geodesic                        & $\num{4.355e-3}$                       & 11.61                                  & $\num{2.038e-2}$ & $\num{1.164e-2}$ & 25.78      & 3.216     \\
-			Non-geodesic                    & $\num{4.168e-3}$                       & 169.5                                  & $\num{1.420e-1}$ & $\num{8.873e-3}$ & 278.1      & 27.81     \\ \bottomrule
-		\end{tabular}
-	\end{table*}
-
-	\begin{subsection}{Channel Singular Values Redistribution}
-		\begin{subsubsection}{Pareto Frontier}
+\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
 	\begin{figure}[!t]
 		\centering
-				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/singular_pareto_sx32_nd.tex}
-					}
-				}
-				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/singular_pareto_sx32.tex}
-					}
-				}
-				\\
-				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/singular_pareto_sx64.tex}
-					}
-				}
-				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/singular_pareto_sx128.tex}
-					}
-				}
-				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
-				\label{fg:singular_pareto}
+		\def\svgwidth{0.9\columnwidth}
+		% \import{assets/}{layout.eps_tex}
+		\input{assets/chapter_3/layout.eps_tex}
+		\caption{System layout in simulation.}
+		\label{fi:layout}
 	\end{figure}
-			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
-			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
-			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
-			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
-			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
-			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
-			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
-			In Fig.
-\subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
-			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
-			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
-			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
-			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
-		\end{subsubsection}
 
-		\begin{subsubsection}{Analytical Bounds and Numerical Results}
-			\begin{figure}[!t]
-				\centering
-				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/singular_bound_rank1_sx32.tex}
-					}
-				}
-				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/singular_bound_rank1_sx64.tex}
-					}
-				}
-				\\
-				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/singular_bound_rank2_sx128.tex}
-					}
-				}
-				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/singular_bound_rank4_sx256.tex}
-					}
-				}
-				\caption{
-					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
-					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
-					`rank-$k$' refers to the forward channel.
-				}
-				\label{fg:singular_bound}
-			\end{figure}
-			Fig.
-\ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
-			Here we assme a rank-$k$ forward channel without loss of generality.
-			When the \gls{ris} is in the vicinity of the transmitter, Figs.
-\subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
-			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
-			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
-			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
-			% The observations align with Proposition \ref{pp:rank_deficient} that t
-			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
-			Those observations align with Proposition \ref{pp:rank_deficient} and Corollary \ref{co:extreme}.
-			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
-			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
-			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.
+	To evaluate the proposed \gls{ris}-aided \gls{swipt} system, we consider the layout in Fig.~\ref{fi:layout} where the \gls{ris} moves along a line parallel to the \gls{ap}-\gls{ue} path.
+Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the \gls{ap} to the \gls{ris}, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
+$d_{\mathrm{D}}=\qty{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$ are chosen as reference.
+The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
+We consider a large open space Wi-Fi-like environment at center frequency \qty{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
+Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \qty{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
+All fadings are modeled as \gls{nlos} with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
+\gls{cscg} variables.
+Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\qty{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
+We also choose the average \gls{eirp} as $P=\qty{40}{dBm}$, the receive antenna gain as \qty{3}{dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
+To further reduce the complexity, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner \gls{r-e} bound for the \gls{lc}-\gls{bcd} algorithm.
+Each \gls{r-e} point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 
@@
 		\centering
-				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/power_bond_txrx1_nd.tex}
+		\resizebox{0.8\columnwidth}{!}{
+			% \includegraphics{assets/channel_amplitude.eps}
+			\input{assets/chapter_3/channel_amplitude.tex}
 		}
-				}
-				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
-					\resizebox{!}{3.25cm}{
-						\input{assets/chapter_3/power_bond_txrx4_nd.tex}
-					}
-				}
-				\caption{
-					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
-					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward subchannels.
-				}
-				\label{fg:power_bond}
+		\caption{Sorted equivalent subchannel amplitude with and without \gls{ris} versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+		\label{fi:channel_amplitude}
 	\end{figure}
 
-			Fig.
-\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
-			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form or via optimization approach \eqref{eq:scattering_power}.
-			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
-			% We observe that the bound is also tight for fully-connected \gls{bd}-\gls{ris}.
-			% Increasing the group size of \gls{bd}-\gls{ris} significantly improves the channel power especially for a large \gls{mimo}.
-			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a fully-connected one can achieve the bound.
-			% The bound here indicates how much power can potentially be extracted from the forward and backward channels.
-			% We observe that using a larger group size can approach the bound better, and full
-			% We observe that the bound is tight for fully-connected \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
-			For the \gls{siso} case in Fig.
-\subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
-			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
-			Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
-			This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
-			Now consider a diagonal \gls{ris} in \gls{mimo}.
-			Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-			Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
-			It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
-			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
-		\end{subsubsection}
-
-		% The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
-		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
-		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
-		% Clearly, a larger group size provides
-		% and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
-		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rate Maximization}
-		\begin{figure}[!t]
-			\centering
-			\subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)\label{fg:power_sx_txrx16_nd}]{
-				\resizebox{!}{3.25cm}{
-					\input{assets/chapter_3/power_sx_txrx16_nd.tex}
-				}
-			}
-			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
-				\resizebox{!}{3.25cm}{
-					\input{assets/chapter_3/power_sx_txrx16.tex}
-				}
-			}
-			\caption{
-				Average maximum channel power versus \gls{ris} configuration.
-				`OP-left' and `OP-right' refer to the suboptimal solutions to problem \eqref{op:power_passive} by lossy transformation \eqref{op:standard_orthogonal_procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
-			}
-			\label{fg:power_sx}
-		\end{figure}
-
-		We first focus on channel shaping subproblem \eqref{op:power_passive_approx}.
-		Fig. \ref{fg:power_sx} shows the achievable channel power under different \gls{ris} configurations.
-		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} is even larger with direct link.
-		For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power as a 256-element diagonal \gls{ris} in Fig.
-\ref{fg:power_sx_txrx16}, but not in Fig.
-\ref{fg:power_sx_txrx16_nd}.
-		% This again credits to the superior subspace alignment capability of \gls{bd}-\gls{ris}.
-		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the subspace alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
-		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.
+	Fig.~\ref{fi:channel_amplitude} reveals how \gls{ris} influences the sorted equivalent subchannel amplitude for one channel realization.
+Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for \gls{wit} and \gls{wpt} are dissimilar.
+Under the specified configuration, the \gls{wpt}-optimized \gls{ris} aligns the strong subbands to exploit the rectifier nonlinearity.
+On the other hand, the \gls{wit}-optimized \gls{ris} provides a fair gain over all subchannels when $L$ is sufficiently large.
+This is reminiscent of the \gls{wf} scheme at high \gls{snr}, but is realized by channel alignment instead of resource allocation.
+Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding a \gls{ris} (the plots are not attached).
+In other words, \gls{ris} has a subtle impact on the waveform design.
 
@@
 		\centering
-			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
-				\resizebox{!}{3.25cm}{
-					\input{assets/chapter_3/rate_beamforming.tex}
+		\subfloat[\gls{r-e} region\label{fi:re_subband}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_subband.eps}
+				\input{assets/chapter_3/re_subband.tex}
 			}
 		}
-			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
-				\resizebox{!}{3.25cm}{
-					\input{assets/chapter_3/rate_txrx.tex}
+		\subfloat[\gls{wpt} waveform amplitude\label{fi:waveform_subband}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/waveform_subband.eps}
+				\input{assets/chapter_3/waveform_subband.tex}
 			}
 		}
-			\\
-			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
-				\resizebox{!}{3.25cm}{
-					\input{assets/chapter_3/rate_sx.tex}
+		\caption{Average \gls{r-e} region and \gls{wpt} waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+	\end{figure}
+
+	Fig.~\subref*{fi:re_subband} illustrates the average \gls{r-e} region versus the number of subband $N$.
+First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
+This is because less power is allocated to each subband but more balanced \gls{dc} terms are introduced by frequency coupling to boost the harvested energy.
+On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for \gls{wpt}.
+It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
+This observation origins from the rectifier nonlinearity.
+Although both waveforms have equivalent second-order \gls{dc} terms \eqref{eq:y_I2} and \eqref{eq:y_P2}, for the fourth-order terms \eqref{eq:y_I4} and \eqref{eq:y_P4}, the modulated waveform has $N^2$ monomials with a modulation gain of \num{2}, while the multisine has $(2N^3+N)/3$ monomials as the components of different frequencies compensate and produce \gls{dc}.
+Second, the \gls{r-e} region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that \gls{ps} outperforms \gls{ts} for a small $N$ and is outperformed for a large $N$.
+When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the \gls{wpt} point and the saddle \gls{ps} \gls{swipt} point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
+When $N$ is relatively small, only modulated waveform is used at both \gls{wit} and \gls{wpt} points, and one can infer that no multisine waveform is needed for the entire \gls{r-e} region.
+It aligns with the conclusion based on the conventional linear harvester model, namely the \gls{r-e} region is convex, \gls{ps} outperforms \gls{ts}, and dedicated power waveform is unnecessary.
+As $N$ becomes sufficiently large, the multisine waveform further boosts \gls{wpt} and creates some concavity in the high-power region, which accounts for the superiority of \gls{ts} under the nonlinear harvester model.
+Therefore, we conclude that the rectifier nonlinearity enlarges the \gls{r-e} region by favoring a different waveform and receiving mode, both heavily depending on $N$.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[\gls{r-e} region\label{fi:re_noise}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_noise.eps}
+				\input{assets/chapter_3/re_noise.tex}
 			}
 		}
-			\subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
-				\resizebox{!}{3.25cm}{
-					\input{assets/chapter_3/rate_kfactor.tex}
+		\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/splitting_ratio_noise.eps}
+				\input{assets/chapter_3/splitting_ratio_noise.tex}
 			}
 		}
-			\caption{
-				Average achievable rate versus \gls{mimo} and \gls{ris} configurations.
-				The noise power is $\eta = \qty{-75}{dB}$, corresponding to a direct \gls{snr} of \num{-10} to \qty{30}{dB}.
-				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
-				`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
-			}
-			\label{fg:rate}
+		\caption{Average \gls{r-e} region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
 	\end{figure}
 
-		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
-		At a transmit power of \qty{10}{dB}, Fig.
-\subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to 4T4R \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
-		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
-		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
-		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
-		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
-		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
-		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better tradeoff between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
-		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
-		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
-	\end{subsection}
+	The average noise power influences the \gls{r-e} region as shown in Fig.~\subref*{fi:re_noise}.
+First, we note that the \gls{r-e} region is roughly concave/convex at low/high \gls{snr} such that \gls{ts}/\gls{ps} are preferred correspondingly.
+At low \gls{snr}, the power is allocated to the modulated waveform on a few strongest subbands to achieve a high rate.
+As the rate constraint $\bar{R}$ decreases, Algorithm~\ref{al:gp} activates more subbands that further boosts the harvested \gls{dc} power because of frequency coupling and harvester nonlinearity.
+Second, there exists a turning point in the \gls{r-e} region, especially for a low noise level ($\sigma_n^2 \le \qty{-40}{dBm}$).
+The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocate more power to the multisine waveform, since a small amplitude multisine could be inefficient for energy purpose.
+As $\bar{R}$ further decreases, thanks to the advantage of multisine, a superposed waveform with a small $\rho$ can outperform a modulated waveform with a large $\rho$.
+The result proves the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.
+Besides, the \gls{lc}-\gls{bcd} algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[\gls{r-e} region\label{fi:re_distance}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_distance.eps}
+				\input{assets/chapter_3/re_distance.tex}
+			}
+		}
+		\subfloat[Path loss product\label{fi:path_loss}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/path_loss.eps}
+				\input{assets/chapter_3/path_loss.tex}
+			}
+		}
+		\caption{Average \gls{r-e} region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{V}}=\qty{2}{\meter}$.}
+	\end{figure}
+
+	In Fig.~\subref*{fi:re_distance}, we compare the average \gls{r-e} region achieved by different \gls{ap}-\gls{ris} horizontal distance $d_{\mathrm{H}}$.
+Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the \gls{ris} should be placed close to either the \gls{ap} or the \gls{ue} based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
+Moreover, there exist two optimal \gls{ris} coordinates around $d_{\mathrm{H}}=0.6$ and \qty{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the \gls{r-e} tradeoff.
+It suggests that equipping the \gls{ap} with a \gls{ris} can potentially extend the operation range of \gls{swipt} systems.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[\gls{r-e} region\label{fi:re_tx}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_tx.eps}
+				\input{assets/chapter_3/re_tx.tex}
+			}
+		}
+		\subfloat[\gls{wit} \gls{snr} and \gls{wpt} \gls{dc}\label{fi:scaling_tx}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/scaling_tx.eps}
+				\input{assets/chapter_3/scaling_tx.tex}
+			}
+		}
+		\caption{Average \gls{r-e} region, \gls{wit} \gls{snr} and \gls{wpt} \gls{dc} versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{0.2}{\meter}$.}
+	\end{figure}
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[\gls{r-e} region\label{fi:re_reflector}]{
+			\resizebox{0.425\columnwidth}{!}{
+				% \includegraphics{assets/re_reflector.eps}
+				\input{assets/chapter_3/re_reflector.tex}
+			}
+		}
+		\subfloat[\gls{wit} \gls{snr} and \gls{wpt} \gls{dc}\label{fi:scaling_reflector}]{
+			\resizebox{0.475\columnwidth}{!}{
+				% \includegraphics{assets/scaling_reflector.eps}
+				\input{assets/chapter_3/scaling_reflector.tex}
+			}
+		}
+		\caption{Average \gls{r-e} region, \gls{wit} \gls{snr} and \gls{wpt} \gls{dc} versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{0.2}{\meter}$.}
+	\end{figure}
+
+	The impacts of the number of transmit antennas $M$ and the \gls{ris} elements $L$ on the \gls{r-e} behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
+First, it is observed that adding either active or passive elements can improve the equivalent \gls{snr}, which produces a nearly concave \gls{r-e} region and favors the \gls{ps} receiver.
+Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
+To investigate the performance loss, we truncate the \gls{dc} objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no \gls{sca} is required; (ii) in the waveform design problem, the \gls{wpt}-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dBA} gap compared to the nonlinear model-based \gls{smf} and \gls{gp} designs.
+Third, doubling $M$ brings a \qty{3}{\dB} gain at the output \gls{snr} and a \qty{12}{dBA} increase at the harvested \gls{dc}, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
+Fourth, when the \gls{ris} is very close to the \gls{ap} or \gls{ue}, doubling $L$ can bring a \qty{6}{\dB} gain at the output \gls{snr} and a \qty{24}{dBA} increase at the harvested \gls{dc}.
+From the perspective of \gls{wit}, it suggests that passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
+An interpretation is that the \gls{ris} coherently combines the incoming signal with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$.
+From the perspective of \gls{wpt}, it suggests that passive beamforming comes with a power scaling order $L^4$ under the truncated nonlinear harvester model.
+We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel becomes negligible.
+Let $X$ be the cascaded small-scale fading coefficient.
+The \gls{dc} in such case reduces to
+	\begin{equation}
+		z = \beta_2 \Lambda_{\mathrm{R}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{R}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
+	\end{equation}
+	which scales quartically with $L$.
+Compared with active antennas, \gls{ris} elements achieve higher array gain and power scaling order, but a very large $L$ is required to compensate the double fading of the auxiliary link.
+These observations demonstrate the \gls{r-e} benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[$B=\qty{1}{\MHz}$\label{fi:re_irs_1mhz}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_irs_1mhz.eps}
+				\input{assets/chapter_3/re_irs_1mhz.tex}
+			}
+		}
+		\subfloat[$B=\qty{10}{\MHz}$\label{fi:re_irs_10mhz}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_irs_10mhz.eps}
+				\input{assets/chapter_3/re_irs_10mhz.tex}
+			}
+		}
+		\caption{Average \gls{r-e} region for ideal, adaptive, fixed and no \gls{ris} versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
+	\end{figure}
+
+	Figs.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the \gls{r-e} region with different \gls{ris} strategies for narrowband and broadband \gls{swipt}.
+The ideal Frequency-Selective (FS) \gls{ris} assumes the reflection coefficient of each element is independent and controllable at different frequencies.
+The adaptive \gls{ris} adjusts the passive beamforming for different \gls{r-e} points by Algorithm~\ref{al:sca}.
+The \gls{wit}/\gls{wpt}-optimized \gls{ris} is retrieved by Algorithm~\ref{al:m_sca} then fixed for the whole \gls{r-e} region.
+The random \gls{ris} models the phase shift of all elements as i.i.d.
+uniform random variables over $[0, 2\pi)$.
+First, random \gls{ris} and no \gls{ris} perform worse than other schemes since no passive beamforming is exploited.
+Their \gls{r-e} boundaries coincide as the antenna mode reflection of the random \gls{ris} is canceled out after averaging.
+Second, when the bandwidth is small, the performance of ideal, adaptive, and \gls{wit}/\gls{wpt}-optimized \gls{ris} are similar; when the bandwidth is large, the adaptive \gls{ris} outperforms the \gls{wit}/\gls{wpt}-optimized \gls{ris} but is outperformed by the ideal FS \gls{ris}.
+In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
+It suggests that for narrowband \gls{swipt}, the optimal passive beamforming for any \gls{r-e} point is optimal for the whole \gls{r-e} region, and the corresponding composite channel and active precoder are also optimal for the whole \gls{r-e} region.
+Hence, the achievable \gls{r-e} region is obtained by optimizing the waveform amplitude and splitting ratio.
+On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal \gls{ris} reflection coefficient varies at different \gls{r-e} tradeoffs points for broadband \gls{swipt}.
+As shown in Fig.~\ref{fi:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high \gls{snr}, or focused on a few strongest subbands to boost the output \gls{dc}, thanks to adaptive passive beamforming.
+
+	\begin{figure}[!t]
+		\centering
+		\subfloat[Imperfect cascaded \gls{csit}\label{fi:re_csi}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_csi.eps}
+				\input{assets/chapter_3/re_csi.tex}
+			}
+		}
+		\subfloat[Quantized \gls{ris}\label{fi:re_quantization}]{
+			\resizebox{0.45\columnwidth}{!}{
+				% \includegraphics{assets/re_quantization.eps}
+				\input{assets/chapter_3/re_quantization.tex}
+			}
+		}
+		\caption{Average \gls{r-e} region with imperfect cascaded \gls{csit} and quantized \gls{ris} for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.
+$\epsilon_{n}=0$ and $\epsilon_{n}=\infty$ correspond respectively to perfect \gls{csit} and no \gls{csit} (and random \gls{ris}); $b=0$ and $b \to \infty$ correspond respectively to no \gls{ris} and continuous \gls{ris}.}
+	\end{figure}
+
+	We then explore the impacts of imperfect cascaded \gls{csit} and quantized \gls{ris} on the \gls{r-e} performance.
+Due to the general lack of \gls{rf}-chains at the \gls{ris}, it can be challenging to acquire accurate cascaded \gls{csit} on a short-term basis.
+We assume the cascaded channel at subband $n$ is
+	\begin{equation}
+		\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n},
+	\end{equation}
+	where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded \gls{csit} and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+\gls{cscg} distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded \gls{csit} inaccuracy for broadband \gls{swipt} with different $L$.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete \gls{ris} codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution \gls{ris}) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable \gls{r-e} gain over the benchmark scheme without \gls{ris}, and the performance gap between $b=4$ and unquantized \gls{ris} is negligible.
+These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical \gls{ris}-aided \gls{swipt} systems.
 \end{section}
 
-\begin{section}{Conclusion}
-	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
-	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
-	This translates to a wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
-	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.
-	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
-	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
-	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior subspace alignment and subchannel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
+\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
+	This paper investigated the \gls{r-e} tradeoff of a single user employing practical receiving strategies in a \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.
+Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable \gls{r-e} region.
+A three-stage \gls{bcd} algorithm was proposed to solve the problem.
+In the first stage, the \gls{ris} phase shift was obtained by the \gls{sca} technique and eigen decomposition.
+In the second and third stages, the active precoder was derived in closed form, and the waveform amplitude and splitting ratio were optimized by the \gls{gp} method.
+We also proposed and combined closed-form adaptive waveform schemes with a modified passive beamforming strategy to formulate a low-complexity \gls{bcd} algorithm that achieves a good balance between performance and complexity.
+Numerical results revealed significant \gls{r-e} gains by modeling harvester nonlinearity in the \gls{ris}-aided \gls{swipt} design.
+Unlike active antennas, \gls{ris} elements cannot be designed independently across frequencies, but can integrate coherent combining and equal gain transmission to enable constructive reflection and flexible subchannel design.
+Compared to the conventional no-\gls{ris} system, the \gls{ris} mainly affects the effective channel instead of the waveform design.
 
-	One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
-	Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
-	Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward subspaces simultaneously.
-	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
-	% into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
-	% even better channel shaping can be achieved by incorporating the \gls{ris} into the \gls{mimo} precoding and combining design.
+	One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier \gls{ris}-aided \gls{swipt} system.
+Also, harvester saturation effect and practical \gls{ris} models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.
 \end{section}

### 2024-03-04 content/chapter_4.tex
:construction: Add section titles

%!TEX root = ../thesis.tex

\graphicspath{{assets/chapter_4/}}

\chapter{RIScatter: Unifying \glsfmtshort{bc} and \glsfmtshort{ris}}

\begin{section}{Introduction}
	\label{sc:introduction}
	Future wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of low-power devices.
	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
	However, conventional backscatter nodes only respond when externally inquired by a nearby reader.
	\gls{ambc} in Fig.~\subref*{fg:ambc} was proposed a decade ago where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections \cite{Liu2013b}.
	It does not require dedicated power source, carrier emitter, or frequency spectrum, but the backscatter decoding is subject to the strong interference from the primary (legacy) link.
	To tackle this, cooperative \gls{ambc} \cite{Yang2018} employs a co-located receiver to decode both coexisting links, and the concept was further refined as \gls{sr} in Fig.~\subref*{fg:sr} \cite{Liang2020}.
	Specifically, the active transmitter generates \gls{rf} wave carrying primary information, the passive node creates a rich-scattering environment and superimposes its own information, and the co-located receiver cooperatively decodes both links.
	In those \gls{bc} applications, the scatter node is considered as an \emph{information source} and the reflection pattern depends exclusively on the information symbol.
	On the other hand, \gls{ris} in Fig.~\subref*{fg:ris} is a smart signal reflector with numerous passive elements of adjustable phase shifts.
	It customizes the wireless environment for signal enhancement, interference suppression, scattering enrichment, and/or non-line-of-sight bypassing \cite{Wu2021b}.
	Each \gls{ris} element is considered as a \emph{channel shaper} and the reflection pattern depends exclusively on the \gls{csi}.

	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	The achievable rate and optimal input distribution for binary-input \gls{ambc} were investigated in \cite{Qian2019b}, but its impact on the primary link was omitted.
	% For binary-input \gls{ambc},  are investigated in \cite{Qian2019b}, but the authors did not consider its impact on the primary link.
	% The \gls{ber} performance of \gls{ml}, linear, and \gls{sic} receivers are derived over flat fading channels \cite{Yang2018}.
	% The authors of \cite{Hassani2023} analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	In \cite{Hassani2023}, the authors analyzed the energy efficiency and achievable rate region for an \gls{ambc}-aided multi-user downlink \gls{noma} system.
	However, they assumed equal symbol duration and perfect synchronization for the coexisting links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to \emph{double fading};
		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
	Under those assumptions, the achievable rate region of cell-free \gls{sr} was characterized in \cite{Dai2023}.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
	However, this assumption severely limits the backscatter throughput.

	\begin{figure}[!t]
		\centering
		\subfloat[\gls{mbc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_4/mbc.tex}
			}
			\label{fg:mbc}
		}
		\subfloat[\gls{bbc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_4/bbc.tex}
			}
			\label{fg:bbc}
		}
		\\
		\subfloat[\gls{ambc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_4/ambc.tex}
			}
			\label{fg:ambc}
		}
		\subfloat[\gls{sr}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_4/sr.tex}
			}
			\label{fg:sr}
		}
		\\
		\subfloat[\gls{ris}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_4/ris.tex}
			}
			\label{fg:ris}
		}
		\subfloat[RIScatter]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/chapter_4/riscatter.tex}
			}
			\label{fg:riscatter}
		}
		\caption{
			Illustration of scattering applications.
			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
		}
		\label{fg:scatter_illustration}
	\end{figure}

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.4}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                       & \glsentryshort{mbc}/\glsentryshort{bbc} & \glsentryshort{ambc}        & \glsentryshort{sr} (large spreading factor)                         & \glsentryshort{ris} & RIScatter                                                          \\ \midrule
			\showrowcolors
			Information link(s)                    & Backscatter                             & Coexisting                  & Coexisting                                                          & Primary             & Coexisting                                                         \\
			Primary signal on backscatter decoding & Carrier                                 & Multiplicative interference & Spreading code                                                      & ---                 & Energy uncertainty                                                 \\
			Backscatter signal on primary decoding & ---                                     & Multiplicative interference & \glsentryshort{csi} uncertainty                                     & Passive beamforming & Dynamic passive beamforming                                        \\
			Cooperative devices                    & ---                                     & No                          & Primary transmitter and co-located receiver                         & ---                 & Primary transmitter, scatter nodes, and co-located receiver        \\
			Sequential decoding                    & ---                                     & No                          & Primary-to-backscatter, \glsentryshort{sic} and \glsentryshort{mrc} & ---                 & Backscatter-to-primary, no \glsentryshort{sic}/\glsentryshort{mrc} \\
			Reflection pattern depends on          & Information source                      & Information source          & Information source                                                  & \glsentryshort{csi} & Information source, \glsentryshort{csi}, and \glsentryshort{qos}   \\
			Reflection state distribution          & Equiprobable                            & Equiprobable                & Equiprobable or Gaussian                                            & Degenerate          & Flexible                                                           \\
			Load-switching speed                   & Fast                                    & Slow                        & Slow                                                                & Quasi-static        & Arbitrary                                                          \\ \bottomrule
		\end{tabularx}
	\end{table*}

	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019b} and \gls{qam} \cite{Dai2020a}.
	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally rate-suboptimal.
	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
	In contrast, \cite{Vardakis2023} exploited commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader at a different frequency, to perform passive beamforming (but no backscatter modulation) towards a legacy user. \label{cm:2.5}
	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
	Most relevant literature considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
	Those problems are addressed in this paper and the contributions are summarized below.

	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
	A co-located receiver cooperatively decodes both coexisting links.
	Each reflection state is simultaneously a passive beamforming codeword and part of information codeword.
	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
	However, two major challenges for RIScatter are the receiver design and input distribution design.
	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.

	\emph{Second,} we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming afterwards.
	The proposed receiver may be built over legacy receivers with minor hardware upgrade, as it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
	This is the first paper to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.

	\emph{Third,} we address the second challenge in a single-user multi-node \gls{miso} scenario.
	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
	A \gls{bcd} algorithm is proposed where the \gls{kkt} input distribution is numerically evaluated by the converging point of a sequence, the active beamforming is optimized by \gls{pga}, and the decision regions are refined by state-of-the-art sequential quantizer designs for \gls{dmtc}.
	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to other detection schemes.
	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.

	\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
	The observations include:
	1) adaptive reflection state distribution design can flexibly shift between backscatter modulation and passive beamforming;
	2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
	3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
	4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
	5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
	6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
	7) \gls{pga} active beamformer effectively increases the primary (resp. backscatter) rate by boosting the receive \gls{snr} (resp. widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
	8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
\end{section}

\begin{section}{RIScatter}
	\label{sc:riscatter}
	\begin{subsection}{Principles}
		\label{sc:principles}
		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
		\begin{equation}
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		\end{equation}
		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
		Specifically,
		\begin{itemize}
			\item \gls{bc}: The scatterer is an information source with random reflection pattern over time.
			The reflection coefficient is used merely as part of information codeword \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha_m \in \mathbb{I}$ is the amplitude scattering ratio at state $m$, and $c_m$ is the corresponding constellation point.
			\item \gls{ris}: The scatterer is a channel shaper with deterministic reflection pattern over time.
			The reflection coefficient is used merely as a passive beamforming codeword \cite{Wu2018}
			\begin{equation}
				\Gamma_m = \alpha_m \exp(j \theta_m),
				\label{eq:passive_beamforming}
			\end{equation}
			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
		\end{itemize}

		RIScatter generalizes \gls{bc} and \gls{ris} from a probabilistic perspective.
		Each reflection coefficient simultaneously acts as a passive beamforming codeword and part of information codeword.
		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/chapter_4/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/chapter_4/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer corresponds to state \num{2}.
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
				\gls{bc} and \gls{ris} can be viewed as extreme cases of RIScatter, where the input distribution boils down to uniform and degenerate, respectively.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		\begin{remark}
			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
			\label{re:dynamic_passive_beamforming}
		\end{remark}

		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user. The node receiver can be implemented using simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/chapter_4/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/chapter_4/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/chapter_4/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
		% The detail will be covered in Section~\ref{st:system_model}.
	\end{subsection}

	\begin{subsection}{System Model}
		\label{sc:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.7\columnwidth}
			\input{assets/chapter_4/riscatter_network.pdf_tex}
			\caption{A single-user multi-node RIScatter network.}
			\label{fg:riscatter_network}
		\end{figure}
		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
		Without loss of generality, we assume all nodes have $M$ available reflection states.
		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes. The impact of channel estimation error will be investigated in Section~\ref{sc:simulation_results}.}.

		Let $\alpha_k \in \mathbb{I}$ be the amplitude scattering ratio of node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ be the (coded) backscatter symbol of node $k$, and $x_{\mathcal{K}} \triangleq (x_1,\ldots,x_K)$ be the backscatter symbol tuple of all nodes.
		Due to double modulation, the composite channel is a function of backscatter symbol tuple\footnote{\eqref{eq:equivalent_channel_bc} and \eqref{eq:equivalent_channel_ris} are often used in \gls{bc} and \gls{ris} literature, respectively.}
		\begin{subequations}
			\label{eq:equivalent_channel}
			\begin{align}
				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
			\end{align}
		\end{subequations}
		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
		Without loss of generality, we assume the spreading factor $N$ is a positive integer.
		Within one backscatter block, the signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\begin{equation}
			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
			\label{eq:receive_signal}
		\end{equation}
		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the maximum average transmit power, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.

		Let $m_k \in \mathcal{M} \triangleq \{1,\ldots,M\}$ be the reflection state index of node $k$, and $m_{\mathcal{K}} \triangleq (m_1,\ldots,m_K)$ be the state index tuple of all nodes.
		The backscatter symbol $x_k$ (resp. symbol tuple $x_{\mathcal{K}}$) is a random variable that takes value $x_{m_k}$ (resp. value tuple $x_{m_{\mathcal{K}}}$) with probability $p(x_{m_k})$ (resp. $p(x_{m_{\mathcal{K}}})$).
		\begin{remark}
			Dispersed RIScatter nodes encode independently such that
			\begin{equation}
				p(x_{m_{\mathcal{K}}}) = \prod_k p(x_{m_k}).
				\label{eq:equivalent_distribution}
			\end{equation}
			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
			\label{re:independent_encoding}
		\end{remark}

		Let $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ be the receive energy per backscatter block.
		When $x_{m_\mathcal{K}}$ is transmitted, the receive signal $y$ follows \gls{cscg} distribution $\mathcal{CN}(0,\sigma_{m_{\mathcal{K}}}^2)$ with variance
		\begin{equation}
			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
			\label{eq:receive_variance}
		\end{equation}
		and $z$ follows Gamma distribution with conditional \gls{pdf}
		\begin{equation}
			f(z|x_{m_{\mathcal{K}}}) = \frac{z^{N-1} \exp(-z/\sigma_{m_{\mathcal{K}}}^2)}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
			\label{eq:energy_distribution}
		\end{equation}

		\begin{remark}
			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Qian2019b,Xu2020b,Zhang2021d,Hua2022,Hu2021a,Qian2019}.
			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
			\label{re:non_gaussian}
		\end{remark}

		The user first jointly decodes the backscatter message of all nodes using a low-complexity energy detector.\footnote{The reliability of the energy detector is improved by the adaptive input distribution and thresholding design. With high-order modulation or large number of scatter nodes, the reliability can be further enhanced by increasing the spreading factor or using error correction codes with low code-rate. In practice, users can decode backscatter nodes ranging from a few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps \cite{Wu2022e}.\label{fn:energy_detector}}
		The energy detector formulates a \gls{dmtc} of size $M^K \times M^K$.

		\begin{remark}
			The capacity-achieving decision region design for \gls{dmtc} with non-binary inputs in arbitrary distribution remains an open issue.
			It was proved deterministic detectors can be rate-optimal, but non-convex regions (consist of non-adjacent partitions) are generally required and the optimal number of thresholds is unknown \cite{Nguyen2018,Nguyen2021}.
			Next, we restrict the energy detector to convex deterministic decision regions and consider sequential threshold design.
		\end{remark}

		Let $L = M^K$ be the number of decision regions.
		Sort $\{\sigma_{m_{\mathcal{K}}}^2\}$ in ascending order and denote the result sequence as $\sigma_1^2,\ldots,\sigma_L^2$.
		With sequential thresholding, the decision region of backscatter symbol tuple $l \in \mathcal{L} \triangleq \{1,\ldots,L\}$ is\footnote{$m_{\mathcal{K}}$ and $l$ are one-to-one mapped. Both notations are used interchangeably in the following context.}
		\begin{equation}
			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l,
		\end{equation}
		where $t_l$ is the decision threshold between hypotheses $x_{l}$ and $x_{l+1}$.
		An example is shown in Fig.~\ref{fg:energy_distribution}.

		\begin{figure}[!t]
			\centering
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/chapter_4/energy_distribution.tex}
			}
			\caption{
				\gls{pdf} of the receive energy per backscatter block conditioned on different reflection state.
			}
			\label{fg:energy_distribution}
		\end{figure}

		When the threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
		\begin{equation}
			q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z|x_{m_{\mathcal{K}}}) \, d z.
			\label{eq:dmmac}
		\end{equation}
		The backscatter mutual information is
		\begin{equation}
			I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_mutual_information}
		\end{equation}
		where $I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}})$ is the backscatter information function
		\begin{equation}
			I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{p(\hat{x}_{m_{\mathcal{K}}'})}.
			\label{eq:backscatter_information_function}
		\end{equation}

		Once the backscatter information is successfully decoded, the user re-encodes to recover the reflection pattern, constructs the composite channel by \eqref{eq:equivalent_channel}, then coherently decodes the primary link.
		The primary mutual information is
		\begin{equation}
			I_{\text{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_mutual_information}
		\end{equation}
		where $I_{\text{P}}(s;y|x_{m_{\mathcal{K}}})$ is the primary information function
		\begin{equation}
			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr).
			\label{eq:primary_information_function}
		\end{equation}
	\end{subsection}
\end{section}

\begin{section}{Rate-Region Characterization}
	With a slight abuse of notation, we define the weighed sum mutual information and information function as
	\begin{align}
		I(x_{\mathcal{K}})
		 & \triangleq \rho I_{\text{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}           \\
		I(x_{m_\mathcal{K}})
		 & \triangleq \rho I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\text{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function}
	\end{align}
	where $\rho \in \mathbb{I}$ is the \gls{qos}.
	To obtain the achievable primary-(total-)backscatter rate region, we consider the weighted sum mutual information maximization problem with independent encoding at all nodes\footnote{Joint encoding over multiple nodes can be viewed as its special case with an augmented backscatter source.\label{fn:joint_encoding}}
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^\mathsf{T} \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0},}{\label{co:nonnegative_threshold}}
	\end{maxi!}
	where $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problems from the vertices of $M$-dimensional probability simplex to the simplex itself.
	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.

	\begin{subsection}{Input Distribution}
		\label{sc:input_distribution}
		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves the product term \eqref{eq:equivalent_distribution} and is generally non-convex (unless $K=1$).
		Following \cite{Rezaeian2004}, we first recast the \gls{kkt} conditions to their equivalent forms, then propose a numerical solution that guarantees those conditions on the converging point of a sequence.
		\begin{proposition}
			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & \text{if} \ p^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & \text{if} \ p^\star(x_{m_k}) = 0,\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			where $I_k(x_{m_k})$ is the weighted sum marginal information
			\begin{align}
				I_k(x_{m_k})
				 & \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} p(x_{m_{\mathcal{K} \setminus \{k\}}}) I(x_{m_\mathcal{K}}).
				\label{eq:weighted_sum_marginal_information}
			\end{align}
			\label{pr:input_kkt_condition}
		\end{proposition}

		\begin{proof}
			Please refer to Appendix \ref{ap:input_kkt_condition}.
			\label{pf:input_kkt_condition}
		\end{proof}

		For each RIScatter node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
		\begin{proposition}
			For any strictly positive initializer $\{\boldsymbol{p}_k^{(0)}\}_{k \in \mathcal{K}}$, the \gls{kkt} input probability of node $k$ at state $m_k$ is given by the converging point of the sequence
			\begin{equation}
				p^{(r+1)}(x_{m_k}) = \frac{p^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} p^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
				\label{eq:input_kkt_solution}
			\end{equation}
			where $r$ is the iteration index.
			\label{pr:input_kkt_solution}
		\end{proposition}
		\begin{proof}
			Please refer to Appendix \ref{ap:input_kkt_solution}.
			\label{pf:input_kkt_solution}
		\end{proof}

		At iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.

		% \setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			% \small
			\caption{Input Distribution Evaluation by a Sequence}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $q(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $p^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}

		\begin{remark}
			The insufficiency of the \gls{kkt} conditions for problem \eqref{op:input_distribution} implies that the proposed method may not converge to the global-optimal solution.
			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
			\label{re:input_kkt_distribution}
		\end{remark}
	\end{subsection}

	\begin{subsection}{Active Beamforming}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{t}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:active_beamforming}}{\label{ob:active_beamforming}}
			\addConstraint{\eqref{co:transmit_power},}
		\end{maxi!}
		which is still non-convex due to the integration and entropy terms.
		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we have
		\begin{align}
			q(x_l|x_{m_{\mathcal{K}}})
			 & = \frac{\int_{{t_{l-1}}/{\sigma_{m_{\mathcal{K}}}^2}}^{{t_l}/{\sigma_{m_{\mathcal{K}}}^2}} z^{N-1} \exp(-z) \, d z}{(N-1)!} \\
			 & = Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr),
			\label{eq:dmmac_gamma}
		\end{align}
		where $Q(N, b_1, b_2) \triangleq \int_{b_1}^{b_2} z^{N-1} \exp(-z) / (N - 1)! \, d z$ is the regularized incomplete Gamma function.
		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
		\begin{align}
			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} \nonumber \\
			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
			\label{eq:regularized_incomplete_gamma}
		\end{align}
		whose gradient with respect to $\boldsymbol{w}^*$ is
		\begin{align}
			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
			 & = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \nonumber \\
			 & \quad \times \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
			\label{eq:regularized_incomplete_gamma_gradient}
		\end{align}
		where
		\begin{equation}
			g_{m_{\mathcal{K}}}(t_l) = t_l\exp\Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\Bigl(-1+\sum_{n=1}^{N-1} \frac{\bigl(n - \frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr) \bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^{n-1}}{n!}\Bigr).
			\label{eq:regularized_incomplete_gamma_gradient_component}
		\end{equation}
		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we rewrite $I(x_{\mathcal{K}})$ and $\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})$ as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
		\begin{figure*}[!b]
			\hrule
			\begin{equation}
				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} p(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
				\label{eq:weighted_sum_mutual_information_explicit}
			\end{equation}
			\begin{align}
				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
				 & = \sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
				\label{eq:weighted_sum_mutual_information_gradient}
			\end{align}
		\end{figure*}
		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
		At iteration $r+1$, the unregulated active beamformer is updated by
		\begin{equation}
			\bar{\boldsymbol{w}}^{(r+1)} = \boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}}),
			\label{eq:beamforming_gradient_ascent}
		\end{equation}
		where $\gamma$ is the step size (refinable by backtracking line search \cite[Section 9.2]{Boyd2004}).
		Then, $\bar{\boldsymbol{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
		\begin{equation}
			\boldsymbol{w} = \frac{\sqrt{P} \bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
			\label{eq:beamforming_projection}
		\end{equation}

		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
		% \setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			% \small
			\caption{Active Beamforming Optimization by \gls{pga}}
			\label{al:active_beamforming}
			\begin{algorithmic}[1]
				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
				\Ensure $\boldsymbol{w}^\star$
				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $p(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
				\State \phantom{Get} $Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)}$ by \eqref{eq:beamforming_gradient_ascent} \label{st:backtracking_line_search_begin}
					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
						\State Redo step \ref{st:backtracking_line_search_begin}--\ref{st:backtracking_line_search_end}
					\EndWhile
					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

	\begin{subsection}{Decision Threshold}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
		\end{maxi!}
		which is still non-convex since $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
		As shown in Fig.~\ref{fg:discrete_outputs}, the decision regions are formulated by grouping adjacent energy bins.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/chapter_4/discrete_outputs.tex}
			}
			\caption{The thresholds are chosen from fine-grained candidates instead of the continuous space. Each decision region consists of at least one bin.}
			\label{fg:discrete_outputs}
		\end{figure}

		\begin{remark}
			The design of the energy detector does not affect the primary achievable rate, since the composite channel \eqref{eq:equivalent_channel} can always be determined after backscatter decoding and re-encoding.
			This implies that any thresholding maximizing the total backscatter rate is optimal for problem \eqref{op:decision_threshold}.
			\label{re:backscatter_decision}
		\end{remark}

		\begin{remark}
			In terms of total backscatter rate, the nodes can be viewed as an augmented source, and problem \eqref{op:decision_threshold} becomes the rate-optimal quantizer design for \gls{dmtc}.
			\label{re:augmented_source}
		\end{remark}

		Thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
			\addConstraint{\eqref{co:sequential_threshold},}
		\end{maxi!}
		whose global optimal solution has been obtained in recent works.
		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$.
		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
		In Section \ref{sc:simulation_results}, both schemes will be compared with the \gls{ml} scheme \cite{Qian2019}
		\begin{equation}
			t_{l}^{\text{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
			\label{eq:detection_threshold_ml}
		\end{equation}
		which is suboptimal for problem \eqref{op:decision_threshold} unless all nodes are with equiprobable inputs.
	\end{subsection}
\end{section}

\begin{section}{Simulation Results}
	\label{sc:simulation_results}
	In this section, we provide numerical results to evaluate the proposed algorithms.
	We assume the AP-user distance is \qty{10}{m} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	The \gls{ap} is with maximum average transmit power $P=\qty{36}{dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the $1-\varepsilon$ confidence bounds of edge hypotheses (i.e., lower bound of $x_1$ and upper bound of $x_L$).
	We set $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate regions are averaged over \num{e3} channel realizations.\footnote{The code is publicly available at \url{https://github.com/snowztail/riscatter/}.}

	\begin{subsection}{Evaluation of Proposed Algorithms}
		\begin{subsubsection}{Initialization}
			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
			For $\rho=0$ where the backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards the sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
			At the following points, both algorithms are initialized by the solutions at the previous point.
		\end{subsubsection}

		\begin{subsubsection}{Convergence}
			\label{sc:convergence}
			\begin{figure}[!t]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\input{assets/chapter_4/wsr_convergence.tex}
				}
				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
				\label{fg:wsr_convergence}
			\end{figure}
			The \gls{bcd} algorithm is convergent for problem \eqref{op:weighted_sum_rate} since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality.
			In company with \gls{bcd}, we also plotted the convergence results of \gls{kkt} and \gls{pga} algorithms in Fig.~\ref{fg:wsr_convergence} to show how much performance is gained by solving each subproblem.
			It is observed that Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} take around \num{100} and \num{10} iterations to converge, respectively.
			Overall, the \gls{bcd} algorithm requires at most \num{5} iterations to converge.
			As $\rho$ increases (not presented here), the convergence of all three algorithms are much faster thanks to the progressive initialization.
		\end{subsubsection}
	\end{subsection}

	\begin{subsection}{Comparison of Scattering Applications}
		On top of the setup in Fig.~\ref{fg:riscatter_network}, we consider RIScatter and the following benchmark applications:
		\begin{itemize}
			\item \emph{Legacy:} Legacy transmission without scatter nodes.
			\item \emph{\gls{bbc}:} The primary signal is \gls{cw} and the receive signal is
			\begin{equation}
				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n].
			\end{equation}
			The total backscatter rate approaches $K \log M$ when $N$ is sufficiently large.
			\item \emph{\gls{ambc}:} The user decodes each link independently and semi-coherently while treating the other as interference.
			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
			\begin{equation}
				I_{\text{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\text{D}}^\mathsf{H}\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
			\end{equation}
			while the total backscatter rate follows \eqref{eq:backscatter_mutual_information} with uniform input distribution.
			\item \emph{\gls{sr}:} For a sufficiently large $N$, the average primary rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\text{D}}^\mathsf{H} \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
			\begin{equation}
				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n].
				\label{eq:intermediate_signal}
			\end{equation}
			The total backscatter rate approaches $K \log M$.
			\item \emph{\gls{ris}:} The reflection pattern is deterministic and the total backscatter rate is zero.
			The primary achievable rate is a special case of \eqref{eq:primary_mutual_information}
			\begin{equation}
				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\end{equation}
			where $m_{\mathcal{K}}^{\star} = \arg \max_{m_{\mathcal{K}}} I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{m_{\mathcal{K}}})$.
		\end{itemize}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/chapter_4/region_comparison.tex}
			}
			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
			\label{fg:region_comparison}
		\end{figure}

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
		On the other hand, its maximum backscatter achievable rate is higher than that of \gls{ambc}.
		This is because the adaptive channel coding of RIScatter outperforms the equiprobable inputs of \gls{ambc}, especially at the low backscatter \gls{snr} caused by double fading.
		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the advantage over \gls{ambc} should be more prominent.
	\end{subsection}

	\begin{subsection}{Input Distribution under Different \glsfmtshort{qos}}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/chapter_4/distribution_weights.tex}
			}
			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.}
			\label{fg:distribution_weights}
		\end{figure}
		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
		This is inline with Shannon's observation that binary antipodal inputs is good enough for channel capacity at low \gls{snr} \cite{Shannon1948}.
		When the scattered signal is relatively weak, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
		The extreme states producing the lowest/highest energy are always assigned with non-zero probability, while the middles cannot provide enough energy diversity and end up unused.
		At $\rho=1$ where the primary link is prioritized, the optimal input distribution is $[0, 0, 1, 0]^\mathsf{T}$ since state 3 provides higher primary \gls{snr} than other states.
		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a static discrete \gls{ris} element.
		Increasing $\rho$ from \num{0} to \num{1} creates a smooth transition from backscatter modulation to passive beamforming, suggesting RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
	\end{subsection}

	\begin{subsection}{Rate Region by Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
				\resizebox{0.6\columnwidth}{!}{
					\input{assets/chapter_4/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$.
			}
		\end{figure}
		\begin{subsubsection}{Input Distribution}
			We compare these input distribution designs for problem \eqref{op:input_distribution}:
			\begin{itemize}
				\item \emph{Cooperation:} Joint encoding using a joint probability array $p(x_{m_{\mathcal{K}}})$ with $M^K$ entries by Algorithm \ref{al:input_distribution};
				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
				\item \emph{\gls{kkt}:} Solution by Algorithm \ref{al:input_distribution};
				\item \emph{Equiprobable:} Uniform input distribution.
			\end{itemize}
			We also consider these independent distribution recovery methods from the joint probability array:
			\begin{itemize}
				\item \emph{Marginalization:} Marginal probability distributions;
				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposed tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
			\end{itemize}

			Fig.~\subref*{fg:region_distribution} shows their average achievable rate regions.
			Cooperation achieves the outer bound of all schemes, but joint encoding over passive devices may incur additional hardware cost.
			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.
			Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
			Those observations emphasize the importance of adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
		\end{subsubsection}

		\begin{subsubsection}{Active Beamforming}
			We consider three typical active beamforming schemes for problem \eqref{op:active_beamforming}:
			\begin{itemize}
				\item \emph{\gls{pga}:} Solution by Algorithm \ref{al:active_beamforming};
				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
			\end{itemize}

			Fig.~\subref*{fg:region_beamforming} presents the average achievable rate regions for those schemes.
			In the low-$\rho$ regime, the proposed \gls{pga} beamformer significantly outperforms both \gls{mrt} schemes in terms of total backscatter rate.
			This is because the semi-coherent backscatter decoding relies on the relative energy difference under different backscatter symbol tuples.
			Such an energy diversity is enhanced by \gls{pga} that effectively exploits backscatter constellation and input distribution knowledge rather than simply maximizes the channel strength.
			As $\rho$ increases, the primary \gls{snr} outweighs the backscatter energy difference in \eqref{eq:weighted_sum_mutual_information_explicit}, and \gls{pga} beamformer approaches E-\gls{mrt}.
			At $\rho=1$, both \gls{pga} and E-\gls{mrt} boil down to \gls{mrt} towards the strongest composite channel.
			The difference between E-\gls{mrt} and D-\gls{mrt} is insignificant when RIScatter nodes are dispersed.
			Those observations confirm that the proposed \gls{pga} active beamforming design can exploit the \gls{csi}, \gls{qos}, and backscatter constellation to enlarge the achievable rate region.
		\end{subsubsection}

		\begin{subsubsection}{Decision Threshold}
			We evaluate the following decision threshold strategies for problem \eqref{op:decision_threshold_discrete}:
			\begin{itemize}
				\item \emph{\gls{dp}:} Benchmark \gls{dp} method for sequential quantizer \cite{He2021};
				\item \emph{\gls{smawk}:} \emph{\gls{dp}} accelerated by the \gls{smawk} algorithm \cite{He2021};
				\item \emph{Bisection:} The traverse-then-bisect algorithm \cite{Nguyen2020a};
				\item \emph{\gls{ml}:} Maximum likelihood detector \eqref{eq:detection_threshold_ml} \cite{Qian2019}.
			\end{itemize}

			Fig.~\subref*{fg:region_threshold} reveals the average achievable rate region for those strategies.
			The distribution-aware schemes \gls{dp}, \gls{smawk} and Bisection ensure higher total backscatter rate than \gls{ml}.
			This is because the total backscatter rate \eqref{eq:backscatter_mutual_information} is a function of both input distribution and decision regions, and the rate-optimal thresholding depends heavily on the input distribution.
			For example, the backscatter symbol tuples with zero input probability should be assigned with empty decision regions, in order to increase the success detection rates of other hypotheses.
			It highlights the importance of joint input distribution and decision threshold design in rate maximization problems.
		\end{subsubsection}

	\end{subsection}

	\begin{subsection}{Rate Region under Different Configurations}
		\begin{figure}[!t]
			\centering
			\subfloat[RIScatter Nodes\label{fg:region_tags}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_tags.tex}
				}
			}
			\subfloat[Reflection States\label{fg:region_states}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_states.tex}
				}
			}
			\\
			\subfloat[Transmit Antennas\label{fg:region_txs}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_txs.tex}
				}
			}
			\subfloat[Spreading Factor\label{fg:region_duration}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_duration.tex}
				}
			}
			\\
			\subfloat[Average Noise Power\label{fg:region_noise}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_noise.tex}
				}
			}
			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_csi.tex}
				}
			}
			\\
			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_snr_primary.tex}
				}
			}
			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/chapter_4/region_snr_backscatter.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different system configurations.
			}
			\label{fg:region_config}
		\end{figure}
		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
		\begin{subsubsection}{Number of Nodes}
			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
			This is because each RIScatter node not only affects the primary \gls{snr} but also influences the relative energy difference that other nodes can make.
			To maximize the total backscatter rate, some nodes closer to the user may need to sacrifice their own rate and use the state that \emph{minimizes} the composite channel strength, in order to increase the backscatter rate of other nodes.
			This accounts for the significant primary rate decrease in the low-$\rho$ regime.
			On the other hand, when the primary link is prioritized, the RIScatter nodes boil down to \gls{ris} elements and enjoy a passive array gain of $K^2$.
		\end{subsubsection}

		\begin{subsubsection}{Number of States}
			Fig.~\subref*{fg:region_states} shows the relationship between the available reflection states (i.e., \gls{qam} order) $M$ and the achievable rate region when $K=1$.
			We notice that increasing the reflection states has a marginal effect on the primary rate but significantly improves the backscatter rate.
			This is because the maximum amplitude normalized-\gls{qam} \eqref{eq:backscatter_modulation} involves more weak reflection points as $M$ increases.
			It enhances the receive energy diversity but cannot provide enough phase shift resolution with maximum reflection.
		\end{subsubsection}

		\begin{subsubsection}{Number of Transmit Antennas}
			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter tradeoff.
			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
		\end{subsubsection}

		\begin{subsubsection}{Spreading factor}
			Fig.~\subref*{fg:region_duration} shows how the spreading factor $N$ affects the achievable rate region.\footnote{Here, the unit of total backscatter rate is bits per primary block to show backscatter throughput.}
			Using a very large $N$ (as in the case of \gls{sr}) can severely constrain the backscatter throughput, since the gain in energy certainty (by the law of large numbers) cannot withstand the loss in the gross rate.
			As $N \to \infty$, RIScatter nodes boil down to static \gls{ris} elements and the total backscatter rate approaches \num{0}.
			On the other hand, when $N$ is too small, the \gls{dmmac} \eqref{eq:dmmac} becomes unreliable and energy detection is error-prone.
			It explains the observation that $N=10$ provides lower backscatter throughput than $N=20$.
			Therefore, we conclude the spreading factor $N$ should be carefully designed over multiple factors (e.g., primary and backscatter \gls{snr}, data rate requirements, load switching speed at the nodes, and signal processing capability at the user).
		\end{subsubsection}

		\begin{subsubsection}{Average Noise Power}
			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
			Note that the noise influences both primary and backscatter \gls{snr}.
			% It shows the proposed adaptive energy detector is suitable for a wide range of noise levels.
			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the \gls{snr} of energy detection.
		\end{subsubsection}

		% \begin{subsubsection}{Coverage Disk Radius}
		% 	Fig.~\subref*{fg:region_coverage} shows the relationship between disk radius $r$ and achievable rate region.
		% 	We observe both primary and backscatter performance are enhanced when nodes are located closer to the user.
		% 	This is because the double fading effect is less severe for near-far setups.
		% 	In a multi-user RIScatter network with dispersed nodes, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
		% \end{subsubsection}

		\begin{subsubsection}{Imperfect \gls{csi}}
			Due to the lack of \gls{rf} chains at RIScatter nodes, fast and accurate acquisition of the cascaded \gls{csi} can be challenging, especially when the backscatter \gls{snr} is weak or the number of nodes is large.
			We consider an imperfect \gls{csi} model, where the cascaded channel of node $k$ is estimated as
			\begin{equation}
				\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
			\end{equation}
			$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d. CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
			In Fig.~\subref*{fg:region_csi}, it is observed that the channel estimation error mainly affects the backscatter rate.
			When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
			This is because the energy detector is sensitive to the \gls{dmmac} \eqref{eq:dmmac} and thus the estimation of the cascaded channel.
			On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state and the primary rate is almost unchanged.
		\end{subsubsection}

		\begin{subsubsection}{Primary \gls{snr}}
			\label{sc:primary_snr}
			The backscatter \gls{snr} is fixed to \qty{0}{dB} with $Q=1$ in this study.
			Interestingly, Fig.~\subref*{fg:region_snr_primary} shows that increasing the primary \gls{snr} can improve the primary rate but degrade the backscatter rate.
			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
		\end{subsubsection}

		\begin{subsubsection}{Backscatter \gls{snr}}
			The primary \gls{snr} is fixed to \qty{20}{dB} with $Q=1$ in this study.
			Fig.~\subref*{fg:region_snr_backscatter} shows that the primary and backscatter rates are both improved when the backscatter \gls{snr} increases.
			This motivates one to use high-efficiency or semi-passive RIScatter nodes to improve the overall performance.
			In a multi-user RIScatter network, each node may be assigned to the nearest user to guarantee uniformly good performance for both links.
		\end{subsubsection}
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	\label{sc:conclusion}
	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris}, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.
	We also proposed a practical \gls{sic}-free receiver that exploits the properties of active-passive coexisting networks to benefit both subsystems.
	The achievable primary-total-backscatter rate region was then studied for a single-user multi-node RIScatter network, where the input distribution, active beamforming, and decision thresholds are iteratively updated.
	Numerical results validated the proposed algorithms and emphasized the importance of adaptive input distribution and cooperative receiver design.

	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.
\end{section}

### 2024-03-04 content/chapter_5.tex
:construction: Add section titles

%!TEX root = ../thesis.tex

\graphicspath{{assets/chapter_5/}}

\chapter{\glsfmtshort{mimo} Channel Shaping using \glsfmtshort{ris}: From Diagonal to Beyond}

\begin{section}{Introduction}
	% The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
	This is empowered by the recent advances in \gls{ris}, a real-time programmable metasurface of numerous non-resonant sub-wavelength scattering elements.
	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than relays.
	Using \gls{ris} for {passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
	On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019b,Dai2020a}.
	Despite fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}

	The answer indeed depends on the hardware architecture and scattering model.
	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which groups adjacent elements using passive components.
	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
	Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.

	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
	Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself.
	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of channel manipulation.
	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020a,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
	In contrast, \gls{bd}-\gls{ris} can provide a higher channel power but existing results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}. \cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
	While these studies offer promising glimpses into the channel shaping potential, a comprehensive understanding of the capabilities and limitations is desired, and a universal design framework is missing.
	This paper aims to answer the channel shaping question through theoretical analysis and numerical optimization.
	The contributions are summarized below.

	First, we quantify the capability of a \gls{bd}-\gls{ris} to reshape the \gls{mimo} point-to-point channel in terms of singular values.
	The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
	% This generalizes most singular value metrics and provides a powerful design framework.
	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
	We then discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
	This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.

	Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
	It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
	This is the first paper to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.

	Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
	The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
	It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.

	% Third, we propose a closed-form iterative algorithm for power centric channel shaping problems.
	% The idea is to successively approximate the quadratic objective by a sequence of affines and solve the local problems by \gls{svd}.
	% Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.

	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.

\end{section}

\begin{section}{\glsfmtlong{bd}-\glsfmtlong{ris} Model}
	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
	This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
	The overall scattering matrix of the \gls{bd}-\gls{ris} is
	\begin{equation}
		\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
	\end{equation}
	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
	That is, $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{H}$ and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
	Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig. 3]{Shen2020a}, \cite[Fig. 5]{Li2023c}, and \cite[Fig. 2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.

	Let $\mathbf{H}_\mathrm{D} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote the direct (transmitter-receiver), backward (\gls{ris}-receiver), and forward (transmitter-\gls{ris}) channels, respectively.
	The equivalent channel is a function of the scattering matrix
	\begin{equation}
		\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
		\label{eq:channel_equivalent}
	\end{equation}
	where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
	% That is, $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns (resp. rows) of $\mathbf{H}_\mathrm{B}$ (resp. $\mathbf{H}_\mathrm{F}$).
	% , corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$.
	% $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$
	Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
	\begin{equation}
		\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{R}_g^\mathsf{H},
	\end{equation}
	where $\mathbf{L}_g, \mathbf{R}_g \in \mathbb{U}^{L \times L}$ are two unitary factor matrices.
	Let $\mathbf{H}_{\mathrm{B},g} = \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \mathbf{V}_{\mathrm{B},g}^\mathsf{H}$ and $\mathbf{H}_{\mathrm{F},g} = \mathbf{U}_{\mathrm{F},g} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}$ be the compact \gls{svd} of the backward and forward channels, respectively.
	The equivalent channel can thus be rewritten as
	\begin{equation}
		\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}.
		\label{eq:channel_equivalent_svd}
	\end{equation}

	\begin{remark}
		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} creates two critical opportunities:
		\begin{itemize}
			\item \textbf{Subspace alignment:} each group can align the singular matrices of the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) channels. In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ is
			\begin{equation}
				\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
			\end{equation}
			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr]$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr]$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
			Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R} \times N_\mathrm{T}$ passing through itself.
			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the direct-indirect and backward-forward alignments.
			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}. but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}, but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching. However,
			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching. However, in \gls{mimo} each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
			% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
			% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
			% is sufficient for perfect alignment
			% and is sufficient for perfect subspace alignment.
			% In \gls{mimo}, perfect subspace alignment is generally impossible due to the lack of direct control over the indirect channels.aa
			% backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) alignments of the singular matrices.
			\item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength. In \gls{siso}, diagonal \gls{ris} provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$. By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
			The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{R} \times N_\mathrm{T}$.
			% effect is more pronounced in \gls{mimo} since the number of subchannels associated with each group grows quadratically with the dimensions.
			% The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions. since the number of subchannels associated with each group grows quadratically with the dimensions.
			% It suggests that the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength. In \gls{siso}, the maximum indirect channel amplitude by diagonal \gls{ris} is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are independent permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$. By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
			% \begin{equation}
			% 	\item \
			% \end{equation}
			% and $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$. By rearrangement inequality,
			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength. In \gls{siso}, the optimal indirect channel amplitude is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ by diagonal \gls{ris} and $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},\pi_\mathrm{B}(n)} \rvert \lvert h_{\mathrm{F},\pi_\mathrm{F}(n)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi(\cdot)$ is a permutation of $\{1, \ldots, N_\mathrm{S}\}$.
			% this is unique to \gls{bd}-\gls{ris} --- each group can rearrange and combine the backward and forward subchannels by strength. In \gls{siso}, the optimal indirect channel amplitude is relaxed from $\sum_n \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ to $\sum_n \lvert h_{\mathrm{B},\pi(n)} \rvert \lvert h_{\mathrm{F},\pi(n)} \rvert$ where $\pi(\cdot)$ is a permutation of $\{1, \ldots, L\}$.
			% from strongest to weakest, which attains the maximum in rearrangement inequality.
		\end{itemize}
	\end{remark}

	% TODO: add illustrations for both

	% In \gls{siso}, the equivalent channel can be further simplified as
	% \begin{equation}
	% 	h = h_\mathrm{D} + \sum_g \mathbf{h}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{h}_{\mathrm{F},g},
	% \end{equation}
	% subspace alignment boils down to phase matching

	% For the \gls{siso} case in Fig. \subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
	% This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
	% Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
	% This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
	% That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
	% Now consider a diagonal \gls{ris} in \gls{mimo}.
	% Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
	% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
	% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
	% We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.

	% \begin{equation}
	% 	\mathbf{H} = \underbrace{\mathbf{H}_\mathrm{D} + \underbrace{\sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}_\text{group-wise}}_\text{direct-indirect},
	% \end{equation}
	% which involves three subspace alignment problems:
	% which involves three subspace alignment problems
	% \begin{equation}
	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g \mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{backward-forward}\\\text{additive alignment}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
	% \end{equation}
	% \begin{equation}
	% 	\mathbf{H} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{L}_g}_{\substack{\text{backward}\\\text{align}}} \underbrace{\mathbf{R}_g^\mathsf{H} \mathbf{U}_{\mathrm{F},g}}_{\substack{\text{forward}\\\text{align}}} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}.
	% \end{equation}
	% Then the equivalent channel can be rewritten as
	% Since the field of (block) unitary matrices formulate a field that is closed under multiplication
	% Since block unitary matrices satisfy the axioms of a field under matrix multiplication
	% \begin{remark}
	% 	% To understand the \gls{b} gain from in-group connections
	% \end{remark}

	% \begin{remark}
	% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
	% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
	% 	\begin{equation}
	% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
	% 		\label{eq:scattering_fc_tight}
	% 	\end{equation}
	% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
	% 	\begin{itemize}
	% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
	% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
	% 	\end{itemize}
	% \end{remark}

	% \begin{remark}
	% 	\gls{bd}-\gls{ris} reduces to diagonal \gls{ris} and unitary \gls{ris} with group size $L$ 1 and $N_\mathrm{S}$, respectively.
	% \end{remark}
	% \begin{remark}
	% 	Individual forward and backward \gls{csi} are required for \gls{bd}-\gls{ris} designs.
	% 	This is different from diagonal \gls{ris} where estimating their product is usually sufficient.
	% 	% Later we will show the potential benefits from the \gls{csi} overhead.
	% \end{remark}
\end{section}

\begin{section}{Channel Singular Values Redistribution}
	\begin{subsection}{A Toy Example}\label{sc:toy_example}
		We first illustrate the channel shaping capabilities of different \gls{ris} by a toy example.
		% We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
		Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
		The diagonal \gls{ris} is modeled by $\mathbf{\Theta}_\mathrm{D} = \mathrm{diag}(e^{\jmath \theta_1}, e^{\jmath \theta_2})$ while the unitary \gls{bd}-\gls{ris} has 4 independent angular parameters
		\begin{equation}
			\mathbf{\Theta}_\mathrm{U} = e^{\jmath \phi} \begin{bmatrix}
				e^{\jmath \alpha} \cos \psi  & e^{\jmath \beta} \sin \psi   \\
				-e^{-\jmath \beta} \sin \psi & e^{-\jmath \alpha} \cos \psi
			\end{bmatrix}.
		\end{equation}
		In particular, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
		We also enforce symmetry by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
		\begin{figure}
			\centering
			\includegraphics[width=\columnwidth]{assets/chapter_5/singular_trend.eps}
			\caption{$2 \times 2 \times 2$ (no direct) channel singular value shaping by diagonal and symmetry unitary \gls{ris}.}
			\label{fg:singular_trend}
		\end{figure}
		Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
		It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and design parameters.
		A larger performance gap is expected when asymmetric \gls{bd}-\gls{ris} is available.
		This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
	\end{subsection}

	\begin{subsection}{Pareto Frontier Characterization}
		We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{\label{op:pareto}}{\label{ob:pareto}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{\label{co:pareto_unitary}}
		\end{maxi!}
		where $n \in \{1,\ldots,N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
		Varying $\{\rho_n\}$ unveils the entire achievable singular value region.
		Thus, the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
		The objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} for group $g$ corresponds to the Stiefel manifold.
		Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.

		Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a block-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
		It leverages the fact that unitary matrices are closed under multiplication.
		At iteration $r$, the gradient is computed in the Euclidean space and translated to the Riemannian manifold \cite{Absil2009}
		\begin{gather}
			\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
			\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
		\end{gather}
		The Polak-Ribierre parameter \cite{Polak1969} is approximated as \cite{Abrudan2009}
		\begin{equation}
			\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
			\label{eq:parameter_cg}
		\end{equation}
		and the conjugate direction is
		\begin{equation}
			\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}. % $\mathcal{O}(N_\mathrm{S}^2)$
			\label{eq:direction_cg}
		\end{equation}
		In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
		\begin{equation}
			\mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}. % $\mathcal{O}(N_\mathrm{S}^3)$
			\label{eq:geodesic}
		\end{equation}
		An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.\footnote{To double the step size, one only need to square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.}
		Finally, the scattering matrix is updated along the geodesic as
		\begin{equation}
			\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
			\label{eq:update_geodesic}
		\end{equation}
		Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
		Convergence to stationary points is guaranteed.

		\begin{remark}
			Compared with universal manifold optimization \cite{Absil2009,Pan2022d}, Algorithm~\ref{ag:rcg} inherits a trifold benefit from \cite{Abrudan2008,Abrudan2009}:
			\begin{enumerate}
				\item No retraction thanks to rotational update \eqref{eq:geodesic}, \eqref{eq:update_geodesic};
				\item Lower computational complexity per iteration;
				\item Faster convergence thanks to proper parameter space.
			\end{enumerate}
		\end{remark}

		% \setalgorithmcaptionfont{\small}
		\begin{algorithm}[!t]
			% \small
			\caption{Block-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
			\label{ag:rcg}
			\begin{algorithmic}[1]
				\Require $f(\mathbf{\Theta})$, $G$
				\Ensure $\mathbf{\Theta}^\star$
				\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
				\Repeat
					\For {$g \gets 1$ to $G$}
						\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean} \label{ln:gradient_euclidean}
						\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riemannian}
						\State $\gamma_g^{(r)} \gets$ \eqref{eq:parameter_cg}
						\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
						\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
							\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
						\EndIf
						\State $\mu \gets 1$
						\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic}
						\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
							\State $\mu \gets 2 \mu$
						\EndWhile
						\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
							\State $\mu \gets \mu / 2$
						\EndWhile
						\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:update_geodesic}
					\EndFor
					\State $r \gets r+1$
				\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}

		\begin{lemma}\label{lm:pareto_gradient}
			The Euclidean gradient of \eqref{ob:pareto} w.r.t. \gls{bd}-\gls{ris} group $g$ is
			\begin{equation}
				\frac{\partial \sum_n \rho_n \sigma_n(\mathbf{H})}{\partial \mathbf{\Theta}_g^*} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \mathbf{U} \mathrm{diag}(\rho_1,\ldots,\rho_N) \mathbf{V}^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^\mathsf{H},
				\label{eq:pareto_gradient}
			\end{equation}
			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}$, respectively.
		\end{lemma}
		\begin{proof}
			Please refer to Appendix~\ref{ap:pareto_gradient}.
		\end{proof}

		%  The Euclidean gradient of \gls{bd}-\gls{ris} group $g$ is computed as
		% where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
		Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto} where line \ref{ln:gradient_euclidean} uses \eqref{eq:pareto_gradient} explicitly.
		% \eqref{eq:pareto_gradient} is used in line \ref{ln:gradient_euclidean}.
	\end{subsection}

	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
		We then discuss some analytical bounds related to channel singular values.
		\begin{proposition}[degree of freedom]\label{pp:dof}
			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
		\end{proposition}
		\begin{proof}
			Please refer to Appendix~\ref{ap:dof}.
		\end{proof}

		\begin{proposition}[rank-deficient channel]\label{pp:rank_deficient}
			% If the forward/backward channel is rank-$k$, then a \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n > k$) channel singular value to the $n-k$-th singular value of $\mathbf{T}$, or suppress the $n$-th ($n < N - k + 1$) channel singular value to the $n$-th singular value of $\mathbf{T}$.
			% If the forward/backward channel is rank-$k$, then a sufficiently large \gls{bd}-\gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ equivalent channel singular values without bounds.
			If the forward or backward channel is rank-$k$, then regardless of the \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
			\begin{align}
				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k, \label{iq:sv_bound_enlarge}          \\
				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1, \label{iq:sv_bound_suppress}
			\end{align}
			where
			% \begin{align}
			% 	\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
			% 	\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k.
			% \end{align}
			\begin{equation}
				\mathbf{T} \mathbf{T}^\mathsf{H} =
				\begin{cases}
					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
				\end{cases}
				\label{eq:auxiliary_matrix}
			\end{equation}
			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
			% where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the forward channel is rank-$k$ and $\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the backward channel is rank-$k$.
		\end{proposition}
		\begin{proof}
			Please refer to Appendix~\ref{ap:rank_deficient}.
		\end{proof}

		% \begin{corollary}[degree of freedom]
		% 	In point-to-point \gls{mimo} with or without direct link, \gls{bd}-\gls{ris} cannot provide a higher \gls{dof} than diagonal \gls{ris}.
		% \end{corollary}

		\begin{corollary}[extreme singular values\label{co:extreme}]
			With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded above while the last $k$ channel singular values can be suppressed to zero.
			% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
			% If the forward or backward channel is rank-$k$ and the \gls{ris} is sufficiently large, then the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
			% If the forward/backward channel is rank-$k$, then the first (resp. last) $k$ singular values of the equivalent channel are unbounded above (resp. below).
			% a sufficiently large \gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ singular values of the equivalent channel without bounds.
		\end{corollary}

		\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} in \cite{Semmler2023}.}\label{co:los}]
			If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp. suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp. $n$-th) singular value of $\mathbf{T}$, that is,
			\begin{equation}
				\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T}) \ge {\sigma_2(\mathbf{H})} \ge \ldots \ge \sigma_{N-1}(\mathbf{T}) \ge {\sigma_N(\mathbf{H})} \ge \sigma_N(\mathbf{T}).
				\label{iq:sv_bound_los}
			\end{equation}
		\end{corollary}

		In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.

		\begin{proposition}[fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
			If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the channel singular values can be manipulated up to
			% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
			% only bounds that apply here are those that apply to the singular values of
			\begin{equation}
				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
			\end{equation}
			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
			% Our focus thus shifts to how the singular values of matrix product are bounded by the singular values of its individual factors.
		\end{proposition}

		\begin{proof}
			Please refer to Appendix~\ref{ap:fully_connected}.
		\end{proof}

		The problem now becomes how the singular values of matrix product are bounded by the singular values of its individual factors.
		Let $N' = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le N'$.
		We have the following corollaries.

		\begin{corollary}[generic singular value bounds \cite{Fulton2000}]
			\begin{equation}
				\prod_{k \in {K}} \sigma_k(\mathbf{H}) \le \prod_{i \in {I}} \sigma_i(\mathbf{H}_\mathrm{B}) \prod_{j \in {J}} \sigma_j(\mathbf{H}_\mathrm{F}),
				\label{iq:sv_bound_fc}
			\end{equation}
			for all admissible triples $(I, J, K) \in T_r^{N'}$ with $r < N'$, where
			\begin{equation*}
				\begin{gathered}
					% T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
					% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
					T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \forall p < r, (F, G, H) \in T_p^r,\\
					\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
				\end{gathered}
			\end{equation*}
			\begin{equation*}
				U_r^{N'} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
			\end{equation*}
		\end{corollary}

		\begin{corollary}[upper bound on the largest singular value]
			\begin{equation}
				\sigma_1(\mathbf{H}) \le \sigma_1(\mathbf{H}_\mathrm{B}) \sigma_1(\mathbf{H}_\mathrm{F}).
			\end{equation}
		\end{corollary}

		% \begin{corollary}[lower bound on the smallest singular value]
		% 	\begin{equation}
		% 		\sigma_{N'}(\mathbf{H}) \ge \sigma_{N'}(\mathbf{H}_\mathrm{B}) \sigma_{N'}(\mathbf{H}_\mathrm{F}).
		% 	\end{equation}
		% \end{corollary}

		\begin{corollary}[upper bound on the product of first $k$ singular values]
			\begin{equation}
				\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
			\end{equation}
		\end{corollary}

		% \begin{corollary}[lower bound on the product of last $k$ singular values]
		% 	\begin{equation}
		% 		\prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
		% 	\end{equation}
		% \end{corollary}

		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
			\begin{equation}
				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
				\label{iq:sv_bound_fc_power}
			\end{equation}
			When $k = N'$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels.
		\end{corollary}

		% \begin{remark}
		% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
		% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
		% 	\begin{equation}
		% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
		% 		\label{eq:scattering_fc_tight}
		% 	\end{equation}
		% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
		% 	\begin{itemize}
		% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
		% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
		% 	\end{itemize}
		% \end{remark}

		Tight bounds are inapplicable when a \gls{mimo} direct link is present, as the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
		Such a balance often involves optimization approaches and another example will be discussed in Section~\ref{sc:low_complexity}.
	\end{subsection}

\end{section}

\begin{section}{Achievable Rate Maximization}\label{sc:rate}
	The \gls{mimo} achievable rate maximization problem is formulated w.r.t. joint active and passive beamforming
	\begin{maxi!}
		{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
		\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
	\end{maxi!}
	where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the noise power, and $P$ is the transmit power budget.
	Two methods are proposed below to solve problem \eqref{op:rate}.

	\begin{subsection}{Alternating Optimization}
		Consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
		For a given $\mathbf{W}$, the passive beamforming subproblem is
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\log \det \biggl(\mathbf{I} + \frac{\mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H}}{\eta}\biggr)}{\label{op:rate_passive}}{\label{ob:rate_passive}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		\end{maxi!}
		where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
		\begin{lemma}\label{lm:rate_gradient}
			The Euclidean gradient of \eqref{ob:rate_passive} w.r.t. \gls{bd}-\gls{ris} block $g$ is
			\begin{equation}
				\frac{\partial R}{\partial \mathbf{\Theta}_g^*} = \frac{1}{\eta} \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \biggl(\mathbf{I} + \frac{\mathbf{H}\mathbf{Q}\mathbf{H}^\mathsf{H}}{\eta}\biggr)^{-1} \mathbf{H} \mathbf{Q} \mathbf{H}_{\mathrm{F},g}^\mathsf{H}.
				\label{eq:rate_gradient}
			\end{equation}
		\end{lemma}

		\begin{proof}
			Please refer to Appendix~\ref{ap:rate_gradient}.
		\end{proof}
		Algorithm \ref{ag:rcg} is then invoked to solve problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
		Since \eqref{ob:rate_passive} is a concave function of $\mathbf{\Theta}$, convergence to local-optimal points is guaranteed.
		On the other hand, the global optimal transmit precoder for a fixed $\mathbf{\Theta}$ is given by the eigenmode transmission \cite{Clerckx2013}
		\begin{equation}
			\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
			\label{eq:precoder_eigenmode}
		\end{equation}
		where $\mathbf{V}$ is the right channel singular matrix and $\mathbf{S}^\star$ is the optimal water-filling power allocation matrix.
		The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
	\end{subsection}

	\begin{subsection}{Low-Complexity Solution}\label{sc:low_complexity}
		We then propose a low-complexity solution to problem \eqref{op:rate} based on channel shaping.
		The passive beamforming subproblem \eqref{op:rate_passive} involves transmit covariance matrix $\mathbf{Q}$ and thus requires iterative \gls{rcg} update.
		Instead, we decouple the joint \gls{ris}-transceiver design by recasting \eqref{op:rate_passive} as channel power maximization
		\begin{maxi!}
			{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
		\end{maxi!}
		% which only accounts for channel characteristics but has no trivial solution.
		\begin{remark}
			As mentioned in Section \ref{sc:bounds}, the key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
			Problem \eqref{op:power_passive} is very similar (in terms of maximizing the inner product of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$) to the weighted orthogonal Procrustes problem \cite{Gower2004}
			\begin{mini!}
				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
			\end{mini!}
			which has no trivial solution.
			One lossy transformation, by moving $\mathbf{\Theta}$ to one side \cite{Bell2003}, formulates standard orthogonal Procrustes problems
			\begin{mini!}
				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
			\end{mini!}
			which has global optimal solutions
			\begin{equation}
				\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}
				\label{eq:orthogonal_procrustes_solution}
			\end{equation}
			where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
			This suboptimal solution only applies to fully-connected \gls{bd}-\gls{ris}.
		\end{remark}

		Inspired by \cite{Nie2017}, we propose a general solution to problem \eqref{op:power_passive} with arbitrary group size.
		The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form.

		\begin{proposition}\label{pp:power}
			Starting from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
			\begin{equation}
				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
				\label{eq:scattering_power}
			\end{equation}
			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
			\begin{equation}
				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
				\label{eq:auxiliary_matrix_power}
			\end{equation}
		\end{proposition}

		\begin{proof}
			Please refer to Appendix~\ref{ap:power}.
		\end{proof}
		Once the channel shaping problem \eqref{op:power_passive} is solved, the transmit precoder can be obtained by \eqref{eq:precoder_eigenmode}.
		This two-stage approach decouples both blocks and is computationally efficient.
	\end{subsection}

	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{fg:pc_rate_sx}]{
	% 		\resizebox{0.48\columnwidth}{!}{
	% 			\input{assets/chapter_5/pc_rate_sx.tex}
	% 		}
	% 	}
	% 	\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{fg:pc_rate_tx}]{
	% 		\resizebox{0.48\columnwidth}{!}{
	% 			\input{assets/chapter_5/pc_rate_tx.tex}
	% 		}
	% 	}
	% 	\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
	% 	\label{fg:pc_rate}
	% \end{figure}

	% Fig.~\ref{fg:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
	% To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
	% This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
	% If tetrads can be formed in \gls{bd}-\gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
	% Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
	% We thus conclude dyadic or tetradic \gls{bd}-\gls{ris} usually strike a good balance between performance and complexity.

	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{0.65\columnwidth}{!}{
	% 		\input{assets/chapter_5/power_sx.tex}
	% 	}
	% 	\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$. $(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
	% 	\label{fg:power_sx}
	% \end{figure}

	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[Without Direct Link\label{fg:pc_power_bond_nd}]{
	% 		\resizebox{0.48\columnwidth}{!}{
	% 			\input{assets/chapter_5/pc_power_bond_nd.tex}
	% 		}
	% 	}
	% 	\subfloat[With Direct Link\label{fg:pc_power_bond_hd}]{
	% 		\resizebox{0.48\columnwidth}{!}{
	% 			\input{assets/chapter_5/pc_power_bond_hd.tex}
	% 		}
	% 	}
	% 	\caption{Average channel power versus \gls{ris} group size $L$. $(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
	% 	\label{fg:pc_power_bond}
	% \end{figure}
	% % Fig.~\ref{fg:power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
	% % Fig.~\ref{fg:power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
	% Fig.~\ref{fg:power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
	% % The behavior is more obvious for a large \gls{ris}.
	% This behavior is more pronounced for a large \gls{ris}.
	% For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
	% % \gls{bd}-\gls{ris} provides a higher channel power than conventional \gls{ris}.
	% % As $L$ increases from 1 to 2,
	% It implies that the channel shaping capability of \gls{bd}-\gls{ris} scales with group size $L$.

	% Fig.~\ref{fg:pc_power_bond_hd} and \ref{fg:pc_power_bond_nd} compare the average channel power without and with direct link.
	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
	% % ``Cascaded'' means the maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
	% % maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
	% % ? ``Cascaded'' means the \emph{power product} of the forward and backward channels.
	% % ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues of the forward and backward channels.
	% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
	% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect subspace.
	% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
	% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward subspace alignment for an optimal channel boost.
	% It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
	% This again emphasizes the advantage of in-group connection of \gls{bd}-\gls{ris}.
	% % This is because the direct and indirect channels superpose
	% % the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
	% % When the direct link is present, a small $L$ cannot align the direct-indirect subspace.

	% % neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
	% % We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
	% % For conventional \gls{ris},
	% % align the direct-indirect subspace.
	% % When the direct link is present, a small $L$ can neither align the direct-indirect subspace nor the forward-backward subspace.
	% % For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
	% % neither the direct-indirect nor the forward-backward subspace can be effectively aligned with a small $L$.

	% % When the direct link is present, a small $L$ can neither preserve the
	% % neither align the direct-indirect subspace nor the forward-backward subspace.

	% % When the direct link is absent, a large $L$ can align the forward-backward subspace but cannot preserve the forward-backward power balance.

\end{section}

\begin{section}{Simulation Results}\label{sc:simulation}
	In this section, we provide numerical results to evaluate the proposed \gls{bd}-\gls{ris} designs.
	Consider a distance-dependent path loss model $\Lambda(d) = \Lambda_0 d^{-\gamma}$ where $\Lambda_0$ is the reference path loss at distance \qty{1}{m}, $d$ is the propagation distance, and $\gamma$ is the path loss exponent.
	The small-scale fading model is $\mathbf{H} = \sqrt{\kappa/(1+\kappa)} \mathbf{H}_\text{LoS} + \sqrt{1/(1+\kappa)} \mathbf{H}_\text{NLoS}$, where $\kappa$ is the Rician $K$-factor, $\mathbf{H}_\text{LoS}$ is the deterministic \gls{los} component, and $\mathbf{H}_\text{NLoS} \sim \mathcal{CN}(\mathbf{0}, \mathbf{I})$ is the Rayleigh component.
	We set $\Lambda_0=\qty{-30}{dB}$, $d_\mathrm{D}=\qty{14.7}{m}$, $d_\mathrm{F}=\qty{10}{m}$, $d_\mathrm{B}=\qty{6.3}{m}$, $\gamma_\mathrm{D}=3$, $\gamma_\mathrm{F}=2.4$ and $\gamma_\mathrm{B}=2$ for reference, which corresponds to a typical indoor environment with $\Lambda_\mathrm{D}=\qty{-65}{dB}$, $\Lambda_\mathrm{F}=\qty{-54}{dB}$, $\Lambda_\mathrm{B}=\qty{-46}{dB}$.
	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
	$\kappa \to \infty$ is assumed for all channels unless otherwise specified.

	\begin{table*}[!t]
		\caption{Average Performance of \gls{bd}-\gls{ris} Designs}
		\label{tb:complexity_test}
		\centering
		\begin{tabular}{ccccccc}
			\toprule
			\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                                 \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
			                                & Objective                              & Iterations                             & Time [s]         & Objective        & Iterations & Time [s]  \\ \midrule
			Geodesic                        & $\num{4.355e-3}$                       & 11.61                                  & $\num{2.038e-2}$ & $\num{1.164e-2}$ & 25.78      & 3.216     \\
			Non-geodesic                    & $\num{4.168e-3}$                       & 169.5                                  & $\num{1.420e-1}$ & $\num{8.873e-3}$ & 278.1      & 27.81     \\ \bottomrule
		\end{tabular}
	\end{table*}

	\begin{subsection}{Channel Singular Values Redistribution}
		\begin{subsubsection}{Pareto Frontier}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx32_nd.tex}
					}
				}
				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_pareto_sx128.tex}
					}
				}
				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
				\label{fg:singular_pareto}
			\end{figure}
			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
		\end{subsubsection}

		\begin{subsubsection}{Analytical Bounds and Numerical Results}
			\begin{figure}[!t]
				\centering
				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_bound_rank1_sx32.tex}
					}
				}
				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_bound_rank1_sx64.tex}
					}
				}
				\\
				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_bound_rank2_sx128.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/singular_bound_rank4_sx256.tex}
					}
				}
				\caption{
					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
					`rank-$k$' refers to the forward channel.
				}
				\label{fg:singular_bound}
			\end{figure}
			Fig. \ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
			Here we assme a rank-$k$ forward channel without loss of generality.
			When the \gls{ris} is in the vicinity of the transmitter, Figs. \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
			% The observations align with Proposition \ref{pp:rank_deficient} that t
			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
			Those observations align with Proposition \ref{pp:rank_deficient} and Corollary \ref{co:extreme}.
			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.

			\begin{figure}[!t]
				\centering
				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/power_bond_txrx1_nd.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/chapter_5/power_bond_txrx4_nd.tex}
					}
				}
				\caption{
					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward subchannels.
				}
				\label{fg:power_bond}
			\end{figure}

			Fig. \ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form or via optimization approach \eqref{eq:scattering_power}.
			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
			% We observe that the bound is also tight for fully-connected \gls{bd}-\gls{ris}.
			% Increasing the group size of \gls{bd}-\gls{ris} significantly improves the channel power especially for a large \gls{mimo}.
			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a fully-connected one can achieve the bound.
			% The bound here indicates how much power can potentially be extracted from the forward and backward channels.
			% We observe that using a larger group size can approach the bound better, and full
			% We observe that the bound is tight for fully-connected \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
			For the \gls{siso} case in Fig. \subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
			Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
			This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
			Now consider a diagonal \gls{ris} in \gls{mimo}.
			Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
			Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
			It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
		\end{subsubsection}

		% The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
		% Clearly, a larger group size provides
		% and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
	\end{subsection}

	\begin{subsection}{Achievable Rate Maximization}
		\begin{figure}[!t]
			\centering
			\subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)\label{fg:power_sx_txrx16_nd}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_5/power_sx_txrx16_nd.tex}
				}
			}
			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_5/power_sx_txrx16.tex}
				}
			}
			\caption{
				Average maximum channel power versus \gls{ris} configuration.
				`OP-left' and `OP-right' refer to the suboptimal solutions to problem \eqref{op:power_passive} by lossy transformation \eqref{op:standard_orthogonal_procrustes} where $\mathbf{\Theta}$ is to the left and right of the product, respectively.
			}
			\label{fg:power_sx}
		\end{figure}

		We first focus on channel shaping subproblem \eqref{op:power_passive_approx}.
		Fig. \ref{fg:power_sx} shows the achievable channel power under different \gls{ris} configurations.
		An interesting observation is that the relative power gain of \gls{bd}-\gls{ris} over diagonal \gls{ris} is even larger with direct link.
		For example, a 64-element fully \gls{bd}-\gls{ris} can almost provide the same channel power as a 256-element diagonal \gls{ris} in Fig. \ref{fg:power_sx_txrx16}, but not in Fig. \ref{fg:power_sx_txrx16_nd}.
		% This again credits to the superior subspace alignment capability of \gls{bd}-\gls{ris}.
		This is because the \gls{ris} needs to balance the multiplicative forward-backward combining and the additive direct-indirect combining, such that the subspace alignment advantage of \gls{bd}-\gls{ris} becomes more pronounced.
		We also notice that the suboptimal solutions \eqref{eq:orthogonal_procrustes_solution} for fully-connected \gls{bd}-\gls{ris} by lossy transformation \eqref{op:standard_orthogonal_procrustes} are very close to optimal especially for a large $N_\mathrm{S}$.

		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_5/rate_beamforming.tex}
				}
			}
			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_5/rate_txrx.tex}
				}
			}
			\\
			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_5/rate_sx.tex}
				}
			}
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
				\resizebox{!}{3.25cm}{
					\input{assets/chapter_5/rate_kfactor.tex}
				}
			}
			\caption{
				Average achievable rate versus \gls{mimo} and \gls{ris} configurations.
				The noise power is $\eta = \qty{-75}{dB}$, corresponding to a direct \gls{snr} of \num{-10} to \qty{30}{dB}.
				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
				`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
			}
			\label{fg:rate}
		\end{figure}

		Fig. \ref{fg:rate} presents the achievable rate under different \gls{mimo} and \gls{ris} configurations.
		At a transmit power of \qty{10}{dB}, Fig. \subref*{fg:rate_beamforming} shows that introducing a 128-element diagonal \gls{ris} to 4T4R \gls{mimo} can improve the achievable rate from \qty{22.2}{bps/Hz} to \qty{29.2}{bps/Hz} ($+\qty{31.5}{\percent}$).
		In contrast, a \gls{bd}-\gls{ris} of group size 4 and 128 can further improve the rate to \qty{32.1}{bps/Hz} ($+\qty{44.6}{\percent}$) and \qty{34}{bps/Hz}  ($+\qty{53.2}{\percent}$), respectively.
		Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
		Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better tradeoff between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
		The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
	\end{subsection}
\end{section}

\begin{section}{Conclusion}
	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
	This translates to a wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.
	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior subspace alignment and subchannel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.

	One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
	Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
	Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward subspaces simultaneously.
	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
	% into the \gls{mimo} precoding and combining design is also an interesting topic for future research.
	% even better channel shaping can be achieved by incorporating the \gls{ris} into the \gls{mimo} precoding and combining design.
\end{section}

### 2024-03-05 content/chapter_1.tex
:construction: Add motivation

@@
 \begin{section}{Motivation}
+	The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
+	Great successes have been made at the transmitter and receiver sides over the past century, and the communications society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
+	Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
+	This is made possible by the latest advances in machine learning and programmable metamaterials --- the former enables the network to learn from the environment while the latter allows the environment to adapt to the network.
+	Together, they form a symbiotic relationship that can revolutionize the way we communicate, sense, and interact with the world.
+	One promising candidate to fulfill this vision is \gls{ris}, a programmable metasurface that recycles and redistributes the ambient electromagnetic waves for improved wireless performance.
+	It is a disruptive technology that can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security management.
+	Apart from the communications domain, \gls{ris} has also found applications in radar, imaging, and sensing, where it can be used to manipulate the electromagnetic waves for better resolution, penetration, and detection.
 

### 2024-03-06 content/chapter_1.tex
:construction: Update motivation

@@
 	One promising candidate to fulfill this vision is \gls{ris}, a programmable metasurface that recycles and redistributes the ambient electromagnetic waves for improved wireless performance.
-	It is a disruptive technology that can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security management.
-	Apart from the communications domain, \gls{ris} has also found applications in radar, imaging, and sensing, where it can be used to manipulate the electromagnetic waves for better resolution, penetration, and detection.
+	This disruptive technology can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security improvement.
+	Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance with fewer active components, lower power consumption, and lower hardware complexity.
+	\gls{ris} is also different from conventional relays as it features no \gls{rf} chains, no symbol dependency, minimum signal processing, and negligible additional noise.
+	Moreover, it can be easily deployed in various forms, such as walls, windows, ceilings, and furniture, to provide seamless coverage and powerful customization for indoor and outdoor environments.
+	These unique characteristics make \gls{ris} a ubiquitous and cost-effective solution for future wireless communication, sensing, and power transfer systems.
 
+	Despite the great possibilities, the prototyping of \gls{ris} is still in its infancy and no commercial product has been released by the first quarter of 2024.
+	The transition from theory to practice is hindered by many challenges including channel acquisition, phase resolution, out-of-band response mitigation, placement optimization, and integration with existing systems.
+	Most importantly, a comprehensive understanding of its potential is still missing and the precise role it should play in future networks remains ambiguous.
+	For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in the space as a standalone device for \emph{channel shaping}.
+	Each of these applications has distinctive requirements and trade-offs, but they are based on the same physical principle and not mutually exclusive.
+	Imagine a future where 
 \end{section}
 
-\begin{section}{Objectives and Challenges}
+\begin{section}{Objectives}
 
@@
 \begin{section}{Publications}
-
 \end{section}

### 2024-03-06 content/chapter_1.tex
:construction: Update motivation

@@
 	This disruptive technology can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security improvement.
-	Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance with fewer active components, lower power consumption, and lower hardware complexity.
+	Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance using fewer active components, lower power consumption, and lower hardware complexity.
 	\gls{ris} is also different from conventional relays as it features no \gls{rf} chains, no symbol dependency, minimum signal processing, and negligible additional noise.
@@
 	Despite the great possibilities, the prototyping of \gls{ris} is still in its infancy and no commercial product has been released by the first quarter of 2024.
-	The transition from theory to practice is hindered by many challenges including channel acquisition, phase resolution, out-of-band response mitigation, placement optimization, and integration with existing systems.
-	Most importantly, a comprehensive understanding of its potential is still missing and the precise role it should play in future networks remains ambiguous.
-	For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in the space as a standalone device for \emph{channel shaping}.
-	Each of these applications has distinctive requirements and trade-offs, but they are based on the same physical principle and not mutually exclusive.
-	Imagine a future where 
+	The transition from theory to practice is hindered by many challenges including channel acquisition, scatter resolution, out-of-band response mitigation, placement optimization, and integration with existing systems.
+	Most importantly, a comprehensive understanding of its potential is still missing and the precise role it shall play in 6G remains ambiguous.
+	For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in space as a standalone device for \emph{channel shaping}.
+	These applications have distinctive requirements and trade-offs, but they are not mutually exclusive and can be evolved into a versatile tool that blurs the boundary between the network and environment.
+	Imagine a truly wireless future where most objects become aware and responsive by smartly exploiting the surrounding waves to energize itself, communicate with others, sense the environment, and support other devices when idle.
+	% can recycle the
+	% only a few ``source'' devices radiate and other objects can exploit the surrounding waves to energize itself, communicate with others, sense the environment, and support other devices when idle.
+	% the most devices can exploit the existing
 \end{section}

### 2024-03-07 content/chapter_1.tex
:construction: Update motivation

--- 2024-03-05 content/chapter_1.tex
@@
 	Together, they form a symbiotic relationship that can revolutionize the way we communicate, sense, and interact with the world.
-	One promising candidate to fulfill this vision is \gls{ris}, a programmable metasurface that recycles and redistributes the ambient electromagnetic waves for improved wireless performance.
-	It is a disruptive technology that can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security management.
-	Apart from the communications domain, \gls{ris} has also found applications in radar, imaging, and sensing, where it can be used to manipulate the electromagnetic waves for better resolution, penetration, and detection.
+	One promising candidate to fulfill this vision is \gls{ris}, a programmable metasurface that recycles and redistributes the electromagnetic waves in the air for improved wireless performance.
+	This disruptive technology can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security control.
+	Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance using fewer active components, lower power consumption, and lower hardware complexity.
+	\gls{ris} is also different from conventional relays as it features no \gls{rf} chains, no symbol dependency, minimum signal processing, and negligible additional noise.
+	Moreover, it can be easily deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
+	These unique characteristics make \gls{ris} a ubiquitous and cost-effective solution for future communication, sensing, and power transfer systems.
 
+	Despite the great possibilities, the prototyping of \gls{ris} is still in its infancy and no commercial product has been released by the first quarter of 2024.
+	The transition from theory to practice is hindered by many challenges, such as channel acquisition, response resolution, out-of-band response mitigation, placement optimization, and integration with existing systems.
+	Most importantly, a comprehensive understanding of its potential is still missing and the precise role it shall play in 6G remains ambiguous.
+	For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in space as a standalone device for \emph{channel shaping}.
+	These applications have distinctive requirements and trade-offs, but they are not mutually exclusive and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
+	Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
+	Only a few electromagnetic sources are needed, while most objects can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
+	To realize this vision, we need to:
+	\begin{itemize}
+		\item investigate the impact of \gls{ris} on various wireless applications and propose effective configurations for enhanced performance trade-off;
+		\item compare the principles of \gls{ris} with other scatter-based technologies and develop a novel protocol for beamforming-modulation integration;
+		\item rethink the architecture and modeling of \gls{ris} and explore its ultimate performance limits for further design evolution;
+	\end{itemize}
+	which are the motivations for Chapters \ref{ch:ris_aided_swipt}--\ref{ch:channel_shaping} of this thesis, respectively.
 \end{section}
 
-\begin{section}{Objectives and Challenges}
+\begin{section}{Objectives}
 

### 2024-03-08 content/chapter_1.tex
:construction: Update aims

@@
 
-\begin{section}{Motivation}
+\begin{section}{Motivation and Aims}
 	The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
@@
 	Only a few electromagnetic sources are needed, while most objects can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
-	To realize this vision, we need to:
+	This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.
+	In particular, Chapters \ref{ch:ris_aided_swipt}--\ref{ch:channel_shaping} respectively aim to:
 	\begin{itemize}
-		\item investigate the impact of \gls{ris} on various wireless applications and propose effective configurations for enhanced performance trade-off;
-		\item compare the principles of \gls{ris} with other scatter-based technologies and develop a novel protocol for beamforming-modulation integration;
-		\item rethink the architecture and modeling of \gls{ris} and explore its ultimate performance limits for further design evolution;
+		\item Investigate the impact of \gls{ris} on wireless information and power transfer and propose effective configurations for enhanced performance trade-off;
+		\item Compare the principles of \gls{ris} with various backscatter applications and develop a novel protocol for beamforming-modulation integration;
+		\item Rethink the architecture and modeling of \gls{ris} and characterize its ultimate channel shaping capabilities for further design reference.
 	\end{itemize}
-	which are the motivations for Chapters \ref{ch:ris_aided_swipt}--\ref{ch:channel_shaping} of this thesis, respectively.
 \end{section}
 
-\begin{section}{Objectives}
+\begin{section}{Summary of Contributions}
+	The key contributions of Chapter \ref{ch:ris_aided_swipt} are summarized as follows:
+	\begin{itemize}
+		\item Introduce \gls{ris} to a multi-antenna multi-carrier \gls{swipt} system with various receiver architectures;
+		\item Consider joint waveform and beamforming design for the proposed system under a practical energy harvester model;
+		\item Characterize the \gls{r-e} performance trade-off and provide insights into the transceiver design;
+		\item Formulate the optimization problem as harvested energy maximization subject to minimum communication rate constraints;
+		\item Propose local-optimal and low-complexity algorithms and evaluate their performance through numerical simulations;
+		\item Discuss the array gain for communication and the scaling order for power transfer in terms of the number of transmit antennas and \gls{ris} elements.
+	\end{itemize}
 
+	The key contributions of Chapter \ref{ch:ris_modulation} are summarized as follows:
 \end{section}
 
-\begin{section}{Outline and Contributions}
+\begin{section}{Outline}
 

### 2024-03-09 content/chapter_1.tex
:pencil: Update outline and contributions

--- 2024-03-07 content/chapter_1.tex
@@
 
-\chapter{Introduction}
+\chapter{Introduction}\label{ch:introduction}
 % \chapter{Summary of research problems and contribution}
@@
 	Only a few electromagnetic sources are needed, while most objects can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
-	To realize this vision, we need to:
-	\begin{itemize}
-		\item investigate the impact of \gls{ris} on various wireless applications and propose effective configurations for enhanced performance trade-off;
-		\item compare the principles of \gls{ris} with other scatter-based technologies and develop a novel protocol for beamforming-modulation integration;
-		\item rethink the architecture and modeling of \gls{ris} and explore its ultimate performance limits for further design evolution;
-	\end{itemize}
-	which are the motivations for Chapters \ref{ch:ris_aided_swipt}--\ref{ch:channel_shaping} of this thesis, respectively.
+	This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.
+	% In particular, Chapters \ref{ch:ris_aided_swipt}--\ref{ch:channel_shaping} respectively aim to:
+	% \begin{itemize}
+	% 	\item Investigate the impact of \gls{ris} on wireless information and power transfer and propose effective configurations for enhanced performance trade-off;
+	% 	\item Compare the principles of \gls{ris} with various backscatter applications and develop a novel protocol for beamforming-modulation integration;
+	% 	\item Rethink the architecture and modeling of \gls{ris} and characterize its ultimate channel shaping capabilities for further design reference.
+	% \end{itemize}
 \end{section}
 
-\begin{section}{Objectives}
+% \begin{section}{Summary of Contributions}
+% 	The key contributions of Chapter \ref{ch:ris_aided_swipt} are summarized as follows:
+% 	\begin{itemize}
+% 		\item Introduce \gls{ris} to a multi-antenna multi-carrier \gls{swipt} system with different receiver architectures;
+% 		\item Consider joint waveform and beamforming design for the proposed system under a practical energy harvester model;
+% 		\item Characterize the \gls{r-e} performance trade-off by maximizing harvested energy subject to different communication rate constraints;
+% 		\item Propose local-optimal and low-complexity algorithms and evaluate their narrow and wideband performance through numerical simulations;
+% 		\item Discuss the array gain for communication and the scaling order for power transfer in terms of the number of transmit antennas and \gls{ris} elements.
+% 	\end{itemize}
 
-\end{section}
+% 	The key contributions of Chapter \ref{ch:riscatter} are summarized as follows:
+% 	\begin{itemize}
+% 		\item Compare \gls{ris} with state-of-the-art \gls{bc} technologies and discuss the key properties of active and passive transmissions coexisting systems;
+% 		\item Unify \gls{ris} and \gls{bc} as one battery-free cognitive radio called RIScatter, where dispersed or co-located scatter nodes ride over an active primary link to modulate their own information and engineering the legacy channel simultaneously;
+% 		\item Integrate backscatter modulation and passive beamforming seamlessly into the input distribution design that allows arbitrary trade-off in between;
+% 		\item Propose a low-complexity cooperative receiver that sequentially decodes both coexisting links and exploits backscatter detection as part of channel training;
+% 		\item Characterize the achievable primary-backscatter rate region over different designs of input distribution at the scatter nodes, active beamforming at the \gls{ap}, and energy detector at the receiver;
+% 		\item Discuss the impact of practical factors such as the number of scatter nodes and states, transmit antenna size, backscatter symbol duration, and \gls{snr} on the system performance.
+% 	\end{itemize}
+
+% 	The key contributions of Chapter \ref{ch:channel_shaping} are summarized as follows:
+% 	\begin{itemize}
+% 		\item Quantify the capability of a passive \gls{ris} to reshape the \gls{mimo} \gls{pc} in terms of singular values via analytical bounds and numerical optimization;
+% 		\item Focus on a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior signal processing performance (subspace alignment and subchannel rearrangement) over the widely-adopted diagonal model;
+% 		\item Propose an efficient \gls{rcg} algorithm for general \gls{bd}-\gls{ris} optimization and provide low-complexity solutions for quadratic problems;
+% 		\item Characterize the Pareto frontiers of channel singular values and obtain power- and rate-optimal \gls{bd}-\gls{ris} configurations in \gls{mimo} \gls{pc};
+% 		\item Investigate the impact of \gls{bd}-\gls{ris} on leakage interference suppression and \gls{wsr} maximization in \gls{mimo} \gls{ic};
+% 		\item Discuss how channel shaping helps to decouple joint \gls{ris}-transceiver designs with comparable performance and significantly reduced complexity.
+% 	\end{itemize}
+% \end{section}
 
 \begin{section}{Outline and Contributions}
-
+	The thesis is outlined as follows:
+	\begin{itemize}
+		\item Chapter \ref{ch:introduction} introduces \gls{ris} as a promising technology for ambient wave redirection and highlights its potential benefits in future wireless networks.
+It discusses the motivation, objectives, and contributions of each research chapter.
+A list of publications is also provided.
+		\item Chapter \ref{ch:background} provides the necessary background knowledge for the subsequent chapters, including the fundamental concepts, operating principles, hardware implementation, signal and system models, performance metrics, and design challenges for \gls{ris}, \gls{wpt}, \gls{swipt}, \gls{bc}, and \gls{mimo} systems.
+It also reviews the state-of-the-art research in relevant topics and raise critical questions to be addressed in the following chapters.
+		\item Chapter \ref{ch:ris_aided_swipt} investigate the impact of \gls{ris} on wireless information and power transfer. The key contributions include:
+		\begin{itemize}
+			\item Introduce \gls{ris} to a multi-antenna multi-carrier \gls{swipt} system with different receiver architectures;
+			\item Consider joint waveform and beamforming design for the proposed system under a practical energy harvester model;
+			\item Characterize the \gls{r-e} performance trade-off by maximizing harvested energy subject to different communication rate constraints;
+			\item Propose local-optimal and low-complexity algorithms and evaluate their narrow and wideband performance through numerical simulations;
+			\item Discuss the array gain for communication and the scaling order for power transfer in terms of the number of transmit antennas and \gls{ris} elements.
+		\end{itemize}
+		\item Chapter \ref{ch:riscatter} develops a novel scatter protocol that integrates beamforming and modulation. The key contributions include:
+		\begin{itemize}
+			\item Provide an in-depth comparison of \gls{ris} with state-of-the-art \gls{bc} technologies and discuss the key properties of active and passive transmissions coexisting systems;
+			\item Unify \gls{ris} and \gls{bc} as one battery-free cognitive radio called RIScatter, where dispersed or co-located scatter nodes ride over an active primary link to modulate their own information and engineering the legacy channel simultaneously;
+			\item Integrate backscatter modulation and passive beamforming seamlessly into the input distribution design that allows arbitrary trade-off in between;
+			\item Propose a low-complexity cooperative receiver that sequentially decodes both coexisting links and exploits backscatter detection as part of channel training;
+			\item Characterize the achievable primary-backscatter rate region over different designs of input distribution at the scatter nodes, active beamforming at the \gls{ap}, and energy detector at the receiver;
+			\item Discuss the impact of practical factors such as the number of scatter nodes and states, transmit antenna size, backscatter symbol duration, and \gls{snr} on the system performance.
+		\end{itemize}
+		\item Chapter \ref{ch:channel_shaping} explores the ultimate channel shaping capabilities of \gls{ris} in \gls{mimo} systems. The key contributions include:
+		\begin{itemize}
+			\item Quantify the capability of a passive \gls{ris} to reshape the \gls{mimo} \gls{pc} in terms of singular values via analytical bounds and numerical optimization;
+			\item Focus on a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior signal processing performance (subspace alignment and subchannel rearrangement) over the widely-adopted diagonal model;
+			\item Propose an efficient \gls{rcg} algorithm for general \gls{bd}-\gls{ris} optimization and provide low-complexity solutions for quadratic problems;
+			\item Characterize the Pareto frontiers of channel singular values and obtain power- and rate-optimal \gls{bd}-\gls{ris} configurations in \gls{mimo} \gls{pc};
+			\item Investigate the impact of \gls{bd}-\gls{ris} on leakage interference suppression and \gls{wsr} maximization in \gls{mimo} \gls{ic};
+			\item Discuss how channel shaping helps to decouple joint \gls{ris}-transceiver designs with comparable performance and significantly reduced complexity.
+		\end{itemize}
+	\end{itemize}
 \end{section}
@@
 \begin{section}{Publications}
+	\begin{itemize}
+		\item \bibentry{Zhao2022}
+		\item \bibentry{Zhao2022a}
+		\item \bibentry{Zhao2023}
+		\item \bibentry{Zhao2024}
+	\end{itemize}
 \end{section}

### 2024-03-12 assets/chapter_2/nim_flows.tex
:pencil: Update introduction structure

\begin{tikzpicture}[background rectangle/.style={fill=blue!10}, show background rectangle]

	\def\f{1/exp(((\x)^2)/2)}

	\begin{axis}[thick,ticks=none,domain=-pi:pi,samples=100,axis x line*=middle,axis y line=none,xlabel=\empty,xmin=-4,xmax=4,ymax=4,ymin=-2]

		\addplot[smooth, color=blue] (\x,{sin((9*(deg(x))) )*\f}) coordinate[pos=0.42] (W);
		\addplot[smooth, color=black] (\x,\f) coordinate[pos=0.6] (E);
		\addplot[smooth, color=black] (\x,-\f);

	\end{axis}
	\draw[-latex,thick] (E) to ++(1,0) node[anchor=west] {energy flow};
	\draw[-latex,thick,blue] (W) to ++(-1,0) node[anchor=east,blue] {wave direction};
\end{tikzpicture}

### 2024-03-12 content/chapter_2.tex
:construction: Add motivation
:pencil: Update outline and contributions
:pencil: Update introduction structure

@@
 
-\chapter{Background and Literature Review}
+\chapter{Background and Literature Review}\label{ch:background}
 
@@
 		\begin{subsubsection}{Programmable Metamaterials}
-
+			Metamaterials refer to artificial structures engineered for unusual properties that may not be found in nature.
+			The concept was initially proposed by Victor Veselago in 1967, who conjectured the existence of mediums with negative dielectric constant $\epsilon < 0$ and negative permeability $\mu < 0$ \cite{Veselago1968}.
+			Such metamaterials are known as ``negative-index'' because the refraction index is defined as the \emph{negative} square root $n = - \sqrt{\epsilon \mu} < 0$, in order to be consistent with Maxwell's equations.
+			It was not until 1999 that their feasibility was experimentally demonstrated by John Pendry at Imperial College using split-ring resonators \cite{Pendry1999}.
+			Since then, metamaterials have attracted significant interests due to their counterintuitive properties, to name a few:
+			\begin{itemize}
+				\item \emph{Negative refraction:} As shown in Fig.
+\ref{fg:nim_refraction}, the incident and refracted rays stay at the same side of the normal axis.
+This phenomenon is in contrast to the usual refraction but can still be predicted from Snell's law
+				\begin{equation}
+					\frac{\sin \theta_1}{\sin \theta_2} = n.
+				\end{equation}
+				\begin{figure}[H]
+					\centering
+					\resizebox{0.5\columnwidth}{!}{
+						\input{assets/chapter_2/nim_refraction.tex}
+					}
+					\caption{Refraction of electromagnetic waves at the interface between a positive-index and a negative-index material.}
+					\label{fg:nim_refraction}
+				\end{figure}
+				\item \emph{Opposite wave direction:} As shown in Fig.
+\ref{fg:nim_flows}, the wave vector and energy flow (indicated by the Poynting vector) are opposite to each other in a negative-index material.
+This can be inferred from the electric field equation
+				\begin{equation}
+					\vec{E} = \vec{E}_0 \exp(\jmath k z - \jmath \omega t)
+				\end{equation}
+				where $k = k_0 n < 0$ is the wavenumber, $\vec{E}_0$ and $k_0$ are the free-space reference, $z$ is the propagation distance, $\omega$ is the angular frequency, and $t$ is the time.
+				Negative-index materials are thus also called ``left-hand'' because the propagation direction of the electric and magnetic fields can be determined by a left-hand rule.
+				\begin{figure}[H]
+					\centering
+					\resizebox{0.5\columnwidth}{!}{
+						\input{assets/chapter_2/nim_flows.tex}
+					}
+					\caption{Wave and energy flows in a negative-index material.}
+					\label{fg:nim_flows}
+				\end{figure}
+			\end{itemize}
 		\end{subsubsection}
@@
 	\begin{subsection}{Wave Scattering Model}
-		\begin{subsubsection}{Radiation Pattern}
-
-		\end{subsubsection}
-
-		\begin{subsubsection}{Circuit Topology}
-
-		\end{subsubsection}
-
 		\begin{subsubsection}{Active and Passive Elements}
@@
 
-		\begin{subsubsection}{}
+		\begin{subsubsection}{Independent Scattering: Diagonal Model}
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{Cooperative Scattering: \glsfmtfull{bd} Model}
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{Impact of Radiation Pattern and Circuit Topology}
 
@@
 \begin{section}{\glsfmtfull{wpt}}
-	\begin{subsection}{Building Blocks and Coupling Effect}
+	\begin{subsection}{Near- and Far-Field Techniques}
+
+	\end{subsection}
+
+	\begin{subsection}{Modules and Coupling Effect}
 		\begin{subsubsection}{Block Diagram}
@@
 
-		\begin{subsubsection}{Coupling between Modules}
+		\begin{subsubsection}{Blockwise Coupling}
 
@@
 	\begin{subsection}{Non-Linear Harvester Behavior}
-		\begin{subsubsection}{Rectifier Circuit Design}
+		\begin{subsubsection}{Rectifier Circuits}
 
@@
 \begin{section}{\glsfmtfull{mimo}}
+	\begin{subsection}{\glsfmtfull{pc}: Channel Shaping}
 
+	\end{subsection}
+
+	\begin{subsection}{\glsfmtfull{ic}: Interference Alignment}
+
+	\end{subsection}
 \end{section}

### 2024-03-13 content/chapter_1.tex
:pencil: Update introduction structure
:pencil: Update background and motivation

@@
 
-\begin{section}{Motivation}
-	The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
+\begin{section}{Background and Motivation}
+	The quest for better wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
 	Great successes have been made at the transmitter and receiver sides over the past century, and the communications society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
-	This is made possible by the latest advances in machine learning and programmable metamaterials --- the former enables the network to learn from the environment while the latter allows the environment to adapt to the network.
-	Together, they form a symbiotic relationship that can revolutionize the way we communicate, sense, and interact with the world.
-	One promising candidate to fulfill this vision is \gls{ris}, a programmable metasurface that recycles and redistributes the electromagnetic waves in the air for improved wireless performance.
-	This disruptive technology can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security control.
-	Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance using fewer active components, lower power consumption, and lower hardware complexity.
-	\gls{ris} is also different from conventional relays as it features no \gls{rf} chains, no symbol dependency, minimum signal processing, and negligible additional noise.
-	Moreover, it can be easily deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
-	These unique characteristics make \gls{ris} a ubiquitous and cost-effective solution for future communication, sensing, and power transfer systems.
+	By 2025, global mobile data traffic is expected to reach {607} exabytes per year \cite{Tariq2020} while the number of connected devices may exceed {75} billion \cite{Georgiev2024}.
+	At the same time, wireless applications are also evolving in various forms to address world-changing incidents like COVID-19, climate change, and \gls{ai} revolution.
+	An initial attempt was made in 5G where the network prioritizes among high-throughput, ubiquitous-coverage, high-reliability, low-latency, massive-connectivity, and energy-efficient services \cite{Shafi2017}.
+	However, the desire of human and machine for better communication shows no signs of slowing down.
+	Emerging applications such as smart cities, autonomous driving, telemedicine, extended reality, federated learning, and generative intelligence are calling for a stronger and smarter wireless infrastructure.
+	It is envisioned that 6G will be designed to meet the following requirements \cite{Tataria2021,Alsabah2021,Jiang2021}:
+	\begin{itemize}
+		\item \emph{Throughput}: The network would be able to provide a peak data rate of 1 Tbps and an average data rate of 100 Gbps per user.
+		\item \emph{Latency}: Sub-millisecond end-to-end latency would be achieved for low-latency applications like autonomous driving and remote surgery.
+		\item \emph{Reliability}: A success rate of 99.9999\% would be guaranteed for ultra-reliable applications like industrial automation and cooperative robotics.
+		\item \emph{Connectivity}: The number of connected devices per kilometer square would be increased to 10 million for supporting \gls{ioe}.
+		\item \emph{Mobility}: Commercial airlines with a maximal velocity of 1000 km/h would be the target application scenario.
+		\item \emph{Energy efficiency}: Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by 90\% in 6G to reduce the carbon footprint.
+		\item \emph{Positioning accuracy}: Thanks to THz base stations, a 3D positioning accuracy of centimeter level may be achieved for indoor and outdoor environments.
+		\item \emph{Coverage}: A terrestrial-satellite-aerial integrated network would be able to provide a ubiquitous and uniform coverage for urban, rural, and remote areas.
+		\item \emph{Security and privacy}: Physical-layer security can be improved with narrower beams at higher frequencies and destructive scattering at the environment.
+Privacy can be enhanced with federated learning and homomorphic encryption.
+		% \item \emph{Superintelligent}: The network may integrate human, machine, environment, and \gls{ai} into a superintelligent system that can sense, communicate, and act in a coordinated manner.
+	\end{itemize}
 
-	Despite the great possibilities, the prototyping of \gls{ris} is still in its infancy and no commercial product has been released by the first quarter of 2024.
-	The transition from theory to practice is hindered by many challenges, such as channel acquisition, response resolution, out-of-band response mitigation, placement optimization, and integration with existing systems.
-	Most importantly, a comprehensive understanding of its potential is still missing and the precise role it shall play in 6G remains ambiguous.
-	For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in space as a standalone device for \emph{channel shaping}.
-	These applications have distinctive requirements and trade-offs, but they are not mutually exclusive and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
-	Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
-	Only a few electromagnetic sources are needed, while most objects can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
-	This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.
-	% In particular, Chapters \ref{ch:ris_aided_swipt}--\ref{ch:channel_shaping} respectively aim to:
-	% \begin{itemize}
-	% 	\item Investigate the impact of \gls{ris} on wireless information and power transfer and propose effective configurations for enhanced performance trade-off;
-	% 	\item Compare the principles of \gls{ris} with various backscatter applications and develop a novel protocol for beamforming-modulation integration;
-	% 	\item Rethink the architecture and modeling of \gls{ris} and characterize its ultimate channel shaping capabilities for further design reference.
-	% \end{itemize}
+	% From Wireless Research for IoT to Integrating Human, Generative AI and Communications Network for Superintelligent Systems
+	% Enabling Effective and Efficient Federated Learning at Future Network Edge
+	% Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
+	% This is made possible by the latest advances in machine learning and programmable metamaterials --- the former enables the network to learn from the environment while the latter allows the environment to adapt to the network.
+	% Together, they form a symbiotic relationship that can revolutionize the way we communicate, sense, and interact with the world.
+	% One promising candidate to fulfill this vision is \gls{ris}, a programmable metasurface that recycles and redistributes the electromagnetic waves in the air for improved wireless performance.
+	% This disruptive technology can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security control.
+	% Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance using fewer active components, lower power consumption, and lower hardware complexity.
+	% \gls{ris} is also different from conventional relays as it features no \gls{rf} chains, no symbol dependency, minimum signal processing, and negligible additional noise.
+	% Moreover, it can be easily deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
+	% These unique characteristics make \gls{ris} a ubiquitous and cost-effective solution for future communication, sensing, and power transfer systems.
+
+	% Despite the great possibilities, the prototyping of \gls{ris} is still in its infancy and no commercial product has been released by the first quarter of 2024.
+	% The transition from theory to practice is hindered by many challenges, such as channel acquisition, response resolution, out-of-band response mitigation, placement optimization, and integration with existing systems.
+	% Most importantly, a comprehensive understanding of its potential is still missing and the precise role it shall play in 6G remains ambiguous.
+	% For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in space as a standalone device for \emph{channel shaping}.
+	% These applications have distinctive requirements and trade-offs, but they are not mutually exclusive and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
+	% Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
+	% Only a few electromagnetic sources are needed, while most objects can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
+	% This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.
 \end{section}
 
-% \begin{section}{Summary of Contributions}
-% 	The key contributions of Chapter \ref{ch:ris_aided_swipt} are summarized as follows:
-% 	\begin{itemize}
-% 		\item Introduce \gls{ris} to a multi-antenna multi-carrier \gls{swipt} system with different receiver architectures;
-% 		\item Consider joint waveform and beamforming design for the proposed system under a practical energy harvester model;
-% 		\item Characterize the \gls{r-e} performance trade-off by maximizing harvested energy subject to different communication rate constraints;
-% 		\item Propose local-optimal and low-complexity algorithms and evaluate their narrow and wideband performance through numerical simulations;
-% 		\item Discuss the array gain for communication and the scaling order for power transfer in terms of the number of transmit antennas and \gls{ris} elements.
-% 	\end{itemize}
+\begin{section}{Overview on \glsfmtfull{ris}}
+	\begin{subsection}{Background}
 
-% 	The key contributions of Chapter \ref{ch:riscatter} are summarized as follows:
-% 	\begin{itemize}
-% 		\item Compare \gls{ris} with state-of-the-art \gls{bc} technologies and discuss the key properties of active and passive transmissions coexisting systems;
-% 		\item Unify \gls{ris} and \gls{bc} as one battery-free cognitive radio called RIScatter, where dispersed or co-located scatter nodes ride over an active primary link to modulate their own information and engineering the legacy channel simultaneously;
-% 		\item Integrate backscatter modulation and passive beamforming seamlessly into the input distribution design that allows arbitrary trade-off in between;
-% 		\item Propose a low-complexity cooperative receiver that sequentially decodes both coexisting links and exploits backscatter detection as part of channel training;
-% 		\item Characterize the achievable primary-backscatter rate region over different designs of input distribution at the scatter nodes, active beamforming at the \gls{ap}, and energy detector at the receiver;
-% 		\item Discuss the impact of practical factors such as the number of scatter nodes and states, transmit antenna size, backscatter symbol duration, and \gls{snr} on the system performance.
-% 	\end{itemize}
+	\end{subsection}
 
-% 	The key contributions of Chapter \ref{ch:channel_shaping} are summarized as follows:
-% 	\begin{itemize}
-% 		\item Quantify the capability of a passive \gls{ris} to reshape the \gls{mimo} \gls{pc} in terms of singular values via analytical bounds and numerical optimization;
-% 		\item Focus on a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior signal processing performance (subspace alignment and subchannel rearrangement) over the widely-adopted diagonal model;
-% 		\item Propose an efficient \gls{rcg} algorithm for general \gls{bd}-\gls{ris} optimization and provide low-complexity solutions for quadratic problems;
-% 		\item Characterize the Pareto frontiers of channel singular values and obtain power- and rate-optimal \gls{bd}-\gls{ris} configurations in \gls{mimo} \gls{pc};
-% 		\item Investigate the impact of \gls{bd}-\gls{ris} on leakage interference suppression and \gls{wsr} maximization in \gls{mimo} \gls{ic};
-% 		\item Discuss how channel shaping helps to decouple joint \gls{ris}-transceiver designs with comparable performance and significantly reduced complexity.
-% 	\end{itemize}
-% \end{section}
+	\begin{subsection}{Concept}
+
+	\end{subsection}
+
+	\begin{subsection}{Characteristics}
+
+	\end{subsection}
+
+	\begin{subsection}{Applications}
+
+	\end{subsection}
+\end{section}
 

### 2024-03-13 misc/glossaries.tex
:construction: Update hooks for first chapter
:construction: Add section titles
:pencil: Update outline and contributions
:pencil: Update background and motivation

--- 2024-02-29 glossaries.tex
@@
+\newacronym{ai}{AI}{Artificial Intelligence}
 \newacronym{af}{AF}{Amplify-and-Forward}
@@
 \newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
-\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
+\newacronym{bbc}{BBC}{Bistatic \glsfmtlong{bc}}
 \newacronym{bcd}{BCD}{Block Coordinate Descent}
@@
 \newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
-\newacronym{csit}{CSIT}{\gls{csi} at the Transmitter}
+\newacronym{csit}{CSIT}{\glsfmtlong{csi} at the Transmitter}
 \newacronym{csi}{CSI}{Channel State Information}
@@
 \newacronym{iid}{i.i.d.}{independent and identically distributed}
+\newacronym{im}{IM}{Index Modulation}
 \newacronym{ioe}{IoE}{Internet of Everything}
@@
 \newacronym{mac}{MAC}{Multiple Access Channel}
-\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
+\newacronym{mbc}{MBC}{Monostatic \glsfmtlong{bc}}
 \newacronym{mc}{MC}{Multiplication Coding}
@@
 \newacronym{mse}{MSE}{Mean-Square Error}
-\newacronym{nlos}{NLoS}{Non-\gls{los}}
+\newacronym{nlos}{NLoS}{Non-\glsfmtlong{los}}
 \newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
@@
 \newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
-\newacronym{rfid}{RFID}{\gls{rf} Identification}
+\newacronym{rfid}{RFID}{\glsfmtlong{rf} Identification}
 \newacronym{rf}{RF}{Radio-Frequency}
@@
 \newacronym{wpt}{WPT}{Wireless Power Transfer}
+\newacronym{wsr}{WSR}{Weighted Sum-Rate}
 \newacronym{zf}{ZF}{Zero-Forcing}
+\newacronym{lc}{LC}{Low-Complexity}
+
+\newacronym{embb}{eMBB}{enhanced Mobile Broadband}
+\newacronym{urllc}{URLLC}{Ultra-Reliable Low-Latency Communication}
+\newacronym{mmtc}{mMTC}{massive Machine-Type Communication}
 
@@
 \nomenclature[o-d]{$(\cdot)^\dagger$}{Moore-Penrose inverse}
-\nomenclature[o-e]{$(\cdot)^+$}{Ramp functio $\max(0, \cdot)$}
+\nomenclature[o-e]{$(\cdot)^+$}{Ramp function $\max(0, \cdot)$}
 \nomenclature[o-f]{$\lvert \cdot \rvert$}{Absolute value of a complex number}
@@
 \nomenclature[o-t]{$\mathbb{E}(\cdot)$}{Expectation operator}
-\nomenclature[o-u]{$\mathbb{A}(\cdot)$}{Extracts the \glsdesc{dc} component of a signal}
+\nomenclature[o-u]{$\mathbb{A}(\cdot)$}{Extracts the \glsfmtlong{dc} component of a signal}
 \nomenclature[o-v]{$\odot$}{Hadamard product}
@@
 \nomenclature[r-a]{$\sim$}{Follows a distribution}
-\nomenclature[r-b]{$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$}{Multivariate \glsdesc{cscg} with covariance $\mathbf{\Sigma}$}
+\nomenclature[r-b]{$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$}{Multivariate \glsfmtlong{cscg} with covariance $\mathbf{\Sigma}$}
 

### 2024-03-14 content/chapter_1.tex
:pencil: Update motivation and add concept

@@
 	By 2025, global mobile data traffic is expected to reach {607} exabytes per year \cite{Tariq2020} while the number of connected devices may exceed {75} billion \cite{Georgiev2024}.
-	At the same time, wireless applications are also evolving in various forms to address world-changing incidents like COVID-19, climate change, and \gls{ai} revolution.
+	At the same time, wireless applications are also evolving in various forms to address world-changing incidents like COVID-19, climate change, geopolitical tensions, and \gls{ai} revolution.
 	An initial attempt was made in 5G where the network prioritizes among high-throughput, ubiquitous-coverage, high-reliability, low-latency, massive-connectivity, and energy-efficient services \cite{Shafi2017}.
@@
 		\item \emph{Mobility}: Commercial airlines with a maximal velocity of 1000 km/h would be the target application scenario.
-		\item \emph{Energy efficiency}: Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by 90\% in 6G to reduce the carbon footprint.
+		\item \emph{Energy efficiency}: Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by over 90\% in 6G to reduce carbon footprints.
 		\item \emph{Positioning accuracy}: Thanks to THz base stations, a 3D positioning accuracy of centimeter level may be achieved for indoor and outdoor environments.
-		\item \emph{Coverage}: A terrestrial-satellite-aerial integrated network would be able to provide a ubiquitous and uniform coverage for urban, rural, and remote areas.
+		\item \emph{Coverage}: Poor coverage has been another bottleneck for 5G.
+A terrestrial-satellite-aerial integrated network would provide a ubiquitous and uniform coverage for urban, rural, and remote areas.
 		\item \emph{Security and privacy}: Physical-layer security can be improved with narrower beams at higher frequencies and destructive scattering at the environment.
@@
 
-	% From Wireless Research for IoT to Integrating Human, Generative AI and Communications Network for Superintelligent Systems
-	% Enabling Effective and Efficient Federated Learning at Future Network Edge
-	% Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
-	% This is made possible by the latest advances in machine learning and programmable metamaterials --- the former enables the network to learn from the environment while the latter allows the environment to adapt to the network.
-	% Together, they form a symbiotic relationship that can revolutionize the way we communicate, sense, and interact with the world.
-	% One promising candidate to fulfill this vision is \gls{ris}, a programmable metasurface that recycles and redistributes the electromagnetic waves in the air for improved wireless performance.
-	% This disruptive technology can be integrated into the next-generation wireless systems for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security control.
-	% Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance using fewer active components, lower power consumption, and lower hardware complexity.
-	% \gls{ris} is also different from conventional relays as it features no \gls{rf} chains, no symbol dependency, minimum signal processing, and negligible additional noise.
-	% Moreover, it can be easily deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
-	% These unique characteristics make \gls{ris} a ubiquitous and cost-effective solution for future communication, sensing, and power transfer systems.
+	Beyond the statistical requirements above, the next-generation wireless network is desired to integrate human, machine, environment, and \gls{ai} seamlessly for a harmonic ecosphere.
+	This paradigm shift from \emph{connectivity} to \emph{intelligence} is fueled by the latest advances in machine learning (theory) and programmable metamaterials (hardware).
+	The former enables the network to understand the environment while the latter evolves the environment from a chaotic medium to a conscious agent that can serve on demand.
+	Together, they form a symbiotic relationship with the potential to revolutionize how the world energize, sense, communicate, and interact.
+
+	One promising candidate within this 6G vision is \gls{ris}, a programmable metasurface that recycles and redistributes the electromagnetic waves in the air for improved wireless performance.
+	It could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or simply placed in space as a standalone device for \emph{channel shaping}.
+	These applications have distinctive requirements and trade-offs, but the operation principles are the same and those roles are not mutually exclusive.
+	Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
+	Only a few active radiating sources (like the sun) are needed, while most objects (like the universe) can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
+	This vision motivates three research questions to be addressed in this thesis:
+	\begin{itemize}
+		\item \emph{How does \gls{ris} impact different wireless applications such as communication and far-field power transfer?}
+		\item \emph{Is it possible to integrate \gls{ris} with \gls{bc} into a versatile tool that blurs the boundary between the network and environment?}
+		\item \emph{What is the ultimate limit of channel reshaping through passive \gls{ris} and what are the implications on transceiver designs?}
+	\end{itemize}
+
+	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications in the next section.
+	A detailed literature review and technical discussion on \gls{ris} and other topics will be reserved for Chapter \ref{ch:background}.
+\end{section}
+
+\begin{section}{Overview on \glsfmtfull{ris}}
+	% and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
+	% This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.
 
@@
 	% Most importantly, a comprehensive understanding of its potential is still missing and the precise role it shall play in 6G remains ambiguous.
-	% For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in space as a standalone device for \emph{channel shaping}.
-	% These applications have distinctive requirements and trade-offs, but they are not mutually exclusive and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
-	% Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
-	% Only a few electromagnetic sources are needed, while most objects can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
-	% This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.
-\end{section}
-
-\begin{section}{Overview on \glsfmtfull{ris}}
-	\begin{subsection}{Background}
-
-	\end{subsection}
 
 	\begin{subsection}{Concept}
-
+		\gls{ris} is commonly known as a planar surface involving numerous wave scattering elements (a.k.a.
+unit cells, reflective patches), whose amplitude and phase responses can be engineered in real-time to achieve a desired radiation pattern.
+		As shown in Fig. \ref{fg:ris_architecture}, its typical architecture consists of three stacked layers and a controller \cite{Wu2020}.
+		The top layer is a two-dimensional array of scattering elements printed on a dielectric substrate.
+		The elements directly interact with the impinging waves, which are usually fabricated from metamaterial or patch/dipole antennas with sub-wavelength dimension and spacing.
+		The middle layer is a copper ground plate that provides voltage reference and avoids signal leakage.
+		The bottom later is a circuit board that associate each element with adjustable components like varactor and \gls{pin} diodes \cite{Dai2020}.
+		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with other devices in the network.
+		By adjusting the scatter response of each element, the \gls{ris} can effectively manipulate the wavefront and thus improve the ambient wireless environment.
+		\begin{figure}
+			\centering
+			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
+			\caption{A typical architecture of \gls{ris} \cite{Wu2020}.}
+			\label{fg:ris_architecture}
+		\end{figure}
 	\end{subsection}
@@
 	\begin{subsection}{Characteristics}
-
+		The key characteristics of \gls{ris} are summarized as follows:
+		\begin{itemize}
+			\item \emph{Passive and environmental-friendly:} \gls{ris} reflects the incident waves in a passive manner and does not require dedicated \gls{rf} chains.\footnote{The controller may be implemented with low-power components and powered by ambient energy.} This is different from \gls{af} relays that require power-hungry oscillators and introduces additional thermal noise.
+			\item \emph{Flexible:} It provides a software configurable environment that can be adapted for different applications and scenarios.
+This is different from reflectarray \cite{Nayeri2018} and frequency selective surfaces \cite{Anwar2018} with predefined radiation patterns and frequency response.
+			\item \emph{Full-duplex and universal:} This physical-layer solution can simultaneously benefit downlink and uplink thanks to channel reciprocity \cite{Wu2021}, and simultaneously support communication, sensing, and power transfer without self-interference.
+This is different from \gls{df} relays that are designed for a specific communication link and suffers from packet delays.
+			\item \emph{Low-cost and conformal:} It can be manufactured from low-cost materials and deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
+This is different from conventional multi-antenna systems that features complex hardware and bulky structures.
+		\end{itemize}
 	\end{subsection}
@@
 
+	% Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance using fewer active components, lower power consumption, and lower hardware complexity.
+	% It also features no \gls{rf} chains, no symbol dependency, minimum signal processing, negligible additional noise, and can be deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
+	% These unique characteristics make \gls{ris} a ubiquitous and cost-effective solution for future wireless communication, sensing, and power transfer systems.
+
+	% This disruptive technology can be introduced to legacy networks for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security control.
 	\end{subsection}

### 2024-03-16 content/chapter_1.tex
:pencil: Add applications

@@
 
-	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications in the next section.
+	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications.
 	A detailed literature review and technical discussion on \gls{ris} and other topics will be reserved for Chapter \ref{ch:background}.
@@
 \begin{section}{Overview on \glsfmtfull{ris}}
+
+	% Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance using fewer active components, lower power consumption, and lower hardware complexity.
+	% It also features no \gls{rf} chains, no symbol dependency, minimum signal processing, negligible additional noise, and can be deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
+	% These unique characteristics make \gls{ris} a ubiquitous and cost-effective solution for future wireless communication, sensing, and power transfer systems.
+
 	% and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
@@
 		The middle layer is a copper ground plate that provides voltage reference and avoids signal leakage.
-		The bottom later is a circuit board that associate each element with adjustable components like varactor and \gls{pin} diodes \cite{Dai2020}.
-		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with other devices in the network.
-		By adjusting the scatter response of each element, the \gls{ris} can effectively manipulate the wavefront and thus improve the ambient wireless environment.
+		The bottom later is a circuit board that associate each element with adjustable components, such as varactor and \gls{pin} diodes \cite{Dai2020}.
+		It also hosts a \gls{fpga} controller that controls the circuit and coordinate with transceivers in the network.
+		By adjusting the scatter response of all elements, the \gls{ris} can effectively manipulate the wavefront for a constructive or destructive superposition and thus improve the ambient wireless environment.
 		\begin{figure}
@@
 			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
-			\caption{A typical architecture of \gls{ris} \cite{Wu2020}.}
+			\caption{A typical architecture of \gls{ris}. Modified from \cite{Wu2020}.}
 			\label{fg:ris_architecture}
@@
 			\item \emph{Flexible:} It provides a software configurable environment that can be adapted for different applications and scenarios.
-This is different from reflectarray \cite{Nayeri2018} and frequency selective surfaces \cite{Anwar2018} with predefined radiation patterns and frequency response.
-			\item \emph{Full-duplex and universal:} This physical-layer solution can simultaneously benefit downlink and uplink thanks to channel reciprocity \cite{Wu2021}, and simultaneously support communication, sensing, and power transfer without self-interference.
+This is different from conventional reflectarray \cite{Nayeri2018} and frequency selective surfaces \cite{Anwar2018} with predefined radiation patterns and frequency response.
+			\item \emph{Full-duplex and universal:} This physical-layer solution can simultaneously support communication, sensing, and power transfer without self-interference.
+Thanks to channel reciprocity, the optimal configuration for downlink and uplink coincide with each other \cite{Wu2021}.
 This is different from \gls{df} relays that are designed for a specific communication link and suffers from packet delays.
@@
 	\begin{subsection}{Applications}
+		The channel manipulation capability of \gls{ris} unlocks a wide range of unprecedented applications, such as signal enhancement \cite{Wu2019}, interference suppression \cite{Jiang2022}, blockage bypassing \cite{Ghatak2021}, coverage extension \cite{Zeng2021}, and security control \cite{Almohamad2020}.
+		It also has the potential to convey additional information \cite{Ye2022}, compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for multi-antenna systems \cite{Ozdogan2020a}, and create artificial time diversity for multi-user orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple accesses.
 
-	% Compared with traditional multi-antenna techniques, \gls{ris} has the potential to achieve a similar performance using fewer active components, lower power consumption, and lower hardware complexity.
-	% It also features no \gls{rf} chains, no symbol dependency, minimum signal processing, negligible additional noise, and can be deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
-	% These unique characteristics make \gls{ris} a ubiquitous and cost-effective solution for future wireless communication, sensing, and power transfer systems.
-
-	% This disruptive technology can be introduced to legacy networks for signal enhancement, interference suppression, scattering enrichment, blockage bypassing, coverage extension, and security control.
+		Those fancy characteristics and applications of \gls{ris} have also attracted significant attention from the industry.
+		The first public testing attempt was made in 2018 by NTT Docomo and Metawave, which demonstrated a metasurface reflectarray in the FR2 band of 5G can boost a downlink data rate from \qty{60}{Mbps} to \qty{560}{Mbps} \cite{Liu2022b}.
+		Later in 2020, NTT Docomo developed a transparent dynamic \gls{ris} that can allows 28GHz signals to reflect or pass through with negligible power loss.
+		A regional ``\gls{ris} alliance'' was formed in 2021 by Chinese companies and institutes including ZTE, China Mobile, and CAICT, which soon released a white paper \cite{Rista2023} to promote the technology and standardization.
+		In December 2022, ITU-R drafted a recommendation report for IMT-2030 (6G) \cite{Itu2022} that marks \gls{ris} as a key technology to enhance the radio interface for multiple physical dimension transmission.
+		These developments showcase the rapid progress of \gls{ris} from theoretical concept to practical implementation, paving the way for its integration into the next-generation network.
 	\end{subsection}
@@
 	\begin{itemize}
-		\item Chapter \ref{ch:introduction} introduces \gls{ris} as a promising technology for ambient wave redirection and highlights its potential benefits in future wireless networks.
-It discusses the motivation, objectives, and contributions of each research chapter.
+		\item Chapter \ref{ch:introduction} provides an overview of the thesis.
+It introduces the background and motivation, discusses the characteristics and applications of \gls{ris}, and summarizes the objectives and contributions of each research chapter.
 A list of publications is also provided.
-		\item Chapter \ref{ch:background} provides the necessary background knowledge for the subsequent chapters, including the fundamental concepts, operating principles, hardware implementation, signal and system models, performance metrics, and design challenges for \gls{ris}, \gls{wpt}, \gls{swipt}, \gls{bc}, and \gls{mimo} systems.
+		\item Chapter \ref{ch:background} provides the necessary background knowledge for the subsequent chapters, including the fundamental principles, hardware implementation, signal and system models, performance metrics, and design challenges for \gls{ris}, \gls{wpt}, \gls{swipt}, \gls{bc}, and \gls{mimo} systems.
 It also reviews the state-of-the-art research in relevant topics and raise critical questions to be addressed in the following chapters.

### 2024-03-16 content/chapter_1.tex
:lipstick: Add reflected wave plots

@@
 
-\begin{section}{Background and Motivation}
+\begin{section}{Motivation}
 	The quest for better wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
@@
 unit cells, reflective patches), whose amplitude and phase responses can be engineered in real-time to achieve a desired radiation pattern.
+		It behaves like a delicate \gls{rf} mirror with adjustable curvature and orientation, which allows the incident signals to be focused and redirected in a particular direction.
 		As shown in Fig. \ref{fg:ris_architecture}, its typical architecture consists of three stacked layers and a controller \cite{Wu2020}.
@@
 		\item Chapter \ref{ch:introduction} provides an overview of the thesis.
-It introduces the background and motivation, discusses the characteristics and applications of \gls{ris}, and summarizes the objectives and contributions of each research chapter.
+It introduces the motivation and objectives, discusses the characteristics and applications of \gls{ris}, and summarizes the topics and contributions of each research chapter.
 A list of publications is also provided.

### 2024-03-16 content/chapter_2.tex
:pencil: Update motivation and add concept
:lipstick: Add reflected wave plots

@@
 \begin{section}{\glsfmtfull{ris}}
-	% \begin{subsection}{Programmable Metamaterials}
-
-	% \end{subsection}
-
-	\begin{subsection}{Hardware Implementation}
-		\begin{subsubsection}{Programmable Metamaterials}
+	\begin{subsection}{Programmable Metamaterials}
 		Metamaterials refer to artificial structures engineered for unusual properties that may not be found in nature.
@@
 				\centering
-					\resizebox{0.5\columnwidth}{!}{
+				\subfloat[Negative Index Material\label{fg:nim_refraction}]{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_2/nim_refraction.tex}
 					}
-					\caption{Refraction of electromagnetic waves at the interface between a positive-index and a negative-index material.}
-					\label{fg:nim_refraction}
+				}
+				\subfloat[Positive Index Material\label{fg:pim_refraction}]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/chapter_2/pim_refraction.tex}
+					}
+				}
+				\caption{Refraction in negative and positive index materials. Incident and refracted rays stay at the same side of the normal axis in a negative-index material.}
 			\end{figure}
@@
 			\end{equation}
-				where $k = k_0 n < 0$ is the wavenumber, $\vec{E}_0$ and $k_0$ are the free-space reference, $z$ is the propagation distance, $\omega$ is the angular frequency, and $t$ is the time.
+			where $k = k_0 n < 0$ is the wavenumber, $\vec{E}_0$ and $k_0$ are the free-space electric field and wavenumber reference, $z$ is the propagation distance, $\omega$ is the angular frequency, and $t$ is the time.
 			Negative-index materials are thus also called ``left-hand'' because the propagation direction of the electric and magnetic fields can be determined by a left-hand rule.
@@
 				}
-					\caption{Wave and energy flows in a negative-index material.}
+				\caption{Wave and energy have opposite directions in a negative-index material.}
 				\label{fg:nim_flows}
 			\end{figure}
+
 		\end{itemize}
-		\end{subsubsection}
 
-		\begin{subsubsection}{Physical Architecture}
-
-		\end{subsubsection}
+		% TODO Programmable
+		\begin{figure}[H]
+			\centering
+			\subfloat[Incident Wave\label{fg:wave_incident}]{
+				\resizebox{!}{4.04cm}{
+					\input{assets/chapter_2/wave_incident.tex}
+				}
+			}
+			\subfloat[Reflected Wave\label{fg:wave_reflected}]{
+				\resizebox{!}{4cm}{
+					\input{assets/chapter_2/wave_reflected.tex}
+				}
+			}
+			\caption{Incident and reflected waves in a programmable metamaterial.}
+		\end{figure}
 	\end{subsection}
@@
 
-	\begin{subsection}{Comparison with Reflectarrays and Relays}
-		\begin{subsubsection}{Functionality}
-
-		\end{subsubsection}
-
-		\begin{subsubsection}{Reconfigurability}
-
-		\end{subsubsection}
-
-		\begin{subsubsection}{Complexity}
-
-		\end{subsubsection}
-
-		\begin{subsubsection}{Power Consumption}
-
-		\end{subsubsection}
-
-		\begin{subsubsection}{Dimension and Cost}
-
-		\end{subsubsection}
-
-		\begin{subsubsection}{Applications}
-
-		\end{subsubsection}
-	\end{subsection}
 \end{section}

### 2024-03-16 content/chapter_2.tex
:lipstick: Add refracted wave plots

@@
 				\centering
-				\resizebox{0.5\columnwidth}{!}{
+				\subfloat[Negative Index Material\label{fg:nim_flows}]{
+					\resizebox{!}{2cm}{
 							\input{assets/chapter_2/nim_flows.tex}
 					}
+				}
+				\subfloat[Positive Index Material\label{fg:pim_flows}]{
+					\resizebox{!}{2cm}{
+						\input{assets/chapter_2/pim_flows.tex}
+					}
+				}
 				\caption{Wave and energy have opposite directions in a negative-index material.}
-				\label{fg:nim_flows}
+			\end{figure}
+
+			\begin{figure}[H]
+				\centering
+				\subfloat[Negative Index Material\label{fg:nim_focus}]{
+					\resizebox{0.45\columnwidth}{!}{
+							\input{assets/chapter_2/nim_focus.tex}
+					}
+				}
+				\subfloat[Positive Index Material\label{fg:pim_diverge}]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/chapter_2/pim_diverge.tex}
+					}
+				}
+				\caption{Beams diverging from a point source is set in reverse and converges back to a point.}
 			\end{figure}

### 2024-03-17 content/chapter_1.tex
:pencil: Add programmable metamaterials

@@
 	\begin{itemize}
-		\item \emph{Throughput}: The network would be able to provide a peak data rate of 1 Tbps and an average data rate of 100 Gbps per user.
-		\item \emph{Latency}: Sub-millisecond end-to-end latency would be achieved for low-latency applications like autonomous driving and remote surgery.
-		\item \emph{Reliability}: A success rate of 99.9999\% would be guaranteed for ultra-reliable applications like industrial automation and cooperative robotics.
-		\item \emph{Connectivity}: The number of connected devices per kilometer square would be increased to 10 million for supporting \gls{ioe}.
-		\item \emph{Mobility}: Commercial airlines with a maximal velocity of 1000 km/h would be the target application scenario.
-		\item \emph{Energy efficiency}: Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by over 90\% in 6G to reduce carbon footprints.
-		\item \emph{Positioning accuracy}: Thanks to THz base stations, a 3D positioning accuracy of centimeter level may be achieved for indoor and outdoor environments.
-		\item \emph{Coverage}: Poor coverage has been another bottleneck for 5G.
+		\item \emph{Throughput:} The network would be able to provide a peak data rate of 1 Tbps and an average data rate of 100 Gbps per user.
+		\item \emph{Latency:} Sub-millisecond end-to-end latency would be achieved for low-latency applications like autonomous driving and remote surgery.
+		\item \emph{Reliability:} A success rate of 99.9999\% would be guaranteed for ultra-reliable applications like industrial automation and cooperative robotics.
+		\item \emph{Connectivity:} The number of connected devices per kilometer square would be increased to 10 million for supporting \gls{ioe}.
+		\item \emph{Mobility:} Commercial airlines with a maximal velocity of 1000 km/h would be the target application scenario.
+		\item \emph{Energy efficiency:} Power consumption has been a major criticism for 5G. It is expected that energy per bit would be reduced by over 90\% in 6G to reduce carbon footprints.
+		\item \emph{Positioning accuracy:} Thanks to THz base stations, a 3D positioning accuracy of centimeter level may be achieved for indoor and outdoor environments.
+		\item \emph{Coverage:} Poor coverage has been another bottleneck for 5G.
 A terrestrial-satellite-aerial integrated network would provide a ubiquitous and uniform coverage for urban, rural, and remote areas.
-		\item \emph{Security and privacy}: Physical-layer security can be improved with narrower beams at higher frequencies and destructive scattering at the environment.
+		\item \emph{Security and privacy:} Physical-layer security can be improved with narrower beams at higher frequencies and destructive scattering at the environment.
 Privacy can be enhanced with federated learning and homomorphic encryption.
-		% \item \emph{Superintelligent}: The network may integrate human, machine, environment, and \gls{ai} into a superintelligent system that can sense, communicate, and act in a coordinated manner.
+		% \item \emph{Superintelligent:} The network may integrate human, machine, environment, and \gls{ai} into a superintelligent system that can sense, communicate, and act in a coordinated manner.
 	\end{itemize}
@@
 
-\begin{section}{Overview on \glsfmtfull{ris}}
+\begin{section}{Overview on \glsfmtfull{ris}}\label{sc:ris_overview}
 

### 2024-03-17 content/chapter_2.tex
:pencil: Add programmable metamaterials

--- 2024-03-16 content/chapter_2.tex
@@
 			\item \emph{Negative refraction:} As shown in Fig.
-\ref{fg:nim_refraction}, the incident and refracted rays stay at the same side of the normal axis.
+\ref{fg:nim_refraction}, the incident and refracted rays stay at the same side of the normal axis \cite{Veselago1968}.
 This phenomenon is in contrast to the usual refraction but can still be predicted from Snell's law
@@
 			\end{equation}
+			It is worth mentioning that a generalized law of refraction and refraction has been proposed in \cite{Yu2011}, which has become a standard reference for the design and analysis of metamaterials.
 			\begin{figure}[H]
 				\centering
-				\subfloat[Negative Index Material\label{fg:nim_refraction}]{
+				\subfloat[Negative-Index Material\label{fg:nim_refraction}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-				\subfloat[Positive Index Material\label{fg:pim_refraction}]{
+				\subfloat[Positive-Index Material\label{fg:pim_refraction}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-				\caption{Refraction in negative and positive index materials. Incident and refracted rays stay at the same side of the normal axis in a negative-index material.}
+				\caption{Refraction in negative and positive-index materials. Incident and refracted rays stay at the same side of the normal axis in a negative-index material.}
 			\end{figure}
 			\item \emph{Opposite wave direction:} As shown in Fig.
-\ref{fg:nim_flows}, the wave vector and energy flow (indicated by the Poynting vector) are opposite to each other in a negative-index material.
+\ref{fg:nim_flows}, the wave vector and energy flow (indicated by the Poynting vector) are opposite to each other in a negative-index material \cite{Pendry2004}.
 This can be inferred from the electric field equation
@@
 				\centering
-				\resizebox{0.5\columnwidth}{!}{
+				\subfloat[Negative-Index Material\label{fg:nim_flows}]{
+					\resizebox{!}{2cm}{
 							\input{assets/chapter_2/nim_flows.tex}
 					}
+				}
+				\subfloat[Positive-Index Material\label{fg:pim_flows}]{
+					\resizebox{!}{2cm}{
+						\input{assets/chapter_2/pim_flows.tex}
+					}
+				}
 				\caption{Wave and energy have opposite directions in a negative-index material.}
-				\label{fg:nim_flows}
 			\end{figure}
-
 		\end{itemize}
 
-		% TODO Programmable
+		Conventional metamaterials have fixed properties that depend on the geometry and arrangement of their constituent elements.
+		Once fabricated, these properties cannot be easily changed unless the structure is physically altered.
+		This limits their early usage to military and defense, with applications such as invisibility cloaks and optical illusions.
+		In 2014, the concept of ``coding'' and ``programmable'' metamaterials was validated by researchers at Southeast University \cite{Cui2014}, who realized digital control of radar cross-section using biased diodes and \gls{fpga}.
+		With a proper model of the target properties and external citation, the metamaterial can be reconfigured in real-time for desired behaviors.
+		For example, a self-adaptive metasurface equipped with motion and light sensors have been developed in \cite{Ma2019} for single- and multi-beam steering.
+
+		Next, we discuss the principles of electromagnetic wave redirection via refraction and reflection:
+		\begin{itemize}
+			\item \emph{Refraction:} As shown in Fig.
+\ref{fg:nim_focus}, the negative-index material can re-focus the beams diverging from a point source to another point behind the material \cite{Padilla2006}.
+This could be helpful for wireless applications where the transmitter and receiver are at different sides of the material.
+			\item \emph{Reflection:} As shown in Fig.
+\ref{fg:wave_reflected}, the scattering elements cooperatively alter the phase of the incident wave for a constructive (or destructive) superposition of the reflected waves in the target direction \cite{Poulakis2022}.
+This could be helpful for wireless applications where the transmitter and receiver are at the same side of the material.
+		\end{itemize}
+		% electromagnetic wave refraction and reflection.
+
+		\begin{figure}[H]
+			\centering
+			\subfloat[Negative-Index Material\label{fg:nim_focus}]{
+				\resizebox{0.45\columnwidth}{!}{
+						\input{assets/chapter_2/nim_focus.tex}
+				}
+			}
+			\subfloat[Positive-Index Material\label{fg:pim_diverge}]{
+				\resizebox{0.45\columnwidth}{!}{
+					\input{assets/chapter_2/pim_diverge.tex}
+				}
+			}
+			\caption{Refraction through metamaterials. For negative-index material, beams diverging from a point source is set in reverse and converges back to another point.}
+		\end{figure}
 		\begin{figure}[H]
@@
 			}
-			\caption{Incident and reflected waves in a programmable metamaterial.}
+			\caption{Reflection through metamaterials.
+Yellow dots represent scattering elements.
+Solid and dashed lines denote wavefronts and rays, respectively.
+The scattering elements work together to manipulate the phases of incident waves, resulting in a focused beam steered in the intended direction.}
 		\end{figure}
+		It is worth noticing that refraction and reflection can be regarded as different forms of \emph{passive beamforming} where the phase and amplitude of the ambient signal are altered by the metamaterial for a desired net effect.
+		In the next subsection, we will some typical \gls{ris} scattering models and their assumptions.
 	\end{subsection}

### 2024-03-19 content/chapter_2.tex
:pencil: Add wave scattering models

@@
 		\end{figure}
-		It is worth noticing that refraction and reflection can be regarded as different forms of \emph{passive beamforming} where the phase and amplitude of the ambient signal are altered by the metamaterial for a desired net effect.
-		In the next subsection, we will some typical \gls{ris} scattering models and their assumptions.
+		It is worth noticing that refraction and reflection are different implementations of \emph{passive beamforming} where the phase and amplitude of the ambient signal are altered by the metamaterial for a desired net effect.
+		In the next subsection, we will some typical \gls{ris} scattering models and their physical architecture.
 	\end{subsection}
 
-	\begin{subsection}{Wave Scattering Model}
-		\begin{subsubsection}{Active and Passive Elements}
+	\begin{subsection}{Wave Scattering Models}
+		\begin{subsection}{Principles}
+			\label{sc:principles}
+			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
+			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
+			In contrast, the latter allows the wave to feed into and collect from the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
+			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
+			The corresponding scattered field is \cite{Hansen1989}
+			\begin{equation}
+				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
+			\end{equation}
+			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
+			\begin{equation}
+				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
+				\label{eq:reflection_coefficient}
+			\end{equation}
+			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
+			It is worth mentioning that
+			\begin{itemize}
+				\item \emph{Structural component:} Depends on the geometry and material of the scatterer.
+It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or simply regarded a \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
+				\item \emph{Antenna component:} Depends on the reflection coefficient that can be altered by load impedance.
+This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2022a}.
+			\end{itemize}
+			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
+			More accurate models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and measurement fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature.
+			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
+		\end{subsection}
 
-		\end{subsubsection}
+		\begin{subsection}{Diagonal Phase Shift Model}
+			A straightforward way to model the \gls{ris} scattering effect is to consider independent scattering elements with purely reactive load impedance \cite{Wu2018}.
+			The reflection coefficient of the $n$-th element is thus
+			\begin{equation}
+				\theta_n = \frac{\jmath X_n - Z^*}{\jmath X_n + Z} = \exp(\jmath \phi_n),
+			\end{equation}
+			where $X_n$ is the reactance and $\phi_n$ is the phase shift on the scattered wave.
+			For a total of $N_\mathrm{S}$ elements, the \gls{ris} scattering matrix is \emph{diagonal with complex unit-magnitude entries}
+			\begin{equation}
+				\mathbf{\Theta} = \mathrm{diag}(\theta_1, \ldots, \theta_{N_\mathrm{S}}) =
+				\begin{bmatrix}
+					\theta_1 & 0 & \cdots & 0 \\
+					0 & \theta_2 & \cdots & 0 \\
+					\vdots & \vdots & \ddots & \vdots \\
+					0 & 0 & \cdots & \theta_{N_\mathrm{S}}
+				\end{bmatrix}.
+			\end{equation}
+			Despite the strong assumptions, this diagonal phase shift model is widely used for the analysis of \gls{ris} systems due to its simplicity and analytical tractability.
+		\end{subsection}
 
-		\begin{subsubsection}{Independent Scattering: Diagonal Model}
+		\begin{subsection}{\glsfmtfull{bd} Model}
+			How to model the \gls{ris} response if the passive scattering elements can be cooperative instead of independent?
+			This question has been answered by \cite{Shen2020a} where a \gls{bd} model was proposed.
+			From a network theory perspective \cite{Ivrlac2010}, the interaction between the scattering elements can be modelled as lossless (but not necessarily symmetric) in-group connections in an $N_\mathrm{S}$-port circuit network, as shown in Figs.
+\ref{fg:bd_ris_architecture_1} and \ref{fg:bd_ris_architecture_2} \cite{Shen2020a}.
+			This architecture allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group.
+			\begin{figure}[H]
+				\centering
+				\resizebox{0.75\columnwidth}{!}{
+					\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
+				}
+				\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. The figure is from \cite{Shen2020a}.}
+				\label{fg:bd_ris_architecture_1}
+			\end{figure}
+			\begin{figure}[H]
+				\centering
+				\resizebox{0.75\columnwidth}{!}{
+					\includegraphics{assets/chapter_2/bd_ris_architecture_2.eps}
+				}
+				\caption{Network model of an 8-element \gls{ris} with group-wise cooperative scattering of group size (a) 2 and (b) 4.
+The group size is a design parameter to balance the circuit complexity and scattering performance.
+The figure is from \cite{Shen2020a}.}
+				\label{fg:bd_ris_architecture_2}
+			\end{figure}
 
-		\end{subsubsection}
+			A general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
+			With symmetric components (e.g., capacitors and inductors), the scattering matrix of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$ is \cite{Shen2020a}
+			\begin{equation}
+				\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I}),
+			\end{equation}
+			which satisfies both \emph{symmetric} and \emph{unitary} properties
+			\begin{subequations}
+				\begin{equation}
+					\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T},
+					\label{eq:symmetric_property}
+				\end{equation}
+				\begin{equation}
+					\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}.
+					\label{eq:unitary_property}
+				\end{equation}
+			\end{subequations}
+			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} such that the symmetric constraint \eqref{eq:symmetric_property} can be relaxed.
+			This corresponds to the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as widely considered in quantum physics.
+			The overall scattering matrix of asymmetric \gls{bd}-\gls{ris} is thus \emph{block-diagonal with unitary blocks}
+			\begin{equation}
+				\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) =
+				\begin{bmatrix}
+					\mathbf{\Theta}_1 & \mathbf{0} & \cdots & \mathbf{0} \\
+					\mathbf{0} & \mathbf{\Theta}_2 & \cdots & \mathbf{0} \\
+					\vdots & \vdots & \ddots & \vdots \\
+					\mathbf{0} & \mathbf{0} & \cdots & \mathbf{\Theta}_G
+				\end{bmatrix},
+				\label{eq:bd_scattering_matrix}
+			\end{equation}
+			where \eqref{eq:unitary_property} is equivalently denoted as $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
+			The group size $L$ is a design parameter to balance the circuit complexity and scattering performance.
+			Diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be viewed as extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
+			Therefore, the \gls{bd} model \eqref{eq:bd_scattering_matrix} is envisioned to be the next-generation theoretical foundation for passive \gls{ris}, which grants more design freedom and stronger signal processing capability.
 
-		\begin{subsubsection}{Cooperative Scattering: \glsfmtfull{bd} Model}
+			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2023a}.
+			One element is in the same group with another if and only if there is at least one path (via edges) between them.
+			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
+			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
+			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
 
-		\end{subsubsection}
+		\end{subsection}
 
-		\begin{subsubsection}{Impact of Radiation Pattern and Circuit Topology}
-
-		\end{subsubsection}
 	\end{subsection}

### 2024-03-20 content/chapter_2.tex
:pencil: Add WPT introduction

@@
 			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
-
 		\end{subsection}
-
 	\end{subsection}
-
 \end{section}
@@
 \begin{section}{\glsfmtfull{wpt}}
-	\begin{subsection}{Near- and Far-Field Techniques}
+	\begin{subsection}{Introduction}
+		Wireless devices are becoming smarter as well as more energy-efficient and eco-friendly.
+		Koomey's law \citep{Koomey2011} predicts the computing efficiency roughly doubles every 19 months and the amount of power needed for the same operation decreases to 1\% in a decade.
+		Over the past 15 years, the rise of low-power technologies like \gls{wsn} and \gls{iot} have hatched life-changing applications including smart homes, digital healthcare, and industrial automation.
+		% This low-power trend has been accelerated by the rise of \gls{iot} and \gls{wsn} technologies, which enabled revolutionary applications including smart homes, digital healthcare, and industrial automation.
+		Today, \gls{rfid} tags and basic sensors (e.g., thermometer and proximeter) can operate on microwatts of power \cite{Huang2019,Hao2018}, while communication protocols like \gls{ble} and \gls{lorawan} only consume tens of milliwatts \cite{Correia2017b}.
+		This low-power trend together with the upsurge of mobile devices is calling for a \emph{truly wireless} energy solution that eliminates the need for periodic cable plugging or battery replacement.
+		% While solutions like solar and piezoelectric offer benefits in specific scenarios, their bulky components, unpredictable power sources, and limited range make them unsuitable for most wireless applications.
+		While great successes have been witnessed for candidates like solar and piezoelectric, their prospects in wireless systems remain unclear due to the bulky converter, unpredictable source, and limited operation range.
+		One promising solution on the horizon is \gls{wpt} through electromagnetic waves.
+		It can be classified into two categories based on the operation principle \cite{Zhou2022}:
+		\begin{itemize}
+			\item \emph{Non-radiative near-field:} Power is transferred over a short distance (typically a few centimeters) by inductive coupling between coils or capacitive coupling between electrodes in a field-to-field manner.
+The former has been widely standardized (e.g., Qi 2.0) and commercialized (e.g., wireless charging pads), while the latter is still in the research stage.
+			\item \emph{Radiative far-field:} Power is transferred over a long distance (typically a few meters) by directional microwave or laser beams between antennas in a point-to-point manner.
+It shares many similarities with \gls{rf} communication (e.g., infrastructure and wireless environment) but suffers from lower energy efficiency than non-radiative \gls{wpt} due to pathloss.
+		\end{itemize}
 
+		Radiative \gls{wpt}\footnote{In the following part of the thesis, \gls{wpt} refers to radiative \gls{wpt}.} brings numerous opportunities to future wireless networks.
+		First, it completely eliminates wired connections and can be integrated into existing wireless systems with minimum modifications.
+		Those properties translate to simple deployment, high scalability, and low maintenance cost.
+		Second, the power can be simultaneously radiated to multiple devices on demand in a predictable, sustainable and reliable manner.
+		This supports our initial vision and is different from other uncontrollable and intermittent energy sources.
+		Third and most importantly, radio waves carries power and information simultaneously such that \gls{wpt} can be jointly designed with \gls{wit} to make the most of radiation, spectrum and infrastructures.
+		However, energy efficiency and safety concerns have been two major obstacles that limit the practical development of \gls{wpt}.
+		We will discuss how \gls{ris} can help address these issues in Section \ref{sc:swipt}
 	\end{subsection}
@@
 
-\begin{section}{\glsfmtfull{swipt}}
+\begin{section}{\glsfmtfull{swipt}}\label{sc:swipt}
 	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}

### 2024-03-22 assets/chapter_2/wpt_architecture.tex
:pencil: Add WPT modules and harvester behavior

\begin{circuitikz}[transform shape,align=center,font=\footnotesize]
	\draw(0,0) node[draw](rf){\gls{rf}\\source};
	\draw(rf.east) node[txantenna]{};
	\draw(1,1) node{Tx};
	\draw(4.875,2) node[draw]{\gls{ris}};
	\draw(4.875,1) node[draw]{Channel};
	\draw(10,0) node[draw](mc){Matching\\network};
	\draw(mc.west) node[rxantenna,xscale=-1]{};
	\draw(8.7,1) node{Rx};
	\draw(mc.east) to ++(0.85,0) node[anchor=west,draw](d){Diode};
	\draw(d.east) to ++(0.85,0) node[anchor=west,draw](lpf){Low-pass\\filter};
	\draw(lpf.east) to ++(1,0) node[anchor=west,draw](dd){\gls{dc}-\gls{dc}\\converter};
	\draw(dd.east) to ++(1,0) node[anchor=west,draw](s){Storage};

	\draw [dashed] (-0.95,-0.75) rectangle (3.75,2.75);
	\draw (1.4,3) node[]{Energy transmitter};
	\draw [dotted] (6.25,-0.5) rectangle (15.6,2.5);
	\draw (10.925,2) node[]{Rectenna};
	\draw [dotted] (16,-0.5) rectangle (20.5,1.25);
	\draw (18.25,0.875) node[]{Power management unit};
	\draw [dashed] (6,-0.75) rectangle (20.75,2.75);
	\draw (13.375,3) node[]{Energy receiver};

	\draw (-0.95,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{T}}$};
	\draw (3.75,-1) node[]{$P_{\mathrm{RF}}^{\mathrm{T}}$};
	\draw (6,-1) node[]{$P_{\mathrm{RF}}^{\mathrm{R}}$};
	\draw (15.8,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{R}}$};
	\draw (20.5,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{S}}$};

	\draw[gray,dashdotted,-latex] (10.925,-0.5) to ++(0,-1.5) to ++(-1,0) node[anchor=east,draw](c){Channel\\feedback};
	\draw[gray,dashdotted,latex-] (1.4,-0.75) to ++(0,-1.25) to ++(1,0) node[anchor=west,draw](s){Signal\\optimization};
	\draw[gray,dashdotted,-latex] (c.west) to (s.east);
	\draw[gray] (6.45,-2) node[]{Reverse\\communication link};
\end{circuitikz}

### 2024-03-22 content/chapter_2.tex
:pencil: Add WPT modules and harvester behavior

@@
 	\begin{subsection}{Wave Scattering Models}
-		\begin{subsection}{Principles}
+		\begin{subsubsection}{Principles}
 			\label{sc:principles}
@@
 			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
-		\end{subsection}
+		\end{subsubsection}
 
-		\begin{subsection}{Diagonal Phase Shift Model}
+		\begin{subsubsection}{Diagonal Phase Shift Model}
 			A straightforward way to model the \gls{ris} scattering effect is to consider independent scattering elements with purely reactive load impedance \cite{Wu2018}.
@@
 			Despite the strong assumptions, this diagonal phase shift model is widely used for the analysis of \gls{ris} systems due to its simplicity and analytical tractability.
-		\end{subsection}
+		\end{subsubsection}
 
-		\begin{subsection}{\glsfmtfull{bd} Model}
+		\begin{subsubsection}{\glsfmtfull{bd} Model}
 			How to model the \gls{ris} response if the passive scattering elements can be cooperative instead of independent?
@@
 			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
-		\end{subsection}
+		\end{subsubsection}
 	\end{subsection}
@@
 		This supports our initial vision and is different from other uncontrollable and intermittent energy sources.
-		Third and most importantly, radio waves carries power and information simultaneously such that \gls{wpt} can be jointly designed with \gls{wit} to make the most of radiation, spectrum and infrastructures.
+		Third and most importantly, radio waves carries power and information simultaneously.
+		\gls{wpt} can therefore be jointly designed with \gls{wit} to make the most of radiation, spectrum and infrastructures.
 		However, energy efficiency and safety concerns have been two major obstacles that limit the practical development of \gls{wpt}.
-		We will discuss how \gls{ris} can help address these issues in Section \ref{sc:swipt}
+		In Section \ref{sc:swipt}, we will discuss how \gls{ris} can help address these issues.
 	\end{subsection}
@@
 	\begin{subsection}{Modules and Coupling Effect}
-		\begin{subsubsection}{Block Diagram}
+		\begin{figure}[H]
+			\centering
+			\resizebox{\columnwidth}{!}{
+				\input{assets/chapter_2/wpt_architecture.tex}
+			}
+			\caption{Block diagram of a closed-loop \gls{ris}-aided \gls{wpt}.}
+			\label{fg:wpt_architecture}
+		\end{figure}
 
-		\end{subsubsection}
-
-		\begin{subsubsection}{Blockwise Coupling}
-
-		\end{subsubsection}
+		The block diagram a closed-loop \gls{ris}-aided \gls{wpt} system is illustrated in Fig. \ref{fg:wpt_architecture}.
+		The \gls{rf} signal is generated and radiated by the energy transmitter, propagated through a wireless channel in the presence of a \gls{ris}, captured by the antenna(s) at the receiver, converted to \gls{dc} power by rectifier(s), then passed to the power management unit.
+		Upon successful harvesting, the \gls{dc} power is either delivered directly to the device or stored in a battery/super capacitor for future operations.
+		When a feedback link is available, one can acquire \gls{csi} at the energy transmitter and exploit it for signal optimization.
+		Such a closed-loop \gls{ris}-aided \gls{wpt} system can provide a complete control of transmitter, channel, and receiver, which is essential for maximizing the end-to-end power transfer efficiency
+		\begin{equation}
+			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4},
+		\end{equation}
+		where $P_{\mathrm{DC}}^\mathrm{T}$ is the transmitted \gls{dc} power, $P_{\mathrm{RF}}^\mathrm{T}$ is the transmitted \gls{rf} power, $P_{\mathrm{RF}}^\mathrm{R}$ is the received \gls{rf} power, $P_{\mathrm{DC}}^\mathrm{R}$ is the received \gls{dc} power, and $P_{\mathrm{DC}}^\mathrm{S}$ is the stored \gls{dc} power.
+		The power conversion efficiencies are specified below:
+		\begin{itemize}
+			\item $\eta_1$: Transmitter \gls{dc}-to-\gls{rf} conversion efficiency\footnote{This is different from \gls{pae} used in amplifier rating, which takes into account both \gls{dc} power and input waveform power \cite{Joung2015}.} that depends on the \gls{rf} power amplifier and transmit antenna.
+It is also called ``drain efficiency'' and state-of-the-art designs can achieve $\eta_1 \ge 70\%$ \cite{Alizadeh2020}.
+			\item $\eta_2$: Channel \gls{rf}-to-\gls{rf} conversion efficiency that depends on the wireless environment and \gls{ris} configuration.
+This is the major bottleneck of \gls{wpt} since the radiated power is inversely proportional to the propagation distance squared.
+			\item $\eta_3$: Receiver \gls{rf}-to-\gls{dc} conversion efficiency that depends on the impedance matching and rectifier design. We will discuss its behavior and modelling in the next subsection.
+			\item $\eta_4$: Storage \gls{dc}-to-\gls{dc} conversion efficiency that depends on the converter circuit and battery characteristics.
+Modern power management units can achieve a charging efficiency $\eta_4 \ge 90\%$ \cite{Tan2012}.
+		\end{itemize}
+		It is worth mentioning that $\eta_1$ and $\eta_3$ also depend on the characteristics of input waveform like power level, carrier frequency, and \gls{papr} \cite{Clerckx2016a}.
+		Extensive efforts have been contributed from \gls{rf}, wireless communications, and power electronic communities to improve the conversion efficiency of individual modules.
+		However, it is often overlooked in the literature that a practical \gls{wpt} system is highly \emph{non-linear} since the amplifier and rectifier are very sensitive to the input waveform.
+		This non-linear behavior can lead to a \emph{coupling effect} between the modules, such that optimizing $\eta_1$ to $\eta_4$ independently does not necessarily maximize the end-to-end power efficiency $\eta$ \cite{Clerckx2016a}.
+		Besides, the system modeling and analysis are subject to practical constraints like diode threshold and reverse-breakdown voltages, device parasitics, impedance mismatch, and harmonic generation  \citep{Valenta2014}.
 	\end{subsection}
@@
 	\begin{subsection}{Non-Linear Harvester Behavior}
-		\begin{subsubsection}{Rectifier Circuits}
-
+		\begin{subsubsection}{Equivalent Circuits}
+			\begin{figure}[H]
+				\centering
+				\subfloat[Rectenna]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/chapter_2/rectenna.tex}
+					}
+					\label{fg:rectenna}
+				}
+				\subfloat[Half-wave rectifier]{
+					\resizebox{0.45\columnwidth}{!}{
+						\input{assets/chapter_2/halfwave_rectifier.tex}
+					}
+					\label{fg:halfwave_rectifier}
+				}
+				\caption{
+					Equivalent circuit of (a) rectenna and (b) single-diode half-wave rectifier.
+				}
+				\label{fg:harvester_circuit}
+			\end{figure}
+			The rectifier is a nonlinear circuit that converts the \gls{rf} signal to \gls{dc} power by rectifying and filtering the input signal.
+			Figs.
+\ref{fg:harvester_circuit} illustrates the equivalent circuits of a rectenna (antenna and rectifier) and a single-diode half-wave rectifier, where $v_{\mathrm{S}}$ is the source voltage on the receive antenna, $Z_{\mathrm{A}} = R_{\mathrm{A}} + \jmath X_{\mathrm{A}}$ is the antenna impedance, $Z_{\mathrm{in}} = R_{\mathrm{in}} + \jmath X_{\mathrm{in}}$ is the total impedance of the matching network and rectifier, $v_{\mathrm{in}}$ is input voltage on the matching network and rectifier, $v_{\mathrm{D}}$ is the diode voltage, $C$ is the buffer capacitance, $R_{\mathrm{L}}$ is the rectifier load resistance, and $v_{\mathrm{out}}$ is the output voltage.
+			It is worth mentioning that the half-wave rectifier is the most popular choice in \gls{wpt} literature due to its simple behavior and low cost.
+			Other rectifier topologies like full-wave, bridge, and voltage doubler can potentially improve the \gls{rf}-to-\gls{dc} conversion efficiency \cite{Rotenberg2020}, but their modeling and analysis are much more complicated.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Operation Regions and Signal Models}
+			The diode is the key non-linear component that determines to the harvested energy.
+			Generally speaking, the behavior of any rectenna can be separated into three operation regions \cite{Clerckx2016a}:
+			\begin{itemize}
+				\item \emph{Linear region:} When the input power level is relatively low, the output power is proportional to the input and the \gls{rf}-to-\gls{dc} conversion efficiency $\eta_3$ is a constant.
+Most early \gls{wpt} research (especially from communications society) assume the rectenna works in this region.
+For a received signal $y(t)$, the harvested \gls{dc} power in this region can be modelled as
+				\begin{equation}
+					P_\mathrm{DC}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{E}\bigl\{ \lvert y(t) \rvert^2 \bigr\},
+					\label{eq:dc_power_linear}
+				\end{equation}
+				which suggests that maximizing the received \gls{rf} signal power is sufficient to maximize the harvested \gls{dc} power.
+				\item \emph{Non-linear (transition) region:} When the input power level is moderate, the output power increases \emph{exponentially} with the input and $\eta_3$ is significantly higher than the linear region.
+This is the most interesting region that can be exploited to improve the overall power efficiency.
+				For a tractable model, consider a perfectly matched ($Z_\mathrm{in} = Z_\mathrm{A}^*$) half-wave rectifier in Fig.~\subref*{fg:halfwave_rectifier} and assume the voltage across the matching network is negligible.
+The received \gls{rf} power is totally transferred to the rectifier input $P_\mathrm{RF}^\mathrm{R} = \mathbb{E}\bigl\{ \lvert y(t) \rvert^2 \bigr\} = \mathbb{E}\bigl\{ \lvert v_\mathrm{in}(t) \rvert^2 / R_\mathrm{in} \bigr\} = \mathbb{E}\bigl\{ \lvert v_\mathrm{in}(t) \rvert^2 / R_\mathrm{A} \bigr\}$ such that the voltage sources can be expressed in terms of the received signal \cite{Clerckx2016a}
+				\begin{equation}
+					v_\mathrm{in}(t) = y(t) \sqrt{R_\mathrm{A}}, \quad v_\mathrm{S}(t) = 2 y(t) \sqrt{R_\mathrm{A}}.
+				\end{equation}
+				The current passing through the diode is given by the characteristic equation $i_\mathrm{D}(t) = I_\mathrm{S} \bigl( \exp(v_\mathrm{D}(t) / n v_\mathrm{T}) - 1 \bigr)$, where $I_\mathrm{S}$ is the reverse bias saturation current, $v_\mathrm{T}$ is the thermal voltage, and $n$ is the ideality factor.
+Its Taylor expansion around the steady point $-v_\mathrm{out}$ is \cite{Clerckx2016a}
+				\begin{equation}
+					i_\mathrm{D}(t) = \sum_{i=0}^\infty k_i \bigl(v_\mathrm{D}(t)+v_\mathrm{out}\bigr)^i = \sum_{i=0}^\infty k_i v_\mathrm{in}^i(t) = \sum_{i=0}^\infty k_i R_\mathrm{A}^{i/2} y^i(t),
+				\end{equation}
+				where $k_0 = I_\mathrm{S} \bigl(\exp(-{v_\mathrm{out}}/{n v_\mathrm{T}})-1\bigr)$, $k_i = I_\mathrm{S} \frac{\exp(-v_\mathrm{out}/n v_\mathrm{T})}{i!(n v_\mathrm{T})^i}$ for $k \in \mathbb{N}$.
+				The rectifier output \gls{dc} current can be written as a function of the received signal
+				\begin{equation}
+					i_\mathrm{out} = \sum_{i=0}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{E}\bigl\{ y^i(t) \bigr\} = \sum_{i=0,\text{even}}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{E}\bigl\{ y^i(t) \bigr\}
+					\label{eq:dc_current_expansion}
+				\end{equation}
+				where the second equality is because $\mathbb{E}\bigl\{y^i(t)\bigr\} = 0$ for odd $i$.
+Note that the dependency of $k_i$ on $-v_\mathrm{out}=-i_\mathrm{out} R_\mathrm{L}$ makes it nontrivial to formulate a closed-form expression for the harvested \gls{dc} power.
+				Fortunately, it is shown in \cite{Clerckx2016a} that maximizing the harvested \gls{dc} power is equivalent to maximizing the quantity
+				\begin{equation}
+					z = \sum_{i=2,\text{even}}^\infty \beta_i \mathbb{E}\bigl\{ y^i(t) \bigr\},
+					\label{eq:dc_power_nonlinear}
+				\end{equation}
+				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant.
+Truncating \eqref{eq:dc_power_nonlinear} at the second order yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model.
+For a moderate excitation, the contribution of higher-order terms is significant and should be modelled in the harvested \gls{dc} power.
+				\item \emph{Saturation region:} When the input power level is too high, the diode works in the reverse breakdown region, the rectifier is saturated, and the output power is a constant.
+This is the region where the $\eta_3$ significantly drops and should be avoided by circuit design.
+				For a fixed rectenna with Gaussian input signal, a parametric model was proposed in \cite{Boshkovska2015}
+				\begin{equation}
+					P_{\mathrm{DC}}^\mathrm{R} = \frac{\Psi_{\mathrm{DC}}-P_{\text{sat}}\Omega}{1-\Omega}, \quad \Psi_{\mathrm{DC}} = \frac{P_{\text{sat}}}{1+\exp\bigl(-a(P_{\mathrm{RF}}^\mathrm{R}-b)\bigr)}, \quad \Omega = \frac{1}{1 + \exp(ab)},
+					\label{eq:saturation_model}
+				\end{equation}
+				where the constant $P_{\text{sat}}$ denotes the maximum harvested power when the rectifier is saturated, and the constants $a$ and $b$ model the nonlinear charging rate with respect to input power and the minimum turn-on voltage of the rectifier, respectively.
+				Parameters $P_{\text{sat}}$, $a$, and $b$ can be obtained by curve fitting over measurement results.
+			\end{itemize}
 
-		\end{subsubsection}
-
-		\begin{subsubsection}{Impact on Waveform Selection}
-
+			The exact boundaries between those regions depend on the rectifier circuit and input waveform \citep{Zeng2017}.
+			Signals with a higher \gls{papr} usually exhibit the nonlinear and saturation effects at lower input power levels.
+			For example, the nonlinear region is typically $[-20,0]$ dBm for a \gls{cw} and $[-30,-10]$ dBm for a multisine \citep{DelPrete2016}.
+			This not only motivates adaptive multi-carrier waveform designs \cite{Clerckx2016a,Zeng2017,Huang2017,Shen2021} but also calls for a joint optimization of the transmitter, channel (via \gls{ris}), and receiver to improve the end-to-end power efficiency.
 		\end{subsubsection}

### 2024-03-22 misc/glossaries.tex
:pencil: Add wave scattering models
:pencil: Add WPT introduction
:pencil: Add WPT modules and harvester behavior

@@
 \newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
+\newacronym{star}{STAR}{Simultaneous Transmission and Reflection}
 \newacronym{smf}{SMF}{Scaled Matched Filter}
@@
 \newacronym{wpt}{WPT}{Wireless Power Transfer}
+\newacronym{wsn}{WSN}{Wireless Sensor Network}
 \newacronym{wsr}{WSR}{Weighted Sum-Rate}
@@
 \newacronym{lc}{LC}{Low-Complexity}
+\newacronym{ble}{BLE}{Bluetooth Low Energy}
+\newacronym{lorawan}{LoRaWAN}{Long Range Wide Area Network}
+\newacronym{pae}{PAE}{Power-Added Efficiency}
+\newacronym{papr}{PAPR}{Peak-to-Average Power Ratio}
 
@@
 
-\nomenclature[n-1]{$\mathbb{R}$}{Real numbers}
-\nomenclature[n-2]{$\mathbb{R}_+$}{Real nonnegative numbers}
-\nomenclature[n-3]{$\mathbb{C}$}{Complex numbers}
-\nomenclature[n-4]{$\mathbb{I}$}{Probability domain $[0,1]$}
-\nomenclature[n-5]{$\mathbb{H}_+^{n \times n}$}{Positive semi-definite matrices of dimension $n \times n$}
-\nomenclature[n-6]{$\mathbb{U}^{n \times n}$}{Unitary matrices of dimension $n \times n$}
+\nomenclature[n-1]{$\mathbb{N}$}{Natural numbers (excluding 0)}
+\nomenclature[n-2]{$\mathbb{R}$}{Real numbers}
+\nomenclature[n-3]{$\mathbb{R}_+$}{Real nonnegative numbers}
+\nomenclature[n-4]{$\mathbb{C}$}{Complex numbers}
+\nomenclature[n-5]{$\mathbb{I}$}{Probability domain $[0,1]$}
+\nomenclature[n-6]{$\mathbb{H}_+^{n \times n}$}{Positive semi-definite matrices of dimension $n \times n$}
+\nomenclature[n-7]{$\mathbb{U}^{n \times n}$}{Unitary matrices of dimension $n \times n$}
 
-\nomenclature[c-j]{$\jmath$}{The imaginary unit $= \sqrt{-1}$}
+\nomenclature[c-j]{$\jmath$}{Imaginary unit $= \sqrt{-1}$}
 \nomenclature[c-e]{$e$}{Euler's number $\simeq 2.71828\ldots$}

### 2024-03-23 content/chapter_1.tex
:pencil: Add wave scattering models
:pencil: Add SWIPT introduction and R-E tradeoff

@@
 			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
-			\caption{A typical architecture of \gls{ris}. Modified from \cite{Wu2020}.}
+			\caption{A typical architecture of \gls{ris}. The figure is modified from \cite{Wu2020}.}
 			\label{fg:ris_architecture}
@@
 
-	\begin{subsection}{Applications}
+	\begin{subsection}{Applications}\label{sc:ris_applications}
 		The channel manipulation capability of \gls{ris} unlocks a wide range of unprecedented applications, such as signal enhancement \cite{Wu2019}, interference suppression \cite{Jiang2022}, blockage bypassing \cite{Ghatak2021}, coverage extension \cite{Zeng2021}, and security control \cite{Almohamad2020}.

### 2024-03-23 content/chapter_2.tex
:pencil: Add SWIPT introduction and R-E tradeoff

@@
 
-\chapter{Background and Literature Review}\label{ch:background}
+\chapter{Background}\label{ch:background}
 
@@
 				\centering
-				\subfloat[Negative-Index Material\label{fg:nim_refraction}]{
+				\subfloat[Negative-index material\label{fg:nim_refraction}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-				\subfloat[Positive-Index Material\label{fg:pim_refraction}]{
+				\subfloat[Positive-index material\label{fg:pim_refraction}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				\centering
-				\subfloat[Negative-Index Material\label{fg:nim_flows}]{
+				\subfloat[Negative-index material\label{fg:nim_flows}]{
 					\resizebox{!}{2cm}{
@@
 				}
-				\subfloat[Positive-Index Material\label{fg:pim_flows}]{
+				\subfloat[Positive-index material\label{fg:pim_flows}]{
 					\resizebox{!}{2cm}{
@@
 			\centering
-			\subfloat[Negative-Index Material\label{fg:nim_focus}]{
+			\subfloat[Negative-index material\label{fg:nim_focus}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 			}
-			\subfloat[Positive-Index Material\label{fg:pim_diverge}]{
+			\subfloat[Positive-index material\label{fg:pim_diverge}]{
 				\resizebox{0.45\columnwidth}{!}{
@@
 			\centering
-			\subfloat[Incident Wave\label{fg:wave_incident}]{
+			\subfloat[Incident wave\label{fg:wave_incident}]{
 				\resizebox{!}{4.04cm}{
@@
 			}
-			\subfloat[Reflected Wave\label{fg:wave_reflected}]{
+			\subfloat[Reflected wave\label{fg:wave_reflected}]{
 				\resizebox{!}{4cm}{
@@
 				\begin{equation}
-					z = \sum_{i=2,\text{even}}^\infty \beta_i \mathbb{E}\bigl\{ y^i(t) \bigr\},
+					z \triangleq \sum_{i=2,\text{even}}^\infty \beta_i \mathbb{E}\bigl\{ y^i(t) \bigr\},
 					\label{eq:dc_power_nonlinear}
@@
 \begin{section}{\glsfmtfull{swipt}}\label{sc:swipt}
-	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
+	\begin{subsection}{Introduction}
+		\gls{wit} and \gls{wpt} have been treated separately over the past century and have made significant progress in their respective fields.
+		Interestingly, electromagnetic waves carry information and energy simultaneously and the same signal can be used for communication and power transfer.
+		The idea of \gls{swipt} was first proposed in 2008 \cite{Varshney2008} and has since attracted significant attention from both academia and industry.
+		It is a promising solution to connect and energize trillions of low-power mobile devices, providing power at microwatt level and coverage up to tens of meters in a unified manner \cite{Clerckx2018b}.
+		\gls{swipt} can also smoothly shift between the two extreme cases to fully exploit the \gls{rf} spectrum and network infrastructure.
+		It is envisioned that future network providers will be able to offer a complete wireless solution including data and power services, which is essential for the upcoming intelligent era.
 
+		One of the most important issues in \gls{swipt} is that the energy harvester requires a much higher received signal power (several orders of magnitude) than the information decoder \cite{Clerckx2019}.
+		Since the channel \gls{rf}-to-\gls{rf} efficiency $\eta_2$ is the primary constraint on the overall power efficiency, how to combat the pathloss and fading effects has been recognized as a crucial research topic for \gls{wpt} \gls{swipt}.
+		Fortunately, this issue can be effectively mitigated by introducing a \gls{ris} to the environment.
+		By carefully tuning the scatter response of the \gls{ris} elements, one can potentially achieve the following benefits:
+		\begin{itemize}
+			\item \emph{Energy focusing:} The scattered waves can be steered towards the receivers or focused on a dedicated ``hotspot zone'' to increase the harvester input power level.
+This is also helpful to extend the coverage and improve the reliability of the energy link.
+			\item \emph{Beam splitting:} Instead of transmitting one strong beam towards each user, the energy signal can be split into multiple weaker beams rerouted by the \gls{ris} to even out the spatial power distribution.
+This is useful to bypass physical obstacles (especially in high-frequency and large-scale networks) and reduce the health risk of radiation.
+		\end{itemize}
+		\gls{ris} can also be used to assist the information link by \gls{snr} enhancement and interference suppression, as mentioned in subsection \ref{sc:ris_applications}.
 	\end{subsection}
 
-	\begin{subsection}{Receiver Architectures}
+	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
+		Despite \gls{wit} and \gls{wpt} share many similarities, their difference in design objectives, system architectures, and practical constraints make a joint implementation of \gls{swipt} particularly challenging.
+		Some preference of \gls{wit} and \gls{wpt} are inherently conflicting, for example:
+		\begin{itemize}
+			\item \emph{Waveform and modulation:} Under an average power constraint, \gls{wit} favors Gaussian signaling with maximum entropy distribution \cite{Cover2005} while \gls{wpt} prefers deterministic (unmodulated) multisine with higher \gls{papr} \cite{Trotter2009}.
+			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
+			\item \emph{Receiver:} The power sensitivity is usually in the range of -40 to -80 dBm for information receivers and -10 to -30 dBm for energy harvesters \cite{Lu2015}.
+		\end{itemize}
+		Those disparities translate to a fundamental tradeoff between information and power transfer in \gls{swipt} systems, which is often quantified by a convex \emph{\gls{r-e} region}.
+		\begin{equation}
+			\mathcal{C}_\mathrm{R-E}(P) \triangleq \Bigl\{ (r,e) : 0 \le r \le \log(1 + \gamma), \ 0 \le e \le z \Bigr\},
+		\end{equation}
+		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ defined in \eqref{eq:dc_power_nonlinear} is uniquely mapped to the harvested \gls{dc} power.
+		Each point in this region corresponds to a \emph{rate-energy pair} achieved by a particular \emph{resource allocation scheme}.
+		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions (instead of different points in the same region), which motivates a joint optimization of the transmitter, channel, and receiver.
+	\end{subsection}
+
+	\begin{subsection}{System Architecture}
+
+		\begin{subsubsection}{Information and Energy Flows}
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{Receiver Architectures}
+
+		\end{subsubsection}
+		As shown in Figs. \subref*{fg:swipt_colocated} and \subref*{fg:swipt_separated}, \gls{swipt} can be classified into two categories based on the receiver configuration:
+		% \begin{itemize}
+		% 	\item \emph{\gls{swipt}:} Energy and information are simultaneously delivered in the downlink to co-located and/or separated information receiver(s) and energy receiver(s);
+		% 	\item \emph{\gls{wpcn}:} Energy is delivered in the downlink to active device(s) that generate and transmit information-bearing signals in the uplink;
+		% 	\item \emph{\gls{wpbc}:} Energy is delivered in the downlink to passive node(s) that reflect part of incoming waves and embed information in the uplink.
+		% \end{itemize}
+		\begin{figure}[H]
+			\centering
+			\subfloat[\gls{swipt} with co-located receiver]{
+				\resizebox{7cm}{!}{
+					\input{assets/chapter_2/swipt_colocated.tex}
+				}
+				\label{fg:swipt_colocated}
+			}
+			\subfloat[\gls{swipt} with separated receivers]{
+				\resizebox{7cm}{!}{
+					\input{assets/chapter_2/swipt_separated.tex}
+				}
+				\label{fg:swipt_separated}
+			}
+			\\
+			\subfloat[Monostatic backscatter]{
+				\resizebox{7cm}{!}{
+					\input{assets/chapter_2/backcom_monostatic.tex}
+				}
+				\label{fg:backcom_monostatic}
+			}
+			\subfloat[Bistatic backscatter]{
+				\resizebox{7cm}{!}{
+					\input{assets/chapter_2/backcom_bistatic.tex}
+				}
+				\label{fg:backcom_bistatic}
+			}
+			\caption{
+				Information and energy flows in different WIPT schemes. Dashed and dotted lines denote energy and information flows, respectively.
+			}
+			\label{fg:wipt_schemes}
+		\end{figure}
 

### 2024-03-23 content/declaration.tex
:pencil: Add SWIPT introduction and R-E tradeoff

--- 2024-02-29 Declaration/declaration.tex
@@
 Any work from other researchers, scholars, or sources have been properly cited and acknowledged.
+Figures, tables, and results presented in this dissertation are generated by myself, unless otherwise stated.
+I would like to acknowledge the use of large language models for assistance in improving the clarity and readability of introduction and background sections of this thesis.
 The contents have not been submitted in whole or in part for consideration of any other degree or qualification in any academic institution.
-I am aware of the ethical standards and academic integrity policies of Imperial College London, and I have adhered to these principles throughout the course of my study.
+I am aware of the ethical standards and academic integrity policies of Imperial College London, and I have adhered to these principles throughout the course of study.
 In signing this declaration, I affirm my commitment to academic honesty, intellectual integrity, and the pursuit of knowledge in the service of truth and understanding.

### 2024-03-23 assets/chapter_2/receiver_ps.tex
:pencil: Add SWIPT modules and operation modes

\begin{circuitikz}[transform shape,align=center]
	\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
		to[short] ++(0,-1)
		to node[coupler,anchor=left up](c){Power splitter} ++(1,0);
	\draw (c.right up)
		to[short] ++(0.5,0)
		to ++(0,0.5)
		to ++(1,0) node[draw,minimum width=2.5cm,anchor=west](eh){Energy\\harvester};
	\draw (eh.east) to ++(1,0) node[draw,anchor=west,minimum width=2.5cm]{Power\\management};
	\draw (c.right down)
		to[short] ++(0.5,0)
		to ++(0,-0.5)
		to ++(1,0) node[draw,anchor=west,minimum width=2.5cm]{Information\\decoder};
\end{circuitikz}

### 2024-03-23 assets/chapter_2/receiver_ts.tex
:pencil: Add SWIPT modules and operation modes

\begin{circuitikz}[transform shape,align=center]
	\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
		to[short] ++(0,-1) node[below]{Time switcher}
		to[short] node[spdt,anchor=in](s){} ++(0.5,0);

	\draw (s.out 1)
		to ++(1.25,0)
		to ++(0,0.5)
		to ++(1,0) node[draw,minimum width=2.5cm,anchor=west](eh){Energy\\harvester};
	\draw (eh.east) to ++(1,0) node[draw,anchor=west,minimum width=2.5cm]{Power\\management};

	\draw (s.out 2)
		to ++(1.25,0)
		to ++(0,-0.5)
		to ++(1,0) node[draw,anchor=west,minimum width=2.5cm]{Information\\decoder};
\end{circuitikz}

% \begin{circuitikz}[transform shape,align=center]
% 	\draw (0,0) node[bareRXantenna](r){Rx}(r.center)
% 		to[short] ++(0,-1)
% 		to node[coupler,anchor=left up](c){Power splitter} ++(1,0);
% 	\draw (c.right up)
% 		to[short] ++(0.5,0)
% 		to ++(0,0.5)
% 		to ++(1,0) node[draw,minimum width=2.5cm,anchor=west](eh){Energy\\harvester};
% 	\draw (eh.east) to ++(1,0) node[draw,anchor=west,minimum width=2.5cm]{Power\\management};
% 	\draw (c.right down)
% 		to[short] ++(0.5,0)
% 		to ++(0,-0.5)
% 		to ++(1,0) node[draw,anchor=west,minimum width=2.5cm]{Information\\decoder};
% \end{circuitikz}

### 2024-03-23 content/chapter_2.tex
:pencil: Add SWIPT modules and operation modes

@@
 		\end{itemize}
-		Those disparities translate to a fundamental tradeoff between information and power transfer in \gls{swipt} systems, which is often quantified by a convex \emph{\gls{r-e} region}.
+		Those disparities translate to a fundamental tradeoff between information and power transfer in \gls{swipt} systems, which is often quantified by a \emph{\gls{r-e} region}.
 		\begin{equation}
@@
 
-	\begin{subsection}{System Architecture}
-
+	\begin{subsection}{Modules and Operation Modes}
 		\begin{subsubsection}{Information and Energy Flows}
-
-		\end{subsubsection}
-
-		\begin{subsubsection}{Receiver Architectures}
-
-		\end{subsubsection}
-		As shown in Figs. \subref*{fg:swipt_colocated} and \subref*{fg:swipt_separated}, \gls{swipt} can be classified into two categories based on the receiver configuration:
-		% \begin{itemize}
-		% 	\item \emph{\gls{swipt}:} Energy and information are simultaneously delivered in the downlink to co-located and/or separated information receiver(s) and energy receiver(s);
-		% 	\item \emph{\gls{wpcn}:} Energy is delivered in the downlink to active device(s) that generate and transmit information-bearing signals in the uplink;
-		% 	\item \emph{\gls{wpbc}:} Energy is delivered in the downlink to passive node(s) that reflect part of incoming waves and embed information in the uplink.
-		% \end{itemize}
+			In \gls{swipt}, the information and energy are always transmitted from the same source while their receivers can be either co-located or separated, as shown in Figs.
+\subref*{fg:swipt_colocated} and \subref*{fg:swipt_separated}.
+			This is different from \gls{bc} where the energy is delivered in the downlink and the information is sent in the uplink, as shown in Figs.
+\subref*{fg:backcom_monostatic} and \subref*{fg:backcom_bistatic}.
 			\begin{figure}[H]
@@
 				\caption{
-				Information and energy flows in different WIPT schemes. Dashed and dotted lines denote energy and information flows, respectively.
+					Information and energy flows in \gls{swipt} and \gls{bc} systems. Blue and black parts denote information and power subsystems, respectively.
 				}
@@
 			\end{figure}
+			From a design perspective, co-located \gls{swipt} receiver is a more general model since it can exploit the received signal for either purpose or a mixture in between.
+			We thus focus on this model in the following context.
+		\end{subsubsection}
 
+		\begin{subsubsection}{Receiver Architectures}
+			Figure \ref{fg:swipt_receiver_architectures} illustrates four potential architectures for a co-located \gls{swipt} receiver \cite{Clerckx2022}:
+			\begin{figure}[H]
+				\centering
+				\subfloat[Ideal receiver]{
+					\resizebox{0.6\columnwidth}{!}{
+						\input{assets/chapter_2/receiver_ideal.tex}
+					}
+					\label{fg:receiver_ideal}
+				}
+				\\
+				\subfloat[Time switching receiver]{
+					\resizebox{0.6\columnwidth}{!}{
+						\input{assets/chapter_2/receiver_ts.tex}
+					}
+					\label{fg:receiver_ts}
+				}
+				\\
+				\subfloat[Power splitting receiver]{
+					\resizebox{0.6\columnwidth}{!}{
+						\input{assets/chapter_2/receiver_ps.tex}
+					}
+					\label{fg:receiver_ps}
+				}
+				\\
+				\subfloat[Integrated receiver]{
+					\resizebox{0.6\columnwidth}{!}{
+						\input{assets/chapter_2/receiver_integrated.tex}
+					}
+					\label{fg:receiver_integrated}
+				}
+				\caption{
+					Architectures of a co-located \gls{swipt} receiver.
+				}
+				\label{fg:swipt_receiver_architectures}
+			\end{figure}
+
+			\begin{itemize}
+				\item \emph{Ideal receiver:} The received signal is used for both information decoding and energy harvesting.
+This is theoretically the most efficient design with a rectangle \gls{r-e} region but is unimplementable in practice due to hardware constraints.
+				\item \emph{\gls{ts} receiver:} Each time frame is divided into individual \gls{wit} and \gls{wpt} phases, where the receiver switches between information decoder and energy harvester, respectively.
+The transmitted waveform and \gls{ris} response are optimized independently for each phase, and the resulting \gls{r-e} region is a triangle with two vertices corresponding to \gls{wit}-only and \gls{wpt}-only.
+				\item \emph{\gls{ps} receiver:} The received signal is split into two parts with power ratio $\rho$ and $1{-}\rho$.
+The former is fed into the energy harvester and the latter is used for information decoding.
+The transmitter and \gls{ris} are jointly optimized for both purposes with the knowledge of splitting ratio, and the resulting \gls{r-e} region may be non-convex.
+				\item \emph{Integrated receiver \cite{Kim2021a}:} The transmit signal is modulated in properties that can be well-preserved after rectification (e.g., pulse position) such that information can be decoded from the energy harvester output.
+			\end{itemize}
+
+			The most popular architectures in the literature are \gls{ts} and \gls{ps} due to their practicality and tractability.
+			The \gls{r-e} region of the former can be inferred from that of the latter, since the \gls{wit}-only and \gls{wpt}-only vertices in \gls{ts} correspond to $\rho=1$ and $\rho=0$ in \gls{ps}, respectively.
+			Integrated receiver eliminates the need of \gls{rf} chains and advanced architectures, but experiences information degradation and works better for low-throughput applications.
+		\end{subsubsection}
 	\end{subsection}

### 2024-03-24 content/chapter_2.tex
:pencil: Add BackCom introduction and MCS

@@
 				}
-				\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. The figure is from \cite{Shen2020a}.}
+				\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: Modified from \cite{Shen2020a}.}
 				\label{fg:bd_ris_architecture_1}
@@
 The group size is a design parameter to balance the circuit complexity and scattering performance.
-The figure is from \cite{Shen2020a}.}
+Source: Modified from \cite{Shen2020a}.}
 				\label{fg:bd_ris_architecture_2}
@@
 \begin{section}{\glsfmtfull{bc}}
-	\begin{subsection}{\glsfmtfull{mbc}}
+	\begin{subsection}{Introduction}
+		The scattered waves from any object inherently contain some information about the object.
+		This contributed to the great success of radar in the World War II, where the ``objective'' information about the target (e.g., size, speed, and position) can be extracted from the reflected signal.
+		Soon after the war in 1948, Stockman demonstrated the concept of \gls{bc} where the target is no longer a dumb wave scatterer but part of the communication system that is willing to modulates its ``subjective'' information over the reflected signal \cite{Stockman1948}.
+		The communication society quickly realized its potential to separate the power-hungry \gls{rf} carrier emitter with the low-power information modulator, which is essential for miniaturizing wireless devices and increasing the network scale.
+		As shown in Figs.
+\subref*{fg:backcom_monostatic} and \subref*{fg:backcom_bistatic} on Page \pageref{fg:wipt_schemes}, the backscatter node (a.k.a.
+tag) is activated by an energy signal (also functions as carrier) in the downlink and modulates over the scattered signal in the uplink.
+The energy transmitter (a.k.a.
+carrier emitter) and information receiver (a.k.a.
+reader) can be either co-located or separated, known respectively as monostatic and bistatic \gls{bc}.
 
+		One of the most well-known \gls{bc} applications is \gls{rfid} which made its debut in the 1970s \cite{Landt2005}.
+		\gls{rfid} readers sends a query signal and exploit the reflected signal from nodes (attached to objects) to identify and track them.
+		The nodes can be powered wirelessly by the impinging wave and does not have to be in the vicinity of the reader.
+		It has been standardized in ISO/IEC 18000 and EPC Gen2 \cite{Abbasi2021a} and widely used in supply chain management, access control, and asset tracking.
+		On the other hand, \gls{bc} also plays an important role in emerging applications like \gls{iot}, \gls{wsn}, and \gls{m2m} communications.
+		Their main difference to \gls{rfid} is that the message is no longer a static identifier but can be dynamically sensed from the environment or generated on demand.
+		This enables a new paradigm of self-sustainable, intelligent, and pervasive sensing and communication, which is a key building block for our initial vision.
+
+		Nevertheless, low throughput and limited coverage are acknowledged as two critical problems for conventional \gls{bc} systems.
+		Those are inevitably inherited from the nature of wave scattering --- the radiated signal has to travel a round trip (emitter-node-reader) with double pathloss, while the scatter response is frequency-dependent and usually results in a narrow bandwidth.
+		Monostatic \gls{bc} is also subject to a strong self-interference that further degrades the error performance and achievable rate.
+		Finally, the nodes are idle most of the time and only respond when externally inquired.
+		This is in sharp contrast to \gls{ris} where the elements are contributing for channel enhancement all the time.
+		To mitigate those issues, multi-antenna techniques and special modulation schemes are two promising solutions in the literature.
+		For example, a multi-antenna carrier emitter can perform energy beamforming \cite{Yang2015b}, a multi-antenna node can perform energy combining with spatial modulation \cite{Chen2020,Goudeli2020} or space-time coding \cite{Liu2021a}, and a multi-antenna reader can perform coherent \cite{He2020d,Wang2021b} or non-coherent \cite{Devineni2021} detection.
+		We will discuss some popular modulation and coding techniques for \gls{bc} in the following subsection.
 	\end{subsection}
 
-	\begin{subsection}{\glsfmtfull{bbc}}
+	\begin{subsection}{Modulation and Coding Schemes}
+		\gls{bc} and \gls{ris} share the same wave scattering model in Section \ref{sc:principles}, but the reflection coefficient $\Gamma$ in \eqref{eq:reflection_coefficient} is exploited in different manners.
+		The difference is two-fold:
+		\begin{itemize}
+			\item \emph{Modulation requires variation:} \gls{bc} relies on dynamically changing the reflection coefficient over time to encode information.
+This is different from \gls{ris} where the optimal configuration (and reflection coefficient) is fixed for a given channel realization.
+			\item \emph{Harvesting requires absorption:} Part of the impinging wave should be fed into the node to power its operation.
+This is different from \gls{ris} where a full reflection is desired to maximize its channel control capability.
+		\end{itemize}
+		Denote the amplitude scattering ratio of the \gls{bc} node as $\alpha$, i.e., the power absorption ratio is $(1-\alpha)^2$. Some popular modulation schemes are summarized below:
+		\begin{itemize}
+			\item \emph{\gls{qam} \cite{Thomas2012a}:} The reflection coefficient corresponding to the $m$-th symbol is
+			\begin{equation}
+				\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert}
+			\end{equation}
+			where $c_m$ is the corresponding constellation point.
+			This scheme is simple but exhibits a low detection \gls{snr} especially when the constellation size is large.
+			\item \emph{\gls{fsk} \cite{Abbasi2021a}:} For 2-\gls{fsk}, the reflection coefficient is
+			\begin{equation}
+				\Gamma(t) =
+				\begin{cases}
+					\alpha, & t \in \bigl[\frac{n}{\Delta f},\frac{2n+1}{2 \Delta f}\bigr) \\
+					-\alpha, & t \in \bigl[\frac{2n+1}{2 \Delta f},\frac{n+1}{\Delta f}\bigr)
+				\end{cases}
+				= \frac{\pi}{4} \sum_{m=1,\text{odd}}^\infty \frac{1}{m} \sin\bigl(2\pi m \Delta f t\bigr),
+			\end{equation}
+			where $n \in \mathbb{N}$.
+			If the incident wave is a \gls{cw} at frequency $f_0$, the reflected signal is dominated by its first harmonic
+			% \begin{equation}
+			% 	y(t) = \sum_{m=1,\text{odd}}^\infty \frac{\pi}{4m} \cos(2 \pi f_0 t) \sin\bigl(2\pi m \Delta f t\bigr),
+			% \end{equation}
+			\begin{equation}
+				s_1(t) = \frac{\pi}{2} \Bigl(\sin\bigl(2 \pi (f_0 {+} \Delta f) t\bigr) - \sin\bigl(2 \pi (f_0 {-} \Delta f) t\bigr)\Bigr).
+			\end{equation}
+			That is, periodically switching the reflection coefficient at rate $\Delta f$ results in a frequency shift $\pm \Delta f$ on the reflected signal.
+			Practical implementations have been demonstrated on a variety of license-free protocols (e.g., HitchHike \cite{Zhang2016a}, Inter-Technology \cite{Iyer2016}, Passive Wi-Fi \cite{Kellogg2017}, \gls{ble}-Backscatter \cite{Ensworth2017}) where the mirror copy can be suppressed.
+			\item \emph{\gls{css} \cite{Talla2017}:} A chirp is a signal whose frequency increases or decreases over time.
+			\gls{css} uses wideband linear-frequency modulated chirps to encode information, which is from \gls{dsss} and \gls{fsss} with pseudo-random sequences and \gls{fsk} with discrete frequencies.
+			In particular, $N+1$ reflection coefficients of the same envelope are sequentially selected at a regular rate $\Delta f$, given by
+			\begin{equation}
+				\Gamma_n = \alpha \exp(\jmath \phi_n), \quad n \in \{0, 1, \ldots, N\},
+			\end{equation}
+			where $\phi_n = \frac{2 \pi}{\Delta f}(A n^2 + B n)$ and $A$, $B$ are constants.
+			As the core modulation scheme in \gls{lora}, it is more robust to noise and interference (with a reception sensitivity of -149 dBm), harder to be detected by eavesdroppers, and can be used for ranging and localization \cite{Abbasi2021a}.
 
+			Common \gls{bc} channel coding schemes include unipolar \gls{rz} and \gls{nrz}, Manchester, differential, pulse-pause and FM0.
+			They are not the focus of the thesis and the readers are referred to \cite[Chapter 2.3]{Hoang2020} for details.
+		\end{itemize}
 	\end{subsection}
 
-	\begin{subsection}{\glsfmtfull{ambc}}
+	\begin{subsection}{Applications}
+		\begin{subsubsection}{\glsfmtfull{mbc}}
 
-	\end{subsection}
+		\end{subsubsection}
 
-	\begin{subsection}{\glsfmtfull{sr}}
+		\begin{subsubsection}{\glsfmtfull{bbc}}
 
+		\end{subsubsection}
+
+		\begin{subsubsection}{\glsfmtfull{ambc}}
+
+		\end{subsubsection}
+
+		\begin{subsubsection}{\glsfmtfull{sr}}
+
+		\end{subsubsection}
 	\end{subsection}
@@
 
-\begin{section}{\glsfmtfull{mimo}}
-	\begin{subsection}{\glsfmtfull{pc}: Channel Shaping}
+% \begin{section}{\glsfmtfull{mimo}}
+% 	\begin{subsection}{\glsfmtfull{pc}: Channel Shaping}
 
-	\end{subsection}
+% 	\end{subsection}
 
-	\begin{subsection}{\glsfmtfull{ic}: Interference Alignment}
+% 	\begin{subsection}{\glsfmtfull{ic}: Interference Alignment}
 
-	\end{subsection}
-\end{section}
+% 	\end{subsection}
+% \end{section}

### 2024-03-24 misc/glossaries.tex
:pencil: Add BackCom introduction and MCS

@@
 \newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
-\newacronym{bbc}{BBC}{Bistatic \glsfmtlong{bc}}
+\newacronym{bbc}{BBC}{Bistatic Backscatter Communication}
 \newacronym{bcd}{BCD}{Block Coordinate Descent}
@@
 \newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
-\newacronym{csit}{CSIT}{\glsfmtlong{csi} at the Transmitter}
+\newacronym{csit}{CSIT}{Channel State Information at the Transmitter}
 \newacronym{csi}{CSI}{Channel State Information}
@@
 \newacronym{mac}{MAC}{Multiple Access Channel}
-\newacronym{mbc}{MBC}{Monostatic \glsfmtlong{bc}}
+\newacronym{mbc}{MBC}{Monostatic Backscatter Communication}
 \newacronym{mc}{MC}{Multiplication Coding}
@@
 \newacronym{mse}{MSE}{Mean-Square Error}
-\newacronym{nlos}{NLoS}{Non-\glsfmtlong{los}}
+\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
 \newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
@@
 \newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
-\newacronym{rfid}{RFID}{\glsfmtlong{rf} Identification}
+\newacronym{rfid}{RFID}{Radio-Frequency Identification}
 \newacronym{rf}{RF}{Radio-Frequency}
@@
 \newacronym{ble}{BLE}{Bluetooth Low Energy}
+\newacronym{lora}{LoRa}{Long Range}
 \newacronym{lorawan}{LoRaWAN}{Long Range Wide Area Network}
@@
 \newacronym{papr}{PAPR}{Peak-to-Average Power Ratio}
+\newacronym{fsk}{FSK}{Frequency-Shift Keying}
+\newacronym{css}{CSS}{Chirp Spread Spectrum}
+\newacronym{dsss}{DSSS}{Direct-Sequence Spread Spectrum}
+\newacronym{fsss}{FSSS}{Frequency-Hopping Spread Spectrum}
+\newacronym{rz}{RZ}{Return-to-Zero}
+\newacronym{nrz}{NRZ}{Non-Return-to-Zero}
 

### 2024-03-24 assets/chapter_2/ambc.tex
:pencil: Add abstract and BackCom applications

\begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
	\node at (1.5,3.5) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (6.5,3) [rectangle,minimum size=1cm] {};
	\node at (8,0.35) [dart,shape border rotate=270,minimum width=1cm] {};

	\node[draw=none] at (0,-1.375) {Primary\\Transmitter};
	\node[draw=none] at (1,4.375) {Backscatter\\Reader};
	\node[draw=none] at (7,4.375) {Scatter\\Node};
	\node[draw=none] at (8,-1.375) {Primary\\Receiver};

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.5) -- (7.5,-0.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.25,1) -- (0.75,3);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.75,0.25) -- (5.5,2.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (5.5,3.5) -- (2.5,3.5);
	\draw[magenta,decorate,decoration={crosses,segment length=16mm,shape size=1.5mm}] (5.11,3.5) -- (2.5,3.5);
	\draw[lightgray,decorate,decoration={waves,segment length=4mm,radius=2mm}] (7.43,3.28) -- (8,1);
	\draw[lightgray,decorate,decoration={crosses,segment length=16mm,shape size=1.5mm}] (7.525,2.9) -- (8,1);

	\node[draw=none] at (4,0.35) {Modulated};
	\node[draw=none] at (4,3.95) {Doubly-};
	\node[draw=none] at (4,3) {Modulated};
\end{tikzpicture}

### 2024-03-24 assets/chapter_2/bbc.tex
:pencil: Add abstract and BackCom applications

\begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+90,minimum size=1cm,minimum height=1cm,anchor=north] {};
	\node at (5,2) [rectangle,minimum size=1cm] {};
	\node at (8,0) [isosceles triangle,isosceles triangle stretches,shape border rotate=+270,minimum size=1cm,minimum height=1cm,anchor=north] {};

	\node[draw=none] at (0,-1.95) {Carrier\\Emitter};
	\node[draw=none] at (5,3.35) {Scatter\\Node};
	\node[draw=none] at (8,-1.95) {Backscatter\\Reader};

	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (1,-1) -- (7.5,-1);
	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0) -- (4,2);
	\draw[magenta,decorate,decoration={snake,pre length=7.5mm,post length=7.5mm},-latex] (6,2) -- (8,0.35);

	\node[draw=none] at (1.5,1.75) {Carrier};
	\node[draw=none] at (7.2,1.7) {1};
	\node[draw=none] at (6.6,2.25) {0};
	\node[draw=none] at (7.8,1.15) {0};
\end{tikzpicture}

### 2024-03-24 assets/chapter_2/mbc.tex
:pencil: Add abstract and BackCom applications

\begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [kite,minimum size=0.75cm,kite vertex angles=60] {};
	\node at (8,3) [rectangle,minimum size=1cm] {};

	\node[draw=none] at (0,-1.125) {Interrogator};
	\node[draw=none] at (8,4.375) {Scatter\\Node};

	\draw[lightgray,decorate,decoration={snake,post length=2.5mm},-latex] (0.5,0.75) -- (7,3);
	\draw[magenta,decorate,decoration={snake,pre length=2cm,post length=2cm},-latex] (7.25,2.25) -- (0.75,0);

	\node[draw=none] at (3.5,2.625) {Carrier};
	\node[draw=none] at (4.2,0.5) {1};
	\node[draw=none] at (2,-0.125) {0};
	\node[draw=none] at (6.4,1.3) {0};
\end{tikzpicture}

### 2024-03-24 content/abstract.tex
:pencil: Add abstract and BackCom applications

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{abstract}
	\gls{ris} is the most promising physical-layer technology for 6G.
	It adopts many low-power scattering elements to customize the propagation environment for improved network performance, unlocking a new potential of \emph{channel design} as never before.
	In this dissertation, we first provide an overview of its structure, characteristics, applications, principles, and models, then discuss how it addresses the key issues in \gls{swipt} and compare it with \gls{bc} in terms of functionalities, principles, models, and preferences.
	The work chapters investigate three typical use cases of \gls{ris}: Joint design with transceiver for a particular objective (beamforming); ride its own information over legacy networks (modulation); and manipulate the wireless environment as a stand-alone device (channel shaping).
	In particular,
	\begin{itemize}
		\item \emph{\gls{ris}-aided \gls{swipt}:} We introduce \gls{ris} into multi-antenna, multi-carrier \gls{swipt} systems, investigating joint waveform and beamforming design for maximizing harvested energy under various communication rate constraints. Algorithms, performance trade-offs, and asymptotic behaviors are analyzed.
		\item \emph{RIScatter:} This novel scatter protocol integrates \gls{ris} and \gls{bc} from an input distribution perspective. The reflection pattern is exploited simultaneously for primary-link beamforming and backscatter-link modulation. We propose a practical cooperative receiver, characterize the achievable rate region, and analyze the impact of system parameters.
		\item \emph{\gls{mimo} channel shaping:} We exploit an advanced \gls{bd}-\gls{ris} architecture for singular value redistribution and power maximization in \gls{pc}, and leakage interference minimization in \gls{ic}.
		Their implications on rate-optimal joint designs are also discussed.
		We highlight the unique features of \gls{bd}-\gls{ris} and propose an efficient design framework.
	\end{itemize}
\end{abstract}

### 2024-03-24 content/chapter_1.tex
:pencil: Add BackCom introduction and MCS
:pencil: Add abstract and BackCom applications

@@
 		\item \emph{How does \gls{ris} impact different wireless applications such as communication and far-field power transfer?}
-		\item \emph{Is it possible to integrate \gls{ris} with \gls{bc} into a versatile tool that blurs the boundary between the network and environment?}
+		\item \emph{Is it possible to integrate \gls{ris} with other scattering applications into a versatile tool that blurs the boundary between the network and environment?}
 		\item \emph{What is the ultimate limit of channel reshaping through passive \gls{ris} and what are the implications on transceiver designs?}
@@
 	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications.
-	A detailed literature review and technical discussion on \gls{ris} and other topics will be reserved for Chapter \ref{ch:background}.
+	A detailed literature review and technical discussion on \gls{ris} and other technologies will be reserved for Chapter \ref{ch:background}.
 \end{section}
@@
 			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
-			\caption{A typical architecture of \gls{ris}. The figure is modified from \cite{Wu2020}.}
+			\caption{A typical architecture of \gls{ris}. Source: Modified from \cite{Wu2020}.}
 			\label{fg:ris_architecture}
@@
 		\item Chapter \ref{ch:introduction} provides an overview of the thesis.
-It introduces the motivation and objectives, discusses the characteristics and applications of \gls{ris}, and summarizes the topics and contributions of each research chapter.
+It introduces the motivation and objectives, raise critical research questions, discusses the characteristics and applications of \gls{ris}, and summarizes the contributions of each research chapter.
 A list of publications is also provided.
-		\item Chapter \ref{ch:background} provides the necessary background knowledge for the subsequent chapters, including the fundamental principles, hardware implementation, signal and system models, performance metrics, and design challenges for \gls{ris}, \gls{wpt}, \gls{swipt}, \gls{bc}, and \gls{mimo} systems.
-It also reviews the state-of-the-art research in relevant topics and raise critical questions to be addressed in the following chapters.
+		\item Chapter \ref{ch:background} provides necessary background knowledge for \gls{ris}, \gls{wpt}, \gls{swipt}, and \gls{bc}.
+It covers fundamental principles, hardware implementation, signal and system models, performance metrics, design challenges, and state-of-the-art research.
 		\item Chapter \ref{ch:ris_aided_swipt} investigate the impact of \gls{ris} on wireless information and power transfer. The key contributions include:

### 2024-03-24 content/chapter_2.tex
:pencil: Add abstract and BackCom applications

@@
 \chapter{Background}\label{ch:background}
+
+This chapter provides essential background for topics covered in the thesis. A detailed literature review will be presented within each research chapter.
 
@@
 				\caption{
-					Information and energy flows in \gls{swipt} and \gls{bc} systems. Blue and black parts denote information and power subsystems, respectively.
+					Information and energy flows in \gls{swipt} and \gls{bc} systems. The blue and black parts denote information and power subsystems, respectively.
 				}
@@
 	\begin{subsection}{Applications}
+		\begin{figure}[!t]
+			\centering
+			\subfloat[Monostatic backscatter]{
+				\resizebox{0.48\linewidth}{!}{
+					\input{assets/chapter_2/mbc.tex}
+				}
+				\label{fg:mbc}
+			}
+			\subfloat[Bistatic backscatter]{
+				\resizebox{0.48\linewidth}{!}{
+					\input{assets/chapter_2/bbc.tex}
+				}
+				\label{fg:bbc}
+			}
+			\\
+			\subfloat[Ambient backscatter]{
+				\resizebox{0.48\linewidth}{!}{
+					\input{assets/chapter_2/ambc.tex}
+				}
+				\label{fg:ambc}
+			}
+			\subfloat[Symbiotic radio]{
+				\resizebox{0.48\linewidth}{!}{
+					\input{assets/chapter_2/sr.tex}
+				}
+				\label{fg:sr}
+			}
+			\caption{
+				Illustration of scattering applications.
+				The blue flows denote the primary link while the magenta flows denote the backscatter link.
+			}
+		\end{figure}
+
 		\begin{subsubsection}{\glsfmtfull{mbc}}
-
+			\gls{mbc} is the most common architecture where the carrier emitter and reader are integrated into one device called interrogator.
+			As shown in \subref*{fg:backcom_monostatic} and \subref*{fg:mbc}, the interrogator transmits a \gls{cw} in the downlink and receives the reflected information-bearing signal in the uplink.
+			The node varies its load impedance over time to switch between two states.
+			Ideally, a full absorption (perfect matching, $\Gamma_0 = 0$) maps to bit ``0'' where energy is harvested, and a full reflection (perfect mismatch, $\lvert \Gamma_1 \rvert = 1$) maps to bit ``1'' where \gls{snr} is determined.
+			\gls{mbc} is widely used in \gls{rfid} systems.
+			The integrated transceiver design reduces the hardware cost but suffers from strong self-interference and limited coverage.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{\glsfmtfull{bbc}}
-
+			\gls{bbc} separates the carrier emitter and reader into two individual devices, as illustrated in \subref*{fg:backcom_bistatic} and \subref*{fg:bbc}.
+			This helps to combat self-interference and extend the operation range, but the system involves three devices and requires more complex coordination and synchronization.
+			It is more popular in more complicated scenarios like \gls{wsn} and \gls{iot} with potentially moving nodes.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{\glsfmtfull{ambc}}
-
+			\gls{ambc} has been recognized as a revolutionary technology since its debut in 2013 \cite{Liu2013b}.
+			As shown in \subref*{fg:ambc}, it gets rid of dedicated \gls{rf} sources and relies on ambient signals (e.g., TV, FM, and Wi-Fi) for both energy harvesting and information transfer.
+			Compared with \gls{mbc} and \gls{bbc}, its carrier waveform is no longer a \gls{cw} but a mixture of already modulated signals with different frequencies and amplitudes, which makes the detection more challenging.
+			Therefore, it often employs \gls{fsk} modulation to shift the scattered signals to a different band for reduced interference on both coexisting systems.
+			\gls{ambc} is a plug-and-play and environmental-friendly \gls{iot} solution, but its practical deployment is limited by the availability and quality of ambient signals.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{\glsfmtfull{sr}}
-
+			\gls{sr} is a relatively new concept proposed in 2019 that introduced itself as ``cooperative \gls{ambc}'' \cite{Guo2019b}.
+			As shown in \subref*{fg:sr}, it shares not only the transmitter, \gls{rf} source, but also the receiver with a primary transmission.
+			This is different from traditional \gls{ambc} where the legacy system can be unaware of the backscatter link and the node wants to minimize its footprint.
+			Such a symbiotic interaction can improve the reliability of the backscatter link as well as the energy efficiency of the primary link, but unavoidably challenges the system design.
+			For example, the acquisition of backscatter \gls{csi} can be difficult due to its passive characteristic, the detection of node message may involve complicated signal processing like \gls{sic}, and the synchronization of both links can be nontrivial due to the load-switching constraints.
+			If those issues can be mitigated, \gls{sr} would be a win-win solution that supercharges resource-constrained devices by leveraging the existing network infrastructure.
 		\end{subsubsection}

### 2024-03-24 content/declaration.tex
:pencil: Add abstract and BackCom applications

@@
 \begin{declaration}
-
-I hereby declare that the contents presented in this dissertation are original and have been carried out by myself under the guidance of my supervisor Prof. Bruno Clerckx.
+	The contents presented in this dissertation are original and have been carried out by myself under the guidance of my supervisor Prof. Bruno Clerckx.
 	Any work from other researchers, scholars, or sources have been properly cited and acknowledged.
@@
 
+	Any comments, suggestions, or corrections are greatly acknowledged and can be sent to \href{mailto:i@snowztail.com}{\url{i@snowztail.com}}.
 	The source code of all simulation results in this dissertation are publicly available at \url{https://github.com/snowztail/}.
-
+	Finally, I would like to appreciate Bruno, my colleagues, and whoever is reading this dissertation.
 \end{declaration}

### 2024-03-25 assets/chapter_3/channel_amplitude.tex
:construction: Updating notations

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
\definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=3, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00540099400856952\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No RIS}

\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00757609645318138\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{WIT-optimized}

\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00757609644840316\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{WPT-optimized}

\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00314170999160457\\
2	0.00572485908105548\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00502314747430184\\
2	0.00698106265038798\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00330170889121358\\
2	0.00768466635770749\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
ylabel style={font=\color{white!15!black}},
ylabel={Channel amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0016696476908254\\
2	0.00438348129943761\\
3	0.00457133324563245\\
4	0.00586320993785494\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00326549483873511\\
2	0.00557307586676685\\
3	0.00614450761039544\\
4	0.00726164815517615\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00166671759288851\\
2	0.0056728199729895\\
3	0.00568370327308551\\
4	0.00789867646413342\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.00121164184157658\\
2	0.00238340383353008\\
3	0.00380683420957256\\
4	0.00397337725168322\\
5	0.00492524818026471\\
6	0.00528740868681232\\
7	0.00572071220385092\\
8	0.00587459497346489\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00264154779713112\\
2	0.00407667250014311\\
3	0.0049500895867949\\
4	0.00561010487339341\\
5	0.00637593781159189\\
6	0.0066081911104957\\
7	0.00719542472167268\\
8	0.00721447474714219\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00139675837927404\\
2	0.00297327122282322\\
3	0.00519768343232529\\
4	0.00524568965358895\\
5	0.00679027772006842\\
6	0.00680292145999757\\
7	0.00768611044981794\\
8	0.00771790378640739\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
bar shift auto,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=0.01,
ytick={   0, 0.01},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
]
\addplot[ybar, bar width=0.178, fill=mycolor1, draw=black, area legend] table[row sep=crcr] {%
1	0.0011086419762005\\
2	0.00139817672195447\\
3	0.00200749223129634\\
4	0.00276896018192483\\
5	0.00348858569071252\\
6	0.00390863609607119\\
7	0.00410205684728188\\
8	0.00421746375099375\\
9	0.0046579451399174\\
10	0.00494987881895202\\
11	0.00517723522936086\\
12	0.00554845359626313\\
13	0.00558432983698075\\
14	0.00581133838542614\\
15	0.00582728083668895\\
16	0.00588378650142745\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor2, draw=black, area legend] table[row sep=crcr] {%
1	0.00243240737767257\\
2	0.00291012490661641\\
3	0.00364483122694576\\
4	0.00450699183712641\\
5	0.00487492494056207\\
6	0.00519805292278296\\
7	0.00528263562038442\\
8	0.00589785004825321\\
9	0.0059831692545346\\
10	0.00639251285950617\\
11	0.00669911334288142\\
12	0.00680111371923813\\
13	0.00709923174422509\\
14	0.0071115147925566\\
15	0.00725582025143191\\
16	0.00726750007562416\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ybar, bar width=0.178, fill=mycolor3, draw=black, area legend] table[row sep=crcr] {%
1	0.00123628236378877\\
2	0.00164057003125897\\
3	0.00244260991306404\\
4	0.00355854925167237\\
5	0.00469336613331463\\
6	0.00513906379517623\\
7	0.00552284927791181\\
8	0.00566659546513512\\
9	0.00636655282038687\\
10	0.0064643206674846\\
11	0.00710638804550398\\
12	0.00714275219594531\\
13	0.00755098826468563\\
14	0.00759919845334804\\
15	0.00776427719266845\\
16	0.00777739000911697\\
};
\addplot[forget plot, color=white!15!black] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2024-03-25 assets/chapter_3/waveform_wit_modulated.tex
:construction: Updating notations

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,3.296in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{RIS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No RIS: {\boldmath${s}$}$_{\mathrm{I}}$}

\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,2.586in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=3.16339693422903,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16197544010622\\
2	3.16257985135002\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16115798980538\\
2	3.16339693422903\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,1.877in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=2.24021589430493,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23378952118842\\
2	2.23654464483002\\
3	2.23679993610816\\
4	2.23713622127432\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.22545319620151\\
2	2.23919103086275\\
3	2.23937811584463\\
4	2.24021589430493\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=2,
ytick={0, 1, 2},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.57492536161738\\
2	1.58019558798915\\
3	1.58142030797172\\
4	1.58199169722726\\
5	1.58244513043393\\
6	1.58255247448636\\
7	1.58277901011216\\
8	1.58278544606781\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.54658301793324\\
2	1.57890604600973\\
3	1.58567053153604\\
4	1.58602764687811\\
5	1.58742152113889\\
6	1.58776504632019\\
7	1.58809335949322\\
8	1.5881928373826\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=2,
ytick={0, 1, 2},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10693759886133\\
2	1.11152957304454\\
3	1.1153740214668\\
4	1.11770662066146\\
5	1.11834620668734\\
6	1.11879936603067\\
7	1.11890444505621\\
8	1.11953756000214\\
9	1.11961027059849\\
10	1.1199195311366\\
11	1.12011494881618\\
12	1.12017416958603\\
13	1.12033284686217\\
14	1.12033895948864\\
15	1.12040846172897\\
16	1.12041390652564\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.05608889731275\\
2	1.08431501210806\\
3	1.10834050856176\\
4	1.11891055117252\\
5	1.12321530567299\\
6	1.12470216682288\\
7	1.12523793678797\\
8	1.12552298915589\\
9	1.12642268676024\\
10	1.12689100352585\\
11	1.127202079253\\
12	1.12763006638833\\
13	1.12766695997673\\
14	1.12788476342969\\
15	1.1278991085713\\
16	1.12794901573584\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2024-03-25 assets/chapter_3/waveform_wpt_modulated.tex
:construction: Updating notations

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,3.251in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595034367\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{RIS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213593685897\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No RIS: {\boldmath${s}$}$_{\mathrm{I}}$}

\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,2.553in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000570870326956724\\
2	4.4721359179404\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0110856763978608\\
2	4.47212221176042\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,1.855in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=5,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.82810775851695e-05\\
2	3.53085892593064e-05\\
3	3.54347120351704e-05\\
4	4.42555930751421\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.22676166428777e-05\\
2	2.19662118918467e-05\\
3	2.35611473414708e-05\\
4	4.38314990531919\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,1.157in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	6.25263040326118e-06\\
2	6.27921380470113e-06\\
3	6.34955721457943e-06\\
4	6.35150273149039e-06\\
5	6.42390701416729e-06\\
6	6.42457974220412e-06\\
7	6.47741859691329e-06\\
8	6.47969375628299e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.07597912435039e-05\\
2	2.10621157490525e-05\\
3	2.27177871268911e-05\\
4	2.34764127724776e-05\\
5	0.000633429285281999\\
6	0.00299168089473067\\
7	0.0168627108170759\\
8	0.0302609478988545\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.46841221768753e-06\\
2	1.46853581584948e-06\\
3	1.46888556831603e-06\\
4	1.46960879811052e-06\\
5	1.47063822579491e-06\\
6	1.47112726920342e-06\\
7	1.47158812622008e-06\\
8	1.47177039924161e-06\\
9	1.47273523214333e-06\\
10	1.47288042283048e-06\\
11	1.47389962773962e-06\\
12	1.47396082891411e-06\\
13	1.47467419234042e-06\\
14	1.47476166458671e-06\\
15	1.47506643379659e-06\\
16	1.47509099313304e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.08632407458004e-05\\
2	1.08877007745949e-05\\
3	1.09594364217047e-05\\
4	1.10938027865036e-05\\
5	1.12827891666553e-05\\
6	1.15378065652616e-05\\
7	1.19617266900702e-05\\
8	1.41613520483063e-05\\
9	6.92466622068608e-05\\
10	0.000224790946436711\\
11	0.000536194940235116\\
12	0.0020179447121528\\
13	0.00228142595005787\\
14	0.00484194141261625\\
15	0.00509975660438143\\
16	0.00611499201390601\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2024-03-25 assets/chapter_3/waveform_wpt_multisine.tex
:construction: Updating notations

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,3.198in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	0.000179640013528533\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{RIS: {\boldmath${s}$}$_{\mathrm{P}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000397123673947016\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No RIS: {\boldmath${s}$}$_{\mathrm{P}}$}

\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,2.513in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.79500700797208e-06\\
2	4.08912055500049e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.49290916575988e-05\\
2	1.5984007495811e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.828in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=1,
ytick={0, 1},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.7047574186968e-05\\
2	5.43653691324513e-05\\
3	5.45654270177953e-05\\
4	0.643758338055473\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.36848368645437e-05\\
2	2.47445070835246e-05\\
3	2.69448998495505e-05\\
4	0.887691893042722\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,1.143in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0867788582585271\\
2	0.354584687432597\\
3	0.978311956865194\\
4	1.00526014633142\\
5	1.77421254564815\\
6	1.81146146011329\\
7	2.39316922290828\\
8	2.39637542235877\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0902176300392888\\
2	0.346545381997116\\
3	0.920392715728033\\
4	1.00603974348273\\
5	1.68636658487784\\
6	1.88211529376329\\
7	2.36040788303805\\
8	2.46040714408403\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.407in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0464370103565898\\
2	0.0888998754115983\\
3	0.182477468723257\\
4	0.351067698858224\\
5	0.586511157963407\\
6	0.614337078252067\\
7	0.810319773242887\\
8	0.860994249853337\\
9	1.10132170987082\\
10	1.14707079761106\\
11	1.39883656543765\\
12	1.41535986846215\\
13	1.61724209266044\\
14	1.62252465458191\\
15	1.72749872908311\\
16	1.73005229015507\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0510852453116461\\
2	0.0931309188028207\\
3	0.185327611314329\\
4	0.340208570070271\\
5	0.54797982875002\\
6	0.640935330786823\\
7	0.791412536150533\\
8	0.84579943866006\\
9	1.06112099796475\\
10	1.16793555562456\\
11	1.33939925851288\\
12	1.47707717171709\\
13	1.57685904146789\\
14	1.6756197826186\\
15	1.71965928671636\\
16	1.75172173644803\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2024-03-25 content/chapter_3.tex
:pencil: Add wave scattering models
:construction: Updating notations

@@
 \gls{swipt} is a promising solution to connect and power mobile devices via \gls{rf} waves.
-It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and \gls{m2m} networks.
+It provides low power at milliwatt level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the \gls{iot} and \gls{m2m} networks.
 The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on \gls{wpt} and \gls{swipt} \cite{Clerckx2019}.
@@
 A low-complexity adaptive waveform design by \gls{smf} was proposed in \cite{Clerckx2017} to exploit the rectifier nonlinearity, whose advantage was then demonstrated in a prototype with channel acquisition \cite{Kim2017}.
-Beyond \gls{wpt}, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to \gls{swipt} design, namely (i) modulated and unmodulated waveforms are not equally suitable for wireless power delivery; (ii) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the \gls{r-e} region; (iii) a combination of \gls{ps} and \gls{ts} is generally the best strategy; (iv) the optimal input distribution is not the conventional \gls{cscg}; (v) modeling rectifier nonlinearity is beneficial to system performance and essential to efficient \gls{swipt} design.
+Beyond \gls{wpt}, \cite{Clerckx2018b} uniquely showed that the rectifier nonlinearity brings radical changes to \gls{swipt} design, namely:
+		\begin{itemize}
+			\item Modulated and unmodulated waveforms are not equally suitable for wireless power delivery;
+			\item A multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform can enlarge the \gls{r-e} region;
+			\item A combination of \gls{ps} and \gls{ts} is generally the best strategy;
+			\item The optimal input distribution is not the conventional \gls{cscg};
+			\item Modeling rectifier nonlinearity is beneficial to system performance and essential to efficient \gls{swipt} design.
+		\end{itemize}
 		Those observations, validated experimentally in \cite{Kim2019}, led to the question: \emph{What is the optimal input distribution for \gls{swipt} under nonlinearity?} This question was answered in \cite{Varasteh2020} for single-carrier \gls{swipt}, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier \gls{swipt}.
@@
 The hardware architecture, design challenges, and application opportunities of practical \gls{ris} were covered in \cite{Wu2020}.
-In \cite{Dai2020}, a prototype \gls{ris} with \num{256} \num{2}-bit elements based on \gls{pin} diodes was developed to support real-time video transmission at \si{GHz} and mmWave frequency.
+In \cite{Dai2020}, a prototype \gls{ris} with \num{256} \num{2}-bit elements based on \gls{pin} diodes was developed to support real-time video transmission at gigahertz and mmWave frequency.
 	\end{subsection}
@@
 To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this paper, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output \gls{dc} power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for \gls{swipt} with the passive beamforming capability of \gls{ris}, to investigate the \gls{r-e} tradeoff for one \gls{swipt} user with co-located information decoder and energy harvester.
-We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the \gls{r-e} region of \gls{ris}-aided \gls{swipt}?} The contributions of this paper are summarized as follows.
+In this chapter, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output \gls{dc} power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for \gls{swipt} with the passive beamforming capability of \gls{ris}, to investigate the \gls{r-e} tradeoff for one \gls{swipt} user with co-located information decoder and energy harvester.
+We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the \gls{r-e} region of \gls{ris}-aided \gls{swipt}?} The contributions of this chapter are summarized as follows.
 
@@
 The proposed joint waveform, active and passive beamforming architecture exploits the rectifier nonlinearity, the channel selectivity, and a beamforming gain across frequency and spatial domains to enlarge the achievable \gls{r-e} region.
-This is the first paper to propose a joint waveform, active and passive beamforming architecture for \gls{ris}-aided \gls{swipt}.
+This is the first work to propose a joint waveform, active and passive beamforming architecture for \gls{ris}-aided \gls{swipt}.
 
@@
 The \gls{ris} phase shift, active precoder, and waveform amplitude are updated iteratively until convergence.
-This is the first paper to jointly optimize waveform and active/passive beamforming in \gls{ris}-aided \gls{swipt}.
+This is the first work to jointly optimize waveform and active/passive beamforming in \gls{ris}-aided \gls{swipt}.
 
@@
 
-		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms.
-It is concluded that (i) \gls{ris} enables constructive reflection and flexible subchannel design in the frequency domain that is essential for \gls{swipt} systems; (ii) \gls{ris} mainly affects the effective channel instead of the waveform design; (iii) multisine waveform is beneficial to energy transfer especially when the number of subbands is large; (iv) \gls{ts} is preferred at low \gls{snr} while \gls{ps} is preferred at high \gls{snr}; (v) there exist two optimal \gls{ris} development locations, one close to the \gls{ap} and one close to the \gls{ue}; (vi) the output \gls{snr} scales linearly with the number of transmit antennas and quadratically with the number of \gls{ris} elements; (vii) due to the rectifier nonlinearity, the output \gls{dc} scales quadratically with the number of transmit antennas and quartically with the number of \gls{ris} elements; (viii) for narrowband \gls{swipt}, the optimal active and passive beamforming for any \gls{r-e} point are also optimal for the whole \gls{r-e} region; (ix) for broadband \gls{swipt}, the optimal active and passive beamforming depend on specific \gls{r-e} point and require adaptive designs; (x) the proposed algorithms are robust to practical impairments such as inaccurate cascaded \gls{csit} and finite \gls{ris} reflection states.
+		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that
+		\begin{itemize}
+			\item \gls{ris} enables constructive reflection and flexible subchannel design in the frequency domain that is essential for \gls{swipt} systems;
+			\item \gls{ris} mainly affects the effective channel instead of the waveform design;
+			\item Multisine waveform is beneficial to energy transfer especially when the number of subbands is large;
+			\item \gls{ts} is preferred at low \gls{snr} while \gls{ps} is preferred at high \gls{snr};
+			\item There exist two optimal \gls{ris} development locations, one close to the \gls{ap} and one close to the \gls{ue};
+			\item The output \gls{snr} scales linearly with the number of transmit antennas and quadratically with the number of \gls{ris} elements;
+			\item Due to the rectifier nonlinearity, the output \gls{dc} scales quadratically with the number of transmit antennas and quartically with the number of \gls{ris} elements;
+			\item For narrowband \gls{swipt}, the optimal active and passive beamforming for any \gls{r-e} point are also optimal for the whole \gls{r-e} region;
+			\item For broadband \gls{swipt}, the optimal active and passive beamforming depend on specific \gls{r-e} point and require adaptive designs;
+			\item The proposed algorithms are robust to practical impairments such as inaccurate cascaded \gls{csit} and finite \gls{ris} reflection states.
+		\end{itemize}
 	\end{subsection}
@@
 \begin{section}{System Model}\label{se:system_model}
-	\begin{figure}[!t]
+	\begin{figure}[H]
 		\centering
@@
 		\begin{equation}
-			\boldsymbol{x}_{\mathrm{I},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
+			\mathbf{x}_{\mathrm{I},n}(t) = \Re\left\{\mathbf{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
 		\end{equation}
-		where $\boldsymbol{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$.
+		where $\mathbf{w}_{\mathrm{I},n} \in \mathbb{C}^{M \times 1}$ is the information precoder at subband $n$, $\tilde{x}_{\mathrm{I},n}\sim\mathcal{CN}(0,1)$ is the information symbol at subband $n$, and $f_n$ is the frequency of subband $n$.
 On the other hand, the power signal transmitted over subband $n$ at time $t$ is
 		\begin{equation}
-			\boldsymbol{x}_{\mathrm{P},n}(t) = \Re\left\{\boldsymbol{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
+			\mathbf{x}_{\mathrm{P},n}(t) = \Re\left\{\mathbf{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
 		\end{equation}
-		where $\boldsymbol{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
+		where $\mathbf{w}_{\mathrm{P},n} \in \mathbb{C}^{M \times 1}$ is the power precoder at subband $n$. Therefore, the superposed signal transmitted over all subbands at time $t$ is
 		\begin{equation}
-			\boldsymbol{x}(t) = \Re{\left\{\sum_{n=1}^N(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
+			\mathbf{x}(t) = \Re{\left\{\sum_{n=1}^N(\mathbf{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\mathbf{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
 		\end{equation}
-		We also define $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$.
+		We also define $\mathbf{w}_{\mathrm{I/P}} \triangleq [\mathbf{w}_{\mathrm{I/P},1}^\mathsf{T},\dots,\mathbf{w}_{\mathrm{I/P},N}^\mathsf{T}]^\mathsf{T} \in \mathbb{C}^{MN \times 1}$.
 	\end{subsection}
@@
 		where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the \gls{ris}, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
-This paper sticks to the most common \gls{ris} model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical \gls{ris}-aided \gls{swipt}.} and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\boldsymbol{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the \gls{ris} vector and matrix, respectively.
+This chapter sticks to the most common \gls{ris} model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical \gls{ris}-aided \gls{swipt}.} and $\theta_l \in [0,2\pi)$ is the phase shift.
+We also define $\mathbf{\phi} \triangleq [\phi_1, \dots, \phi_L]^\mathsf{H} \in \mathbb{C}^{L \times 1}$ and $\mathbf{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\mathbf{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the \gls{ris} vector and matrix, respectively.
 
@@
 Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
-In this paper, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each \gls{ris} element is the same at all subbands.
+In this chapter, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each \gls{ris} element is the same at all subbands.
 		\end{remark}
 
-		At subband $n$, we denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, the \gls{ap}-\gls{ris} incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and the \gls{ris}-\gls{ue} reflected channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$.
+		At subband $n$, we denote the \gls{ap}-\gls{ue} direct channel as $\mathbf{h}_{\mathrm{D},n}^\mathsf{H} \in \mathbb{C}^{1 \times M}$, the \gls{ap}-\gls{ris} incident channel as $\mathbf{H}_{\mathrm{F},n} \in \mathbb{C}^{L \times M}$, and the \gls{ris}-\gls{ue} reflected channel as $\mathbf{h}_{\mathrm{B},n}^\mathsf{H} \in \mathbb{C}^{1 \times L}$.
 The auxiliary \gls{ap}-\gls{ris}-\gls{ue} link can be modeled as a concatenation of the incident channel, the \gls{ris} reflection, and the reflected channel.
@@
 		\begin{equation}\label{eq:h_n}
-			\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n},
+			\mathbf{h}_{n}^\mathsf{H} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{h}_{\mathrm{B},n}^\mathsf{H} \mathbf{\Theta} \mathbf{H}_{\mathrm{F},n} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{\phi}^\mathsf{H} \mathbf{V}_{n},
 		\end{equation}
-		where we define the cascaded incident-reflected channel at subband $n$ as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
-We also define $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$.
+		where we define the cascaded incident-reflected channel at subband $n$ as $\mathbf{V}_{n} \triangleq \mathrm{diag}(\mathbf{h}_{\mathrm{B},n}^\mathsf{H})\mathbf{H}_{\mathrm{F},n} \in \mathbb{C}^{L \times M}$.
+We also define $\mathbf{h} \triangleq [\mathbf{h}_1^\mathsf{T},\dots,\mathbf{h}_N^\mathsf{T}]^\mathsf{T} \in \mathbb{C}^{MN \times 1}$.
 
@@
 Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier \gls{swipt}.
-For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\phi},n} \lVert \boldsymbol{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\phi}} \min_n \lVert \boldsymbol{h}_n \rVert$).
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\mathbf{\phi},n} \lVert \mathbf{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\mathbf{\phi}} \min_n \lVert \mathbf{h}_n \rVert$).
 That is to say, \gls{ris} essentially enables a flexible subchannel design.
@@
 		\begin{equation}
-			y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\boldsymbol{h}_{n}^H}{(\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\boldsymbol{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
+			y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\mathbf{h}_{n}^\mathsf{H}}{(\mathbf{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\mathbf{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
 		\end{equation}
@@
 		\begin{equation}\label{eq:R}
-			R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
+			R(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
 		\end{equation}
@@
 		\begin{equation}\label{eq:z}
-			z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}},
+			z(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}},
 		\end{equation}
 		where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
-With a slight abuse of notation, we refer to $z$ as the average output \gls{dc} in this paper.
+With a slight abuse of notation, we refer to $z$ as the average output \gls{dc} in this chapter.
 It can be observed that the conventional linear harvester model, where the output \gls{dc} power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$.
@@
 Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order \gls{dc} terms.
-Let $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$.
+Let $\mathbf{W}_{\mathrm{I/P}} \triangleq \mathbf{w}_{\mathrm{I/P}}\mathbf{w}_{\mathrm{I/P}}^\mathsf{H} \in \mathbb{C}^{MN \times MN}$.
+As illustrated by Fig.~\ref{fi:block_diagonal}, $\mathbf{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\mathbf{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\mathbf{0}$.
 Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
@@
 			\begin{equation*}
-				\boldsymbol{W}_{\mathrm{I/P}}=
+				\mathbf{W}_{\mathrm{I/P}}=
 				\begin{tikzpicture}[>=stealth,thick,baseline,every right delimiter/.append style={name=rd},]
@@
 					{
-						\boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},2}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
-						\boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},1}^H & \boldsymbol{w}_{\mathrm{I/P},2}\boldsymbol{w}_{\mathrm{I/P},2}^H & \ddots & \vdots \\
-						\vdots & \ddots & \ddots & \boldsymbol{w}_{\mathrm{I/P},N-1}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
-						\boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},1}^H & \dots & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N-1}^H & \boldsymbol{w}_{\mathrm{I/P},N}\boldsymbol{w}_{\mathrm{I/P},N}^H \\
+						\mathbf{w}_{\mathrm{I/P},1}\mathbf{w}_{\mathrm{I/P},1}^\mathsf{H} & \mathbf{w}_{\mathrm{I/P},1}\mathbf{w}_{\mathrm{I/P},2}^\mathsf{H} & \dots & \mathbf{w}_{\mathrm{I/P},1}\mathbf{w}_{\mathrm{I/P},n}^\mathsf{H} \\
+						\mathbf{w}_{\mathrm{I/P},2}\mathbf{w}_{\mathrm{I/P},1}^\mathsf{H} & \mathbf{w}_{\mathrm{I/P},2}\mathbf{w}_{\mathrm{I/P},2}^\mathsf{H} & \ddots & \vdots \\
+						\vdots & \ddots & \ddots & \mathbf{w}_{\mathrm{I/P},N-1}\mathbf{w}_{\mathrm{I/P},n}^\mathsf{H} \\
+						\mathbf{w}_{\mathrm{I/P},N}\mathbf{w}_{\mathrm{I/P},1}^\mathsf{H} & \dots & \mathbf{w}_{\mathrm{I/P},N}\mathbf{w}_{\mathrm{I/P},N-1}^\mathsf{H} & \mathbf{w}_{\mathrm{I/P},N}\mathbf{w}_{\mathrm{I/P},n}^\mathsf{H} \\
 					};
@@
 			\end{equation*}
-			\caption{$\boldsymbol{W}_{\mathrm{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
-$\boldsymbol{W}_{\mathrm{I/P},k}$ keeps the $k$-th block diagonal of $\boldsymbol{W}_{\mathrm{I/P}}$ and nulls all remaining blocks.
+			\caption{$\mathbf{W}_{\mathrm{I/P}}$ consists of $N \times N$ blocks of size $M \times M$.
+$\mathbf{W}_{\mathrm{I/P},k}$ keeps the $k$-th block diagonal of $\mathbf{W}_{\mathrm{I/P}}$ and nulls all remaining blocks.
 Solid, dashed and dotted blocks correspond to $k>0$, $k=0$ and $k<0$, respectively.
-For $\boldsymbol{w}_{\mathrm{I/P},n_1}\boldsymbol{w}_{\mathrm{I/P},n_2}^H$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
+For $\mathbf{w}_{\mathrm{I/P},n_1}\mathbf{w}_{\mathrm{I/P},n_2}^\mathsf{H}$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
 			\label{fi:block_diagonal}
@@
 			\begin{align}
-				&z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
-				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h},\label{eq:y_I2}\\
-				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I},0}\boldsymbol{h})^2,\label{eq:y_I4}\\
-				&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})(\boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{P},n})^*} = \frac{1}{2}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},0}\boldsymbol{h},\label{eq:y_P2}\\
-				&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\boldsymbol{h}_{{n_1}}^H\boldsymbol{w}_{\mathrm{P},{n_1}})(\boldsymbol{h}_{{n_2}}^H\boldsymbol{w}_{\mathrm{P},{n_2}})(\boldsymbol{h}_{{n_3}}^H\boldsymbol{w}_{\mathrm{P},{n_3}})^*(\boldsymbol{h}_{{n_4}}^H\boldsymbol{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})(\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{P},k}\boldsymbol{h})^*.\label{eq:y_P4}
+				&z(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
+				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})^*} = \frac{1}{2}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I},0}\mathbf{h},\label{eq:y_I2}\\
+				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I},0}\mathbf{h})^2,\label{eq:y_I4}\\
+				&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{P},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{P},n})^*} = \frac{1}{2}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},0}\mathbf{h},\label{eq:y_P2}\\
+				&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\mathbf{h}_{{n_1}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_1}})(\mathbf{h}_{{n_2}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_2}})(\mathbf{h}_{{n_3}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_3}})^*(\mathbf{h}_{{n_4}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},k}\mathbf{h})(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},k}\mathbf{h})^*.\label{eq:y_P4}
 			\end{align}
@@
 			&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
-			&\quad \frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
+			&\quad \frac{1}{2}\left(\lVert{\mathbf{w}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
 		\end{align}
@@
 	\begin{maxi!}
-		{\scriptstyle{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
-		\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
-		\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
-		\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
+		{\scriptstyle{\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho}}{z(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+		\addConstraint{R(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
+		\addConstraint{\frac{1}{2}\left(\lVert{\mathbf{w}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
+		\addConstraint{\lvert{\mathbf{\phi}}\rvert=\mathbf{1}}\label{co:original_modulus}
 		\addConstraint{0 \le \rho \le 1.}
@@
 	\begin{subsection}{Passive Beamforming}
-		In this section, we optimize the \gls{ris} phase shift $\boldsymbol{\phi}$ for any given waveform $\boldsymbol{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
+		In this section, we optimize the \gls{ris} phase shift $\mathbf{\phi}$ for any given waveform $\mathbf{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
 		\begin{align}
-			\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2
-			& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{h}_n\boldsymbol{h}_n^H\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-			& = \boldsymbol{w}_{\mathrm{I},n}^H(\boldsymbol{h}_{\mathrm{D},n}+\boldsymbol{V}_n^H\boldsymbol{\phi})(\boldsymbol{h}_{\mathrm{D},n}^H+\boldsymbol{\phi}^H\boldsymbol{V}_n)\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-			& = \boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi}\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\nonumber\\
-			& = \mathrm{tr}(\boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H\boldsymbol{\Phi})\nonumber\\
-			& = \mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi}),
+			\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2
+			& = \mathbf{w}_{a\mathrm{I},n}^\mathsf{H}\mathbf{h}_n\mathbf{h}_n^\mathsf{H}\mathbf{w}_{\mathrm{I},n}\nonumber\\
+			& = \mathbf{w}_{\mathrm{I},n}^\mathsf{H}(\mathbf{h}_{\mathrm{D},n}+\mathbf{V}_n^\mathsf{H}\mathbf{\phi})(\mathbf{h}_{\mathrm{D},n}^\mathsf{H}+\mathbf{\phi}^\mathsf{H}\mathbf{V}_n)\mathbf{w}_{\mathrm{I},n}\nonumber\\
+			& = \mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H}\mathbf{\Phi}\mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\nonumber\\
+			& = \mathrm{tr}(\mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H}\mathbf{\Phi})\nonumber\\
+			& = \mathrm{tr}(\mathbf{C}_n\mathbf{\Phi}),
 		\end{align}
-		where $\boldsymbol{M}_n \triangleq [\boldsymbol{V}_n^H, \boldsymbol{h}_{\mathrm{D},n}]^H \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\phi}} \triangleq [\boldsymbol{\phi}^H, t']^H \in \mathbb{C}^{(L+1) \times 1}$, $\boldsymbol{\Phi} \triangleq \bar{\boldsymbol{\phi}}\bar{\boldsymbol{\phi}}^H \in \mathbb{C}^{(L+1) \times (L+1)}$, $\boldsymbol{C}_n \triangleq \boldsymbol{M}_n\boldsymbol{w}_{\mathrm{I},n}\boldsymbol{w}_{\mathrm{I},n}^H\boldsymbol{M}_n^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+		where $\mathbf{M}_n \triangleq [\mathbf{V}_n^\mathsf{H}, \mathbf{h}_{\mathrm{D},n}]^\mathsf{H} \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\mathbf{\phi}} \triangleq [\mathbf{\phi}^\mathsf{H}, t']^\mathsf{H} \in \mathbb{C}^{(L+1) \times 1}$, $\mathbf{\Phi} \triangleq \bar{\mathbf{\phi}}\bar{\mathbf{\phi}}^\mathsf{H} \in \mathbb{C}^{(L+1) \times (L+1)}$, $\mathbf{C}_n \triangleq \mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H} \in \mathbb{C}^{(L+1)\times(L+1)}$.
 On the other hand, we define $t_{\mathrm{I/P},k}$ as
@@
 			t_{\mathrm{I/P},k}
-			& \triangleq \boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{h}\nonumber\\
-			& = \mathrm{tr}(\boldsymbol{h}\boldsymbol{h}^H\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-			& = \mathrm{tr}\left((\boldsymbol{h}_{D}+\boldsymbol{V}^H\boldsymbol{\phi})(\boldsymbol{h}_{D}^H+\boldsymbol{\phi}^H\boldsymbol{V})\boldsymbol{W}_{\mathrm{I/P},k}\right)\nonumber\\
-			& = \mathrm{tr}(\boldsymbol{M}^H\boldsymbol{\Phi}\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k})\nonumber\\
-			& = \mathrm{tr}(\boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H\boldsymbol{\Phi})\nonumber\\
-			& = \mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},k}\boldsymbol{\Phi})\label{eq:t_k},
+			& \triangleq \mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I/P},k}\mathbf{h}\nonumber\\
+			& = \mathrm{tr}(\mathbf{h}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I/P},k})\nonumber\\
+			& = \mathrm{tr}\left((\mathbf{h}_{D}+\mathbf{V}^\mathsf{H}\mathbf{\phi})(\mathbf{h}_{D}^\mathsf{H}+\mathbf{\phi}^\mathsf{H}\mathbf{V})\mathbf{W}_{\mathrm{I/P},k}\right)\nonumber\\
+			& = \mathrm{tr}(\mathbf{M}^\mathsf{H}\mathbf{\Phi}\mathbf{M}\mathbf{W}_{\mathrm{I/P},k})\nonumber\\
+			& = \mathrm{tr}(\mathbf{M}\mathbf{W}_{\mathrm{I/P},k}\mathbf{M}^\mathsf{H}\mathbf{\Phi})\nonumber\\
+			& = \mathrm{tr}(\mathbf{C}_{\mathrm{I/P},k}\mathbf{\Phi})\label{eq:t_k},
 		\end{align}
-		where $\boldsymbol{V} \triangleq [\boldsymbol{V}_1,\dots,\boldsymbol{V}_N] \in \mathbb{C}^{L \times MN}$, $\boldsymbol{M} \triangleq [\boldsymbol{V}^H, \boldsymbol{h}_{D}]^H \in \mathbb{C}^{(L+1) \times MN}$, $\boldsymbol{C}_{\mathrm{I/P},k} \triangleq \boldsymbol{M}\boldsymbol{W}_{\mathrm{I/P},k}\boldsymbol{M}^H \in \mathbb{C}^{(L+1)\times(L+1)}$.
+		where $\mathbf{V} \triangleq [\mathbf{V}_1,\dots,\mathbf{V}_N] \in \mathbb{C}^{L \times MN}$, $\mathbf{M} \triangleq [\mathbf{V}^\mathsf{H}, \mathbf{h}_{D}]^\mathsf{H} \in \mathbb{C}^{(L+1) \times MN}$, $\mathbf{C}_{\mathrm{I/P},k} \triangleq \mathbf{M}\mathbf{W}_{\mathrm{I/P},k}\mathbf{M}^\mathsf{H} \in \mathbb{C}^{(L+1)\times(L+1)}$.
 On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
 		\begin{align}
-			R(\boldsymbol{\Phi})
-			& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\boldsymbol{C}_n\boldsymbol{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
-			z(\boldsymbol{\Phi})
+			R(\mathbf{\Phi})
+			& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\mathbf{C}_n\mathbf{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
+			z(\mathbf{\Phi})
 			& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
@@
 		\end{align}
-		Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real-valued because $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices.
+		Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\mathbf{C}_{\mathrm{I/P},0}\mathbf{\Phi})$ is real-valued because $\mathbf{C}_{\mathrm{I/P},0}$ and $\mathbf{\Phi}$ are Hermitian matrices.
 Due to symmetry \cite{Golub2013}, we have
@@
 			\begin{align}
-				\tilde{z}(\boldsymbol{\Phi}^{(i)})
+				\tilde{z}(\mathbf{\Phi}^{(i)})
 				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
@@
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{\Phi}}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
-			\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
-			\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_modulus}
-			\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
-			\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
+			{\scriptstyle{\mathbf{\Phi}}}{\tilde{z}(\mathbf{\Phi})}{\label{op:irs}}{\label{ob:irs}}
+			\addConstraint{R(\mathbf{\Phi}) \ge \bar{R}}\label{co:irs_rate}
+			\addConstraint{\mathrm{diag}^{-1}(\mathbf{\Phi})=\mathbf{1}}\label{co:irs_modulus}
+			\addConstraint{\mathbf{\Phi}\succeq{\mathbf{0}}}\label{co:irs_sd}
+			\addConstraint{\mathrm{rank}(\mathbf{\Phi})=1.\label{co:irs_rank}}
 		\end{maxi!}
@@
 		\begin{proposition}\label{pr:relaxation}
-			Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by \gls{sdr}.
+			Any optimal solution $\mathbf{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by \gls{sdr}.
 		\end{proposition}
@@
 
-		In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the	\gls{ris} vector by $\boldsymbol{\phi}^{\star}=e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$.
+		In summary, we update $\mathbf{\Phi}^{(i)}$ until convergence, extract $\hat{\mathbf{\phi}}^\star$ by eigen decomposition, and retrieve the	\gls{ris} vector by $\mathbf{\phi}^{\star}=e^{j \arg\left([\hat{\mathbf{\phi}}^\star]_{(1:L)} \middle/ [\hat{\mathbf{\phi}}^\star]_{(L+1)}\right)}$.
 The passive beamforming design is summarized in the \gls{sca} Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
@@
 			\begin{algorithmic}[1]
-				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
-				\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
-				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\mathbf{h}_{\mathrm{D},n}$, $\mathbf{V}_{n}$, $\sigma_n$, $\mathbf{w}_{\mathrm{I/P},n}$, $\rho$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State Construct $\mathbf{V}$, $\mathbf{M}$, $\mathbf{M}_n$, $\mathbf{C}_{n}$, $\mathbf{C}_{\mathrm{I/P},k}$, $\forall n,k$
+				\State \textbf{Initialize} $i \gets 0$, $\mathbf{\Phi}^{(0)}$
 				\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
@@
 					\State $i \gets i + 1$
-					\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
+					\State Get $\mathbf{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
 					\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
@@
 				\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-				\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
-				\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-				\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
-				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
+				\State Set $\mathbf{\Phi}^{\star} \gets \mathbf{\Phi}^{(i)}$
+				\State Get $\hat{\mathbf{\phi}}^\star$ by eigen decomposition, $\mathbf{\Phi}^{\star}=\hat{\mathbf{\phi}}^\star(\hat{\mathbf{\phi}}^\star)^\mathsf{H}$
+				\State Set $\mathbf{\phi}^{\star} \gets e^{j \arg\left([\hat{\mathbf{\phi}}^\star]_{(1:L)} \middle/ [\hat{\mathbf{\phi}}^\star]_{(L+1)}\right)}$
+				\State \textbf{Output} $\mathbf{\phi}^{\star}$
 			\end{algorithmic}
@@
 	\begin{subsection}{Active Beamforming}
-		The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\boldsymbol{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
+		The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\mathbf{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
 Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduce the size of variables from $2MN$ to $2(M+N)$.
@@
 		\begin{equation}\label{eq:w}
-			\boldsymbol{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \boldsymbol{b}_{\mathrm{I/P}, n},
+			\mathbf{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \mathbf{b}_{\mathrm{I/P}, n},
 		\end{equation}
-		where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\boldsymbol{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
-Define $\boldsymbol{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^T \in \mathbb{R}_+^{N \times 1}$.
+		where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\mathbf{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
+Define $\mathbf{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^\mathsf{T} \in \mathbb{R}_+^{N \times 1}$.
 The \gls{mrt} precoder at subband $n$ is given by
 		\begin{equation}\label{eq:b_n}
-			\boldsymbol{b}_{\mathrm{I/P}, n}^\star = \frac{\boldsymbol{h}_n}{\lVert{\boldsymbol{h}_n}\rVert}.
+			\mathbf{b}_{\mathrm{I/P}, n}^\star = \frac{\mathbf{h}_n}{\lVert{\mathbf{h}_n}\rVert}.
 		\end{equation}
@@
 	\begin{subsection}{Waveform and Splitting Ratio}
-		Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given \gls{ris} phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$.
-On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$.
+		Next, we jointly optimize the waveform amplitude $\mathbf{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given \gls{ris} phase shift $\mathbf{\phi}$ and active precoder $\mathbf{b}_{\mathrm{I/P},n}$, $\forall n$.
+On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\mathbf{h}_n}\rVert$.
 Hence, the rate \eqref{eq:R} reduces to
 		\begin{equation}\label{eq:R_waveform}
-			R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right),
+			R(\mathbf{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\mathbf{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right),
 		\end{equation}
@@
 			\begin{align}
-				z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
-				& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
+				z(\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho)
+				& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\mathbf{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\mathbf{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\mathbf{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
+				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\mathbf{h}_{n_1}}\rVert^2 \lVert{\mathbf{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
 			\end{align}
@@
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
-			\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}}
-			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}.}
+			{\scriptstyle{\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho}}{z(\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
+			\addConstraint{R(\mathbf{s}_{\mathrm{I}},\rho) \ge \bar{R}}
+			\addConstraint{\frac{1}{2}\left(\lVert{\mathbf{s}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{s}_\mathrm{P}}\rVert^2\right)\le{P}.}
 		\end{maxi!}
@@
 		\begin{mini!}
-			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
-			\addConstraint{\frac{t''}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
-			\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
-			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
+			{\scriptstyle{\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_rgp}}{}
+			\addConstraint{\frac{t''}{z(\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho)} \le 1}\label{co:waveform_objective}
+			\addConstraint{\frac{2^{\bar{R}}}{\prod_{n=1}^N \left(1+{\bar{\rho}\lVert{\mathbf{h}_n}\rVert^2 s_{\mathrm{I},n}^2}\big/{\sigma_n^2}\right)} \le 1}\label{co:waveform_rate}
+			\addConstraint{\frac{1}{2}\left(\lVert{\mathbf{s}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{s}_\mathrm{P}}\rVert^2\right) \le P}\label{co:waveform_power}
 			\addConstraint{\rho + \bar{\rho} \le 1.}\label{co:waveform_splitting_ratio}
@@
 		\begin{align}
-			1+\frac{\bar{\rho}\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
-			z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}\label{eq:g_P}.
+			1+\frac{\bar{\rho}\lVert{\mathbf{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2} &\triangleq \sum_{m_{\mathrm{I},n}}g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})\label{eq:g_I},\\
+			z(\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho) &\triangleq \sum_{m_\mathrm{P}}{g_{m_\mathrm{P}}(\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho)}\label{eq:g_P}.
 		\end{align}
@@
 		\begin{mini!}
-			{\scriptstyle{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
-			\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
+			{\scriptstyle{\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho,\bar{\rho},t''}}{\frac{1}{t''}}{\label{op:waveform_gp}}{}
+			\addConstraint{{t''}\prod_{m_\mathrm{P}}{\left(\frac{g_{{m_\mathrm{P}}}(\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho)}{\gamma_{{m_\mathrm{P}}}}\right)^{-\gamma_{{m_\mathrm{P}}}}}\le{1}}
 			\addConstraint{2^{\bar{R}}\prod_{n}\prod_{m_{\mathrm{I},n}}\left(\frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n},\bar{\rho})}{\gamma_{m_{\mathrm{I},n}}}\right)^{-\gamma_{m_{\mathrm{I},n}}}\le{1}}
-			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
+			\addConstraint{\frac{1}{2}\left(\lVert{\mathbf{s}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{s}_\mathrm{P}}\rVert^2\right)\le{P}}
 			\addConstraint{\rho + \bar{\rho} \le 1,}
@@
 		\begin{align}
-			\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\boldsymbol{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
-			\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_{\mathrm{I}}^{(i-1)},\boldsymbol{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
+			\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\mathbf{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
+			\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\mathbf{s}_{\mathrm{I}}^{(i-1)},\mathbf{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\mathbf{s}_{\mathrm{I}}^{(i-1)},\mathbf{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
 		\end{align}
 		With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as \texttt{CVX toolbox} \cite{Grant2016}.
-We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
+We update $\mathbf{s}_{\mathrm{I}}^{(i)},\mathbf{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
 The joint waveform amplitude and splitting ratio design is summarized in the \gls{gp} Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
@@
 			\begin{algorithmic}[1]
-				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
-				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\mathbf{h}_n$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\mathbf{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
 				\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
@@
 					\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
-					\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
+					\State Get $\mathbf{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
 					\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
@@
 				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-				\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
-				\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star}$, $\boldsymbol{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
+				\State Set $\mathbf{s}_{\mathrm{I/P}}^{\star} \gets \mathbf{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
+				\State \textbf{Output} $\mathbf{s}_{\mathrm{I}}^{\star}$, $\mathbf{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
 			\end{algorithmic}
@@
 		\begin{equation}\label{eq:wf}
-			s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
+			s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\mathbf{h}_n}\rVert^2}\right)^+},
 		\end{equation}
-		where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$.
+		where $\lambda$ is chosen to satisfy the power constraint $\lVert{\mathbf{s}_I}\rVert^2 / 2 \le P$.
 The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
@@
 		\begin{equation}\label{eq:smf}
-			s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
+			s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\mathbf{h}_n \rVert^{2 \alpha}}}}\lVert{\mathbf{h}_n}\rVert^\alpha,
 		\end{equation}
@@
 		\begin{align}
-			s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
-			s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha, \label{eq:s_p}
+			s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\mathbf{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
+			s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\mathbf{h}_n \rVert^{2 \alpha}}}}\lVert{\mathbf{h}_n}\rVert^\alpha, \label{eq:s_p}
 		\end{align}
@@
 			\begin{algorithmic}[1]
-				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $\sigma_n$, $\boldsymbol{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
-				\State Construct $\boldsymbol{V}$, $\boldsymbol{M}$, $\boldsymbol{M}_n$, $\boldsymbol{C}_{n}$, $\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
-				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\mathbf{h}_{\mathrm{D},n}$, $\mathbf{V}_{n}$, $\sigma_n$, $\mathbf{w}_{\mathrm{I/P},n}$, $\rho$, $\epsilon$, $\forall n$
+				\State Construct $\mathbf{V}$, $\mathbf{M}$, $\mathbf{M}_n$, $\mathbf{C}_{n}$, $\mathbf{C}_{\mathrm{I/P},k}$, $\forall n,k$
+				\State \textbf{Initialize} $i \gets 0$, $\mathbf{\Phi}^{(0)}$
 				\If{$\rho=0$}
-					\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+					\State Get $\mathbf{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
 				\Else
@@
 						\State $i \gets i + 1$
-							\State Get $\boldsymbol{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+							\State Get $\mathbf{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
 							\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
@@
 					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\boldsymbol{\Phi}^{\star} \gets \boldsymbol{\Phi}^{(i)}$
+					\State Set $\mathbf{\Phi}^{\star} \gets \mathbf{\Phi}^{(i)}$
 				\EndIf
-				\State Get $\hat{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\hat{\boldsymbol{\phi}}^\star(\hat{\boldsymbol{\phi}}^\star)^H$
-				\State Set $\boldsymbol{\phi}^{\star} \gets e^{j \arg\left([\hat{\boldsymbol{\phi}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\phi}}^\star]_{(L+1)}\right)}$
-				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
+				\State Get $\hat{\mathbf{\phi}}^\star$ by eigen decomposition, $\mathbf{\Phi}^{\star}=\hat{\mathbf{\phi}}^\star(\hat{\mathbf{\phi}}^\star)^\mathsf{H}$
+				\State Set $\mathbf{\phi}^{\star} \gets e^{j \arg\left([\hat{\mathbf{\phi}}^\star]_{(1:L)} \middle/ [\hat{\mathbf{\phi}}^\star]_{(L+1)}\right)}$
+				\State \textbf{Output} $\mathbf{\phi}^{\star}$
 			\end{algorithmic}
@@
 	\begin{subsection}{Block Coordinate Descent}
-		Based on the direct and cascaded \gls{csit}, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+		Based on the direct and cascaded \gls{csit}, we iteratively update the passive beamforming $\mathbf{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\mathbf{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\mathbf{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
 The steps are summarized in the \gls{bcd} Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
@@
 			\begin{algorithmic}[1]
-				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
-				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
-				\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\mathbf{h}_{\mathrm{D},n}$, $\mathbf{V}_{n}$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\mathbf{\phi}^{(0)}$, $\mathbf{b}_{\mathrm{I/P},n}^{(0)}$, $\mathbf{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
+				\State Set $\mathbf{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
 				\State Compute $z^{(0)}$ by \eqref{eq:z_waveform}
@@
 					\State $i \gets i + 1$
-					\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$, $\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
-					\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-					\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by Algorithm~\ref{al:gp}
-					\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+					\State Get $\mathbf{\phi}^{(i)}$ based on $\mathbf{w}_{\mathrm{I/P}}^{(i-1)}$, $\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
+					\State Update $\mathbf{h}_n^{(i)}$, $\mathbf{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+					\State Get $\mathbf{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by Algorithm~\ref{al:gp}
+					\State Update $\mathbf{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
 					\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
 				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-				\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
-				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
+				\State Set $\mathbf{\phi}^{\star} \gets \mathbf{\phi}^{(i)}$, $\mathbf{w}_{\mathrm{I/P}}^{\star} \gets \mathbf{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
+				\State \textbf{Output} $\mathbf{\phi}^{\star}$, $\mathbf{w}_{\mathrm{I}}^{\star}$, $\mathbf{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
 			\end{algorithmic}
@@
 
-		For the low-complexity design under \gls{ps} mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+		For the low-complexity design under \gls{ps} mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\mathbf{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
 To achieve the \gls{wit} point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the \gls{bcd} algorithm obtains the \gls{r-e} region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable \gls{r-e} region of the \gls{lc}-\gls{bcd} algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
@@
 			\begin{algorithmic}[1]
-				\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
-				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
-				\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
+				\State \textbf{Input} $\beta_2$, $\beta_4$, $\mathbf{h}_{\mathrm{D},n}$, $\mathbf{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\mathbf{\phi}^{(0)}$, $\mathbf{b}_{\mathrm{I/P},n}^{(0)}$, $\mathbf{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
+				\State Set $\mathbf{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
 				\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
@@
 					\State $i \gets i + 1$
-					\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
-					\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-					\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
-					\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
+					\State Get $\mathbf{\phi}^{(i)}$ based on $\mathbf{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
+					\State Update $\mathbf{h}_n^{(i)}$, $\mathbf{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
+					\State Update $\mathbf{s}_{\mathrm{I}}^{(i)}$, $\mathbf{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
+					\State Update $\mathbf{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
 					\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
@@
 				\Until $\lvert \Delta \rvert \le \epsilon$
-				\State Set $\boldsymbol{\phi}^{\star} \gets \boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star} \gets \boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
-				\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
+				\State Set $\mathbf{\phi}^{\star} \gets \mathbf{\phi}^{(i)}$, $\mathbf{w}_{\mathrm{I/P}}^{\star} \gets \mathbf{w}_{\mathrm{I/P}}^{(i)}$
+				\State \textbf{Output} $\mathbf{\phi}^{\star}$, $\mathbf{w}_{\mathrm{I}}^{\star}$, $\mathbf{w}_{\mathrm{P}}^{\star}$
 			\end{algorithmic}
@@
 	To evaluate the proposed \gls{ris}-aided \gls{swipt} system, we consider the layout in Fig.~\ref{fi:layout} where the \gls{ris} moves along a line parallel to the \gls{ap}-\gls{ue} path.
-Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the \gls{ap} to the \gls{ris}, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
+Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the \gls{ap} to the \gls{ris}, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{B}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
 $d_{\mathrm{D}}=\qty{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$ are chosen as reference.
-The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{R}}$, respectively.
+The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{B}}$, respectively.
 We consider a large open space Wi-Fi-like environment at center frequency \qty{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
@@
 This is because less power is allocated to each subband but more balanced \gls{dc} terms are introduced by frequency coupling to boost the harvested energy.
-On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ for \gls{wpt}.
+On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\mathbf{s}_{\mathrm{I/P}}$ for \gls{wpt}.
 It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
@@
 Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the \gls{dc} objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\boldsymbol{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no \gls{sca} is required; (ii) in the waveform design problem, the \gls{wpt}-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+To investigate the performance loss, we truncate the \gls{dc} objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\mathbf{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no \gls{sca} is required; (ii) in the waveform design problem, the \gls{wpt}-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
 As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dBA} gap compared to the nonlinear model-based \gls{smf} and \gls{gp} designs.
@@
 	\begin{equation}
-		z = \beta_2 \Lambda_{\mathrm{R}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{R}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
+		z = \beta_2 \Lambda_{\mathrm{B}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{B}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
 	\end{equation}
@@
 	\begin{equation}
-		\boldsymbol{V}_{n} = \hat{\boldsymbol{V}}_{n} + \tilde{\boldsymbol{V}}_{n},
+		\mathbf{V}_{n} = \hat{\mathbf{V}}_{n} + \tilde{\mathbf{V}}_{n},
 	\end{equation}
-	where $\hat{\boldsymbol{V}}_{n}$ is the estimated cascaded \gls{csit} and $\tilde{\boldsymbol{V}}_{n}$ is the estimation error with entries following i.i.d.
+	where $\hat{\mathbf{V}}_{n}$ is the estimated cascaded \gls{csit} and $\tilde{\mathbf{V}}_{n}$ is the estimation error with entries following i.i.d.
 \gls{cscg} distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded \gls{csit} inaccuracy for broadband \gls{swipt} with different $L$.
@@
 \begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-	This paper investigated the \gls{r-e} tradeoff of a single user employing practical receiving strategies in a \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.
+	This chapter investigated the \gls{r-e} tradeoff of a single user employing practical receiving strategies in a \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.
 Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable \gls{r-e} region.
@@
 
-	One particular unanswered question of this paper is how to design waveform, active and passive beamforming in a multi-user multi-carrier \gls{ris}-aided \gls{swipt} system.
+	One particular unanswered question of this chapter is how to design waveform, active and passive beamforming in a multi-user multi-carrier \gls{ris}-aided \gls{swipt} system.
 Also, harvester saturation effect and practical \gls{ris} models with amplitude-phase coupling \cite{Abeywickrama2020}, angle-dependent reflection \cite{Tang2021}, frequency-dependent reflection, and/or partially/fully-connected architecture \cite{Shen2020a} could be considered in future works.

### 2024-03-26 content/chapter_2.tex
:pencil: Update chapter 3

@@
 	\begin{subsection}{Wave Scattering Models}
-		\begin{subsubsection}{Principles}
-			\label{sc:principles}
+		\begin{subsubsection}{Principles}\label{sc:principles}
 			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
@@
 				\theta_n = \frac{\jmath X_n - Z^*}{\jmath X_n + Z} = \exp(\jmath \phi_n),
+				\label{eq:reflection_coefficient_ris}
 			\end{equation}
@@
 
-		\begin{subsubsection}{Operation Regions and Signal Models}
+		\begin{subsubsection}{Operation Regions and Signal Models}\label{sc:operation_regions}
 			The diode is the key non-linear component that determines to the harvested energy.
@@
 				\begin{equation}
-					P_\mathrm{DC}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{E}\bigl\{ \lvert y(t) \rvert^2 \bigr\},
+					P_\mathrm{DC}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{A}\bigl\{ \lvert y(t) \rvert^2 \bigr\},
 					\label{eq:dc_power_linear}
@@
 				\begin{equation}
-					i_\mathrm{out} = \sum_{i=0}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{E}\bigl\{ y^i(t) \bigr\} = \sum_{i=0,\text{even}}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{E}\bigl\{ y^i(t) \bigr\}
+					i_\mathrm{out} = \sum_{i=0}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{A}\bigl\{ y^i(t) \bigr\} = \sum_{i=0,\text{even}}^\infty k_i R_\mathrm{A}^{i/2} \mathbb{A}\bigl\{ y^i(t) \bigr\}
 					\label{eq:dc_current_expansion}
 				\end{equation}
-				where the second equality is because $\mathbb{E}\bigl\{y^i(t)\bigr\} = 0$ for odd $i$.
+				where the second equality is because $\mathbb{A}\bigl\{y^i(t)\bigr\} = 0$ for odd $i$.
 Note that the dependency of $k_i$ on $-v_\mathrm{out}=-i_\mathrm{out} R_\mathrm{L}$ makes it nontrivial to formulate a closed-form expression for the harvested \gls{dc} power.
@@
 				\begin{equation}
-					z \triangleq \sum_{i=2,\text{even}}^\infty \beta_i \mathbb{E}\bigl\{ y^i(t) \bigr\},
+					z \triangleq \sum_{i=2,\text{even}}^{n_0} \beta_i \mathbb{A}\bigl\{ y^i(t) \bigr\},
 					\label{eq:dc_power_nonlinear}
 				\end{equation}
-				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant.
-Truncating \eqref{eq:dc_power_nonlinear} at the second order yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model.
+				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant and $n_0$ is the truncation order.
+Selecting $n_0=2$ yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model.
 For a moderate excitation, the contribution of higher-order terms is significant and should be modelled in the harvested \gls{dc} power.
@@
 		\end{itemize}
-		Those disparities translate to a fundamental tradeoff between information and power transfer in \gls{swipt} systems, which is often quantified by a \emph{\gls{r-e} region}.
+		Those disparities translate to a fundamental trade-off between information and power transfer in \gls{swipt} systems, which is often quantified by a \emph{\gls{r-e} region}.
 		\begin{equation}
@@
 
-		\begin{subsubsection}{Receiver Architectures}
+		\begin{subsubsection}{Receiver Architectures}\label{sc:receiver_architectures}
 			Figure \ref{fg:swipt_receiver_architectures} illustrates four potential architectures for a co-located \gls{swipt} receiver \cite{Clerckx2022}:
@@
 This is theoretically the most efficient design with a rectangle \gls{r-e} region but is unimplementable in practice due to hardware constraints.
-				\item \emph{\gls{ts} receiver:} Each time frame is divided into individual \gls{wit} and \gls{wpt} phases, where the receiver switches between information decoder and energy harvester, respectively.
+				\item \emph{\gls{ts} receiver:} Each time block is divided into individual \gls{wit} and \gls{wpt} phases, where the receiver switches between information decoder and energy harvester, respectively.
 The transmitted waveform and \gls{ris} response are optimized independently for each phase, and the resulting \gls{r-e} region is a triangle with two vertices corresponding to \gls{wit}-only and \gls{wpt}-only.
@@
 				\end{cases}
-				= \frac{\pi}{4} \sum_{m=1,\text{odd}}^\infty \frac{1}{m} \sin\bigl(2\pi m \Delta f t\bigr),
+				= \frac{\pi}{4} \sum_{m=1,\text{odd}}^\infty \frac{\alpha}{m} \sin\bigl(2\pi m \Delta f t\bigr),
 			\end{equation}
@@
 			\begin{equation}
-				s_1(t) = \frac{\pi}{2} \Bigl(\sin\bigl(2 \pi (f_0 {+} \Delta f) t\bigr) - \sin\bigl(2 \pi (f_0 {-} \Delta f) t\bigr)\Bigr).
+				s_1(t) = \frac{\alpha \pi}{2} \Bigl(\sin\bigl(2 \pi (f_0 {+} \Delta f) t\bigr) - \sin\bigl(2 \pi (f_0 {-} \Delta f) t\bigr)\Bigr).
 			\end{equation}

### 2024-03-26 content/chapter_3.tex
:pencil: Update chapter 3

@@
 
-		The concept of \gls{swipt} was first cast in \cite{Varshney2008}, where the authors investigated the \gls{r-e} tradeoff for a flat Gaussian channel and typical discrete channels.
+		The concept of \gls{swipt} was first cast in \cite{Varshney2008}, where the authors investigated the \gls{r-e} trade-off for a flat Gaussian channel and typical discrete channels.
 \cite{Zhou2013} proposed two practical co-located information and power receivers, i.e., \gls{ts} and \gls{ps}.
@@
 	\begin{subsection}{\glsfmtshort{ris}-Aided \glsfmtshort{swipt}}
-		By integrating \gls{ris} with \gls{swipt}, the constructive reflection can boost the end-to-end power efficiency and improve the \gls{r-e} tradeoff.
+		By integrating \gls{ris} with \gls{swipt}, the constructive reflection can boost the end-to-end power efficiency and improve the \gls{r-e} trade-off.
 In multi-user cases, dedicated energy beams were proved unnecessary for the weighted sum-power maximization \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}.
@@
 Based on practical \gls{ris} and harvester models, \cite{Xu2021c} introduced a scalable resource allocation framework for a large-scale tile-based \gls{ris}-assisted \gls{swipt} system, where the optimization consists of a reflection design stage and a joint reflection selection and precoder design stage.
-The proposed framework provides a flexible tradeoff between performance and complexity.
+The proposed framework provides a flexible trade-off between performance and complexity.
 To the best of our knowledge, all existing papers considered resource allocation and beamforming design for dedicated information and energy users in a single-carrier network.
-In this chapter, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output \gls{dc} power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for \gls{swipt} with the passive beamforming capability of \gls{ris}, to investigate the \gls{r-e} tradeoff for one \gls{swipt} user with co-located information decoder and energy harvester.
+In this chapter, we instead build our design based on a proper nonlinear harvester model that captures the dependency of the output \gls{dc} power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for \gls{swipt} with the passive beamforming capability of \gls{ris}, to investigate the \gls{r-e} trade-off for one \gls{swipt} user with co-located information decoder and energy harvester.
 We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the \gls{r-e} region of \gls{ris}-aided \gls{swipt}?} The contributions of this chapter are summarized as follows.
 
-		\emph{First,} we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \cite{Clerckx2016a}.
+		\emph{First,} we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \eqref{eq:dc_power_nonlinear} \cite{Clerckx2016a}.
 Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output \gls{dc} power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce \gls{dc}), waveform coupling (i.e., different waveforms jointly contribute to \gls{dc}), and high-order objective function.
@@
 
-		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that
+		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that:
 		\begin{itemize}
@@
 
-\begin{section}{System Model}\label{se:system_model}
+\begin{section}{System Model}\label{sc:system_model}
 	\begin{figure}[H]
@@
 		\caption{An \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
-		\label{fi:system}
+		\label{fg:system}
 	\end{figure}
 
-	As shown in Fig.~\ref{fi:system}, we propose a \gls{ris}-aided \gls{swipt} system where an $M$-antenna \gls{ap} delivers information and power simultaneously, through an $L$-element \gls{ris}, to a single-antenna \gls{ue} over $N$ orthogonal evenly-spaced subbands.
-We consider a quasi-static block fading model and assume the \gls{csit} of direct and cascaded channels is known.
+	As shown in Fig.~\ref{fg:system}, we propose a \gls{ris}-aided \gls{swipt} system where an $M$-antenna \gls{ap} delivers information and power simultaneously, through an $L$-element \gls{ris}, to a single-antenna \gls{ue} over $N$ orthogonal evenly-spaced subbands.
+We consider a quasi-static block fading model and assume the \gls{csit} of direct and cascaded channels (defined in Section \ref{sc:reflection_pattern}) can be acquired.
 The signals reflected by two or more times are omitted, and the noise power is assumed too small to be harvested.
+	We assume that the time difference of signal arrival via direct and reflected paths is negligible compared to the symbol period.
 
@@
 		Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
-The information signal transmitted over subband $n \in \{1, \dots, N\}$ at time $t$ is
+The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
 		\begin{equation}
-			\mathbf{x}_{\mathrm{I},n}(t) = \Re\left\{\mathbf{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{j2{\pi}{f_n}{t}}\right\},
+			\mathbf{x}_{\mathrm{I},n}(t) = \Re\left\{\mathbf{w}_{\mathrm{I},n} \tilde{x}_{\mathrm{I},n}(t) e^{\jmath 2{\pi}{f_n}{t}}\right\},
 		\end{equation}
@@
 		\begin{equation}
-			\mathbf{x}_{\mathrm{P},n}(t) = \Re\left\{\mathbf{w}_{\mathrm{P},n} e^{j2{\pi}{f_n}{t}}\right\},
+			\mathbf{x}_{\mathrm{P},n}(t) = \Re\left\{\mathbf{w}_{\mathrm{P},n} e^{\jmath 2{\pi}{f_n}{t}}\right\},
 		\end{equation}
@@
 		\begin{equation}
-			\mathbf{x}(t) = \Re{\left\{\sum_{n=1}^N(\mathbf{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\mathbf{w}_{\mathrm{P},n}){e^{j2{\pi}{f_n}{t}}}\right\}}.
+			\mathbf{x}(t) = \Re{\left\{\sum_{n=1}^N(\mathbf{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\mathbf{w}_{\mathrm{P},n}){e^{\jmath 2{\pi}{f_n}{t}}}\right\}}.
 		\end{equation}
@@
 
-	\begin{subsection}{Reflection Pattern and Composite Channel}
-		According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
+	\begin{subsection}{Reflection Pattern and Composite Channel}\label{sc:reflection_pattern}
+		% According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component.
 The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedance.
-\gls{ris} element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and the reflection coefficient is defined as
-		\begin{equation}
-			\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l},
-		\end{equation}
-		where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the \gls{ris}, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
-This chapter sticks to the most common \gls{ris} model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical \gls{ris}-aided \gls{swipt}.} and $\theta_l \in [0,2\pi)$ is the phase shift.
-We also define $\mathbf{\phi} \triangleq [\phi_1, \dots, \phi_L]^\mathsf{H} \in \mathbb{C}^{L \times 1}$ and $\mathbf{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\mathbf{\Phi}^*) \in \mathbb{C}^{L \times L}$ as the \gls{ris} vector and matrix, respectively.
+		As discussed in Section \ref{sc:principles}, \gls{ris} element $l \in \mathcal{L} \triangleq \{1, \dots, L\}$ varies its load impedance $Z_l$ to manipulate the reflection coefficient $\theta_l$ \eqref{eq:reflection_coefficient_ris}.
+		In the ideal scenario, this corresponds to a full reflection $\lvert \theta_l \rvert = 1$ with phase shift $\phi_l \in [0,2\pi)$.
+
+		% reflect the incoming signal, and the reflection coefficient is defined as
+		% \begin{equation}
+		% 	\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{\jmath \theta_l},
+		% \end{equation}
+		% where $Z_0$ is the real-valued characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude,\footnote{Due to the non-zero power consumption at the \gls{ris}, $R_l > 0$ in practice such that $\eta_l < 1$ and is a function of $\theta_l$.
+This chapter sticks to the most common \gls{ris} model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical \gls{ris}-aided \gls{swipt}.}
+
+		% and $\theta_l \in [0,2\pi)$ is the phase shift.
+We also define $\boldsymbol{\theta} \triangleq [\phi_1, \dots, \phi_L]^\mathsf{H} \in \mathbb{C}^{L \times 1}$ and $\mathbf{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L)=\mathrm{diag}(\bar{\mathbf{\Theta}}^*) \in \mathbb{C}^{L \times L}$ as the \gls{ris} vector and matrix, respectively.
 
 		\begin{remark}\label{re:reflection_coefficient}
-			The element impedance $Z_l$ maps to the reflection coefficient $\phi_l$ uniquely.
-Since the reactance $X_l$ depends on the frequency, the reflection coefficient $\phi_l$ is also a function of frequency and cannot be designed independently at different subbands.
-In this chapter, we assume the bandwidth is small compared to the operating frequency such that the reflection coefficient of each \gls{ris} element is the same at all subbands.
+			Since the reactance $X_l$ is a function of frequency, the reflection coefficient $\theta_l$ cannot be designed independently at different subbands.
+In this chapter, we assume the bandwidth is small compared to the operating frequency, such that the reflection coefficient at different subbands is approximately the same.
 		\end{remark}
 
-		At subband $n$, we denote the \gls{ap}-\gls{ue} direct channel as $\mathbf{h}_{\mathrm{D},n}^\mathsf{H} \in \mathbb{C}^{1 \times M}$, the \gls{ap}-\gls{ris} incident channel as $\mathbf{H}_{\mathrm{F},n} \in \mathbb{C}^{L \times M}$, and the \gls{ris}-\gls{ue} reflected channel as $\mathbf{h}_{\mathrm{B},n}^\mathsf{H} \in \mathbb{C}^{1 \times L}$.
-The auxiliary \gls{ap}-\gls{ris}-\gls{ue} link can be modeled as a concatenation of the incident channel, the \gls{ris} reflection, and the reflected channel.
-Hence, the composite equivalent channel reduces to
+		At subband $n$, we denote the \gls{ap}-\gls{ue} direct channel as $\mathbf{h}_{\mathrm{D},n}^\mathsf{H} \in \mathbb{C}^{1 \times M}$, the \gls{ap}-\gls{ris} forward channel as $\mathbf{H}_{\mathrm{F},n} \in \mathbb{C}^{L \times M}$, and the \gls{ris}-\gls{ue} backward channel as $\mathbf{h}_{\mathrm{B},n}^\mathsf{H} \in \mathbb{C}^{1 \times L}$.
+		The auxiliary \gls{ap}-\gls{ris}-\gls{ue} link can be modeled as a concatenation of the backward channel, the \gls{ris} reflection, and the forward channel.
+		Hence, the equivalent channel is given by
 		\begin{equation}\label{eq:h_n}
-			\mathbf{h}_{n}^\mathsf{H} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{h}_{\mathrm{B},n}^\mathsf{H} \mathbf{\Theta} \mathbf{H}_{\mathrm{F},n} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{\phi}^\mathsf{H} \mathbf{V}_{n},
+			\mathbf{h}_{n}^\mathsf{H} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{h}_{\mathrm{B},n}^\mathsf{H} \mathbf{\Theta} \mathbf{H}_{\mathrm{F},n} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \boldsymbol{\theta}^\mathsf{H} \mathbf{V}_{n},
 		\end{equation}
-		where we define the cascaded incident-reflected channel at subband $n$ as $\mathbf{V}_{n} \triangleq \mathrm{diag}(\mathbf{h}_{\mathrm{B},n}^\mathsf{H})\mathbf{H}_{\mathrm{F},n} \in \mathbb{C}^{L \times M}$.
-We also define $\mathbf{h} \triangleq [\mathbf{h}_1^\mathsf{T},\dots,\mathbf{h}_N^\mathsf{T}]^\mathsf{T} \in \mathbb{C}^{MN \times 1}$.
+		where $\boldsymbol{\theta} \triangleq [\theta_1,\ldots,\theta_L]^\mathsf{H} \in \mathbb{C}^{L \times 1}$ and $\mathbf{V}_{n} \triangleq \mathrm{diag}(\mathbf{h}_{\mathrm{B},n}^\mathsf{H})\mathbf{H}_{\mathrm{F},n} \in \mathbb{C}^{L \times M}$ is the cascaded \gls{ris} channel.
+		% We also define $\mathbf{h} \triangleq [\mathbf{h}_1^\mathsf{T},\dots,\mathbf{h}_N^\mathsf{T}]^\mathsf{T} \in \mathbb{C}^{MN \times 1}$.
 
 		\begin{remark}\label{re:subband_tradeoff}
-			The cascaded channel varies at different subbands, but the reflection cannot be designed independently at different frequencies.
-Therefore, there exists a tradeoff for the passive beamforming design in the frequency domain, and the composite subchannels should be tuned adaptively to meet the specific requirement of multi-carrier \gls{swipt}.
-For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\mathbf{\phi},n} \lVert \mathbf{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\mathbf{\phi}} \min_n \lVert \mathbf{h}_n \rVert$).
-That is to say, \gls{ris} essentially enables a flexible subchannel design.
-In the \gls{miso} case, a similar effect also exists in the spatial domain.
-Therefore, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
+			The cascaded channel $\mathbf{V}_{n}$ varies at different subbands and there exists a trade-off for passive beamforming design in the frequency domain.
+			Therefore, the equivalent subchannels should be carefully designed to meet specific requirements of multi-carrier \gls{swipt}.
+For example, one can design the reflection pattern to either enhance the strongest subband (e.g., $\max_{\boldsymbol{\theta},n} \lVert \mathbf{h}_n \rVert$), or improve the fairness among subbands (e.g., $\max_{\boldsymbol{\theta}} \min_n \lVert \mathbf{h}_n \rVert$).
+That is to say, \gls{ris} enables a flexible subchannel design in multi-carrier transmissions.
+A similar effect also exists in the spatial domain for multi-antenna scenarios.
+In total, each reflection coefficient is indeed shared by $M$ antennas over $N$ subbands.
 		\end{remark}
@@
 	\begin{subsection}{Received Signal}
-		The received superposed signal at the single-antenna \gls{ue} is\footnote{We assume that the time difference of signal arrival via direct and auxiliary link is negligible compared to the symbol period.}
+		The received superposed signal at the single-antenna \gls{ue} is
 		\begin{equation}
-			y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\mathbf{h}_{n}^\mathsf{H}}{(\mathbf{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\mathbf{w}_{\mathrm{P},n})+\tilde{n}_n(t)\Bigr)}{e^{j2{\pi}{f_n}{t}}}\right\},
+			y(t) = \Re\left\{\sum_{n=1}^N{\Bigl(\mathbf{h}_{n}^\mathsf{H}}{(\mathbf{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)+\mathbf{w}_{\mathrm{P},n})+v_n(t)\Bigr)}{e^{\jmath 2{\pi}{f_n}{t}}}\right\},
 		\end{equation}
-		where $\tilde{n}_n(t)$ is the noise at \gls{rf} band $n$.
-Note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
+		where $v_n(t)$ is the noise at \gls{rf} band $n$.
+		Please note that the modulated component can be used for energy harvesting if necessary, but the multisine component carries no information and cannot be used for information decoding.
 	\end{subsection}
@@
 	\begin{subsection}{Receiving Modes}
-		\begin{figure}[!t]
-			\centering
-			\subfloat[\gls{ts} receiver\label{fi:ts_receiver}]{
-				\resizebox{0.9\columnwidth}{!}{
-					\input{assets/chapter_3/ts_receiver.tex}
-				}
-			}
-			\\
-			\subfloat[\gls{ps} receiver\label{fi:ps_receiver}]{
-				\resizebox{0.9\columnwidth}{!}{
-					\input{assets/chapter_3/ps_receiver.tex}
-				}
-			}
-			\caption{Diagrams of practical co-located receivers.}
-			\label{fi:receiver}
-		\end{figure}
-
-		As illustrated in Fig.~\ref{fi:receiver}, there are two practical receiving modes for the co-located information decoder and energy harvester \cite{Zhou2013}.
+		Following the discussion in Section \ref{sc:receiver_architectures}, we investigate the performance of \gls{ts} and \gls{ps} receivers in this work.
 The \gls{ts} receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
 During each session, the transmitter optimizes the waveform for either \gls{wit} or \gls{wpt}, while the receiver activates the information decoder or the energy harvester correspondingly.
-The duration ratio $\eta$ controls the \gls{r-e} tradeoff and is independent from the waveform and beamforming design.
+The duration ratio $\eta$ thus controls the \gls{r-e} trade-off and is independent from the waveform and beamforming design.
 On the other hand, the \gls{ps} receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively.
 The data stream is fed into the information decoder while the energy stream is fed into the energy harvester.
-During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different \gls{r-e} tradeoffs.
-In the following context, we consider the optimization with the \gls{ps} receiver, as the \gls{ts} receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
+During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different performance trade-offs.
+		Since the \gls{r-e} region of the \gls{ts} receiver can be inferred from that of the \gls{ps} receiver, we focus on the optimization with the \gls{ps} receiver in the following context.
 	\end{subsection}
@@
 	\begin{subsection}{Information Decoder}
-		A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform \cite{Clerckx2018b}.
-Therefore, the achievable rate is\footnote{It requires waveform cancellation or translated demodulation \cite{Clerckx2018b}.}
+		A major benefit of the superposed waveform is that the multisine is deterministic and its impact on \gls{wit} can be completely eliminated by waveform cancellation or translated demodulation \cite{Clerckx2018b}.
+		Therefore, the achievable rate is
 		\begin{equation}\label{eq:R}
-			R(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
+			R(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},
 		\end{equation}
-		where $\sigma_n^2$ is the noise variance at the \gls{rf}-band and during the \gls{rf}-to-baseband conversion on tone $n$.
+		where $\sigma_n^2$ is the variance of the total noise (at the \gls{rf}-band and during the \gls{rf}-to-baseband conversion) on tone $n$.
 	\end{subsection}
 
-	\begin{subsection}{Energy Harvester}\label{se:energy_harvester}
-		\begin{figure}[!t]
-			\centering
-			\subfloat[Antenna equivalent circuit\label{fi:antenna_equivalent_circuit}]{
-				\resizebox{0.45\columnwidth}{!}{
-					% \includegraphics{assets/antenna_equivalent_circuit.eps}
-					\input{assets/chapter_3/antenna_equivalent_circuit.tex}
-				}
-			}
-			\subfloat[A single diode rectifier\label{fi:single_diode_rectifier}]{
-				\resizebox{0.45\columnwidth}{!}{
-					% \includegraphics{assets/a_single_diode_rectifier.eps}
-					\input{assets/chapter_3/a_single_diode_rectifier.tex}
-				}
-			}
-			\caption{Equivalent circuits of receive antenna and energy harvester.}
-		\end{figure}
-
-		Taken from \cite{Clerckx2016a}, the rectenna model used in this section captures the dependency of the output \gls{dc} on both the power and shape of the received signal.
-Fig.~\subref*{fi:antenna_equivalent_circuit} illustrates the equivalent circuit of an ideal antenna, where the antenna has a resistance $R_{\mathrm{A}}$ and the incoming signal creates a voltage source $v_{\mathrm{S}}(t)$.
-Let $R_{\mathrm{in}}$ be the total input resistance of the rectifier and matching network, and we assume the voltage across the matching network is negligible.
-When perfectly matched (i.e., $R_{\mathrm{in}}=R_{\mathrm{A}}$), the rectifier input voltage is $v_{\mathrm{in}}(t)=y(t)\sqrt{\rho R_{\mathrm{A}}}$.
-Consider a simplified rectifier model in Fig.~\subref*{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load.
-As detailed in \cite{Clerckx2018b}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output \gls{dc} is equivalent to maximizing a monotonic function\footnote{This small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
+	\begin{subsection}{Energy Harvester}\label{sc:energy_harvester}
+		As discussed in Section \ref{sc:operation_regions}, the output \gls{dc} power of the energy harvester is a nonlinear function of the input power and waveform shape.
+		When the diode is forward-biased and unsaturated, a truncated Taylor expansion of the diode I-V characteristic equation suggests that maximizing the average output \gls{dc} is equivalent to maximizing a monotonic function \cite{Clerckx2018b}
 		\begin{equation}\label{eq:z}
-			z(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}},
+			z(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho)=\sum_{i=2,\text{even}}^{n_0}{\beta_i}{\rho^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y^i(t)\right\}\right\}},
 		\end{equation}
-		where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage).
+		which is slightly different from \eqref{eq:dc_power_nonlinear} in that (i) only a power ratio $\rho$ of the received signal is used for energy harvesting and (ii) part of the received waveform is modulated such that expectation has to be taken.
 		With a slight abuse of notation, we refer to $z$ as the average output \gls{dc} in this chapter.
@@
 In other words, even-order terms with $i \ge 4$ account for the nonlinear diode behavior.
-For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}.
-Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order \gls{dc} terms.
-Let $\mathbf{W}_{\mathrm{I/P}} \triangleq \mathbf{w}_{\mathrm{I/P}}\mathbf{w}_{\mathrm{I/P}}^\mathsf{H} \in \mathbb{C}^{MN \times MN}$.
-As illustrated by Fig.~\ref{fi:block_diagonal}, $\mathbf{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\mathbf{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\mathbf{0}$.
-Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4} \cite{Golub2013}.
+For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity.
+The average output \gls{dc} power is then
+		\begin{equation}
+			\begin{split}
+				z(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho)
+				& = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)\\
+				& \quad +\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}
+			\end{split}
+		\end{equation}
+		and the components can be further rewritten as (note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$ applies a modulation gain on the fourth-order \gls{dc} terms)
+		\begin{subequations}
+			\begin{equation}
+				\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})^*} = \frac{1}{2}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I},0}\mathbf{h},\label{eq:y_I2}
+				% \begin{split}
+				% 	\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}
+				% 	& = \frac{1}{2}\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})^*}\\
+				% 	& = \frac{1}{2}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I},0}\mathbf{h},\label{eq:y_I2}
+				% \end{split}
+			\end{equation}
+			\begin{equation}
+					\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I},0}\mathbf{h})^2,\label{eq:y_I4}
+				% \begin{split}
+				% 	\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}
+				% 	& = \frac{3}{4}\left(\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})^*}\right)^2\\
+				% 	& = \frac{3}{4}(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I},0}\mathbf{h})^2,\label{eq:y_I4}
+				% \end{split}
+			\end{equation}
+			\begin{equation}
+				\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{P},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{P},n})^*} = \frac{1}{2}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},0}\mathbf{h},\label{eq:y_P2}
+				% \begin{split}
+				% 	\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}
+				% 	& = \frac{1}{2}\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{P},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{P},n})^*}\\
+				% 	& = \frac{1}{2}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},0}\mathbf{h},\label{eq:y_P2}
+				% \end{split}
+			\end{equation}
+			\begin{equation}
+				\begin{split}
+					\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}
+					& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\mathbf{h}_{{n_1}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_1}})(\mathbf{h}_{{n_2}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_2}})(\mathbf{h}_{{n_3}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_3}})^*(\mathbf{h}_{{n_4}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_4}})^*}\\
+					& = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},k}\mathbf{h})(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},k}\mathbf{h})^*,\label{eq:y_P4}
+				\end{split}
+			\end{equation}
+		\end{subequations}
+		where we define $\mathbf{h} \triangleq [\mathbf{h}_1^\mathsf{T},\dots,\mathbf{h}_N^\mathsf{T}]^\mathsf{T} \in \mathbb{C}^{MN \times 1}$ and $\mathbf{W}_{\mathrm{I/P}} \triangleq \mathbf{w}_{\mathrm{I/P}}\mathbf{w}_{\mathrm{I/P}}^\mathsf{H} \in \mathbb{H}_+^{MN \times MN}$.
+As illustrated by Fig.~\ref{fg:block_diagonal}, $\mathbf{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$.
+Let $\mathbf{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\mathbf{0}$.
 
-		\begin{figure*}[!t]
+		\begin{figure}[H]
 			\begin{equation*}
@@
 For $\mathbf{w}_{\mathrm{I/P},n_1}\mathbf{w}_{\mathrm{I/P},n_2}^\mathsf{H}$, the $k$-th block diagonal satisfies $k=n_2-n_1$.}
-			\label{fi:block_diagonal}
-		\end{figure*}
-
-		\begin{figure*}[!b]
-			\hrule
-			\begin{align}
-				&z(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho) = \beta_2\rho\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr)+\beta_4\rho^2\Bigl(\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}+\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}+6\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\}\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\}\Bigr),\label{eq:z_expand}\\
-				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^2(t)\right\}\right\} = \frac{1}{2}\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})^*} = \frac{1}{2}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I},0}\mathbf{h},\label{eq:y_I2}\\
-				&\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\} = \frac{3}{4}\left(\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n})^*}\right)^2 = \frac{3}{4}(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I},0}\mathbf{h})^2,\label{eq:y_I4}\\
-				&\mathbb{A}\left\{y_{\mathrm{P}}^2(t)\right\} = \frac{1}{2}\sum_{n=1}^N{(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{P},n})(\mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{P},n})^*} = \frac{1}{2}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},0}\mathbf{h},\label{eq:y_P2}\\
-				&\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\} = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(\mathbf{h}_{{n_1}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_1}})(\mathbf{h}_{{n_2}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_2}})(\mathbf{h}_{{n_3}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_3}})^*(\mathbf{h}_{{n_4}}^\mathsf{H}\mathbf{w}_{\mathrm{P},{n_4}})^*} = \frac{3}{8}\sum_{k=-N+1}^{N-1}(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},k}\mathbf{h})(\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{P},k}\mathbf{h})^*.\label{eq:y_P4}
-			\end{align}
-		\end{figure*}
+			\label{fg:block_diagonal}
+		\end{figure}
 	\end{subsection}
@@
 	\begin{subsection}{Rate-Energy Region}
-		The achievable \gls{r-e} region is defined as
-		\begin{align}
-			\mathcal{C}_{\mathrm{\gls{r-e}}}
-			&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
-			&\quad \frac{1}{2}\left(\lVert{\mathbf{w}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
-		\end{align}
-		where $P$ is the average transmit power budget and 1/2 converts the peak value of the sine waves to the average value.
+		The achievable \gls{r-e} region for the \gls{ps} receiver is explicitly defined as
+		% \begin{align}
+		% 	\mathcal{C}_{\mathrm{\gls{r-e}}}
+		% 	&\triangleq \biggl\{(R_{\mathrm{ID}}, z_{\mathrm{EH}}) \in \mathbb{R}_+^2 \mid R_{\mathrm{ID}} \le R, z_{\mathrm{EH}} \le z,\nonumber\\
+		% 	&\quad \frac{1}{2}\left(\lVert{\mathbf{w}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{w}_{\mathrm{P}}}\rVert^2\right) \le P\biggr\},
+		% \end{align}
+		\begin{equation}
+			\begin{split}
+				\mathcal{C}_\mathrm{R-E}(P)\triangleq \Bigl\{
+					& (r,e) : 0 \le r \le R(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\rho), \ 0 \le e \le z(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho),\\
+					& \quad \left(\lVert{\mathbf{w}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{w}_{\mathrm{P}}}\rVert^2\right)/2 \le P \Bigr\},
+			\end{split}
+		\end{equation}
+		where $P$ is the average transmit power budget and the 1/2 converts the peak to average.
 	\end{subsection}
@@
 
-\begin{section}{Problem Formulation}\label{se:problem_formulation}
-	We characterize each \gls{r-e} boundary point through a current maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
+\begin{section}{Problem Formulation}\label{sc:problem_formulation}
+	We characterize each \gls{r-e} boundary point through a \gls{dc} maximization problem subject to sum rate, transmit power, and reflection amplitude constraints as
 	\begin{maxi!}
-		{\scriptstyle{\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho}}{z(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
-		\addConstraint{R(\mathbf{\phi},\mathbf{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
+		{\scriptstyle{\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho}}{z(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
+		\addConstraint{R(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
 		\addConstraint{\frac{1}{2}\left(\lVert{\mathbf{w}_{\mathrm{I}}}\rVert^2+\lVert{\mathbf{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
-		\addConstraint{\lvert{\mathbf{\phi}}\rvert=\mathbf{1}}\label{co:original_modulus}
+		\addConstraint{\lvert{\boldsymbol{\theta}}\rvert=\mathbf{1}}\label{co:original_modulus}
 		\addConstraint{0 \le \rho \le 1.}
@@
 	\begin{subsection}{Passive Beamforming}
-		In this section, we optimize the \gls{ris} phase shift $\mathbf{\phi}$ for any given waveform $\mathbf{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
+		In this section, we optimize the \gls{ris} phase shift $\boldsymbol{\theta}$ for any given waveform $\mathbf{w}_{\mathrm{I/P}}$ and splitting ratio $\rho$. Note that
 		\begin{align}
@@
 			& = \mathbf{w}_{a\mathrm{I},n}^\mathsf{H}\mathbf{h}_n\mathbf{h}_n^\mathsf{H}\mathbf{w}_{\mathrm{I},n}\nonumber\\
-			& = \mathbf{w}_{\mathrm{I},n}^\mathsf{H}(\mathbf{h}_{\mathrm{D},n}+\mathbf{V}_n^\mathsf{H}\mathbf{\phi})(\mathbf{h}_{\mathrm{D},n}^\mathsf{H}+\mathbf{\phi}^\mathsf{H}\mathbf{V}_n)\mathbf{w}_{\mathrm{I},n}\nonumber\\
-			& = \mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H}\mathbf{\Phi}\mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\nonumber\\
-			& = \mathrm{tr}(\mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H}\mathbf{\Phi})\nonumber\\
-			& = \mathrm{tr}(\mathbf{C}_n\mathbf{\Phi}),
+			& = \mathbf{w}_{\mathrm{I},n}^\mathsf{H}(\mathbf{h}_{\mathrm{D},n}+\mathbf{V}_n^\mathsf{H}\boldsymbol{\theta})(\mathbf{h}_{\mathrm{D},n}^\mathsf{H}+\boldsymbol{\theta}^\mathsf{H}\mathbf{V}_n)\mathbf{w}_{\mathrm{I},n}\nonumber\\
+			& = \mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H}\bar{\mathbf{\Theta}}\mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\nonumber\\
+			& = \mathrm{tr}(\mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H}\bar{\mathbf{\Theta}})\nonumber\\
+			& = \mathrm{tr}(\mathbf{C}_n\bar{\mathbf{\Theta}}),
 		\end{align}
-		where $\mathbf{M}_n \triangleq [\mathbf{V}_n^\mathsf{H}, \mathbf{h}_{\mathrm{D},n}]^\mathsf{H} \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\mathbf{\phi}} \triangleq [\mathbf{\phi}^\mathsf{H}, t']^\mathsf{H} \in \mathbb{C}^{(L+1) \times 1}$, $\mathbf{\Phi} \triangleq \bar{\mathbf{\phi}}\bar{\mathbf{\phi}}^\mathsf{H} \in \mathbb{C}^{(L+1) \times (L+1)}$, $\mathbf{C}_n \triangleq \mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H} \in \mathbb{C}^{(L+1)\times(L+1)}$.
+		where $\mathbf{M}_n \triangleq [\mathbf{V}_n^\mathsf{H}, \mathbf{h}_{\mathrm{D},n}]^\mathsf{H} \in \mathbb{C}^{(L+1) \times M}$, $t'$ is an auxiliary variable with unit modulus, $\bar{\boldsymbol{\theta}} \triangleq [\boldsymbol{\theta}^\mathsf{H}, t']^\mathsf{H} \in \mathbb{C}^{(L+1) \times 1}$, $\bar{\mathbf{\Theta}} \triangleq \bar{\boldsymbol{\theta}}\bar{\boldsymbol{\theta}}^\mathsf{H} \in \mathbb{H}_+^{(L+1) \times (L+1)}$, $\mathbf{C}_n \triangleq \mathbf{M}_n\mathbf{w}_{\mathrm{I},n}\mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{M}_n^\mathsf{H} \in \mathbb{H}_+^{(L+1)\times(L+1)}$.
 On the other hand, we define $t_{\mathrm{I/P},k}$ as
@@
 			& = \mathrm{tr}(\mathbf{h}\mathbf{h}^\mathsf{H}\mathbf{W}_{\mathrm{I/P},k})\nonumber\\
-			& = \mathrm{tr}\left((\mathbf{h}_{D}+\mathbf{V}^\mathsf{H}\mathbf{\phi})(\mathbf{h}_{D}^\mathsf{H}+\mathbf{\phi}^\mathsf{H}\mathbf{V})\mathbf{W}_{\mathrm{I/P},k}\right)\nonumber\\
-			& = \mathrm{tr}(\mathbf{M}^\mathsf{H}\mathbf{\Phi}\mathbf{M}\mathbf{W}_{\mathrm{I/P},k})\nonumber\\
-			& = \mathrm{tr}(\mathbf{M}\mathbf{W}_{\mathrm{I/P},k}\mathbf{M}^\mathsf{H}\mathbf{\Phi})\nonumber\\
-			& = \mathrm{tr}(\mathbf{C}_{\mathrm{I/P},k}\mathbf{\Phi})\label{eq:t_k},
+			& = \mathrm{tr}\left((\mathbf{h}_{D}+\mathbf{V}^\mathsf{H}\boldsymbol{\theta})(\mathbf{h}_{D}^\mathsf{H}+\boldsymbol{\theta}^\mathsf{H}\mathbf{V})\mathbf{W}_{\mathrm{I/P},k}\right)\nonumber\\
+			& = \mathrm{tr}(\mathbf{M}^\mathsf{H}\bar{\mathbf{\Theta}}\mathbf{M}\mathbf{W}_{\mathrm{I/P},k})\nonumber\\
+			& = \mathrm{tr}(\mathbf{M}\mathbf{W}_{\mathrm{I/P},k}\mathbf{M}^\mathsf{H}\bar{\mathbf{\Theta}})\nonumber\\
+			& = \mathrm{tr}(\mathbf{C}_{\mathrm{I/P},k}\bar{\mathbf{\Theta}})\label{eq:t_k},
 		\end{align}
@@
 On top of this, \eqref{eq:R} and \eqref{eq:z_expand} reduce respectively to
+		\begin{equation}
+			R(\bar{\mathbf{\Theta}}) = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\mathbf{C}_n\bar{\mathbf{\Theta}})}{\sigma_n^2}\right)},\label{eq:R_irs}
+		\end{equation}
+		\begin{equation}
+			z(\bar{\mathbf{\Theta}}) = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right) + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+		\end{equation}
+		To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
+Based on the solution at iteration $r{-}1$, the approximations at iteration $r$ are
 		\begin{align}
-			R(\mathbf{\Phi})
-			& = \sum_{n=1}^{N}{\log_2\left(1+\frac{(1-\rho)\mathrm{tr}(\mathbf{C}_n\mathbf{\Phi})}{\sigma_n^2}\right)},\label{eq:R_irs}\\
-			z(\mathbf{\Phi})
-			& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0}) + \frac{3}{8}{\beta_4}{\rho^2} \left(2t_{\mathrm{I},0}^2 + \sum_{k=-N+1}^{N-1}{t_{\mathrm{P},k}t_{\mathrm{P},k}^*}\right)\nonumber\\
-			& \quad + \frac{3}{2}{\beta_4}{\rho^2}t_{\mathrm{I},0}t_{\mathrm{P},0}.\label{eq:z_irs}
+			(t_{\mathrm{I},0}^{(r)})^2
+			& \ge 2 t_{\mathrm{I},0}^{(r)}t_{\mathrm{I},0}^{(r-1)} - (t_{\mathrm{I},0}^{(r-1)})^2,\label{eq:taylor_1}\\
+			t_{\mathrm{P},k}^{(r)} (t_{\mathrm{P},k}^{(r)})^*
+			& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(r)} (t_{\mathrm{P},k}^{(r-1)})^*\right\} - t_{\mathrm{P},k}^{(r-1)} (t_{\mathrm{P},k}^{(r-1)})^*,\label{eq:taylor_2}\\
+			t_{\mathrm{I},0}^{(r)} t_{\mathrm{P},0}^{(r)}
+			& \ge t_{\mathrm{I},0}^{(r)} t_{\mathrm{P},0}^{(r-1)} + t_{\mathrm{P},0}^{(r)} t_{\mathrm{I},0}^{(r-1)} - t_{\mathrm{I},0}^{(r-1)} t_{\mathrm{P},0}^{(r-1)}.\label{eq:taylor_3}
 		\end{align}
-		To maximize the non-concave expression \eqref{eq:z_irs}, we successively lower bound the second-order terms by their first-order Taylor expansions \cite{Adali2010}.
-Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are
-		\begin{align}
-			(t_{\mathrm{I},0}^{(i)})^2
-			& \ge 2 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - (t_{\mathrm{I},0}^{(i-1)})^2,\label{eq:taylor_1}\\
-			t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i)})^*
-			& \ge 2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*,\label{eq:taylor_2}\\
-			t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i)}
-			& \ge t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}.\label{eq:taylor_3}
-		\end{align}
-		Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\mathbf{C}_{\mathrm{I/P},0}\mathbf{\Phi})$ is real-valued because $\mathbf{C}_{\mathrm{I/P},0}$ and $\mathbf{\Phi}$ are Hermitian matrices.
+		Note that $t_{\mathrm{I/P},0}=\mathrm{tr}(\mathbf{C}_{\mathrm{I/P},0}\bar{\mathbf{\Theta}})$ is real-valued because $\mathbf{C}_{\mathrm{I/P},0}$ and $\bar{\mathbf{\Theta}}$ are Hermitian matrices.
 Due to symmetry \cite{Golub2013}, we have
 		\begin{equation}\label{eq:coupled_terms}
-			\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*.
+			\sum_{k=-N+1}^{N-1} \Re\left\{t_{\mathrm{P},k}^{(r)} (t_{\mathrm{P},k}^{(r-1)})^*\right\} = \sum_{k=-N+1}^{N-1} t_{\mathrm{P},k}^{(r)} (t_{\mathrm{P},k}^{(r-1)})^*.
 		\end{equation}
-		Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the \gls{dc} approximation $\tilde{z}$ as \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
-		\begin{figure*}[!b]
-			\hrule
-			\begin{align}
-				\tilde{z}(\mathbf{\Phi}^{(i)})
-				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
-				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(i)} t_{\mathrm{P},0}^{(i-1)} + t_{\mathrm{P},0}^{(i)} t_{\mathrm{I},0}^{(i-1)} - t_{\mathrm{I},0}^{(i-1)} t_{\mathrm{P},0}^{(i-1)}\right).\label{eq:z_irs_approx}
-			\end{align}
-		\end{figure*}
+		Plugging \eqref{eq:taylor_1}--\eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the \gls{dc} approximation $\tilde{z}$ as
+		\begin{equation}
+			\begin{split}
+				\tilde{z}(\bar{\mathbf{\Theta}}^{(r)})
+				& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(r)}+t_{\mathrm{P},0}^{(r)}) + \frac{3}{2}{\beta_4}{\rho^2} \left(t_{\mathrm{I},0}^{(r)} t_{\mathrm{P},0}^{(r-1)} + t_{\mathrm{P},0}^{(r)} t_{\mathrm{I},0}^{(r-1)} - t_{\mathrm{I},0}^{(r-1)} t_{\mathrm{P},0}^{(r-1)}\right)\\
+				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(r)}t_{\mathrm{I},0}^{(r-1)} - 2 (t_{\mathrm{I},0}^{(r-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(r)} (t_{\mathrm{P},k}^{(r-1)})^* - t_{\mathrm{P},k}^{(r-1)} (t_{\mathrm{P},k}^{(r-1)})^*}\right), \label{eq:z_irs_approx}
+			\end{split}
+		\end{equation}
+		and transform problem~\eqref{op:original} to
 		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Phi}}}{\tilde{z}(\mathbf{\Phi})}{\label{op:irs}}{\label{ob:irs}}
-			\addConstraint{R(\mathbf{\Phi}) \ge \bar{R}}\label{co:irs_rate}
-			\addConstraint{\mathrm{diag}^{-1}(\mathbf{\Phi})=\mathbf{1}}\label{co:irs_modulus}
-			\addConstraint{\mathbf{\Phi}\succeq{\mathbf{0}}}\label{co:irs_sd}
-			\addConstraint{\mathrm{rank}(\mathbf{\Phi})=1.\label{co:irs_rank}}
+			{\scriptstyle{\bar{\mathbf{\Theta}}}}{\tilde{z}(\bar{\mathbf{\Theta}})}{\label{op:irs}}{\label{ob:irs}}
+			\addConstraint{R(\bar{\mathbf{\Theta}}) \ge \bar{R}}\label{co:irs_rate}
+			\addConstraint{\mathrm{diag}^{-1}(\bar{\mathbf{\Theta}})=\mathbf{1}}\label{co:irs_modulus}
+			\addConstraint{\bar{\mathbf{\Theta}}\succeq{\mathbf{0}}}\label{co:irs_sd}
+			\addConstraint{\mathrm{rank}(\bar{\mathbf{\Theta}})=1.\label{co:irs_rank}}
 		\end{maxi!}
-		We then apply \gls{sdr} to the unit-rank constraint \eqref{co:irs_rank} and formulate a \gls{sdp} with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}.
-In this specific case, we found the solution provided by \texttt{CVX toolbox} \cite{Grant2016} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}.
-This conclusion is summarized below.
+		The unit-rank constraint \eqref{co:irs_rank} can be relaxed to formulate a \gls{sdp} with approximation accuracy no greater than $\pi/4$ \cite{Luo2010b}.
+		The resulting problem can be solved efficiently by \texttt{CVX toolbox} \cite{Grant2016}.
 
 		\begin{proposition}\label{pr:relaxation}
-			Any optimal solution $\mathbf{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by \gls{sdr}.
+			Any optimal solution $\bar{\mathbf{\Theta}}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is strictly rank-\num{1}.
+			That is to say, \eqref{co:irs_rank} is redundant and no loss is introduced by \gls{sdr}.
 		\end{proposition}
@@
 
-		In summary, we update $\mathbf{\Phi}^{(i)}$ until convergence, extract $\hat{\mathbf{\phi}}^\star$ by eigen decomposition, and retrieve the	\gls{ris} vector by $\mathbf{\phi}^{\star}=e^{j \arg\left([\hat{\mathbf{\phi}}^\star]_{(1:L)} \middle/ [\hat{\mathbf{\phi}}^\star]_{(L+1)}\right)}$.
+		In summary, we update $\bar{\mathbf{\Theta}}^{(r)}$ by iteratively solving \eqref{ob:irs}--\eqref{co:irs_sd} until convergence, extract $\hat{\boldsymbol{\theta}}^\star$ by eigen decomposition, and retrieve the \gls{ris} vector by $\boldsymbol{\theta}^{\star}=e^{\jmath  \arg\left([\hat{\boldsymbol{\theta}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\theta}}^\star]_{(L+1)}\right)}$.
 The passive beamforming design is summarized in the \gls{sca} Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints.
@@
 				\State Construct $\mathbf{V}$, $\mathbf{M}$, $\mathbf{M}_n$, $\mathbf{C}_{n}$, $\mathbf{C}_{\mathrm{I/P},k}$, $\forall n,k$
-				\State \textbf{Initialize} $i \gets 0$, $\mathbf{\Phi}^{(0)}$
+				\State \textbf{Initialize} $i \gets 0$, $\bar{\mathbf{\Theta}}^{(0)}$
 				\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
@@
 					\State $i \gets i + 1$
-					\State Get $\mathbf{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
-					\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-					\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-				\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-				\State Set $\mathbf{\Phi}^{\star} \gets \mathbf{\Phi}^{(i)}$
-				\State Get $\hat{\mathbf{\phi}}^\star$ by eigen decomposition, $\mathbf{\Phi}^{\star}=\hat{\mathbf{\phi}}^\star(\hat{\mathbf{\phi}}^\star)^\mathsf{H}$
-				\State Set $\mathbf{\phi}^{\star} \gets e^{j \arg\left([\hat{\mathbf{\phi}}^\star]_{(1:L)} \middle/ [\hat{\mathbf{\phi}}^\star]_{(L+1)}\right)}$
-				\State \textbf{Output} $\mathbf{\phi}^{\star}$
+					\State Get $\bar{\mathbf{\Theta}}^{(r)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
+					\State Update $t_{\mathrm{I/P},k}^{(r)}$, $\forall k$ by \eqref{eq:t_k}
+					\State Compute $z^{(r)}$ by \eqref{eq:z_irs}
+				\Until $\lvert z^{(r)}-z^{(r-1)} \rvert \le \epsilon$
+				\State Set $\bar{\mathbf{\Theta}}^{\star} \gets \bar{\mathbf{\Theta}}^{(r)}$
+				\State Get $\hat{\boldsymbol{\theta}}^\star$ by eigen decomposition, $\bar{\mathbf{\Theta}}^{\star}=\hat{\boldsymbol{\theta}}^\star(\hat{\boldsymbol{\theta}}^\star)^\mathsf{H}$
+				\State Set $\boldsymbol{\theta}^{\star} \gets e^{\jmath  \arg\left([\hat{\boldsymbol{\theta}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\theta}}^\star]_{(L+1)}\right)}$
+				\State \textbf{Output} $\boldsymbol{\theta}^{\star}$
 			\end{algorithmic}
@@
 	\begin{subsection}{Active Beamforming}
-		The original waveform and active beamforming problem~\eqref{op:original} is over complex vectors $\mathbf{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
-Next, we decouple the design in spatial and frequency domains, enable independent optimizations correspondingly, and reduce the size of variables from $2MN$ to $2(M+N)$.
-The weight on subband $n$ is essentially
+		The original waveform and active beamforming problem~\eqref{op:original} is over complex-valued vectors $\mathbf{w}_{\mathrm{I/P}}$ of size $MN \times 1$.
+		The weight on subband $n$ can be decomposed in spatial and frequency domains as
 		\begin{equation}\label{eq:w}
-			\mathbf{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \mathbf{b}_{\mathrm{I/P}, n},
+			\mathbf{w}_{\mathrm{I/P}, n} = s_{\mathrm{I/P}, n} \mathbf{p}_{\mathrm{I/P}, n},
 		\end{equation}
-		where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\mathbf{b}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
-Define $\mathbf{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^\mathsf{T} \in \mathbb{R}_+^{N \times 1}$.
-The \gls{mrt} precoder at subband $n$ is given by
-		\begin{equation}\label{eq:b_n}
-			\mathbf{b}_{\mathrm{I/P}, n}^\star = \frac{\mathbf{h}_n}{\lVert{\mathbf{h}_n}\rVert}.
+		where $s_{\mathrm{I/P},n}$ denotes the amplitude of the modulated/multisine waveform at tone $n$, and $\mathbf{p}_{\mathrm{I/P}, n}$ denotes the corresponding information/power precoder.
+		This decoupling allows independent spatial and frequency optimizations, reducing the size of variables from $2MN$ to $2(M+N)$.
+		\begin{proposition}\label{pr:mrt}
+			For single-user \gls{swipt}, the global optimal information and power precoders coincide at the \gls{mrt}
+			\begin{equation}\label{eq:precoder_mrt}
+				\mathbf{p}_{\mathrm{I/P}, n}^\star = \frac{\mathbf{h}_n}{\lVert{\mathbf{h}_n}\rVert}.
 			\end{equation}
-
-		\begin{proposition}\label{pr:mrt}
-			For single-user \gls{swipt}, the global optimal information and power precoders coincide at the \gls{mrt}.
 		\end{proposition}
@@
 	\begin{subsection}{Waveform and Splitting Ratio}
-		Next, we jointly optimize the waveform amplitude $\mathbf{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given \gls{ris} phase shift $\mathbf{\phi}$ and active precoder $\mathbf{b}_{\mathrm{I/P},n}$, $\forall n$.
-On top of \eqref{eq:b_n}, the equivalent channel strength at subband $n$ is $\lVert{\mathbf{h}_n}\rVert$.
-Hence, the rate \eqref{eq:R} reduces to
+		% Let $\mathbf{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^\mathsf{T} \in \mathbb{R}_+^{N \times 1}$.
+		Next, we jointly optimize the waveform amplitude $\mathbf{s}_{\mathrm{I/P}} \triangleq [s_{\mathrm{I/P},1},\dots,s_{\mathrm{I/P},N}]^\mathsf{T} \in \mathbb{R}_+^{N \times 1}$ and the splitting ratio $\rho \in \mathbb{I}$ for any given \gls{ris} phase shift $\boldsymbol{\theta}$ and active precoder $\mathbf{p}_{\mathrm{I/P},n}$, $\forall n$.
+		With \gls{mrt} precoder \eqref{eq:precoder_mrt}, the equivalent channel strength at subband $n$ is $\lVert{\mathbf{h}_n}\rVert$, such that the achievable rate \eqref{eq:R} reduces to
 		\begin{equation}\label{eq:R_waveform}
@@
 		\end{equation}
-		and the \gls{dc} \eqref{eq:z_expand} rewrites as \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
-		\begin{figure*}[!b]
-			\hrule
-			\begin{align}
+		and the \gls{dc} \eqref{eq:z_expand} rewrites as
+		\begin{equation}
+			\begin{split}
 				z(\mathbf{s}_{\mathrm{I}},\mathbf{s}_\mathrm{P},\rho)
-				& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\mathbf{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\mathbf{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\mathbf{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
+				& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\mathbf{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2)\\
+				& \quad + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\mathbf{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\mathbf{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\\
 				& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\mathbf{h}_{n_1}}\rVert^2 \lVert{\mathbf{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).\label{eq:z_waveform}
-			\end{align}
-		\end{figure*}
+			\end{split}
+		\end{equation}
+		Problem~\eqref{op:original} boils down to
 		\begin{maxi!}
@@
 		\end{mini!}
-		It can be concluded that $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power is wasted at the receiver.
+		Apparently, $\bar{\rho}^{\star}=1-\rho^{\star}$ as no power should be wasted at the receiver.
 The denominators of \eqref{co:waveform_rate} and \eqref{co:waveform_objective} consist of posynomials \cite{Boyd2007} that can be decomposed as sums of monomials
@@
 		where $\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}} \ge 0$ and $\sum_{m_{\mathrm{I},n}}\gamma_{m_{\mathrm{I},n}}=\sum_{m_\mathrm{P}}\gamma_{m_\mathrm{P}}=1$.
-The tightness of the AM-GM inequality depends on $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $i$ is
+The tightness of the AM-GM inequality depends on the selection of $\{\gamma_{m_{\mathrm{I},n}},\gamma_{m_\mathrm{P}}\}$, and a feasible choice at iteration $r$ is
 		\begin{align}
-			\gamma_{m_{\mathrm{I},n}}^{(i)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(i-1)},\bar{\rho}^{(i-1)})}{1+{\bar{\rho}^{(i-1)}\lVert{\mathbf{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(i-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
-			\gamma_{m_\mathrm{P}}^{(i)} & = \frac{g_{m_\mathrm{P}}(\mathbf{s}_{\mathrm{I}}^{(i-1)},\mathbf{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}{z(\mathbf{s}_{\mathrm{I}}^{(i-1)},\mathbf{s}_\mathrm{P}^{(i-1)},\rho^{(i-1)})}\label{eq:gamma_P}.
+			\gamma_{m_{\mathrm{I},n}}^{(r)} & = \frac{g_{m_{\mathrm{I},n}}(s_{\mathrm{I},n}^{(r-1)},\bar{\rho}^{(r-1)})}{1+{\bar{\rho}^{(r-1)}\lVert{\mathbf{h}_n}\rVert^2 (s_{\mathrm{I},n}^{(r-1)})^2}\big/{\sigma_n^2}}\label{eq:gamma_I},\\
+			\gamma_{m_\mathrm{P}}^{(r)} & = \frac{g_{m_\mathrm{P}}(\mathbf{s}_{\mathrm{I}}^{(r-1)},\mathbf{s}_\mathrm{P}^{(r-1)},\rho^{(r-1)})}{z(\mathbf{s}_{\mathrm{I}}^{(r-1)},\mathbf{s}_\mathrm{P}^{(r-1)},\rho^{(r-1)})}\label{eq:gamma_P}.
 		\end{align}
-		With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as \texttt{CVX toolbox} \cite{Grant2016}.
-We update $\mathbf{s}_{\mathrm{I}}^{(i)},\mathbf{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence.
+		With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} becomes convex and can be solved by \texttt{CVX toolbox} \cite{Grant2016}.
+We update $\mathbf{s}_{\mathrm{I}}^{(r)},\mathbf{s}_\mathrm{P}^{(r)},\rho^{(r)}$ iteratively until convergence.
 The joint waveform amplitude and splitting ratio design is summarized in the \gls{gp} Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.
@@
 					\State $i \gets i + 1$
-					\State Update $\gamma_{m_{\mathrm{I},n}}^{(i)}$, $\gamma_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
-					\State Get $\mathbf{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
-					\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
-					\State Update $g_{m_{\mathrm{I},n}}^{(i)}$, $g_{m_\mathrm{P}}^{(i)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
-				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-				\State Set $\mathbf{s}_{\mathrm{I/P}}^{\star} \gets \mathbf{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
+					\State Update $\gamma_{m_{\mathrm{I},n}}^{(r)}$, $\gamma_{m_\mathrm{P}}^{(r)}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
+					\State Get $\mathbf{s}_{\mathrm{I/P}}^{(r)}$, $\rho^{(r)}$ by solving problem~\eqref{op:waveform_gp}
+					\State Compute $R^{(r)}$, $z^{(r)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\State Update $g_{m_{\mathrm{I},n}}^{(r)}$, $g_{m_\mathrm{P}}^{(r)}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
+				\Until $\lvert z^{(r)} - z^{(r-1)} \rvert \le \epsilon$
+				\State Set $\mathbf{s}_{\mathrm{I/P}}^{\star} \gets \mathbf{s}_{\mathrm{I/P}}^{(r)}$, $\rho^{\star} \gets \rho^{(r)}$
 				\State \textbf{Output} $\mathbf{s}_{\mathrm{I}}^{\star}$, $\mathbf{s}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
@@
 		\begin{proof}\label{pf:gp}
-			Please refer to \cite{Clerckx2016a,Clerckx2018b}.
+			The proof is similar to \cite{Clerckx2016a,Clerckx2018b} and is omitted here.
 		\end{proof}
@@
 	\begin{subsection}{Low-Complexity Adaptive Design}
-		To facilitate practical \gls{swipt} implementation, we propose two closed-form adaptive waveform amplitude schemes by combining \gls{wf} and \gls{smf} in time and power domains, respectively.
-For \gls{wit}, the optimal \gls{wf} strategy assigns the amplitude of modulated tone $n$ by
+		To facilitate practical \gls{swipt} implementation, we propose two closed-form waveform schemes for \gls{ts} and \gls{ps} receivers, respectively.
+		\begin{itemize}
+			\item \emph{\gls{ts}:} As discussed Section \ref{sc:receiver_architectures}, each time block is divided into orthogonal phases and there is no waveform superposition.
+			For the \gls{wit} phase, the optimal modulated waveform amplitude is given by the \gls{wf} strategy \cite{Tse2005}
 			\begin{equation}\label{eq:wf}
@@
 			\end{equation}
-		where $\lambda$ is chosen to satisfy the power constraint $\lVert{\mathbf{s}_I}\rVert^2 / 2 \le P$.
-The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here.
-On the other hand, \gls{smf} was proposed in \cite{Clerckx2017} as a suboptimal \gls{wpt} resource allocation scheme that assigns the amplitude of sinewave $n$ by
+			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\mathbf{s}_I}\rVert^2 / 2 \le P$ and can be obtained by iterative methods \cite{Clerckx2013}.
+			For the \gls{wpt} phase, a reasonable multisine waveform amplitude is given by the \gls{smf} strategy \cite{Clerckx2017}
 			\begin{equation}\label{eq:smf}
@@
 			\end{equation}
-		where the scaling ratio $\alpha \ge 1$ is predetermined to exploit the rectifier nonlinearity and frequency selectivity.
-When the receiver works in \gls{ts} mode, there is no superposition in the suboptimal waveform design (modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session).
-When the receiver works in \gls{ps} mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
+			where the scaling ratio $\alpha \ge 1$ is a design parameter that exploits the rectifier nonlinearity and frequency selectivity.
+			\item \emph{\gls{ps}:} When the receiver works in \gls{ps} mode, the modulated and multisine components in the superposed waveform are respectively
+			% we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
 			\begin{align}
@@
 			\end{align}
-		where the $\delta$ determines the power ratio of multisine waveform at the transmitter, and $\rho$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the \gls{wit} point and $\delta^{\star}=\rho^{\star}=1$ at the \gls{wpt} point when $N$ is relatively large.
-Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated for efficient \gls{swipt} design.}
+			where the $\delta \in \mathbb{I}$ determines the power ratio of multisine waveform at the transmitter, and $\rho \in \mathbb{I}$ determines the power ratio of the energy harvester at the receiver.\footnote{We notice that $\delta^{\star}=\rho^{\star}=0$ at the \gls{wit} point and $\delta^{\star}=\rho^{\star}=1$ at the \gls{wpt} point.
+Intuitively, $\delta^{\star}$ and $\rho^{\star}$ should be positively correlated to improve the \gls{r-e} trade-off.}
+		\end{itemize}
 
-		Besides, minor modifications are required for passive beamforming to accommodate the low-complexity waveform schemes.
-Specifically, the rate constraint \eqref{co:irs_rate} should be dropped as the achievable rate is controlled by $\eta$ or $\{\delta,\rho\}$.
-To achieve the \gls{wit} point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized, the current expression \eqref{eq:z_irs_approx} is not needed and no \gls{sca} is involved.
+		To accommodate the low-complexity waveform schemes, minor modifications should be made for the passive beamforming design.
+		Specifically, the rate constraint \eqref{co:irs_rate} should be dropped, since the achievable rate is controlled by $\eta$ in \gls{ts} or $\{\delta,\rho\}$ in \gls{ps}.
+		To achieve the \gls{wit} point, the rate \eqref{eq:R_irs} should be maximized and the \gls{dc} expression \eqref{eq:z_irs_approx} can be dropped.
 The Modified-\gls{sca} (M-\gls{sca}) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in \gls{ps} mode.
-Similarly, no loss is introduced by \gls{sdr} and local optimality is guaranteed.
-The proofs are omitted here.
+		Similar to propositions \ref{pr:relaxation} and \ref{pr:sca}, no loss is introduced by \gls{sdr} and local optimality is guaranteed.
 Since each \gls{sdp} involves $(L+1)$ linear constraints, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-\gls{sca}}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-\gls{sca}}}$ denotes the number of M-\gls{sca} iterations \cite{Luo2010b}.
-Note that no \gls{sca} is involved at the \gls{wit} point where $I_{\mathrm{M-\gls{sca}}}=1$.
 
@@
 				\State Construct $\mathbf{V}$, $\mathbf{M}$, $\mathbf{M}_n$, $\mathbf{C}_{n}$, $\mathbf{C}_{\mathrm{I/P},k}$, $\forall n,k$
-				\State \textbf{Initialize} $i \gets 0$, $\mathbf{\Phi}^{(0)}$
+				\State \textbf{Initialize} $i \gets 0$, $\bar{\mathbf{\Theta}}^{(0)}$
 				\If{$\rho=0$}
-					\State Get $\mathbf{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+					\State Get $\bar{\mathbf{\Theta}}^{\star}$ by maximizing \eqref{eq:R_irs} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
 				\Else
@@
 						\State $i \gets i + 1$
-							\State Get $\mathbf{\Phi}^{(i)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
-							\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
-							\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
-					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
-					\State Set $\mathbf{\Phi}^{\star} \gets \mathbf{\Phi}^{(i)}$
+							\State Get $\bar{\mathbf{\Theta}}^{(r)}$ by maximizing \eqref{eq:z_irs_approx} s.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
+							\State Update $t_{\mathrm{I/P},k}^{(r)}$, $\forall k$ by \eqref{eq:t_k}
+							\State Compute $z^{(r)}$ by \eqref{eq:z_irs}
+					\Until $\lvert z^{(r)}-z^{(r-1)} \rvert \le \epsilon$
+					\State Set $\bar{\mathbf{\Theta}}^{\star} \gets \bar{\mathbf{\Theta}}^{(r)}$
 				\EndIf
-				\State Get $\hat{\mathbf{\phi}}^\star$ by eigen decomposition, $\mathbf{\Phi}^{\star}=\hat{\mathbf{\phi}}^\star(\hat{\mathbf{\phi}}^\star)^\mathsf{H}$
-				\State Set $\mathbf{\phi}^{\star} \gets e^{j \arg\left([\hat{\mathbf{\phi}}^\star]_{(1:L)} \middle/ [\hat{\mathbf{\phi}}^\star]_{(L+1)}\right)}$
-				\State \textbf{Output} $\mathbf{\phi}^{\star}$
+				\State Get $\hat{\boldsymbol{\theta}}^\star$ by eigen decomposition, $\bar{\mathbf{\Theta}}^{\star}=\hat{\boldsymbol{\theta}}^\star(\hat{\boldsymbol{\theta}}^\star)^\mathsf{H}$
+				\State Set $\boldsymbol{\theta}^{\star} \gets e^{\jmath  \arg\left([\hat{\boldsymbol{\theta}}^\star]_{(1:L)} \middle/ [\hat{\boldsymbol{\theta}}^\star]_{(L+1)}\right)}$
+				\State \textbf{Output} $\boldsymbol{\theta}^{\star}$
 			\end{algorithmic}
@@
 	\begin{subsection}{Block Coordinate Descent}
-		Based on the direct and cascaded \gls{csit}, we iteratively update the passive beamforming $\mathbf{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\mathbf{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\mathbf{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
+		Based on the direct and cascaded \gls{csit}, we iteratively update the passive beamforming $\boldsymbol{\theta}$ by Algorithm~\ref{al:sca}, the active precoder $\mathbf{p}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:precoder_mrt}, and the waveform amplitude $\mathbf{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence.
 The steps are summarized in the \gls{bcd} Algorithm~\ref{al:bcd}, whose computational complexity is exponential as inherited from Algorithm~\ref{al:gp}.
 It is guaranteed to converge, but may end up with a suboptimal solution because variables are coupled in constraint~\eqref{co:original_rate} \cite{Grippo2000}.
+		The \gls{r-e} region is obtained by varying the rate constraint from \num{0} to $C_{\max}$.
 
@@
 				\State \textbf{Input} $\beta_2$, $\beta_4$, $\mathbf{h}_{\mathrm{D},n}$, $\mathbf{V}_{n}$, $P$, $\sigma_n$, $\bar{R}$, $\epsilon$, $\forall n$
-				\State \textbf{Initialize} $i \gets 0$, $\mathbf{\phi}^{(0)}$, $\mathbf{b}_{\mathrm{I/P},n}^{(0)}$, $\mathbf{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\theta}^{(0)}$, $\mathbf{p}_{\mathrm{I/P},n}^{(0)}$, $\mathbf{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$, $\forall n$
 				\State Set $\mathbf{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
@@
 					\State $i \gets i + 1$
-					\State Get $\mathbf{\phi}^{(i)}$ based on $\mathbf{w}_{\mathrm{I/P}}^{(i-1)}$, $\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
-					\State Update $\mathbf{h}_n^{(i)}$, $\mathbf{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-					\State Get $\mathbf{s}_{\mathrm{I/P}}^{(i)}$, $\rho^{(i)}$ by Algorithm~\ref{al:gp}
-					\State Update $\mathbf{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-					\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
-				\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
-				\State Set $\mathbf{\phi}^{\star} \gets \mathbf{\phi}^{(i)}$, $\mathbf{w}_{\mathrm{I/P}}^{\star} \gets \mathbf{w}_{\mathrm{I/P}}^{(i)}$, $\rho^{\star} \gets \rho^{(i)}$
-				\State \textbf{Output} $\mathbf{\phi}^{\star}$, $\mathbf{w}_{\mathrm{I}}^{\star}$, $\mathbf{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
+					\State Get $\boldsymbol{\theta}^{(r)}$ based on $\mathbf{w}_{\mathrm{I/P}}^{(r-1)}$, $\rho^{(r-1)}$ by Algorithm~\ref{al:sca}
+					\State Update $\mathbf{h}_n^{(r)}$, $\mathbf{p}_n^{(r)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:precoder_mrt}
+					\State Get $\mathbf{s}_{\mathrm{I/P}}^{(r)}$, $\rho^{(r)}$ by Algorithm~\ref{al:gp}
+					\State Update $\mathbf{w}_{\mathrm{I/P},n}^{(r)}$, $\forall n$ by \eqref{eq:w}
+					\State Compute $z^{(r)}$ by \eqref{eq:z_waveform}
+				\Until $\lvert z^{(r)} - z^{(r-1)} \rvert \le \epsilon$
+				\State Set $\boldsymbol{\theta}^{\star} \gets \boldsymbol{\theta}^{(r)}$, $\mathbf{w}_{\mathrm{I/P}}^{\star} \gets \mathbf{w}_{\mathrm{I/P}}^{(r)}$, $\rho^{\star} \gets \rho^{(r)}$
+				\State \textbf{Output} $\boldsymbol{\theta}^{\star}$, $\mathbf{w}_{\mathrm{I}}^{\star}$, $\mathbf{w}_{\mathrm{P}}^{\star}$, $\rho^{\star}$
 			\end{algorithmic}
@@
 
-		For the low-complexity design under \gls{ps} mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\mathbf{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
-To achieve the \gls{wit} point ($\rho=0$), the rate \eqref{eq:R_irs} should be maximized to obtain the maximum capacity $C_{\max}$.\footnote{Recall in Remark~\ref{re:subband_tradeoff} that different subchannel designs lead to different capacities.} Note that the \gls{bcd} algorithm obtains the \gls{r-e} region by varying the rate constraint from \num{0} to $C_{\max}$, while the achievable \gls{r-e} region of the \gls{lc}-\gls{bcd} algorithm can be obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
+		For the \gls{lc} design under \gls{ps} mode, we obtain the phase shift by Algorithm~\ref{al:m_sca}, the active precoder $\mathbf{p}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:precoder_mrt}, and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}.
+		The \gls{r-e} region is obtained by performing a two-dimensional search over $(\delta, \rho)$ from $(0, 0)$ to $(1, 1)$.
 The steps are summarized in Algorithm~\ref{al:lc_bcd}.
@@
 				\State \textbf{Input} $\beta_2$, $\beta_4$, $\mathbf{h}_{\mathrm{D},n}$, $\mathbf{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
-				\State \textbf{Initialize} $i \gets 0$, $\mathbf{\phi}^{(0)}$, $\mathbf{b}_{\mathrm{I/P},n}^{(0)}$, $\mathbf{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
+				\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\theta}^{(0)}$, $\mathbf{p}_{\mathrm{I/P},n}^{(0)}$, $\mathbf{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
 				\State Set $\mathbf{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
@@
 					\State $i \gets i + 1$
-					\State Get $\mathbf{\phi}^{(i)}$ based on $\mathbf{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
-					\State Update $\mathbf{h}_n^{(i)}$, $\mathbf{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
-					\State Update $\mathbf{s}_{\mathrm{I}}^{(i)}$, $\mathbf{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
-					\State Update $\mathbf{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
-					\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
+					\State Get $\boldsymbol{\theta}^{(r)}$ based on $\mathbf{w}_{\mathrm{I/P}}^{(r-1)}$ by Algorithm~\ref{al:m_sca}
+					\State Update $\mathbf{h}_n^{(r)}$, $\mathbf{p}_n^{(r)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:precoder_mrt}
+					\State Update $\mathbf{s}_{\mathrm{I}}^{(r)}$, $\mathbf{s}_{\mathrm{P}}^{(r)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
+					\State Update $\mathbf{w}_{\mathrm{I/P},n}^{(r)}$, $\forall n$ by \eqref{eq:w}
+					\State Compute $R^{(r)}$, $z^{(r)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
 					\If{$\rho=0$}
-						\State $\Delta \gets R^{(i)} - R^{(i-1)}$
+						\State $\Delta \gets R^{(r)} - R^{(r-1)}$
 					\Else
-						\State $\Delta \gets z^{(i)} - z^{(i-1)}$
+						\State $\Delta \gets z^{(r)} - z^{(r-1)}$
 					\EndIf
 				\Until $\lvert \Delta \rvert \le \epsilon$
-				\State Set $\mathbf{\phi}^{\star} \gets \mathbf{\phi}^{(i)}$, $\mathbf{w}_{\mathrm{I/P}}^{\star} \gets \mathbf{w}_{\mathrm{I/P}}^{(i)}$
-				\State \textbf{Output} $\mathbf{\phi}^{\star}$, $\mathbf{w}_{\mathrm{I}}^{\star}$, $\mathbf{w}_{\mathrm{P}}^{\star}$
+				\State Set $\boldsymbol{\theta}^{\star} \gets \boldsymbol{\theta}^{(r)}$, $\mathbf{w}_{\mathrm{I/P}}^{\star} \gets \mathbf{w}_{\mathrm{I/P}}^{(r)}$
+				\State \textbf{Output} $\boldsymbol{\theta}^{\star}$, $\mathbf{w}_{\mathrm{I}}^{\star}$, $\mathbf{w}_{\mathrm{P}}^{\star}$
 			\end{algorithmic}
@@
 
-\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
-	\begin{figure}[!t]
+\begin{section}{Performance Evaluations}\label{sc:performance_evaluation}
+	\begin{figure}[H]
 		\centering
 		\def\svgwidth{0.9\columnwidth}
-		% \import{assets/}{layout.eps_tex}
 		\input{assets/chapter_3/layout.eps_tex}
 		\caption{System layout in simulation.}
-		\label{fi:layout}
+		\label{fg:layout}
 	\end{figure}
 
-	To evaluate the proposed \gls{ris}-aided \gls{swipt} system, we consider the layout in Fig.~\ref{fi:layout} where the \gls{ris} moves along a line parallel to the \gls{ap}-\gls{ue} path.
-Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the \gls{ap} to the \gls{ris}, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{B}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflected links.
-$d_{\mathrm{D}}=\qty{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$ are chosen as reference.
-The path loss of direct, incident and reflected links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{I}}$ and $\Lambda_{\mathrm{B}}$, respectively.
+	To evaluate the proposed \gls{ris}-aided \gls{swipt} system, we consider the layout in Fig.~\ref{fg:layout} where the \gls{ris} moves along a line parallel to the \gls{ap}-\gls{ue} path.
+Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the \gls{ap} to the \gls{ris}, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{F}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{B}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, forward and backward links.
+Set $d_{\mathrm{D}}=\qty{12}{\meter}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$ as reference.
+The path loss of direct, forward and backward links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{F}}$ and $\Lambda_{\mathrm{B}}$, respectively.
 We consider a large open space Wi-Fi-like environment at center frequency \qty{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
-Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \qty{10}{\meter}, and \num{3.5} onwards to further penalize the channels with large distance.
+Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \qty{10}{\meter}, and \num{3.5} onwards to penalize the potential blockage.
 All fadings are modeled as \gls{nlos} with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
@@
 We also choose the average \gls{eirp} as $P=\qty{40}{dBm}$, the receive antenna gain as \qty{3}{dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
-To further reduce the complexity, we assume $\delta=\rho$ for simplicity and perform a one-dimensional search from \num{0} to \num{1} to obtain a inner \gls{r-e} bound for the \gls{lc}-\gls{bcd} algorithm.
+To further reduce the complexity, we assume $\delta=\rho$ and perform a one-dimensional search for the \gls{lc}-\gls{bcd} algorithm.
 Each \gls{r-e} point is averaged over \num{200} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.
 
-	\begin{figure}[!t]
+	\begin{subsection}{Subchannel Manipulation}
+		\begin{figure}[H]
 			\centering
@@
 			\caption{Sorted equivalent subchannel amplitude with and without \gls{ris} versus $N$ for $M=1$, $L=100$, $\sigma_n^2=\qty{-40}{dBm}$, $B=\qty{10}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\qty{2}{\meter}$.}
-		\label{fi:channel_amplitude}
+			\label{fg:channel_amplitude}
 		\end{figure}
 
-	Fig.~\ref{fi:channel_amplitude} reveals how \gls{ris} influences the sorted equivalent subchannel amplitude for one channel realization.
+		Fig.~\ref{fg:channel_amplitude} reveals how \gls{ris} influences the sorted equivalent subchannel amplitude for one channel realization.
 Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for \gls{wit} and \gls{wpt} are dissimilar.
@@
 On the other hand, the \gls{wit}-optimized \gls{ris} provides a fair gain over all subchannels when $L$ is sufficiently large.
-This is reminiscent of the \gls{wf} scheme at high \gls{snr}, but is realized by channel alignment instead of resource allocation.
-Nevertheless, the amplitude of modulated and multisine waveforms remains approximately unchanged when adding a \gls{ris} (the plots are not attached).
-In other words, \gls{ris} has a subtle impact on the waveform design.
+This is reminiscent of the \gls{wf} scheme at high \gls{snr}, but is realized by channel alignment by \gls{ris} instead of resource allocation by transmitter.
+	\end{subsection}
 
-	\begin{figure}[!t]
+	\begin{subsection}{\glsfmtshort{r-e} Region Characterization}
+		\begin{subsubsection}{Number of Subbands}
+			\begin{figure}[H]
 				\centering
-		\subfloat[\gls{r-e} region\label{fi:re_subband}]{
+				\subfloat[\gls{r-e} region\label{fg:re_subband}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-		\subfloat[\gls{wpt} waveform amplitude\label{fi:waveform_subband}]{
+				\subfloat[\gls{wpt} waveform amplitude\label{fg:waveform_subband}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 
-	Fig.~\subref*{fi:re_subband} illustrates the average \gls{r-e} region versus the number of subband $N$.
+			Fig.~\subref*{fg:re_subband} illustrates the average \gls{r-e} region versus the number of subband $N$.
 First, it is observed that increasing $N$ reduces the per-subband rate but boosts the harvested energy.
 This is because less power is allocated to each subband but more balanced \gls{dc} terms are introduced by frequency coupling to boost the harvested energy.
-On the other hand, Fig.~\subref*{fi:waveform_subband} presents the sorted modulated/multisine amplitude $\mathbf{s}_{\mathrm{I/P}}$ for \gls{wpt}.
+On the other hand, Fig.~\subref*{fg:waveform_subband} presents the sorted modulated/multisine amplitude $\mathbf{s}_{\mathrm{I/P}}$ for \gls{wpt}.
 It demonstrates that a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$.
@@
 Second, the \gls{r-e} region is convex for $N \in \{2,4\}$ and concave-convex for $N \in \{8,16\}$, such that \gls{ps} outperforms \gls{ts} for a small $N$ and is outperformed for a large $N$.
-When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the \gls{wpt} point and the saddle \gls{ps} \gls{swipt} point (as denoted by the red curve in Fig.~\subref*{fi:re_subband}).
+When $N$ is in between, the optimal strategy is a combination of both, i.e., a time sharing between the \gls{wpt} point and the saddle \gls{ps} \gls{swipt} point (as denoted by the red curve in Fig.~\subref*{fg:re_subband}).
 When $N$ is relatively small, only modulated waveform is used at both \gls{wit} and \gls{wpt} points, and one can infer that no multisine waveform is needed for the entire \gls{r-e} region.
@@
 Therefore, we conclude that the rectifier nonlinearity enlarges the \gls{r-e} region by favoring a different waveform and receiving mode, both heavily depending on $N$.
+		\end{subsubsection}
 
-	\begin{figure}[!t]
+		\begin{subsubsection}{Average Noise Power}
+			\begin{figure}[H]
 				\centering
-		\subfloat[\gls{r-e} region\label{fi:re_noise}]{
+				\subfloat[\gls{r-e} region\label{fg:re_noise}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-		\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
+				\subfloat[Splitting ratio\label{fg:splitting_ratio_noise}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 
-	The average noise power influences the \gls{r-e} region as shown in Fig.~\subref*{fi:re_noise}.
+			The average noise power influences the \gls{r-e} region as shown in Fig.~\subref*{fg:re_noise}.
 First, we note that the \gls{r-e} region is roughly concave/convex at low/high \gls{snr} such that \gls{ts}/\gls{ps} are preferred correspondingly.
@@
 Besides, the \gls{lc}-\gls{bcd} algorithm achieves a good balance between performance and complexity even if one-dimensional search is considered for $\delta=\rho$ from \num{0} to \num{1}.
+		\end{subsubsection}
 
-	\begin{figure}[!t]
+		\begin{subsubsection}{\glsfmtshort{ris} Development}
+			\begin{figure}[H]
 				\centering
-		\subfloat[\gls{r-e} region\label{fi:re_distance}]{
+				\subfloat[\gls{r-e} region\label{fg:re_distance}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-		\subfloat[Path loss product\label{fi:path_loss}]{
+				\subfloat[Path loss product\label{fg:path_loss}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 
-	In Fig.~\subref*{fi:re_distance}, we compare the average \gls{r-e} region achieved by different \gls{ap}-\gls{ris} horizontal distance $d_{\mathrm{H}}$.
-Different from the active Amplify-and-Forward (AF) relay that favors midpoint development \cite{Li2017}, the \gls{ris} should be placed close to either the \gls{ap} or the \gls{ue} based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
-Moreover, there exist two optimal \gls{ris} coordinates around $d_{\mathrm{H}}=0.6$ and \qty{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ and maximize the \gls{r-e} tradeoff.
+			In Fig.~\subref*{fg:re_distance}, we compare the average \gls{r-e} region achieved by different \gls{ap}-\gls{ris} horizontal distance $d_{\mathrm{H}}$.
+Different from the active \gls{af} relay that favors midpoint development \cite{Li2017}, the \gls{ris} should be placed close to either the \gls{ap} or the \gls{ue} based on the product path loss model that applies to finite-size element reflection \cite{Ozdogan2020,Tang2021}.
+Moreover, there exist two optimal \gls{ris} coordinates around $d_{\mathrm{H}}=0.6$ and \qty{11.4}{\meter} that minimize the path loss product $\Lambda_{\mathrm{F}}\Lambda_R$ and maximize the \gls{r-e} trade-off.
 It suggests that equipping the \gls{ap} with a \gls{ris} can potentially extend the operation range of \gls{swipt} systems.
+		\end{subsubsection}
 
-	\begin{figure}[!t]
+		\begin{subsubsection}{Number of Transmit Antennas and \glsfmtshort{ris} Elements}
+			\begin{figure}[H]
 				\centering
-		\subfloat[\gls{r-e} region\label{fi:re_tx}]{
+				\subfloat[\gls{r-e} region\label{fg:re_tx}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-		\subfloat[\gls{wit} \gls{snr} and \gls{wpt} \gls{dc}\label{fi:scaling_tx}]{
+				\subfloat[\gls{wit} \gls{snr} and \gls{wpt} \gls{dc}\label{fg:scaling_tx}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 
-	\begin{figure}[!t]
+			\begin{figure}[H]
 				\centering
-		\subfloat[\gls{r-e} region\label{fi:re_reflector}]{
+				\subfloat[\gls{r-e} region\label{fg:re_reflector}]{
 					\resizebox{0.425\columnwidth}{!}{
@@
 				}
-		\subfloat[\gls{wit} \gls{snr} and \gls{wpt} \gls{dc}\label{fi:scaling_reflector}]{
+				\subfloat[\gls{wit} \gls{snr} and \gls{wpt} \gls{dc}\label{fg:scaling_reflector}]{
 					\resizebox{0.475\columnwidth}{!}{
@@
 
-	The impacts of the number of transmit antennas $M$ and the \gls{ris} elements $L$ on the \gls{r-e} behavior are revealed in Figs.~\subref*{fi:re_tx} and \subref*{fi:re_reflector}.
+			The impacts of the number of transmit antennas $M$ and the \gls{ris} elements $L$ on the \gls{r-e} behavior are revealed in Figs.~\subref*{fg:re_tx} and \subref*{fg:re_reflector}.
 First, it is observed that adding either active or passive elements can improve the equivalent \gls{snr}, which produces a nearly concave \gls{r-e} region and favors the \gls{ps} receiver.
-Second, the conventional Linear Energy Harvester (LEH) model leads to a power-inefficient design.
-To investigate the performance loss, we truncate the \gls{dc} objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\mathbf{\Phi}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no \gls{sca} is required; (ii) in the waveform design problem, the \gls{wpt}-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fi:scaling_tx} and \subref*{fi:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dBA} gap compared to the nonlinear model-based \gls{smf} and \gls{gp} designs.
+Second, the conventional \gls{leh} model leads to a power-inefficient design.
+To investigate the performance loss, we truncate the \gls{dc} objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\bar{\mathbf{\Theta}}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no \gls{sca} is required; (ii) in the waveform design problem, the \gls{wpt}-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
+As shown in Figs.~\subref*{fg:scaling_tx} and \subref*{fg:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dBA} gap compared to the nonlinear model-based \gls{smf} and \gls{gp} designs.
 Third, doubling $M$ brings a \qty{3}{\dB} gain at the output \gls{snr} and a \qty{12}{dBA} increase at the harvested \gls{dc}, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
@@
 			\begin{equation}
-		z = \beta_2 \Lambda_{\mathrm{B}}^2 \Lambda_{\mathrm{I}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{B}}^4 \Lambda_{\mathrm{I}}^4 \lvert X \rvert^4 L^4 P^2,
+				z = \beta_2 \Lambda_{\mathrm{B}}^2 \Lambda_{\mathrm{F}}^2 \lvert X \rvert^2 L^2 P + \beta_4 \frac{2N^2 + 1}{2N} \Lambda_{\mathrm{B}}^4 \Lambda_{\mathrm{F}}^4 \lvert X \rvert^4 L^4 P^2,
 			\end{equation}
@@
 These observations demonstrate the \gls{r-e} benefit of passive beamforming and emphasize the importance of accounting for the harvester nonlinearity in the waveform and beamforming design.
+		\end{subsubsection}
 
-	\begin{figure}[!t]
+		\begin{subsubsection}{Bandwidth}
+			\begin{figure}[H]
 				\centering
-		\subfloat[$B=\qty{1}{\MHz}$\label{fi:re_irs_1mhz}]{
+				\subfloat[$B=\qty{1}{\MHz}$\label{fg:re_irs_1mhz}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-		\subfloat[$B=\qty{10}{\MHz}$\label{fi:re_irs_10mhz}]{
+				\subfloat[$B=\qty{10}{\MHz}$\label{fg:re_irs_10mhz}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 
-	Figs.~\subref*{fi:re_irs_1mhz} and \subref*{fi:re_irs_10mhz} explore the \gls{r-e} region with different \gls{ris} strategies for narrowband and broadband \gls{swipt}.
-The ideal Frequency-Selective (FS) \gls{ris} assumes the reflection coefficient of each element is independent and controllable at different frequencies.
+			Figs.~\subref*{fg:re_irs_1mhz} and \subref*{fg:re_irs_10mhz} explore the \gls{r-e} region with different \gls{ris} strategies for narrowband and broadband \gls{swipt}.
+The ideal \gls{fs} \gls{ris} assumes the reflection coefficient of each element is independent and controllable at different frequencies.
 The adaptive \gls{ris} adjusts the passive beamforming for different \gls{r-e} points by Algorithm~\ref{al:sca}.
@@
 Their \gls{r-e} boundaries coincide as the antenna mode reflection of the random \gls{ris} is canceled out after averaging.
-Second, when the bandwidth is small, the performance of ideal, adaptive, and \gls{wit}/\gls{wpt}-optimized \gls{ris} are similar; when the bandwidth is large, the adaptive \gls{ris} outperforms the \gls{wit}/\gls{wpt}-optimized \gls{ris} but is outperformed by the ideal FS \gls{ris}.
-In the former case, the subband responses are close to each other such that the tradeoff in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
-It suggests that for narrowband \gls{swipt}, the optimal passive beamforming for any \gls{r-e} point is optimal for the whole \gls{r-e} region, and the corresponding composite channel and active precoder are also optimal for the whole \gls{r-e} region.
+Second, when the bandwidth is small, the performance of ideal, adaptive, and \gls{wit}/\gls{wpt}-optimized \gls{ris} are similar; when the bandwidth is large, the adaptive \gls{ris} outperforms the \gls{wit}/\gls{wpt}-optimized \gls{ris} but is outperformed by the ideal \gls{fs} \gls{ris}.
+In the former case, the subband responses are close to each other such that the trade-off in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
+It suggests that for narrowband \gls{swipt}, the optimal passive beamforming for any \gls{r-e} point is optimal for the whole \gls{r-e} region, and the corresponding equivalent channel and active precoder are also optimal for the whole \gls{r-e} region.
 Hence, the achievable \gls{r-e} region is obtained by optimizing the waveform amplitude and splitting ratio.
-On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal \gls{ris} reflection coefficient varies at different \gls{r-e} tradeoffs points for broadband \gls{swipt}.
-As shown in Fig.~\ref{fi:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high \gls{snr}, or focused on a few strongest subbands to boost the output \gls{dc}, thanks to adaptive passive beamforming.
+On the other hand, since the channel frequency selectivity affects the performance of the information decoder and energy harvester differently, the optimal \gls{ris} reflection coefficient varies at different \gls{r-e} trade-offs points for broadband \gls{swipt}.
+As shown in Fig.~\ref{fg:channel_amplitude}, the subchannel amplification can be either spread evenly to improve the rate at high \gls{snr}, or focused on a few strongest subbands to boost the output \gls{dc}, thanks to adaptive passive beamforming.
+		\end{subsubsection}
 
-	\begin{figure}[!t]
+		\begin{subsubsection}{Imperfect \gls{csit}}
+			\begin{figure}[H]
 				\centering
-		\subfloat[Imperfect cascaded \gls{csit}\label{fi:re_csi}]{
+				\subfloat[Imperfect cascaded \gls{csit}\label{fg:re_csi}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 				}
-		\subfloat[Quantized \gls{ris}\label{fi:re_quantization}]{
+				\subfloat[Quantized \gls{ris}\label{fg:re_quantization}]{
 					\resizebox{0.45\columnwidth}{!}{
@@
 			where $\hat{\mathbf{V}}_{n}$ is the estimated cascaded \gls{csit} and $\tilde{\mathbf{V}}_{n}$ is the estimation error with entries following i.i.d.
-\gls{cscg} distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fi:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded \gls{csit} inaccuracy for broadband \gls{swipt} with different $L$.
-On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete \gls{ris} codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.\footnote{This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution \gls{ris}) \cite{Wu2020c}.} Figure~\subref*{fi:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable \gls{r-e} gain over the benchmark scheme without \gls{ris}, and the performance gap between $b=4$ and unquantized \gls{ris} is negligible.
+\gls{cscg} distribution $\mathcal{CN}(0, \epsilon_{n}^2)$.\footnote{Note that the subchannel responses are correlated but the estimations can be independent.} Figure~\subref*{fg:re_csi} shows that the proposed passive beamforming Algorithm~\ref{al:sca} is robust to cascaded \gls{csit} inaccuracy for broadband \gls{swipt} with different $L$.
+On the other hand, since the practical reflection coefficient depends on the available element impedances, we consider a discrete \gls{ris} codebook $\mathcal{C}_\phi = \{e^{\jmath 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and uniformly quantize the continuous reflection coefficients obtained by Algorithm~\ref{al:bcd} to reduce the circuit complexity and control overhead.
+This relax-then-quantize approach can bring notable performance loss compared with direct optimization over the discrete phase shift set, especially for a small $b$ (i.e., low-resolution \gls{ris}) \cite{Wu2020c}.
+Figure~\subref*{fg:re_quantization} suggests that even $b=1$ (i.e., two-state reflection) brings considerable \gls{r-e} gain over the benchmark scheme without \gls{ris}, and the performance gap between $b=4$ and continuous \gls{ris} is negligible.
 These observations demonstrate the advantage of the proposed joint waveform, active and passive beamforming design in practical \gls{ris}-aided \gls{swipt} systems.
+		\end{subsubsection}
+	\end{subsection}
 \end{section}
 
-\begin{section}{Conclusion and Future Works}\label{se:conclusion_and_future_works}
-	This chapter investigated the \gls{r-e} tradeoff of a single user employing practical receiving strategies in a \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.
+\begin{section}{Conclusion and Future Works}\label{sc:conclusion_and_future_works}
+	This chapter investigated the \gls{r-e} trade-off of a single user employing practical receiving strategies in a \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.
 Uniquely, we considered the joint waveform, active and passive beamforming design under rectifier nonlinearity to maximize the achievable \gls{r-e} region.

### 2024-03-26 content/chapter_4.tex
:construction: Update motivation
:pencil: Update chapter 3

@@
 
-\chapter{RIScatter: Unifying \glsfmtshort{bc} and \glsfmtshort{ris}}
+\chapter{RIScatter: Unifying \glsfmtshort{bc} and \glsfmtshort{ris}}\label{ch:riscatter}
 
@@
 		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
-		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
+		\emph{Third,} RIScatter enables a flexible primary-backscatter trade-off with adaptive input distribution design.
 		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
@@
 		\begin{subsubsection}{Number of Nodes}
-			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter tradeoff.
+			Fig.~\subref*{fg:region_tags} reveals how the number RIScatter nodes $K$ influences the primary-backscatter trade-off.
 			Interestingly, we observe that increasing $K$ has a larger benefit on the total backscatter rate than primary.
@@
 			Fig.~\subref*{fg:region_txs} illustrates the impact of transmit antennas $Q$ on the average performance.
-			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter tradeoff.
+			As $Q$ increases, more scattered paths become available and the channel diversity can be better exploited to improve the primary-backscatter trade-off.
 			It emphasizes the importance of multi-antenna RIScatter systems and demonstrate the effectiveness of the proposed \gls{pga} design.
@@
 			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.
-			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter tradeoff in active-passive coexisting networks.
+			% This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of primary-backscatter trade-off in active-passive coexisting networks.
 		\end{subsubsection}

### 2024-03-26 content/chapter_5.tex
:construction: Add motivation
:construction: Update motivation
:pencil: Add wave scattering models
:pencil: Update chapter 3

@@
 
-\chapter{\glsfmtshort{mimo} Channel Shaping using \glsfmtshort{ris}: From Diagonal to Beyond}
+\chapter{Channel Shaping and Interference Alignment using \glsfmtshort{ris}: From Diagonal to Beyond}\label{ch:channel_shaping}
 
@@
 	where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
-	That is, $\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{H}$ and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
+	That is, $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
 	Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
@@
 			Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R} \times N_\mathrm{T}$ passing through itself.
-			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a tradeoff between the direct-indirect and backward-forward alignments.
+			Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a trade-off between the direct-indirect and backward-forward alignments.
 			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}.
@@
 			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
-			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
+			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between aligning the two subspaces.
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
@@
 			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
-			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
+			This transformation not only provides a better trade-off in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
 			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
@@
 		In the low power regime (\num{-20} to \qty{-10}{dB}), the slope of the achievable rate is significantly larger with \gls{bd}-\gls{ris}, suggesting that multiple streams can be activated at a much lower \gls{snr}.
-		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better tradeoff between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
+		This is because \gls{bd}-\gls{ris} not only spreads the channel singular values to a wider range, but also provides a better trade-off between subchannels (c.f. Fig. \ref{fg:singular_pareto}).
 		Finally, Fig. \subref*{fg:rate_kfactor} shows that the gap between diagonal and \gls{bd}-\gls{ris} narrows as the Rician $K$-factor increases and becomes indistinguishable in \gls{los} environment.
@@
 	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
-	This translates to a wider dynamic range (with better tradeoff) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
+	This translates to a wider dynamic range (with better trade-off) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
 	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.

### 2024-03-27 assets/chapter_4/ris.tex
:pencil: Update chapter 4

\begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
	\node at (5,3.25) [semicircle,shape border rotate=180,minimum width=1.5cm] {};
	\node at (8,0.35) [dart,shape border rotate=270,minimum width=1cm] {};

	\node[draw=none] at (0,-1) {Transmitter};
	\node[draw=none] at (5,4.4375) {Reflect\\Element};
	\node[draw=none] at (8,-1) {Receiver};

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);

	\node[draw=none] at (4.625,1) {Modulated};
\end{tikzpicture}

### 2024-03-27 assets/chapter_4/riscatter.tex
:pencil: Update chapter 4

--- 2024-03-27 assets/chapter_4/ris.tex
@@
 \begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
-	\node at (0,0) [dart,shape border rotate=90,minimum width=1cm] {};
-	\node at (5,3.25) [semicircle,shape border rotate=180,minimum width=1.5cm] {};
-	\node at (8,0.35) [dart,shape border rotate=270,minimum width=1cm] {};
+	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
+	\node at (5,3) [circle,minimum size=1.25cm] {};
+	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};
 
-	\node[draw=none] at (0,-1) {Transmitter};
-	\node[draw=none] at (5,4.4375) {Reflect\\Element};
-	\node[draw=none] at (8,-1) {Receiver};
+	\node[draw=none] at (0,-1.25) {Primary\\Transmitter};
+	\node[draw=none] at (5,4.5) {RIScatter\\Node};
+	\node[draw=none] at (8,-1.25) {Co-located\\Receiver};
 
@@
 	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
+	\draw[green,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);
 
-	\node[draw=none] at (4.625,1) {Modulated};
+	\node[draw=none] at (3.5,0.75) {Modulated};
+	\node[draw=none] at (8,2.76) {Flexible};
 \end{tikzpicture}

### 2024-03-27 assets/chapter_5/ic_rate_user.tex
:pencil: Update chapter 4

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
%
\begin{tikzpicture}

\begin{axis}[%
width=9.509cm,
height=7.5cm,
at={(0cm,0cm)},
scale only axis,
xmin=2,
xmax=10,
xlabel style={font=\color{white!15!black}},
xlabel={User Pairs},
ymin=24.0366620568765,
ymax=62.9320178950178,
ylabel style={font=\color{white!15!black}},
ylabel={Weighted Sum-Rate [bit/s/Hz]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
2	24.0366620568765\\
4	34.2503871208668\\
6	41.622749643327\\
8	44.0380050877313\\
10	43.8795026226494\\
};
\addlegendentry{$N_\mathrm{S} = 0$}

\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
2	25.3990077780911\\
4	36.3182517013294\\
6	42.844297578367\\
8	46.9811600018883\\
10	47.4095039520004\\
};
\addlegendentry{$(N_\mathrm{S}, L) = (16, 1)$}

\addplot [color=mycolor1, dashed, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
2	26.1302675490509\\
4	37.2433314642391\\
6	43.8241685215847\\
8	48.7515778844427\\
10	50.0262345258606\\
};
\addlegendentry{$(N_\mathrm{S}, L) = (16, 4)$}

\addplot [color=mycolor1, dotted, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
2	26.5005433882963\\
4	37.8529809047498\\
6	44.5290585688344\\
8	50.1996330401944\\
10	51.8865599593385\\
};
\addlegendentry{$(N_\mathrm{S}, L) = (16, 16)$}

\addplot [color=mycolor2, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
2	29.0139251001163\\
4	39.8325157791058\\
6	47.087891457604\\
8	52.0445486861005\\
10	53.9856612942705\\
};
\addlegendentry{$(N_\mathrm{S}, L) = (64, 1)$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
2	31.3276950788263\\
4	42.7749665094192\\
6	50.0160405682383\\
8	56.5092293329805\\
10	59.5047215843355\\
};
\addlegendentry{$(N_\mathrm{S}, L) = (64, 4)$}

\addplot [color=mycolor2, dotted, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
2	32.6664816559571\\
4	44.5042904532228\\
6	51.6271886078106\\
8	58.8237458788222\\
10	62.9320178950178\\
};
\addlegendentry{$(N_\mathrm{S}, L) = (64, 64)$}

\end{axis}
\end{tikzpicture}%

### 2024-03-27 content/chapter_2.tex
:pencil: Update chapter 4

@@
 				\end{bmatrix}.
+				\label{eq:diagonal_scattering_matrix}
 			\end{equation}
@@
 	\begin{subsection}{Applications}
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
@@
 				}
-				\label{fg:mbc}
+				\label{fg:mbc_intro}
 			}
@@
 				}
-				\label{fg:bbc}
+				\label{fg:bbc_intro}
 			}
@@
 				}
-				\label{fg:ambc}
+				\label{fg:ambc_intro}
 			}
@@
 				}
-				\label{fg:sr}
+				\label{fg:sr_intro}
 			}
@@
 			\gls{mbc} is the most common architecture where the carrier emitter and reader are integrated into one device called interrogator.
-			As shown in \subref*{fg:backcom_monostatic} and \subref*{fg:mbc}, the interrogator transmits a \gls{cw} in the downlink and receives the reflected information-bearing signal in the uplink.
+			As shown in \subref*{fg:backcom_monostatic} and \subref*{fg:mbc_intro}, the interrogator transmits a \gls{cw} in the downlink and receives the reflected information-bearing signal in the uplink.
 			The node varies its load impedance over time to switch between two states.
@@
 		\begin{subsubsection}{\glsfmtfull{bbc}}
-			\gls{bbc} separates the carrier emitter and reader into two individual devices, as illustrated in \subref*{fg:backcom_bistatic} and \subref*{fg:bbc}.
+			\gls{bbc} separates the carrier emitter and reader into two individual devices, as illustrated in \subref*{fg:backcom_bistatic} and \subref*{fg:bbc_intro}.
 			This helps to combat self-interference and extend the operation range, but the system involves three devices and requires more complex coordination and synchronization.
@@
 			\gls{ambc} has been recognized as a revolutionary technology since its debut in 2013 \cite{Liu2013b}.
-			As shown in \subref*{fg:ambc}, it gets rid of dedicated \gls{rf} sources and relies on ambient signals (e.g., TV, FM, and Wi-Fi) for both energy harvesting and information transfer.
+			As shown in \subref*{fg:ambc_intro}, it gets rid of dedicated \gls{rf} sources and relies on ambient signals (e.g., TV, FM, and Wi-Fi) for both energy harvesting and information transfer.
 			Compared with \gls{mbc} and \gls{bbc}, its carrier waveform is no longer a \gls{cw} but a mixture of already modulated signals with different frequencies and amplitudes, which makes the detection more challenging.
@@
 			\gls{sr} is a relatively new concept proposed in 2019 that introduced itself as ``cooperative \gls{ambc}'' \cite{Guo2019b}.
-			As shown in \subref*{fg:sr}, it shares not only the transmitter, \gls{rf} source, but also the receiver with a primary transmission.
+			As shown in \subref*{fg:sr_intro}, it shares not only the transmitter, \gls{rf} source, but also the receiver with a primary transmission.
 			This is different from traditional \gls{ambc} where the legacy system can be unaware of the backscatter link and the node wants to minimize its footprint.

### 2024-03-27 content/chapter_3.tex
:pencil: Update chapter 4

@@
 
-		\emph{First,} we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \eqref{eq:dc_power_nonlinear} \cite{Clerckx2016a}.
+		First, we propose a novel \gls{ris}-aided \gls{swipt} architecture based on joint waveform, active and passive beamforming design under the diode nonlinear model \eqref{eq:dc_power_nonlinear} \cite{Clerckx2016a}.
 Although this tractable harvester model accurately reveals how the input power level and waveform shape influence the output \gls{dc} power, it also introduces design challenges such as frequency coupling (i.e., components of different frequencies compensate and produce \gls{dc}), waveform coupling (i.e., different waveforms jointly contribute to \gls{dc}), and high-order objective function.
@@
 
-		\emph{Second,} we characterize each \gls{r-e} boundary point by energy maximization under a rate constraint.
+		Second, we characterize each \gls{r-e} boundary point by energy maximization under a rate constraint.
 The problem is solved by a \gls{bcd} algorithm based on the \gls{csit}.
@@
 
-		\emph{Third,} we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the \gls{gp} algorithm.
+		Third, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the \gls{gp} algorithm.
 To facilitate practical \gls{swipt} implementation, the \gls{wf} strategy for modulated waveform and the \gls{smf} strategy for multisine waveform are combined in time and power domains, respectively.
@@
 
-		\emph{Fourth,} we provide numerical results to evaluate the proposed algorithms. It is concluded that:
+		Fourth, we provide numerical results to evaluate the proposed algorithms. It is concluded that:
 		\begin{itemize}
@@
 
-\begin{section}{System Model}\label{sc:system_model}
+\begin{section}{System Model}
 	\begin{figure}[H]
@@
 
-		\begin{subsubsection}{Imperfect \gls{csit}}
+		\begin{subsubsection}{Imperfect \glsfmtshort{csit}}
 			\begin{figure}[H]

### 2024-03-27 content/chapter_4.tex
:pencil: Update chapter 4

@@
 	\gls{bc} separates a transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
-	The receiver (reader) can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
+	The receiver can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig.~\subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
 	Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized to embrace the \gls{ioe}.
@@
 	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small.
+	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small, respectively.
 	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
 	Under those assumptions, the achievable rate region of cell-free \gls{sr} was characterized in \cite{Dai2023}.
-	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
+	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this chapter, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart such that both links are approximately interference-free \cite{Long2020a}.
 	However, this assumption severely limits the backscatter throughput.
 
-	\begin{figure}[!t]
+	\begin{figure}[H]
 		\centering
@@
 			Illustration of scattering applications.
-			The blue flow(s) constitutes the primary link while the magenta/green flow denotes the backscatter link.
+			The blue flows denote the primary link while the magenta/green flows denote the backscatter link.
 		}
@@
 
-	\begin{table*}[!t]
+	\begin{sidewaystable}
 		\caption{Comparison of Scattering Applications}
@@
 		\end{tabularx}
-	\end{table*}
+	\end{sidewaystable}
 
@@
 	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
-	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp.
-information elements) for passive beamforming (resp.
-backscatter modulation) \cite{Hu2021a}.
+	In particular,
+	\begin{itemize}
+		\item \emph{Symbol level precoding:} Maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020};
+		\item \emph{Overlay modulation:} Superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022};
+		\item \emph{Spatial modulation:} Switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021};
+		\item \emph{Index modulation:} Employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
+	\end{itemize}
 	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
@@
 	Most relevant literature considered either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
-	Those problems are addressed in this paper and the contributions are summarized below.
+	Those problems are addressed in this chapter and the contributions are summarized below.
 
-	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
+	First, we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
 	The concept is shown in Fig.~\subref*{fg:riscatter}, where one or more RIScatter nodes ride over an active transmission to simultaneously modulate their information and engineer the wireless channel.
@@
 	However, two major challenges for RIScatter are the receiver design and input distribution design.
-	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
+	This is the first work to unify \gls{bc} and \gls{ris} from the perspective of input distribution.
 
-	\emph{Second,} we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
+	Second, we address the first challenge and propose a low-complexity \gls{sic}-free receiver.
 	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
@@
 	The energy detector can also be tailored for arbitrary input distribution and spreading factor to increase backscatter throughput.
-	This is the first paper to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.
+	This is the first work to propose a \gls{sic}-free cooperative receiver for active-passive coexisting networks.
 
-	\emph{Third,} we address the second challenge in a single-user multi-node \gls{miso} scenario.
+	Third, we address the second challenge in a single-user multi-node \gls{miso} scenario.
 	We characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at RIScatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user under different \gls{qos}.
@@
 	Uniquely, our optimization problem takes into account the \gls{csi}, \gls{qos}, and backscatter constellation, and the resulting input distribution is applicable to other detection schemes.
-	This is also the first paper to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
+	This is also the first work to reveal the importance of backscatter input distribution and decision region designs in active-passive coexisting networks.
 
-	\emph{Fourth,} we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
+	Fourth, we provide numerical results to demonstrate the benefits of RIScatter and proposed algorithms.
 	The observations include:
-	1) adaptive reflection state distribution design can flexibly shift between backscatter modulation and passive beamforming;
-	2) when the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
-	3) when the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
-	4) co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
-	5) the proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced to $1/N$ and no re-precoding/cancellation;
-	6) it also supports scatter nodes with faster load-switching speed for potentially higher throughput;
-	7) \gls{pga} active beamformer effectively increases the primary (resp.
+	\begin{itemize}
+		\item Adaptive reflection state distribution design can flexibly shift between backscatter modulation and passive beamforming;
+		\item When the primary link is prioritized, input distribution becomes degenerate and RIScatter nodes coincide with discrete \gls{ris};
+		\item When the backscatter link is prioritized, adaptive RIScatter encoding achieves higher backscatter rate than conventional line-coded \gls{bc} with equiprobable inputs;
+		\item Co-located RIScatter nodes can further leverage total backscatter rate by joint encoding;
+		\item The proposed receiver maintains the passive beamforming benefit and provides comparable backscatter rate to \gls{sic}-based \gls{sr}, with re-encoding costs reduced by $N$ times ($N$ is the spreading factor) and no re-precoding/cancellation;
+		\item It also supports scatter nodes with faster load-switching speed for potentially higher throughput;
+		\item \gls{pga} active beamformer effectively increases the primary (resp.
 backscatter) rate by boosting the receive \gls{snr} (resp.
 widening the energy gap under different reflection states), and can smoothly transition in between under different \gls{qos};
-	8) distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
+		\item Distribution-aware backscatter detectors provide higher backscatter rate than the conventional \gls{ml} detector.
+	\end{itemize}
 \end{section}
@@
 	\begin{subsection}{Principles}
-		\label{sc:principles}
-		\gls{rf} wave scattering or reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
-		The former receives the impinging signals and reradiates some back to the space, while the latter reflects at the space-cell boundary and mainly applies a phase shift.
-		In the scattered signal, the structural mode component depends on the scatterer geometry and material.
-		Its impact is usually modelled as part of environment multipath \cite{Thomas2012,Liang2020}, or simply a baseband \gls{dc} offset when the impinging signal is a \gls{cw} \cite{Boyer2014}.
-		On the other hand, the antenna mode component depends on the impedance mismatch and is widely exploited in scattering applications.
-		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is \cite{VanHuynh2017,Liang2022}
-		\begin{equation}
-			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
-			\label{eq:reflection_coefficient}
-		\end{equation}
-		where $Z_m$ is the antenna load (resp. metamaterial cell) impedance at state $m$, and $Z$ is the antenna input (resp. medium characteristic) impedance.
-		Specifically,
+		Following the discussion on Section \ref{sc:principles}, we have the following conclusions:
 		\begin{itemize}
@@
 			\begin{equation}
-				\Gamma_m = \alpha_m \exp(j \theta_m),
+				\Gamma_m = \alpha_m \exp(\jmath \phi_m),
 				\label{eq:passive_beamforming}
 			\end{equation}
-			where $\theta_m$ is the phase shift at state $m$.\footnote{Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.\label{fn:scattering_ratio}}
+			where $\phi_m$ is the phase shift at state $m$. Most papers assume $\alpha_m = \alpha$, with $\alpha \ll 1$ for \gls{bc} and $\alpha=1$ for \gls{ris}.
 		\end{itemize}
@@
 		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
@@
 
-		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user.
-The node receiver can be implemented using simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
-		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
-		\begin{figure*}[!t]
+		\begin{figure}[H]
 			\centering
 			\subfloat[Block Diagram]{
-				\resizebox{0.32\linewidth}{!}{
+				\resizebox{0.7\linewidth}{!}{
 					\input{assets/chapter_4/block_diagram.tex}
@@
 			}
+			\\
 			\subfloat[Equivalent Circuit]{
-				\resizebox{0.37\linewidth}{!}{
+				\resizebox{0.7\linewidth}{!}{
 					\input{assets/chapter_4/equivalent_circuit.tex}
@@
 			}
+			\\
 			\subfloat[Scatter Model]{
-				\resizebox{0.28\linewidth}{!}{
+				\resizebox{0.7\linewidth}{!}{
 					\input{assets/chapter_4/scatter_model.tex}
@@
 			\label{fg:riscatter_node}
-		\end{figure*}
+		\end{figure}
+		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user.
+The node receiver can be implemented using simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
+		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
 		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
@@
 	\begin{subsection}{System Model}
-		\label{sc:system_model}
-		\begin{figure}[!t]
+		\label{sc:system_model_4}
+		\begin{figure}[H]
 			\centering
@@
 		Without loss of generality, we assume all nodes have $M$ available reflection states.
-		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
-		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
+		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel enhanced by RIScatter nodes.
+		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.
+		We assume the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference), and the signal going through two or more RIScatter nodes is too weak to be received by the user.
 		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
-		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
-		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.
-The impact of channel estimation error will be investigated in Section~\ref{sc:simulation_results}.}.
+		Denote the \gls{ap}-user direct channel as $\mathbf{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\mathbf{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\mathbf{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \mathbf{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
+		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and the user.
+		The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.
+The impact of channel estimation error will be investigated in Section~\ref{sc:simulation_results}.
 
@@
 			\begin{align}
-				\boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}})
-				 & \triangleq \boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
-				 & = \boldsymbol{h}_{\text{D}}^\mathsf{H} + \boldsymbol{x}^\mathsf{H} \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
+				\mathbf{h}^\mathsf{H}(x_{\mathcal{K}})
+				 & \triangleq \mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} x_k \label{eq:equivalent_channel_bc}                    \\
+				 & = \mathbf{h}_{\text{D}}^\mathsf{H} + \mathbf{x}^\mathsf{H} \mathrm{diag}(\mathbf{\alpha}) \mathbf{H}_{\text{C}}, \label{eq:equivalent_channel_ris}
 			\end{align}
 		\end{subequations}
-		where $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\boldsymbol{H}_{\text{C}} \triangleq [\boldsymbol{h}_{\text{C},1},\ldots,\boldsymbol{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
+		where $\mathbf{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^\mathsf{T} \in \mathbb{I}^{K}$, $\mathbf{x} \triangleq [x_1,\ldots,x_K]^\mathsf{H} \in \mathcal{X}^{K}$, and $\mathbf{H}_{\text{C}} \triangleq [\mathbf{h}_{\text{C},1},\ldots,\mathbf{h}_{\text{C},K}]^\mathsf{H} \in \mathbb{C}^{K \times Q}$.
 		Without loss of generality, we assume the spreading factor $N$ is a positive integer.
@@
 		\begin{equation}
-			y[n] = \boldsymbol{h}^\mathsf{H}(x_{\mathcal{K}}) \boldsymbol{w} s[n] + v[n],
+			y[n] = \mathbf{h}^\mathsf{H}(x_{\mathcal{K}}) \mathbf{w} s[n] + v[n],
 			\label{eq:receive_signal}
 		\end{equation}
-		where $\boldsymbol{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the maximum average transmit power, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
+		where $\mathbf{w} \in \mathbb{C}^{Q}$ is the active beamformer satisfying $\lVert \mathbf{w} \rVert^2 \le P$, $P$ is the maximum average transmit power, $s \sim \mathcal{CN}(0,1)$ is the primary symbol, and $v \sim \mathcal{CN}(0,\sigma_v^2)$ is the \gls{awgn} with variance $\sigma_v^2$.
 
@@
 		\begin{equation}
-			\sigma_{m_{\mathcal{K}}}^2 = \lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2 + \sigma_v^2,
+			\sigma_{m_{\mathcal{K}}}^2 = \lvert \mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \mathbf{w} \rvert^2 + \sigma_v^2,
 			\label{eq:receive_variance}
@@
 
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
@@
 
-		When the threshold vector $\boldsymbol{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
+		When the threshold vector $\mathbf{t} \triangleq [t_0,\ldots,t_L]^\mathsf{T} \in \mathbb{R}_+^{L+1}$ is given, we can formulate a \gls{dmmac} with transition probability from input $x_{m_{\mathcal{K}}}$ to output $\hat{x}_{m_{\mathcal{K}}'}$ as
 		\begin{equation}
@@
 		\begin{equation}
-			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr).
+			I_{\text{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \mathbf{w} \rvert^2}{\sigma_v^2}\Bigr).
 			\label{eq:primary_information_function}
@@
 	\begin{maxi!}
-		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
-		\addConstraint{\boldsymbol{1}^\mathsf{T} \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
-		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
-		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
+		{\scriptstyle{\{\mathbf{p}_k\}_{k \in \mathcal{K}},\mathbf{w},\mathbf{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
+		\addConstraint{\mathbf{1}^\mathsf{T} \mathbf{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
+		\addConstraint{\mathbf{p}_k}{\ge \mathbf{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
+		\addConstraint{\lVert \mathbf{w} \rVert^2}{\le P}{\label{co:transmit_power}}
 		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
-		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0},}{\label{co:nonnegative_threshold}}
+		\addConstraint{\mathbf{t}}{\ge \mathbf{0},}{\label{co:nonnegative_threshold}}
 	\end{maxi!}
-	where $\boldsymbol{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
+	where $\mathbf{p}_k = [p(x_{1_k}), \ldots, p(x_{M_k})]^\mathsf{T} \in \mathbb{I}^M$ is the input distribution of node $k$.
 	Problem \eqref{op:weighted_sum_rate} generalizes \gls{bc} by allowing \gls{csi}- and \gls{qos}-adaptive input distribution and decision region design.
 	On the other hand, it also relaxes the feasible domain of discrete \gls{ris} phase shift selection problems from the vertices of $M$-dimensional probability simplex to the simplex itself.
-	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$.
+	The original problem is highly non-convex and we propose a \gls{bcd} algorithm that iteratively updates $\{\mathbf{p}_k\}_{k \in \mathcal{K}}$, $\mathbf{w}$ and $\mathbf{t}$.
 
@@
 		\label{sc:input_distribution}
-		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
+		For any given $\mathbf{w}$ and $\mathbf{t}$, we can formulate a \gls{dmmac} by \eqref{eq:dmmac} and simplify \eqref{op:weighted_sum_rate} to
 		\begin{maxi!}
-			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
+			{\scriptstyle{\{\mathbf{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
 			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
@@
 		\begin{proposition}
-			For any strictly positive initializer $\{\boldsymbol{p}_k^{(0)}\}_{k \in \mathcal{K}}$, the \gls{kkt} input probability of node $k$ at state $m_k$ is given by the converging point of the sequence
+			For any strictly positive initializer $\{\mathbf{p}_k^{(0)}\}_{k \in \mathcal{K}}$, the \gls{kkt} input probability of node $k$ at state $m_k$ is given by the converging point of the sequence
 			\begin{equation}
@@
 
-		At iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
+		At iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\mathbf{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\mathbf{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
 		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.
@@
 			\begin{algorithmic}[1]
-				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
-				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
-				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
+				\Require $K$, $N$, $\mathbf{h}_{\text{D}}^\mathsf{H}$, $\mathbf{H}_{\text{C}}$, $\mathbf{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\mathbf{w}$, $\mathbf{t}$, $\epsilon$
+				\Ensure $\{\mathbf{p}_k^\star\}_{k \in \mathcal{K}}$
+				\State Set $\mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
 				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
@@
 				\State Initialize $r \gets 0$
-				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
+				\State \phantom{Initialize} $\mathbf{p}_k^{(0)} > \mathbf{0}$, $\forall k$
 				\State Get $p^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
@@
 					\State Update $r \gets r+1$
-					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
+					\State \phantom{Update} $\mathbf{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
 					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
@@
 	\begin{subsection}{Active Beamforming}
-		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{t}$, problem \eqref{op:weighted_sum_rate} reduces to
+		For any given $\{\mathbf{p}_k\}_{k \in \mathcal{K}}$ and $\mathbf{t}$, problem \eqref{op:weighted_sum_rate} reduces to
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:active_beamforming}}{\label{ob:active_beamforming}}
+			{\scriptstyle{\mathbf{w}}}{I(x_{\mathcal{K}})}{\label{op:active_beamforming}}{\label{ob:active_beamforming}}
 			\addConstraint{\eqref{co:transmit_power},}
@@
 		which is still non-convex due to the integration and entropy terms.
-		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\boldsymbol{w}$.
+		Note the \gls{dmmac} $q(x_l|x_{m_{\mathcal{K}}})$ depends on the variance of accumulated receive energy $\sigma_{m_{\mathcal{K}}}^2$, which is a function of $\mathbf{w}$.
 		Plugging \eqref{eq:energy_distribution} into \eqref{eq:dmmac}, we have
@@
 		Its series expansion is given by \cite[Theorem 3]{Jameson2016}
-		\begin{align}
-			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
-			 & = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} \nonumber \\
-			 & \quad - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
+		\begin{equation}
+			Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \exp \Bigl(-\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!} - \exp \Bigl(-\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \sum_{n=0}^{N-1} \frac{\bigl(\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)^n}{n!},
 			\label{eq:regularized_incomplete_gamma}
-		\end{align}
-		whose gradient with respect to $\boldsymbol{w}^*$ is
-		\begin{align}
-			\nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)
-			 & = \frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \nonumber \\
-			 & \quad \times \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
+		\end{equation}
+		whose gradient with respect to $\mathbf{w}^*$ is
+		\begin{equation}
+			\nabla_{\mathbf{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) = \frac{\mathbf{h}(x_{m_{\mathcal{K}}})\mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\mathbf{w}}{(\sigma_{m_{\mathcal{K}}}^2)^2} \Bigl(g_{m_{\mathcal{K}}}(t_l) - g_{m_{\mathcal{K}}}(t_{l-1})\Bigr),
 			\label{eq:regularized_incomplete_gamma_gradient}
-		\end{align}
+		\end{equation}
 		where
@@
 		\end{equation}
-		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, we rewrite $I(x_{\mathcal{K}})$ and $\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})$ as \eqref{eq:weighted_sum_mutual_information_explicit} and \eqref{eq:weighted_sum_mutual_information_gradient} at the end of page \pageref{eq:weighted_sum_mutual_information_explicit}, respectively.
-		\begin{figure*}[!b]
-			\hrule
+		On top of \eqref{eq:regularized_incomplete_gamma} and \eqref{eq:regularized_incomplete_gamma_gradient}, the mutual information \eqref{eq:weighted_sum_mutual_information} can be rewritten as
 		\begin{equation}
-				I(x_{\mathcal{K}})=\sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}\rvert^2}{\sigma_v^2}\Bigr)+(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} p(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+			\begin{split}
+				I(x_{\mathcal{K}})
+				& =\sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\log\Bigl(1+\frac{\lvert\mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\mathbf{w}\rvert^2}{\sigma_v^2}\Bigr)\\
+				& \quad +(1-\rho)\sum_l Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr) \log \frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'} p(x_{m_{\mathcal{K}}'}) Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
 				\label{eq:weighted_sum_mutual_information_explicit}
+			\end{split}
 		\end{equation}
-			\begin{align}
-				\nabla_{\boldsymbol{w}^*} I(x_{\mathcal{K}})
-				 & = \sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\boldsymbol{h}(x_{m_{\mathcal{K}}})\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\boldsymbol{w}}{\sigma_{m_{\mathcal{K}}}^2}+(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr)\nonumber                                                                                   \\
-				 & \qquad \times \nabla_{\boldsymbol{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)-\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})\nabla_{\boldsymbol{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
+		and its gradient with respect to $\mathbf{w}^*$ is
+		\begin{equation}
+			\begin{split}
+				\nabla_{\mathbf{w}^*} I(x_{\mathcal{K}})
+				& = \sum_{m_{\mathcal{K}}}p(x_{m_{\mathcal{K}}})\Biggl(\rho\frac{\mathbf{h}(x_{m_{\mathcal{K}}})\mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}})\mathbf{w}}{\sigma_{m_{\mathcal{K}}}^2}\\
+				& \quad +(1-\rho)\sum_l\biggl(\log\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}+1\biggr) \nabla_{\mathbf{w}^*} Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\\
+				& \quad -\frac{Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\Bigr)\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})\nabla_{\mathbf{w}^*}Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}{\sum_{m_{\mathcal{K}}'}p(x_{m_{\mathcal{K}}'})Q\Bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}'}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}'}^2}\Bigr)}\Biggr)
 				\label{eq:weighted_sum_mutual_information_gradient}
-			\end{align}
-		\end{figure*}
+			\end{split}
+		\end{equation}
 		Problem \eqref{op:active_beamforming} can thus be solved by the \gls{pga} method.
@@
 		\begin{equation}
-			\bar{\boldsymbol{w}}^{(r+1)} = \boldsymbol{w}^{(r)}+\gamma\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}}),
+			\bar{\mathbf{w}}^{(r+1)} = \mathbf{w}^{(r)}+\gamma\nabla_{\mathbf{w}^*} I^{(r)}(x_{\mathcal{K}}),
 			\label{eq:beamforming_gradient_ascent}
@@
 		where $\gamma$ is the step size (refinable by backtracking line search \cite[Section 9.2]{Boyd2004}).
-		Then, $\bar{\boldsymbol{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
+		Then, $\bar{\mathbf{w}}$ is projected onto the feasible domain \eqref{co:transmit_power} to retrieve the active beamformer
 		\begin{equation}
-			\boldsymbol{w} = \frac{\sqrt{P} \bar{\boldsymbol{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\boldsymbol{w}}\rVert\bigr)}.
+			\mathbf{w} = \frac{\sqrt{P} \bar{\mathbf{w}}}{\max\bigl(\sqrt{P},\lVert\bar{\mathbf{w}}\rVert\bigr)}.
 			\label{eq:beamforming_projection}
 		\end{equation}
-
 		The \gls{pga} active beamforming design is summarized in Algorithm \ref{al:active_beamforming}.
@@
 			\begin{algorithmic}[1]
-				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
-				\Ensure $\boldsymbol{w}^\star$
-				\State Set $\boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
+				\Require $Q$, $N$, $\mathbf{h}_{\text{D}}^\mathsf{H}$, $\mathbf{H}_{\text{C}}$, $\mathbf{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\mathbf{p}_k\}_{k \in \mathcal{K}}$, $\mathbf{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$
+				\Ensure $\mathbf{w}^\star$
+				\State Set $\mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
 				\State \phantom{Set} $p(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution}
 				\State Initialize $r \gets 0$
-				\State \phantom{Initialize} $\boldsymbol{w}^{(0)}$, $\lVert\boldsymbol{w}^{(0)}\rVert^2 \le P$
+				\State \phantom{Initialize} $\mathbf{w}^{(0)}$, $\lVert\mathbf{w}^{(0)}\rVert^2 \le P$
 				\State Get $(\sigma_{m_{\mathcal{K}}}^{(r)})^2$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance} \label{st:gradient_descent_begin}
@@
 				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_explicit} \label{st:gradient_descent_end}
-				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
-				\State \phantom{Get} $\nabla_{\boldsymbol{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
+				\State \phantom{Get} $\nabla_{\mathbf{w}^*} Q^{(r)}\bigl(N,\frac{t_{l-1}}{\sigma_{m_{\mathcal{K}}}^2},\frac{t_l}{\sigma_{m_{\mathcal{K}}}^2}\bigr)$, $\forall m_{\mathcal{K}},l$ by \eqref{eq:regularized_incomplete_gamma_gradient} \label{st:gradient_update_start}
+				\State \phantom{Get} $\nabla_{\mathbf{w}^*} I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:weighted_sum_mutual_information_gradient} \label{st:gradient_update_end}
 				\Repeat
@@
 					\State \phantom{Update} $\gamma^{(r)}\gets\gamma$
-					\State \phantom{Update} $\bar{\boldsymbol{w}}^{(r)}$ by \eqref{eq:beamforming_gradient_ascent} \label{st:backtracking_line_search_begin}
-					\State \phantom{Update} $\boldsymbol{w}^{(r)}$ by \eqref{eq:beamforming_projection}
+					\State \phantom{Update} $\bar{\mathbf{w}}^{(r)}$ by \eqref{eq:beamforming_gradient_ascent} \label{st:backtracking_line_search_begin}
+					\State \phantom{Update} $\mathbf{w}^{(r)}$ by \eqref{eq:beamforming_projection}
 					\State Redo step \ref{st:gradient_descent_begin}--\ref{st:gradient_descent_end} \label{st:backtracking_line_search_end}
-					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\boldsymbol{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
+					\While{$I^{(r)}(x_{\mathcal{K}})<I^{(r-1)}(x_{\mathcal{K}})+\alpha\gamma\lVert\nabla_{\mathbf{w}^*}I^{(r-1)}(x_{\mathcal{K}})\rVert^2$}
 						\State Set $\gamma^{(r)}\gets\beta\gamma^{(r)}$
@@
 					\State Redo step \ref{st:gradient_update_start}, \ref{st:gradient_update_end}
-				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$
+				\Until $\lVert\mathbf{w}^{(r)}-\mathbf{w}^{(r-1)}\rVert \le \epsilon$
 			\end{algorithmic}
@@
 	\begin{subsection}{Decision Threshold}
-		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
+		For any given $\{\mathbf{p}_k\}_{k \in \mathcal{K}}$ and $\mathbf{w}$, problem \eqref{op:weighted_sum_rate} reduces to
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
+			{\scriptstyle{\mathbf{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
 			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
 		\end{maxi!}
-		which is still non-convex since $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmmac}.
+		which is still non-convex since $\mathbf{t}$ appears on the limits of integration \eqref{eq:dmmac}.
 		Instead of solving it directly, we constrain the feasible domain from continuous space $\mathbb{R}_+^{L+1}$ to discrete candidates (i.e., fine-grained energy levels) $\mathcal{T}^{L+1}$.
 		As shown in Fig.~\ref{fg:discrete_outputs}, the decision regions are formulated by grouping adjacent energy bins.
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
@@
 		\begin{maxi!}
-			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
+			{\scriptstyle{\mathbf{t} \in \mathcal{T}^{L+1}}}{I_{\text{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
 			\addConstraint{\eqref{co:sequential_threshold},}
@@
 		whose global optimal solution has been obtained in recent works.
-		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$.
+		\cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T}){-}L)\bigr)$.
 		On the other hand, \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
@@
 	\begin{equation}
-		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
+		\mathbf{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\mathbf{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\mathbf{H}},
 	\end{equation}
-	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
+	where $d$ is the transmission distance, $L_0=-\qty{30}{dB}$ is the reference path loss at $d_0=\qty{1}{m}$, $\kappa$ is the Rician K-factor, $\bar{\mathbf{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\mathbf{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
 	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
@@
 	We set $b=9$ and $\varepsilon=\num{e-3}$.
-	All achievable rate regions are averaged over \num{e3} channel realizations.\footnote{The code is publicly available at \url{https://github.com/snowztail/riscatter/}.}
+	All achievable rate regions are averaged over \num{e3} channel realizations.
 
@@
 			To characterize the achievable rate region, we progressively obtain all boundary points by successively increasing $\rho$ and solving problem \eqref{op:weighted_sum_rate}.
-			For $\rho=0$ where the backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards the sum cascaded channel $\sum_{k} \boldsymbol{h}_{\text{C},k}^\mathsf{H}$, respectively.
+			For $\rho=0$ where the backscatter link is prioritized, we initialize Algorithm \ref{al:input_distribution} and \ref{al:active_beamforming} by uniform input distribution and \gls{mrt} towards the sum cascaded channel $\sum_{k} \mathbf{h}_{\text{C},k}^\mathsf{H}$, respectively.
 			At the following points, both algorithms are initialized by the solutions at the previous point.
@@
 			\label{sc:convergence}
-			\begin{figure}[!t]
+			\begin{figure}[H]
 				\centering
@@
 			\begin{equation}
-				y^{\text{\gls{bbc}}}[n] = \Bigl(\boldsymbol{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \boldsymbol{w} + v[n].
+				y^{\text{\gls{bbc}}}[n] = \Bigl(\mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} x_k\Bigr) \mathbf{w} + v[n].
 			\end{equation}
@@
 			\item \emph{\gls{ambc}:} The user decodes each link independently and semi-coherently while treating the other as interference.
-			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
+			The primary achievable rate is approximately\footnote{The scattered component is treated as interference with average power $\mathbb{E}\bigl\{\sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} x_k \mathbf{w}s[n]\bigr\} = \sum_{k} \lvert \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \mathbf{w} \rvert^2$ \cite{Long2020a}.\label{fn:ambc}}
 			\begin{equation}
-				I_{\text{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\boldsymbol{h}_{\text{D}}^\mathsf{H}\boldsymbol{w}\rvert^2}{\sum_{k}\lvert \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} \boldsymbol{w}\rvert^2+\sigma_v^2}\Bigr),
+				I_{\text{P}}^{\text{\gls{ambc}}}(s;y) \approx \log \Bigl(1 + \frac{\lvert\mathbf{h}_{\text{D}}^\mathsf{H}\mathbf{w}\rvert^2}{\sum_{k}\lvert \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \mathbf{w}\rvert^2+\sigma_v^2}\Bigr),
 			\end{equation}
@@
 			\item \emph{\gls{sr}:} For a sufficiently large $N$, the average primary rate under semi-coherent detection asymptotically approaches \eqref{eq:primary_mutual_information} with uniform input distribution \cite{Long2020a}.
-			When $s[n]$ is successfully decoded and the direct interference $\boldsymbol{h}_{\text{D}}^\mathsf{H} \boldsymbol{w} s[n]$ is perfectly cancelled, the intermediate signal is
+			When $s[n]$ is successfully decoded and the direct interference $\mathbf{h}_{\text{D}}^\mathsf{H} \mathbf{w} s[n]$ is perfectly cancelled, the intermediate signal is
 			\begin{equation}
-				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \boldsymbol{h}_{\text{C},k}^\mathsf{H} x_k \boldsymbol{w} s[n] + v[n].
+				\hat{y}^{\text{\gls{sr}}}[n] = \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} x_k \mathbf{w} s[n] + v[n].
 				\label{eq:intermediate_signal}
@@
 			\begin{equation}
-				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
+				I_{\text{P}}^{\text{\gls{ris}}}(s;y|x_{\mathcal{K}}) = I_{\text{P}}(s;y|x_{m_{\mathcal{K}}^{\star}}) = \log \Bigl(1 + \frac{\lvert \mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}^{\star}}) \mathbf{w} \rvert^2}{\sigma_v^2}\Bigr),
 			\end{equation}
@@
 		\end{itemize}
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
@@
 		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those strategies.
-		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
+		First, we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to the coherent decoding.
 		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
 		Since \gls{sr} requires a very large $N$ to guarantee the primary rate, the signal processing cost at the receiver can be prohibitive, and the backscatter \emph{throughput} can be severely constrained.
-		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
+		Second, the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node, and the benefit of \gls{sr} is not obvious.
 		This is because the cascaded channel is around \qty{25}{dB} weaker than the direct channel.
@@
 		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
-		\emph{Third,} RIScatter enables a flexible primary-backscatter trade-off with adaptive input distribution design.
+		Third, RIScatter enables a flexible primary-backscatter trade-off with adaptive input distribution design.
 		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by using the static reflection pattern that maximizes the primary \gls{snr} all the time.
@@
 	\begin{subsection}{Input Distribution under Different \glsfmtshort{qos}}
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
@@
 	\begin{subsection}{Rate Region by Different Schemes}
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
@@
 				\item \emph{\gls{pga}:} Solution by Algorithm \ref{al:active_beamforming};
-				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \boldsymbol{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
-				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\boldsymbol{h}_{\text{D}}^\mathsf{H}$.
+				\item \emph{E-\gls{mrt}:} \gls{mrt} towards the ergodic composite channel $\sum_{m_{\mathcal{K}}} p(x_{m_{\mathcal{K}}}) \mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}})$;
+				\item \emph{D-\gls{mrt}:} \gls{mrt} towards the direct channel $\mathbf{h}_{\text{D}}^\mathsf{H}$.
 			\end{itemize}
@@
 	\begin{subsection}{Rate Region under Different Configurations}
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
@@
 			}
-			\\
-			\subfloat[Average Noise Power\label{fg:region_noise}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_4/region_noise.tex}
-				}
-			}
-			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_4/region_csi.tex}
-				}
-			}
-			\\
-			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_4/region_snr_primary.tex}
-				}
-			}
-			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
-				\resizebox{0.48\columnwidth}{!}{
-					\input{assets/chapter_4/region_snr_backscatter.tex}
-				}
-			}
 			\caption{
@@
 			}
-			\label{fg:region_config}
+			\label{fg:region_config_1}
 		\end{figure}
+
 		In this study, we choose $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{dBm}$ and $r=\qty{2}{m}$ as a reference, unless otherwise specified.
@@
 
+		\begin{figure}[H]
+			\centering
+			\subfloat[Average Noise Power\label{fg:region_noise}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/chapter_4/region_noise.tex}
+				}
+			}
+			\subfloat[Imperfect \gls{csi}\label{fg:region_csi}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/chapter_4/region_csi.tex}
+				}
+			}
+			\\
+			\subfloat[Primary \gls{snr}\label{fg:region_snr_primary}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/chapter_4/region_snr_primary.tex}
+				}
+			}
+			\subfloat[Backscatter \gls{snr}\label{fg:region_snr_backscatter}]{
+				\resizebox{0.48\columnwidth}{!}{
+					\input{assets/chapter_4/region_snr_backscatter.tex}
+				}
+			}
+			\caption{
+				Average primary-total-backscatter rate regions for different system configurations.
+			}
+			\label{fg:region_config_2}
+		\end{figure}
+
 		\begin{subsubsection}{Average Noise Power}
@@
 
-		\begin{subsubsection}{Imperfect \gls{csi}}
+		\begin{subsubsection}{Imperfect \glsfmtshort{csi}}
 			Due to the lack of \gls{rf} chains at RIScatter nodes, fast and accurate acquisition of the cascaded \gls{csi} can be challenging, especially when the backscatter \gls{snr} is weak or the number of nodes is large.
@@
 			\begin{equation}
-				\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
+				\hat{\mathbf{h}}_{\text{C},k} = \mathbf{h}_{\text{C},k} + \tilde{\mathbf{h}}_{\text{C},k},
 			\end{equation}
-			$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d.
+			$\tilde{\mathbf{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d.
 CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
@@
 
-		\begin{subsubsection}{Primary \gls{snr}}
+		\begin{subsubsection}{Primary \glsfmtshort{snr}}
 			\label{sc:primary_snr}
@@
 
-		\begin{subsubsection}{Backscatter \gls{snr}}
+		\begin{subsubsection}{Backscatter \glsfmtshort{snr}}
 			The primary \gls{snr} is fixed to \qty{20}{dB} with $Q=1$ in this study.
@@
 	\label{sc:conclusion}
-	This paper introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
+	This chapter introduced RIScatter as a novel scatter protocol that bridges backscatter modulation and passive beamforming.
 	Starting from scattering principles, we showed how RIScatter nodes generalize information nodes of \gls{bc} and reflect elements of \gls{ris}, how they can be built over existing passive scatter devices, and how they simultaneously encode self information and assist legacy transmission.

### 2024-03-27 content/chapter_5.tex
:pencil: Update chapter 4

@@
 
-\chapter{Channel Shaping and Interference Alignment using \glsfmtshort{ris}: From Diagonal to Beyond}\label{ch:channel_shaping}
+\chapter{Channel Shaping using \glsfmtshort{ris}: From Diagonal Model to Beyond}\label{ch:channel_shaping}
 
@@
 
-	The answer indeed depends on the hardware architecture and scattering model.
-	In conventional (a.k.a. diagonal) \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
-	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which groups adjacent elements using passive components.
+	The answer depends heavily on the hardware architecture and scattering model.
+	In diagonal \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
+	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which physically connects adjacent elements using passive components.
 	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
-	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries to block diagonal with  unitary blocks.
+	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries \eqref{eq:diagonal_scattering_matrix} to block diagonal with unitary blocks \eqref{eq:bd_scattering_matrix}.
 	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
@@
 	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
-	Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself.
-	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of channel manipulation.
-	For example, diagonal \gls{ris} has been proved useful for improving channel power \cite{Ning2020}, degree of freedom \cite{Ozdogan2020a,Li2023h}, condition number \cite{Zheng2022,Huang2023}, and effective rank \cite{ElMossallamy2021,Meng2023} in \gls{mimo}.
-	In contrast, \gls{bd}-\gls{ris} can provide a higher channel power but existing results are limited to \gls{siso}\footnote{In terms of channel shaping, single-stream \gls{mimo} with given precoder and combiner \cite{Nerini2023} is equivalent to \gls{siso}.}.
-\cite{Nerini2023} and \gls{miso} \cite{Santamaria2023}.
-	While these studies offer promising glimpses into the channel shaping potential, a comprehensive understanding of the capabilities and limitations is desired, and a universal design framework is missing.
-	This paper aims to answer the channel shaping question through theoretical analysis and numerical optimization.
+	Channel shaping is different from passive beamforming discussed in Chapters \ref{ch:ris_aided_swipt} and \ref{ch:riscatter} because \gls{ris} is exploited as a stand-alone device to modify the inherent properties of the wireless channel.
+	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of wave manipulation.
+	Relevant design criteria can be roughly classified into two categories:
+	\begin{itemize}
+		\item \emph{Singular value centric:} Focus on the singular values of the equivalent channel matrix, which are closely related to the channel capacity and the diversity-multiplexing trade-off.
+Relevant designs are more complicated since they involve the entire channel matrix.
+		\item \emph{Power centric:} Focus on the second-order characteristics of the channel matrix, which are useful in \gls{miso} but less informative in \gls{mimo}.
+Relevant designs are more practical and straightforward.
+	\end{itemize}
+	The former has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023} in \gls{pc}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023} in \gls{ic}.
+	The latter has been studied in terms of channel power \cite{Wu2019,Nerini2023,Santamaria2023} in \gls{pc} and leakage interference \cite{Santamaria2023a} in \gls{ic}.
+	Although the results are insightful, the big picture is far from complete since there exists neither a systematic channel shaping study nor a universal \gls{ris} optimization framework.
+	To the best of our knowledge, the most general channel shaping scenario (\gls{bd}-\gls{ris}-aided \gls{mimo}) has not been studied, and the great potential of \gls{bd}-\gls{ris} has not been fully exploited or understood.
+	This chapter aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
 	The contributions are summarized below.
 
-	First, we quantify the capability of a \gls{bd}-\gls{ris} to reshape the \gls{mimo} point-to-point channel in terms of singular values.
+	First, we exploit the Riemannian geometry of the Stiefel manifold to design a novel geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization.
+	This method modified from \cite{Abrudan2008,Abrudan2009} not only features lower complexity and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also fits arbitrary group size and any smooth \gls{ris} optimization problem.
+	Specifically, block-wise rotational update is performed along the geodesics of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
+	This is the first work to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
+
+	Second, we quantify the capability of a \gls{bd}-\gls{ris} to redistribute the singular values of \gls{mimo}-\gls{pc}.
 	The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
-	% This generalizes most singular value metrics and provides a powerful design framework.
-	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-	We then discuss some analytical singular value bounds in rank-deficient and fully-connected scenarios, which help to demystify the gain from off-diagonal entries.
-	This is the first paper to answer the channel shaping question and highlight the \gls{bd}-\gls{ris} gain from a Pareto perspective.
-
-	Second, we propose a \gls{rcg} algorithm adapted from \cite{Abrudan2008,Abrudan2009} for smooth optimization problems of asymmetric \gls{bd}-\gls{ris} with arbitrary group size.
-	Specifically, block-wise update is performed along the geodesics\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
-	It features lower complexity and faster convergence than general manifold optimization \cite{Absil2009,Pan2022d}, and solves the Pareto singular value problem.
-	This is the first paper to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
-
-	Third, we tackle \gls{bd}-\gls{ris} \gls{mimo} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
-	The former updates active and passive beamformers by eigenmode transmission and \gls{rcg} algorithm, respectively.
+	This problem is solved by the proposed geodesic \gls{rcg} algorithm.
+	The resulting achievable singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	We also demystify the \gls{bd}-\gls{ris} gain from off-diagonal entries and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected (a.k.a. unitary) \gls{ris}.
+	This is the first work to comprehensively answer the channel shaping question and fully unveil the potential or \gls{bd}-\gls{ris}.
+
+	Third, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo}-\gls{pc} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
+	The former updates active and passive beamforming by eigenmode transmission and \gls{rcg} algorithm, respectively.
 	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
-	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal (single-connected) to unitary (fully-connected).
-	It suggests channel shaping offers a promising low-complexity solution for joint \gls{ris}-transceiver designs.
-
-	% Third, we propose a closed-form iterative algorithm for power centric channel shaping problems.
-	% The idea is to successively approximate the quadratic objective by a sequence of affines and solve the local problems by \gls{svd}.
-	% Case studies are conducted for channel power maximization in \gls{pc} and leakage interference minimization in \gls{ic}.
-
-	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
-	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
-	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
-	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
+	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal to unitary.
+	It suggests channel shaping decouples the \gls{ris}-transceiver design and offers a promising low-complexity solution.
+	This is the first work to discuss the implications of channel shaping in joint active-passive beamforming optimization.
+
+	Fourth, we extend the aforementioned approaches to \gls{mimo}-\gls{ic} where the \gls{bd}-\gls{ris} is used for leakage interference minimization and \gls{wsr} maximization.
+	In the former case, we update the receive combiner, transmit precoder, and scattering matrix iteratively in closed forms with optimality proof.
+	In the latter case, we alternatively updates the transmit precoder by bisection and the scattering matrix by \gls{rcg} algorithm.
+	We also compare the impact of \gls{ris} on \gls{pc} and \gls{ic}.
+	% provide a comprehensive comparison between the two approaches and discuss the implications of channel shaping in \gls{ic}.
+
+	% Fifth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
+	% In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
+	% The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
+	% It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.
 
@@
 
-	% \begin{figure}[!t]
+	% \begin{figure}[H]
 	% 	\centering
@@
 
-	% Fig.~\ref{fg:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo} \gls{pc} achievable rate.
+	% Fig.~\ref{fg:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo}-\gls{pc} achievable rate.
 	% To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
@@
 
+\begin{section}{\glsfmtshort{mimo}-\glsfmtshort{ic}}
+	\begin{subsection}{Leakage Interference Minimization}
+		\begin{mini!}
+			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}_{kj}^\mathrm{D} + \mathbf{H}_k^\mathrm{B} \mathbf{\Theta} \mathbf{H}_j^\mathrm{F}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+			\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad \mathbf{W}_k^\mathsf{H} \mathbf{W}_k=\mathbf{I}, \quad \forall k.}{}{}
+		\end{mini!}
+		The non-convex problem can be solved by \gls{bcd} method.
+		For a given $\mathbf{\Theta}$, it reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
+		At iteration $r$, the combiner at receiver $k$ is updated as
+		\begin{equation}
+			\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
+		\end{equation}
+		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H}$.
+		The precoder at transmitter $j$ is updated as
+		\begin{equation}
+			\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
+		\end{equation}
+		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds to interference covariance matrix $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} \mathbf{H}_{kj}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} \mathbf{H}_{kj}$ in the reciprocal network.
+		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_k\}$ are determined, we define $\bar{\mathbf{H}}_{kj}^\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}_{kj}^\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}_k^\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}_k^\mathrm{B}$, and $\bar{\mathbf{H}}_j^\mathrm{F} \triangleq \mathbf{H}_j^\mathrm{F} \mathbf{W}_j$.
+		The \gls{bd} \gls{ris} subproblem reduces to
+		\begin{mini!}
+			{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}_{kj}^\mathrm{D} + \bar{\mathbf{H}}_k^\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}_j^\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
+		\end{mini!}
+
+		\begin{proposition}
+			Start from any $\mathbf{\Theta}^{(0)}$, the sequence
+			\begin{equation}
+				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+			\end{equation}
+			converges to a stationary point of \eqref{op:ic_interference_ris}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are left and right singular matrix of
+			\begin{equation}
+				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}_{j,g}^\mathrm{F} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{D}_{kj,g}^{(r)}\bigr) {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H},
+			\end{equation}
+			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{k,g}^\mathrm{B}$ and
+			\begin{equation}
+				\mathbf{D}_{kj,g}^{(r)} = \mathbf{H}_{jk}^\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
+			\end{equation}
+		\end{proposition}
+		\begin{proof}
+			To be added.
+		\end{proof}
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/chapter_5/ic_interference_sx.tex}
+			}
+			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
+Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}.
+$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$, and reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB}.}
+			\label{sm:ic_interference_sx}
+		\end{figure}
+		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd} \gls{ris} helps to reduce the leakage interference.
+		In this case, a fully-connected $2^n$-element \gls{bd} \gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
+		Interestingly, the result suggests that \gls{bd} \gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
+	\end{subsection}
+
+	\begin{subsection}{Weighted Sum-Rate Maximization}
+		\begin{maxi!}
+			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{J_2 = \sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k \mathbf{H}_{kj}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kj} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
+			\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k. \quad \forall k}{}{}
+		\end{maxi!}
+		where $\rho_k$ is the weight of user $k$ and $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix
+		\begin{equation}
+			\mathbf{Q}_k = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H} + \eta \mathbf{I}.
+		\end{equation}
+		For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution based on mutual information-\gls{mmse} relationship is proposed in \cite{Negro2010}.
+		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
+		\begin{equation}
+			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H}\bigr)^{-1},
+		\end{equation}
+		the corresponding error matrix is
+		\begin{equation}
+			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{(r-1)} \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+		\end{equation}
+		the \gls{mse} weight is
+		\begin{equation}
+			\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)}}^{-1},
+		\end{equation}
+		the Lagrange multiplier is
+		% \begin{equation}
+		% 	\begin{split}
+		% 		\lambda_k^{(r)}
+		% 		& = \frac{\sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)}}^\mathsf{H}) - \sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)}}^\mathsf{H})}{P_k} \\
+		% 		& \quad + \frac{\mathrm{tr}(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H})}{P_k}
+		% 	\end{split}
+		% \end{equation}
+		\begin{equation}
+			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)}}^\mathsf{H} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)}}^\mathsf{H} \bigr)}{P_k},
+		\end{equation}
+		where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} \mathbf{H}_{kj} \mathbf{W}_j^{(r)}$.
+		The precoder at transmitter $k$ is
+		\begin{equation}
+			\mathbf{W}_k^{(r)} = \Bigl(\sum_j \mathbf{H}_{jk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}_{jk} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \mathbf{H}_{kk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
+		\end{equation}
+		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} w.r.t. \gls{ris} block $g$ is
+		\begin{equation}
+			\begin{split}
+				\frac{\partial J_2}{\partial \mathbf{\Theta}_g^*}
+				& = \sum_k \rho_k {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kk} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
+				& \quad \times \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H}\bigr).
+			\end{split}
+			\label{eq:ic_rate_gradient_ris}
+		\end{equation}
+		The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:ic_rate_gradient_ris}.
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/chapter_5/ic_rate_sx.tex}
+			}
+			\caption{Average weighted sum-rate versus \gls{snr}, \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
+$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
+			\label{sm:ic_rate_sx}
+		\end{figure}
+
+		\begin{figure}[!t]
+			\centering
+			\resizebox{0.65\columnwidth}{!}{
+				\input{assets/chapter_5/ic_rate_user.tex}
+			}
+			\caption{Average weighted sum-rate versus user pairs $K$, \gls{ris} elements $N^\mathrm{S}$ and group size $L$ at $\mathrm{SNR} = \qty{15}{dB}$.
+$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}) = (4, 4, 3)$, $\rho_k = 1, \ \forall k$.}
+			\label{sm:ic_rate_user}
+		\end{figure}
+
+		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd} \gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
+	\end{subsection}
+\end{section}
+
 \begin{section}{Simulation Results}\label{sc:simulation}
@@
 	\begin{table*}[!t]
+		\footnotesize
 		\caption{Average Performance of \gls{bd}-\gls{ris} Designs}
@@
 		\begin{subsubsection}{Pareto Frontier}
-			\begin{figure}[!t]
+			\begin{figure}[H]
 				\centering
 				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/singular_pareto_sx32_nd.tex}
@@
 				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/singular_pareto_sx32.tex}
@@
 				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/singular_pareto_sx64.tex}
@@
 				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/singular_pareto_sx128.tex}
@@
 		\begin{subsubsection}{Analytical Bounds and Numerical Results}
-			\begin{figure}[!t]
+			\begin{figure}[H]
 				\centering
 				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/singular_bound_rank1_sx32.tex}
@@
 				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/singular_bound_rank1_sx64.tex}
@@
 				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/singular_bound_rank2_sx128.tex}
@@
 				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/singular_bound_rank4_sx256.tex}
@@
 
-			\begin{figure}[!t]
+			\begin{figure}[H]
 				\centering
 				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/power_bond_txrx1_nd.tex}
@@
 				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
-					\resizebox{!}{3.25cm}{
+					\resizebox{0.45\columnwidth}{!}{
 						\input{assets/chapter_5/power_bond_txrx4_nd.tex}
@@
 	\begin{subsection}{Achievable Rate Maximization}
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
 			\subfloat[$16 \times N_\mathrm{S} \times 16$ (no direct)\label{fg:power_sx_txrx16_nd}]{
-				\resizebox{!}{3.25cm}{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/chapter_5/power_sx_txrx16_nd.tex}
@@
 			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
-				\resizebox{!}{3.25cm}{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/chapter_5/power_sx_txrx16.tex}
@@
 
-		\begin{figure}[!t]
+		\begin{figure}[H]
 			\centering
 			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
-				\resizebox{!}{3.25cm}{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/chapter_5/rate_beamforming.tex}
@@
 			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
-				\resizebox{!}{3.25cm}{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/chapter_5/rate_txrx.tex}
@@
 			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
-				\resizebox{!}{3.25cm}{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/chapter_5/rate_sx.tex}
@@
 			\subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
-				\resizebox{!}{3.25cm}{
+				\resizebox{0.45\columnwidth}{!}{
 					\input{assets/chapter_5/rate_kfactor.tex}
@@
 \begin{section}{Conclusion}
-	This paper analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
+	This chapter analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
 	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.

### 2024-03-29 content/chapter_2.tex
:pencil: Add conclusion

@@
 
-			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2023a}.
+			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2024}.
 			One element is in the same group with another if and only if there is at least one path (via edges) between them.
@@
 
-	\begin{subsection}{\glsfmtfull{r-e} Tradeoff}
+	\begin{subsection}{\glsfmtfull{r-e} Trade-off}
 		Despite \gls{wit} and \gls{wpt} share many similarities, their difference in design objectives, system architectures, and practical constraints make a joint implementation of \gls{swipt} particularly challenging.
@@
 			That is, periodically switching the reflection coefficient at rate $\Delta f$ results in a frequency shift $\pm \Delta f$ on the reflected signal.
-			Practical implementations have been demonstrated on a variety of license-free protocols (e.g., HitchHike \cite{Zhang2016a}, Inter-Technology \cite{Iyer2016}, Passive Wi-Fi \cite{Kellogg2017}, \gls{ble}-Backscatter \cite{Ensworth2017}) where the mirror copy can be suppressed.
+			Practical implementations have been demonstrated on a variety of license-free protocols (e.g., HitchHike \cite{Zhang2016a}, inter-technology \cite{Iyer2016}, Passive Wi-Fi \cite{Kellogg2017}, \gls{ble}-Backscatter \cite{Ensworth2017}) where the mirror copy can be suppressed.
 			\item \emph{\gls{css} \cite{Talla2017}:} A chirp is a signal whose frequency increases or decreases over time.

### 2024-03-29 content/chapter_4.tex
:pencil: Add conclusion

@@
 
-	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising.
+	To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2024} and learning-based approaches can be promising.
 	Another interesting question is how to design RIScatter nodes and receivers in a multi-user system to fully exploit the dynamic passive beamforming that naturally origins from backscatter modulation.

### 2024-03-29 content/chapter_5.tex
:pencil: Add conclusion

@@
 	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries \eqref{eq:diagonal_scattering_matrix} to block diagonal with unitary blocks \eqref{eq:bd_scattering_matrix}.
-	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2023a}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2023a,Li2023d,Bartoli2023,Li2023c}.
+	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2024}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2024,Li2023d,Bartoli2023,Li2023c}.
 	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
@@
 	The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2023a,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
+	To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2024,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
 	The overall scattering matrix of the \gls{bd}-\gls{ris} is
@@
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2023a}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
+2]{Nerini2024}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
 

### 2024-03-29 content/chapter_6.tex
:pencil: Add conclusion

%!TEX root = ../thesis.tex

\chapter{Conclusions and Future Works}\label{ch:conclusions}

\begin{section}{Conclusions}
	This thesis explored the versatile potential of \gls{ris} for augmenting future wireless networks from a physical-layer perspective.
	After introducing the necessary background, we focused on three most promising directions (passive beamforming, backscatter modulation, channel shaping) and investigated those in different application scenarios:
	\begin{itemize}
		\item In the domain of \gls{swipt}, we unveiled new trade-offs and design insights by introducing \gls{ris} into multi-antenna, multi-carrier systems. Considering harvester nonlinearity, we characterize the achievable \gls{r-e} region through a joint optimization of waveform, active and passive beamforming based on the \gls{csit}. This problem is solved by \gls{bcd}, where we obtain the active precoder in closed form, the passive beamforming by \gls{sca}, and the waveform amplitude by \gls{gp}. To facilitate practical implementation, we also propose two low-complexity designs based on closed-form adaptive waveform schemes. Simulation results highlight a second-order array gain and a fourth-order power scaling order with respect to \gls{ris} elements, while being robust to \gls{csi} inaccuracy and \gls{ris} resolution.
		\item The proposed RIScatter concept demonstrated the synergy between active and passive transmissions. RIScatter is a batteryless cognitive radio that recycles ambient signal in an adaptive and customizable manner, where dispersed or co-located scatter nodes partially modulate their information and partially engineer the wireless channel.
		The key is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and relative priority of coexisting links.
		This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either in special cases; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
		We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
		For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
		Simulation results demonstrate the received signal can be exploited for dual purposes and the nodes can shift smoothly between backscatter modulation and passive beamforming via input distribution control.
		\item Finally, we investigated the fundamental limits of \gls{ris} for reshaping \gls{mimo} \gls{pc} and \gls{ic}. We depart from the widely-adopted diagonal phase shift model to a general \gls{bd} architecture with superior subspace alignment and subchannel rearrangement capabilities.
		An efficient geodesic \gls{rcg} algorithm is tailored for smooth \gls{bd}-\gls{ris} optimization problems, which features lower complexity and faster convergence.
		For \gls{mimo}-\gls{pc}, we characterize the achievable channel singular value region through numerical and analytical approaches, then tackle the rate maximization problem by a local-optimal \gls{ao} approach and a low-complexity shaping-inspired approach.
		For \gls{mimo}-\gls{ic}, we extend the proposed algorithms to solve leakage interference minimization and \gls{wsr} maximization problems.
		Simulation results suggest channel shaping offers a promising path to decouple the joint \gls{ris}-transceiver design with minor performance degradation and much lower computational complexity.
	\end{itemize}
\end{section}

\begin{section}{Future Works}
	Many interesting problems are countered during the research but not fully addressed due to time constraints, to name a few:
	\begin{itemize}
		\item \emph{\gls{ris}-aided multi-user \gls{swipt}:} Extension to multi-user scenario is non-trivial because (i) the waveform and passive beamforming are shared among users while the active beamforming and power splitting ratios are user-specific; (ii) the interference can be harvested for power purpose such that dedicated information and power precoders are desired; (iii) due to harvester nonlinearity, the optimal design is highly non-convex and depends heavily on the multiple access scheme; (iv) a proper criterion is needed to cover the \gls{r-e} trade-off and fairness among users.
		\item \emph{Capacity region of RIScatter:} The current work considers a decoding order from backscatter to primary, corresponding to a primary-optimal point (but not a corner due to energy detector) in the capacity region.
		If the primary message can be decoded first, it can be modelled as a spreading sequence that enhances the backscatter \gls{snr} by $N$ times (where $N$ is the symbol period ratio) \cite{Long2020a}, corresponding to a backscatter-optimal point.
		Besides, the backscatter detection can be performed coherently in the signal domain to further improve the achievable rate.
		\item \emph{RIScatter, index modulation, and rate splitting:} In RIScatter, the primary and backscatter symbols are superimposed by multiplicative coding, and the nodes usually have a finite number of reflection states. Instead of acting as a pure channel controller or individual information source, a \gls{ris} can be integrated into the \gls{rf} transmitter as an additional index modulator to enhance the spectral efficiency \cite{Basar2020}.
		The transmitted message is thus split into an amplitude-phase modulated component and an index-modulated component, which can be decoded separately at the receiver \cite{Zhong2018}. This could further improve the capacity of \gls{ris}-aided \gls{mimo} systems \cite{Ye2022}, or make a low-complexity realization of \gls{rsma} \cite{Mao2018} in a multi-user system where the reflection pattern conveys the common message.
		\item \emph{RIScatter and sensing:} The proposed RIScatter concept can be extended to sensing applications, where the scatter nodes are equipped with sensors to monitor the environment and report the information to the \gls{ap}. The challenge is to design the input distribution and reflection states to stabilize the environment for improved sensing performance while guaranteeing the communication quality.
		\item \emph{\gls{bd}-\gls{ris} and frequency shifting:} Similar to \gls{ambc}, the different groups of \gls{bd}-\gls{ris} can be used to shift the incident wave to different frequencies.
		This phenomenon can be exploited to mitigate the self and inter-operator interference \cite{Miridakis2024}, generate a multi-frequency signal out of a \gls{cw}, or manipulate the response of frequency-selective channels. However, it could be challenging to design and implement the time-varying scattering matrices at a low power consumption.
		\item \emph{Multi-sector \gls{bd}-\gls{ris} and interference alignment:} The current work solves leakage interference minimization and \gls{wsr} maximization problems in \gls{ris}-aided \gls{ic}.
		It remains unknown how many scattering elements are required to completely eliminate the interference, and what is the \gls{dof} in a $(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ \gls{ic}.
		Besides, there exists a multi-sector model \cite{Li2023c} that provides full-space coverage and highly directional beams.
		It would be interesting to see how those sector-specific (instead of being shared by all users) scattering matrices can help to align the interference and improve the fairness issue.
	\end{itemize}
\end{section}

### 2024-03-30 content/chapter_3.tex
:triangular_flag_on_post: Initial submission 240330

@@
 
-		\begin{remark}\label{re:reflection_coefficient}
+		\begin{remark}\label{rm:reflection_coefficient}
 			Since the reactance $X_l$ is a function of frequency, the reflection coefficient $\theta_l$ cannot be designed independently at different subbands.
@@
 
-		\begin{remark}\label{re:subband_tradeoff}
+		\begin{remark}\label{rm:subband_tradeoff}
 			The cascaded channel $\mathbf{V}_{n}$ varies at different subbands and there exists a trade-off for passive beamforming design in the frequency domain.
@@
 Second, when the bandwidth is small, the performance of ideal, adaptive, and \gls{wit}/\gls{wpt}-optimized \gls{ris} are similar; when the bandwidth is large, the adaptive \gls{ris} outperforms the \gls{wit}/\gls{wpt}-optimized \gls{ris} but is outperformed by the ideal \gls{fs} \gls{ris}.
-In the former case, the subband responses are close to each other such that the trade-off in Remark~\ref{re:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
+In the former case, the subband responses are close to each other such that the trade-off in Remark~\ref{rm:subband_tradeoff} becomes insignificant, and the auxiliary link can be roughly maximized at all subbands.
 It suggests that for narrowband \gls{swipt}, the optimal passive beamforming for any \gls{r-e} point is optimal for the whole \gls{r-e} region, and the corresponding equivalent channel and active precoder are also optimal for the whole \gls{r-e} region.

### 2024-03-30 content/chapter_4.tex
:triangular_flag_on_post: Initial submission 240330

@@
 			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
-			\label{re:dynamic_passive_beamforming}
+			\label{rm:dynamic_passive_beamforming}
 		\end{remark}
@@
 			When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly.
-			\label{re:independent_encoding}
+			\label{rm:independent_encoding}
 		\end{remark}
@@
 			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
-			\label{re:non_gaussian}
+			\label{rm:non_gaussian}
 		\end{remark}
@@
 			However, simulation results in Section~\ref{sc:simulation_results} will show that the average performance gap is indistinguishable at a moderate $K$.
-			\label{re:input_kkt_distribution}
+			\label{rm:input_kkt_distribution}
 		\end{remark}
@@
 			This implies that any thresholding maximizing the total backscatter rate is optimal for problem \eqref{op:decision_threshold}.
-			\label{re:backscatter_decision}
+			\label{rm:backscatter_decision}
 		\end{remark}
@@
 			In terms of total backscatter rate, the nodes can be viewed as an augmented source, and problem \eqref{op:decision_threshold} becomes the rate-optimal quantizer design for \gls{dmtc}.
-			\label{re:augmented_source}
+			\label{rm:augmented_source}
 		\end{remark}
 
-		Thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
+		Thanks to Remark \ref{rm:backscatter_decision} and \ref{rm:augmented_source}, problem \eqref{op:decision_threshold} can be recast as
 		\begin{maxi!}
@@
 			Besides, the average rate performance of Exhaustion and \gls{kkt} completely coincide with each other when $K=2$.
-			This confirms Remark \ref{re:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
+			This confirms Remark \ref{rm:input_kkt_distribution} that the \gls{kkt} input distribution can be good enough when $K$ is moderate.
 			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}, and those gaps should be larger when $M$ or $K$ increases.

### 2024-03-30 content/chapter_5.tex
:triangular_flag_on_post: Initial submission 240330

@@
 
-\begin{section}{\glsfmtlong{bd}-\glsfmtlong{ris} Model}
-	Consider a \gls{bd}-\gls{ris} aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
+\begin{section}{\glsfmtshort{mimo}-\glsfmtshort{pc}}
+	\begin{subsection}{System Model}
+		Consider a \gls{bd}-\gls{ris}-aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
 		This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
@@
 			\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{R}_g^\mathsf{H},
+			\label{eq:unitary_decomposition}
 		\end{equation}
@@
 
-	\begin{remark}
+		\begin{remark}\label{rm:channel_shaping}
 			By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} creates two critical opportunities:
 			\begin{itemize}
-			\item \textbf{Subspace alignment:} each group can align the singular matrices of the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) channels.
+				\item \textbf{Subspace alignment:} Each group can align the singular matrices of the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) channels.
 In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ is
@@
 				Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a trade-off between the direct-indirect and backward-forward alignments.
-			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}.
-but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
-			% It suggests that diagonal \gls{ris} applying a phase shift to each indirect channel is sufficient for phase matching in \gls{siso}, but its disadvantage in subspace alignment scales with \gls{mimo} dimensions.
-			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching. However,
-			% It is obvious that diagonal \gls{ris} is sufficient for perfect phase matching.
-However, in \gls{mimo} each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
-			% Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
-			% It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
-			% is sufficient for perfect alignment
-			% and is sufficient for perfect subspace alignment.
-			% In \gls{mimo}, perfect subspace alignment is generally impossible due to the lack of direct control over the indirect channels.aa
-			% backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) alignments of the singular matrices.
-			\item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
+				\item \textbf{Subchannel rearrangement:} This unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
 In \gls{siso}, diagonal \gls{ris} provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
@@
 				The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{R} \times N_\mathrm{T}$.
-			% effect is more pronounced in \gls{mimo} since the number of subchannels associated with each group grows quadratically with the dimensions.
-			% The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
-since the number of subchannels associated with each group grows quadratically with the dimensions.
-			% It suggests that the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions.
-			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the maximum indirect channel amplitude by diagonal \gls{ris} is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are independent permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
-			% \begin{equation}
-			% 	\item \
-			% \end{equation}
-			% and $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality,
-			% \item \textbf{Subchannel rearrangement:} this unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the optimal indirect channel amplitude is $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ by diagonal \gls{ris} and $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},\pi_\mathrm{B}(n)} \rvert \lvert h_{\mathrm{F},\pi_\mathrm{F}(n)} \rvert$ by \gls{bd}-\gls{ris}, where $\pi(\cdot)$ is a permutation of $\{1, \ldots, N_\mathrm{S}\}$.
-			% this is unique to \gls{bd}-\gls{ris} --- each group can rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, the optimal indirect channel amplitude is relaxed from $\sum_n \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ to $\sum_n \lvert h_{\mathrm{B},\pi(n)} \rvert \lvert h_{\mathrm{F},\pi(n)} \rvert$ where $\pi(\cdot)$ is a permutation of $\{1, \ldots, L\}$.
-			% from strongest to weakest, which attains the maximum in rearrangement inequality.
 			\end{itemize}
@@
 		% \end{remark}
-\end{section}
-
-\begin{section}{Channel Singular Values Redistribution}
-	\begin{subsection}{A Toy Example}\label{sc:toy_example}
+	\end{subsection}
+
+	\begin{subsection}{Channel Singular Values Redistribution}
+		\begin{subsubsection}{A Toy Example}\label{sc:toy_example}
 			We first illustrate the channel shaping capabilities of different \gls{ris} by a toy example.
@@
 			\end{equation}
-		In particular, $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
-		We also enforce symmetry by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
+			It is worth noting that $\phi$ has no impact on the singular value because $\mathrm{sv}(e^{\jmath \phi} \mathbf{A}) = \mathrm{sv}(\mathbf{A})$.
+			For a fair comparison, we also enforce symmetry $\mathbf{\Theta}_\mathrm{U} = \mathbf{\Theta}_\mathrm{U}^\mathsf{T}$ by $\beta = \pi / 2$ such that both architectures have the same number of angular parameters.
 			\begin{figure}
@@
 			This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
-	\end{subsection}
-
-	\begin{subsection}{Pareto Frontier Characterization}
+		\end{subsubsection}
+
+		\begin{subsubsection}{Pareto Frontier Characterization}\label{sc:pareto_frontier}
 			We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
@@
 			Varying $\{\rho_n\}$ unveils the entire achievable singular value region.
-		Thus, the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
+			Thus, we claim the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
 			The objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} for group $g$ corresponds to the Stiefel manifold.
-		Next, we zoom out to general smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
+			Next, we zoom out and provide an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
 
@@
 			\end{equation}
-		An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.\footnote{To double the step size, one only need to square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.}
+			An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.
+			To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.
+			To halve the step size, taking its square root is sufficient in theory but is subject to numerical instability in practice.
 			Finally, the scattering matrix is updated along the geodesic as
@@
 				\begin{enumerate}
-				\item No retraction thanks to rotational update \eqref{eq:geodesic}, \eqref{eq:update_geodesic};
+					\item No retraction from Euclidean space to Stiefel manifold thanks to rotational update \eqref{eq:geodesic}, \eqref{eq:update_geodesic};
 					\item Lower computational complexity per iteration;
@@
 			\begin{lemma}\label{lm:pareto_gradient}
-			The Euclidean gradient of \eqref{ob:pareto} w.r.t. \gls{bd}-\gls{ris} group $g$ is
+				The Euclidean gradient of \eqref{ob:pareto} with respect to \gls{bd}-\gls{ris} group $g$ is
 				\begin{equation}
@@
 			% \eqref{eq:pareto_gradient} is used in line \ref{ln:gradient_euclidean}.
-	\end{subsection}
-
-	\begin{subsection}{Some Analytical Bounds}\label{sc:bounds}
-		We then discuss some analytical bounds related to channel singular values.
-		\begin{proposition}[degree of freedom]\label{pp:dof}
+		\end{subsubsection}
+
+		\begin{subsubsection}{Some Analytical Bounds}\label{sc:bounds}
+			We then discuss some interesting analytical bounds related to channel singular values.
+			\begin{proposition}[Degree of freedom]\label{pp:dof}
 				In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
@@
 
-		\begin{proposition}[rank-deficient channel]\label{pp:rank_deficient}
+			\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
 				% If the forward/backward channel is rank-$k$, then a \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n > k$) channel singular value to the $n-k$-th singular value of $\mathbf{T}$, or suppress the $n$-th ($n < N - k + 1$) channel singular value to the $n$-th singular value of $\mathbf{T}$.
@@
 
-		\begin{corollary}[extreme singular values\label{co:extreme}]
-			With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded above while the last $k$ channel singular values can be suppressed to zero.
+			\begin{corollary}[Extreme singular values\label{co:extreme}]
+				With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded above \footnote{\textellipsis while respecting energy conservation law $\sum_n \sigma_n^2 \le 1$.
+This constraint is omitted in the following context.} while the last $k$ channel singular values can be suppressed to zero.
 				% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
@@
 
-		\begin{proposition}[fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
+			\begin{proposition}[Fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
 				% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
@@
 
-		The problem now becomes how the singular values of matrix product are bounded by the singular values of its individual factors.
+			The problem now becomes \emph{how the singular values of matrix product are bounded by the singular values of its individual factors.}
 			Let $N' = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le N'$.
@@
 
-		\begin{corollary}[generic singular value bounds \cite{Fulton2000}]
+			\begin{corollary}[Generic singular value bounds]
 				\begin{equation}
@@
 			\end{corollary}
-
-		\begin{corollary}[upper bound on the largest singular value]
+			\begin{proof}
+				Please refer to \cite[Theorem 8]{Fulton2000}. This implies the Corollaries~\ref{co:largest_singular_value} and \ref{co:product_singular_values}.
+			\end{proof}
+
+			\begin{corollary}[Upper bound on the largest singular value]\label{co:largest_singular_value}
 				\begin{equation}
@@
 
-		\begin{corollary}[upper bound on the product of first $k$ singular values]
+			\begin{corollary}[Upper bound on the product of first $k$ singular values]\label{co:product_singular_values}
 				\begin{equation}
@@
 
-		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
+			\begin{corollary}[Upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
 				\begin{equation}
@@
 			\end{corollary}
-
-		% \begin{remark}
-		% 	From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-		% 	% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-		% 	\begin{equation}
-		% 		\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
-		% 		\label{eq:scattering_fc_tight}
-		% 	\end{equation}
-		% 	An interpretation is that the off-diagonal entries can enhance the capabilities of
-		% 	\begin{itemize}
-		% 		\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
-		% 		\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximum in rearrangement inequality.
-		% 	\end{itemize}
-		% \end{remark}
+			\begin{proof}
+				Please refer to \cite[Inequality 24.4.7]{Hogben2013}.
+			\end{proof}
+
+			\begin{remark}
+				It is straightforward to verify \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
+				\begin{equation}
+					\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
+					\label{eq:scattering_fc_tight}
+				\end{equation}
+				where $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively.
+			\end{remark}
 
 			Tight bounds are inapplicable when a \gls{mimo} direct link is present, as the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
-		Such a balance often involves optimization approaches and another example will be discussed in Section~\ref{sc:low_complexity}.
+			Such a balance often involves optimization approaches discussed in Section~\ref{sc:pareto_frontier}. Another example will be discussed in Section~\ref{sc:low_complexity}.
+		\end{subsubsection}
+
 	\end{subsection}
 
-\end{section}
-
-\begin{section}{Achievable Rate Maximization}\label{sc:rate}
-	The \gls{mimo} achievable rate maximization problem is formulated w.r.t. joint active and passive beamforming
+	\begin{subsection}{Achievable Rate Maximization}\label{sc:rate}
+		The \gls{mimo} achievable rate maximization problem can be formulated with respect to joint active and passive beamforming.
+		This problem is different from channel shaping because the \gls{ris} is jointly design with the transmitter for an explicit objective
 		\begin{maxi!}
@@
 		where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the noise power, and $P$ is the transmit power budget.
-	Two methods are proposed below to solve problem \eqref{op:rate}.
-
-	\begin{subsection}{Alternating Optimization}
+		Next, we propose a local-optimal solution based on joint \gls{ris}-transceiver design and a low-complexity decoupled solution based on channel shaping.
+
+		\begin{subsubsection}{Alternating Optimization}
 			Consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
@@
 			\begin{lemma}\label{lm:rate_gradient}
-			The Euclidean gradient of \eqref{ob:rate_passive} w.r.t. \gls{bd}-\gls{ris} block $g$ is
+				The Euclidean gradient of \eqref{ob:rate_passive} with respect to \gls{bd}-\gls{ris} block $g$ is
 				\begin{equation}
@@
 			The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-	\end{subsection}
-
-	\begin{subsection}{Low-Complexity Solution}\label{sc:low_complexity}
+		\end{subsubsection}
+
+		\begin{subsubsection}{Low-Complexity Solution}\label{sc:low_complexity}
 			We then propose a low-complexity solution to problem \eqref{op:rate} based on channel shaping.
@@
 				where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-			This suboptimal solution only applies to fully-connected \gls{bd}-\gls{ris}.
+				It is worth noticing this suboptimal one-step solution only applies to fully-connected \gls{bd}-\gls{ris}.
 			\end{remark}
 
-		Inspired by \cite{Nie2017}, we propose a general solution to problem \eqref{op:power_passive} with arbitrary group size.
+			Inspired by \cite{Nie2017}, we propose a solution to problem \eqref{op:power_passive} with arbitrary group size.
 			The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form.
@@
 			Once the channel shaping problem \eqref{op:power_passive} is solved, the transmit precoder can be obtained by \eqref{eq:precoder_eigenmode}.
-		This two-stage approach decouples both blocks and is computationally efficient.
+			This two-stage approach decouples both blocks and is computationally more efficient than the geodesic \gls{rcg} method.
+		\end{subsubsection}
 	\end{subsection}
-
-	% \begin{figure}[H]
-	% 	\centering
-	% 	\subfloat[\gls{ris} Elements, $N^\mathrm{T} = 8$\label{fg:pc_rate_sx}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/chapter_5/pc_rate_sx.tex}
-	% 		}
-	% 	}
-	% 	\subfloat[Transmit Antenna, $N^\mathrm{S} = 256$\label{fg:pc_rate_tx}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/chapter_5/pc_rate_tx.tex}
-	% 		}
-	% 	}
-	% 	\caption{Average achievable rate versus group size $L$. $N^\mathrm{R} = 4$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:pc_rate}
-	% \end{figure}
-
-	% Fig.~\ref{fg:pc_rate_sx} illustrates how \gls{ris} configuration influences the \gls{mimo}-\gls{pc} achievable rate.
-	% To ensure a \qty{20}{bit/s/Hz} transmission, an \gls{snr} of \qty{13.5}{\dB} is required for a 8T4R system.
-	% This value decreases to \qty{12.5}{\dB} (resp. \qty{8}{\dB}) when 32- (resp. 256-) element diagonal \gls{ris} is present.
-	% If tetrads can be formed in \gls{bd}-\gls{ris}, the \gls{snr} can be reduced by another \qty{20}{\percent} (resp. \qty{44}{\percent}).
-	% Further increase in $L$ yields a marginal gain and incurs $\mathcal{O}(L^2)$ connections.
-	% We thus conclude dyadic or tetradic \gls{bd}-\gls{ris} usually strike a good balance between performance and complexity.
-
-	% \begin{figure}[H]
-	% 	\centering
-	% 	\resizebox{0.65\columnwidth}{!}{
-	% 		\input{assets/chapter_5/power_sx.tex}
-	% 	}
-	% 	\caption{Average channel power versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
-$(N^\mathrm{T}, N^\mathrm{R}) = (8, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:power_sx}
-	% \end{figure}
-
-	% \begin{figure}[H]
-	% 	\centering
-	% 	\subfloat[Without Direct Link\label{fg:pc_power_bond_nd}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/chapter_5/pc_power_bond_nd.tex}
-	% 		}
-	% 	}
-	% 	\subfloat[With Direct Link\label{fg:pc_power_bond_hd}]{
-	% 		\resizebox{0.48\columnwidth}{!}{
-	% 			\input{assets/chapter_5/pc_power_bond_hd.tex}
-	% 		}
-	% 	}
-	% 	\caption{Average channel power versus \gls{ris} group size $L$.
-$(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R}) = (8, 256, 4)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$.}
-	% 	\label{fg:pc_power_bond}
-	% \end{figure}
-	% % Fig.~\ref{fg:power_sx} shows that, apart from numerous reflecting elements, a sufficiently large group size can help
-	% % Fig.~\ref{fg:power_sx} shows that increasing the group size can improve the channel power especially for a large \gls{ris}.
-	% Fig.~\ref{fg:power_sx} shows that, apart from adding reflecting elements $N^\mathrm{S}$, increasing the group size $L$ also improves the channel power.
-	% % The behavior is more obvious for a large \gls{ris}.
-	% This behavior is more pronounced for a large \gls{ris}.
-	% For example, the gain of pairwise connection is \qty{2.8}{\percent} for $N^\mathrm{S} = 16$ and \qty{28}{\percent} for $N^\mathrm{S} = 256$.
-	% % \gls{bd}-\gls{ris} provides a higher channel power than conventional \gls{ris}.
-	% % As $L$ increases from 1 to 2,
-	% It implies that the channel shaping capability of \gls{bd}-\gls{ris} scales with group size $L$.
-
-	% Fig.~\ref{fg:pc_power_bond_hd} and \ref{fg:pc_power_bond_nd} compare the average channel power without and with direct link.
-	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % where the cascaded channel power available to passive \gls{ris} is $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % ``Cascaded'' means the maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % maximum power of the cascaded channel, i.e., $\lVert \mathbf{H}^\mathrm{B} \rVert _\mathrm{F}^2 \lVert \mathbf{H}^\mathrm{F} \rVert _\mathrm{F}^2$.
-	% % ? ``Cascaded'' means the \emph{power product} of the forward and backward channels.
-	% % ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues of the forward and backward channels.
-	% ``Cascaded'' means the sum of element-wise product of first $N = \min(N^\mathrm{T}, N^\mathrm{S}, N^\mathrm{R})$ eigenvalues (i.e., element-wise power product) of the forward and backward channels.
-	% We observe that diagonal \gls{ris} wastes substantial cascaded power and struggles to align the direct-indirect subspace.
-	% When the direct link is absent, only \qty{2.6}{\percent} of available power is utilized by diagonal \gls{ris} while \qty{100}{\percent} power is recycled by fully-connected \gls{ris}.
-	% When the direct link is present, the proposed \gls{bd}-\gls{ris} design can balance the direct-indirect and forward-backward subspace alignment for an optimal channel boost.
-	% It is worth noting that, when $L$ is sufficiently large, the composite channel power surpasses the power sum of direct and cascaded channels, thanks to the constructive \emph{amplitude superposition} of direct and cascaded channels.
-	% This again emphasizes the advantage of in-group connection of \gls{bd}-\gls{ris}.
-	% % This is because the direct and indirect channels superpose
-	% % the proposed \gls{bd}-\gls{ris} design can also be applied to conventional \gls{ris} to improve the channel power.
-	% % When the direct link is present, a small $L$ cannot align the direct-indirect subspace.
-
-	% % neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
-	% % We observe that conventional \gls{ris} neither effectively utilizes the cascaded channel power, nor effectively align the direct-indirect subspace.
-	% % For conventional \gls{ris},
-	% % align the direct-indirect subspace.
-	% % When the direct link is present, a small $L$ can neither align the direct-indirect subspace nor the forward-backward subspace.
-	% % For a relatively large $N^\mathrm{S}$, conventional \gls{ris} cannot
-	% % neither the direct-indirect nor the forward-backward subspace can be effectively aligned with a small $L$.
-
-	% % When the direct link is present, a small $L$ can neither preserve the
-	% % neither align the direct-indirect subspace nor the forward-backward subspace.
-
-	% % When the direct link is absent, a large $L$ can align the forward-backward subspace but cannot preserve the forward-backward power balance.
-
 \end{section}
@@
 \begin{section}{\glsfmtshort{mimo}-\glsfmtshort{ic}}
+	\begin{subsection}{System Model}
+		We then shift the focus to an $N_\mathrm{S}$-element \gls{bd}-\gls{ris}-aided interference \gls{mimo} system of $K$ transmitter-receiver pairs, where each transmitter is equipped with $N_\mathrm{T}$ antennas and each receiver is equipped with $N_\mathrm{R}$ antennas.
+		Let $\mathbf{H}_\mathrm{D}^{[kj]} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$, $\mathbf{H}_\mathrm{B}^{[k]} \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{S}}$, $\mathbf{H}_\mathrm{F}^{[j]} \in \mathbb{C}^{N_\mathrm{S} \times N_\mathrm{T}}$ denote respectively the direct channel from transmitter $j$ to receiver $k$, backward channel of receiver $k$, and forward channel of transmitter $j$, where $j, k \in \{1,\ldots,K\} \triangleq \mathcal{K}$.
+		It is assumed that all devices are at the same side of the \gls{ris} and share a common scattering matrix $\mathbf{\Theta}$.
+		The equivalent channel from transmitter $j$ to receiver $k$ is
+		\begin{equation}
+			\mathbf{H}^{[kj]} = \mathbf{H}_\mathrm{D}^{[kj]} + \mathbf{H}_\mathrm{B}^{[k]} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{[j]} = \mathbf{H}_\mathrm{D}^{[kj]} + \sum_g \mathbf{H}_{\mathrm{B},g}^{[k]} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{[j]},
+			\label{eq:channel_equivalent_ic}
+		\end{equation}
+		where $\mathbf{H}_{\mathrm{B},g}^{[k]} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g}^{[j]} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are associated with \gls{ris} group $g$.
+	\end{subsection}
 	\begin{subsection}{Leakage Interference Minimization}
+		Leakage interference refers to the sum of all interference terms in \gls{ic}.
+		Assume all transmitter sends $N_\mathrm{E} \le N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ data streams to its intended receiver.
+		The leakage interference minimization problem is formulated with respect to all transmit precoders, all receiver combiners, and the scattering matrix as
 		\begin{mini!}
-			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}_{kj}^\mathrm{D} + \mathbf{H}_k^\mathrm{B} \mathbf{\Theta} \mathbf{H}_j^\mathrm{F}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{}{}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
-			\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad \mathbf{W}_k^\mathsf{H} \mathbf{W}_k=\mathbf{I}, \quad \forall k.}{}{}
+			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert \mathbf{G}_k (\mathbf{H}^{[kj]}_\mathrm{D} + \mathbf{H}^{[k]}_\mathrm{B} \mathbf{\Theta} \mathbf{H}^{[j]}_{\mathrm{F}}) \mathbf{W}_j \right\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
+			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
+			\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
+			\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
 		\end{mini!}
-		The non-convex problem can be solved by \gls{bcd} method.
-		For a given $\mathbf{\Theta}$, it reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
+		where $\mathbf{G}_k \in \mathbb{C}^{N_\mathrm{D} \times N_\mathrm{R}}$ is the combiner at receiver $k$ and $\mathbf{W}_j \in \mathbb{C}^{N_\mathrm{T} \times N_\mathrm{D}}$ is the precoder at transmitter $j$.
+		It is worth noting that $\mathbf{\Theta}_g$ is a square unitary matrix and $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}$ is equivalent to $\mathbf{\Theta}_g \mathbf{\Theta}_g^\mathsf{H}=\mathbf{I}$, while $\mathbf{G}_k$ and $\mathbf{W}_j$ may be respectively ``fat'' and ``tall'' rectangular semi-unitary matrices such that \eqref{co:combiner} and \eqref{co:precoder} are required.
+		The non-convex problem can be solved iteratively by the \gls{bcd} method detailed below.
+
+		\begin{subsubsection}{Combiner and Precoder Design}
+			For a given $\mathbf{\Theta}$, problem \eqref{op:leakage} reduces to conventional linear beamforming problem, for which an iterative algorithm alternating between the original and reciprocal networks is proposed in \cite{Gomadam2011,Clerckx2013}.
 			At iteration $r$, the combiner at receiver $k$ is updated as
@@
 				\mathbf{G}_k^{(r)} = {\mathbf{U}_{k,N}^{(r-1)}}^\mathsf{H},
-		\end{equation}
-		where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H}$.
+				\label{eq:combiner_leakage}
+			\end{equation}
+			where $\mathbf{U}_{k,N}^{(r-1)}$ is the eigenvectors corresponding to $N$ smallest eigenvalues of the interference covariance matrix $\mathbf{Q}_k^{(r-1)} = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j^{(r-1)} {\mathbf{W}_j^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H}$.
 			The precoder at transmitter $j$ is updated as
@@
 				\mathbf{W}_j^{(r)} = \bar{\mathbf{U}}_{j,N}^{(r)},
-		\end{equation}
-		where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds to interference covariance matrix $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} \mathbf{H}_{kj}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} \mathbf{H}_{kj}$ in the reciprocal network.
-		Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_k\}$ are determined, we define $\bar{\mathbf{H}}_{kj}^\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}_{kj}^\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}_k^\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}_k^\mathrm{B}$, and $\bar{\mathbf{H}}_j^\mathrm{F} \triangleq \mathbf{H}_j^\mathrm{F} \mathbf{W}_j$.
-		The \gls{bd} \gls{ris} subproblem reduces to
+				\label{eq:precoder_leakage}
+			\end{equation}
+			where $\bar{\mathbf{U}}_{j,N}^{(r)}$ corresponds $\bar{\mathbf{Q}}_j^{(r)} = \sum_{k \ne j} {\mathbf{H}^{[kj]}}^\mathsf{H} {\mathbf{G}_k^{(r)}}^\mathsf{H} \mathbf{G}_k^{(r)} {\mathbf{H}^{[kj]}}$ in the reciprocal network.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Scattering Matrix Design}
+			Once $\{\mathbf{G}_k\}$ and $\{\mathbf{W}_j\}$ are determined, we define $\bar{\mathbf{H}}^{[kj]}_\mathrm{D} \triangleq \mathbf{G}_k \mathbf{H}^{[kj]}_\mathrm{D} \mathbf{W}_j$, $\bar{\mathbf{H}}^{[k]}_\mathrm{B} \triangleq \mathbf{G}_k \mathbf{H}^{[k]}_\mathrm{B}$, and $\bar{\mathbf{H}}^{[j]}_\mathrm{F} \triangleq \mathbf{H}^{[j]}_\mathrm{F} \mathbf{W}_j$.
+			The \gls{bd}-\gls{ris} subproblem boils down to
 			\begin{mini!}
-			{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}_{kj}^\mathrm{D} + \bar{\mathbf{H}}_k^\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}_j^\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
+				{\scriptstyle{\mathbf{\Theta}}}{\mathop{\sum\sum}_{j \neq k} \left\lVert (\bar{\mathbf{H}}^{[kj]}_\mathrm{D} + \bar{\mathbf{H}}^{[k]}_\mathrm{B} \mathbf{\Theta} \bar{\mathbf{H}}^{[j]}_\mathrm{F}) \right\rVert _{\mathrm{F}}^2}{\label{op:ic_interference_ris}}{}
+				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
 			\end{mini!}
+			which can be viewed as a channel shaping problem on $\bar{\mathbf{H}}^{[kj]}_\mathrm{D}$, $\bar{\mathbf{H}}^{[k]}_\mathrm{B}$, and $\bar{\mathbf{H}}^{[j]}_\mathrm{F}$.
 
@@
 					\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
+					\label{eq:scatter_leakage}
 				\end{equation}
@@
 				\begin{equation}
-				\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}_{j,g}^\mathrm{F} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{D}_{kj,g}^{(r)}\bigr) {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H},
-			\end{equation}
-			where $\mathbf{B}_{k,g} = \lambda_1\bigl(\mathbf{H}_{k,g}^\mathrm{B} {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H}\bigr) \mathbf{I} - {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{H}_{k,g}^\mathrm{B}$ and
-			\begin{equation}
-				\mathbf{D}_{kj,g}^{(r)} = \mathbf{H}_{jk}^\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
+					\mathbf{M}_g^{(r)} = \mathop{\sum\sum}_{j \neq k} \bigl(\mathbf{B}_{k,g} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{[j]}_{\mathrm{F},g} - {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} {\mathbf{D}^{[kj]}_{g}}^{(r)}\bigr) {\mathbf{H}^{[j]}_{\mathrm{F},g}}^\mathsf{H},
+				\end{equation}
+				where $\mathbf{B}_{k,g} = \lambda_1\bigl({\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{H}^{[k]}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{H}^{[k]}_{\mathrm{B},g}$ and
+				\begin{equation}
+					{\mathbf{D}^{[kj]}_{g}}^{(r)} = \mathbf{H}^{[jk]}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{k,g'}^\mathrm{F} + \sum_{g'>g} {\mathbf{H}_{k,g'}^\mathrm{B}}^\mathsf{H} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{k,g'}^\mathrm{F}.
 				\end{equation}
@@
 			\begin{proof}
-			To be added.
+				The proof is similar to Appendix~\ref{ap:power} and omitted here.
 			\end{proof}
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/chapter_5/ic_interference_sx.tex}
-			}
-			\caption{Average leakage interference versus \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
-Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}.
-$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\gamma^\mathrm{D}, \gamma^\mathrm{F}, \gamma^\mathrm{B}) = (3, 2.4, 2.4)$, and reference pathloss at \qty{1}{\meter} is \qty{-30}{\dB}.}
-			\label{sm:ic_interference_sx}
-		\end{figure}
-		Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd} \gls{ris} helps to reduce the leakage interference.
-		In this case, a fully-connected $2^n$-element \gls{bd} \gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
-		Interestingly, the result suggests that \gls{bd} \gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} (as discussed in \ref{sc:pc_rank_deficient}).
+		\end{subsubsection}
+
+		Problem \eqref{op:leakage} can be solved iteratively by \eqref{eq:combiner_leakage}, \eqref{eq:precoder_leakage}, and \eqref{eq:scatter_leakage}.
+		Convergence to local-optimal points is guaranteed since each subproblem is solved optimally and the objective is bounded above.
+
 	\end{subsection}
@@
 	\begin{subsection}{Weighted Sum-Rate Maximization}
+		Finally, we consider weighted sum-rate maximization in \gls{mimo}-\gls{ic} by joint active and passive beamforming design.
+		The achievable rate of transmission $k$ is given by
+		\begin{equation}
+			R_k = \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{[kj]}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kj]}} \mathbf{W}_k\biggr),
+		\end{equation}
+		where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
+		\begin{equation}
+			\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H} + \eta \mathbf{I},
+		\end{equation}
+		and $\eta$ is the average noise power.
+		The optimization problem is formulated as
 		\begin{maxi!}
-			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{J_2 = \sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k \mathbf{H}_{kj}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kj} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
+			{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{\sum_k \rho_k R_k}{\label{op:ic_rate}}{\label{ob:ic_rate}}
 			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g}{}{}
@@
 		\end{maxi!}
-		where $\rho_k$ is the weight of user $k$ and $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix
-		\begin{equation}
-			\mathbf{Q}_k = \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} \mathbf{H}_{kj}^\mathsf{H} + \eta \mathbf{I}.
-		\end{equation}
-		For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution based on mutual information-\gls{mmse} relationship is proposed in \cite{Negro2010}.
+		where $\rho_k$ is the weight of transmission $k$.
+		The problem is non-convex and can be solved by the \gls{ao} method detailed below.
+
+		\begin{subsubsection}{Precoder Design}
+			For a given $\mathbf{\Theta}$, \eqref{op:ic_rate} reduces to conventional linear beamforming problem, for which a closed-form iterative solution has been proposed in \cite{Negro2010} based on mutual information-\gls{mmse} relationship \cite{Guo2005}.
+			We restate the steps as follows.
+
 			At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
 			\begin{equation}
-			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H}\bigr)^{-1},
+				\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H} \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{[kk]}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H}\bigr)^{-1},
 			\end{equation}
@@
 			\begin{equation}
-			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{(r-1)} \mathbf{H}_{kk} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
+				\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)}}^\mathsf{H} {\mathbf{H}^{[kk]}}^\mathsf{H} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{[kk]}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
 			\end{equation}
@@
 			the Lagrange multiplier is
-		% \begin{equation}
-		% 	\begin{split}
-		% 		\lambda_k^{(r)}
-		% 		& = \frac{\sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_k^{(r)}\mathbf{F}_{kj}^{(r)} {\mathbf{F}_{kj}^{(r)}}^\mathsf{H}) - \sum_{j \ne k} \mathrm{tr}(\mathbf{\Omega}_j^{(r)}\mathbf{F}_{jk}^{(r)} {\mathbf{F}_{jk}^{(r)}}^\mathsf{H})}{P_k} \\
-		% 		& \quad + \frac{\mathrm{tr}(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)}}^\mathsf{H})}{P_k}
-		% 	\end{split}
-		% \end{equation}
 			\begin{equation}
@@
 			\end{equation}
-		where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} \mathbf{H}_{kj} \mathbf{W}_j^{(r)}$.
-		The precoder at transmitter $k$ is
-		\begin{equation}
-			\mathbf{W}_k^{(r)} = \Bigl(\sum_j \mathbf{H}_{jk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}_{jk} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \mathbf{H}_{kk}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
-		\end{equation}
-		Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} w.r.t. \gls{ris} block $g$ is
-		\begin{equation}
-			\begin{split}
-				\frac{\partial J_2}{\partial \mathbf{\Theta}_g^*}
-				& = \sum_k \rho_k {\mathbf{H}_{k,g}^\mathrm{B}}^\mathsf{H} \mathbf{Q}_k^{-1} \mathbf{H}_{kk} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \\
-				& \quad \times \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - \mathbf{H}_{kk}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} \mathbf{H}_{kj} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}_{j,g}^\mathrm{F}}^\mathsf{H}\bigr).
-			\end{split}
+			where $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{[kj]}} \mathbf{W}_j^{(r)}$.
+			The optimal precoder at transmitter $k$ is given by
+			\begin{equation}
+				\mathbf{W}_k^{(r)} = \Bigl(\sum_j {\mathbf{H}^{[jk]}}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{[jk]} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} {\mathbf{H}^{[kk]}}^\mathsf{H} {\mathbf{G}_j^{(r)}}^\mathsf{H} \mathbf{\Omega}_k^{(r)}.
+			\end{equation}
+		\end{subsubsection}
+
+		\begin{subsubsection}{Scattering Matrix Design}
+			Once $\{\mathbf{W}_k\}$ is determined, the complex derivative of \eqref{ob:ic_rate} with respect to \gls{ris} block $g$ is
+			\begin{equation}
+				\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_k \rho_k {\mathbf{H}^{[k]}_{\mathrm{B},g}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kk]}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \bigl({\mathbf{H}_{k,g}^\mathrm{F}}^\mathsf{H} - {\mathbf{H}^{[kk]}}^\mathsf{H} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{[j]}_{\mathrm{F},g}}^\mathsf{H}\bigr).
 				\label{eq:ic_rate_gradient_ris}
 			\end{equation}
-		The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:pc_rate_ris} with \eqref{eq:pc_rate_gradient_ris} replaced by \eqref{eq:ic_rate_gradient_ris}.
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/chapter_5/ic_rate_sx.tex}
-			}
-			\caption{Average weighted sum-rate versus \gls{snr}, \gls{ris} elements $N^\mathrm{S}$ and group size $L$.
-$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}, K) = (8, 4, 3, 5)$, $(\Lambda^\mathrm{D}, \Lambda^\mathrm{F}, \Lambda^\mathrm{B}) = (65, 54, 46) \unit{dB}$, $\rho_k = 1, \ \forall k$.}
-			\label{sm:ic_rate_sx}
-		\end{figure}
-
-		\begin{figure}[!t]
-			\centering
-			\resizebox{0.65\columnwidth}{!}{
-				\input{assets/chapter_5/ic_rate_user.tex}
-			}
-			\caption{Average weighted sum-rate versus user pairs $K$, \gls{ris} elements $N^\mathrm{S}$ and group size $L$ at $\mathrm{SNR} = \qty{15}{dB}$.
-$(N^\mathrm{T}, N^\mathrm{R}, N^\mathrm{E}) = (4, 4, 3)$, $\rho_k = 1, \ \forall k$.}
-			\label{sm:ic_rate_user}
-		\end{figure}
-
-		A new observation from Fig.~\ref{sm:ic_rate_sx} that the interference alignment capability of \gls{bd} \gls{ris} scales much faster with group size than number of elements.\footnote{The results are not very stable and depend heavily on initialization.}
+		\end{subsubsection}
+		The \gls{ris} subproblem can be solved by \gls{rcg} Algorithm~\ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses \eqref{eq:ic_rate_gradient_ris} explicitly.
 	\end{subsection}
@@
 
-	\begin{table*}[!t]
+	\begin{subsection}{Algorithm Evaluation}
+		\begin{table}[H]
 			\footnotesize
-		\caption{Average Performance of \gls{bd}-\gls{ris} Designs}
+			\caption{Average performance of \gls{rcg} algorithms on problem \eqref{op:pareto}. Minimum relative gain per iteration $\epsilon=\num{e-4}$ and number of channel realizations $T=100$.}
 			\label{tb:complexity_test}
@@
 			\end{tabular}
-	\end{table*}
-
-	\begin{subsection}{Channel Singular Values Redistribution}
+		\end{table}
+
+		We first compare the proposed geodesic \gls{rcg} algorithm with the general non-geodesic approach \cite{Absil2009,Pan2022d} on problem \eqref{op:pareto}.
+		It is observed that the geodesic \gls{rcg} algorithm achieves a slightly higher objective value with significantly (around 10$\times$) lower number of iterations and shorter computational time than the non-geodesic one.
+		The results suggest that the proposed optimization framework is very efficient for asymmetric \gls{bd}-\gls{ris} design.
+		If the scattering matrix has to be symmetric, one can project the solution to the feasible domain by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.
+	\end{subsection}
+
+	\begin{subsection}{\glsfmtshort{mimo}-\glsfmtshort{pc}}
 		\begin{subsubsection}{Pareto Frontier}
@@
 			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris}.
 		\end{subsubsection}
@@
 					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
+					The intersections of the blue and red bars denote the singular values of the direct channel.
+					The blue (resp. red) bars are obtained by solving problem \eqref{op:pareto} with $\rho_n = -1$ (resp. $+1$) and $\rho_{n'} = 0$, $\forall n' \ne n$.
 					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
-					`rank-$k$' refers to the forward channel.
+					`rank-$k$' refers to the rank of the forward channel.
 				}
@@
 \ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
-			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form or via optimization approach \eqref{eq:scattering_power}.
+			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_tight} or via optimization approach \eqref{eq:scattering_power}.
 			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
@@
 			This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
-			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
+			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement.
 			Now consider a diagonal \gls{ris} in \gls{mimo}.
@@
 
-		% The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
-		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
-		% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
-		% Clearly, a larger group size provides
-		% and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
-		% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
-	\end{subsection}
-
-	\begin{subsection}{Achievable Rate Maximization}
+		% \begin{subsection}{Channel Singular Values Redistribution}
+		% 	% The Pareto singular value frontiers of a $2 \times 2$ \gls{mimo} with a 32-element \gls{bd}-\gls{ris} is shown in Fig.~\ref{fg:singular_pareto}.
+		% 	% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
+		% 	% The Pareto frontier of channel singular values reshaped by \gls{bd}-\gls{ris} is shown in Fig. \ref{fg:singular_pareto}.
+		% 	% Clearly, a larger group size provides
+		% 	% and evolving trend of channel singular values are shown in Fig.~\ref{fg:singular_pareto} and \ref{fg:pc_singular_bound}.
+		% 	% Clearly, \gls{bd}-\gls{ris} with a larger group size can redistribute the channel singular values to a wider range.
+		% \end{subsection}
+
+		\begin{subsubsection}{Channel Power and Achievable Rate Maximization}
 			\begin{figure}[H]
@@
 
-		We first focus on channel shaping subproblem \eqref{op:power_passive_approx}.
+			We first focus on channel shaping subproblem \eqref{op:power_passive}.
 			Fig. \ref{fg:power_sx} shows the achievable channel power under different \gls{ris} configurations.
@@
 			Interestingly, the gap between the optimal \gls{ao} approach \eqref{op:rate_passive}--\eqref{eq:precoder_eigenmode} and the low-complexity solution \eqref{eq:scattering_power} and \eqref{eq:precoder_eigenmode} narrows as the group size increases, and completely vanishes for a fully-connected \gls{bd}-\gls{ris}.
-		This implies that the \gls{ris}-transceiver design can be completely decoupled via channel shaping with marginal performance loss.
+			This implies that the \gls{ris}-transceiver design can often be decoupled via channel shaping with marginal performance loss.
 			Figs. \subref*{fg:rate_txrx} and \subref*{fg:rate_sx} also confirm the advantage of \gls{bd}-\gls{ris} grows with the number of transmit, scatter, and receive antennas.
@@
 			The observation is expected from previous studies \cite{Shen2020a,Li2023b,Nerini2023} and aligns with Corollary \ref{co:los}, which suggests that the \gls{bd}-\gls{ris} should be deployed in rich-scattering environments to exploit its channel shaping potential.
+		\end{subsubsection}
+	\end{subsection}
+
+	\begin{subsection}{\glsfmtshort{mimo}-\glsfmtshort{ic}}
+		\begin{subsubsection}{Leakage Interference Minimization}
+			\begin{figure}[H]
+				\centering
+				\resizebox{0.65\columnwidth}{!}{
+					\input{assets/chapter_5/ic_interference_sx.tex}
+				}
+				\caption{Average leakage interference versus \gls{ris} elements $N_\mathrm{S}$ and group size $L$.
+Transmitters and receivers are randomly generated in a disk of radius 50 m centered at the \gls{ris}.
+$(N_\mathrm{T}, N_\mathrm{R}, N_\mathrm{E}, K) = (8, 4, 3, 5)$.}
+				\label{sm:ic_interference_sx}
+			\end{figure}
+			Fig.~\ref{sm:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
+			In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a diagonal $2^{n+2}$-element \gls{ris} in terms of leakage interference.
+			Interestingly, the result suggests that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo}-\gls{ic}, which is not the case in \gls{mimo}-\gls{pc} as discussed in \ref{pp:dof}.
+			This demonstrates the potential of \gls{bd}-\gls{ris} in interference alignment or cancellation.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Weighted Sum-Rate Maximization}
+			\begin{figure}[H]
+				\centering
+				\resizebox{0.65\columnwidth}{!}{
+					\input{assets/chapter_5/ic_rate_sx.tex}
+				}
+				\caption{Average weighted sum-rate versus average transmit power, \gls{ris} elements $N_\mathrm{S}$, and group size $L$. $(N_\mathrm{T}, N_\mathrm{R}, N_\mathrm{E}, K) = (8, 4, 3, 5)$.}
+				\label{sm:ic_rate_sx}
+			\end{figure}
+
+			Fig.~\ref{sm:ic_rate_sx} shows the average weighted sum-rate versus average transmit power and \gls{ris} configuration.
+			We observe that the advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} becomes more pronounced when the number of reflecting elements increases.
+			This is because the total number of subchannels in the system grows linearly with $N_\mathrm{S}$ such that the gain from subchannel rearrangement capability of \gls{bd}-\gls{ris} is amplified.
+			It suggests cooperative scattering among elements is particularly important for large-scale \gls{ris} deployments in \gls{mimo}-\gls{ic} systems, where the performance-complexity trade-off is more favorable than \gls{siso} and single-user scenarios.
+
+			\begin{figure}[H]
+				\centering
+				\resizebox{0.65\columnwidth}{!}{
+					\input{assets/chapter_5/ic_rate_user.tex}
+				}
+				\caption{Average weighted sum-rate versus transmitter-receiver pairs $K$, \gls{ris} elements $N_\mathrm{S}$, and group size $L$.
+$(N_\mathrm{T}, N_\mathrm{R}, N_\mathrm{E}) = (4, 4, 3)$, $P = \qty{25}{dB}$, and $\rho_k = 1, \ \forall k$.}
+				\label{sm:ic_rate_user}
+			\end{figure}
+
+			Fig.~\ref{sm:ic_rate_user} shows the average weighted sum-rate versus the number of transmitter-receiver pairs and \gls{ris} configuration.
+			We observe that introducing a \gls{ris} to \gls{ic} systems is helpful to mitigate the rate saturation effect as the number of users increases.
+			In the overloaded regime ($K \ge 8$), \gls{bd}-\gls{ris} provides a larger slope of the achievable rate than diagonal \gls{ris}.
+			This is because the \gls{bd}-\gls{ris} can better align the interference subspaces of different users, as discussed in Remark \ref{rm:channel_shaping}.
+			At $K=10$, adding a 64-element diagonal and \gls{bd}-\gls{ris} can improve the weighted sum-rate by \qty{23}{\percent} and \qty{43}{\percent}, respectively.
+			% These results highlight the importance of \gls{ris}, and particularly t configurations, for maximizing the capacity of overloaded multi-user interference channels
+			These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where \gls{bd} configurations can significantly enhance the network capacity.
+		\end{subsubsection}
 	\end{subsection}
@@
 \begin{section}{Conclusion}
-	This chapter analyzes the channel shaping capability of \gls{ris} in terms of singular values redistribution.
-	We consider a general \gls{bd} architecture that allows elements within the same group to interact, enabling more sophisticated manipulation than diagonal \gls{ris}.
-	This translates to a wider dynamic range (with better trade-off) of singular values and significant power and rate gains, especially in large-scale \gls{mimo} systems.
-	We characterize the Pareto frontiers of channel singular values via optimization approach and provide analytical bounds in rank-deficient and fully-connected scenarios.
-	An efficient \gls{rcg} algorithm is proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
-	We also present two beamforming designs for rate maximization problem, one based on alternating optimization for optimal performance and the other decouples the \gls{ris}-transceiver design for lower complexity.
-	Extensive simulations show that the advantage of \gls{bd}-\gls{ris} stems from its superior subspace alignment and subchannel rearrangement capability, which scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity.
-
-	One future direction is introducing \gls{bd}-\gls{ris} to \gls{mimo} interference channel for interference alignment or cancellation.
-	Another open issue is to exploit different groups of \gls{bd}-\gls{ris} to enhance the channel response (and possibly ride extra information) at different frequencies.
-	Incorporating a \gls{ris} at both transmitter and receiver sides provides even stronger manipulation that potentially align both direct-indirect and forward-backward subspaces simultaneously.
+	This chapter studied the channel shaping capability of \gls{ris} in \gls{mimo}-\gls{pc} and \gls{ic}.
+	We considered a general \gls{bd} architecture that allows elements within the same group to cooperate, enabling advanced wave manipulation than conventional \gls{ris}.
+	% This translates to a wider dynamic range (with better trade-off) of channel singular values with significant power and rate gains in \gls{pc}, and lower leakage interference and higher \gls{dof} in \gls{ic}.
+	% Those advantages are more pronounced in rich-scattering environments and large-scale systems.
+	An efficient \gls{rcg} algorithm was proposed for smooth \gls{bd}-\gls{ris} optimization problems, which offers lower computation complexity and faster convergence than existing methods.
+	For \gls{pc}, we characterized the Pareto frontiers of channel singular values via optimization approach and provided analytical bounds in rank-deficient and fully-connected scenarios.
+	Two joint beamforming designs were proposed for rate maximization problem, one based on \gls{ao} for optimal performance and one based on channel shaping for lower complexity.
+	For \gls{ic}, we highlighted that \gls{bd}-\gls{ris} can reduce the leakage interference and improve the weighted sum-rate.
+	Extensive simulation results and theoretical analysis showed that the advantage of \gls{bd}-\gls{ris} scales with the number of elements, group size, \gls{mimo} dimensions, and channel diversity, thanks to its superior subspace alignment and subchannel rearrangement capability.
+
+	One future direction is incorporating one \gls{ris} at transmitter and one at receiver for stronger channel manipulation, which may fully align both direct-indirect and forward-backward subspaces simultaneously.
 	% Finally, integrating the \gls{ris} into the \gls{mimo} precoding and combining design is also an interesting topic for future research.

### 2024-03-30 content/chapter_6.tex
:triangular_flag_on_post: Initial submission 240330

@@
 		\item In the domain of \gls{swipt}, we unveiled new trade-offs and design insights by introducing \gls{ris} into multi-antenna, multi-carrier systems.
-Considering harvester nonlinearity, we characterize the achievable \gls{r-e} region through a joint optimization of waveform, active and passive beamforming based on the \gls{csit}.
-This problem is solved by \gls{bcd}, where we obtain the active precoder in closed form, the passive beamforming by \gls{sca}, and the waveform amplitude by \gls{gp}.
-To facilitate practical implementation, we also propose two low-complexity designs based on closed-form adaptive waveform schemes.
-Simulation results highlight a second-order array gain and a fourth-order power scaling order with respect to \gls{ris} elements, while being robust to \gls{csi} inaccuracy and \gls{ris} resolution.
+Considering harvester nonlinearity, we characterized the achievable \gls{r-e} region through a joint optimization of waveform, active and passive beamforming based on the \gls{csit}.
+This problem was solved by \gls{bcd}, where we obtained the active precoder in closed form, the passive beamforming by \gls{sca}, and the waveform amplitude by \gls{gp}.
+To facilitate practical implementation, we also proposed two low-complexity designs based on closed-form adaptive waveform schemes.
+Simulation results highlighted a second-order array gain and a fourth-order power scaling order with respect to \gls{ris} elements, while being robust to \gls{csi} inaccuracy and \gls{ris} resolution.
 		\item The proposed RIScatter concept demonstrated the synergy between active and passive transmissions.
@@
 		This enables RIScatter to softly bridge \gls{bc} and \gls{ris}; reduce to either in special cases; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
-		We also propose a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
-		For a single-user multi-node network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
-		Simulation results demonstrate the received signal can be exploited for dual purposes and the nodes can shift smoothly between backscatter modulation and passive beamforming via input distribution control.
+		We also proposed a low-complexity \gls{sic}-free receiver that exploits the properties of RIScatter.
+		For a single-user multi-node network, we characterized the achievable primary-(total-)backscatter rate region by optimizing the input distribution at scatter nodes, the active beamforming at the \gls{ap}, and the energy decision regions at the user.
+		Simulation results demonstrated that the received signal can be exploited for dual purposes and the nodes can shift smoothly between backscatter modulation and passive beamforming via input distribution control.
 		\item Finally, we investigated the fundamental limits of \gls{ris} for reshaping \gls{mimo} \gls{pc} and \gls{ic}.
-We depart from the widely-adopted diagonal phase shift model to a general \gls{bd} architecture with superior subspace alignment and subchannel rearrangement capabilities.
-		An efficient geodesic \gls{rcg} algorithm is tailored for smooth \gls{bd}-\gls{ris} optimization problems, which features lower complexity and faster convergence.
-		For \gls{mimo}-\gls{pc}, we characterize the achievable channel singular value region through numerical and analytical approaches, then tackle the rate maximization problem by a local-optimal \gls{ao} approach and a low-complexity shaping-inspired approach.
-		For \gls{mimo}-\gls{ic}, we extend the proposed algorithms to solve leakage interference minimization and \gls{wsr} maximization problems.
-		Simulation results suggest channel shaping offers a promising path to decouple the joint \gls{ris}-transceiver design with minor performance degradation and much lower computational complexity.
+We departed from the widely-adopted diagonal phase shift model to a general \gls{bd} architecture with superior subspace alignment and subchannel rearrangement capabilities.
+		An efficient geodesic \gls{rcg} algorithm was tailored for smooth \gls{bd}-\gls{ris} optimization problems, which features lower complexity and faster convergence.
+		For \gls{mimo}-\gls{pc}, we characterized the achievable channel singular value region through numerical and analytical approaches, then tackled the rate maximization problem by a local-optimal \gls{ao} approach and a low-complexity shaping-inspired approach.
+		For \gls{mimo}-\gls{ic}, we extended the proposed algorithms to solve leakage interference minimization and \gls{wsr} maximization problems.
+		Simulation results suggested channel shaping offers a promising path to decouple the joint \gls{ris}-transceiver design with minor performance degradation and much lower computational complexity.
 	\end{itemize}
@@
 		\item \emph{Multi-sector \gls{bd}-\gls{ris} and interference alignment:} The current work solves leakage interference minimization and \gls{wsr} maximization problems in \gls{ris}-aided \gls{ic}.
-		It remains unknown how many scattering elements are required to completely eliminate the interference, and what is the \gls{dof} in a $(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ \gls{ic}.
+		It remains unknown how many scattering elements are required to completely eliminate the interference, and what is the \gls{dof} in a $K$-user $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ \gls{ic}.
 		Besides, there exists a multi-sector model \cite{Li2023c} that provides full-space coverage and highly directional beams.

### 2024-03-30 content/declaration.tex
:triangular_flag_on_post: Initial submission 240330

@@
 	Figures, tables, and results presented in this dissertation are generated by myself, unless otherwise stated.
-	I would like to acknowledge the use of large language models for assistance in improving the clarity and readability of introduction and background sections of this thesis.
+	I would like to acknowledge the use of large language models for assistance in improving the clarity and readability of this thesis.
 	The contents have not been submitted in whole or in part for consideration of any other degree or qualification in any academic institution.

### 2024-03-30 misc/glossaries.tex
:pencil: Update chapter 3
:pencil: Add conclusion
:triangular_flag_on_post: Initial submission 240330

@@
 \newacronym{nrz}{NRZ}{Non-Return-to-Zero}
+\newacronym{leh}{LEH}{Linear Energy Harvester}
+\newacronym{fs}{FS}{Frequency-Selective}
+\newacronym{rsma}{RSMA}{Rate-Splitting Multiple Access}
 
@@
 \nomenclature[e-3]{$\mathcal{A}$}{Finite set}
-\nomenclature[e-4]{$\mathbf{0}$}{Zero matrix}
-\nomenclature[e-5]{$\mathbf{1}$}{One matrix}
+\nomenclature[e-4]{$\mathbf{0}$}{All-zero matrix}
+\nomenclature[e-5]{$\mathbf{1}$}{All-one matrix}
 \nomenclature[e-6]{$\mathbf{I}$}{Identity matrix}
@@
 \nomenclature[o-t]{$\mathbb{E}(\cdot)$}{Expectation operator}
-\nomenclature[o-u]{$\mathbb{A}(\cdot)$}{Extracts the \glsfmtlong{dc} component of a signal}
+\nomenclature[o-u]{$\mathbb{A}(\cdot)$}{Extracts the direct current component of a signal}
 \nomenclature[o-v]{$\odot$}{Hadamard product}
@@
 \nomenclature[r-a]{$\sim$}{Follows a distribution}
-\nomenclature[r-b]{$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$}{Multivariate \glsfmtlong{cscg} with covariance $\mathbf{\Sigma}$}
+\nomenclature[r-b]{$\mathcal{CN}(\mathbf{0}, \mathbf{\Sigma})$}{Multivariate circularly symmetric complex Gaussian with covariance $\mathbf{\Sigma}$}
 
-\nomenclature[s-d]{$(\cdot)_\text{D}$}{Direct}
-\nomenclature[s-f]{$(\cdot)_\text{F}$}{Forward}
-\nomenclature[s-b]{$(\cdot)_\text{B}$}{Backward}
-\nomenclature[s-i]{$(\cdot)_\text{I}$}{Information}
-\nomenclature[s-p]{$(\cdot)_\text{P}$}{Power}
+\nomenclature[s-1]{$(\cdot)_\text{D}$}{Direct}
+\nomenclature[s-2]{$(\cdot)_\text{F}$}{Forward}
+\nomenclature[s-3]{$(\cdot)_\text{B}$}{Backward}
+\nomenclature[s-4]{$(\cdot)_\text{I}$}{Information}
+\nomenclature[s-5]{$(\cdot)_\text{P}$}{Power}
+\nomenclature[s-6]{$(\cdot)_\text{T}$}{Transmit}
+\nomenclature[s-7]{$(\cdot)_\text{S}$}{Scatter}
+\nomenclature[s-8]{$(\cdot)_\text{R}$}{Receive}
 
@@
 \nomenclature[u-b]{$(\cdot)^\star$}{Stationary point}
+\nomenclature[u-c]{$(\cdot)^{[kj]}$}{Associated with transmitter $j$ and receiver $k$}

### 2024-04-30 assets/viva/receiver.tex
:construction: Add viva slides

\begin{tikzpicture}[
		% every axis plot/.append style={thick},
		every node/.append style={draw,minimum width=6cm},
		align=center
	]
	\draw[-{Latex[length=4mm]}] (0,0) node[anchor=south](0){Semi-coherently decode node message} to ++(0,-0.5) node[anchor=north](1){Re-encode for reflection pattern};
	\draw[-{Latex[length=4mm]}] (1.south) to ++(0,-0.5) node[anchor=north](2){Model within equivalent channel};
	\draw[-{Latex[length=4mm]}] (2.south) to ++(0,-0.5) node[anchor=north](3){Coherently decode primary message};
\end{tikzpicture}

### 2024-04-30 assets/viva/region_comparison.tex
:construction: Add viva slides

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.30100,0.74500,0.93300}%
\definecolor{mycolor2}{rgb}{0.46600,0.67400,0.18800}%
\definecolor{mycolor3}{rgb}{0.49400,0.18400,0.55600}%
\definecolor{mycolor4}{rgb}{0.92900,0.69400,0.12500}%
\definecolor{mycolor5}{rgb}{0.85000,0.32500,0.09800}%
\definecolor{mycolor6}{rgb}{0.00000,0.44700,0.74100}%
%
\begin{tikzpicture}

\begin{axis}[%
	width=4.079in,
	height=3.432in,
at={(0.673in,0.356in)},
scale only axis,
xmin=0,
xmax=6.5227548374066,
xlabel style={font=\color{white!15!black}},
xlabel={Primary Rate [bits/s/Hz]},
ymin=0,
ymax=2,
ylabel style={font=\color{white!15!black}},
ylabel={Backscatter Rate [bits/BB]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black},
align=center,
title style={font=\huge},
label style={font=\huge},
ticklabel style={font=\LARGE},
legend style={font=\LARGE},
reverse legend,
every axis plot/.append style={line width=2pt}
]
\addplot [color=mycolor1, line width=2.0pt, mark=triangle, mark options={solid, rotate=180, mycolor1}]
  table[row sep=crcr]{%
6.33724402501803	1.39764296268229\\
0	1.39764296268229\\
0	0\\
6.52275483678685	0\\
6.52275483678685	2.37312052924553e-08\\
6.38739454470992	1.3235811846854\\
6.35422040211439	1.38916612409166\\
6.34857862205488	1.39386686170527\\
6.3445353675389	1.39608085009443\\
6.34291602910554	1.3966977322109\\
6.34149846039129	1.39711118534274\\
6.34024731759122	1.39737797077851\\
6.3391350240222	1.3975379071887\\
6.33862394227692	1.39758701988787\\
6.33813974610465	1.39761939115801\\
6.33795313341839	1.39762818964178\\
6.33777036860279	1.39763482338317\\
6.3375913342378	1.3976394187338\\
6.33741590881855	1.39764209463684\\
6.33724402501803	1.39764296268229\\
};
\addlegendentry{RIScatter}

\addplot[only marks, mark=triangle, mark options={}, mark size=2.3570pt, draw=mycolor2] table[row sep=crcr]{%
x	y\\
6.5227548374066	0\\
};
\addlegendentry{RIS}

\addplot[only marks, mark=+, mark options={}, mark size=3.5355pt, draw=mycolor3] table[row sep=crcr]{%
x	y\\
6.34321982467796	2\\
};
\addlegendentry{SR}

\addplot[only marks, mark=x, mark options={}, mark size=3.5355pt, draw=mycolor4] table[row sep=crcr]{%
x	y\\
5.90778796357092	1.34857377961699\\
};
\addlegendentry{AmBC}

\addplot[only marks, mark=square, mark options={}, mark size=2.5000pt, draw=mycolor5] table[row sep=crcr]{%
x	y\\
0	1.99999999999997\\
};
\addlegendentry{BBC}

\addplot[only marks, mark=o, mark options={}, mark size=2.7386pt, draw=mycolor6] table[row sep=crcr]{%
x	y\\
6.34314881160129	0\\
};
\addlegendentry{Legacy}

\end{axis}
\end{tikzpicture}%

### 2024-04-30 assets/viva/riscatter.tex
:construction: Add viva slides

--- 2024-03-27 assets/chapter_4/riscatter.tex
@@
-\begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
+\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
 	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
@@
 	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
-	\draw[green,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);
+	\draw[orange,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);
 

### 2024-04-30 assets/viva/wpt_architecture.tex
:construction: Add viva slides

--- 2024-03-22 assets/chapter_2/wpt_architecture.tex
@@
-\begin{circuitikz}[transform shape,align=center,font=\footnotesize]
+\begin{circuitikz}[transform shape,align=center]
 	\draw(0,0) node[draw](rf){\gls{rf}\\source};
@@
 	\draw(1,1) node{Tx};
-	\draw(4.875,2) node[draw]{\gls{ris}};
-	\draw(4.875,1) node[draw]{Channel};
+	\draw(4.875,2) node[draw]{\textcolor{orange}{\gls{ris}}};
+	\draw(4.875,1) node[draw]{\textcolor{orange}{Channel}};
 	\draw(10,0) node[draw](mc){Matching\\network};
@@
 	\draw(8.7,1) node{Rx};
-	\draw(mc.east) to ++(0.85,0) node[anchor=west,draw](d){Diode};
-	\draw(d.east) to ++(0.85,0) node[anchor=west,draw](lpf){Low-pass\\filter};
-	\draw(lpf.east) to ++(1,0) node[anchor=west,draw](dd){\gls{dc}-\gls{dc}\\converter};
+	\draw(mc.east) to ++(0.85,0) node[anchor=west,draw](r){\textcolor{blue}{Rectifier}};
+	% \draw(d.east) to ++(0.85,0) node[anchor=west,draw](r){Low-pass\\filter};
+	\draw(r.east) to ++(1,0) node[anchor=west,draw](dd){\gls{dc}-\gls{dc}\\converter};
 	\draw(dd.east) to ++(1,0) node[anchor=west,draw](s){Storage};
@@
 	\draw (1.4,3) node[]{Energy transmitter};
-	\draw [dotted] (6.25,-0.5) rectangle (15.6,2.5);
-	\draw (10.925,2) node[]{Rectenna};
-	\draw [dotted] (16,-0.5) rectangle (20.5,1.25);
-	\draw (18.25,0.875) node[]{Power management unit};
-	\draw [dashed] (6,-0.75) rectangle (20.75,2.75);
+	\draw [dotted] (6.25,-0.5) rectangle (13.2,2.5);
+	\draw (9.9,2) node[]{\textcolor{blue}{Rectenna}};
+	\draw [dotted] (13.8,-0.5) rectangle (19.9,1.25);
+	\draw (16.75,0.875) node[]{Power management unit};
+	\draw [dashed] (6,-0.75) rectangle (20.1,2.75);
 	\draw (13.375,3) node[]{Energy receiver};
@@
 	\draw (6,-1) node[]{$P_{\mathrm{RF}}^{\mathrm{R}}$};
-	\draw (15.8,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{R}}$};
-	\draw (20.5,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{S}}$};
+	\draw (13.5,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{R}}$};
+	\draw (20.3,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{S}}$};
 

### 2024-04-30 viva/slides.tex
:construction: Add viva slides

\documentclass[presentation,xcolor={table},9pt]{beamer}

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[makeroom]{cancel}
\usepackage[american]{circuitikz}
\usepackage{cite}
% \usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{lastpage}
\usepackage{caption}
\setbeamerfont{caption}{size=\footnotesize}
\captionsetup[figure]{labelformat=empty}
\usefonttheme[onlymath]{serif}

\makeatletter
\@addtoreset{subfigure}{framenumber}
\makeatother

\makeatletter
\newcommand{\forcealgorithm}{\let\@latex@error\@gobble}
\makeatother

% footnote
\newcommand\blfootnote[1]{%
\begingroup
\renewcommand\thefootnote{}\footnote{#1}%
\addtocounter{footnote}{-1}%
\endgroup
}

% amsthm
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
% \newtheorem{lemma}{Lemma}
% \newtheorem{corollary}{Corollary}[proposition]

% PGF/TikZ
\pgfplotsset{compat=1.18}
\usepgfplotslibrary{fillbetween,groupplots,patchplots}
\usetikzlibrary{arrows,arrows.meta,automata,backgrounds,calc,math,matrix,patterns,plotmarks,positioning,shapes,angles,quotes}
\usetikzlibrary{decorations.pathmorphing,decorations.pathreplacing,decorations.markings,decorations.shapes,shapes.geometric}

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{ai}{AI}{Artificial Intelligence}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{am}{AM}{Arithmetic Mean}
\newacronym{ao}{AO}{Alternating Optimization}
\newacronym{ap}{AP}{Access Point}
\newacronym{apm}{APM}{Amplitude-Phase Modulation}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communication}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bd}{BD}{Beyond-Diagonal}
\newacronym{ber}{BER}{Bit Error Rate}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{clt}{CLT}{Central Limit Theorem}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csit}{CSIT}{Channel State Information at the Transmitter}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{cw}{CW}{Continuous Waveform}
\newacronym{d2d}{D2D}{Device-to-Device}
\newacronym{dcmc}{DCMC}{Discrete-input Continuous-output Memoryless Channel}
\newacronym{dc}{DC}{Direct Current}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmmac}{DMMAC}{Discrete Memoryless Multiple Access Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dof}{DoF}{Degree of Freedom}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{eirp}{EIRP}{Effective Isotropic Radiated Power}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}
\newacronym{gm}{GM}{Geomtric Mean}
\newacronym{gp}{GP}{Geometric Programming}
\newacronym{ic}{IC}{Interference Channel}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{im}{IM}{Index Modulation}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{los}{LoS}{Line-of-Sight}
\newacronym{m2m}{M2M}{Machine-to-Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communication}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{mse}{MSE}{Mean-Square Error}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pc}{PC}{Point-to-point Channel}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pga}{PGA}{Projected Gradient Ascent}
\newacronym{pin}{PIN}{Positive Intrinsic Negative}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{ps}{PS}{Power Splitting}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{r-e}{R-E}{Rate-Energy}
\newacronym{rcg}{RCG}{Riemannian Conjugate Gradient}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sca}{SCA}{Successive Convex Approximation}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{sdp}{SDP}{Semi-Definite Programming}
\newacronym{sdr}{SDR}{Semi-Definite Relaxation}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{siso}{SISO}{Single-Input Single-Output}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{star}{STAR}{Simultaneous Transmission and Reflection}
\newacronym{smf}{SMF}{Scaled Matched Filter}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{svd}{SVD}{Singular Value Decomposition}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ts}{TS}{Time Switching}
\newacronym{ue}{UE}{User Equipment}
\newacronym{wf}{WF}{Water-Filling}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{wsn}{WSN}{Wireless Sensor Network}
\newacronym{wsr}{WSR}{Weighted Sum-Rate}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{lc}{LC}{Low-Complexity}
\newacronym{ble}{BLE}{Bluetooth Low Energy}
\newacronym{lora}{LoRa}{Long Range}
\newacronym{lorawan}{LoRaWAN}{Long Range Wide Area Network}
\newacronym{pae}{PAE}{Power-Added Efficiency}
\newacronym{papr}{PAPR}{Peak-to-Average Power Ratio}
\newacronym{fsk}{FSK}{Frequency-Shift Keying}
\newacronym{css}{CSS}{Chirp Spread Spectrum}
\newacronym{dsss}{DSSS}{Direct-Sequence Spread Spectrum}
\newacronym{fsss}{FSSS}{Frequency-Hopping Spread Spectrum}
\newacronym{rz}{RZ}{Return-to-Zero}
\newacronym{nrz}{NRZ}{Non-Return-to-Zero}
\newacronym{leh}{LEH}{Linear Energy Harvester}
\newacronym{fs}{FS}{Frequency-Selective}
\newacronym{rsma}{RSMA}{Rate-Splitting Multiple Access}

\newacronym{embb}{eMBB}{enhanced Mobile Broadband}
\newacronym{urllc}{URLLC}{Ultra-Reliable Low-Latency Communication}
\newacronym{mmtc}{mMTC}{massive Machine-Type Communication}

\usetheme{Frankfurt}
\addtobeamertemplate{navigation symbols}{}{%
    \usebeamerfont{footline}%
    \usebeamercolor[fg]{footline}%
    \hspace{1em}%
	\raisebox{1.5pt}[0pt][0pt]{\insertframenumber/\inserttotalframenumber}
}

\epstopdfsetup{outdir=../assets/viva/}

\title[\glsfmtshort{ris}: Beamforming, Modulation, and Channel Shaping]{\textbf{\glsfmtfull{ris}:\\Beamforming, Modulation, and Channel Shaping}}
\subtitle{Viva Presentation}
\author{Yang Zhao, supervised by Prof Bruno Clerckx}
\institute{Department of Electrical and Electronic Engineering\\Imperial College London}
% \date{\today}
\date{May 2, 2024}

\begin{document}

\frame{\titlepage}

\begin{section}{Intro}
	\begin{frame}{Do we want more waves in the air?}
		\begin{block}{Massive \glsfmtshort{mimo} is here}
			\begin{figure}
				\centering
				\subfloat[8T8R and m\glsfmtshort{mimo} at Imperial]{
					\resizebox{!}{3cm}{
						\includegraphics{../assets/viva/massive_mimo.jpg}
					}
				}
				\subfloat[Cellular statistics]{
					\resizebox{!}{3cm}{
						\includegraphics{../assets/viva/cellular_analysis.png}
					}
				}
			\end{figure}
		\end{block}
		\begin{block}{How far are we from the Shannon capacity?}
			\begin{equation*}
				C(\mathbf{H}) = \max_{\mathbf{Q} \succeq 0, \mathrm{tr}(\mathbf{Q}) \le P} \log \det \left( \mathbf{I} + \rho \mathbf{H} \mathbf{Q} \mathbf{H}^\mathsf{H} \right)
			\end{equation*}
			\vspace{-1em}
			\begin{itemize}
				\item Modulation, coding, and beamforming to \textcolor{gray}{adapt to} the stochastic channel
				\item \gls{ris} can \textcolor{blue}{shape and control} the channel
			\end{itemize}
		\end{block}
	\end{frame}

	\begin{frame}{What is \glsfmtshort{ris}?}
		A planar surface of controllable scattering elements for signal amplitude and phase manipulation \cite{Wu2020}.
		\begin{figure}
			\centering
			\includegraphics[width=0.65\textwidth]{../assets/viva/ris_architecture.pdf}
			\label{fg:ris_architecture}
		\end{figure}
		\begin{block}{Characteristics}
			\begin{itemize}
				\item Low-power and low-cost
				\item Negligible noise and latency
				\item Full-duplex without self-interference
				\item Programmable in real-time
			\end{itemize}
		\end{block}
	\end{frame}

	\begin{frame}{Ancestor of \glsfmtshort{ris}: Reflectarray antenna}
		% not parabolic with parallel phase front
		A reflectarray antenna consists of an array illuminated by a feeding antenna \cite{Deng2016}.
		\begin{figure}
			\centering
			\includegraphics[width=0.45\textwidth]{../assets/viva/reflectarray.png}
		\end{figure}
		A progressive phase shift can be applied to the unit cells (a.k.a. elements) to steer the beam direction.
	\end{frame}

	\begin{frame}{What is the difference in \glsfmtshort{ris}?}
		\begin{enumerate}
			\item Metamaterial enables \textcolor{blue}{real-time control} and \textcolor{blue}{unconventional bahavior}.
			\item Impinging waves can be \textcolor{blue}{partially refracted and reflected}.
			\item The feed can be \textcolor{blue}{mobile} while the surface is \textcolor{blue}{scalable and multi-functional}.
			\item Elements can be physically interconnected for \textcolor{blue}{cooperative wave scattering}.
		\end{enumerate}
		\begin{exampleblock}{Refraction}
			\begin{columns}[T]
				\begin{column}{.25\textwidth}
					\begin{figure}
						\centering
						\resizebox{\columnwidth}{!}{
							\input{../assets/viva/nim_focus.tex}
						}
					\end{figure}
				\end{column}
				% \hfill
				\begin{column}{.6\textwidth}
					\vspace{0.5cm}
					\begin{itemize}
						\item Negative index material can focus waves
						\item Amplitude and phase responses can be tuned by diodes and \glsfmtshort{fpga}
						\item Similar for wave reflection
					\end{itemize}
				\end{column}
			\end{columns}
		\end{exampleblock}
		\begin{exampleblock}{Reflection}
			\vspace{-1cm}
			\begin{figure}[H]
				\centering
				\subfloat[Incident wave\label{fg:wave_incident}]{
					\resizebox{!}{2.02cm}{
						\input{../assets/viva/wave_incident.tex}
					}
				}
				\subfloat[Reflected wave\label{fg:wave_reflected}]{
					\resizebox{!}{2cm}{
						\input{../assets/viva/wave_reflected.tex}
					}
				}
			\end{figure}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Use case: Beamforming}
		% \textcolor{blue}{Joint beamforming} design of \gls{ris} and transceiver for a specific performance measure \cite{Wu2020}.
		% \gls{ris} and transceiver \textcolor{blue}{joint beamforming} design for a specific performance measure \cite{Wu2020}.
		\textcolor{blue}{Beamforming} of \gls{ris} and transceiver can be jointly designed for a specific performance measure \cite{Wu2020}.
		\begin{figure}
			\centering
			\subfloat[Coverage extension]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_coverage.pdf}
				}
			}
			\subfloat[Security enhancement]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_security.pdf}
				}
			}
			\subfloat[Interference mitigation]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_interference.pdf}
				}
			}
			\\
			\subfloat[Assist \glsfmtshort{d2d} network]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_network.pdf}
				}
			}
			\subfloat[Assist information and power transfer]{
				\resizebox{!}{2.75cm}{
					\includegraphics{../assets/viva/ris_beamforming_swipt.pdf}
				}
			}
		\end{figure}
	\end{frame}

	\begin{frame}{Use case: Modulation}
		\gls{ris} can be used for backscatter \textcolor{blue}{modulation} by periodically switching the reflection pattern \cite{Hu2021a}.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{../assets/viva/ris_modulation.pdf}
		\end{figure}
	\end{frame}

	\begin{frame}{Use case: Channel shaping}
		\textcolor{blue}{Channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment \cite{Arslan2022}.
		\begin{figure}
			\centering
			\includegraphics[width=0.9\textwidth]{../assets/viva/ris_shaping.pdf}
		\end{figure}
	\end{frame}
\end{section}

\begin{section}{Beamforming: \glsfmtshort{ris}-Aided \glsfmtshort{swipt}}
	\begin{frame}{\glsfmtshort{ris}-aided \glsfmtshort{swipt}: Joint waveform and beamforming design}
		\begin{block}{Overview}
			\begin{itemize}\setlength\itemsep{20pt}
				\item \textit{What does this paper propose?}

				A single-user multi-carrier \gls{swipt} system aided by a passive \gls{ris}.
				\item \textit{How does it differ from previous work?}

				We consider waveform and beamforming design for practical receiver architectures under non-linear harvester and frequency-flat \gls{ris} models.
				\item \textit{What are the benefits?}

				It exploits the spatial-frequency domain and rectifier behavior to enlarge the \gls{r-e} region, achieving squared asymptotic performance than conventional designs.
			\end{itemize}
		\end{block}
	\end{frame}

	\begin{frame}{\glsfmtshort{wpt} via radio waves}
		\vspace{-0.5cm}
		\begin{table}
			\footnotesize
			\rowcolors{2}{gray!25}{white}
			\renewcommand{\arraystretch}{1.25}
			\resizebox{\linewidth}{!}{
				\begin{tabular}{c c c c c c}
					\toprule
					% \hiderowcolors
					Categories                   & Medium                     & Device                     & Power level                            & Frequency                                & Range                     \\ \midrule
					% \showrowcolors
					                             & Magnetic resonant coupling & Resonators                 & Up to \SI{10}{\W}                      & \si{\kHz} -- \si{\MHz}                   & \si{\m}                   \\
					\cellcolor{white}            & Inductive coupling         & Wire coils                 & Up to \SI{10}{\W}                      & \si{\Hz} -- \si{\MHz}                    & \si{\cm}                  \\
					\multirow{-3}{*}{Near-field} & Capacitive coupling        & Metal plates               & Up to \SI{1}{\W}                       & \si{\kHz} -- \si{\MHz}                   & \si{\mm}                  \\
					\cellcolor{white}            & \textcolor{blue}{\gls{rf} wave}  & \textcolor{blue}{Rectenna} & \textcolor{blue}{\si{\uW} -- \si{\mW}} & \textcolor{blue}{\si{\MHz} -- \si{\GHz}} & \textcolor{blue}{\si{\m}} \\
					\multirow{-2}{*}{Far-field}  & Light wave                 & Laser                      & \si{\uW} -- \si{\mW}                   & \si{\THz}                                & \si{\km}                  \\ \bottomrule
				\end{tabular}
			}
		\end{table}
		\vspace{-0.25cm}
		\begin{figure}[H]
			\centering
			\resizebox{\columnwidth}{!}{
				\input{../assets/viva/wpt_architecture.tex}
			}
			\label{fg:wpt_architecture}
		\end{figure}
		\vspace{-1em}
		The end-to-end \gls{wpt} efficiency is
		\begin{equation*}
			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \textcolor{orange}{\underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2}} \textcolor{blue}{\underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3}} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4}
		\end{equation*}
		where $\eta_2$ and $\eta_3$ models the channel and rectenna, respectively.
	\end{frame}

	\begin{frame}{Received signal and harvested power}
		The rectenna efficiency $\eta_3$ depends on its input waveform (power and shape).
		\begin{block}{Rectenna model}
			% \vspace{-0.25cm}
			% \begin{figure}[H]
			% 	\centering
			% 	\subfloat[Rectenna]{
			% 		\resizebox{0.35\columnwidth}{!}{
			% 			\input{../assets/viva/rectenna.tex}
			% 		}
			% 		\label{fg:rectenna}
			% 	}
			% 	\subfloat[Half-wave rectifier]{
			% 		\resizebox{0.35\columnwidth}{!}{
			% 			\input{../assets/viva/halfwave_rectifier.tex}
			% 		}
			% 		\label{fg:halfwave_rectifier}
			% 	}
			% \end{figure}
			% \vspace{-0.25cm}
			\begin{itemize}
				\item Linear region (constant $\eta_3$): $P_{\mathrm{DC}}^\mathrm{R} = \eta_3 P_\mathrm{RF}^\mathrm{R} = \eta_3 \mathbb{A}\bigl\{ \lvert y(t) \rvert^2 \bigr\}$
				\item Non-linear region: Taylor expansion on diode characteristic equation
				\vspace{-0.25cm}
				\begin{equation*}
					\arg_{x(t)} \max P_{\mathrm{DC}}^\mathrm{R} = \arg_{x(t)} \max z \triangleq \sum_{i=2,\text{even}}^{n_0} \beta_i \mathbb{A}\bigl\{ y^i(t) \bigr\},
					\vspace{-0.5cm}
				\end{equation*}
				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant and $n_0$ is the truncation order.
			\end{itemize}
		\end{block}
		\begin{alertblock}{In multi-carrier \glsfmtshort{wpt} \textellipsis}
			\begin{itemize}
				\item $n_0 \ge 4$ allows components to compensate each other for higher \gls{dc} power
				\item High \gls{papr} (e.g., multi-sine) is preferred \cite{Trotter2009}
			\end{itemize}
			\vspace{-0.5cm}
			\begin{figure}
				\centering
				\subfloat{
					\resizebox{!}{2.5cm}{
						\includegraphics{../assets/viva/multisine_frequency_domain.eps}
					}
				}
				\subfloat{
					\resizebox{!}{2.5cm}{
						\includegraphics{../assets/viva/multisine_time_domain.eps}
					}
				}
			\end{figure}
		\end{alertblock}
	\end{frame}

	\begin{frame}{From \glsfmtshort{wpt} to \gls{ris}-aided \glsfmtshort{swipt}}
		\begin{figure}[H]
			\centering
			\def\svgwidth{0.5\columnwidth}
			\input{../assets/viva/system.eps_tex}
		\end{figure}

		\begin{itemize}
			\item \gls{swipt} features shared signal, spectrum, and infrastructure
			\item \gls{ris} enhances the RF-to-RF efficiency $\eta_2$ which has been a major concern
		\end{itemize}
		\begin{block}{Transmit waveform}
			\begin{equation*}
				\mathbf{x}(t) = \Re \left\{\sum_{n=1}^N \Bigl(\mathbf{w}_{\mathrm{I},n} \cdot \underbrace{\tilde{x}_{\mathrm{I},n}(t) e^{\jmath 2{\pi}{f_n}{t}}}_\text{modulated}+\mathbf{w}_{\mathrm{P},n} \cdot \underbrace{e^{\jmath 2{\pi}{f_n}{t}}}_\text{multi-sine}\Bigr) \right\}
			\end{equation*}
		\end{block}
		\begin{block}{Frequency-flat \glsfmtshort{ris} model}
			\begin{equation*}
				\mathbf{h}_{n}^\mathsf{H} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{h}_{\mathrm{B},n}^\mathsf{H} \mathbf{\Theta} \mathbf{H}_{\mathrm{F},n}
			\end{equation*}
		\end{block}
	\end{frame}

	\begin{frame}{Performance analysis}
		\begin{block}{Receiver architectures}
			\vspace{-0.5cm}
			\begin{figure}
				\centering
				\subfloat[\gls{ts} receiver]{
					\resizebox{0.48\columnwidth}{!}{
						\input{../assets/viva/receiver_ts.tex}
					}
					\label{fg:receiver_ts}
				}
				\subfloat[\gls{ps} receiver]{
					\resizebox{0.48\columnwidth}{!}{
						\input{../assets/viva/receiver_ps.tex}
					}
					\label{fg:receiver_ps}
				}
			\end{figure}
		\end{block}
		\begin{block}{\glsfmtfull{r-e} region of \glsfmtshort{ps}}
			\vspace{-0.25cm}
			\begin{align*}
				R(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\rho) &= \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},\\
				z(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho) &= \sum_{i=2,\text{even}}^{n_0}{\beta_i}{\rho^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y^i(t)\right\}\right\}},
			\end{align*}
			\begin{equation*}
				\mathcal{C}_\mathrm{R-E}(P)\triangleq \Bigl\{(r,e) : 0 \le r \le R, \ 0 \le e \le z, \lVert{\mathbf{W}_{\mathrm{I}}}\rVert _\mathrm{F}^2/2 + \lVert{\mathbf{W}_{\mathrm{P}}}\rVert _\mathrm{F}^2/2 \le P \Bigr\}
			\end{equation*}
		\end{block}
	\end{frame}

	\begin{frame}{Joint waveform and beamforming design}
		\begin{block}{Problem formulation}
			\vspace{-0.25cm}
			\begin{maxi*}
				{\scriptstyle{\boldsymbol{\theta},\mathbf{W}_\mathrm{I},\mathbf{W}_\mathrm{P},\rho}}{z(\boldsymbol{\theta},\mathbf{W}_\mathrm{I},\mathbf{W}_\mathrm{P},\rho)}{}{}
				\addConstraint{\lVert{\mathbf{W}_{\mathrm{I}}}\rVert _\mathrm{F}^2/2 + \lVert{\mathbf{W}_{\mathrm{P}}}\rVert _\mathrm{F}^2/2\le{P}}
				\addConstraint{R(\boldsymbol{\theta},\mathbf{W}_\mathrm{I},\rho) \ge \bar{R}}
				\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}
				\addConstraint{0 \le \rho \le 1,}
			\end{maxi*}
		\end{block}
		\begin{exampleblock}{Solution by \glsfmtfull{bcd}}
			\begin{itemize}
				\item Optimally decouple the spatial and frequency domain design
				\begin{equation*}
					\mathbf{w}_{\mathrm{I/P}, n} = \underbrace{s_{\mathrm{I/P}, n}}_\text{frequency} \underbrace{\mathbf{p}_{\mathrm{I/P}, n}}_\text{spatial}
				\end{equation*}
				\item Active beamforming $\mathbf{p}$: \gls{mrt}
				\item Passive beamforming $\boldsymbol{\theta}$: \gls{sca}
				\item Power allocation $\mathbf{s}$ and splitting ratio $\rho$: \gls{gp}
			\end{itemize}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Simulation results: Number of subbands $N$}
		\begin{figure}
			\centering
			\subfloat[\gls{r-e} region]{
				\resizebox{0.45\columnwidth}{!}{
					\input{../assets/viva/re_subband.tex}
				}
			}
			\subfloat[Waveform amplitude]{
				\resizebox{0.45\columnwidth}{!}{
					\input{../assets/viva/waveform_subband.tex}
				}
			}
		\end{figure}
		\begin{itemize}
			\item Increasing $N$ reduces per-subband rate but boosts harvested energy
			\item Region is convex at small $N$ (favors \gls{ps}) and concave at large $N$ (favors \gls{ts})
			\item Dedicated multi-sine power waveform is unnecessary at small $N$
		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation results: Asymptotic behavior}
		\begin{figure}
			\centering
			\subfloat[Number of transmit antennas $M$]{
				\resizebox{0.45\columnwidth}{!}{
					\input{../assets/viva/scaling_tx.tex}
				}
			}
			\subfloat[Number of \gls{ris} elements $L$]{
				\resizebox{0.45\columnwidth}{!}{
					\input{../assets/viva/scaling_reflector.tex}
				}
			}
		\end{figure}
		\begin{itemize}
			\item Active beamforming: array gain $M$ and harvested power order $M^2$
			\item Passive beamforming: array gain $L^2$ and harvested power order $L^4$
			\item Superlinear thanks to coherent scattering and rectifier nonlinearity
		\end{itemize}
	\end{frame}
\end{section}

\begin{section}{Modulation: RIScatter}
	\begin{frame}{RIScatter: Unifying \gls{bc} and \glsfmtshort{ris}}
		\begin{block}{Overview}
			\begin{itemize}\setlength\itemsep{20pt}
				\item \textit{What does this paper propose?}

				RIScatter --- a batteryless cognitive radio that recycles ambient signal in an adaptive and customizable manner.
				\item \textit{How does it differ from previous work?}

				Backscatter modulation and passive beamforming are seamlessly integrated from the perspective of probability distribution.
				\item \textit{What are the benefits?}

				It supports cooperative and distributed deployment, avoids complex architecture and signal processing, and can be built over legacy systems.
			\end{itemize}
		\end{block}
	\end{frame}

	\begin{frame}{Node architecture}
		\vspace{-0.5cm}
		\begin{figure}
			\centering
			\subfloat[Block Diagram]{
				\resizebox{!}{2cm}{
					\input{../assets/viva/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[\glsentryshort{rfid} tag with harvester \cite{Molina-Farrugia2017}]{
				\resizebox{!}{2.5cm}{
					\includegraphics[width=0.9\linewidth]{../assets/viva/passive_tag_prototype.png}
				}
				\label{fi:passive_tag_prototype}
			}\\
			\subfloat[Equivalent Circuit]{
				\resizebox{0.7\linewidth}{!}{
					\input{../assets/viva/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
		\end{figure}
		Impinging waves can be used for powering, modulation, \textcolor{blue}{and beamforming.}
	\end{frame}

	\begin{frame}{Reflection coefficient}
		The node changes state by switching load impedance (and reflection coefficient)
		\begin{equation*}
			\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0}
		\end{equation*}
		\vspace{-0.25cm}
		\begin{figure}
			\centering
			\resizebox{0.6\columnwidth}{!}{
				\input{../assets/viva/time_structure.tex}
			}
		\end{figure}
		\vspace{-0.25cm}
		\begin{itemize}
			\item \gls{ris}: the state at a specific time is known (as a passive beamforming codeword) to the transceiver
			\begin{equation*}
				\Gamma_m = \exp(j \phi_m),
			\end{equation*}
			\item \gls{bc}: all states occur with equal probability (as part of information codeword) to be detected at the receiver
			\begin{equation*}
				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\end{equation*}
		\end{itemize}
	\end{frame}

	\begin{frame}{RIScatter system}
		\begin{table}
			\rowcolors{2}{gray!25}{white}
			\renewcommand{\arraystretch}{1.25}
			\resizebox{\linewidth}{!}{
				\begin{tabular}{c c c c c c}
					\toprule
					\hiderowcolors
					                       & Backscatter        & Ambient backscatter         & Symbiotic radio          & \gls{ris}           & RIScatter                        \\ \midrule
					\showrowcolors
					Information link(s)    & Backscatter        & Coexisting                  & Coexisting               & Primary             & Coexisting                       \\
					Primary on backscatter & Carrier            & Multiplicative interference & Spreading code           & ---                 & Energy uncertainty               \\
					Backscatter on primary & ---                & Multiplicative interference & Channel uncertainty      & Passive beamforming & Dynamic passive beamforming      \\
					Cooperative devices    & ---                & No                          & Transmitter and receiver & ---                 & Transmitter, nodes, and receiver \\
					Sequential decoding    & ---                & No                          & Primary-to-backscatter   & ---                 & Backscatter-to-primary           \\
					Reflection pattern by  & Information source & Information source          & Information source       & Channel             & Source, channel, and priority    \\
					Input distribution     & Equiprobable       & Equiprobable                & Equiprobable or Gaussian & Degenerate          & Flexible                         \\
					Load-switching speed   & Fast               & Slow                        & Slow                     & Quasi-static        & Arbitrary                        \\ \bottomrule
				\end{tabular}
			}
		\end{table}
		\begin{columns}
			\begin{column}{0.4\textwidth}
				\begin{figure}
					\centering
					\resizebox{\linewidth}{!}{
						\input{../assets/viva/riscatter.tex}
					}
					\label{fg:riscatter}
				\end{figure}
			\end{column}
			\begin{column}{0.5\textwidth}
				\begin{itemize}
						\item {\color{blue}Primary link:} active legacy transmission from an \gls{rf} source
						\item {\color{orange}Backscatter link:} passive free-ride transmission from RIScatter nodes
				\end{itemize}
			\end{column}
		\end{columns}
		RIScatter renders the node input distribution as a function of information source, \gls{csi}, and priority of coexisting links.
	\end{frame}

	\begin{frame}{Signal model}
		\begin{figure}[H]
			\centering
			\def\svgwidth{0.6\columnwidth}
			\input{../assets/viva/riscatter_network.pdf_tex}
			\label{fg:riscatter_network}
		\end{figure}
		Within each backscatter block, received signal at primary block $n$ is
		\begin{equation*}
			y[n] = \underbrace{\mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \textcolor{orange}{x_k}}_{\mathbf{h}^\mathsf{H}(\textcolor{orange}{x_{\mathcal{K}}})} \mathbf{w} \textcolor{blue}{s[n]} + v[n],
		\end{equation*}
		\vspace{-0.25cm}
		\begin{block}{Properties}
			\begin{enumerate}
				\item \textcolor{blue}{Primary} and \textcolor{orange}{backscatter} symbols are superimposed by {double modulation}
				\item Backscatter signal is much weaker due to {double fading}
				\item The spreading factor (i.e., symbol period ratio $N$) is usually large
				\item Each {state} is simultaneously part of information and beamforming {codeword}
				\item Reflection pattern over time is guided by input probability distribution
			\end{enumerate}
		\end{block}
	\end{frame}

	\begin{frame}{Low-Complexity Receiver}
		We propose a low-complexity receiver that exploits the aforementioned properties to avoid \gls{sic}.
		\begin{figure}[!t]
			\centering
			\subfloat{
				\resizebox{0.42\linewidth}{!}{
					\input{../assets/viva/receiver.tex}
				}
			}
			\subfloat{
				\resizebox{0.58\linewidth}{!}{
					\input{../assets/viva/energy_distribution.tex}
				}
			}
			\label{fg:receiver}
		\end{figure}
		\vspace{0.5cm}
		\begin{itemize}
			\item Accumulated receive energy $z=\sum_{n} \bigl\lvert y[n] \bigr\rvert^2$ follows Gamma distribution
			\item \textcolor{orange}{Backscatter detection} under primary uncertainty is part of \textcolor{blue}{channel training}
			\item Requires one energy comparison and re-encoding per backscatter symbol (much simpler than symbiotic radio with $N$ \gls{sic} and 1 combining)
		\end{itemize}
	\end{frame}

	\begin{frame}{Joint beamforming, input distribution, and energy detector design}
		\vspace{-0.125cm}
		\begin{block}{Achievable rate}
			\vspace{-0.25cm}
			\begin{align*}
				\sum_k R_{\text{B},k} &= \sum\nolimits_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum\nolimits_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log {P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}/{P(\hat{x}_{m_{\mathcal{K}}'})}\\
				R_{\text{P}} &= \sum\nolimits_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log \left(1 + \frac{\lvert \mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \mathbf{w} \rvert^2}{\sigma_w^2}\right)
			\end{align*}
		\end{block}
		\begin{block}{Problem formulation}
			\vspace{-0.25cm}
			\begin{maxi*}
				{\scriptstyle{\{\mathbf{p}_k\},\mathbf{w},\mathbf{t}}}{\rho R_\text{P} + (1-\rho) \sum\nolimits_{k} R_{\text{B},k}}{}{}
				\addConstraint{\mathbf{1}^\mathsf{T} \mathbf{p}_k=1,}{\quad \mathbf{p}_k \ge \mathbf{0},}{\quad \forall k}
				\addConstraint{t_{l-1} \le t_l,}{\quad t_l \ge 0,}{\quad \forall l}
				\addConstraint{\lVert \mathbf{w} \rVert^2 \le P,}{}{}
			\end{maxi*}
		\end{block}
		\begin{exampleblock}{Solution by \gls{bcd}}
			\begin{itemize}
				\item Input distribution $\{\mathbf{p}_k\}$: \gls{kkt}
				\item Active beamforming $\mathbf{w}$: \gls{pga}
				\item Energy decision threshold $\mathbf{t}$: \gls{dp}
			\end{itemize}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Simulation results: Input distribution}
		\begin{figure}[!t]
			\centering
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/input_distribution.tex}
				}
			}
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/distribution_weights.tex}
				}
			}
		\end{figure}
		\begin{itemize}
			\item \gls{bc} and \gls{ris} are special cases of RIScatter with uniform and degenerate input distribution
			\item Increasing $\rho$ from 0 to 1 creates a smooth transition from backscatter modulation to passive beamforming
		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation results: Rate region}
		\begin{figure}[!t]
			\centering
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/region_comparison.tex}
				}
			}
			\subfloat{
				\resizebox{0.48\linewidth}{!}{
					\input{../assets/viva/region_duration.tex}
				}
			}
		\end{figure}
		\begin{itemize}
			\item RIScatter backscatter rate is lower than symbiotic radio (due to energy detection) but higher than ambient backscatter (due to adaptive encoding)
			\item A large spreading factor $N$ improves backscatter \glsfmtshort{ber} but reduces data rate
			\item Active and passive transmission can share resource with mutual benefits
		\end{itemize}
	\end{frame}
\end{section}

\begin{section}{Shaping: \glsfmtshort{bd}-\glsfmtshort{ris} in \glsfmtshort{mimo}}
	\begin{frame}{Channel shaping using \glsfmtshort{ris}: From diagonal model to beyond}
		\begin{block}{Overview}
			\begin{itemize}\setlength\itemsep{20pt}
				\item \textit{What does this paper study?}

				To what extent can a passive \gls{ris} redistribute the singular values of a \gls{mimo} channel.
				\item \textit{How does it differ from previous work?}

				We consider a \gls{bd} architecture, depict the singular value region, derive analytical bounds, and solve the rate maximization problem.
				\item \textit{What are the benefits?}

				Channel shaping is ubiquitous for communication, sensing, and power transfer, which helps to decouple the \gls{ris}-transceiver design.
				We also propose an efficient and universal \gls{bd}-\gls{ris} design framework.
			\end{itemize}
		\end{block}
	\end{frame}

	\begin{frame}{Wave scattering model}
		\begin{block}{Diagonal \glsfmtshort{ris}}
			Each element acts as an individual scatterer with phase shift only
			\begin{equation*}
				\mathbf{\Theta} = \mathrm{diag}(\theta_1, \ldots, \theta_{N_\mathrm{S}}) = \mathrm{diag}(e^{\jmath \phi_1}, \ldots, e^{\jmath \phi_{N_\mathrm{S}}})
				%  =
				% \begin{bsmallmatrix}
				% 	\theta_1 & 0 & \cdots & 0 \\
				% 	0 & \theta_2 & \cdots & 0 \\
				% 	\vdots & \vdots & \ddots & \vdots \\
				% 	0 & 0 & \cdots & \theta_{N_\mathrm{S}}
				% \end{bsmallmatrix}
				\label{eq:diagonal_scattering_matrix}
			\end{equation*}
		\end{block}

		\begin{block}{\glsfmtshort{bd}-\glsfmtshort{ris}}
			Each group contains $L$ connected elements, allowing amplitude and phase control
			\vspace{-0.25cm}
			\begin{equation*}
				\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G), \quad \mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}_L, \quad \forall g
				\label{eq:bd_ris}
			\end{equation*}
			\vspace{-0.5cm}
			\begin{itemize}
				\item \emph{Subchannel rearrangement:} allows each group to rearrange and combine the backward and forward subchannels by strength
				\vspace{-0.25cm}
				\begin{equation*}
					\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert \to \sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert
					\vspace{-0.25cm}
				\end{equation*}
				\item \emph{Subspace alignment:} rotate backward-forward (intra-group, multiplicative) and direct-indirect (inter-group, additive) singular vectors
				\vspace{-0.25cm}
				\begin{equation*}
					\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{\Theta}_g \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}
					\label{eq:channel_equivalent_svd}
				\end{equation*}
			\end{itemize}
		\end{block}
	\end{frame}

	\begin{frame}{Some concepts in differential geometry}
		The feasible domain of $\mathbf{\Theta}_g$ is a unitary Lie group $U(L)$ with Lie algebra $\mathfrak{u}(L)$.
		\vspace{0.25em}
		\begin{itemize}
			\item \emph{Geodesic:} shortest path between two points on a manifold
			\item \emph{Lie group:} a group that is also a differentiable manifold
			\item \emph{Lie algebra:} tangent space of Lie group at the identity element
			% \item \emph{Exponential map:} maps the Lie algebra to the Lie group
		\end{itemize}
		\begin{figure}
			\centering
			\includegraphics[width=0.65\textwidth]{../assets/viva/lie_group.pdf}
		\end{figure}
		A geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ can be described by the exponential map
		\begin{equation*}
			\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D})
			\label{eq:geodesic_identity}
		\end{equation*}

	\end{frame}

	\begin{frame}{Geodesic \glsfmtshort{rcg} via Lie algebra}
		\begin{block}{Non-geodesic vs geodesic \gls{rcg}}
			\begin{itemize}
				\item Non-geodesic: add then retract
				\begin{equation*}
					\bar{\mathbf{\Theta}}_g^{(r+1)} = \mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)}, \quad \mathbf{\Theta}_g^{(r+1)} = \bar{\mathbf{\Theta}}_g^{(r+1)} \bigl({\bar{\mathbf{\Theta}}_g^{(r+1)\mathsf{H}}} \bar{\mathbf{\Theta}}_g^{(r+1)}\bigr)^{-1/2}
				\end{equation*}
				\item Geodesic: multiplicative and rotational update
				\begin{equation*}
					\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}
					\label{eq:update_geodesic}
				\end{equation*}
			\end{itemize}
		\end{block}
		\begin{exampleblock}{Performance comparison}
			\begin{table}
				\label{tb:complexity_test}
				\centering
				\tiny
				\begin{tabular}{ccccccc}
					\toprule
					\multirow{2}{*}{\gls{rcg} path} & \multicolumn{3}{c}{$N_\mathrm{S}=16$} & \multicolumn{3}{c}{$N_\mathrm{S}=256$}                                                               \\ \cmidrule(lr){2-4} \cmidrule(lr){5-7}
													& Objective                             & Iterations                             & Time [s]         & Objective        & Iterations & Time [s] \\ \midrule
					Geodesic                        & $\num{4.359e-3}$                      & 11.59                                  & $\num{1.839e-2}$ & $\num{1.163e-2}$ & 25.58      & 3.461    \\
					Non-geodesic                    & $\num{4.329e-3}$                      & 30.92                                  & $\num{5.743e-2}$ & $\num{1.116e-2}$ & 61.40      & 13.50    \\ \bottomrule
				\end{tabular}
			\end{table}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Singular value redistribution: Optimization approach}
		\begin{block}{Pareto frontier of singular values}
			\begin{maxi*}
				{\scriptstyle{\mathbf{\Theta}}}{\sum_n \rho_n \sigma_n(\mathbf{H})}{}{}
				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I},}{\quad \forall g,}{}
			\end{maxi*}
		\end{block}
		\begin{exampleblock}{Solution by group-wise geodesic \glsfmtshort{rcg}}
			\begin{itemize}
				\item Faster convergence thanks to appropriate parameter space
				\item Step size $\mu$ can be obtained by the Armijo rule
				\item Doubling $\mu$ is computationally efficient $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$
			\end{itemize}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Singular value redistribution: Analysis approach}
		\fontsize{6pt}{7.2}\selectfont
		\begin{proposition}[Degree of freedom]\label{pp:dof}
			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
		\end{proposition}
		\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
			If the forward or backward channel is rank-$k$ ($k \le N$), then regardless of the passive \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
			\begin{align*}
				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k,         \\
				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1,
			\end{align*}
			where
			\begin{equation*}
				\mathbf{T} \mathbf{T}^\mathsf{H} =
				\begin{cases}
					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
				\end{cases}
				\label{eq:auxiliary_matrix}
			\end{equation*}
			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
		\end{proposition}
		\begin{proposition}[Unitary \gls{ris} without direct link]\label{pp:fully_connected}
			If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the channel singular values can be manipulated up to
			\begin{equation*}
				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
			\end{equation*}
			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
		\end{proposition}
	\end{frame}

	\begin{frame}{Achievable rate maximization}
		\begin{block}{Problem formulation}
			\begin{maxi*}
				{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{}{}
				\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g.}
			\end{maxi*}
		\end{block}
		\begin{exampleblock}{Local-optimal solution: \gls{bcd}}
			\begin{itemize}
				\item Passive beamforming $\mathbf{\Theta}$: group-wise geodesic \gls{rcg}
				\item Active beamforming $\mathbf{W}$: eigenmode transmission and water-filling
			\end{itemize}
		\end{exampleblock}
		\begin{exampleblock}{Low-complexity solution: two-stage}
			\begin{itemize}
				\item Shaping stage: channel power gain maximization, solved in closed form
				\item Transmission stage: eigenmode transmission and water-filling
			\end{itemize}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Simulation results: Singular value}
		\begin{figure}
			\centering
			\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
				\resizebox{!}{3cm}{
					\input{../assets/viva/singular_pareto_sx32.tex}
				}
			}
			\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
				\resizebox{!}{3cm}{
					\input{../assets/viva/singular_pareto_sx128.tex}
				}
			}
			\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank2_sx128}]{
				\resizebox{!}{3cm}{
					\input{../assets/viva/singular_bound_rank2_sx128.tex}
				}
			}
			\label{fg:singular_bound}
		\end{figure}
		\vspace{1em}
		\begin{itemize}
			\item \gls{bd}-\gls{ris} provides \qty{22}{\percent} and \qty{38}{\percent} dynamic range gain for $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$
			\item Increasing group size enlarges singular value region with better trade-off
			\item Asymptotic bounds in rank-deficient channels are valid for both architectures
		\end{itemize}
	\end{frame}

	\begin{frame}{Simulation results: Achievable rate}
		\begin{figure}
			\centering
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
				\resizebox{!}{2.9cm}{
					\input{../assets/viva/rate_beamforming.tex}
				}
			}
			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
				\resizebox{!}{2.9cm}{
					\input{../assets/viva/rate_txrx.tex}
				}
			}
			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
				\resizebox{!}{2.9cm}{
					\input{../assets/viva/rate_sx.tex}
				}
			}
			\label{fg:rate}
		\end{figure}
		\vspace{1em}
		\begin{itemize}
			\item Deficit from low-complexity design vanishes as \gls{ris} evolves towards unitary
			\item \gls{bd}-\gls{ris} can activate multiple streams at lower transmit power
			\item Percentage rate gain of \gls{bd}-\gls{ris} scales with \gls{mimo} dimension and group size
		\end{itemize}
	\end{frame}
\end{section}

\begin{section}{Outro}
	\begin{frame}{Future works: I}
		\begin{block}{Coherent RIScatter detector}
			\begin{equation*}
				y[n] = {\mathbf{h}_{\text{D}}^\mathsf{H} + \mathbf{h}_{\text{C}}^\mathsf{H} {x}} \mathbf{w} {s[n]} + v[n],
			\end{equation*}
			\begin{itemize}
				\item Same model as index modulation
				\item $x$ has finite support $\to$ $y[n]$ is a Gaussian mixture (non-elementary entropy)
				\item Achievable rate can be approximated as
				\begin{equation*}
					R_\text{B} = \sum_i p(x_i) \log \sum_j p(x_j) \frac{4 \sigma_i^2 \sigma_j^2}{(\sigma_i^2 + \sigma_j^2)^2}
				\end{equation*}
				\item \gls{ber} performance?
				\item Code-domain \gls{noma}?
			\end{itemize}
		\end{block}
	\end{frame}

	\begin{frame}{Future works: II}
		\begin{block}{Multiplicative broadcast channel}
			The received signal is
			\begin{equation*}
				y_k = h_k \prod_q x_q + n.
			\end{equation*}
			\begin{itemize}
				\item \gls{sic} $\to$ successive channel refinement (better symbol-level precoding)
				\item \textcolor{blue}{Log-normal} is also maximum entropy distribution
				\item Product of log-normal is log-normal
			\end{itemize}
		\end{block}

		\begin{exampleblock}{Index modulation is a special case with superuser $R = R_1 + R_2$}
			\begin{itemize}
				\item $x_1 \sim \mathcal{CN}(0, \sigma_1^2)$ and $x_2$ with finite support
				\item Index message encoded in the Euclidean distance between $h x_2^{(i)}$
				\item Decode $x_2$ first, rate depends on {entropy of Gaussian mixture}
			\end{itemize}
		\end{exampleblock}
	\end{frame}

	\begin{frame}{Future works: III}
		\begin{block}{Rate splitting $\times$ index modulation}
			The received signal is
			\begin{equation*}
				y_k = h_k \theta \sum_q x_q + n.
			\end{equation*}
			\vspace{-1em}
			\begin{itemize}
				\item Dynamic \gls{ris} achieves the convex hull below by time-sharing \cite{Mu2021a}
				\begin{figure}
					\centering
					\subfloat{
						\resizebox{0.4\columnwidth}{!}{
							\includegraphics[scale=1]{../assets/viva/rate_region_noma.jpg}
						}
					}
					\subfloat{
						\resizebox{0.4\columnwidth}{!}{
							\includegraphics[scale=1]{../assets/viva/rate_region_oma.jpg}
						}
					}
				\end{figure}
				\item Common message can be embedded in $\theta$ to push the boundary
			\end{itemize}
		\end{block}
	\end{frame}

	\begin{frame}{Future works: III}
		\begin{block}{Feasibility of interference alignment by \gls{ris}}
			\begin{align*}
				&\text{find} && \mathbf{\Theta} &&&\\
				&\text{s.t.} && \mathbf{H}^{[kj]} = \mathbf{H}_\mathrm{D}^{[kj]} + \mathbf{H}_\mathrm{B}^{[k]} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{[j]} = \mathbf{0}, &&& \forall j \neq k\\
				& && \mathrm{rank}(\mathbf{H}^{[kk]}) = d_k, &&& \forall k
			\end{align*}
			\begin{itemize}
				\item Necessary and sufficient feasibility conditions?
				\item How many scattering elements are required on expectation?
				\item Multi-sector \gls{bd}-\gls{ris} \cite{Li2023c}?
			\end{itemize}
		\end{block}
	\end{frame}

\end{section}
% \end{section}

% \begin{section}{Research Proposal}
% 	\begin{subsection}{STAR-RIS: Interference Alignment}
% 		\begin{frame}{STAR-RIS in Interference Channel (I)}
% 			Consider a STAR-RIS-aided interference \gls{mimo} of $K$ transmitter-receiver pairs.
% 			\begin{block}{Leakage interference minimization}
% 				\vspace{-2em}
% 				\begin{mini!}
% 					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \bigl\lVert \mathbf{G}_k \underbrace{(\mathbf{H}^{[kj]}_\mathrm{D} + \mathbf{H}^{[k]}_\mathrm{B} \mathbf{\Theta}^{[kj]} \mathbf{H}^{[j]}_{\mathrm{F}})}_{\triangleq \mathbf{H}^{[kj]}} \mathbf{W}_j \bigr\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
% 					\addConstraint{\mathbf{\Theta}_{\mathrm{T},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{T},g}+\mathbf{\Theta}_{\mathrm{R},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{R},g}=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
% 					\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
% 					\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
% 				\end{mini!}
% 			\end{block}

% 			\begin{block}{Feasibility of interference alignment}
% 				\vspace{-1em}
% 				\begin{subequations}
% 					\begin{align}
% 						&\text{find} && \mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\} &&&\\
% 						&\text{s.t.} && \mathbf{G}_k \mathbf{H}^{[kj]} \mathbf{W}_j = \mathbf{0}, &&& \forall j \neq k\\
% 						& && \mathrm{rank}(\mathbf{G}_k \mathbf{H}^{[kk]} \mathbf{W}_k) = d_k, &&& \forall k
% 					\end{align}
% 				\end{subequations}
% 			\end{block}
% 		\end{frame}

% 		\begin{frame}{STAR-RIS in Interference Channel (II)}
% 			\begin{block}{Weighted sum-rate maximization}
% 				\vspace{-2em}
% 				\begin{maxi!}
% 					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{\sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{[kj]}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kj]}} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
% 					\addConstraint{\mathbf{\Theta}_{\mathrm{T},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{T},g}+\mathbf{\Theta}_{\mathrm{R},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{R},g}=\mathbf{I}, \quad}{\forall g}{}
% 					\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k, \quad}{\forall k,}{}
% 				\end{maxi!}
% 				where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
% 				\begin{equation*}
% 					\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H} + \eta \mathbf{I},
% 				\end{equation*}
% 			\end{block}
% 		\end{frame}
% 	\end{subsection}

% 	\begin{subsection}{NOMA: Index Modulation}
% 		\begin{frame}{\glsfmtlong{im} is a Multiplicative NOMA}
% 			\begin{block}{Multiplicative broadcast channel}
% 				The received signal is
% 				\begin{equation*}
% 					y_k = h_k \prod_q x_q + n.
% 				\end{equation*}
% 				\begin{itemize}
% 					\item \gls{sic} $\to$ successive channel refinement (better symbol-level precoding)
% 					\item \textcolor{blue}{Log-normal} is also maximum entropy distribution
% 					\item Product of log-normal is log-normal
% 				\end{itemize}
% 			\end{block}

% 			\begin{exampleblock}{Index modulation is a special case with superuser $R = R_1 + R_2$}
% 				\begin{itemize}
% 					\item $x_1 \sim \mathcal{CN}(0, \sigma_1^2)$ and $x_2$ with finite support
% 					\item Index message encoded in the Euclidean distance between $h x_2^{(i)}$
% 					\item Decode $x_2$ first, rate depends on \textcolor{blue}{entropy of Gaussian mixture}
% 				\end{itemize}
% 			\end{exampleblock}
% 		\end{frame}

% 		\begin{frame}{Multiplicative NOMA: Another Example}
% 			\begin{block}{Joint transmitter-\gls{ris} encoding}
% 				The received signal is
% 				\begin{equation*}
% 					y_k = h_k \theta \sum_q x_q + n.
% 				\end{equation*}
% 				\vspace{-1em}
% 				\begin{itemize}
% 					\item Dynamic \gls{ris} can achieve the convex hull of static \gls{ris} \cite{Mu2021a}
% 					\begin{figure}
% 						\centering
% 						\subfloat{
% 							\resizebox{0.4\columnwidth}{!}{
% 								\includegraphics[scale=1]{assets/rate_region_noma.jpg}
% 							}
% 						}
% 						\subfloat{
% 							\resizebox{0.4\columnwidth}{!}{
% 								\includegraphics[scale=1]{assets/rate_region_oma.jpg}
% 							}
% 						}
% 					\end{figure}
% 					\item Joint encoding rides additional information on $\theta$ as ``common message''
% 				\end{itemize}
% 			\end{block}
% 		\end{frame}
% 		\begin{frame}{Thank You}
% 			\begin{figure}
% 				\centering
% 				\includegraphics[width=0.8\columnwidth]{assets/ris.jpg}
% 			\end{figure}
% 		\end{frame}
% 	\end{subsection}
% \end{section}

\bibliographystyle{IEEEtran}
\bibliography{../misc/library.bib}
\end{document}

### 2024-05-01 assets/chapter_3/channel_amplitude.tex
:triangular_flag_on_post: Viva

@@
 %
-\begin{tikzpicture}
+\begin{tikzpicture}[font=\footnotesize]
 
@@
 legend style={at={(0.5,1.03)}, anchor=south, legend columns=3, legend cell align=left, align=left, draw=white!15!black},
-title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
+scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
 ]
@@
 ymajorgrids,
-title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}, scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
+scaled y ticks=false, yticklabel=\pgfkeys{/pgf/number format/.cd,fixed,precision=2}\pgfmathprintnumber{\tick}
 ]

### 2024-05-01 assets/chapter_3/convergence_bcd.tex
:triangular_flag_on_post: Viva

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=1.399in,
at={(0.677in,2.455in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
ymin=0,
ymax=23.9521333022272,
ylabel style={font=\color{white!15!black}},
ylabel={DC [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	2.22044604925031e-10\\
2	23.9477142509994\\
3	23.9521333022272\\
4	23.9521333022272\\
5	23.9521333022272\\
6	23.9521333022272\\
7	23.9521333022272\\
8	23.9521333022272\\
9	23.9521333022272\\
10	23.9521333022272\\
11	23.9521333022272\\
12	23.9521333022272\\
13	23.9521333022272\\
14	23.9521333022272\\
15	23.9521333022272\\
};
\addlegendentry{BCD}

\end{axis}

\begin{axis}[%
width=4.036in,
height=1.399in,
at={(0.677in,0.472in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
xlabel style={font=\color{white!15!black}},
xlabel={Iteration index},
ymin=0,
ymax=23.4661978529908,
ylabel style={font=\color{white!15!black}},
ylabel={DC [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	2.22044604925031e-10\\
2	23.4267512312375\\
3	23.4652236267543\\
4	23.4661978529908\\
5	23.4661978529908\\
6	23.4661978529908\\
7	23.4661978529908\\
8	23.4661978529908\\
9	23.4661978529908\\
10	23.4661978529908\\
11	23.4661978529908\\
12	23.4661978529908\\
13	23.4661978529908\\
14	23.4661978529908\\
15	23.4661978529908\\
};
\addlegendentry{LC-BCD}

\end{axis}
\end{tikzpicture}%

### 2024-05-01 assets/chapter_3/convergence_sca.tex
:triangular_flag_on_post: Viva

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
%
\begin{tikzpicture}

\begin{axis}[%
width=3.972in,
height=1.383in,
at={(0.666in,2.433in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
ymin=23.6,
ymax=24,
ylabel style={font=\color{white!15!black}},
ylabel={DC [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	23.6339898147867\\
2	23.9359168430033\\
3	23.9359212944279\\
4	23.9359212944279\\
5	23.9359212944279\\
6	23.9359212944279\\
7	23.9359212944279\\
8	23.9359212944279\\
9	23.9359212944279\\
10	23.9359212944279\\
11	23.9359212944279\\
12	23.9359212944279\\
13	23.9359212944279\\
14	23.9359212944279\\
15	23.9359212944279\\
};
\addlegendentry{SCA}

\end{axis}

\begin{axis}[%
width=3.972in,
height=1.383in,
at={(0.666in,0.472in)},
scale only axis,
xmin=1,
xmax=15,
xtick={ 1,  5, 10, 15},
xlabel style={font=\color{white!15!black}},
xlabel={Iteration index},
ymin=23.1,
ymax=23.4267428478373,
ylabel style={font=\color{white!15!black}},
ylabel={DC [$\mu$A]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.97,0.03)}, anchor=south east, legend cell align=left, align=left, draw=white!15!black},
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}, /pgf/number format/.cd,fixed,precision=4
]
\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	23.1650475635163\\
2	23.4267359303359\\
3	23.4267428478373\\
4	23.4267428478373\\
5	23.4267428478373\\
6	23.4267428478373\\
7	23.4267428478373\\
8	23.4267428478373\\
9	23.4267428478373\\
10	23.4267428478373\\
11	23.4267428478373\\
12	23.4267428478373\\
13	23.4267428478373\\
14	23.4267428478373\\
15	23.4267428478373\\
};
\addlegendentry{M-SCA}

\end{axis}
\end{tikzpicture}%

### 2024-05-01 assets/chapter_4/discrete_outputs.tex
:triangular_flag_on_post: Viva

\begin{tikzpicture}[font=\scriptsize]
	\begin{axis}[width=10cm,height=5cm,xmin=0,xmax=6.5,ymin=-0.1,ymax=0.1,xlabel=$z$,axis x line=middle,axis y line=none,xtick={0,2,3,4,6},xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},xtick style={draw=none},every axis x label/.style={at=(current axis.right of origin),anchor=west},domain=0:6]
		\addplot[mark=*,mark size=0.5pt,only marks,color=gray] {0};
		\addplot[mark=*,mark size=1pt,only marks,color=black] coordinates{(0,0) (2,0) (3,0) (4,0) (6,0)};
		\draw[decorate,decoration={brace,amplitude=10}] (0,0) -- (2,0) node[above,midway,yshift=10]{$\mathcal{R}_1$};
		\draw[decorate,decoration={brace,amplitude=10}] (2,0) -- (3,0) node[above,midway,yshift=10]{$\mathcal{R}_2$};
		\draw[decorate,decoration={brace,amplitude=10}] (3,0) -- (4,0) node[above,midway,yshift=10]{$\mathcal{R}_3$};
		\draw[decorate,decoration={brace,amplitude=10}] (4,0) -- (6,0) node[above,midway,yshift=10]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

### 2024-05-01 assets/chapter_4/energy_distribution.tex
:triangular_flag_on_post: Viva

\definecolor{color1}{HTML}{0072BD}
\definecolor{color2}{HTML}{D95319}
\definecolor{color3}{HTML}{EDB120}
\definecolor{color4}{HTML}{7E2F8E}

\begin{tikzpicture}[font=\scriptsize]
	\begin{axis}[
			clip mode=individual,
			height=4cm,
			width=10cm,
			xlabel = $z$,
			ylabel = {Probability Density},
			no markers,
			xmin=0,
			ymin=0,
			xmax=70,
			xtick={0,12.78,20.28,29.62,70},
			xticklabels={$t_0$,$t_1$,$t_2$,$t_3$,$t_4$},
			yticklabels=\empty,
			samples = 200
		]

		\addplot+[very thick,solid,color1] gnuplot[raw gnuplot,smooth] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,1)};
		\addlegendentryexpanded{$f(z \mid x_1)$}

		\addplot+[very thick,dashed,color2] gnuplot[raw gnuplot,smooth] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.6)};
		\addlegendentryexpanded{$f(z \mid x_2)$}

		\addplot+[very thick,dotted,color3] gnuplot[raw gnuplot,smooth] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.4)};
		\addlegendentryexpanded{$f(z \mid x_3)$}

		\addplot+[very thick,dashdotted,color4] gnuplot[raw gnuplot,smooth] {%
				isint(x) = (int(x)==x);
				gmm(x,rho,lambda)=rho<=0||lambda<=0?1/0:  x<0?0.0:x==0?(rho>1?0.0:rho==1?real(lambda):1/0):  exp(rho*log(lambda)+(rho-1.0)*log(x)-lgamma(rho)-lambda*x);
				set xrange [0:80];
				set yrange [0:1];
				samples=200;
				plot gmm(x,10,0.28)};
		\addlegendentryexpanded{$f(z \mid x_4)$}
		\draw[latex-latex] (0,0) -- (12.78,0) node[above,midway,yshift=-2]{$\mathcal{R}_1$};
		\draw[latex-latex] (12.78,0) -- (20.28,0) node[above,midway,yshift=-2]{$\mathcal{R}_2$};
		\draw[latex-latex] (20.28,0) -- (29.62,0) node[above,midway,yshift=-2]{$\mathcal{R}_3$};
		\draw[latex-latex] (29.62,0) -- (70,0) node[above,midway,yshift=-2]{$\mathcal{R}_4$};
	\end{axis}
\end{tikzpicture}

### 2024-05-01 assets/chapter_4/equivalent_circuit.tex
:triangular_flag_on_post: Viva

\begin{circuitikz}[transform shape,font=\large]
	% \tikzstyle{every node}=[font=\Large]
	\draw (0,0) coordinate(O)
	to [sV,l=$V_0$] ++(0,1.5)
	to [L,l=$X_{\text{A}}$] ++(0,1.5)
	to [R=$R_{\text{A}}$,-*] ++(3,0) coordinate(AM)
	to [sI,l_=$I_0$,-*] ++(0,-3)
	to [short] (O);
	\draw (AM)
	to [short] ++(0.5,0)
	to [L,l=$X_m$,-*] ++(3,0) coordinate(M)
	to [R=$R_{\text{S},m}$] ++(3,0) coordinate(MH);
	\draw (M)
	to [R=$R_{\text{P},m}$,-*] ++(0,-3);
	\draw (MH)
	to [D,-*] ++(1.5,0) coordinate(H)
	to [C=$X_{\text{H}}$,-*] ++(0,-3);
	\draw (H)
	to [short] ++(1.5,0)
	to [R=$R_{\text{H}}$] ++(0,-3)
	to [short] (O);

	\draw [dashed] (-1.125,-0.5) rectangle (3.5,4);
	\draw [dashed] (4,-0.5) rectangle (9,4);
	\draw [dashed] (9.5,-0.5) rectangle (13.5,4);

	\draw (1.125,4.25) node[]{Antenna};
	\draw (6.5,4.25) node[]{Modulator};
	\draw (11.5,4.25) node[]{Harvester \& Chip};

	\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\text{A}}$] (3.125,3.175);
	\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_m$] (4.375,0.375);
	\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\text{H}}$] (9.875,0.375);
\end{circuitikz}

### 2024-05-01 assets/chapter_4/input_distribution.tex
:triangular_flag_on_post: Viva

\begin{tikzpicture}[font=\footnotesize]
	\begin{groupplot}
		[group style={
					rows=3,
					group name=plots,
					x descriptions at=edge bottom,
					y descriptions at=edge left,
					vertical sep=10
				},
			ybar,
			xmin=0,
			xmax=4,
			xtick={1,2,3,4},
			ymin=0,
			ymax=1,
			xlabel={Reflection State},
			enlarge x limits={value=0.25,upper},
			enlarge y limits={value=0.1,upper},
			width=10cm,
			height=2.6cm,
			every axis plot/.append style={bar shift=0}
		]
		\nextgroupplot
		\addplot[blue,fill=blue!30!white] coordinates {(-1,-1)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0.25)};
		\addplot[blue,fill=blue!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0.25)};
		\legend{BackCom}
		\nextgroupplot[ylabel={Probability Distribution}]
		\addplot[red,fill=red!30!white] coordinates {(-1,-1)};
		\addplot[red,fill=red!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,1)};
		\addplot[red,fill=red!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
		\addplot[red,fill=red!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0)};
		\legend{RIS}
		\nextgroupplot
		\addplot[brown,fill=brown!30!white] coordinates {(-1,-1)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north west lines},pattern color=.] coordinates {(1,0.25)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=north east lines},pattern color=.] coordinates {(2,0.75)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=vertical lines},pattern color=.] coordinates {(3,0)};
		\addplot[brown,fill=brown!30!white,postaction={pattern=horizontal lines},pattern color=.] coordinates {(4,0)};
		\legend{RIScatter}
	\end{groupplot}
\end{tikzpicture}

### 2024-05-01 assets/chapter_4/region_comparison.tex
:triangular_flag_on_post: Viva

--- 2024-04-30 assets/viva/region_comparison.tex
@@
 \begin{axis}[%
-	width=4.079in,
-	height=3.432in,
+width=4.014in,
+height=1.552in,
 at={(0.673in,0.356in)},
@@
 ylabel style={font=\color{white!15!black}},
-ylabel={Backscatter Rate [bits/BB]},
+ylabel={Backscatter\\Rate [bits/BB]},
 axis background/.style={fill=white},
@@
 align=center,
-title style={font=\huge},
-label style={font=\huge},
-ticklabel style={font=\LARGE},
-legend style={font=\LARGE},
+% title style={font=\LARGE},
+% label style={font=\LARGE},
+% ticklabel style={font=\Large},
+% legend style={font=\Large},
 reverse legend,

### 2024-05-01 assets/chapter_4/scatter_model.tex
:triangular_flag_on_post: Viva

\begin{circuitikz}[transform shape,font=\scriptsize]
	% \tikzstyle{every node}=[font=\large]
	\ctikzset{multipoles/rotary/arrow=both}
	\draw (0,0) node[bareantenna](bareantenna){};
	\draw (bareantenna.west) ++(-1,0) node[waves](WI){};
	\draw (WI.north east) ++(0.25,0) node{$\vec{E}_{\text{I}}$};
	\draw (WI.south east) ++(0.25,0) node{$\vec{H}_{\text{I}}$};
	\draw (bareantenna.east) ++(0.5,0) node[waves](WR){};
	\draw (WR.north east) ++(0.35,0) node{$\vec{E}_m$};
	\draw (WR.south east) ++(0.35,0) node{$\vec{H}_m$};
	\draw (bareantenna) to ++(0,-1.1) to [generic,l=$Z_{\text{A}}$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.3,0) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=0](SW){};
	\draw (SW.cout 1) to ++(0.625,+0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E1);
	\draw (SW.cout 2) node[above right]{$m$} to [generic,l=$Z_m$,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E2);
	\draw (SW.cout 3) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E3);
	\draw (SW.cout 4) to ++(0.625,-0.5) to [generic,/tikz/circuitikz/bipoles/length=0.75cm] ++(2.2,0) coordinate(E4);
	\draw (E1) to[short,-*] (E2);
	\draw (E2) to[short,-*] (E3);
	\draw (E3) to[short] (E4);
	\draw (E2) to[short] ++(0.2,0) node[ground,rotate=90]{};
\end{circuitikz}

### 2024-05-01 assets/chapter_4/time_structure.tex
:triangular_flag_on_post: Viva

\begin{tikzpicture}[font=\footnotesize]
	% MBC/BBC
	\foreach \x in {0}{
			\draw[blue,ultra thick,postaction={pattern=north west lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
		}
	\foreach \x in {1}{
			\draw[blue,ultra thick,postaction={pattern=north east lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
		}
	\foreach \x in {2}{
			\draw[blue,ultra thick,postaction={pattern=vertical lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
		}
	\foreach \x in {3}{
			\draw[blue,ultra thick,postaction={pattern=horizontal lines},pattern color=.] (2*\x,4) rectangle ++(2,0.25);
		}
	\draw[latex-latex] (0,4.35) -- (2,4.35) node[above,midway]{BB};
	\node at (-1.5,4.125) {MBC/BBC};

	% AmBC/SR
	\foreach \x in {0,...,7}{
			\draw[teal,fill=teal!35!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {8,...,15}{
			\draw[teal,fill=teal!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,3) rectangle ++(0.5,0.25);
		}
	\foreach \x in {0,...,1}{
			\draw[teal,ultra thick] (4*\x,3) rectangle ++(4,0.25);
		}
	\draw[latex-latex] (0,3.35) -- (4,3.35) node[above,midway]{BB};
	\draw[latex-latex] (0,2.9) -- (0.5,2.9) node[below,midway]{PB};
	\node at (-1.5,3.125) {AmBC/SR};

	% RIS
	\foreach \x in {0,...,15}{
			\draw[red,fill=red!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,2) rectangle ++(0.5,0.25);
		}
	\draw[red,ultra thick] (0,2) rectangle ++(8,0.25);
	\draw[latex-latex] (0,2.35) -- (8,2.35) node[above,midway]{CB};
	\draw[latex-latex] (0,1.9) -- (0.5,1.9) node[below,midway]{PB};
	\node at (-1.5,2.125) {RIS};

	% RIScatter
	\foreach \x in {0,...,3}{
			\draw[brown,fill=brown!35!white,postaction={pattern=north west lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {4,...,15}{
			\draw[brown,fill=brown!35!white,postaction={pattern=north east lines},pattern color=.] (0.5*\x,1) rectangle ++(0.5,0.25);
		}
	\foreach \x in {0,...,3}{
			\draw[brown,ultra thick] (2*\x,1) rectangle ++(2,0.25);
		}
	\draw[latex-latex] (0,1.35) -- (2,1.35) node[above,midway]{BB};
	\draw[latex-latex] (0,0.9) -- (0.5,0.9) node[below,midway]{PB};

	\node at (-1.5,1.125) {RIScatter};

	\draw [pattern=north west lines,ultra thick](0.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 1};
	\draw [pattern=north east lines,ultra thick](2.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 2};
	\draw [pattern=vertical lines,ultra thick](4.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 3};
	\draw [pattern=horizontal lines,ultra thick](6.15,5) rectangle ++(0.5,0.25) node[xshift=20,yshift=-3.5] {State 4};
\end{tikzpicture}

### 2024-05-01 assets/viva/region_comparison.tex
:triangular_flag_on_post: Viva

@@
 align=center,
-title style={font=\huge},
-label style={font=\huge},
-ticklabel style={font=\LARGE},
-legend style={font=\LARGE},
+% title style={font=\huge},
+% label style={font=\huge},
+% ticklabel style={font=\LARGE},
+% legend style={font=\LARGE},
 reverse legend,

### 2024-05-01 assets/viva/waveform_subband.tex
:triangular_flag_on_post: Viva

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor2}{rgb}{0.85000,0.32500,0.09800}%
%
\begin{tikzpicture}

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,3.21in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213593809508\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{{\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000358590327058133\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{{\boldmath${s}$}$_{\mathrm{P}}$}

\end{axis}

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,2.522in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.550823184768846\\
2	4.36837845097092\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.48597207854411e-05\\
2	1.53805823004565e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,1.834in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0326721056203988\\
2	0.0697944085211443\\
3	0.193520763120912\\
4	1.91750698481035\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.972503011468572\\
2	1.22779327868874\\
3	1.48063097057209\\
4	2.13162879975205\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,1.146in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00676327571402152\\
2	0.00930781551713654\\
3	0.0129863266085796\\
4	0.0182780278377859\\
5	0.0264785684252956\\
6	0.0417816477229242\\
7	0.0921547943904462\\
8	0.387871897134795\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.897080828535262\\
2	1.11267484124012\\
3	1.2760937466216\\
4	1.42973823824102\\
5	1.54367522426452\\
6	1.64897920494507\\
7	1.73956386270218\\
8	1.89059947472085\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.462in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\Large}, label style={font=\Large}, ticklabel style={font=\Large}, legend style={font=\Large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00205132551819701\\
2	0.00235447373497551\\
3	0.00272196136127332\\
4	0.00316588966668174\\
5	0.00369517036368117\\
6	0.00432537450541609\\
7	0.00508695652011363\\
8	0.00600094215308655\\
9	0.00710012267822671\\
10	0.00851262778314969\\
11	0.0103510448032954\\
12	0.0128569172775466\\
13	0.0164283761517276\\
14	0.0229541038226562\\
15	0.0402894292810385\\
16	0.0926842285796484\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.628841069483884\\
2	0.717675502523908\\
3	0.795496148359302\\
4	0.864626670343281\\
5	0.930591126638763\\
6	0.989724762400551\\
7	1.04508455096183\\
8	1.09678731061405\\
9	1.14380160245268\\
10	1.18636001210616\\
11	1.2248217690153\\
12	1.2585853066132\\
13	1.28750705323146\\
14	1.31224542931104\\
15	1.33460858167442\\
16	1.35822969320702\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2024-05-01 content/abstract.tex
:pencil: Update chapter 3
:pencil: Add conclusion
:triangular_flag_on_post: Viva

@@
 \begin{abstract}
-	\gls{ris} is the most promising physical-layer technology for 6G.
-	It adopts many low-power scattering elements to customize the propagation environment for improved network performance, unlocking a new potential of \emph{channel design} as never before.
-	In this dissertation, we first provide an overview of its structure, characteristics, applications, principles, and models, then discuss how it addresses the key issues in \gls{swipt} and compare it with \gls{bc} in terms of functionalities, principles, models, and preferences.
-	The work chapters investigate three typical use cases of \gls{ris}: Joint design with transceiver for a particular objective (beamforming); ride its own information over legacy networks (modulation); and manipulate the wireless environment as a stand-alone device (channel shaping).
-	In particular,
+	\gls{ris} is one of the most promising physical-layer technology for 6G.
+	It adopts numerous low-power scattering elements to customize the propagation environment for improved network performance, unlocking a new potential of \emph{channel design} as never before.
+	In this dissertation, we first provide an overview of its physical structure, characteristics, applications, and scattering models, then discuss how it addresses the key issues in \gls{swipt} and compare it with \gls{bc} in terms of functionalities and preferences.
+	The work chapters investigate three typical use cases of \gls{ris}: Joint design with transceiver for a specific performance measure (beamforming); ride its own information over legacy networks (modulation); and manipulate the inherent properties of the wireless environment as a stand-alone device (channel shaping).
+	In particular, we address the following topics:
 	\begin{itemize}
-		\item \emph{\gls{ris}-aided \gls{swipt}:} We introduce \gls{ris} into multi-antenna, multi-carrier \gls{swipt} systems, investigating joint waveform and beamforming design for maximizing harvested energy under various communication rate constraints.
-Algorithms, performance trade-offs, and asymptotic behaviors are analyzed.
+		\item \emph{\gls{ris}-aided \gls{swipt}:} We introduce \gls{ris} into multi-antenna, multi-carrier \gls{swipt} systems, investigating joint waveform and beamforming design.
+\gls{r-e} region of practical receivers are characterized under non-linear harvester and frequency-flat \gls{ris} models.
 		\item \emph{RIScatter:} This novel scatter protocol integrates \gls{ris} and \gls{bc} from an input distribution perspective.
-The reflection pattern is exploited simultaneously for primary-link beamforming and backscatter-link modulation.
-We propose a practical cooperative receiver, characterize the achievable rate region, and analyze the impact of system parameters.
-		\item \emph{\gls{mimo} channel shaping:} We exploit an advanced \gls{bd}-\gls{ris} architecture for singular value redistribution and power maximization in \gls{pc}, and leakage interference minimization in \gls{ic}.
-		Their implications on rate-optimal joint designs are also discussed.
-		We highlight the unique features of \gls{bd}-\gls{ris} and propose an efficient design framework.
+The reflection pattern is exploited simultaneously for beamforming of the primary link and modulation of the backscatter link.
+We propose a practical cooperative receiver and characterize the achievable rate region.
+		\item \emph{\gls{mimo} channel shaping:} We exploit an advanced \gls{bd}-\gls{ris} architecture for singular value redistribution in \gls{pc} and leakage interference minimization in \gls{ic}.
+		Their implications on joint \gls{ris}-transceiver designs are also discussed.
+		We also propose an efficient and universal \gls{bd}-\gls{ris} design framework.
 	\end{itemize}

### 2024-05-01 content/chapter_1.tex
:triangular_flag_on_post: Viva

@@
 	Great successes have been made at the transmitter and receiver sides over the past century, and the communications society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	By 2025, global mobile data traffic is expected to reach {607} exabytes per year \cite{Tariq2020} while the number of connected devices may exceed {75} billion \cite{Georgiev2024}.
+	By 2025, global mobile data traffic is expected to reach {607} exabytes (1 exabyte is \num{e18} bytes) per year \cite{Tariq2020} while the number of connected devices may exceed {75} billion (almost 10 per person on average) \cite{Georgiev2024}.
 	At the same time, wireless applications are also evolving in various forms to address world-changing incidents like COVID-19, climate change, geopolitical tensions, and \gls{ai} revolution.
@@
 	Before delving into these questions, we first provide a short overview of \gls{ris} and introduce some potential applications.
-	A detailed literature review and technical discussion on \gls{ris} and other technologies will be reserved for Chapter \ref{ch:background}.
+	A detailed literature review and technical discussion on \gls{ris} and other technologies will be reserved for the following chapters.
 \end{section}
@@
 		\begin{itemize}
-			\item \emph{Passive and environmental-friendly:} \gls{ris} reflects the incident waves in a passive manner and does not require dedicated \gls{rf} chains.\footnote{The controller may be implemented with low-power components and powered by ambient energy.} This is different from \gls{af} relays that require power-hungry oscillators and introduces additional thermal noise.
-			\item \emph{Flexible:} It provides a software configurable environment that can be adapted for different applications and scenarios.
+			\item \emph{Low-power with negligible noise:} \gls{ris} reflects the incident waves in a passive manner and does not require dedicated \gls{rf} chains.\footnote{The controller may be implemented with low-power components and powered by ambient energy.} This is different from \gls{af} relays that require power-hungry oscillators and introduces considerable thermal noise.
+			\item \emph{Programmable in real-time:} It provides a software configurable environment that can be adapted for different applications and scenarios.
 This is different from conventional reflectarray \cite{Nayeri2018} and frequency selective surfaces \cite{Anwar2018} with predefined radiation patterns and frequency response.
-			\item \emph{Full-duplex and universal:} This physical-layer solution can simultaneously support communication, sensing, and power transfer without self-interference.
-Thanks to channel reciprocity, the optimal configuration for downlink and uplink coincide with each other \cite{Wu2021}.
-This is different from \gls{df} relays that are designed for a specific communication link and suffers from packet delays.
-			\item \emph{Low-cost and conformal:} It can be manufactured from low-cost materials and deployed in various forms (e.g., walls, windows, ceilings, tables) to provide seamless coverage and powerful customization for indoor and outdoor environments.
-This is different from conventional multi-antenna systems that features complex hardware and bulky structures.
+			\item \emph{Full-duplex without self-interference and delay:} This physical-layer solution can simultaneously support communication, sensing, and power transfer without self-interference.
+The optimal downlink and uplink configurations coincide with each other thanks to channel reciprocity \cite{Wu2021}.
+This is different from \gls{df} relays that are designed for a specific transmission and suffers from packet delays.
+			\item \emph{Low-cost and conformal:} It can be manufactured from low-cost materials and deployed in various forms (e.g., walls, windows, ceilings) to provide seamless coverage and powerful customization for indoor and outdoor environments.
+This is different from conventional \gls{mimo} systems that features complex hardware and bulky structures.
 		\end{itemize}
@@
 	\begin{subsection}{Applications}\label{sc:ris_applications}
-		The channel manipulation capability of \gls{ris} unlocks a wide range of unprecedented applications, such as signal enhancement \cite{Wu2019}, interference suppression \cite{Jiang2022}, blockage bypassing \cite{Ghatak2021}, coverage extension \cite{Zeng2021}, and security control \cite{Almohamad2020}.
+		The channel manipulation capability of \gls{ris} unlocks a wide range of applications, such as signal enhancement \cite{Wu2019}, interference suppression \cite{Jiang2022}, blockage bypassing \cite{Ghatak2021}, coverage extension \cite{Zeng2021}, and security control \cite{Almohamad2020}.
 		It also has the potential to convey additional information \cite{Ye2022}, compensate for the Doppler effect \cite{Basar2021}, transform frequency-selective channels into frequency-flat \cite{Arslan2022}, improve the spatial diversity for multi-antenna systems \cite{Ozdogan2020a}, and create artificial time diversity for multi-user orthogonal \cite{Yang2019} and non-orthogonal \cite{Chen2023} multiple accesses.
@@
 		Those fancy characteristics and applications of \gls{ris} have also attracted significant attention from the industry.
-		The first public testing attempt was made in 2018 by NTT Docomo and Metawave, which demonstrated a metasurface reflectarray in the FR2 band of 5G can boost a downlink data rate from \qty{60}{Mbps} to \qty{560}{Mbps} \cite{Liu2022b}.
+		The first public testing attempt was made in 2018 by NTT Docomo and Metawave, who demonstrated a metasurface-based reflectarray in the FR2 band of 5G can boost a downlink data rate from \qty{60}{Mbps} to \qty{560}{Mbps} \cite{Liu2022b}.
 		Later in 2020, NTT Docomo developed a transparent dynamic \gls{ris} that can allows 28GHz signals to reflect or pass through with negligible power loss.
-		A regional ``\gls{ris} alliance'' was formed in 2021 by Chinese companies and institutes including ZTE, China Mobile, and CAICT, which soon released a white paper \cite{Rista2023} to promote the technology and standardization.
+		``\gls{ris} alliance'' was formed in 2021 by Chinese companies and institutes including ZTE, China Mobile, and CAICT, which soon released a white paper \cite{Rista2023} to promote the technology and standardization.
 		In December 2022, ITU-R drafted a recommendation report for IMT-2030 (6G) \cite{Itu2022} that marks \gls{ris} as a key technology to enhance the radio interface for multiple physical dimension transmission.
@@
 			\item Quantify the capability of a passive \gls{ris} to reshape the \gls{mimo} \gls{pc} in terms of singular values via analytical bounds and numerical optimization;
-			\item Focus on a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior signal processing performance (subspace alignment and subchannel rearrangement) over the widely-adopted diagonal model;
+			\item Zoom out to a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior shaping performance in terms of subspace alignment and subchannel rearrangement;
 			\item Propose an efficient \gls{rcg} algorithm for general \gls{bd}-\gls{ris} optimization and provide low-complexity solutions for quadratic problems;
@@
 		\item \bibentry{Zhao2022}
-		\item \bibentry{Zhao2022a}
 		\item \bibentry{Zhao2023}
 		\item \bibentry{Zhao2024}
+		\item \bibentry{Zhao2024a}
 	\end{itemize}

### 2024-05-01 content/chapter_2.tex
:triangular_flag_on_post: Viva

@@
 		Once fabricated, these properties cannot be easily changed unless the structure is physically altered.
-		This limits their early usage to military and defense, with applications such as invisibility cloaks and optical illusions.
+		This limits their early usage to military, with applications such as invisibility cloaks and optical illusions.
 		In 2014, the concept of ``coding'' and ``programmable'' metamaterials was validated by researchers at Southeast University \cite{Cui2014}, who realized digital control of radar cross-section using biased diodes and \gls{fpga}.
@@
 			\item \emph{Refraction:} As shown in Fig.
-\ref{fg:nim_focus}, the negative-index material can re-focus the beams diverging from a point source to another point behind the material \cite{Padilla2006}.
-This could be helpful for wireless applications where the transmitter and receiver are at different sides of the material.
+\subref*{fg:nim_focus}, the negative-index material can re-focus the beams diverging from a point source to another point behind the material \cite{Padilla2006}.
+This could be helpful for wireless applications where the transmitter and receiver are at different sides of the obstacle.
 			\item \emph{Reflection:} As shown in Fig.
-\ref{fg:wave_reflected}, the scattering elements cooperatively alter the phase of the incident wave for a constructive (or destructive) superposition of the reflected waves in the target direction \cite{Poulakis2022}.
-This could be helpful for wireless applications where the transmitter and receiver are at the same side of the material.
+\subref*{fg:wave_reflected}, the scattering elements cooperatively alter the phase of the incident wave for a constructive (or destructive) superposition of the reflected waves in the target direction \cite{Poulakis2022}.
+This could be helpful to concentrate ambient electromagnetic energy within a specific area.
 		\end{itemize}
@@
 			}
-			\caption{Refraction through metamaterials. For negative-index material, beams diverging from a point source is set in reverse and converges back to another point.}
+			\caption{Refraction through metamaterials. For negative-index material, beams diverging from a point source is set in reverse and converges back to another point behind the material.}
 		\end{figure}
@@
 			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
-			In contrast, the latter allows the wave to feed into and collect from the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
+			In contrast, the latter allows the wave to feed into the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
 			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
@@
 			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
-			It is worth mentioning that
+			Specifically,
 			\begin{itemize}
 				\item \emph{Structural component:} Depends on the geometry and material of the scatterer.
-It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or simply regarded a \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
-				\item \emph{Antenna component:} Depends on the reflection coefficient that can be altered by load impedance.
-This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2022a}.
+It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or a baseband \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
+				\item \emph{Antenna component:} Depends on the reflection coefficient and load impedance.
+This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2024}.
 			\end{itemize}
 			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
-			More accurate models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and measurement fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature.
+			Advanced models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and parametric fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature for accurate and practical analysis.
 			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
@@
 		\begin{subsubsection}{\glsfmtfull{bd} Model}
-			How to model the \gls{ris} response if the passive scattering elements can be cooperative instead of independent?
-			This question has been answered by \cite{Shen2020a} where a \gls{bd} model was proposed.
-			From a network theory perspective \cite{Ivrlac2010}, the interaction between the scattering elements can be modelled as lossless (but not necessarily symmetric) in-group connections in an $N_\mathrm{S}$-port circuit network, as shown in Figs.
-\ref{fg:bd_ris_architecture_1} and \ref{fg:bd_ris_architecture_2} \cite{Shen2020a}.
-			This architecture allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group.
-			\begin{figure}[H]
-				\centering
-				\resizebox{0.75\columnwidth}{!}{
-					\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
-				}
-				\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: Modified from \cite{Shen2020a}.}
-				\label{fg:bd_ris_architecture_1}
-			\end{figure}
+			How to model the \gls{ris} response if the passive scattering elements can cooperate with neighbors via physical connections?
+			This question has been answered by \cite{Shen2020a} through a \gls{bd} model.
+			From a network theory perspective \cite{Ivrlac2010}, a general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
+			It allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group, such that both amplitude and phase of the scattered wave can be redistributed with zero power loss.
+			Fig. \ref{fg:bd_ris_architecture_2} illustrates an 8-element \gls{ris} with group size 2 (left) and 4 (right).
 			\begin{figure}[H]
@@
 
-			A general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
+			% thus redistribute both amplitude and phase of the scattered wave with zero power loss.
+			% \begin{figure}[H]
+			% 	\centering
+			% 	\resizebox{0.75\columnwidth}{!}{
+			% 		\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
+			% 	}
+			% 	\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: Modified from \cite{Shen2020a}.}
+			% 	\label{fg:bd_ris_architecture_1}
+			% \end{figure}
+
+			% A general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
 			With symmetric components (e.g., capacitors and inductors), the scattering matrix of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$ is \cite{Shen2020a}
@@
 			\end{subequations}
-			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} such that the symmetric constraint \eqref{eq:symmetric_property} can be relaxed.
-			This corresponds to the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as widely considered in quantum physics.
-			The overall scattering matrix of asymmetric \gls{bd}-\gls{ris} is thus \emph{block-diagonal with unitary blocks}
+			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} such that the symmetric constraint \eqref{eq:symmetric_property} is unnecessary.
+			This corresponds to the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as has been widely adopted in quantum physics.
+			The overall scattering matrix of asymmetric \gls{bd}-\gls{ris} is thus \emph{block-diagonal with unitary diagonal blocks}
 			\begin{equation}
@@
 			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2024}.
-			One element is in the same group with another if and only if there is at least one path (via edges) between them.
+			Two elements are in the same group if and only if there is at least one path (via edges) between them.
 			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
@@
 		Second, the power can be simultaneously radiated to multiple devices on demand in a predictable, sustainable and reliable manner.
-		This supports our initial vision and is different from other uncontrollable and intermittent energy sources.
+		This fits in our initial vision and differs from other unstable energy sources.
 		Third and most importantly, radio waves carries power and information simultaneously.
@@
 		\end{itemize}
-		It is worth mentioning that $\eta_1$ and $\eta_3$ also depend on the characteristics of input waveform like power level, carrier frequency, and \gls{papr} \cite{Clerckx2016a}.
+		It is worth mentioning that $\eta_1$ and $\eta_3$ also depend on the signal characteristics such as power level, carrier frequency, and \gls{papr} \cite{Clerckx2016a}.
 		Extensive efforts have been contributed from \gls{rf}, wireless communications, and power electronic communities to improve the conversion efficiency of individual modules.
 		However, it is often overlooked in the literature that a practical \gls{wpt} system is highly \emph{non-linear} since the amplifier and rectifier are very sensitive to the input waveform.
-		This non-linear behavior can lead to a \emph{coupling effect} between the modules, such that optimizing $\eta_1$ to $\eta_4$ independently does not necessarily maximize the end-to-end power efficiency $\eta$ \cite{Clerckx2016a}.
+		This non-linear behavior can lead to a {coupling effect} between the modules, such that optimizing $\eta_1$ to $\eta_4$ independently does not necessarily maximize the end-to-end power efficiency $\eta$ \cite{Clerckx2016a}.
 		Besides, the system modeling and analysis are subject to practical constraints like diode threshold and reverse-breakdown voltages, device parasitics, impedance mismatch, and harmonic generation  \citep{Valenta2014}.
@@
 			The rectifier is a nonlinear circuit that converts the \gls{rf} signal to \gls{dc} power by rectifying and filtering the input signal.
-			Figs.
+			Fig.
 \ref{fg:harvester_circuit} illustrates the equivalent circuits of a rectenna (antenna and rectifier) and a single-diode half-wave rectifier, where $v_{\mathrm{S}}$ is the source voltage on the receive antenna, $Z_{\mathrm{A}} = R_{\mathrm{A}} + \jmath X_{\mathrm{A}}$ is the antenna impedance, $Z_{\mathrm{in}} = R_{\mathrm{in}} + \jmath X_{\mathrm{in}}$ is the total impedance of the matching network and rectifier, $v_{\mathrm{in}}$ is input voltage on the matching network and rectifier, $v_{\mathrm{D}}$ is the diode voltage, $C$ is the buffer capacitance, $R_{\mathrm{L}}$ is the rectifier load resistance, and $v_{\mathrm{out}}$ is the output voltage.
-			It is worth mentioning that the half-wave rectifier is the most popular choice in \gls{wpt} literature due to its simple behavior and low cost.
+			It is worth mentioning that the half-wave rectifier is the most popular choice in \gls{wpt} literature due to its simple layout and low cost.
 			Other rectifier topologies like full-wave, bridge, and voltage doubler can potentially improve the \gls{rf}-to-\gls{dc} conversion efficiency \cite{Rotenberg2020}, but their modeling and analysis are much more complicated.
@@
 			The diode is the key non-linear component that determines to the harvested energy.
-			Generally speaking, the behavior of any rectenna can be separated into three operation regions \cite{Clerckx2016a}:
+			Roughly speaking, the behavior of any rectenna can be separated into three operation regions \cite{Clerckx2016a}:
 			\begin{itemize}
@@
 			\item \emph{Waveform and modulation:} Under an average power constraint, \gls{wit} favors Gaussian signaling with maximum entropy distribution \cite{Cover2005} while \gls{wpt} prefers deterministic (unmodulated) multisine with higher \gls{papr} \cite{Trotter2009}.
-			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
+			\item \emph{Channel:} In a \gls{mimo} scenario, \gls{wit} favors full-rank \gls{nlos} with high spatial diversity at high \gls{snr} while \gls{wpt} prefers rank-deficient \gls{los} with high spatial correlation \cite{Wu2022a}.
 			\item \emph{Receiver:} The power sensitivity is usually in the range of -40 to -80 dBm for information receivers and -10 to -30 dBm for energy harvesters \cite{Lu2015}.
@@
 		\end{equation}
-		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ defined in \eqref{eq:dc_power_nonlinear} is uniquely mapped to the harvested \gls{dc} power.
+		where $P$ is the average transmit power, $\gamma$ is the \gls{snr} at the information decoder, and $z$ in \eqref{eq:dc_power_nonlinear} relates to the harvested \gls{dc} power.
 		Each point in this region corresponds to a \emph{rate-energy pair} achieved by a particular \emph{resource allocation scheme}.
-		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions (instead of different points in the same region), which motivates a joint optimization of the transmitter, channel, and receiver.
+		It is worth mentioning that different transceive strategies (e.g., waveform and receiver design) can lead to totally different \gls{r-e} regions instead of different points in the same region, which motivates a joint optimization of the transmitter, channel, and receiver.
 	\end{subsection}
@@
 				\subfloat[Ideal receiver]{
-					\resizebox{0.6\columnwidth}{!}{
+					\resizebox{!}{2.25cm}{
 						\input{assets/chapter_2/receiver_ideal.tex}
@@
 				}
-				\\
 				\subfloat[Time switching receiver]{
-					\resizebox{0.6\columnwidth}{!}{
+					\resizebox{!}{2.25cm}{
 						\input{assets/chapter_2/receiver_ts.tex}
@@
 				\subfloat[Power splitting receiver]{
-					\resizebox{0.6\columnwidth}{!}{
+					\resizebox{!}{2.25cm}{
 						\input{assets/chapter_2/receiver_ps.tex}
@@
 				}
-				\\
 				\subfloat[Integrated receiver]{
-					\resizebox{0.6\columnwidth}{!}{
+					\resizebox{!}{1.75cm}{
 						\input{assets/chapter_2/receiver_integrated.tex}
@@
 			The \gls{r-e} region of the former can be inferred from that of the latter, since the \gls{wit}-only and \gls{wpt}-only vertices in \gls{ts} correspond to $\rho=1$ and $\rho=0$ in \gls{ps}, respectively.
-			Integrated receiver eliminates the need of \gls{rf} chains and advanced architectures, but experiences information degradation and works better for low-throughput applications.
+			Integrated receiver eliminates the need of \gls{rf} chains and advanced architectures, but experiences information degradation and fits low-throughput applications.
 		\end{subsubsection}
@@
 			\item \emph{Harvesting requires absorption:} Part of the impinging wave should be fed into the node to power its operation.
-This is different from \gls{ris} where a full reflection is desired to maximize its channel control capability.
+This is different from \gls{ris} where a full reflection is desired to maximize its energy efficiency.
 		\end{itemize}
-		Denote the amplitude scattering ratio of the \gls{bc} node as $\alpha$, i.e., the power absorption ratio is $(1-\alpha)^2$. Some popular modulation schemes are summarized below:
+		Denote the amplitude scattering ratio of the \gls{bc} node as $\alpha$ that corresponds to a power absorption ratio $(1-\alpha)^2$. Some popular modulation schemes are summarized below:
 		\begin{itemize}
@@
 			As the core modulation scheme in \gls{lora}, it is more robust to noise and interference (with a reception sensitivity of -149 dBm), harder to be detected by eavesdroppers, and can be used for ranging and localization \cite{Abbasi2021a}.
-
+		\end{itemize}
 		Common \gls{bc} channel coding schemes include unipolar \gls{rz} and \gls{nrz}, Manchester, differential, pulse-pause and FM0.
 		They are not the focus of the thesis and the readers are referred to \cite[Chapter 2.3]{Hoang2020} for details.
-		\end{itemize}
 	\end{subsection}
@@
 		\begin{subsubsection}{\glsfmtfull{mbc}}
-			\gls{mbc} is the most common architecture where the carrier emitter and reader are integrated into one device called interrogator.
-			As shown in \subref*{fg:backcom_monostatic} and \subref*{fg:mbc_intro}, the interrogator transmits a \gls{cw} in the downlink and receives the reflected information-bearing signal in the uplink.
+			\gls{mbc} is probably the most common \gls{bc} scenario where the carrier emitter and reader are integrated into one device called interrogator.
+			As shown in Figs.
+\subref*{fg:backcom_monostatic} and \subref*{fg:mbc_intro}, the interrogator transmits a \gls{cw} in the downlink and receives the reflected information-bearing signal in the uplink.
 			The node varies its load impedance over time to switch between two states.
@@
 		\begin{subsubsection}{\glsfmtfull{bbc}}
-			\gls{bbc} separates the carrier emitter and reader into two individual devices, as illustrated in \subref*{fg:backcom_bistatic} and \subref*{fg:bbc_intro}.
+			\gls{bbc} separates the carrier emitter and reader into two individual devices, as illustrated in Figs. \subref*{fg:backcom_bistatic} and \subref*{fg:bbc_intro}.
 			This helps to combat self-interference and extend the operation range, but the system involves three devices and requires more complex coordination and synchronization.
@@
 			\gls{ambc} has been recognized as a revolutionary technology since its debut in 2013 \cite{Liu2013b}.
-			As shown in \subref*{fg:ambc_intro}, it gets rid of dedicated \gls{rf} sources and relies on ambient signals (e.g., TV, FM, and Wi-Fi) for both energy harvesting and information transfer.
+			As shown in Fig. \subref*{fg:ambc_intro}, it gets rid of dedicated \gls{rf} sources and relies on ambient signals (e.g., TV, FM, and Wi-Fi) for both energy harvesting and information transfer.
 			Compared with \gls{mbc} and \gls{bbc}, its carrier waveform is no longer a \gls{cw} but a mixture of already modulated signals with different frequencies and amplitudes, which makes the detection more challenging.
-			Therefore, it often employs \gls{fsk} modulation to shift the scattered signals to a different band for reduced interference on both coexisting systems.
+			Therefore, it often employs \gls{fsk} modulation that shifts the scattered signals to a different band for reduced interference on both coexisting systems.
 			\gls{ambc} is a plug-and-play and environmental-friendly \gls{iot} solution, but its practical deployment is limited by the availability and quality of ambient signals.
@@
 			\gls{sr} is a relatively new concept proposed in 2019 that introduced itself as ``cooperative \gls{ambc}'' \cite{Guo2019b}.
-			As shown in \subref*{fg:sr_intro}, it shares not only the transmitter, \gls{rf} source, but also the receiver with a primary transmission.
+			As shown in Fig. \subref*{fg:sr_intro}, it shares not only the transmitter, \gls{rf} source, but also the receiver with a primary transmission.
 			This is different from traditional \gls{ambc} where the legacy system can be unaware of the backscatter link and the node wants to minimize its footprint.
@@
 \end{section}
-
-% \begin{section}{\glsfmtfull{im}}
-
-% \end{section}
-
-% \begin{section}{\glsfmtfull{mimo}}
-% 	\begin{subsection}{\glsfmtfull{pc}: Channel Shaping}
-
-% 	\end{subsection}
-
-% 	\begin{subsection}{\glsfmtfull{ic}: Interference Alignment}
-
-% 	\end{subsection}
-% \end{section}

### 2024-05-01 content/chapter_5.tex
:triangular_flag_on_post: Viva

@@
 \begin{section}{Introduction}
-	% The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
-	% Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
-	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
-	This is empowered by the recent advances in \gls{ris}, a real-time programmable metasurface of numerous non-resonant sub-wavelength scattering elements.
-	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than relays.
-	Using \gls{ris} for {passive beamforming} has attracted significant interest in wireless communication \cite{Wu2019,Wu2020c,Yang2020,Zheng2021}, backscatter \cite{Jia2020,Liang2022}, sensing \cite{Liu2022a,Hua2023}, and power transfer literature \cite{Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
-	On the other hand, \gls{ris} also enables {backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Karasik2020,Basar2020,Zhao2022a} and prototyped \cite{Tang2019b,Dai2020a}.
-	Despite fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape the wireless channel?}
-
-	The answer depends heavily on the hardware architecture and scattering model.
-	In diagonal \gls{ris}, each scattering element is tuned by a dedicated impedance and acts as an \emph{individual} phase shifter \cite{Wu2020}.
-	The concept is generalized to \gls{bd}-\gls{ris} \cite{Shen2020a,Li2023b} which physically connects adjacent elements using passive components.
+	Today we are witnessing a paradigm shift from connectivity to intelligence, where the wireless environment is no longer a chaotic medium but a conscious agent that can serve on demand.
+	This is empowered by the recent advances in \gls{ris}, a programmable metasurface that recycles and redistributes ambient electromagnetic waves for improved wireless performance.
+	A typical \gls{ris} consists of numerous low-power sub-wavelength non-resonant scattering elements, whose response can be engineered in real-time to manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019}.
+	% It not only experiences negligible noise and supports full-duplex transmissions, but also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
+	It enables low-noise, full-duplex operation, and also features better flexibility than reflectarrays, lighter footprint than various relays, and greater scalability than conventional multi-antenna techniques.
+	The most popular \gls{ris} research direction is \emph{joint beamforming} design with transceivers for a specific performance measure, which has attracted significant attention in wireless communication \cite{Wu2019,Guo2020,Liu2022}, sensing \cite{He2022,Luo2022,Hua2023}, and power transfer literature \cite{Wu2020a,Feng2022,Zhao2022}.
+	While passive beamforming suffers severe attenuation from double fading, it usually offers a squared asymptotic behavior than active beamforming (e.g., second-order array gain and fourth-order harvested power \cite{Zhao2022}).
+	On the other hand, \gls{ris} can also be used for \emph{backscatter modulation} by periodically switching its reflection pattern within channel coherence time.
+	This creates a free-ride message stream (similar to index modulation \cite{Basar2017}) with dual benefits: integrating with the legacy transmitter for enhanced channel capacity \cite{Karasik2020,Basar2020,Ye2022} or serving as a dedicated source for low-power uplink communication \cite{Liang2020,Zhao2024,Yang2024}.
+	Different from above directions, \emph{channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment.
+	This provides a ubiquitous wave scattering benchmark for different wireless applications and helps to decouple the \gls{ris}-transceiver design.
+	Relevant shaping metrics can be classified into two categories:
+	\begin{itemize}
+		\item \emph{Singular value centric:} Closely related to the performance measures (e.g., achievable rate and harvested power \cite{Shen2021}) but sensitive to numerical perturbations.
+The impact of \gls{ris} has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023}.
+		\item \emph{Power centric:} The second-order statistics are less informative in \gls{mimo} but easier to analyze and optimize.
+The impact of \gls{ris} has been studied in terms of channel power gain \cite{Wu2019,Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and leakage interference \cite{Santamaria2023a}.
+	\end{itemize}
+
+	While those works offer initial glimpses into the channel shaping potential, one critical question remains unaddressed: \emph{To what extent can a passive \gls{ris} reshape the \gls{mimo} channel in terms of singular values?}
+	% \begin{enumerate}
+	% 	\item What is the entire singular value region of a \gls{mimo} channel with \gls{ris}?
+	% \end{enumerate}
+	% they neither discuss the limitation
+	% depict the entire singular value region nor provide a universal optimization framework.
+	% It motivates the ultimate question: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels in terms of singular values?}
+	% Despite the great potentials and fruitful outcomes, one critical unanswered question is the {channel shaping} capability: \emph{To what extent can a passive \gls{ris} reshape \gls{mimo} channels?}
+	The answer depends heavily on the scattering model and hardware architecture.
+	Most relevant works \cite{ElMossallamy2021,Meng2023,Zheng2022,Huang2023,Bafghi2022,Zheng2023,Chae2023,Wu2019,Santamaria2023a} assumed that each \gls{ris} element is tuned by a dedicated impedance and acts as an \emph{individual} scatterer \cite{Wu2020}.
+	This ideally translates to a scattering matrix with unit-magnitude entries on the main diagonal and zeros elsewhere, applying merely a phase shift to the incoming signal.
+	The concept was soon generalized to \gls{bd}-\gls{ris} \cite{Shen2020a} that physically groups adjacent elements using passive reconfigurable components.\footnote{Those components can be either symmetric (e.g., capacitors and inductors) or asymmetric (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}, resulting in symmetric and asymmetric scattering matrices, respectively.}
 	This allows \emph{cooperative} scattering --- wave impinging on one element can propagate within the circuit and depart partially from any element in the same group.
-	\gls{bd}-\gls{ris} can thus control both amplitude and phase of the reflected wave, generalizing the scattering matrix from diagonal with unit-magnitude entries \eqref{eq:diagonal_scattering_matrix} to block diagonal with unitary blocks \eqref{eq:bd_scattering_matrix}.
-	Its benefit has been recently shown in receive power maximization \cite{Nerini2023,Santamaria2023,Fang2023,Nerini2024}, transmit power minimization \cite{Zhou2023}, and rate maximization \cite{Zhou2023,Nerini2024,Li2023d,Bartoli2023,Li2023c}.
-	Practical issues such as channel estimation \cite{Li2023e} and mutual coupling \cite{Li2023f} have also been investigated.
-	Therefore, \gls{bd}-\gls{ris} is envisioned as the next generation channel shaper with stronger signal processing flexibility \cite{Li2023g}.
-
-	% Attempts to characterize the channel shaping capability can be classified into \emph{singular value centric} and \emph{power centric} methods.
-	% Channel shaping is different from passive beamforming as it seeks to modify the inherent properties of the channel itself, allowing one to decouple \gls{ris} and transceiver design.
-	Channel shaping is different from passive beamforming discussed in Chapters \ref{ch:ris_aided_swipt} and \ref{ch:riscatter} because \gls{ris} is exploited as a stand-alone device to modify the inherent properties of the wireless channel.
-	This allows one to decouple the \gls{ris}-transceiver design and explore the fundamental limits of wave manipulation.
-	Relevant design criteria can be roughly classified into two categories:
-	\begin{itemize}
-		\item \emph{Singular value centric:} Focus on the singular values of the equivalent channel matrix, which are closely related to the channel capacity and the diversity-multiplexing trade-off.
-Relevant designs are more complicated since they involve the entire channel matrix.
-		\item \emph{Power centric:} Focus on the second-order characteristics of the channel matrix, which are useful in \gls{miso} but less informative in \gls{mimo}.
-Relevant designs are more practical and straightforward.
-	\end{itemize}
-	The former has been studied in terms of minimum singular value \cite{ElMossallamy2021}, effective rank \cite{ElMossallamy2021,Meng2023}, condition number \cite{Zheng2022,Huang2023} in \gls{pc}, and degree of freedom \cite{Bafghi2022,Zheng2023,Chae2023} in \gls{ic}.
-	The latter has been studied in terms of channel power \cite{Wu2019,Nerini2023,Santamaria2023} in \gls{pc} and leakage interference \cite{Santamaria2023a} in \gls{ic}.
-	Although the results are insightful, the big picture is far from complete since there exists neither a systematic channel shaping study nor a universal \gls{ris} optimization framework.
-	To the best of our knowledge, the most general channel shaping scenario (\gls{bd}-\gls{ris}-aided \gls{mimo}) has not been studied, and the great potential of \gls{bd}-\gls{ris} has not been fully exploited or understood.
-	This chapter aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
+	It can thus redistribute both amplitude and phase of the scattered wave with zero power loss, generalizing the scattering matrix to block-diagonal with unitary blocks.
+	Such a powerful model can be realized at reduced hardware cost using tree- and forest-connected architectures inspired by graph theory \cite{Nerini2024}.
+	\gls{bd}-\gls{ris} can also function in hybrid transmitting-and-reflecting mode \cite{Li2023b} and multi-sector mode \cite{Li2023c} to provide full-space coverage and multi-user support.
+	Many practical design challenges have been addressed including channel estimation \cite{Li2024}, mutual coupling \cite{Li2023f}, and wideband modelling \cite{Li2024a}.
+	Its beamforming superiority has been studied extensively in \gls{siso} and \gls{miso} systems, where the problems were cast as single-user \gls{snr} maximization \cite{Shen2020a,Nerini2023,Nerini2024,Santamaria2023} and multi-user \gls{wsr} maximization \cite{Fang2023,Zhou2023,Li2023c,Soleymani2024}.
+	However, the interplay between \gls{bd}-\gls{ris} and \gls{mimo} systems is still in the infancy stage.
+	The authors of \cite{Bartoli2023} investigated the rate-optimal joint beamforming design for a specific \gls{bd}-\gls{ris}-aided \gls{mimo} system with blocked direct link and unitary (a.k.a.
+fully-connected) \gls{ris}.
+	Similar constraints were also adopted in \cite{Mishra2024}, which introduces a transmitter-side \gls{bd}-\gls{ris} to massive \gls{mimo} that exploits statistical \gls{csi} for improved spectral efficiency.
+	Received power maximization problem was studied over continuous-valued \cite{Nerini2023} and discrete-valued \cite{Nerini2023b} \gls{bd}-\gls{ris}, but the proposed single-stream transceiver is rate-suboptimal and the passive beamforming problem is equivalent to \gls{siso}.
+	A practical frequency-dependent \gls{bd}-\gls{ris} model has been recently proposed for multi-band multi-cell \gls{mimo} networks to facilitate practical deployments \cite{Sena2024}.
+	Although the results are promising, the channel shaping capability from off-diagonal entries deserves further investigation, and there lacks a universal yet efficient \gls{bd}-\gls{ris} design framework.
+	Furthermore, no previous work has attempted to characterize the singular value region of a \gls{mimo} channel manipulated by any type of \gls{ris}, and the \gls{bd}-\gls{ris}-aided \gls{mimo} rate maximization problem remains unsolved.
+	This paper aims for a comprehensive answer to the channel shaping question through theoretical analysis and numerical optimization.
 	The contributions are summarized below.
 
-	First, we exploit the Riemannian geometry of the Stiefel manifold to design a novel geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg} algorithm for \gls{bd}-\gls{ris} optimization.
-	This method modified from \cite{Abrudan2008,Abrudan2009} not only features lower complexity and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also fits arbitrary group size and any smooth \gls{ris} optimization problem.
-	Specifically, block-wise rotational update is performed along the geodesics of the Stiefel manifold, which are expressed compactly by the exponential map \cite{Edelman1998}.
-	This is the first work to tailor an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
-
-	Second, we quantify the capability of a \gls{bd}-\gls{ris} to redistribute the singular values of \gls{mimo}-\gls{pc}.
-	The \emph{Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
+	% 1. need a general study on BD-RIS x MIMO and explain the potential from off-diagonal entries
+	% 2. need a general optimization framework for BD-RIS
+	% 3. need a comprehensive answer to the channel shaping question
+	% 4. need a low-complexity solution from shaping
+
+	First, we discuss the shaping potential from off-diagonal entries of \gls{bd}-\gls{ris} in terms of subchannel rearrangement and subspace alignment.
+	Subchannel rearrangement enables a flexible in-group permutation and combination of backward and forward channels by their strength.
+	This unique feature of \gls{bd}-\gls{ris} provides a higher shaping freedom and exploits spatial diversity more effectively than diagonal \gls{ris}.
+	On the other hand, subspace alignment in \gls{mimo} generalizes phase matching in \gls{siso} and \gls{miso} to the high-dimensional singular vector space.
+	The scattering matrix simultaneously affects the multiplicative intra-group alignment and additive inter-group alignment.
+	However, both subspaces cannot be perfectly aligned at the same time and a balance needs to be struck in between.
+	Increasing \gls{mimo} dimensions highlights the advantage of \gls{bd}-\gls{ris} for subchannel rearrangement while exposing the limitation of diagonal \gls{ris} in subspace alignment.
+	This is the first paper to study \gls{bd}-\gls{ris} in general \gls{mimo} systems and discuss its shaping potential.
+	% unveil and interpret the potential of \gls{bd}-\gls{ris} in general \gls{mimo} systems.
+
+	Second, we exploit the Riemannian geometry of the Stiefel manifold and propose an efficient \gls{bd}-\gls{ris} design framework based on geodesic\footnote{A geodesic refers to the shortest path between two points in a Riemannian manifold.} \gls{rcg}.
+	This method modified from \cite{Abrudan2008,Abrudan2009} not only provides better objective value and faster convergence than general non-geodesic approach \cite{Absil2009,Pan2022d}, but also works for arbitrary group size and any smooth optimization problem.
+	Specifically, group-wise multiplicative rotational updates are performed along the geodesics of the Stiefel manifold and compactly evaluated as the exponential map \cite{Edelman1998}.
+	By exploiting the inherent structure of unitary matrices, this method avoids retractions from the Euclidean space and facilitates the step size selection, which improves the computational efficiency and stability.
+	This is the first work to tailor an efficient and universal optimization framework for \gls{bd}-\gls{ris}.
+
+	% pioneer
+	Third, we quantify the capability of a \gls{bd}-\gls{ris} to redistribute the singular values of a \gls{mimo} \gls{pc} channel.
+	The {Pareto frontiers} are characterized by optimizing the {weighted sum of singular values}, where the weights can be positive, zero, or negative.
 	This problem is solved by the proposed geodesic \gls{rcg} algorithm.
-	The resulting achievable singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
-	We also demystify the \gls{bd}-\gls{ris} gain from off-diagonal entries and derive some analytical singular value bounds for rank-deficient \gls{mimo} and fully-connected (a.k.a. unitary) \gls{ris}.
-	This is the first work to comprehensively answer the channel shaping question and fully unveil the potential or \gls{bd}-\gls{ris}.
-
-	Third, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo}-\gls{pc} rate maximization with two solutions: a local-optimal approach through \gls{ao} and a low-complexity approach over channel shaping.
-	The former updates active and passive beamforming by eigenmode transmission and \gls{rcg} algorithm, respectively.
-	The latter suboptimally decouples both blocks, recasts the shaping problem as channel power maximization, and solves it iteratively in closed form.
-	Interestingly, the gap in between vanishes as \gls{bd}-\gls{ris} evolves from diagonal to unitary.
-	It suggests channel shaping decouples the \gls{ris}-transceiver design and offers a promising low-complexity solution.
-	This is the first work to discuss the implications of channel shaping in joint active-passive beamforming optimization.
-
-	Fourth, we extend the aforementioned approaches to \gls{mimo}-\gls{ic} where the \gls{bd}-\gls{ris} is used for leakage interference minimization and \gls{wsr} maximization.
+	The resulting singular value region generalizes most relevant metrics and provides an intuitive channel shaping benchmark.
+	% We also and derive some analytical singular value bounds for rank-deficient \gls{mimo} and unitary \gls{ris}.
+	To explore the shaping limits of different \gls{ris} architectures, we also derive individual and collective singular value bounds for rank-deficient channels and unitary \gls{ris} via matrix analysis.
+	Results validate those bounds and show that increasing \gls{bd}-\gls{ris} group size significantly enlarges the singular value region, providing wider dynamic range and better trade-off.
+	% dynamic range and trade-off of singular values are significantly improved by \gls{bd}-\gls{ris}, especially in large-scale \gls{mimo} systems.
+	This is the first work to comprehensively answer the channel shaping capability question from both numerical and analytical perspectives in the most general \gls{bd}-\gls{ris} setup.
+	% from a Pareto perspective.
+
+	Fourth, we tackle \gls{bd}-\gls{ris}-aided \gls{mimo} achievable rate maximization problem with two beamforming solutions: a local-optimal approach via \gls{ao} and a low-complexity approach over channel shaping.
+	The former iteratively updates active beamforming by eigenmode transmission and passive beamforming by geodesic \gls{rcg} until convergence.
+	The latter suboptimally decouples the joint design into a channel power gain maximization subproblem and a conventional \gls{mimo} transmission subproblem, then propose a closed-form two-stage solution.
+	We observe that \gls{bd}-\gls{ris} yields higher channel power and achievable rate than diagonal \gls{ris}, while the relative gains scale with the group size and \gls{mimo} dimensions.
+	% especially with large group sizes and \gls{mimo} dimensions.
+	Moreover, the rate difference between the optimal and shaping-inspired designs diminishes as the \gls{ris} evolves from diagonal to unitary.
+	% Interestingly, the rate difference between the optimal and low-complexity designs diminishes as the \gls{ris} evolves from diagonal to unitary.
+	Those results emphasize the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems and suggest channel shaping offers a promising path to decouple joint \gls{ris}-transceiver designs.
+
+	Fifth, we extend the aforementioned approaches to \gls{mimo}-\gls{ic} where the \gls{bd}-\gls{ris} is used for leakage interference minimization and \gls{wsr} maximization.
 	In the former case, we update the receive combiner, transmit precoder, and scattering matrix iteratively in closed forms with optimality proof.
@@
 \begin{section}{\glsfmtshort{mimo}-\glsfmtshort{pc}}
+
 	\begin{subsection}{System Model}
-		Consider a \gls{bd}-\gls{ris}-aided point-to-point \gls{mimo} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
+		Consider a \gls{bd}-\gls{ris} aided \gls{mimo} \gls{pc} system with $N_\mathrm{T}$, $N_\mathrm{S}$, $N_\mathrm{R}$ transmit, scatter, and receive antennas, respectively.
 		This configuration is denoted as $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ in the following context.
-		The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
-		To simplify the analysis, we assume a lossless asymmetric network\footnote{While symmetric \gls{bd}-\gls{ris} (involving capacitors and inductors) is often considered in the literature \cite{Shen2020a,Nerini2023,Santamaria2023,Fang2023,Nerini2024,Zhou2023,Li2023d,Bartoli2023}, asymmetric \gls{bd}-\gls{ris} can be built over reconfigurable asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006}.} without mutual coupling between scatter elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
-		The overall scattering matrix of the \gls{bd}-\gls{ris} is
+		The \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network \cite{Ivrlac2010} that further divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components \cite{Shen2020a}.
+		To simplify the analysis and explore the performance limits, we assume a lossless asymmetric network without mutual coupling between scattering elements, as previously considered in \cite{Li2023b,Li2023c,Bartoli2023}.
+		The overall scattering matrix of the \gls{bd}-\gls{ris} is block-unitary
 		\begin{equation}
 			\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G),
-		\end{equation}
-		where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is a unitary matrix that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
-		That is, $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$.
-		Note that diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
+			\label{eq:bd_ris}
+		\end{equation}
+		where $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$ is the $g$-th unitary block (i.e., $\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}$) that describes the response of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$.
+		Note that diagonal and unitary \gls{ris} can be regarded as its extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
 		Some potential physical architectures of \gls{bd}-\gls{ris} are illustrated in \cite[Fig.
@@
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2024}, where the radiation pattern and circuit topology have impacts on the scattering matrix.
+2]{Nerini2024}, where the radiation pattern and circuit topology need to be modelled in the scattering matrix.
 
@@
 		\begin{equation}
-			\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g},
+			\mathbf{H} = \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} = \mathbf{H}_\mathrm{D} + \sum_g \underbrace{\mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}}_{\triangleq \mathbf{H}_g},
 			\label{eq:channel_equivalent}
 		\end{equation}
-		where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
-		% That is, $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns (resp. rows) of $\mathbf{H}_\mathrm{B}$ (resp. $\mathbf{H}_\mathrm{F}$).
-		% , corresponding to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$.
-		% $\mathbf{H}_{\mathrm{B},g}$ (resp. $\mathbf{H}_{\mathrm{F},g}$) corresponds to the $(g-1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$
+		where $\mathbf{H}_{\mathrm{B},g} \in \mathbb{C}^{N_\mathrm{R} \times L}$ and $\mathbf{H}_{\mathrm{F},g} \in \mathbb{C}^{L \times N_\mathrm{T}}$ are the backward and forward subchannels for \gls{ris} group $g$, corresponding to the $(g{-}1)L$ to $gL$ columns of $\mathbf{H}_\mathrm{B}$ and rows of $\mathbf{H}_\mathrm{F}$, respectively.
+		Let $\mathbf{H}_g \triangleq \mathbf{H}_{\mathrm{B},g} \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}$ be the indirect channel via \gls{bd}-\gls{ris} group $g$.
 		Since unitary matrices constitute an algebraic group with respect to multiplication, the scattering matrix of group $g$ can be decomposed as
@@
 			\mathbf{\Theta}_g = \mathbf{L}_g \mathbf{R}_g^\mathsf{H},
-			\label{eq:unitary_decomposition}
 		\end{equation}
@@
 
-		\begin{remark}\label{rm:channel_shaping}
-			By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that channel shaping through \gls{bd}-\gls{ris} creates two critical opportunities:
+		% \begin{remark}
+		By analyzing \eqref{eq:channel_equivalent_svd}, we conclude that the off-diagonal entries of the \gls{bd}-\gls{ris} scattering matrix provide two key potentials for \gls{mimo} channel shaping:
 		\begin{itemize}
-				\item \textbf{Subspace alignment:} Each group can align the singular matrices of the backward-forward (intra-group, multiplicative) and the direct-indirect (inter-group, additive) channels.
-In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ is
+			\item \emph{Subchannel rearrangement:} This unique feature of \gls{bd}-\gls{ris} exploits the spatial diversity by rearranging and combining the backward and forward channel branches within each group.
+In \gls{siso}, diagonal \gls{ris} with perfect phase matching provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$ while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
+			Note the first summation is over groups and the second summation is over permuted subchannels.
+			By rearrangement inequality, the maximum channel gain is attained by pairing the $l$-th strongest backward and forward branches.
+			% , providing up to \qty{62.5}{\percent} asymptotic power gain over diagonal \gls{ris} in \gls{siso} Rayleigh fading \cite{Shen2020a}.
+			Since the number of subchannels associated with each group is proportional to $N_\mathrm{T} N_\mathrm{R}$, we conclude the advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions,
+			\item \emph{Subspace alignment:} Each group can align the singular vectors of the associated backward-forward (intra-group, multiplicative) channels and direct-indirect (inter-group, additive) channels.
+In \gls{siso}, subspace alignment boils down to phase matching and the optimal scattering matrix of group $g$ that maximizes the channel gain is
 			\begin{equation}
 				\mathbf{\Theta}_g^\star = \exp \bigl(\jmath \mathrm{arg}(h_\mathrm{D})\bigr) \mathbf{V}_{\mathrm{B},g} \mathbf{U}_{\mathrm{F},g}^\mathsf{H},
-				\end{equation}
-				where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr]$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr]$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
-				Diagonal \gls{ris} is thus sufficient for perfect \gls{siso} phase matching (with empty null spaces), but its disadvantage in subspace alignment scales with \gls{mimo} dimensions, since each element can only apply a common phase shift to the ``pinhole'' indirect channel of size $N_\mathrm{R} \times N_\mathrm{T}$ passing through itself.
-				Even if the \gls{bd}-\gls{ris} is fully-connected, there still exists a trade-off between the direct-indirect and backward-forward alignments.
-				\item \textbf{Subchannel rearrangement:} This unique property of \gls{bd}-\gls{ris} allows each group to rearrange and combine the backward and forward subchannels by strength.
-In \gls{siso}, diagonal \gls{ris} provides a maximum indirect channel amplitude of $\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert$, while \gls{bd}-\gls{ris} can generalize it to $\sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert$, where $\pi_{\mathrm{B},g}$ and $\pi_{\mathrm{F},g}$ are permutations of $\mathcal{L} \triangleq \{1, \ldots, L\}$.
-By rearrangement inequality, the maximum is attained by pairing the $l$-th strongest backward and forward subchannels in each group.
-				The advantage of \gls{bd}-\gls{ris} in subchannel rearrangement scales with \gls{mimo} dimensions, since the number of subchannels associated with each group grows with $N_\mathrm{R} \times N_\mathrm{T}$.
+				\label{eq:scattering_siso}
+			\end{equation}
+			where $\mathbf{V}_{\mathrm{B},g} = \bigl[\mathbf{h}_{\mathrm{B},g}/\lVert \mathbf{h}_{\mathrm{B},g} \rVert, \mathbf{N}_{\mathrm{B},g}\bigr] \in \mathbb{U}^{L \times L}$, $\mathbf{U}_{\mathrm{F},g} = \bigl[\mathbf{h}_{\mathrm{F},g}/\lVert \mathbf{h}_{\mathrm{F},g} \rVert, \mathbf{N}_{\mathrm{F},g}\bigr] \in \mathbb{U}^{L \times L}$, and $\mathbf{N}_{\mathrm{B},g}, \mathbf{N}_{\mathrm{F},g} \in \mathbb{C}^{L \times (L-1)}$ are the orthonormal bases of the null spaces of $\mathbf{h}_{\mathrm{B},g}$ and $\mathbf{h}_{\mathrm{F},g}$, respectively.
+			Diagonal \gls{ris} ($L=1$, empty null spaces) thus suffices for perfect phase matching in \gls{siso}.
+			When it comes to \gls{mimo}, each individual scattering element can only apply a common phase shift to the ``pinhole'' indirect channel $\mathbf{H}_g \in \mathbb{C}^{N_\mathrm{R} \times N_\mathrm{T}}$ passing through itself.
+			That is, the disadvantage of diagonal \gls{ris} in subspace alignment scales with \gls{mimo} dimensions.
+			As will be shown later, even if the \gls{bd}-\gls{ris} is unitary, there still exists a tradeoff between the alignment of direct-indirect and backward-forward subspaces.
 		\end{itemize}
-		\end{remark}
+		% \end{remark}
 
@@
 
+	\begin{subsection}{Group-Wise Geodesic \glsfmtshort{rcg}}
+		In this section, we first provide an overview on signal processing techniques for general \gls{bd}-\gls{ris} design problems, then propose a novel group-wise geodesic \gls{rcg} method that exploits the properties of unitary group to operate directly on the Stiefel manifold.
+		% The proposed method is applicable to any smooth optimization problem on the Stiefel manifold and is particularly suitable for \gls{bd}-\gls{ris} design problems.
+		We will later show that the proposed method not only provides better objective value and faster convergence than other approaches, but also works for arbitrary group size and any smooth optimization problem.
+		\begin{subsubsection}{Conventional Techniques}
+			General \gls{bd}-\gls{ris} design techniques can be classified into two categories based on the optimization variable and hardware architecture:
+			\begin{itemize}
+				\item \emph{Scattering matrix $\mathbf{\Theta}$:} This approach is often exploited for asymmetric architectures where the feasible domain of each group is a $L$-dimensional Stiefel manifold $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
+Due to its non-convexity, relevant problems are usually solved by general non-geodesic manifold optimization \cite{Li2023b,Li2023c,Bartoli2023} or relax-then-project methods \cite{Fang2023}.
+The former will be discussed in the next subsection.
+				\item \emph{Reactance matrix $\mathbf{X}$:} This approach is often exploited for symmetric architectures where every pair of elements in the same group are connected by capacitors and inductors.
+According to network theory \cite{Pozar2011}, it maps to the scattering matrix by $\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I})$, which formulates an unconstrained optimization problem on the upper triangular entries of $\{\mathbf{X}_g\}_{g \in \mathcal{G}}$ that is solvable by quasi-Newton methods \cite{Shen2020a}.
+			\end{itemize}
+		\end{subsubsection}
+
+		\begin{subsubsection}{Geodesic vs Non-Geodesic \glsfmtshort{rcg}}
+			We first revisit the general non-geodesic \gls{rcg} method that is applicable to optimization problems over arbitrary manifolds \cite{Absil2009,Pan2022d}.
+			The main idea is to perform {additive} updates along the conjugate direction guided by the Riemannian gradient, then {project} the solution back onto the manifold.
+			% update the feasible point by progressing along conjugate directions then project back to the manifold.
+			% The main idea is to update the feasible point by progressing along conjugate directions then project back to the manifold.
+			For maximization problem with smooth objective $f$ and block-unitary constraint \eqref{eq:bd_ris}, the steps for \gls{bd}-\gls{ris} group $g$ at iteration $r$ are summarized below:
+			\begin{enumerate}
+				\item \emph{Compute the Euclidean gradient \cite{Hjorungnes2007}:} The gradient of $f$ with respect to $\mathbf{\Theta}_g^*$ in the Euclidean space is
+				\begin{equation}
+					\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*};
+					\label{eq:gradient_euclidean}
+				\end{equation}
+				\item \emph{Translate to the Riemannian gradient \cite{Absil2009}:} At point $\mathbf{\Theta}^{(r)}$, the Riemannian gradient lies in the tangent space of the Stiefel manifold $\mathcal{T}_{\mathbf{\Theta}_g^{(r)}}\mathbb{U}^{L \times L} \triangleq \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} \mathbf{\Theta}_g^{(r)} + {\mathbf{\Theta}_g^{(r)\mathsf{H}}} \mathbf{M} = \mathbf{0}\}$.
+It gives the steepest ascent direction of the objective on the manifold can be obtained by projecting the Euclidean gradient onto the tangent space:
+				\begin{equation}
+					% \nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)\mathsf{H}}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}};
+					\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}} \mathbf{\Theta}_g^{(r)};
+					\label{eq:gradient_riemannian}
+				\end{equation}
+				\item \emph{Determine the conjugate direction \cite{Nocedal2006}:} The conjugate direction is obtained over the Riemannian gradient and previous direction as
+				\begin{equation}
+					\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}, % $\mathcal{O}(N_\mathrm{S}^2)$
+					\label{eq:direction_cg}
+				\end{equation}
+				where $\gamma_g^{(r)}$ is the parameter that deviates the conjugate direction from the tangent space for accelerated convergence. A popular choice is the Polak-Ribi\`{e}re formula
+				\begin{equation}
+					\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}; % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+					\label{eq:parameter_cg}
+				\end{equation}
+				\item \emph{Perform additive update \cite{Pan2022d}:} The point is updated by moving along a straight path in the conjugate direction
+				\begin{equation}
+					\bar{\mathbf{\Theta}}_g^{(r+1)} = \mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)},
+					\label{eq:update_additive}
+				\end{equation}
+				where $\mu$ is the step size refinable by the Armijo rule \cite{Armijo1966};
+				\item \emph{Retract for feasibility \cite{Absil2009,Li2023b}:} The resulting point needs to be projected back onto the Stiefel manifold by
+				\begin{equation}
+					\mathbf{\Theta}_g^{(r+1)} = \bar{\mathbf{\Theta}}_g^{(r+1)} \bigl({\bar{\mathbf{\Theta}}_g^{(r+1)\mathsf{H}}} \bar{\mathbf{\Theta}}_g^{(r+1)}\bigr)^{-1/2}.
+					\label{eq:retraction}
+				\end{equation}
+				One can also combine the addition \eqref{eq:update_additive} and retraction \eqref{eq:retraction} in one step
+				\begin{equation}
+					\mathbf{\Theta}_g^{(r+1)} = \bigl(\mathbf{\Theta}_g^{(r)} + \mu \mathbf{D}_g^{(r)}\bigr) \bigl( \mathbf{I} + \mu^2 {\mathbf{D}_g^{(r)\mathsf{H}}} \mathbf{D}_g^{(r)} \bigr)^{-1/2},
+					\label{eq:add_then_retract}
+				\end{equation}
+				and determine the step size therein.
+			\end{enumerate}
+
+			A geodesic is a curve representing the shortest path between two points in a Riemannian manifold, whose tangent vectors remain parallel when transported along the curve.
+			The above method is called non-geodesic since the points are updated in the linear embedding spaces of the manifold by addition and retraction, instead of on the Stiefel manifold itself.
+			Next, we revisit some concepts in differential geometry and introduce a group-wise geodesic \gls{rcg} method on top of \cite{Abrudan2008,Abrudan2009}.
+
+			A Lie group is simultaneously a continuous group and a differentiable manifold.
+			Lie algebra refers to the tangent space of the Lie group at the identity element.
+			The exponential map acts as a bridge between the Lie algebra and Lie group, which allows one to recapture the local group structure using linear algebra techniques.
+			The set of unitary matrices $\mathbb{U}^{L \times L}$ forms a Lie group $U(L)$ under multiplication, and the corresponding Lie algebra $\mathfrak{u}(L) \triangleq \mathcal{T}_{\mathbf{I}}\mathbb{U}^{L \times L} = \{\mathbf{M} \in \mathbb{C}^{L \times L} \mid \mathbf{M}^\mathsf{H} + \mathbf{M} = \mathbf{0}\}$ consists of skew-Hermitian matrices.
+			A geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ can be described by \cite{Edelman1998}
+			\begin{equation}
+				\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D}),
+				\label{eq:geodesic_identity}
+			\end{equation}
+			where $\exp(\mathbf{A}) = \sum_{k=0}^\infty (\mathbf{A}^k/k!)$ is the matrix exponential and $\mu$ is the step size (i.e., magnitude of the tangent vector).
+			Note that the right translation is an isometry in $U(L)$.
+			During the optimization of group $g$, the geodesic evaluated at the identity \eqref{eq:geodesic_identity} should be translated to $\mathbf{\Theta}_g^{(r)}$ for successive updates \cite{Abrudan2008}
+			\begin{equation}
+				\mathbf{G}_g^{(r)}(\mu) = \mathbf{G}_\mathbf{I}(\mu) \mathbf{\Theta}_g^{(r)} = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
+				\label{eq:geodesic_translated}
+			\end{equation}
+			while the Riemannian gradient evaluated at $\mathbf{\Theta}_g^{(r)}$ \eqref{eq:gradient_riemannian} should be translated back to the identity for exploiting the Lie algebra \cite{Abrudan2008}
+			\begin{equation}
+				\tilde{\nabla}_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{R},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} = \nabla_{\mathrm{E},g}^{(r)} \mathbf{\Theta}_g^{(r)\mathsf{H}} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)\mathsf{H}}}.
+				% $\mathcal{O}(2 L^3)$
+				\label{eq:gradient_translated}
+			\end{equation}
+			After gradient translation, the deviation parameter and conjugate direction can be determined similarly to \eqref{eq:parameter_cg} and \eqref{eq:direction_cg}
+			\begin{equation}
+				\tilde{\gamma}_g^{(r)} = \frac{\mathrm{tr}\bigl((\tilde{\nabla}_{\mathrm{R},g}^{(r)} - \tilde{\nabla}_{\mathrm{R},g}^{(r-1)}) {\tilde{\nabla}_{\mathrm{R},g}^{(r)\mathsf{H}}}\bigr)}{\mathrm{tr}\bigl(\tilde{\nabla}_{\mathrm{R},g}^{(r-1)} {\tilde{\nabla}_{\mathrm{R},g}^{(r-1)\mathsf{H}}}\bigr)}.
+% $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
+				\label{eq:parameter_cg_geodesic}
+			\end{equation}
+			\begin{equation}
+				{\mathbf{D}}_g^{(r)} = \tilde{\nabla}_{\mathrm{R},g}^{(r)} + \tilde{\gamma}_g^{(r)} {\mathbf{D}}_g^{(r-1)},
+				\label{eq:direction_cg_geodesic}
+			\end{equation}
+			The solution can thus be updated along the geodesic in a multiplicative rotational manner
+			\begin{equation}
+				\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)},
+				\label{eq:update_geodesic}
+			\end{equation}
+			where an appropriate $\mu$ may be obtained by the Armijo rule.
+			To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, since $\exp^2(\mu \mathbf{D}_g^{(r)}) = \exp(2 \mu \mathbf{D}_g^{(r)})$.
+
+			\begin{algorithm}[!t]
+				\caption{Group-wise geodesic \gls{rcg} for \gls{bd}-\gls{ris} design}
+				\label{ag:rcg}
+				\begin{algorithmic}[1]
+					\Require $f(\mathbf{\Theta})$, $G$
+					\Ensure $\mathbf{\Theta}^\star$
+					\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
+					\Repeat
+						\For {$g \gets 1$ to $G$}
+							\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean} \label{ln:gradient_euclidean}
+							\State $\tilde{\nabla}_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_translated}
+							\State $\tilde{\gamma}_g^{(r)} \gets$ \eqref{eq:parameter_cg_geodesic}
+							\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg_geodesic}
+							\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)\mathsf{H}}} \tilde{\nabla}_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
+								\State $\mathbf{D}_g^{(r)} \gets \tilde{\nabla}_{\mathrm{R},g}^{(r)}$
+							\EndIf
+							\State $\mu \gets 1$
+							\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic_translated}
+							\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$} \label{ln:armijo_start}
+								\State $\mu \gets 2 \mu$
+							\EndWhile
+							\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)\mathsf{H}}}) / 2$}
+								\State $\mu \gets \mu / 2$
+							\EndWhile \label{ln:armijo_end}
+							\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:update_geodesic}
+						\EndFor
+						\State $r \gets r+1$
+					\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
+				\end{algorithmic}
+			\end{algorithm}
+
+			Algorithm~\ref{ag:rcg} summarizes the proposed \gls{bd}-\gls{ris} design framework based on group-wise geodesic \gls{rcg}.
+			Compared to the non-geodesic approach, it leverages the Lie group properties to replace the add-then-retract update \eqref{eq:add_then_retract} with a multiplicative rotational update \eqref{eq:update_geodesic} along the geodesic.
+			This leads to faster convergence and simplifies the step size tuning thanks to appropriate parameter space.
+			% Despite the difference in
+			Convergence to a local optimum is still guaranteed if not initialized at a stationary point.
+			Note that the group-wise updates can be performed in parallel to facilitate large-scale \gls{bd}-\gls{ris} optimization problems.
+			Since block-unitary matrices are also closed under multiplication, one can avoid group-wise updates by directly operating on $\mathbf{\Theta}$ and pinching (i.e., keeping the block diagonal and nulling the other entries) the Euclidean gradient \eqref{eq:gradient_euclidean}, with potentially higher computational complexity and slower convergence.
+		\end{subsubsection}
+	\end{subsection}
+
 	\begin{subsection}{Channel Singular Values Redistribution}
-		\begin{subsubsection}{A Toy Example}\label{sc:toy_example}
-			We first illustrate the channel shaping capabilities of different \gls{ris} by a toy example.
-			% We first use a toy example to illustrate that \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values.
+		\begin{subsubsection}{Toy Example}\label{sc:toy_example}
+			We first illustrate the channel shaping capabilities of different \gls{ris} models by a toy example.
 			Consider a $2 \times 2 \times 2$ setup where the direct link is blocked.
@@
 				\end{bmatrix}.
+				\label{eq:unitary_ris}
 			\end{equation}
@@
 			Fig.~\ref{fg:singular_trend} shows the channel singular values achieved by an exhaustive grid search over $(\theta_1, \theta_2)$ for diagonal \gls{ris} and $(\alpha, \psi)$ for symmetric unitary \gls{ris}.
-			It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements and design parameters.
-			A larger performance gap is expected when asymmetric \gls{bd}-\gls{ris} is available.
+			It is observed that both singular values can be manipulated up to $9\%$ using diagonal \gls{ris} and $42\%$ using symmetric \gls{bd}-\gls{ris}, despite both architectures have the same number of scattering elements.
+			A larger performance gap is expected when the symmetric constraint on \eqref{eq:unitary_ris} can be relaxed.
 			This example shows \gls{bd}-\gls{ris} can provide a wider dynamic range of channel singular values and motivates further studies on channel shaping.
@@
 		\begin{subsubsection}{Pareto Frontier Characterization}\label{sc:pareto_frontier}
-			We then characterize the Pareto frontier of channel singular values by maximizing their weighted sum
+			We then characterize the Pareto frontier of singular values of a general $N_\mathrm{T} \times N_\mathrm{S} \times N_\mathrm{R}$ channel \eqref{eq:channel_equivalent} by maximizing their weighted sum
 			\begin{maxi!}
@@
 			\end{maxi!}
-			where $n \in \{1,\ldots,N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})\}$ and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
-			Varying $\{\rho_n\}$ unveils the entire achievable singular value region.
-			Thus, we claim the Pareto frontier problem~\eqref{op:pareto} generalizes most relevant metrics and provides a powerful shaping framework.
-			The objective \eqref{ob:pareto} is smooth in $\mathbf{\Theta}$ and the feasible domain \eqref{co:pareto_unitary} for group $g$ corresponds to the Stiefel manifold.
-			Next, we zoom out and provide an efficient optimization framework for asymmetric \gls{bd}-\gls{ris}.
-
-			Inspired by \cite{Abrudan2008,Abrudan2009}, we propose a block-wise \gls{rcg} algorithm along the geodesics on the Lie group of unitary matrices $\mathbb{U}^{L \times L}$.
-			It leverages the fact that unitary matrices are closed under multiplication.
-			At iteration $r$, the gradient is computed in the Euclidean space and translated to the Riemannian manifold \cite{Absil2009}
-			\begin{gather}
-				\nabla_{\mathrm{E},g}^{(r)} = \frac{\partial f(\mathbf{\Theta}_g^{(r)})}{\partial \mathbf{\Theta}_g^*},\label{eq:gradient_euclidean}\\
-				\nabla_{\mathrm{R},g}^{(r)} = \nabla_{\mathrm{E},g}^{(r)} {\mathbf{\Theta}_g^{(r)}}^\mathsf{H} - \mathbf{\Theta}_g^{(r)} {\nabla_{\mathrm{E},g}^{(r)}}^\mathsf{H}.\label{eq:gradient_riemannian} % $\mathcal{O}(N_\mathrm{S}^3)$
-			\end{gather}
-			The Polak-Ribierre parameter \cite{Polak1969} is approximated as \cite{Abrudan2009}
-			\begin{equation}
-				\gamma_g^{(r)} = \frac{\mathrm{tr}\bigl((\nabla_{\mathrm{R},g}^{(r)} - \nabla_{\mathrm{R},g}^{(r-1)}) {\nabla_{\mathrm{R},g}^{(r)}}^\mathsf{H}\bigr)}{\mathrm{tr}\bigl(\nabla_{\mathrm{R},g}^{(r-1)} {\nabla_{\mathrm{R},g}^{(r-1)}}^\mathsf{H}\bigr)}, % $\mathcal{O}(2 N_\mathrm{S}^3 + N_\mathrm{S}^2 + 2 N_\mathrm{S})$
-				\label{eq:parameter_cg}
-			\end{equation}
-			and the conjugate direction is
-			\begin{equation}
-				\mathbf{D}_g^{(r)} = \nabla_{\mathrm{R},g}^{(r)} + \gamma_g^{(r)} \mathbf{D}_g^{(r-1)}. % $\mathcal{O}(N_\mathrm{S}^2)$
-				\label{eq:direction_cg}
-			\end{equation}
-			In the Stiefel manifold, the geodesic emanating from $\mathbf{\Theta}_g^{(r)}$ with velocity $\mathbf{D}_g^{(r)}$ and step size $\mu$ is described compactly by the exponential map \cite{Edelman1998}
-			\begin{equation}
-				\mathbf{G}_g^{(r)}(\mu) = \exp(\mu \mathbf{D}_g^{(r)}) \mathbf{\Theta}_g^{(r)}. % $\mathcal{O}(N_\mathrm{S}^3)$
-				\label{eq:geodesic}
-			\end{equation}
-			An appropriate $\mu^\star$ can be obtained by the Armijo rule \cite{Armijo1966}.
-			To double the step size, one can simply square the rotation matrix instead of recomputing the matrix exponential, i.e., $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$.
-			To halve the step size, taking its square root is sufficient in theory but is subject to numerical instability in practice.
-			Finally, the scattering matrix is updated along the geodesic as
-			\begin{equation}
-				\mathbf{\Theta}_g^{(r+1)} = \mathbf{G}_g^{(r)}(\mu^\star).
-				\label{eq:update_geodesic}
-			\end{equation}
-			Algorithm~\ref{ag:rcg} summarizes the proposed block-wise geodesic \gls{rcg} method for smooth maximization problems of asymmetric \gls{bd}-\gls{ris}.
-			Convergence to stationary points is guaranteed.
-
-			\begin{remark}
-				Compared with universal manifold optimization \cite{Absil2009,Pan2022d}, Algorithm~\ref{ag:rcg} inherits a trifold benefit from \cite{Abrudan2008,Abrudan2009}:
-				\begin{enumerate}
-					\item No retraction from Euclidean space to Stiefel manifold thanks to rotational update \eqref{eq:geodesic}, \eqref{eq:update_geodesic};
-					\item Lower computational complexity per iteration;
-					\item Faster convergence thanks to proper parameter space.
-				\end{enumerate}
-			\end{remark}
-
-			% \setalgorithmcaptionfont{\small}
-			\begin{algorithm}[!t]
-				% \small
-				\caption{Block-wise geodesic \gls{rcg} for asymmetric \gls{bd}-\gls{ris}}
-				\label{ag:rcg}
-				\begin{algorithmic}[1]
-					\Require $f(\mathbf{\Theta})$, $G$
-					\Ensure $\mathbf{\Theta}^\star$
-					\Initialize {$r \gets 0$, $\mathbf{\Theta}^{(0)}$}
-					\Repeat
-						\For {$g \gets 1$ to $G$}
-							\State $\nabla_{\mathrm{E},g}^{(r)} \gets$ \eqref{eq:gradient_euclidean} \label{ln:gradient_euclidean}
-							\State $\nabla_{\mathrm{R},g}^{(r)} \gets$ \eqref{eq:gradient_riemannian}
-							\State $\gamma_g^{(r)} \gets$ \eqref{eq:parameter_cg}
-							\State $\mathbf{D}_g^{(r)} \gets$ \eqref{eq:direction_cg}
-							\If {$\Re\bigl\{\mathrm{tr}({\mathbf{D}_g^{(r)}}^\mathsf{H} \nabla_{\mathrm{R},g}^{(r)})\bigr\} < 0$} \Comment{not an ascent direction}
-								\State $\mathbf{D}_g^{(r)} \gets \nabla_{\mathrm{R},g}^{(r)}$
-							\EndIf
-							\State $\mu \gets 1$
-							\State $\mathbf{G}_g^{(r)}(\mu) \gets$ \eqref{eq:geodesic}
-							\While {$f\bigl(\mathbf{G}_g^{(r)}(2\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) \ge \mu \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
-								\State $\mu \gets 2 \mu$
-							\EndWhile
-							\While {$f\bigl(\mathbf{G}_g^{(r)}(\mu)\bigr) - f(\mathbf{\Theta}_g^{(r)}) < \mu / 2 \cdot \mathrm{tr}(\mathbf{D}_g^{(r)} {\mathbf{D}_g^{(r)}}^\mathsf{H}) / 2$}
-								\State $\mu \gets \mu / 2$
-							\EndWhile
-							\State $\mathbf{\Theta}_g^{(r+1)} \gets$ \eqref{eq:update_geodesic}
-						\EndFor
-						\State $r \gets r+1$
-					\Until $\lvert f(\mathbf{\Theta}^{(r)}) - f(\mathbf{\Theta}^{(r-1)}) \rvert / f(\mathbf{\Theta}^{(r-1)}) \le \epsilon$
-				\end{algorithmic}
-			\end{algorithm}
+			where $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, $N \triangleq \min(N_\mathrm{T}, N_\mathrm{R})$ is the maximum channel rank, and $\rho_n$ is the weight of the $n$-th singular value that can be positive, zero, or negative.
+			Varying $\{\rho_n\}_{n \in \mathcal{N}}$ characterizes the Pareto frontier that encloses the entire singular value region.
+			Thus, we claim problem \eqref{op:pareto} generalizes most singular value shaping problems.
+			It can be solved optimally by Algorithm~\ref{ag:rcg} with the Euclidean gradient given by Lemma \ref{lm:pareto_gradient}.
+			% It can be solved optimally by Algorithm~\ref{ag:rcg} where line \ref{ln:gradient_euclidean} uses the following Euclidean gradient expression \eqref{eq:pareto_gradient}.
 
@@
 				\end{equation}
-				where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}$, respectively.
+				where $\mathbf{U}$ and $\mathbf{V}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
 			\end{lemma}
@@
 
-			%  The Euclidean gradient of \gls{bd}-\gls{ris} group $g$ is computed as
-			% where $\mathbf{U} \in \mathbb{C}^{N_\mathrm{R} \times N}$ and $\mathbf{V} \in \mathbb{C}^{N_\mathrm{T} \times N}$ are the left and right compact singular matrices of $\mathbf{H}$, respectively.
-			Algorithm~\ref{ag:rcg} can thus be invoked for the Pareto singular value problem \eqref{op:pareto} where line \ref{ln:gradient_euclidean} uses \eqref{eq:pareto_gradient} explicitly.
-			% \eqref{eq:pareto_gradient} is used in line \ref{ln:gradient_euclidean}.
+			We then analyze the computational complexity of solving Pareto singular value problem \eqref{op:pareto} by Algorithm~\ref{ag:rcg}.
+			To update each \gls{bd}-\gls{ris} group, compact \gls{svd} of $\mathbf{H}$ requires $\mathcal{O}(N N_\mathrm{T} N_\mathrm{R})$, Euclidean gradient \eqref{eq:pareto_gradient} requires $\mathcal{O}\bigl(L N (N_\mathrm{T}+N_\mathrm{R}+L+1) \bigr)$, Riemannian gradient translation \eqref{eq:gradient_translated} requires $\mathcal{O}(L^3)$, deviation parameter \eqref{eq:parameter_cg_geodesic} and conjugate direction \eqref{eq:direction_cg_geodesic} together require $\mathcal{O}(L^2)$, and matrix exponential \eqref{eq:update_geodesic} requires $\mathcal{O}(L^3)$ operations \cite{Moler2003}.
+			The overall complexity is thus $\mathcal{O}\bigl(I_\text{RCG} G \bigl(N N_\mathrm{T} N_\mathrm{R} + L N (N_\mathrm{T}+N_\mathrm{R}+L+1) + I_\text{BLS} L^3\bigr)\bigr)$, where $I_\text{RCG}$ and $I_\text{BLS}$ are the number of iterations for geodesic \gls{rcg} and backtracking line search (line \ref{ln:armijo_start}--\ref{ln:armijo_end} of Algorithm \ref{ag:rcg}), respectively.
 		\end{subsubsection}
@@
 		\begin{subsubsection}{Some Analytical Bounds}\label{sc:bounds}
-			We then discuss some interesting analytical bounds related to channel singular values.
+			We then discuss some analytical bounds related to channel singular values.
 			\begin{proposition}[Degree of freedom]\label{pp:dof}
@@
 			\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
-				% If the forward/backward channel is rank-$k$, then a \gls{bd}-\gls{ris} can at most enlarge the $n$-th ($n > k$) channel singular value to the $n-k$-th singular value of $\mathbf{T}$, or suppress the $n$-th ($n < N - k + 1$) channel singular value to the $n$-th singular value of $\mathbf{T}$.
-				% If the forward/backward channel is rank-$k$, then a sufficiently large \gls{bd}-\gls{ris} can at most enlarge (resp.
-suppress) the first (resp.
-last) $k$ equivalent channel singular values without bounds.
-				If the forward or backward channel is rank-$k$, then regardless of the \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
+				If the forward or backward channel is rank-$k$ ($k \le N$), then regardless of the passive \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
+				\begin{subequations}
 					\begin{align}
@@
 					\end{align}
+					\label{iq:sv_bound_rank_deficient}
+				\end{subequations}
 				where
-				% \begin{align}
-				% 	\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
-				% 	\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k.
-				% \end{align}
 				\begin{equation}
@@
 				and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
-				% where $\mathbf{T} \mathbf{T}^\mathsf{H} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the forward channel is rank-$k$ and $\mathbf{T}^\mathsf{H} \mathbf{T} = \mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{U}_\mathrm{F} \mathbf{U}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}$ if the backward channel is rank-$k$.
 			\end{proposition}
@@
 
-			% \begin{corollary}[degree of freedom]
-			% 	In point-to-point \gls{mimo} with or without direct link, \gls{bd}-\gls{ris} cannot provide a higher \gls{dof} than diagonal \gls{ris}.
-			% \end{corollary}
-
 			\begin{corollary}[Extreme singular values\label{co:extreme}]
-				With a sufficiently large \gls{ris}, the first $k$ channel singular values are unbounded above \footnote{\textellipsis while respecting energy conservation law $\sum_n \sigma_n^2 \le 1$.
-This constraint is omitted in the following context.} while the last $k$ channel singular values can be suppressed to zero.
-				% For a rank-$k$ forward or backward channel with a sufficiently large \gls{ris}, the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
-				% If the forward or backward channel is rank-$k$ and the \gls{ris} is sufficiently large, then the first $k$ singular values of the equivalent channel are unbounded above while the last $k$ singular values can be suppressed to zero.
-				% If the forward/backward channel is rank-$k$, then the first (resp. last) $k$ singular values of the equivalent channel are unbounded above (resp. below).
-				% a sufficiently large \gls{ris} can at most enlarge (resp. suppress) the first (resp. last) $k$ singular values of the equivalent channel without bounds.
+				With a sufficiently large passive \gls{ris} of arbitrary architecture, the first $k$ channel singular values are unbounded above\footnote{The energy conservation law $\sum_n \sigma_n^2(\mathbf{H}) \le 1$ still has to be respected.
+This constraint is omitted in the following context for brevity.} while the last $k$ channel singular values can be suppressed to zero.
 			\end{corollary}
 
-			\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} in \cite{Semmler2023}.}\label{co:los}]
-				If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
+			\begin{proof}
+				This is a direct result of \eqref{iq:sv_bound_rank_deficient}.
+			\end{proof}
+
+			\begin{corollary}[\gls{los} channel\footnote{A similar result has been derived for diagonal \gls{ris} \cite{Semmler2023}.}\label{co:los}]
+				% If the forward or backward channel is \gls{los}, then a \gls{ris} can at most enlarge (resp.
 suppress) the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th (resp.
 $n$-th) singular value of $\mathbf{T}$, that is,
+				If the forward or backward channel is \gls{los}, then a passive \gls{ris} of arbitrary architecture can at most enlarge the $n$-th ($n \ge 2$) channel singular value to the $(n-1)$-th singular value of $\mathbf{T}$, or suppress the $n$-th channel singular value to the $n$-th singular value of $\mathbf{T}$.
+				That is,
 				\begin{equation}
@@
 
-			In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris}.
-
-			\begin{proposition}[Fully-connected \gls{ris} without direct link]\label{pp:fully_connected}
-				% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-				If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the channel singular values can be manipulated up to
-				% If the \gls{bd}-\gls{ris} is fully-connected and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
+			\begin{proof}
+				This is a direct result of \eqref{iq:sv_bound_rank_deficient} with $k = 1$.
+			\end{proof}
+
+			In Section~\ref{sc:simulation}, we will show by simulation that a finite-size \gls{bd}-\gls{ris} can better approach those bounds than diagonal \gls{ris}.
+
+			\begin{proposition}[Unitary \gls{ris} without direct link]\label{pp:fully_connected}
+				% If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the singular value bounds on $\mathbf{H}$ are equivalent to the singular value bounds on $\mathbf{BF}$, where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
+				If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the channel singular values can be manipulated up to
+				% If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the bounds on the channel singular values are equivalent to the singular values of the equivalent channel, that is,
 				% only bounds that apply here are those that apply to the singular values of
@@
 
-			The problem now becomes \emph{how the singular values of matrix product are bounded by the singular values of its individual factors.}
-			Let $N' = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le N'$.
+			The problem now becomes, how the singular values of matrix product are bounded by the singular values of its individual factors.
+			Let $\bar{N} = \max(N_\mathrm{T},N_\mathrm{S},N_\mathrm{R})$ and $\sigma_n(\mathbf{H})=\sigma_n(\mathbf{H}_\mathrm{F})=\sigma_n(\mathbf{H}_\mathrm{B})=0$ for $N < n \le \bar{N}$.
 			We have the following corollaries.
 
-			\begin{corollary}[Generic singular value bounds]
+			\begin{corollary}[Generic singular value bounds\label{co:sv_bound_horn}]
 				\begin{equation}
@@
 				\end{equation}
-				for all admissible triples $(I, J, K) \in T_r^{N'}$ with $r < N'$, where
+				for all admissible triples $(I, J, K) \in T_r^{\bar{N}}$ with $r < \bar{N}$, where
 				\begin{equation*}
 					\begin{gathered}
-						% T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
+						% T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \mid \text{for all } p < r \text{ and all } (F, G, H) \text{ in } T_p^r,\\
 						% \sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
-						T_r^{N'} \triangleq \Bigl\{(I, J, K) \in U_r^{N'} \mid \forall p < r, (F, G, H) \in T_p^r,\\
+						T_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \in U_r^{\bar{N}} \mid \forall p < r, (F, G, H) \in T_p^r,\\
 						\sum_{f \in F} i_f + \sum_{g \in G} j_g \le \sum_{h \in H} k_h + p(p+1)/2 \Bigr\},
@@
 				\begin{equation*}
-					U_r^{N'} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
+					U_r^{\bar{N}} \triangleq \Bigl\{(I, J, K) \mid \sum_{i \in I} i + \sum_{j \in J} j = \sum_{k \in K} k + r(r+1)/2\Bigr\}.
 				\end{equation*}
 			\end{corollary}
-			\begin{proof}
-				Please refer to \cite[Theorem 8]{Fulton2000}. This implies the Corollaries~\ref{co:largest_singular_value} and \ref{co:product_singular_values}.
-			\end{proof}
-
-			\begin{corollary}[Upper bound on the largest singular value]\label{co:largest_singular_value}
+
+			\begin{proof}
+				Please refer to \cite[Theorem~8]{Fulton2000}.
+			\end{proof}
+
+			Corollary \eqref{co:sv_bound_horn} is by far the most comprehensive singular value bound over Proposition~\ref{pp:fully_connected}, which is also recognized as a variation of Horn's inequality \cite{Bhatia2001}.
+			It is worth mentioning that the number of admissible triples (and bounds) grows exponentially with $\bar{N}$.
+			For example, the number of inequalities described by \eqref{iq:sv_bound_fc} grows from 12 to 2062 when $\bar{N}$ increases from 3 to 7.
+			This renders it computationally expensive for applications in large-scale \gls{mimo} systems.
+			Next, we showcase some useful inequalities enclosed by \eqref{iq:sv_bound_fc}.
+			Readers are referred to \cite[Chapter 16, 24]{Hogben2013} for more examples.
+
+			\begin{corollary}[Upper bound on the largest singular value\label{co:sv_largest}]
 				\begin{equation}
@@
 
-			% \begin{corollary}[lower bound on the smallest singular value]
+			\begin{proof}
+				This is a direct result of \eqref{iq:sv_bound_fc} with $r = 1$.
+			\end{proof}
+
+			\begin{corollary}[Lower bound on the smallest singular value\label{co:sv_smallest}]
+				\begin{equation}
+					\sigma_{\bar{N}}(\mathbf{H}) \ge \sigma_{\bar{N}}(\mathbf{H}_\mathrm{B}) \sigma_{\bar{N}}(\mathbf{H}_\mathrm{F}).
+				\end{equation}
+			\end{corollary}
+
+			\begin{proof}
+				This can be deducted from \eqref{iq:sv_bound_fc} with $r_1 = \bar{N}{-}1$ and $r_2 = \bar{N}$.
+			\end{proof}
+
+			\begin{corollary}[Upper bound on the product of first $k$ singular values]
+				\begin{equation}
+					\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
+				\end{equation}
+			\end{corollary}
+
+			\begin{proof}
+				This is a direct result of \eqref{iq:sv_bound_fc} with $r = k$.
+			\end{proof}
+
+			\begin{corollary}[Lower bound on the product of last $k$ singular values\label{co:sv_product_smallest}]
+				\begin{equation}
+					\prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=\bar{N}}^{\bar{N}-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
+				\end{equation}
+			\end{corollary}
+
+			\begin{proof}
+				This can be deducted from \eqref{iq:sv_bound_fc} with $r_1 = \bar{N}-k$ and $r_2 = \bar{N}$.
+			\end{proof}
+
+			Corollaries \ref{co:sv_smallest} and \ref{co:sv_product_smallest} are less informative when $\bar{N} \ne N$ (i.e., unequal number of transmit, scatter, and receive antennas) as the lower bounds would coincide at zero.
+
+			% \begin{corollary}[Upper bound on the sum of first $k$ singular values to the positive $p$-th power\label{co:sum_power} {\cite[Inequality~24.4.7]{Hogben2013}}]
 			% 	\begin{equation}
-			% 		\sigma_{N'}(\mathbf{H}) \ge \sigma_{N'}(\mathbf{H}_\mathrm{B}) \sigma_{N'}(\mathbf{H}_\mathrm{F}).
+			% 		\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
+			% 		\label{iq:sv_bound_fc_power}
+			% 	\end{equation}
+			% 	When $k = N$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels
+			% 	\begin{equation}
+			% 		\lVert \mathbf{H} \rVert _\mathrm{F}^2 \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}),
 			% 	\end{equation}
@@
 
-			\begin{corollary}[Upper bound on the product of first $k$ singular values]\label{co:product_singular_values}
-				\begin{equation}
-					\prod_{n=1}^k \sigma_n(\mathbf{H}) \le \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=1}^k \sigma_n(\mathbf{H}_\mathrm{F}).
+			\begin{corollary}[Upper bound on the channel power gain\label{co:sum_power}]
+				% The channel power gain is upper bounded by the sum of sorted element-wise power product of backward and forward subchannels
+				The channel power gain is upper bounded by the sum of sorted element-wise product of squared singular values of backward and forward subchannels
+				\begin{equation}
+					\lVert \mathbf{H} \rVert _\mathrm{F}^2 = \sum_{n=1}^N \sigma_n^2(\mathbf{H}) \le \sum_{n=1}^N \sigma_n^2(\mathbf{H}_\mathrm{B}) \sigma_n^2(\mathbf{H}_\mathrm{F}).
+					\label{iq:power_gain}
 				\end{equation}
@@
 
-			% \begin{corollary}[lower bound on the product of last $k$ singular values]
-			% 	\begin{equation}
-			% 		\prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}) \ge \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{B}) \prod_{n=N'}^{N'-k+1} \sigma_n(\mathbf{H}_\mathrm{F}).
-			% 	\end{equation}
-			% \end{corollary}
-
-			\begin{corollary}[Upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
-				\begin{equation}
-					\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
-					\label{iq:sv_bound_fc_power}
-				\end{equation}
-				When $k = N'$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels.
-			\end{corollary}
-			\begin{proof}
-				Please refer to \cite[Inequality 24.4.7]{Hogben2013}.
-			\end{proof}
-
-			\begin{remark}
-				It is straightforward to verify \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
-				\begin{equation}
-					\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
-					\label{eq:scattering_fc_tight}
-				\end{equation}
-				where $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively.
-			\end{remark}
-
-			Tight bounds are inapplicable when a \gls{mimo} direct link is present, as the \gls{ris} needs to balance the direct-indirect (additive) and backward-forward (multiplicative) subspace alignments.
-			Such a balance often involves optimization approaches discussed in Section~\ref{sc:pareto_frontier}. Another example will be discussed in Section~\ref{sc:low_complexity}.
-		\end{subsubsection}
-
+			\begin{proof}
+				Please refer to \cite[Inequality~24.4.7]{Hogben2013}.
+			\end{proof}
+
+			To achieve the equalities in Corollaries \eqref{co:sv_largest} -- \eqref{co:sum_power}, the \gls{ris} needs to completely align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$.
+			The resulting scattering matrix is generally required to be unitary
+			\begin{equation}
+				\mathbf{\Theta}^\star = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H},
+				\label{eq:scattering_fc_optimal}
+			\end{equation}
+			which can be concluded from \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in Appendix~\ref{ap:fully_connected}.
+			Interestingly, diagonal \gls{ris} can attain those equalities if and only if $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both rank-1.
+			In such case, the equivalent channel reduces to $\mathbf{H} = \sigma_\mathrm{B} \sigma_\mathrm{F} \mathbf{u}_\mathrm{B} \mathbf{v}_\mathrm{B}^\mathsf{H} \mathbf{\Theta} \mathbf{u}_\mathrm{F} \mathbf{v}_\mathrm{F}^\mathsf{H}$ and the \gls{ris} only needs to align $\mathbf{v}_\mathrm{B}^\mathsf{H}$ and $\mathbf{u}_\mathrm{F}$ by
+			\begin{equation}
+				\mathbf{\Theta}^\star = \mathbf{v}_\mathrm{B} \mathbf{u}_\mathrm{F}^\mathsf{H} \odot \mathbf{I},
+			\end{equation}
+			which becomes a special case of \eqref{eq:scattering_siso}.
+			On the other hand, when $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ are both in Rayleigh fading, the expected maximum channel power gain $\mathbb{E}\bigl\{ \lVert \mathbf{H} \rVert _ \mathrm{F} \bigr\}_{\max}$ can be evaluated as
+			\begin{equation}
+				\sum_{n=1}^N \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{R},N_\mathrm{S})}}(x_n) d x_n \int_0^\infty f_{\lambda_n^{\min(N_\mathrm{S},N_\mathrm{T})}}(x_n) d x_n,
+				\label{eq:power_gain_rayleigh}
+			\end{equation}
+			where $\lambda_n^{K}$ is the $n$-th eigenvalue of the complex $K \times K$ Wishart matrix with probability density function $f_{\lambda_n^{K}}(x_n)$ given by \cite[Equation 51]{Zanella2009}.
+			We notice \eqref{eq:power_gain_rayleigh} is a generalization of \cite[Equation 58]{Shen2020a} to \gls{mimo}.
+
+			Tighter bounds are generally inapplicable when the direct link is present or the \gls{bd}-\gls{ris} is not unitary, since the direct-indirect channels and backward-forward channels cannot be completely aligned at the same time.
+			In such case, we can exploit optimization approaches from a singular value perspective (Section~\ref{sc:pareto_frontier}) or a power gain perspective (Section~\ref{sc:power}).
+		\end{subsubsection}
 	\end{subsection}
 
-	\begin{subsection}{Achievable Rate Maximization}\label{sc:rate}
-		The \gls{mimo} achievable rate maximization problem can be formulated with respect to joint active and passive beamforming.
-		This problem is different from channel shaping because the \gls{ris} is jointly design with the transmitter for an explicit objective
+	\begin{subsection}{Power Gain and Achievable Rate Maximization}\label{sc:power_rate}
+		\begin{subsubsection}{Channel Power Gain}\label{sc:power}
+			The \gls{mimo} channel power gain maximization problem is formulated with respect to the \gls{bd}-\gls{ris} scattering matrix
+			\begin{maxi!}
+				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
+				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+			\end{maxi!}
+			which generalizes the case of \gls{siso} \cite{Shen2020a}, \gls{miso} \cite{Santamaria2023,Fang2023}, single-stream \gls{mimo} \cite{Nerini2023,Nerini2023b}, and direct link-blocked \gls{mimo} with unitary \gls{ris} \eqref{eq:scattering_fc_optimal}.
+			The key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
+			Interestingly, in terms of maximizing the inner product $\langle \mathbf{H}_\mathrm{D}, \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rangle$, \eqref{op:power_passive} is reminiscent of the weighted orthogonal Procrustes problem \cite{Gower2004}
+			\begin{mini!}
+				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
+				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{\label{cs:power_block_unitary}}{}
+			\end{mini!}
+			which relaxes the block-unitary constraint \eqref{cs:power_block_unitary} to unitary but still has no trivial solution.
+			One lossy transformation exploits the Moore-Penrose inverse and moves $\mathbf{\Theta}$ to one side of the product \cite{Bell2003}, formulating two standard orthogonal Procrustes problems
+			\begin{mini!}
+				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
+				\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
+			\end{mini!}
+			which have global optimal solutions
+			\begin{equation}
+				\mathbf{\Theta} = \mathbf{U} \mathbf{V}^\mathsf{H},
+				\label{eq:orthogonal_procrustes_solution}
+			\end{equation}
+			where $\mathbf{U}$ and $\mathbf{V}$ are respectively the left and right compact singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
+			We emphasize that \eqref{eq:scattering_fc_optimal} and \eqref{eq:orthogonal_procrustes_solution} are valid unitary \gls{ris} solutions to \eqref{op:power_passive} when the direct link is absent and present, but the latter is neither optimal nor a generalization of the former due to the lossy transformation.
+
+			Inspired by \cite{Nie2017}, we propose an optimal solution to problem \eqref{op:power_passive} with arbitrary group size.
+			The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form by group-wise \gls{svd}.
+
+			\begin{proposition}\label{pp:power}
+				Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
+				\begin{equation}
+					\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
+					\label{eq:scattering_power}
+				\end{equation}
+				converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrices of
+				\begin{equation}
+					\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
+					\label{eq:auxiliary_matrix_power}
+				\end{equation}
+			\end{proposition}
+
+			\begin{proof}
+				Please refer to Appendix~\ref{ap:power}.
+			\end{proof}
+
+			We then analyze the computational complexity of solving channel gain maximization problem \eqref{op:power_passive} by Proposition \ref{pp:power}.
+			To update each \gls{bd}-\gls{ris} group, matrix multiplication \eqref{eq:auxiliary_matrix_power} requires $\mathcal{O}\bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L)\bigr)$ operations and its compact \gls{svd} requires $\mathcal{O}(L^3)$ operations.
+			The overall complexity is thus $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr)\bigr)$, where $I_\text{SAA}$ is the number iterations for successive affine approximation.
+		\end{subsubsection}
+
+		\begin{subsubsection}{Achievable Rate Maximization}\label{sc:rate}
+			We aim to maximize the achievable rate of the \gls{bd}-\gls{ris}-aided \gls{mimo} system by jointly optimizing the active and passive beamforming
 			\begin{maxi!}
 				{\scriptstyle{\mathbf{W},\mathbf{\Theta}}}{R = \log \det \biggl(\mathbf{I} + \frac{\mathbf{W}^\mathsf{H}\mathbf{H}^\mathsf{H}\mathbf{H}\mathbf{W}}{\eta}\biggr)}{\label{op:rate}}{\label{ob:rate}}
-			\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2 \le P}{}{}
-			\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
+				\addConstraint{\lVert \mathbf{W} \rVert _\mathrm{F}^2}{\le P}
+				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g}{=\mathbf{I}, \quad \forall g,\label{cs:rate_block_unitary}}
 			\end{maxi!}
-		where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the noise power, and $P$ is the transmit power budget.
-		Next, we propose a local-optimal solution based on joint \gls{ris}-transceiver design and a low-complexity decoupled solution based on channel shaping.
-
-		\begin{subsubsection}{Alternating Optimization}
-			Consider an \gls{ao} approach that updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively.
+			where $\mathbf{W}$ is the transmit precoder, $R$ is the achievable rate, $\eta$ is the average noise power, and $P$ is the transmit power constraint.
+			Problem \eqref{op:rate} is non-convex due to the block-unitary constraint \eqref{cs:rate_block_unitary} and the coupling between variables.
+			We propose a local-optimal approach via \gls{ao} and a low-complexity approach based on channel shaping.
+
+			\begin{paragraph}{Alternating Optimization}
+				This approach updates $\mathbf{\Theta}$ and $\mathbf{W}$ iteratively until convergence.
 				For a given $\mathbf{W}$, the passive beamforming subproblem is
@@
 				where $\mathbf{Q} \triangleq \mathbf{W} \mathbf{W}^\mathsf{H}$ is the transmit covariance matrix.
+				Problem \eqref{op:rate_passive} can be solved optimally by Algorithm \ref{ag:rcg} with the Euclidean gradient given by Lemma \ref{lm:rate_gradient}.
 				\begin{lemma}\label{lm:rate_gradient}
@@
 				\end{proof}
-			Algorithm \ref{ag:rcg} is then invoked to solve problem \eqref{op:rate} where line \ref{ln:gradient_euclidean} uses \eqref{eq:rate_gradient} explicitly.
-			Since \eqref{ob:rate_passive} is a concave function of $\mathbf{\Theta}$, convergence to local-optimal points is guaranteed.
-			On the other hand, the global optimal transmit precoder for a fixed $\mathbf{\Theta}$ is given by the eigenmode transmission \cite{Clerckx2013}
-			\begin{equation}
-				\mathbf{W}^\star = \mathbf{V} {\mathbf{S}^\star}^{1/2},
+				For a given $\mathbf{\Theta}$, the global optimal transmit precoder is given by eigenmode transmission \cite{Clerckx2013}
+				\begin{equation}
+					\mathbf{W}^\star = \mathbf{V} {\mathrm{diag}(\mathbf{s}^\star)}^{1/2},
 					\label{eq:precoder_eigenmode}
 				\end{equation}
-			where $\mathbf{V}$ is the right channel singular matrix and $\mathbf{S}^\star$ is the optimal water-filling power allocation matrix.
-			The overall \gls{ao} algorithm converges to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
-		\end{subsubsection}
-
-		\begin{subsubsection}{Low-Complexity Solution}\label{sc:low_complexity}
-			We then propose a low-complexity solution to problem \eqref{op:rate} based on channel shaping.
-			The passive beamforming subproblem \eqref{op:rate_passive} involves transmit covariance matrix $\mathbf{Q}$ and thus requires iterative \gls{rcg} update.
-			Instead, we decouple the joint \gls{ris}-transceiver design by recasting \eqref{op:rate_passive} as channel power maximization
-			\begin{maxi!}
-				{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:power_passive}}{\label{ob:power_passive}}
-				\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g.}{}{}
-			\end{maxi!}
-			% which only accounts for channel characteristics but has no trivial solution.
-			\begin{remark}
-				As mentioned in Section \ref{sc:bounds}, the key of solving \eqref{op:power_passive} is to balance the additive and multiplicative subspace alignments.
-				Problem \eqref{op:power_passive} is very similar (in terms of maximizing the inner product of $\mathbf{H}_\mathrm{D}$ and $\mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F}$) to the weighted orthogonal Procrustes problem \cite{Gower2004}
-				\begin{mini!}
-					{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{D} - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2}{\label{op:weighted_orthogonal_procrustes}}{}
-					\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
-				\end{mini!}
-				which has no trivial solution.
-				One lossy transformation, by moving $\mathbf{\Theta}$ to one side \cite{Bell2003}, formulates standard orthogonal Procrustes problems
-				\begin{mini!}
-					{\scriptstyle{\mathbf{\Theta}}}{\lVert \mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} - \mathbf{\Theta} \mathbf{H}_\mathrm{F} \rVert _\mathrm{F}^2 \text{ or } \lVert \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger - \mathbf{H}_\mathrm{B} \mathbf{\Theta} \rVert _\mathrm{F}^2}{\label{op:standard_orthogonal_procrustes}}{}
-					\addConstraint{\mathbf{\Theta}^\mathsf{H} \mathbf{\Theta}=\mathbf{I},}{}{}
-				\end{mini!}
-				which has global optimal solutions
-				\begin{equation}
-					\mathbf{\Theta}^\star = \mathbf{U} \mathbf{V}^\mathsf{H}
-					\label{eq:orthogonal_procrustes_solution}
-				\end{equation}
-				where $\mathbf{U}$ and $\mathbf{V}$ are the left and right singular matrices of $\mathbf{H}_\mathrm{B}^\dagger \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\mathsf{H}$ or $\mathbf{H}_\mathrm{B}^\mathsf{H} \mathbf{H}_\mathrm{D} \mathbf{H}_\mathrm{F}^\dagger$ \cite{Golub2013}.
-				It is worth noticing this suboptimal one-step solution only applies to fully-connected \gls{bd}-\gls{ris}.
-			\end{remark}
-
-			Inspired by \cite{Nie2017}, we propose a solution to problem \eqref{op:power_passive} with arbitrary group size.
-			The idea is to successively approximate the quadratic objective \eqref{ob:power_passive} by local Taylor expansions and solve each step in closed form.
-
-			\begin{proposition}\label{pp:power}
-				Starting from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
-				\begin{equation}
-					\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g.
-					\label{eq:scattering_power}
-				\end{equation}
-				converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
-				\begin{equation}
-					\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
-					\label{eq:auxiliary_matrix_power}
-				\end{equation}
-			\end{proposition}
-
-			\begin{proof}
-				Please refer to Appendix~\ref{ap:power}.
-			\end{proof}
-			Once the channel shaping problem \eqref{op:power_passive} is solved, the transmit precoder can be obtained by \eqref{eq:precoder_eigenmode}.
-			This two-stage approach decouples both blocks and is computationally more efficient than the geodesic \gls{rcg} method.
+				where $\mathbf{V}$ is the right singular matrix of the equivalent channel and $\mathbf{s}^\star$ is the optimal water-filling power allocation obtainable by the iterative method \cite{Tse2005}.
+
+				The \gls{ao} algorithm is guaranteed to converge to local-optimal points of problem \eqref{op:rate} since each subproblem is solved optimally and the objective is bounded above.
+				Similar to the analysis in Section \ref{sc:pareto_frontier}, the computational complexity of solving subproblem \eqref{op:rate_passive} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3)\bigr)$.
+				On the other hand, the complexity of solving active beamforming subproblem by \eqref{eq:precoder_eigenmode} is $\mathcal{O}\bigl(N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+				The overall complexity is thus $\mathcal{O}\bigl(I_\text{AO}\bigl(I_\text{RCG} G (NL^2 + L N_\mathrm{T} N_\mathrm{R} + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + N_\mathrm{R}^3 + I_\text{BLS} L^3) + N N_\mathrm{T} N_\mathrm{R}\bigr)\bigr)$, where $I_\text{AO}$ is the number of iterations for \gls{ao}.
+			\end{paragraph}
+
+			\begin{paragraph}{Low-Complexity Solution}\label{sc:low_complexity}
+				We then propose a suboptimal two-stage solution to problem \eqref{op:rate} that decouples the joint \gls{ris}-transceiver design.
+				The idea is to first consider channel shaping and replace the rate maximization subproblem \eqref{op:rate_passive} by channel power gain maximization problem \eqref{op:power_passive}, then proceed to conventional eigenmode transmission \eqref{eq:precoder_eigenmode}.
+				Both steps are solved in closed form and the computational complexity is $\mathcal{O}\bigl(I_\text{SAA} G \bigl(N_\mathrm{T} N_\mathrm{R} + (G+1)(NL^2+N_\mathrm{T} N_\mathrm{R} L) + L^3\bigr) + N N_\mathrm{T} N_\mathrm{R}\bigr)$.
+				While suboptimal, this shaping-inspired solution avoids outer iterations and implements inner iterations more efficiently.
+			\end{paragraph}
 		\end{subsubsection}
 	\end{subsection}
+
 \end{section}
@@
 	The indirect path via \gls{ris} is thus \qty{35}{\dB} weaker than the direct path.
-	$\kappa \to \infty$ is assumed for all channels unless otherwise specified.
+	Rayleigh fading (i.e., $\kappa = 0$) is assumed for all channels unless otherwise specified.
 
@@
 			\footnotesize
-			\caption{Average performance of \gls{rcg} algorithms on problem \eqref{op:pareto}. Minimum relative gain per iteration $\epsilon=\num{e-4}$ and number of channel realizations $T=100$.}
+			\caption{Average Performance of Geodesic and Non-Geodesic \gls{rcg} Algorithms on Problem \eqref{op:pareto}}
 			\label{tb:complexity_test}
@@
 												& Objective                             & Iterations                             & Time [s]         & Objective        & Iterations & Time [s] \\ \midrule
-				Geodesic                        & $\num{4.355e-3}$                       & 11.61                                  & $\num{2.038e-2}$ & $\num{1.164e-2}$ & 25.78      & 3.216     \\
-				Non-geodesic                    & $\num{4.168e-3}$                       & 169.5                                  & $\num{1.420e-1}$ & $\num{8.873e-3}$ & 278.1      & 27.81     \\ \bottomrule
+				Geodesic                        & $\num{4.359e-3}$                      & 11.59                                  & $\num{1.839e-2}$ & $\num{1.163e-2}$ & 25.58      & 3.461    \\
+				Non-geodesic                    & $\num{4.329e-3}$                      & 30.92                                  & $\num{5.743e-2}$ & $\num{1.116e-2}$ & 61.40      & 13.50    \\ \bottomrule
 			\end{tabular}
@@
 
-		We first compare the proposed geodesic \gls{rcg} algorithm with the general non-geodesic approach \cite{Absil2009,Pan2022d} on problem \eqref{op:pareto}.
-		It is observed that the geodesic \gls{rcg} algorithm achieves a slightly higher objective value with significantly (around 10$\times$) lower number of iterations and shorter computational time than the non-geodesic one.
-		The results suggest that the proposed optimization framework is very efficient for asymmetric \gls{bd}-\gls{ris} design.
-		If the scattering matrix has to be symmetric, one can project the solution to the feasible domain by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.
+		We first compare the geodesic and non-geodesic \gls{rcg} algorithm on problem \eqref{op:pareto} in a 4T4R system with \gls{bd}-\gls{ris} group size $L=4$.
+		The statistics are averaged over \num{100} independent runs.
+		It is observed that the geodesic \gls{rcg} method achieves a slightly higher objective value with significantly (up to 3$\times$) lower number of iterations and shorter (up to 4$\times$) computational time than the non-geodesic method.
+		The results demonstrate the efficiency of the proposed geodesic \gls{rcg} algorithm especially in large-scale \gls{bd}-\gls{ris} design problems.
+		If the scattering matrix is constrained to be symmetric, one can project the solution to the feasible domain by $\mathbf{\Theta} \gets (\mathbf{\Theta} + \mathbf{\Theta}^\mathsf{T})/2$.
 	\end{subsection}
@@
 			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
-			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between aligning the two subspaces.
+			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a trade-off between the alignment of two subspaces.
 			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
-			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
+			We observe that the smallest singular value can be enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by unitary \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
 			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
@@
 			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
-			This transformation not only provides a better trade-off in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
-			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
-			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
-			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris}.
+			This transformation not only improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, but also provides a better trade-off in manipulating both singular values.
+			It suggests the design freedom from larger group size allows better alignment of multiple subspaces simultaneously.
+			% not only provides a better trade-off in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
+			The singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
+			In particular, Fig.
+\subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled (corresponding to the origin) by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
+			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and emphasizes the importance of cooperative wave scattering.
 		\end{subsubsection}
@@
 			Fig.
-\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
-			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_tight} or via optimization approach \eqref{eq:scattering_power}.
+\ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
+			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_optimal} or via optimization approach \eqref{eq:scattering_power}.
 			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
@@
 
-			We first focus on channel shaping subproblem \eqref{op:power_passive}.
+			We first focus on channel power gain maximization problem \eqref{op:power_passive}.
 			Fig. \ref{fg:power_sx} shows the achievable channel power under different \gls{ris} configurations.
@@
 			In the overloaded regime ($K \ge 8$), \gls{bd}-\gls{ris} provides a larger slope of the achievable rate than diagonal \gls{ris}.
-			This is because the \gls{bd}-\gls{ris} can better align the interference subspaces of different users, as discussed in Remark \ref{rm:channel_shaping}.
+			This is because the \gls{bd}-\gls{ris} can better align the interference subspaces of different users.
 			At $K=10$, adding a 64-element diagonal and \gls{bd}-\gls{ris} can improve the weighted sum-rate by \qty{23}{\percent} and \qty{43}{\percent}, respectively.

### 2024-05-01 viva/slides.tex
:ambulance: Compression

@@
 				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_coverage.pdf}
+					\includegraphics{../assets/viva/ris_beamforming_coverage.jpg}
 				}
@@
 				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_security.pdf}
+					\includegraphics{../assets/viva/ris_beamforming_security.jpg}
 				}
@@
 				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_interference.pdf}
+					\includegraphics{../assets/viva/ris_beamforming_interference.jpg}
 				}
@@
 				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_network.pdf}
+					\includegraphics{../assets/viva/ris_beamforming_network.jpg}
 				}
@@
 				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_swipt.pdf}
+					\includegraphics{../assets/viva/ris_beamforming_swipt.jpg}
 				}

### 2024-05-02 assets/viva/region_comparison.tex
:sparkles: Add lite slides

@@
 	width=4.079in,
-	height=3.432in,
+	height=1.732in,
 at={(0.673in,0.356in)},

### 2024-05-02 viva/slides_lite.tex
:sparkles: Add lite slides

--- 2024-05-01 viva/slides.tex
@@
 
-	\begin{frame}{Ancestor of \glsfmtshort{ris}: Reflectarray antenna}
-		% not parabolic with parallel phase front
-		A reflectarray antenna consists of an array illuminated by a feeding antenna \cite{Deng2016}.
+	\begin{frame}{Use cases of \glsfmtshort{ris}}
+		\begin{itemize}
+			\item \textcolor{blue}{Beamforming} of \gls{ris} and transceiver can be jointly designed for a specific performance measure.
+			\item \gls{ris} can be used for backscatter \textcolor{blue}{modulation} by periodically switching the reflection pattern.
+			\item \textcolor{blue}{Channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment.
+		\end{itemize}
+
 		\begin{figure}
 			\centering
-			\includegraphics[width=0.45\textwidth]{../assets/viva/reflectarray.png}
-		\end{figure}
-		A progressive phase shift can be applied to the unit cells (a.k.a. elements) to steer the beam direction.
-	\end{frame}
-
-	\begin{frame}{What is the difference in \glsfmtshort{ris}?}
-		\begin{enumerate}
-			\item Metamaterial enables \textcolor{blue}{real-time control} and \textcolor{blue}{unconventional bahavior}.
-			\item Impinging waves can be \textcolor{blue}{partially refracted and reflected}.
-			\item The feed can be \textcolor{blue}{mobile} while the surface is \textcolor{blue}{scalable and multi-functional}.
-			\item Elements can be physically interconnected for \textcolor{blue}{cooperative wave scattering}.
-		\end{enumerate}
-		\begin{exampleblock}{Refraction}
-			\begin{columns}[T]
-				\begin{column}{.25\textwidth}
-					\begin{figure}
-						\centering
-						\resizebox{\columnwidth}{!}{
-							\input{../assets/viva/nim_focus.tex}
-						}
-					\end{figure}
-				\end{column}
-				% \hfill
-				\begin{column}{.6\textwidth}
-					\vspace{0.5cm}
-					\begin{itemize}
-						\item Negative index material can focus waves
-						\item Amplitude and phase responses can be tuned by diodes and \glsfmtshort{fpga}
-						\item Similar for wave reflection
-					\end{itemize}
-				\end{column}
-			\end{columns}
-		\end{exampleblock}
-		\begin{exampleblock}{Reflection}
-			\vspace{-1cm}
-			\begin{figure}[H]
-				\centering
-				\subfloat[Incident wave\label{fg:wave_incident}]{
-					\resizebox{!}{2.02cm}{
-						\input{../assets/viva/wave_incident.tex}
-					}
-				}
-				\subfloat[Reflected wave\label{fg:wave_reflected}]{
-					\resizebox{!}{2cm}{
-						\input{../assets/viva/wave_reflected.tex}
-					}
-				}
-			\end{figure}
-		\end{exampleblock}
-	\end{frame}
-
-	\begin{frame}{Use case: Beamforming}
-		% \textcolor{blue}{Joint beamforming} design of \gls{ris} and transceiver for a specific performance measure \cite{Wu2020}.
-		% \gls{ris} and transceiver \textcolor{blue}{joint beamforming} design for a specific performance measure \cite{Wu2020}.
-		\textcolor{blue}{Beamforming} of \gls{ris} and transceiver can be jointly designed for a specific performance measure \cite{Wu2020}.
-		\begin{figure}
-			\centering
-			\subfloat[Coverage extension]{
-				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_coverage.jpg}
-				}
-			}
-			\subfloat[Security enhancement]{
-				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_security.jpg}
-				}
-			}
-			\subfloat[Interference mitigation]{
-				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_interference.jpg}
-				}
-			}
-			\\
-			\subfloat[Assist \glsfmtshort{d2d} network]{
-				\resizebox{!}{2.75cm}{
-					\includegraphics{../assets/viva/ris_beamforming_network.jpg}
-				}
-			}
-			\subfloat[Assist information and power transfer]{
-				\resizebox{!}{2.75cm}{
+			\subfloat[Beamforming \cite{Wu2020}]{
+				\resizebox{0.32\textwidth}{!}{
 					\includegraphics{../assets/viva/ris_beamforming_swipt.jpg}
@@
 			}
-		\end{figure}
-	\end{frame}
-
-	\begin{frame}{Use case: Modulation}
-		\gls{ris} can be used for backscatter \textcolor{blue}{modulation} by periodically switching the reflection pattern \cite{Hu2021a}.
-		\begin{figure}
-			\centering
-			\includegraphics[width=0.9\textwidth]{../assets/viva/ris_modulation.pdf}
-		\end{figure}
-	\end{frame}
-
-	\begin{frame}{Use case: Channel shaping}
-		\textcolor{blue}{Channel shaping} exploits the \gls{ris} as a stand-alone device to modify the inherent properties of the propagation environment \cite{Arslan2022}.
-		\begin{figure}
-			\centering
-			\includegraphics[width=0.9\textwidth]{../assets/viva/ris_shaping.pdf}
+			\subfloat[Modulation \cite{Hu2021a}]{
+				\resizebox{0.32\textwidth}{!}{
+					\includegraphics{../assets/viva/ris_modulation.pdf}
+				}
+			}
+			\subfloat[Channel shaping \cite{Arslan2022}]{
+				\resizebox{0.32\textwidth}{!}{
+					\includegraphics{../assets/viva/ris_shaping.pdf}
+				}
+			}
 		\end{figure}
@@
 
-	\begin{frame}{\glsfmtshort{wpt} via radio waves}
-		\vspace{-0.5cm}
-		\begin{table}
-			\footnotesize
-			\rowcolors{2}{gray!25}{white}
-			\renewcommand{\arraystretch}{1.25}
-			\resizebox{\linewidth}{!}{
-				\begin{tabular}{c c c c c c}
-					\toprule
-					% \hiderowcolors
-					Categories                   & Medium                     & Device                     & Power level                            & Frequency                                & Range                     \\ \midrule
-					% \showrowcolors
-					                             & Magnetic resonant coupling & Resonators                 & Up to \SI{10}{\W}                      & \si{\kHz} -- \si{\MHz}                   & \si{\m}                   \\
-					\cellcolor{white}            & Inductive coupling         & Wire coils                 & Up to \SI{10}{\W}                      & \si{\Hz} -- \si{\MHz}                    & \si{\cm}                  \\
-					\multirow{-3}{*}{Near-field} & Capacitive coupling        & Metal plates               & Up to \SI{1}{\W}                       & \si{\kHz} -- \si{\MHz}                   & \si{\mm}                  \\
-					\cellcolor{white}            & \textcolor{blue}{\gls{rf} wave}  & \textcolor{blue}{Rectenna} & \textcolor{blue}{\si{\uW} -- \si{\mW}} & \textcolor{blue}{\si{\MHz} -- \si{\GHz}} & \textcolor{blue}{\si{\m}} \\
-					\multirow{-2}{*}{Far-field}  & Light wave                 & Laser                      & \si{\uW} -- \si{\mW}                   & \si{\THz}                                & \si{\km}                  \\ \bottomrule
-				\end{tabular}
-			}
-		\end{table}
-		\vspace{-0.25cm}
-		\begin{figure}[H]
-			\centering
-			\resizebox{\columnwidth}{!}{
-				\input{../assets/viva/wpt_architecture.tex}
-			}
-			\label{fg:wpt_architecture}
-		\end{figure}
-		\vspace{-1em}
-		The end-to-end \gls{wpt} efficiency is
-		\begin{equation*}
-			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \textcolor{orange}{\underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2}} \textcolor{blue}{\underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3}} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4}
-		\end{equation*}
-		where $\eta_2$ and $\eta_3$ models the channel and rectenna, respectively.
-	\end{frame}
-
-	\begin{frame}{Received signal and harvested power}
+	\begin{frame}{From received signal to harvested power}
 		The rectenna efficiency $\eta_3$ depends on its input waveform (power and shape).
 		\begin{block}{Rectenna model}
-			% \vspace{-0.25cm}
-			% \begin{figure}[H]
-			% 	\centering
-			% 	\subfloat[Rectenna]{
-			% 		\resizebox{0.35\columnwidth}{!}{
-			% 			\input{../assets/viva/rectenna.tex}
-			% 		}
-			% 		\label{fg:rectenna}
-			% 	}
-			% 	\subfloat[Half-wave rectifier]{
-			% 		\resizebox{0.35\columnwidth}{!}{
-			% 			\input{../assets/viva/halfwave_rectifier.tex}
-			% 		}
-			% 		\label{fg:halfwave_rectifier}
-			% 	}
-			% \end{figure}
-			% \vspace{-0.25cm}
 			\begin{itemize}
@@
 			\begin{itemize}
-				\item $n_0 \ge 4$ allows components to compensate each other for higher \gls{dc} power
+				\item $n_0 \ge 4$ allows components to compensate each other for higher \glsfmtshort{dc} power
 				\item High \gls{papr} (e.g., multi-sine) is preferred \cite{Trotter2009}
@@
 			\centering
-			\def\svgwidth{0.5\columnwidth}
+			\def\svgwidth{0.3\columnwidth}
 			\input{../assets/viva/system.eps_tex}
@@
 		\end{block}
-		\begin{block}{Frequency-flat \glsfmtshort{ris} model}
-			\begin{equation*}
-				\mathbf{h}_{n}^\mathsf{H} = \mathbf{h}_{\mathrm{D},n}^\mathsf{H} + \mathbf{h}_{\mathrm{B},n}^\mathsf{H} \mathbf{\Theta} \mathbf{H}_{\mathrm{F},n}
-			\end{equation*}
-		\end{block}
-	\end{frame}
-
-	\begin{frame}{Performance analysis}
 		\begin{block}{Receiver architectures}
@@
 				\subfloat[\gls{ts} receiver]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{0.35\columnwidth}{!}{
 						\input{../assets/viva/receiver_ts.tex}
@@
 				\subfloat[\gls{ps} receiver]{
-					\resizebox{0.48\columnwidth}{!}{
+					\resizebox{0.35\columnwidth}{!}{
 						\input{../assets/viva/receiver_ps.tex}
@@
 			\end{figure}
-		\end{block}
-		\begin{block}{\glsfmtfull{r-e} region of \glsfmtshort{ps}}
-			\vspace{-0.25cm}
-			\begin{align*}
-				R(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\rho) &= \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)},\\
-				z(\boldsymbol{\theta},\mathbf{w}_{\mathrm{I}},\mathbf{w}_{\mathrm{P}},\rho) &= \sum_{i=2,\text{even}}^{n_0}{\beta_i}{\rho^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y^i(t)\right\}\right\}},
-			\end{align*}
-			\begin{equation*}
-				\mathcal{C}_\mathrm{R-E}(P)\triangleq \Bigl\{(r,e) : 0 \le r \le R, \ 0 \le e \le z, \lVert{\mathbf{W}_{\mathrm{I}}}\rVert _\mathrm{F}^2/2 + \lVert{\mathbf{W}_{\mathrm{P}}}\rVert _\mathrm{F}^2/2 \le P \Bigr\}
-			\end{equation*}
 		\end{block}
@@
 		\end{exampleblock}
-	\end{frame}
-
-	\begin{frame}{Simulation results: Number of subbands $N$}
-		\begin{figure}
-			\centering
-			\subfloat[\gls{r-e} region]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{../assets/viva/re_subband.tex}
-				}
-			}
-			\subfloat[Waveform amplitude]{
-				\resizebox{0.45\columnwidth}{!}{
-					\input{../assets/viva/waveform_subband.tex}
-				}
-			}
-		\end{figure}
-		\begin{itemize}
-			\item Increasing $N$ reduces per-subband rate but boosts harvested energy
-			\item Region is convex at small $N$ (favors \gls{ps}) and concave at large $N$ (favors \gls{ts})
-			\item Dedicated multi-sine power waveform is unnecessary at small $N$
-		\end{itemize}
 	\end{frame}
@@
 
-	\begin{frame}{Node architecture}
-		\vspace{-0.5cm}
-		\begin{figure}
-			\centering
-			\subfloat[Block Diagram]{
-				\resizebox{!}{2cm}{
-					\input{../assets/viva/block_diagram.tex}
-				}
-				\label{fg:block_diagram}
-			}
-			\subfloat[\glsentryshort{rfid} tag with harvester \cite{Molina-Farrugia2017}]{
-				\resizebox{!}{2.5cm}{
-					\includegraphics[width=0.9\linewidth]{../assets/viva/passive_tag_prototype.png}
-				}
-				\label{fi:passive_tag_prototype}
-			}\\
-			\subfloat[Equivalent Circuit]{
-				\resizebox{0.7\linewidth}{!}{
-					\input{../assets/viva/equivalent_circuit.tex}
-				}
-				\label{fg:equivalent_circuit}
-			}
-		\end{figure}
-		Impinging waves can be used for powering, modulation, \textcolor{blue}{and beamforming.}
-	\end{frame}
-
-	\begin{frame}{Reflection coefficient}
-		The node changes state by switching load impedance (and reflection coefficient)
-		\begin{equation*}
-			\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0}
-		\end{equation*}
-		\vspace{-0.25cm}
-		\begin{figure}
-			\centering
-			\resizebox{0.6\columnwidth}{!}{
-				\input{../assets/viva/time_structure.tex}
-			}
-		\end{figure}
-		\vspace{-0.25cm}
-		\begin{itemize}
-			\item \gls{ris}: the state at a specific time is known (as a passive beamforming codeword) to the transceiver
-			\begin{equation*}
-				\Gamma_m = \exp(j \phi_m),
-			\end{equation*}
-			\item \gls{bc}: all states occur with equal probability (as part of information codeword) to be detected at the receiver
-			\begin{equation*}
-				\Gamma_m = \alpha_m \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
-			\end{equation*}
-		\end{itemize}
-	\end{frame}
-
-	\begin{frame}{RIScatter system}
-		\begin{table}
-			\rowcolors{2}{gray!25}{white}
-			\renewcommand{\arraystretch}{1.25}
-			\resizebox{\linewidth}{!}{
-				\begin{tabular}{c c c c c c}
-					\toprule
-					\hiderowcolors
-					                       & Backscatter        & Ambient backscatter         & Symbiotic radio          & \gls{ris}           & RIScatter                        \\ \midrule
-					\showrowcolors
-					Information link(s)    & Backscatter        & Coexisting                  & Coexisting               & Primary             & Coexisting                       \\
-					Primary on backscatter & Carrier            & Multiplicative interference & Spreading code           & ---                 & Energy uncertainty               \\
-					Backscatter on primary & ---                & Multiplicative interference & Channel uncertainty      & Passive beamforming & Dynamic passive beamforming      \\
-					Cooperative devices    & ---                & No                          & Transmitter and receiver & ---                 & Transmitter, nodes, and receiver \\
-					Sequential decoding    & ---                & No                          & Primary-to-backscatter   & ---                 & Backscatter-to-primary           \\
-					Reflection pattern by  & Information source & Information source          & Information source       & Channel             & Source, channel, and priority    \\
-					Input distribution     & Equiprobable       & Equiprobable                & Equiprobable or Gaussian & Degenerate          & Flexible                         \\
-					Load-switching speed   & Fast               & Slow                        & Slow                     & Quasi-static        & Arbitrary                        \\ \bottomrule
-				\end{tabular}
-			}
-		\end{table}
-		\begin{columns}
-			\begin{column}{0.4\textwidth}
-				\begin{figure}
-					\centering
-					\resizebox{\linewidth}{!}{
-						\input{../assets/viva/riscatter.tex}
-					}
-					\label{fg:riscatter}
-				\end{figure}
-			\end{column}
-			\begin{column}{0.5\textwidth}
-				\begin{itemize}
-						\item {\color{blue}Primary link:} active legacy transmission from an \gls{rf} source
-						\item {\color{orange}Backscatter link:} passive free-ride transmission from RIScatter nodes
-				\end{itemize}
-			\end{column}
-		\end{columns}
+	\begin{frame}{Signal model}
 		RIScatter renders the node input distribution as a function of information source, \gls{csi}, and priority of coexisting links.
-	\end{frame}
-
-	\begin{frame}{Signal model}
 		\begin{figure}[H]
@@
 		\end{figure}
-		Within each backscatter block, received signal at primary block $n$ is
 		\begin{equation*}
@@
 	\begin{frame}{Joint beamforming, input distribution, and energy detector design}
-		\vspace{-0.125cm}
-		\begin{block}{Achievable rate}
-			\vspace{-0.25cm}
-			\begin{align*}
-				\sum_k R_{\text{B},k} &= \sum\nolimits_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \sum\nolimits_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) \log {P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}})}/{P(\hat{x}_{m_{\mathcal{K}}'})}\\
-				R_{\text{P}} &= \sum\nolimits_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) N \log \left(1 + \frac{\lvert \mathbf{h}^\mathsf{H}(x_{m_{\mathcal{K}}}) \mathbf{w} \rvert^2}{\sigma_w^2}\right)
-			\end{align*}
-		\end{block}
 		\begin{block}{Problem formulation}
@@
 
-	\begin{frame}{Simulation results: Input distribution}
+	\begin{frame}{Simulation results: Input distribution and rate region}
 		\begin{figure}[!t]
 			\centering
-			\subfloat{
-				\resizebox{0.48\linewidth}{!}{
-					\input{../assets/viva/input_distribution.tex}
-				}
-			}
 			\subfloat{
@@
 			}
-		\end{figure}
-		\begin{itemize}
-			\item \gls{bc} and \gls{ris} are special cases of RIScatter with uniform and degenerate input distribution
-			\item Increasing $\rho$ from 0 to 1 creates a smooth transition from backscatter modulation to passive beamforming
-		\end{itemize}
-	\end{frame}
-
-	\begin{frame}{Simulation results: Rate region}
-		\begin{figure}[!t]
-			\centering
 			\subfloat{
@@
 			}
-			\subfloat{
-				\resizebox{0.48\linewidth}{!}{
-					\input{../assets/viva/region_duration.tex}
-				}
-			}
 		\end{figure}
 		\begin{itemize}
-			\item RIScatter backscatter rate is lower than symbiotic radio (due to energy detection) but higher than ambient backscatter (due to adaptive encoding)
-			\item A large spreading factor $N$ improves backscatter \glsfmtshort{ber} but reduces data rate
+			\item Increasing $\rho$ from 0 to 1 evolves from \gls{bc} to \gls{ris}
+			\item Backscatter rate is lower than \glsfmtshort{sr} (due to energy detection) but higher than \glsfmtshort{ambc} (due to adaptive encoding)
 			\item Active and passive transmission can share resource with mutual benefits
+			% creates a smooth transition from backscatter modulation to passive beamforming
 		\end{itemize}
@@
 			Each group contains $L$ connected elements, allowing amplitude and phase control
-			\vspace{-0.25cm}
+			% \vspace{-0.25cm}
 			\begin{equation*}
@@
 			\vspace{-0.5cm}
-			\begin{itemize}
-				\item \emph{Subchannel rearrangement:} allows each group to rearrange and combine the backward and forward subchannels by strength
-				\vspace{-0.25cm}
-				\begin{equation*}
-					\sum_{n=1}^{N_\mathrm{S}} \lvert h_{\mathrm{B},n} \rvert \lvert h_{\mathrm{F},n} \rvert \to \sum_{g=1}^{G} \sum_{l=1}^{L} \lvert h_{\mathrm{B},\pi_{\mathrm{B},g}(l)} \rvert \lvert h_{\mathrm{F},\pi_{\mathrm{F},g}(l)} \rvert
-					\vspace{-0.25cm}
-				\end{equation*}
-				\item \emph{Subspace alignment:} rotate backward-forward (intra-group, multiplicative) and direct-indirect (inter-group, additive) singular vectors
-				\vspace{-0.25cm}
-				\begin{equation*}
-					\mathbf{H} = \overbrace{\mathbf{H}_\mathrm{D} + \sum_g \mathbf{U}_{\mathrm{B},g} \mathbf{\Sigma}_{\mathrm{B},g} \underbrace{\mathbf{V}_{\mathrm{B},g}^\mathsf{H} \mathbf{\Theta}_g \mathbf{U}_{\mathrm{F},g}}_\text{backward-forward} \mathbf{\Sigma}_{\mathrm{F},g} \mathbf{V}_{\mathrm{F},g}^\mathsf{H}}^\text{direct-indirect}
-					\label{eq:channel_equivalent_svd}
-				\end{equation*}
-			\end{itemize}
+			\begin{figure}[H]
+				\centering
+				\resizebox{0.5\columnwidth}{!}{
+					\includegraphics{../assets/viva/bd_ris_architecture_1.eps}
+				}
+				\caption{Architecture of diagonal and \gls{bd}-\gls{ris} \cite{Shen2020a}}
+				\label{fg:bd_ris_architecture_2}
+			\end{figure}
+
 		\end{block}
@@
 
-	\begin{frame}{Some concepts in differential geometry}
-		The feasible domain of $\mathbf{\Theta}_g$ is a unitary Lie group $U(L)$ with Lie algebra $\mathfrak{u}(L)$.
-		\vspace{0.25em}
-		\begin{itemize}
-			\item \emph{Geodesic:} shortest path between two points on a manifold
-			\item \emph{Lie group:} a group that is also a differentiable manifold
-			\item \emph{Lie algebra:} tangent space of Lie group at the identity element
-			% \item \emph{Exponential map:} maps the Lie algebra to the Lie group
-		\end{itemize}
+	\begin{frame}{Proposed geodesic update via Lie algebra}
+		\vspace{-0.25cm}
 		\begin{figure}
 			\centering
-			\includegraphics[width=0.65\textwidth]{../assets/viva/lie_group.pdf}
+			\includegraphics[width=0.5\textwidth]{../assets/viva/lie_group.pdf}
 		\end{figure}
-		A geodesic emanating from the identity with velocity $\mathbf{D} \in \mathfrak{u}(L)$ can be described by the exponential map
-		\begin{equation*}
-			\mathbf{G}_\mathbf{I}(\mu) = \exp(\mu \mathbf{D})
-			\label{eq:geodesic_identity}
-		\end{equation*}
-
-	\end{frame}
-
-	\begin{frame}{Geodesic \glsfmtshort{rcg} via Lie algebra}
+		\vspace{-0.25cm}
 		\begin{block}{Non-geodesic vs geodesic \gls{rcg}}
@@
 
-	\begin{frame}{Singular value redistribution: Optimization approach}
-		\begin{block}{Pareto frontier of singular values}
+	\begin{frame}{Problem formulation}
+		\begin{block}{Pareto frontier of channel singular values}
+			\vspace{-0.25cm}
 			\begin{maxi*}
@@
 		\end{block}
-		\begin{exampleblock}{Solution by group-wise geodesic \glsfmtshort{rcg}}
-			\begin{itemize}
-				\item Faster convergence thanks to appropriate parameter space
-				\item Step size $\mu$ can be obtained by the Armijo rule
-				\item Doubling $\mu$ is computationally efficient $\exp(2 \mu \mathbf{D}_g^{(r)}) = \exp^2(\mu \mathbf{D}_g^{(r)})$
-			\end{itemize}
-		\end{exampleblock}
-	\end{frame}
-
-	\begin{frame}{Singular value redistribution: Analysis approach}
-		\fontsize{6pt}{7.2}\selectfont
-		\begin{proposition}[Degree of freedom]\label{pp:dof}
-			In point-to-point \gls{mimo}, \gls{bd}-\gls{ris} cannot achieve a higher \gls{dof} than diagonal \gls{ris}.
-		\end{proposition}
-		\begin{proposition}[Rank-deficient channel]\label{pp:rank_deficient}
-			If the forward or backward channel is rank-$k$ ($k \le N$), then regardless of the passive \gls{ris} size and architecture, the $n$-th singular value of the equivalent channel is bounded by
-			\begin{align*}
-				\sigma_n(\mathbf{H}) & \le \sigma_{n-k}(\mathbf{T}), &  & \text{if } n > k,         \\
-				\sigma_n(\mathbf{H}) & \ge \sigma_n(\mathbf{T}),     &  & \text{if } n < N - k + 1,
-			\end{align*}
-			where
-			\begin{equation*}
-				\mathbf{T} \mathbf{T}^\mathsf{H} =
-				\begin{cases}
-					\mathbf{H}_\mathrm{D} (\mathbf{I} - \mathbf{V}_\mathrm{F} \mathbf{V}_\mathrm{F}^\mathsf{H}) \mathbf{H}_\mathrm{D}^\mathsf{H}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{F}) = k, \\
-					\mathbf{H}_\mathrm{D}^\mathsf{H} (\mathbf{I} - \mathbf{U}_\mathrm{B} \mathbf{U}_\mathrm{B}^\mathsf{H}) \mathbf{H}_\mathrm{D}, & \text{if } \mathrm{rank}(\mathbf{H}_\mathrm{B}) = k,
-				\end{cases}
-				\label{eq:auxiliary_matrix}
-			\end{equation*}
-			and $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{B}$ are the right and left compact singular matrices of $\mathbf{H}_\mathrm{F}$ and $\mathbf{H}_\mathrm{B}$, respectively.
-		\end{proposition}
-		\begin{proposition}[Unitary \gls{ris} without direct link]\label{pp:fully_connected}
-			If the \gls{bd}-\gls{ris} is unitary and the direct link is absent, then the channel singular values can be manipulated up to
-			\begin{equation*}
-				\mathrm{sv}(\mathbf{H}) = \mathrm{sv}(\mathbf{BF}),
-			\end{equation*}
-			where $\mathbf{B}$ and $\mathbf{F}$ are arbitrary matrices with the same singular values as $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$, respectively,
-		\end{proposition}
-	\end{frame}
-
-	\begin{frame}{Achievable rate maximization}
-		\begin{block}{Problem formulation}
+		\begin{block}{Achievable rate maximization}
+			\vspace{-0.25cm}
 			\begin{maxi*}
@@
 		\end{block}
-		\begin{exampleblock}{Local-optimal solution: \gls{bcd}}
+		\begin{exampleblock}{Solution by group-wise geodesic \glsfmtshort{rcg}}
 			\begin{itemize}
-				\item Passive beamforming $\mathbf{\Theta}$: group-wise geodesic \gls{rcg}
-				\item Active beamforming $\mathbf{W}$: eigenmode transmission and water-filling
-			\end{itemize}
-		\end{exampleblock}
-		\begin{exampleblock}{Low-complexity solution: two-stage}
-			\begin{itemize}
-				\item Shaping stage: channel power gain maximization, solved in closed form
-				\item Transmission stage: eigenmode transmission and water-filling
+				\item Faster convergence thanks to appropriate parameter space
+				\item Optimal and low-complexity solutions
 			\end{itemize}
@@
 
-	\begin{frame}{Simulation results: Singular value}
+	\begin{frame}{Simulation results: Singular value and achievable rate}
 		\begin{figure}
-			\centering
+			\centering \hspace*{-1cm}
 			\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
-				\resizebox{!}{3cm}{
+				\resizebox{!}{3.2cm}{
 					\input{../assets/viva/singular_pareto_sx32.tex}
@@
 			}
-			\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
-				\resizebox{!}{3cm}{
-					\input{../assets/viva/singular_pareto_sx128.tex}
-				}
-			}
 			\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank2_sx128}]{
-				\resizebox{!}{3cm}{
+				\resizebox{!}{3.2cm}{
 					\input{../assets/viva/singular_bound_rank2_sx128.tex}
@@
 			}
-			\label{fg:singular_bound}
+			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
+				\resizebox{!}{3.1cm}{
+					\input{../assets/viva/rate_txrx.tex}
+				}
+			}
 		\end{figure}
@@
 			\item \gls{bd}-\gls{ris} provides \qty{22}{\percent} and \qty{38}{\percent} dynamic range gain for $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$
-			\item Increasing group size enlarges singular value region with better trade-off
-			\item Asymptotic bounds in rank-deficient channels are valid for both architectures
-		\end{itemize}
-	\end{frame}
-
-	\begin{frame}{Simulation results: Achievable rate}
-		\begin{figure}
-			\centering
-			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
-				\resizebox{!}{2.9cm}{
-					\input{../assets/viva/rate_beamforming.tex}
-				}
-			}
-			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
-				\resizebox{!}{2.9cm}{
-					\input{../assets/viva/rate_txrx.tex}
-				}
-			}
-			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
-				\resizebox{!}{2.9cm}{
-					\input{../assets/viva/rate_sx.tex}
-				}
-			}
-			\label{fg:rate}
-		\end{figure}
-		\vspace{1em}
-		\begin{itemize}
-			\item Deficit from low-complexity design vanishes as \gls{ris} evolves towards unitary
-			\item \gls{bd}-\gls{ris} can activate multiple streams at lower transmit power
+			\item Asymptotic bounds are valid for diagonal and \gls{bd}-\gls{ris}
 			\item Percentage rate gain of \gls{bd}-\gls{ris} scales with \gls{mimo} dimension and group size
@@
 
-\begin{section}{Outro}
-	\begin{frame}{Future works: I}
-		\begin{block}{Coherent RIScatter detector}
-			\begin{equation*}
-				y[n] = {\mathbf{h}_{\text{D}}^\mathsf{H} + \mathbf{h}_{\text{C}}^\mathsf{H} {x}} \mathbf{w} {s[n]} + v[n],
-			\end{equation*}
-			\begin{itemize}
-				\item Same model as index modulation
-				\item $x$ has finite support $\to$ $y[n]$ is a Gaussian mixture (non-elementary entropy)
-				\item Achievable rate can be approximated as
-				\begin{equation*}
-					R_\text{B} = \sum_i p(x_i) \log \sum_j p(x_j) \frac{4 \sigma_i^2 \sigma_j^2}{(\sigma_i^2 + \sigma_j^2)^2}
-				\end{equation*}
-				\item \gls{ber} performance?
-				\item Code-domain \gls{noma}?
-			\end{itemize}
-		\end{block}
-	\end{frame}
-
-	\begin{frame}{Future works: II}
-		\begin{block}{Multiplicative broadcast channel}
-			The received signal is
-			\begin{equation*}
-				y_k = h_k \prod_q x_q + n.
-			\end{equation*}
-			\begin{itemize}
-				\item \gls{sic} $\to$ successive channel refinement (better symbol-level precoding)
-				\item \textcolor{blue}{Log-normal} is also maximum entropy distribution
-				\item Product of log-normal is log-normal
-			\end{itemize}
-		\end{block}
-
-		\begin{exampleblock}{Index modulation is a special case with superuser $R = R_1 + R_2$}
-			\begin{itemize}
-				\item $x_1 \sim \mathcal{CN}(0, \sigma_1^2)$ and $x_2$ with finite support
-				\item Index message encoded in the Euclidean distance between $h x_2^{(i)}$
-				\item Decode $x_2$ first, rate depends on {entropy of Gaussian mixture}
-			\end{itemize}
-		\end{exampleblock}
-	\end{frame}
-
-	\begin{frame}{Future works: III}
-		\begin{block}{Rate splitting $\times$ index modulation}
-			The received signal is
-			\begin{equation*}
-				y_k = h_k \theta \sum_q x_q + n.
-			\end{equation*}
-			\vspace{-1em}
-			\begin{itemize}
-				\item Dynamic \gls{ris} achieves the convex hull below by time-sharing \cite{Mu2021a}
-				\begin{figure}
-					\centering
-					\subfloat{
-						\resizebox{0.4\columnwidth}{!}{
-							\includegraphics[scale=1]{../assets/viva/rate_region_noma.jpg}
-						}
-					}
-					\subfloat{
-						\resizebox{0.4\columnwidth}{!}{
-							\includegraphics[scale=1]{../assets/viva/rate_region_oma.jpg}
-						}
-					}
-				\end{figure}
-				\item Common message can be embedded in $\theta$ to push the boundary
-			\end{itemize}
-		\end{block}
-	\end{frame}
-
-	\begin{frame}{Future works: III}
-		\begin{block}{Feasibility of interference alignment by \gls{ris}}
-			\begin{align*}
-				&\text{find} && \mathbf{\Theta} &&&\\
-				&\text{s.t.} && \mathbf{H}^{[kj]} = \mathbf{H}_\mathrm{D}^{[kj]} + \mathbf{H}_\mathrm{B}^{[k]} \mathbf{\Theta} \mathbf{H}_\mathrm{F}^{[j]} = \mathbf{0}, &&& \forall j \neq k\\
-				& && \mathrm{rank}(\mathbf{H}^{[kk]}) = d_k, &&& \forall k
-			\end{align*}
-			\begin{itemize}
-				\item Necessary and sufficient feasibility conditions?
-				\item How many scattering elements are required on expectation?
-				\item Multi-sector \gls{bd}-\gls{ris} \cite{Li2023c}?
-			\end{itemize}
-		\end{block}
-	\end{frame}
-
-\end{section}
-% \end{section}
-
-% \begin{section}{Research Proposal}
-% 	\begin{subsection}{STAR-RIS: Interference Alignment}
-% 		\begin{frame}{STAR-RIS in Interference Channel (I)}
-% 			Consider a STAR-RIS-aided interference \gls{mimo} of $K$ transmitter-receiver pairs.
-% 			\begin{block}{Leakage interference minimization}
-% 				\vspace{-2em}
-% 				\begin{mini!}
-% 					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \bigl\lVert \mathbf{G}_k \underbrace{(\mathbf{H}^{[kj]}_\mathrm{D} + \mathbf{H}^{[k]}_\mathrm{B} \mathbf{\Theta}^{[kj]} \mathbf{H}^{[j]}_{\mathrm{F}})}_{\triangleq \mathbf{H}^{[kj]}} \mathbf{W}_j \bigr\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
-% 					\addConstraint{\mathbf{\Theta}_{\mathrm{T},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{T},g}+\mathbf{\Theta}_{\mathrm{R},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{R},g}=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
-% 					\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
-% 					\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
-% 				\end{mini!}
-% 			\end{block}
-
-% 			\begin{block}{Feasibility of interference alignment}
-% 				\vspace{-1em}
-% 				\begin{subequations}
-% 					\begin{align}
-% 						&\text{find} && \mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\} &&&\\
-% 						&\text{s.t.} && \mathbf{G}_k \mathbf{H}^{[kj]} \mathbf{W}_j = \mathbf{0}, &&& \forall j \neq k\\
-% 						& && \mathrm{rank}(\mathbf{G}_k \mathbf{H}^{[kk]} \mathbf{W}_k) = d_k, &&& \forall k
-% 					\end{align}
-% 				\end{subequations}
-% 			\end{block}
-% 		\end{frame}
-
-% 		\begin{frame}{STAR-RIS in Interference Channel (II)}
-% 			\begin{block}{Weighted sum-rate maximization}
-% 				\vspace{-2em}
-% 				\begin{maxi!}
-% 					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{\sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{[kj]}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kj]}} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
-% 					\addConstraint{\mathbf{\Theta}_{\mathrm{T},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{T},g}+\mathbf{\Theta}_{\mathrm{R},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{R},g}=\mathbf{I}, \quad}{\forall g}{}
-% 					\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k, \quad}{\forall k,}{}
-% 				\end{maxi!}
-% 				where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
-% 				\begin{equation*}
-% 					\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H} + \eta \mathbf{I},
-% 				\end{equation*}
-% 			\end{block}
-% 		\end{frame}
-% 	\end{subsection}
-
-% 	\begin{subsection}{NOMA: Index Modulation}
-% 		\begin{frame}{\glsfmtlong{im} is a Multiplicative NOMA}
-% 			\begin{block}{Multiplicative broadcast channel}
-% 				The received signal is
-% 				\begin{equation*}
-% 					y_k = h_k \prod_q x_q + n.
-% 				\end{equation*}
-% 				\begin{itemize}
-% 					\item \gls{sic} $\to$ successive channel refinement (better symbol-level precoding)
-% 					\item \textcolor{blue}{Log-normal} is also maximum entropy distribution
-% 					\item Product of log-normal is log-normal
-% 				\end{itemize}
-% 			\end{block}
-
-% 			\begin{exampleblock}{Index modulation is a special case with superuser $R = R_1 + R_2$}
-% 				\begin{itemize}
-% 					\item $x_1 \sim \mathcal{CN}(0, \sigma_1^2)$ and $x_2$ with finite support
-% 					\item Index message encoded in the Euclidean distance between $h x_2^{(i)}$
-% 					\item Decode $x_2$ first, rate depends on \textcolor{blue}{entropy of Gaussian mixture}
-% 				\end{itemize}
-% 			\end{exampleblock}
-% 		\end{frame}
-
-% 		\begin{frame}{Multiplicative NOMA: Another Example}
-% 			\begin{block}{Joint transmitter-\gls{ris} encoding}
-% 				The received signal is
-% 				\begin{equation*}
-% 					y_k = h_k \theta \sum_q x_q + n.
-% 				\end{equation*}
-% 				\vspace{-1em}
-% 				\begin{itemize}
-% 					\item Dynamic \gls{ris} can achieve the convex hull of static \gls{ris} \cite{Mu2021a}
-% 					\begin{figure}
-% 						\centering
-% 						\subfloat{
-% 							\resizebox{0.4\columnwidth}{!}{
-% 								\includegraphics[scale=1]{assets/rate_region_noma.jpg}
-% 							}
-% 						}
-% 						\subfloat{
-% 							\resizebox{0.4\columnwidth}{!}{
-% 								\includegraphics[scale=1]{assets/rate_region_oma.jpg}
-% 							}
-% 						}
-% 					\end{figure}
-% 					\item Joint encoding rides additional information on $\theta$ as ``common message''
-% 				\end{itemize}
-% 			\end{block}
-% 		\end{frame}
-% 		\begin{frame}{Thank You}
-% 			\begin{figure}
-% 				\centering
-% 				\includegraphics[width=0.8\columnwidth]{assets/ris.jpg}
-% 			\end{figure}
-% 		\end{frame}
-% 	\end{subsection}
-% \end{section}
-
 \bibliographystyle{IEEEtran}

### 2024-05-18 viva/response.tex
:triangular_flag_on_post: Minor amendment 240518

\documentclass[10pt]{scrartcl}

\usepackage{scrletter}
\usepackage{parskip}

\usepackage[table]{xcolor}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bookmark}
\usepackage{booktabs}
\usepackage[american]{circuitikz}
\usepackage{cite}
\usepackage{fixmath}
\usepackage[acronym]{glossaries-extra}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
% \usepackage{microtype}
\usepackage[short]{optidef}
\usepackage{pgfplots}
\usepackage{ragged2e}
\usepackage[subtle]{savetrees}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage{tabularx}
\usepackage{tikz}

\usepackage[pagewise]{lineno}
\usepackage{xr}
\externaldocument[m-]{../jsac}

% letter signature
\renewcommand*{\raggedsignature}{\raggedright}

% line referencing
\newcommand{\R}[1]{\label{#1}\linelabel{#1}} % use this to set the placement of the line reference tags
\newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}} % use this to reference the tags (print line numbers)

% quoting
\newcommand\declquotedtext[2]{\expandafter\def\csname quotedtext@#1 \endcsname{#2}} % use around text you may want to quote later, but don't want printed in the main text
\newcommand\defquotedtext[2]{\declquotedtext{#1}{#2}#2} % use around text you want to appear in the main text and that you want to quote later
\newcommand\usequotedtext[1]{\csname quotedtext@#1 \endcsname} % use to print the quoted text
\newcommand{\q}[1]{“#1”} % easier way to get double quotes

\usepackage{geometry}
\usepackage[most]{tcolorbox}

% Colors
\definecolor{lightgray}{rgb}{0.9, 0.9, 0.9}
\definecolor{lightyellow}{rgb}{0.98,0.91,0.71}
\definecolor{lightred}{rgb}{0.8,0.4,0.4}

% Boxes
\newtcolorbox{replybox}{colback=lightgray, grow to right by=-2.5mm, grow to
	left by=-2.5mm, boxrule=0pt, boxsep=0pt, breakable, before skip=10pt}
\newtcolorbox{partialbox}{colback=lightyellow, grow to right by=-2.5mm, grow to
	left by=-2.5mm, boxrule=0pt, boxsep=0pt, breakable, before skip=10pt}
\newtcolorbox{todobox}{colback=lightred, grow to right by=-2.5mm, grow to left
	by=-2.5mm, boxrule=0pt, boxsep=0pt, breakable, before skip=10pt}

% Counters
\newcounter{epntcnt}
\newcounter{rpntcnt}
\newcounter{revcnt}

% Environments
\newenvironment{reviewer}{%
	\refstepcounter{revcnt}%
	\setcounter{rpntcnt}{0}%
	\section*{Reviewer \therevcnt}%
}{}
% Editor environment takes an optional argument
\newenvironment{editor}[1][Editorial Decision]{%
	\setcounter{epntcnt}{0}%
	\section*{#1}%
}{}

% Reply Commands
\newcommand{\reply}[1]{%
	\begin{replybox}%
		#1
	\end{replybox}%
}
\newcommand{\partialreply}[1]{%
	\begin{partialbox}%
		Partial reply: \emph{#1}
	\end{partialbox}%
}
\newcommand{\todoreply}[1]{%
	\begin{todobox}%
		Todo reply: \emph{#1}
	\end{todobox}%
}
\newcommand{\needsreply}{%
	\todoreply{This comment needs a reply.}%
}

% Point command differs depending on the environment
\makeatletter
\newcommand{\point}{%
	\medskip\noindent%
	\def\@tmp{editor}%
	\ifx\@tmp\@currenvir \refstepcounter{epntcnt}\theepntcnt\textbf{.}
	\else%
	\def\@tmp{reviewer}%
	\ifx\@tmp\@currenvir \refstepcounter{rpntcnt}\therpntcnt\textbf{.}
	\else\fi\fi%
}
\makeatother

% Renew the commands for the point counters to get the formatting we want in
% both the references and the item labels.
\renewcommand{\therpntcnt}{\textbf{\textup{\therevcnt.\arabic{rpntcnt}}}}
\renewcommand{\theepntcnt}{\textbf{\textup{E.\arabic{epntcnt}}}}

\setlength\parindent{0pt}
\newcommand{\bft}[1]{\mathbf{#1}}

\begin{document}

\setkomavar{date}{\today}
\setkomavar{signature}{Yang Zhao}
\setkomavar{subject}{Re: Minor amendments on thesis ``Reconfigurable Intelligent Surfaces: Beamforming, Modulation, and Channel Shaping''}

\begin{letter}{%
		Prof Geoffrey Ye Li\\
		Department of Electrical and Electronic Engineering\\
		Imperial College London
	}
	\opening{Dear Prof Li,}
	% Thank you for your time and effort in reviewing my thesis
	I would like to express my sincere gratitude to you and Dr Yuan Ding for reviewing my thesis and providing valuable comments, which helped me to improve the quality of the manuscript significantly.
	% I would like to express my sincere gratitude to you for the valuable comments and suggestions, which helped us improve the quality of the manuscript significantly.
	Below is a point-to-point response highlighting all the changes made to the manuscript.
	I hope that the revisions and clarifications make the thesis meet the PhD standards at Imperial.
	\closing{Yours sincerely,}
\end{letter}

\begin{reviewer}
	\point A few typos and run-on sentences. They were marked in the printed thesis which was left with the student.
	\reply {
		Thank you for reading carefully and pointing out the issues. I have carefully proofread the thesis again and corrected all the grammar issues.
		Besides, I noticed many handwritten questions and comments in the printed thesis, which are not included in the official review report.
		Those have also been addressed in the revised manuscript (mostly in terms of footnotes).
	}

	\point Why RIS elements need to be non-resonant and sub-wavelength?
	\reply {
		We have added a bullet point in Chapter 1 to explain the importance of non-resonant and sub-wavelength RIS elements. That is,
		\begin{itemize}
			\item \emph{Non-resonant and sub-wavelength:} Instead of relying on the resonance effect at a specific frequency, RIS ideally functions as a universal scatterer serving a wide range of frequency bands with independent response control. Miniature elements with sub-wavelength dimension and spacing further reduces mutual coupling and improves spatial resolution. However, they pose a great challenge on the design and optimization of the circuit components and matching network.
		\end{itemize}
	}

	\point  Why only reflection is considered, but not transmission? This needs to be clarified.
	\reply {
		It is worth noticing that refraction and reflection are different forms of {wave scattering} where the signal amplitude and phase are altered by the metamaterial.
		Their contributions can be jointly modeled within the scattering matrix $\mathbf{\Theta}$, which corresponds to the $S$-parameters in microwave engineering and the channel matrix in wireless communications.
	}

	\point As for the non-symmetric BD-RIS, it is better to present and discuss an example to
	justify this.
	\reply {
		We have added the following arguments in Chapter 2 to discuss the implementation of asymmetric BD-RIS.

		On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) such that the symmetric constraint (2.8a) can be relaxed.
		A 4-port ring hybrid is illustrated in Fig. \ref{fg:ring_hybrid}.
		\begin{figure}[H]
			\centering
			\includegraphics[width=0.5\textwidth]{../assets/chapter_2/ring_hybrid.pdf}
			\caption{A 4-port asymmetric ring hybrid. Here the arc length between ports are $\Theta_1 = \Theta_2 = \Theta_3 = \lambda / 4$ and $\Theta_4 = 3 \lambda / 4$ where $\lambda$ is the wavelength. The termination admittances $Y_a$ to $Y_d$ are arbitrary and the characteristic admittances of transmission-line sections are not necessarily the same, such that the scattering parameters can be asymmetric. Source: modified from [3].}
			\label{fg:ring_hybrid}
		\end{figure}

		By reconfiguring passive asymmetric components, we end up with the ultimate passive model where energy conservation (2.8b) is the only constraint for each group, as has been widely adopted in quantum physics.
	}

	\point Need to clarify why deterministic multi-sine is better than modulated multi-carrier signals for wireless power transfer?
	\reply {
		We have added the reasoning in Chapter 3 as below.

		Following [73], we superpose a multi-carrier modulated information-bearing waveform to an unmodulated power-dedicated multisine to boost the spectrum and energy efficiency.
		It is worth mentioning that the latter is beneficial for WPT due to its higher PAPR (as discussed in Section 2.2.3.2) and better high-order statistics on expectation (c.f. (3.9b) and (3.9d) in Section 3.2.6).
	}

	\point Will superimposed multi-sine saturate receiver, so that the baseband model cannot
	be used?
	\reply {
		This is a very good point. We have added the following paragraph in Chapter 3 to discuss the receiver saturation issue.

		A major benefit of the superposed waveform is that the multisine is deterministic and its impact on WIT can be completely eliminated by waveform cancellation or translated demodulation [73].
		The former is achieved by subtracting the multisine from the received signal at additional signal processing cost, while the latter requires a demodulator with higher saturation power level.
	}

	\point As for one of the simulation that 40dBm EIRP is used, could we use lower (within regulation limit) power for same conclusion?
	\reply {
		This is indeed a practical issue since the regulation for EIRP is 36 dBm in the 2.4 GHz band.
		I am totally sure that reducing the EIRP by 4dB will only affect the scale of the simulation results without altering any conclusion in Chapter 3.
		Unfortunately, my access to HPC resources at Imperial has been revoked after the registration period, and re-running all codes on my laptop is too time-consuming.
		I have added a footnote in Chapter 3 on this point and published the corrected source code online for everyone to verify the results.
		% In the revised manuscript, EIRP has been reduced to 36 dBm and relevant simulation results have been updated accordingly. We notice that all conclusions in Chapter 3 remain valid.
	}

	\point The pathloss exponent changes at 12 meters, which makes the simulation model not generic to reveal the benefit of employing RIS.
	\reply {
		This is indeed a special modeling choice that simulates an indoor environment where two rooms are connected by a RIS door. The benefits of employing RIS remain valid under different path loss models, as investigated in Chapters 4 and 5.
		We have added the following explanation in Chapter 3.

		We consider a Wi-Fi-like environment at center frequency \qty{2.4}{\GHz} where the channel follows IEEE TGn channel model D [131]. To simulate an indoor environment where two rooms are separated by a wall and a RIS door, we set the path loss exponent to \num{2} up to \qty{10}{\meter} and \num{3.5} onwards to penalize the penetration loss.
	}

	\point For SWIPT, why we only discuss TS and PS, but not FS?
	\reply {
		Frequency Selection (FS) is a practical SWIPT strategy whose R-E performance is strictly dominated by PS.
		We have added the following footnote in Chapter 3 to discuss this.

		It is worth mentioning that many other SWIPT transceiving strategies have been proposed in the literature. In particular, frequency selection is more practical where multisine is used over $n$ subbands and information is carried over the remaining $N-n$ subbands, where $n$ is a design parameter. This can be viewed as a special case of PS and its R-E region is strictly contained with that of the latter, such that we don't include a special study in this work.
	}

	\point $x_k$: need to justify the assumption of coherent channel block is large then BB.
	\reply {
		In the revised Chapter 4, we have emphasized the assumption when discussing Fig. 4.2(a) and introducing the signal model. The following sentence has been added.

		We assume the coherent channel block is longer than backscatter symbol block, and the backscatter symbol block is longer than primary symbol block.

		We assume the channel coherence time is longer than the backscatter symbol duration, \textellipsis
	}
\end{reviewer}

\end{document}

### 2024-05-18 content/chapter_1.tex
:triangular_flag_on_post: Minor amendment 240518

@@
 			\includegraphics[width=0.9\textwidth]{ris_architecture.pdf}
-			\caption{A typical architecture of \gls{ris}. Source: Modified from \cite{Wu2020}.}
+			\caption{A typical architecture of \gls{ris}. Source: modified from \cite{Wu2020}.}
 			\label{fg:ris_architecture}
@@
 This is different from conventional \gls{mimo} systems that features complex hardware and bulky structures.
+			\item \emph{Non-resonant and sub-wavelength:} Instead of relying on the resonance effect at a specific frequency, \gls{ris} ideally functions as a universal scatterer serving a wide range of frequency bands with independent response control.
+Miniature elements with sub-wavelength dimension and spacing further reduces mutual coupling and improves spatial resolution.
+However, they pose a great challenge on the design and optimization of the circuit components and matching network.
 		\end{itemize}
@@
 
-\begin{section}{Outline and Contributions}
-	The thesis is outlined as follows:
-	\begin{itemize}
-		\item Chapter \ref{ch:introduction} provides an overview of the thesis.
+% \begin{section}{Outline and Contributions}
+% 	The thesis is outlined as follows:
+% 	\begin{itemize}
+% 		\item Chapter \ref{ch:introduction} provides an overview of the thesis.
 It introduces the motivation and objectives, raise critical research questions, discusses the characteristics and applications of \gls{ris}, and summarizes the contributions of each research chapter.
 A list of publications is also provided.
-		\item Chapter \ref{ch:background} provides necessary background knowledge for \gls{ris}, \gls{wpt}, \gls{swipt}, and \gls{bc}.
+% 		\item Chapter \ref{ch:background} provides necessary background knowledge for \gls{ris}, \gls{wpt}, \gls{swipt}, and \gls{bc}.
 It covers fundamental principles, hardware implementation, signal and system models, performance metrics, design challenges, and state-of-the-art research.
-		\item Chapter \ref{ch:ris_aided_swipt} investigate the impact of \gls{ris} on wireless information and power transfer. The key contributions include:
-		\begin{itemize}
-			\item Introduce \gls{ris} to a multi-antenna multi-carrier \gls{swipt} system with different receiver architectures;
-			\item Consider joint waveform and beamforming design for the proposed system under a practical energy harvester model;
-			\item Characterize the \gls{r-e} performance trade-off by maximizing harvested energy subject to different communication rate constraints;
-			\item Propose local-optimal and low-complexity algorithms and evaluate their narrow and wideband performance through numerical simulations;
-			\item Discuss the array gain for communication and the scaling order for power transfer in terms of the number of transmit antennas and \gls{ris} elements.
-		\end{itemize}
-		\item Chapter \ref{ch:riscatter} develops a novel scatter protocol that integrates beamforming and modulation. The key contributions include:
-		\begin{itemize}
-			\item Provide an in-depth comparison of \gls{ris} with state-of-the-art \gls{bc} technologies and discuss the key properties of active and passive transmissions coexisting systems;
-			\item Unify \gls{ris} and \gls{bc} as one battery-free cognitive radio called RIScatter, where dispersed or co-located scatter nodes ride over an active primary link to modulate their own information and engineering the legacy channel simultaneously;
-			\item Integrate backscatter modulation and passive beamforming seamlessly into the input distribution design that allows arbitrary trade-off in between;
-			\item Propose a low-complexity cooperative receiver that sequentially decodes both coexisting links and exploits backscatter detection as part of channel training;
-			\item Characterize the achievable primary-backscatter rate region over different designs of input distribution at the scatter nodes, active beamforming at the \gls{ap}, and energy detector at the receiver;
-			\item Discuss the impact of practical factors such as the number of scatter nodes and states, transmit antenna size, backscatter symbol duration, and \gls{snr} on the system performance.
-		\end{itemize}
-		\item Chapter \ref{ch:channel_shaping} explores the ultimate channel shaping capabilities of \gls{ris} in \gls{mimo} systems. The key contributions include:
-		\begin{itemize}
-			\item Quantify the capability of a passive \gls{ris} to reshape the \gls{mimo} \gls{pc} in terms of singular values via analytical bounds and numerical optimization;
-			\item Zoom out to a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior shaping performance in terms of subspace alignment and subchannel rearrangement;
-			\item Propose an efficient \gls{rcg} algorithm for general \gls{bd}-\gls{ris} optimization and provide low-complexity solutions for quadratic problems;
-			\item Characterize the Pareto frontiers of channel singular values and obtain power- and rate-optimal \gls{bd}-\gls{ris} configurations in \gls{mimo} \gls{pc};
-			\item Investigate the impact of \gls{bd}-\gls{ris} on leakage interference suppression and \gls{wsr} maximization in \gls{mimo} \gls{ic};
-			\item Discuss how channel shaping helps to decouple joint \gls{ris}-transceiver designs with comparable performance and significantly reduced complexity.
-		\end{itemize}
-	\end{itemize}
-\end{section}
+% 		\item Chapter \ref{ch:ris_aided_swipt} investigate the impact of \gls{ris} on wireless information and power transfer. The key contributions include:
+% 		\begin{itemize}
+% 			\item Introduce \gls{ris} to a multi-antenna multi-carrier \gls{swipt} system with different receiver architectures;
+% 			\item Consider joint waveform and beamforming design for the proposed system under a practical energy harvester model;
+% 			\item Characterize the \gls{r-e} performance trade-off by maximizing harvested energy subject to different communication rate constraints;
+% 			\item Propose local-optimal and low-complexity algorithms and evaluate their narrow and wideband performance through numerical simulations;
+% 			\item Discuss the array gain for communication and the scaling order for power transfer in terms of the number of transmit antennas and \gls{ris} elements.
+% 		\end{itemize}
+% 		\item Chapter \ref{ch:riscatter} develops a novel scatter protocol that integrates beamforming and modulation. The key contributions include:
+% 		\begin{itemize}
+% 			\item Provide an in-depth comparison of \gls{ris} with state-of-the-art \gls{bc} technologies and discuss the key properties of active and passive transmissions coexisting systems;
+% 			\item Unify \gls{ris} and \gls{bc} as one battery-free cognitive radio called RIScatter, where dispersed or co-located scatter nodes ride over an active primary link to modulate their own information and engineering the legacy channel simultaneously;
+% 			\item Integrate backscatter modulation and passive beamforming seamlessly into the input distribution design that allows arbitrary trade-off in between;
+% 			\item Propose a low-complexity cooperative receiver that sequentially decodes both coexisting links and exploits backscatter detection as part of channel training;
+% 			\item Characterize the achievable primary-backscatter rate region over different designs of input distribution at the scatter nodes, active beamforming at the \gls{ap}, and energy detector at the receiver;
+% 			\item Discuss the impact of practical factors such as the number of scatter nodes and states, transmit antenna size, backscatter symbol duration, and \gls{snr} on the system performance.
+% 		\end{itemize}
+% 		\item Chapter \ref{ch:channel_shaping} explores the ultimate channel shaping capabilities of \gls{ris} in \gls{mimo} systems. The key contributions include:
+% 		\begin{itemize}
+% 			\item Quantify the capability of a passive \gls{ris} to reshape the \gls{mimo} \gls{pc} in terms of singular values via analytical bounds and numerical optimization;
+% 			\item Zoom out to a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior shaping performance in terms of subspace alignment and subchannel rearrangement;
+% 			\item Propose an efficient \gls{rcg} algorithm for general \gls{bd}-\gls{ris} optimization and provide low-complexity solutions for quadratic problems;
+% 			\item Characterize the Pareto frontiers of channel singular values and obtain power- and rate-optimal \gls{bd}-\gls{ris} configurations in \gls{mimo} \gls{pc};
+% 			\item Investigate the impact of \gls{bd}-\gls{ris} on leakage interference suppression and \gls{wsr} maximization in \gls{mimo} \gls{ic};
+% 			\item Discuss how channel shaping helps to decouple joint \gls{ris}-transceiver designs with comparable performance and significantly reduced complexity.
+% 		\end{itemize}
+% 	\end{itemize}
+% \end{section}
 

### 2024-05-18 content/chapter_2.tex
:triangular_flag_on_post: Minor amendment 240518

@@
 		\end{figure}
-		It is worth noticing that refraction and reflection are different implementations of \emph{passive beamforming} where the phase and amplitude of the ambient signal are altered by the metamaterial for a desired net effect.
-		In the next subsection, we will some typical \gls{ris} scattering models and their physical architecture.
+		It is worth noticing that refraction and reflection are different forms of {wave scattering} where the signal amplitude and phase are altered by the metamaterial.
+		Their contributions can be jointly modeled within the scattering matrix $\mathbf{\Theta}$, which corresponds to the $S$-parameters in microwave engineering and the channel matrix in wireless communications.
+		In the next subsection, we will introduce some typical \gls{ris} scattering models and their physical architecture.
 	\end{subsection}
@@
 				\item \emph{Structural component:} Depends on the geometry and material of the scatterer.
-It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or a baseband \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
+It is usually modeled as part of the environment multipath \cite{Thomas2012,Liang2020} or a baseband \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
 				\item \emph{Antenna component:} Depends on the reflection coefficient and load impedance.
@@
 			This question has been answered by \cite{Shen2020a} through a \gls{bd} model.
-			From a network theory perspective \cite{Ivrlac2010}, a general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
+			From a network theory perspective \cite{Ivrlac2010}, a general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components.
 			It allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group, such that both amplitude and phase of the scattered wave can be redistributed with zero power loss.
-			Fig. \ref{fg:bd_ris_architecture_2} illustrates an 8-element \gls{ris} with group size 2 (left) and 4 (right).
+			Fig. \ref{fg:bd_ris_architecture_2} illustrates an 8-element \gls{bd}-\gls{ris} with group size 2 (left) and 4 (right).
 			\begin{figure}[H]
@@
 The group size is a design parameter to balance the circuit complexity and scattering performance.
-Source: Modified from \cite{Shen2020a}.}
+Source: modified from \cite{Shen2020a}.}
 				\label{fg:bd_ris_architecture_2}
@@
 			% 	}
-			% 	\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: Modified from \cite{Shen2020a}.}
+			% 	\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: modified from \cite{Shen2020a}.}
 			% 	\label{fg:bd_ris_architecture_1}
@@
 			% A general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
-			With symmetric components (e.g., capacitors and inductors), the scattering matrix of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$ is \cite{Shen2020a}
+			Using passive symmetric components (e.g., capacitors and inductors), the scattering matrix of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$ is \cite{Shen2020a}
 			\begin{equation}
@@
 			\end{subequations}
-			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} such that the symmetric constraint \eqref{eq:symmetric_property} is unnecessary.
-			This corresponds to the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as has been widely adopted in quantum physics.
+
+			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) such that the symmetric constraint \eqref{eq:symmetric_property} can be relaxed.
+			A 4-port ring hybrid is illustrated in Fig. \ref{fg:ring_hybrid}.
+			\begin{figure}[H]
+				\centering
+				\includegraphics[width=0.5\textwidth]{assets/chapter_2/ring_hybrid.pdf}
+				\caption{A 4-port asymmetric ring hybrid.
+Here the arc length between ports are $\Theta_1 = \Theta_2 = \Theta_3 = \lambda / 4$ and $\Theta_4 = 3 \lambda / 4$ where $\lambda$ is the wavelength.
+The termination admittances $Y_a$ to $Y_d$ are arbitrary and the characteristic admittances of transmission-line sections are not necessarily the same, such that the scattering parameters can be asymmetric.
+Source: modified from \cite{Ahn2006}.}
+				\label{fg:ring_hybrid}
+			\end{figure}
+
+			By reconfiguring passive asymmetric components, we end up with the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as has been widely adopted in quantum physics.
 			The overall scattering matrix of asymmetric \gls{bd}-\gls{ris} is thus \emph{block-diagonal with unitary diagonal blocks}
@@
 			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
-			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
+			Antenna directivity and radiation pattern should also be modeled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
 			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
@@
 
-		The block diagram a closed-loop \gls{ris}-aided \gls{wpt} system is illustrated in Fig. \ref{fg:wpt_architecture}.
+		The block diagram of a closed-loop \gls{ris}-aided \gls{wpt} system is illustrated in Fig. \ref{fg:wpt_architecture}.
 		The \gls{rf} signal is generated and radiated by the energy transmitter, propagated through a wireless channel in the presence of a \gls{ris}, captured by the antenna(s) at the receiver, converted to \gls{dc} power by rectifier(s), then passed to the power management unit.
@@
 Most early \gls{wpt} research (especially from communications society) assume the rectenna works in this region.
-For a received signal $y(t)$, the harvested \gls{dc} power in this region can be modelled as
+For a received signal $y(t)$, the harvested \gls{dc} power in this region can be modeled as
 				\begin{equation}
@@
 Selecting $n_0=2$ yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model.
-For a moderate excitation, the contribution of higher-order terms is significant and should be modelled in the harvested \gls{dc} power.
+For a moderate excitation, the contribution of higher-order terms is significant and should be modeled in the harvested \gls{dc} power.
 				\item \emph{Saturation region:} When the input power level is too high, the diode works in the reverse breakdown region, the rectifier is saturated, and the output power is a constant.
@@
 		One of the most important issues in \gls{swipt} is that the energy harvester requires a much higher received signal power (several orders of magnitude) than the information decoder \cite{Clerckx2019}.
-		Since the channel \gls{rf}-to-\gls{rf} efficiency $\eta_2$ is the primary constraint on the overall power efficiency, how to combat the pathloss and fading effects has been recognized as a crucial research topic for \gls{wpt} \gls{swipt}.
+		Since the channel \gls{rf}-to-\gls{rf} efficiency $\eta_2$ is the primary constraint on the overall power efficiency, how to combat the pathloss and fading effects has been recognized as a crucial research topic for \gls{wpt} and \gls{swipt}.
 		Fortunately, this issue can be effectively mitigated by introducing a \gls{ris} to the environment.
@@
 	\begin{subsection}{Modulation and Coding Schemes}
+		\label{sc:mcs}
 		\gls{bc} and \gls{ris} share the same wave scattering model in Section \ref{sc:principles}, but the reflection coefficient $\Gamma$ in \eqref{eq:reflection_coefficient} is exploited in different manners.
@@
 			\item \emph{\gls{css} \cite{Talla2017}:} A chirp is a signal whose frequency increases or decreases over time.
-			\gls{css} uses wideband linear-frequency modulated chirps to encode information, which is from \gls{dsss} and \gls{fsss} with pseudo-random sequences and \gls{fsk} with discrete frequencies.
+			\gls{css} uses wideband linear-frequency modulated chirps to encode information, which is from \gls{dsss} and \gls{fhss} with pseudo-random sequences and \gls{fsk} with discrete frequencies.
 			In particular, $N+1$ reflection coefficients of the same envelope are sequentially selected at a regular rate $\Delta f$, given by

### 2024-05-18 content/chapter_3.tex
:construction: Add viva slides
:triangular_flag_on_post: Viva
:triangular_flag_on_post: Minor amendment 240518

@@
 		\centering
-		\def\svgwidth{0.9\columnwidth}
+		\def\svgwidth{0.7\columnwidth}
 		\input{assets/chapter_3/system.eps_tex}
-		\caption{An \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
+		\caption{A \gls{ris}-aided multi-carrier \gls{miso} \gls{swipt} system.}
 		\label{fg:system}
@@
 	\begin{subsection}{Transmitted Signal}
-		Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to a multi-carrier unmodulated power-dedicated deterministic multisine to boost the spectrum and energy efficiency.
+		Following \cite{Clerckx2018b}, we superpose a multi-carrier modulated information-bearing waveform to an unmodulated power-dedicated multisine to boost the spectrum and energy efficiency.
+		It is worth mentioning that the latter is beneficial for \gls{wpt} due to its higher \gls{papr} (as discussed in Section \ref{sc:operation_regions}) and better high-order statistics on expectation (c.f.
+\eqref{eq:y_I4} and \eqref{eq:y_P4} in Section \ref{sc:energy_harvester}).
 		The information signal transmitted over subband $n \in \mathcal{N} \triangleq \{1, \dots, N\}$ at time $t$ is
@@
 	\begin{subsection}{Receiving Modes}
-		Following the discussion in Section \ref{sc:receiver_architectures}, we investigate the performance of \gls{ts} and \gls{ps} receivers in this work.
-The \gls{ts} receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
+		Following the discussion in Section \ref{sc:receiver_architectures}, we investigate the performance of \gls{ts} and \gls{ps} receivers in this work.\footnote{It is worth mentioning that many other \gls{swipt} transceiving strategies have been proposed in the literature.
+In particular, frequency selection is more practical where multisine is used over $n$ subbands and information is carried over the remaining $N-n$ subbands, where $n$ is a design parameter.
+This can be viewed as a special case of \gls{ps} and its \gls{r-e} region is strictly contained with that of the latter, such that we don't include a special study in this work.} The \gls{ts} receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively.
 During each session, the transmitter optimizes the waveform for either \gls{wit} or \gls{wpt}, while the receiver activates the information decoder or the energy harvester correspondingly.
@@
 		A major benefit of the superposed waveform is that the multisine is deterministic and its impact on \gls{wit} can be completely eliminated by waveform cancellation or translated demodulation \cite{Clerckx2018b}.
-		Therefore, the achievable rate is
+		The former is achieved by subtracting the multisine from the received signal at additional signal processing cost, while the latter requires a demodulator with higher saturation power level.
+		% , while the latter is achieved by multiplying the received signal with the conjugate of the multisine.
+		The achievable rate is thus
 		\begin{equation}\label{eq:R}
@@
 			\lvert \mathbf{h}_{n}^\mathsf{H}\mathbf{w}_{\mathrm{I},n} \rvert^2
-			& = \mathbf{w}_{a\mathrm{I},n}^\mathsf{H}\mathbf{h}_n\mathbf{h}_n^\mathsf{H}\mathbf{w}_{\mathrm{I},n}\nonumber\\
+			& = \mathbf{w}_{\mathrm{I},n}^\mathsf{H}\mathbf{h}_n\mathbf{h}_n^\mathsf{H}\mathbf{w}_{\mathrm{I},n}\nonumber\\
 			& = \mathbf{w}_{\mathrm{I},n}^\mathsf{H}(\mathbf{h}_{\mathrm{D},n}+\mathbf{V}_n^\mathsf{H}\boldsymbol{\theta})(\mathbf{h}_{\mathrm{D},n}^\mathsf{H}+\boldsymbol{\theta}^\mathsf{H}\mathbf{V}_n)\mathbf{w}_{\mathrm{I},n}\nonumber\\
@@
 The path loss of direct, forward and backward links are denoted by $\Lambda_{\mathrm{D}}$, $\Lambda_{\mathrm{F}}$ and $\Lambda_{\mathrm{B}}$, respectively.
-We consider a large open space Wi-Fi-like environment at center frequency \qty{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
-Specifically, the path loss exponent is \num{2} (i.e., free-space model) up to \qty{10}{\meter}, and \num{3.5} onwards to penalize the potential blockage.
+We consider a Wi-Fi-like environment at center frequency \qty{2.4}{\GHz} where the channel follows IEEE TGn channel model D \cite{Erceg2004}.
+To simulate an indoor environment where two rooms are separated by a wall and a \gls{ris} door, we set the path loss exponent to \num{2} up to \qty{10}{\meter} and \num{3.5} onwards to penalize the penetration loss.
 All fadings are modeled as \gls{nlos} with tap delays and powers specified in model D, and the tap gains are modeled as i.i.d.
@@
 Rectenna parameters are set to $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\qty{50}{\ohm}$ \cite{Clerckx2016a} such that $\beta_2=0.17$ and $\beta_4=957.25$.
-We also choose the average \gls{eirp} as $P=\qty{40}{dBm}$, the receive antenna gain as \qty{3}{dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
+We also choose the average \gls{eirp} as $P=\qty{40}{dBm}$\footnote{One examiner has kindly pointed out that the regulation for EIRP is 36 dBm in the 2.4 GHz band.
+Unfortunately, re-running all the simulations is too time-consuming at this stage and reducing the EIRP by 4dB will only affect the scale of the simulation results without altering any conclusion.
+We have published the source code on \href{https://github.com/snowztail/irs-aided-swipt-joint-waveform-active-and-passive-beamforming-design-under-nonlinear-harvester-model}{this link} for everyone to verify the results.}, the receive antenna gain as \qty{3}{dBi}, the scaling ratio as $\alpha=2$, and the tolerance as $\epsilon=10^{-8}$.
 To further reduce the complexity, we assume $\delta=\rho$ and perform a one-dimensional search for the \gls{lc}-\gls{bcd} algorithm.
@@
 
-		Fig.~\ref{fg:channel_amplitude} reveals how \gls{ris} influences the sorted equivalent subchannel amplitude for one channel realization.
-Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for \gls{wit} and \gls{wpt} are dissimilar.
+		Fig.~\ref{fg:channel_amplitude} reveals how \gls{ris} influences the sorted equivalent subchannel amplitude for one channel realization.\footnote{The results of \gls{ris} with random phase has not been included in Fig.~\ref{fg:channel_amplitude}, since its impact on subchannel amplitude gets averaged out and the result coincides with no \gls{ris}.
+This can be observed later in Figs.
+\subref*{fg:re_irs_1mhz} and \subref*{fg:re_irs_10mhz}.
+In conclusion, the subchannel amplitude gain origins from the optimization of \gls{ris} rather than the extra propagation path.} Due to the flexible subchannel design enabled by passive beamforming, the optimal amplitude distribution for \gls{wit} and \gls{wpt} are dissimilar.
 Under the specified configuration, the \gls{wpt}-optimized \gls{ris} aligns the strong subbands to exploit the rectifier nonlinearity.
@@
 To investigate the performance loss, we truncate the \gls{dc} objective function \eqref{eq:z} at $n_0=2$ such that (i) in the passive beamforming problem, $z(\bar{\mathbf{\Theta}}) = {\beta_2}{\rho}(t_{\mathrm{I},0}+t_{\mathrm{P},0})/2$ and no \gls{sca} is required; (ii) in the waveform design problem, the \gls{wpt}-optimal strategy is the adaptive single sinewave that allocates all power to the multisine at the strongest subband \cite{Clerckx2016a}.
-As shown in Figs.~\subref*{fg:scaling_tx} and \subref*{fg:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dBA} gap compared to the nonlinear model-based \gls{smf} and \gls{gp} designs.
-Third, doubling $M$ brings a \qty{3}{\dB} gain at the output \gls{snr} and a \qty{12}{dBA} increase at the harvested \gls{dc}, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
-Fourth, when the \gls{ris} is very close to the \gls{ap} or \gls{ue}, doubling $L$ can bring a \qty{6}{\dB} gain at the output \gls{snr} and a \qty{24}{dBA} increase at the harvested \gls{dc}.
+As shown in Figs.~\subref*{fg:scaling_tx} and \subref*{fg:scaling_reflector}, those conventional designs do not exploit the harvester nonlinearity and end up with a nearly \qty{20}{dB} gap compared to the nonlinear model-based \gls{smf} and \gls{gp} designs.
+Third, doubling $M$ brings a \qty{3}{\dB} gain at the output \gls{snr} and a \qty{12}{dB} increase at the harvested \gls{dc}, which verified that active beamforming has an array gain of $M$ \cite{Tse2005} with power scaling order $M^2$ under the truncated nonlinear harvester model \cite{Clerckx2016a,Clerckx2018b}.
+Fourth, when the \gls{ris} is very close to the \gls{ap} or \gls{ue}, doubling $L$ can bring a \qty{6}{\dB} gain at the output \gls{snr} and a \qty{24}{dB} increase at the harvested \gls{dc}.
 From the perspective of \gls{wit}, it suggests that passive beamforming can reach an array gain of $L^2$, as indicated by \cite{Wu2019}.
@@
 From the perspective of \gls{wpt}, it suggests that passive beamforming comes with a power scaling order $L^4$ under the truncated nonlinear harvester model.
-We then verify this novel observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel becomes negligible.
+We then verify this observation in a simplified case where the power is uniformly allocated over multisine, all channels are frequency-flat, and $L$ is sufficiently large such that the direct channel becomes negligible.
 Let $X$ be the cascaded small-scale fading coefficient.

### 2024-05-18 content/chapter_4.tex
:triangular_flag_on_post: Minor amendment 240518

@@
 	\end{enumerate}
-	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
-	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference, when the spreading factor is large or small, respectively.
+	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023} to view \gls{sr} as a multiplicative \gls{noma}\footnote{As discussed in Section \ref{sc:mcs}, a time-varying reflection pattern at rate $\Delta f$ can shift the frequency of the scattered signal by $\pm \Delta f$.
+Therefore, the spreading ratio should be carefully chosen to balance backscatter rate and frequency offset.} and perform \gls{sic} from primary to backscatter link.
+	During primary decoding, the backscatter signal can be modeled as channel uncertainty or multiplicative interference, when the spreading factor is large or small, respectively.
 	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} over primary blocks, which is operation-intensive and \gls{csi}-sensitive.
@@
 	It semi-coherently decodes the weak backscatter signal using an energy detector, re-encodes for the exact reflection pattern, then coherently decodes the primary link.
-	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modelled as dynamic passive beamforming afterwards.
+	Thanks to double modulation, backscatter detection can be viewed as part of channel training, and the impact of backscatter modulation can be modeled as dynamic passive beamforming afterwards.
 	The proposed receiver may be built over legacy receivers with minor hardware upgrade, as it only requires one additional energy comparison and re-encoding per backscatter symbol (instead of primary symbol).
@@
 		Each reflection coefficient simultaneously acts as a passive beamforming codeword and part of information codeword.
-		As shown in Fig.~\ref{fg:scatter_comparison}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
+		As shown in Fig.~\subref*{fg:input_distribution}, the reflection pattern of each RIScatter node over time is semi-random and guided by the input probability assigned to each state.
 		This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}, in order to strike a balance between backscatter modulation and passive beamforming.
+		Fig.~\subref*{fg:time_structure} illustrates the reflection pattern of a RIScatter node over time, where ``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
+		We assume the coherent channel block is longer than backscatter symbol block, and the backscatter symbol block is longer than primary symbol block.
 		\begin{figure}[H]
@@
 			\subfloat[Input Distribution]{
-				\resizebox{0.8\columnwidth}{!}{
+				\resizebox{0.6\columnwidth}{!}{
 					\input{assets/chapter_4/input_distribution.tex}
@@
 			\subfloat[Reflection Pattern]{
-				\resizebox{0.8\columnwidth}{!}{
+				\resizebox{0.6\columnwidth}{!}{
 					\input{assets/chapter_4/time_structure.tex}
@@
 			Unlike dynamic \gls{ris} that simply performs a time sharing between reflection states, RIScatter conveys additional information by randomizing the reflection pattern over time while still guaranteeing the probability of occurrence of each state.
-			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modelled as dynamic passive beamforming.
+			Upon successful backscatter detection, the impact of RIScatter nodes on the primary link can be modeled as dynamic passive beamforming.
 			\label{rm:dynamic_passive_beamforming}
@@
 		In the backscatter multiple access system, the \gls{ap} acts as a carrier emitter, the RIScatter nodes modulate over the scattered signal, and the user jointly decodes all nodes.
-		We assume the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference), and the signal going through two or more RIScatter nodes is too weak to be received by the user.
+		We assume the channel coherence time is longer than the backscatter symbol duration, the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference), and the signal going through two or more RIScatter nodes is too weak to be received by the user.
 		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
@@
 		Here, \gls{ris} ensures a constructive superposition of the direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
-		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
+		When $N$ is moderate, the randomly scattered signals should be modeled as interference rather than stable multipath, and the \gls{sr} point should move vertically towards the \gls{ambc} point.
 		Third, RIScatter enables a flexible primary-backscatter trade-off with adaptive input distribution design.
@@
 		\end{figure}
-		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
+		The objective is to demonstrate that RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
 		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
@@
 			The reason is that the relative strength of the scattered signal compared to the direct signal is weakened, such that the nodes cannot make enough difference to the energy detector.
+			It suggests that the nodes should be positioned in the proximity of the user to avoid \gls{snr} imbalance.
 			This, together with Fig.~\subref*{fg:region_beamforming} and \subref*{fg:region_tags}, emphasizes the importance of balancing the primary and backscatter \gls{snr} in the design of active-passive coexisting networks.

### 2024-05-18 content/chapter_5.tex
:triangular_flag_on_post: Minor amendment 240518

@@
 5]{Li2023c}, and \cite[Fig.
-2]{Nerini2024}, where the radiation pattern and circuit topology need to be modelled in the scattering matrix.
+2]{Nerini2024}, where the radiation pattern and circuit topology need to be modeled in the scattering matrix.
 
@@
 	\begin{subsection}{Weighted Sum-Rate Maximization}
-		Finally, we consider weighted sum-rate maximization in \gls{mimo}-\gls{ic} by joint active and passive beamforming design.
+		Finally, we consider weighted sum-rate maximization in \gls{mimo}-\gls{ic} by joint active beamforming design at the transmitters and passive beamforming design at the \gls{ris}.
 		The achievable rate of transmission $k$ is given by
@@
 		\end{maxi!}
-		where $\rho_k$ is the weight of transmission $k$.
+		where $\rho_k$ is the weight that denotes the priority of transmission $k$.
 		The problem is non-convex and can be solved by the \gls{ao} method detailed below.

### 2024-05-18 content/chapter_6.tex
:triangular_flag_on_post: Minor amendment 240518

@@
 		\item \emph{Capacity region of RIScatter:} The current work considers a decoding order from backscatter to primary, corresponding to a primary-optimal point (but not a corner due to energy detector) in the capacity region.
-		If the primary message can be decoded first, it can be modelled as a spreading sequence that enhances the backscatter \gls{snr} by $N$ times (where $N$ is the symbol period ratio) \cite{Long2020a}, corresponding to a backscatter-optimal point.
+		If the primary message can be decoded first, it can be modeled as a spreading sequence that enhances the backscatter \gls{snr} by $N$ times (where $N$ is the symbol period ratio) \cite{Long2020a}, corresponding to a backscatter-optimal point.
 		Besides, the backscatter detection can be performed coherently in the signal domain to further improve the achievable rate.

### 2024-05-18 viva/slides.tex
:sparkles: Add lite slides
:construction: Fix typos
:triangular_flag_on_post: Minor amendment 240518

@@
 \newacronym{dsss}{DSSS}{Direct-Sequence Spread Spectrum}
-\newacronym{fsss}{FSSS}{Frequency-Hopping Spread Spectrum}
+\newacronym{fhss}{FHSS}{Frequency-Hopping Spread Spectrum}
 \newacronym{rz}{RZ}{Return-to-Zero}
@@
 		\begin{equation*}
-			y[n] = \underbrace{\mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \textcolor{orange}{x_k}}_{\mathbf{h}^\mathsf{H}(\textcolor{orange}{x_{\mathcal{K}}})} \mathbf{w} \textcolor{blue}{s[n]} + v[n],
+			y[n] = \underbrace{\Bigl(\mathbf{h}_{\text{D}}^\mathsf{H} + \sum_{k} \alpha_k \mathbf{h}_{\text{C},k}^\mathsf{H} \textcolor{orange}{x_k}\Bigr)}_{\mathbf{h}^\mathsf{H}(\textcolor{orange}{x_{\mathcal{K}}})} \mathbf{w} \textcolor{blue}{s[n]} + v[n],
 		\end{equation*}
@@
 
-	\begin{frame}{Low-Complexity Receiver}
+	\begin{frame}{Low-complexity receiver}
 		We propose a low-complexity receiver that exploits the aforementioned properties to avoid \gls{sic}.
@@
 
-	\begin{frame}{Future works: III}
+	\begin{frame}{Future works: IV}
 		\begin{block}{Feasibility of interference alignment by \gls{ris}}
@@
 \end{section}
-% \end{section}
-
-% \begin{section}{Research Proposal}
-% 	\begin{subsection}{STAR-RIS: Interference Alignment}
-% 		\begin{frame}{STAR-RIS in Interference Channel (I)}
-% 			Consider a STAR-RIS-aided interference \gls{mimo} of $K$ transmitter-receiver pairs.
-% 			\begin{block}{Leakage interference minimization}
-% 				\vspace{-2em}
-% 				\begin{mini!}
-% 					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\}}}{\mathop{\sum\sum}_{j \neq k} \bigl\lVert \mathbf{G}_k \underbrace{(\mathbf{H}^{[kj]}_\mathrm{D} + \mathbf{H}^{[k]}_\mathrm{B} \mathbf{\Theta}^{[kj]} \mathbf{H}^{[j]}_{\mathrm{F}})}_{\triangleq \mathbf{H}^{[kj]}} \mathbf{W}_j \bigr\rVert _{\mathrm{F}}^2}{\label{op:leakage}}{}
-% 					\addConstraint{\mathbf{\Theta}_{\mathrm{T},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{T},g}+\mathbf{\Theta}_{\mathrm{R},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{R},g}=\mathbf{I}, \quad}{\forall g}{\label{co:scatter}}
-% 					\addConstraint{\mathbf{G}_k \mathbf{G}_k^\mathsf{H}=\mathbf{I}, \quad}{\forall k}{\label{co:combiner}}
-% 					\addConstraint{\mathbf{W}_j^\mathsf{H} \mathbf{W}_j=\mathbf{I}, \quad}{\forall j,}{\label{co:precoder}}
-% 				\end{mini!}
-% 			\end{block}
-
-% 			\begin{block}{Feasibility of interference alignment}
-% 				\vspace{-1em}
-% 				\begin{subequations}
-% 					\begin{align}
-% 						&\text{find} && \mathbf{\Theta}, \{\mathbf{G}_k\}, \{\mathbf{W}_k\} &&&\\
-% 						&\text{s.t.} && \mathbf{G}_k \mathbf{H}^{[kj]} \mathbf{W}_j = \mathbf{0}, &&& \forall j \neq k\\
-% 						& && \mathrm{rank}(\mathbf{G}_k \mathbf{H}^{[kk]} \mathbf{W}_k) = d_k, &&& \forall k
-% 					\end{align}
-% 				\end{subequations}
-% 			\end{block}
-% 		\end{frame}
-
-% 		\begin{frame}{STAR-RIS in Interference Channel (II)}
-% 			\begin{block}{Weighted sum-rate maximization}
-% 				\vspace{-2em}
-% 				\begin{maxi!}
-% 					{\scriptstyle{\mathbf{\Theta}, \{\mathbf{W}_k\}}}{\sum_k \rho_k \log \det \biggl(\mathbf{I} + \mathbf{W}_k {\mathbf{H}^{[kj]}}^\mathsf{H} \mathbf{Q}_k^{-1} {\mathbf{H}^{[kj]}} \mathbf{W}_k\biggr)}{\label{op:ic_rate}}{\label{ob:ic_rate}}
-% 					\addConstraint{\mathbf{\Theta}_{\mathrm{T},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{T},g}+\mathbf{\Theta}_{\mathrm{R},g}^\mathsf{H} \mathbf{\Theta}_{\mathrm{R},g}=\mathbf{I}, \quad}{\forall g}{}
-% 					\addConstraint{\lVert \mathbf{W}_k \rVert _\mathrm{F}^2 \le P_k, \quad}{\forall k,}{}
-% 				\end{maxi!}
-% 				where $\mathbf{Q}_k$ is the interference-plus-noise covariance matrix at receiver $k$
-% 				\begin{equation*}
-% 					\mathbf{Q}_k = \sum_{j \ne k} {\mathbf{H}^{[kj]}} \mathbf{W}_j {\mathbf{W}_j}^\mathsf{H} {\mathbf{H}^{[kj]}}^\mathsf{H} + \eta \mathbf{I},
-% 				\end{equation*}
-% 			\end{block}
-% 		\end{frame}
-% 	\end{subsection}
-
-% 	\begin{subsection}{NOMA: Index Modulation}
-% 		\begin{frame}{\glsfmtlong{im} is a Multiplicative NOMA}
-% 			\begin{block}{Multiplicative broadcast channel}
-% 				The received signal is
-% 				\begin{equation*}
-% 					y_k = h_k \prod_q x_q + n.
-% 				\end{equation*}
-% 				\begin{itemize}
-% 					\item \gls{sic} $\to$ successive channel refinement (better symbol-level precoding)
-% 					\item \textcolor{blue}{Log-normal} is also maximum entropy distribution
-% 					\item Product of log-normal is log-normal
-% 				\end{itemize}
-% 			\end{block}
-
-% 			\begin{exampleblock}{Index modulation is a special case with superuser $R = R_1 + R_2$}
-% 				\begin{itemize}
-% 					\item $x_1 \sim \mathcal{CN}(0, \sigma_1^2)$ and $x_2$ with finite support
-% 					\item Index message encoded in the Euclidean distance between $h x_2^{(i)}$
-% 					\item Decode $x_2$ first, rate depends on \textcolor{blue}{entropy of Gaussian mixture}
-% 				\end{itemize}
-% 			\end{exampleblock}
-% 		\end{frame}
-
-% 		\begin{frame}{Multiplicative NOMA: Another Example}
-% 			\begin{block}{Joint transmitter-\gls{ris} encoding}
-% 				The received signal is
-% 				\begin{equation*}
-% 					y_k = h_k \theta \sum_q x_q + n.
-% 				\end{equation*}
-% 				\vspace{-1em}
-% 				\begin{itemize}
-% 					\item Dynamic \gls{ris} can achieve the convex hull of static \gls{ris} \cite{Mu2021a}
-% 					\begin{figure}
-% 						\centering
-% 						\subfloat{
-% 							\resizebox{0.4\columnwidth}{!}{
-% 								\includegraphics[scale=1]{assets/rate_region_noma.jpg}
-% 							}
-% 						}
-% 						\subfloat{
-% 							\resizebox{0.4\columnwidth}{!}{
-% 								\includegraphics[scale=1]{assets/rate_region_oma.jpg}
-% 							}
-% 						}
-% 					\end{figure}
-% 					\item Joint encoding rides additional information on $\theta$ as ``common message''
-% 				\end{itemize}
-% 			\end{block}
-% 		\end{frame}
-% 		\begin{frame}{Thank You}
-% 			\begin{figure}
-% 				\centering
-% 				\includegraphics[width=0.8\columnwidth]{assets/ris.jpg}
-% 			\end{figure}
-% 		\end{frame}
-% 	\end{subsection}
-% \end{section}
-
 \bibliographystyle{IEEEtran}
